### 2022-04-19 Markdown/Manuscript/Child_RMDs/All_Content.Rmd
initial blank template

---
title: "All_Content"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---

```{r child="../Child_RMDs/MS_Body.Rmd", echo=FALSE}
```

\newpage
# References {-}

<div id="refs"></div>
```{r echo=FALSE}
if(!params$X@tables_in_body_lgl){
  child_tabs_1L_chr <- c("../Child_RMDs/MS_Cndl_Tabs_Not_In_Body.Rmd")
}else{
  child_tabs_1L_chr <- NULL
}
if(!params$X@figures_in_body_lgl){
  child_figs_1L_chr <- c("../Child_RMDs/MS_Cndl_Figs_Not_In_Body.Rmd")
}else{
  child_figs_1L_chr <- NULL
}
```

```{r, child = child_tabs_1L_chr, echo=FALSE}
```
```{r, child = child_figs_1L_chr, echo=FALSE}
```
\newpage
\appendix
\counterwithin{figure}{section}
\counterwithin{table}{section}

# Appendix

```{r child="../Child_RMDs/TA_Body.Rmd", echo=FALSE}
```

<!-- NOTE TO SELF: INCORPORATE TA_CODE.RMD -->

### 2022-04-19 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
initial blank template

---
title: "MS_Aims"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---

<!-- Add aims text here -->

### 2022-04-19 Markdown/Manuscript/Child_RMDs/MS_Conclusion.Rmd
initial blank template

---
title: "MS_Conclusion"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
`r ifelse(is.na(params$X@conclusion_1L_chr),"",params$X@conclusion_1L_chr)`

### 2022-04-19 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
initial blank template

---
title: "MS_Intro_Short"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
`r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`

### 2022-04-19 Markdown/Manuscript/Child_RMDs/MS_Tables.Rmd
initial blank template

---
title: "MA_Results"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---

```{r child="XX_Funs.Rmd", echo=FALSE}
```

```{r echo=FALSE}
if(params$X@tables_in_body_lgl){
  child_docs_ls <- list(one = "../Child_RMDs/MS_Tables_1.RMD",
                      two = "../Child_RMDs/MS_Tables_2.RMD")
}else{
    child_docs_ls <- list(one = NULL,
                      two = NULL)
}
```

### 2022-04-19 Markdown/Manuscript/Parent_HTML/Parent_HTML.Rmd
initial blank template

---
bibliography: ../Data/references.bib
output: 
  bookdown::html_document2: 
    pandoc_args: 
      - "--metadata-file=../Header/header_common.yaml"
      - '--lua-filter=../Filters/scholarly-metadata.lua'
      - '--lua-filter=../Filters/author-info-blocks.lua'
params:
  X: NULL
abstract: "`r paste0(stringr::str_replace_all(stringr::str_replace_all(stringr::str_replace_all(stringr::str_replace_all(readLines('../Header/abstract.txt'),'\\\\\\\\textbf',''),'\\{','**'),'\\}','**'),'\\\\\\\\newline','\\\\n'),collapse=' ')`"
graphics: yes
csl: plos.csl
---

```{r echo = F}
library(ready4show)
```

```{r child="../Child_RMDs/All_Content.Rmd", echo=FALSE}
```

### 2022-04-19 Markdown/Manuscript/Parent_PDF/Main_Bookdown_PDF.Rmd
initial blank template

---
bibliography: ../Data/references.bib
output: 
  bookdown::pdf_document2: 
    includes:
      in_header: preamble.tex
    pandoc_args: 
      - "--metadata-file=../Header/header_common.yaml"
      - '--lua-filter=../Filters/scholarly-metadata.lua'
      - '--lua-filter=../Filters/author-info-blocks.lua'
    toc: no
params:
  X: NULL
abstract: "`r paste0(readLines('../Header/abstract.txt'),collapse=' ')`"
graphics: yes
csl: plos.csl
---

```{r echo = F}
## NOTE: EDITED TEMPLATE FILE To Add rotating and multirow packages as per:
# https://stackoverflow.com/questions/31503418/how-to-add-a-latex-package-to-r-journal-template-from-rticle-package-in-r
library(ready4show)
options(tinytex.verbose = TRUE)
library(xtable)
options(xtable.floating = FALSE)
options(xtable.timestamp = "")
```

```{r child="../Child_RMDs/All_Content.Rmd", echo=FALSE}
```

### 2022-04-19 Markdown/Manuscript/Parent_PDF/Parent_PDF.Rmd
initial blank template

---
bibliography: ../Data/references.bib
output: 
  bookdown::pdf_book: 
    base_format: rticles::arxiv_article
    includes:
      in_header: preamble.tex
    pandoc_args: 
      - "--metadata-file=../Header/header_common.yaml"
      - '--lua-filter=../Filters/scholarly-metadata.lua'
      - '--lua-filter=../Filters/author-info-blocks.lua'
  bookdown::pdf_document2: 
    includes:
      in_header: preamble.tex
    pandoc_args: 
      - "--metadata-file=../Header/header_common.yaml"
      - '--lua-filter=../Filters/scholarly-metadata.lua'
      - '--lua-filter=../Filters/author-info-blocks.lua'
    toc: no
## CUSTOM_AUTHORS_PLACEHOLDER ##
params:
  X: NULL
abstract: "`r paste0(readLines('../Header/abstract.txt'),collapse=' ')`"
graphics: yes
csl: plos.csl
---

```{r echo = F}
## NOTE: EDITED TEMPLATE FILE To Add rotating and multirow packages as per:
# https://stackoverflow.com/questions/31503418/how-to-add-a-latex-package-to-r-journal-template-from-rticle-package-in-r
library(ready4show)
options(tinytex.verbose = TRUE)
library(xtable)
options(xtable.floating = FALSE)
options(xtable.timestamp = "")
```

```{r child="../Child_RMDs/All_Content.Rmd", echo=FALSE}
```

### 2022-04-19 Markdown/Manuscript/Parent_Word/Parent_Word.Rmd
initial blank template

---
bibliography: ../Data/references.bib
output:
  bookdown::markdown_document2:
    base_format: "officedown::rdocx_document"
    number_sections: no
    tables:
      style: Table
      layout: autofit
      width: 1.0
      caption:
        style: Table Caption
        pre: 'Table '
        sep: ': '
      conditional:
        first_row: true
        first_column: false
        last_row: false
        last_column: false
        no_hband: false
        no_vband: true
    pandoc_args: 
      - "--metadata-file=../Header/header_common.yaml"
      - '--lua-filter=../Filters/scholarly-metadata.lua'
      - '--lua-filter=../Filters/author-info-blocks.lua'
      - '--lua-filter=../Filters/pagebreaks.lua'
  bookdown::word_document2:
    tables:
      style: Table
      layout: autofit
      width: 1.0
      caption:
        style: Table Caption
        pre: 'Table '
        sep: ': '
      conditional:
        first_row: true
        first_column: false
        last_row: false
        last_column: false
        no_hband: false
        no_vband: true
    pandoc_args: 
      - "--metadata-file=../Header/header_common.yaml"
      - '--lua-filter=../Filters/scholarly-metadata.lua'
      - '--lua-filter=../Filters/author-info-blocks.lua'
      - '--lua-filter=../Filters/pagebreaks.lua'
  officedown::rdocx_document:
    base_format: "bookdown::word_document2"
    number_sections: no
    tables:
      style: Table
      layout: autofit
      width: 1.0
      caption:
        style: Table Caption
        pre: 'Table '
        sep: ': '
      conditional:
        first_row: true
        first_column: false
        last_row: false
        last_column: false
        no_hband: false
        no_vband: true
    pandoc_args: 
      - "--metadata-file=../Header/header_common.yaml"
      - '--lua-filter=../Filters/scholarly-metadata.lua'
      - '--lua-filter=../Filters/author-info-blocks.lua'
      - '--lua-filter=../Filters/pagebreaks.lua'
params:
  X: NULL
abstract: "`r paste0(stringr::str_replace_all(stringr::str_replace_all(stringr::str_replace_all(stringr::str_replace_all(readLines('../Header/abstract.txt'),'\\\\\\\\textbf',''),'\\{','**'),'\\}','**'),'\\\\\\\\newline','\\\\n'),collapse=' ')`"
graphics: yes
csl: plos.csl
---

```{r echo = F}
library(officedown)
library(ready4show)
```
```{r child="../Child_RMDs/All_Content.Rmd", echo=FALSE}
```

### 2022-04-19 setup.R

@@ -1,0 +1,46 @@
+# Manual step: Create Data and Data > CSVs directories and add authors and institutes csvs
+# if(!dir.exists("Output"))
+#   dir.create("Output")
+library(ready4)
+library(ready4show)
+library(bookdown)
+library(rticles)
+X <- Ready4showSynopsis(#background_1L_chr = "Our study is entirely fictional.",
+                        coi_1L_chr = "None declared.",
+                        #conclusion_1L_chr = "These fake results are not interesting.",
+                        digits_int = 3L,
+                        #ethics_1L_chr = "The study was reviewed and granted approval by Awesome University's Human Research Ethics Committee (1111111.1).",
+                        funding_1L_chr = "The study was funded by Orygen, VicHealth and Victoria University.",
+                        #interval_chr = "three months",
+                        keywords_chr = c("open source models","health economics","mental disorders"),
+                        outp_formats_chr = "PDF",
+                        #sample_desc_1L_chr = "The study sample is fake data that pretends to be young people aged 12 to 25 years who attended Australian primary care services for mental health related needs between November 2019 to August 2020.",
+                        title_1L_chr = "A framework for implementing open source models of the systems shaping mental health outcomes in young people")
+X <- renewSlot(X,
+               "authors_r3", 
+               {
+                 read.csv("Data/CSVs/Authors.csv") %>% 
+                     tibble::as_tibble() %>%
+                     ready4show_authors()
+               }
+               ) 
+X <- renewSlot(X,
+               "institutes_r3",
+               {
+                 read.csv("Data/CSVs/Institutes.csv") %>%
+                     tibble::as_tibble() %>%
+                     ready4show_institutes()
+
+               }) 
+X <- renewSlot(X,
+               "a_Ready4showPaths@outp_data_dir_1L_chr",
+               new_val_xx = ".") #####
+authorData(X)
+# Pause for interactivity
+# Make manual edits of Markdown files
+authorReport(X)
+# Pause for interactivity
+# renewSlot(X,
+#           "outp_formats_chr",
+#           new_val_xx = "Word") %>%
+#   authorReport()

### 2022-04-19 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
added abstract

@@
 ---
-`r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`
+<!-- `r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`  -->

### 2022-04-19 setup.R

@@ -1,6 +1,4 @@
 # Manual step: Create Data and Data > CSVs directories and add authors and institutes csvs
-# if(!dir.exists("Output"))
-#   dir.create("Output")
 library(ready4)
 library(ready4show)
 library(bookdown)
@@ -15,7 +13,7 @@ X <- Ready4showSynopsis(#background_1L_chr = "Our study is entirely fictional.",
                         keywords_chr = c("open source models","health economics","mental disorders"),
                         outp_formats_chr = "PDF",
                         #sample_desc_1L_chr = "The study sample is fake data that pretends to be young people aged 12 to 25 years who attended Australian primary care services for mental health related needs between November 2019 to August 2020.",
-                        title_1L_chr = "A framework for implementing open source models of the systems shaping mental health outcomes in young people")
+                        title_1L_chr = "A framework for implementing open source economic models of the systems shaping mental health outcomes in young people")
 X <- renewSlot(X,
                "authors_r3", 
                {
@@ -34,13 +32,22 @@ X <- renewSlot(X,
                }) 
 X <- renewSlot(X,
                "a_Ready4showPaths@outp_data_dir_1L_chr",
-               new_val_xx = ".") #####
+               new_val_xx = ".") 
+X <- renewSlot(X,
+               "abstract_args_ls",
+               {
+                 args_ls <- X@abstract_args_ls
+                 args_ls$abstract_ls <- list(Background = "Open source approaches have the scope to improve the transparency, quality and decision utility of health economic models of mental health systems. ",
+                                             Objectives = "We aimed to develop a conceptual and technical framework for implementing open source mental health systems models and illustrate how it can be applicatied to economic topics in youth mental health.",
+                                             Methods = "We created a software development kit in R to support standardised implementation of open source computational models. We applied this toolkit to developing open source models to map youth mental health measures to health utility, which we assessed against five principles using 17 standards.",
+                                             Results = "Six R packages and a coding style dataset provide a toolkit for implementing mental health models that TIMELY - Transparent, Iterative, Modular, Epitomised, Licensed and Yielding. We used this toolkit to develop utility mapping models that fully met X and partially met Y TIMELY standards.", 
+                                             Conclusion = "Please fund me",
+                                             Data = "Data")
+                 args_ls
+                 }
+               )
 authorData(X)
 # Pause for interactivity
 # Make manual edits of Markdown files
 authorReport(X)
[…]

### 2022-04-20 Markdown/Manuscript/Child_RMDs/Doodles.Rmd
scribbles

---
title: "Doodles"
author: "Matthew Hamilton"
date: '2022-04-19'
output: html_document
---

ISPOR T & V: 
a multiapplication model, transparency, validation,
For a multiapplication model, transparency, validation,
and reporting are ongoing processes. The multiapplica-
tion model is described (transparency)24 and validated,25
and the descriptions and validations are continuously
updated as science and the model evolve.26 In addition,
each instantiation of the model is described, validated,
and reported as each application is done.27

### 2022-04-20 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
scribbles

@@
 <!-- Add aims text here -->
+In this article, we aim to:
+
+i. Describe a suggested framework for implementing open source mental health systems models comprised of a foundation set of modelling principles and standards and a software development toolkit.
+
+ii. Provide a worked example of applying the framework to developing open source models for mapping psychological measures to health utility in young people.

### 2022-04-20 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
scribbles

--- 2022-04-19 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
@@
 ---
-`r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`
+<!-- `r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`  -->
+Mental disorders impose high health, social and economic burdens worldwide [@RN8].
+Much of this burden is potentially avertable [@RN25], but poorly financed mental health systems are ill-equiped for this challenge[@RN22][@RN23].
+A number of high income countries have begun to increase public expenditures on mental health services[@RN26], and in some cases have embraced ambitious programs of major structural reforms to mental health service systems[REFSGOHERE].
+The large and widespread mental health impacts of the COVID pandemic[LANCET], ***CLIMATE AND MENTAL HEALTH*** have also highlighted the need to improve the resilience and emergency preparedness of these systems.
+Policymakers have also been encouraged to place a greater emphasis on tackling the social determinants of mental disorder[@RN11].
+
+Although combinations of investment, service system improvement and policy innovation are required, the theoretical basis for understanding the systems in which mental disorder emerges and is treated is weak [@RN2111].
+It remains unclear why increased investments in mental health care have yet to have discernable impacts on population mental health [@RN26].
+The voluminous evidence base in mental health economics predominantly addresses issues relating to the affordability and value for money of individual programs [@RN34], with the features and behaviours of complex systems relatively unexplored by mental health simulation studies [@RN73].
+The literature about how the requirements, characteristics and performance of mental health services are shaped by spatiotemporal context is underdeveloped [@RN42].
+Better evidence is also required about how to achieve population mental health gain from social determinants based strategies [@RN43].
+
+These major gaps in our understanding of the systems shaping population mental health may partly explain why stringent scientific standards of the type required for the development of therapeutic goods are not applied to the task of re-engineering mental health systems.
+Lively debates within the mental health policymaking community extend beyond normative issues (what should policy aim to achieve) to technical questions (which system financing and organising choices are most likely to achieve specified objectives) that a more mature mental health systems modelling field might better address.
+
+There is a general lack of scientific theories about the properties and behaviours of mental health systems.
+There is therefore scope for increased use of multi-application, dynamic systems modelling approaches that can provide insights about interdependencies between candidate policy settings that static models of isolated scenarios cannot (Occhipinti, 2021).
+These types of insights could be highly relevant to systems planners seeking to prioritise, sequence and target elements of complex reform programs and to anticipate and mitigate risks to the successful implementation of these reforms.
+
+However, developing such models can be major and complex undertakings which in turn may make them particularly prone to errors (see Fig 1 from (Saltelli, 2019)).
+Although, more flexible - higher burden of transparency and validation.
+This leads to computational model issue.
+This leads to open source.
+
+The absence of common standards and taxonomies make it hard to develop these more extensive models by simply combining existing mental health models.
+
+ which can be used to generate credible predictions about how these systems might respond to phased, multi-component redesign strategies
+
+Developing theories that produce valid and useful predictions about the potential impacts and feasibility of phased, multi-component programs of policy and service system reform is most likely a major and long term challenge.
+This undertaking might become more tractable if it could be chunked into smaller tasks and progressed by a research community that, even when working independently, routinely test, re-use and extend each other's work.
+
+Common standards and frameworks for how computational models are developed could address some of these challenges [@RN73].
+
+Outputs from discrete projects should be reproducible, generalisable and able to be linked like Lego bricks to progressively assemble more complex and realistic representations of the systems being modelled.
+
+ Similarly,
+
+However, of the three components that comprise a mental health computer simulation model - the conceptual model, the mathematical model and the computational model - only the first two are typically developed and reported in a manner that facilitates reuse, refinement and extension by others.
+This is problematic as the code implementation is where the theory represented by a simulation model is most fully elaborated.
+In the limited cases where code is made publicly available it is typically in the form of programs (an algorithm that performs one task) rather than code libraries (where the primary algorithm is decomponsed into multiple component algorithms, that can be re-used for a potentially large number of other purposes).
+
+It is frequently claimed that better approaches to the organising and financing of mental health service systems can generate significant gains in population health (Saxena, 2007; Chisholm, 2016).
+Over the last two decades, policymakers in Australia have acted on these claims by investing in a series of major systemic mental health reforms, with improving the mental health of young people a major focus (McGorry, 2017).
+The scope and complexity of these reforms has increased over time, with the Victorian Government’s current plan to overhaul mental health service delivery (Victoria, 2021) arguably the most ambitious to-date.
+
+ Although Australian mental health policy and system design processes has a formally specified role for a robust model-based decision aid, this tool,  the National Mental Health Services Planning Framework, has limited capacity to meet many of the core decision-support requirements of systems planners (Commission, 2020).
+These requirements are diverse and extensive, but are likely to include models that can:
+
+•	anticipate the distribution and evolution of risk factors and need for mental health care by region and population group;
+
+•	identify the budget, equity and efficiency impacts of alternative resource allocations between mental health programs;
+
+•	provide guidance about how services can be optimally configured to achieve outcomes such as minimising wait times, maximising health gain, meeting patient preferences and improving societal welfare; and
+
+•	predict how the supply, location and behaviour of mental healthcare providers change in response to alternative incentives and conditions.
+
+Although a number of these or similar types of models have been developed for the Australian context, the validity, utility and accessibility of these models vary considerably.
+Access to some model-based decision aids and their constituent algorithms and data is highly restricted.
+The relevance of models to current and future decision contexts can also be limited as mental health models are rarely routinely updated with new data and improved algorithms.
+
+In addition to issues relating to improving the quality and usefulness of models that address narrowly defined topics, there are additional challenges concerning the development of models with much broader scope.
+
+Open source frameworks, which have been recommended for the development of mental health modelling field (Long, 2018), have the potential to help address a number of these challenges.
+Open source approaches can promote common standards and interoperability, improve model transparency and facilitate routine updates to rectify errors, update data and add features.
+They may also have educational value in developing the health systems modelling field (Dunlop, 2017).
+
+However, open source computational models also present a range of conceptual, technical, legal and resourcing issues compared to more traditional approaches to model development.
+If these issues can be successfully addressed, there are potential benefits to both decision makers (who will have access to more relevant and trustworthy model-based decision aids) and modellers (for whom complex models will become more tractable through improved access to relevant code and data).

### 2022-04-20 setup.R

@@ -39,8 +39,8 @@ X <- renewSlot(X,
                  args_ls <- X@abstract_args_ls
                  args_ls$abstract_ls <- list(Background = "Open source approaches have the scope to improve the transparency, quality and decision utility of health economic models of mental health systems. ",
                                              Objectives = "We aimed to develop a conceptual and technical framework for implementing open source mental health systems models and illustrate how it can be applicatied to economic topics in youth mental health.",
-                                             Methods = "We created a software development kit in R to support standardised implementation of open source computational models. We applied this toolkit to developing open source models to map youth mental health measures to health utility, which we assessed against five principles using 17 standards.",
-                                             Results = "Six R packages and a coding style dataset provide a toolkit for implementing mental health models that TIMELY - Transparent, Iterative, Modular, Epitomised, Licensed and Yielding. We used this toolkit to develop utility mapping models that fully met X and partially met Y TIMELY standards.", 
+                                             Methods = "We created a software development kit in R to support standardised implementation of mental health systems models. As a worked example, we applied the toolkit to develop open source youth mental health utility mapping models, which we assessed against five principles using 17 standards.",
+                                             Results = "Six R packages and a coding style dataset provide a toolkit for implementing mental health models that are TIMELY - Transparent, Iterative, Modular, Epitomised, Licensed and Yielding. The utility mapping models we developed with this toolkit fully met X and partially met Y TIMELY standards.", 
                                              Conclusion = "Please fund me",
                                              Data = "Data")
                  args_ls

### 2022-05-06 Markdown/Manuscript/Child_RMDs/Doodles.Rmd
still on intro

@@
 and reported as each application is done.27
+
+CLIPPINGS
+It is frequently claimed that better approaches to the organising and financing of mental health service systems can generate significant gains in population health (Saxena, 2007; Chisholm, 2016).
+Over the last two decades, policymakers in Australia have acted on these claims by investing in a series of major systemic mental health reforms, with improving the mental health of young people a major focus (McGorry, 2017).
+The scope and complexity of these reforms has increased over time, with the Victorian Government’s current plan to overhaul mental health service delivery (Victoria, 2021) arguably the most ambitious to-date.
+
+ Although Australian mental health policy and system design processes has a formally specified role for a robust model-based decision aid, this tool,  the National Mental Health Services Planning Framework, has limited capacity to meet many of the core decision-support requirements of systems planners (Commission, 2020).
+These requirements are diverse and extensive, but are likely to include models that can:
+
+•	anticipate the distribution and evolution of risk factors and need for mental health care by region and population group;
+
+•	identify the budget, equity and efficiency impacts of alternative resource allocations between mental health programs;
+
+•	provide guidance about how services can be optimally configured to achieve outcomes such as minimising wait times, maximising health gain, meeting patient preferences and improving societal welfare; and
+
+•	predict how the supply, location and behaviour of mental healthcare providers change in response to alternative incentives and conditions.
+
+Although a number of these or similar types of models have been developed for the Australian context, the validity, utility and accessibility of these models vary considerably.
+
+and to anticipate and mitigate risks to the successful implementation of these reforms
+
+Developing theories that produce valid and useful predictions about the potential impacts and feasibility of phased, multi-component programs of policy and service system reform is most likely a major and long term challenge.
+This undertaking might become more tractable if it could be chunked into smaller tasks and progressed by a research community that, even when working independently, routinely test, re-use and extend each other's work.
+
+However, developing  This leads to computational model issue. This leads to open source.
+
+The absence of common standards and taxonomies make it hard to develop these more extensive models by simply combining existing mental health models.
+
+ which can be used to generate credible predictions about how these systems might respond to phased, multi-component redesign strategies
+
+Common standards and frameworks for how computational models are developed could address some of these challenges [@RN73].
+
+Outputs from discrete projects should be reproducible, generalisable and able to be linked like Lego bricks to progressively assemble more complex and realistic representations of the systems being modelled.
+
+ Similarly,
+
+These knowledge gaps may partly explain why debates within the mental health policymaking community extend beyond normative issues (what should policy aim to achieve) to technical questions (which system financing and organising choices are most likely to achieve specified objectives).
+A more mature mental health systems modelling field might see the technical aspects of re-engineering mental health systems subject to the same stringent scientific standards as those required for the development of therapeutic goods.
+Yet,
+
+If these issues can be successfully addressed, there are potential benefits to both decision makers (who will have access to more relevant and trustworthy model-based decision aids) and modellers (for whom complex models will become more tractable through improved access to relevant code and data).
+
+Access to some model-based decision aids and their constituent algorithms and data is highly restricted.
+The relevance of models to current and future decision contexts can also be limited as mental health models are rarely routinely updated with new data and improved algorithms.
+
+In addition to issues relating to improving the quality and usefulness of models that address narrowly defined topics, there are additional challenges concerning the development of models with much broader scope.
+
+A number of high income countries have begun to increase public expenditures on mental health services[@RN26], and in some cases have embraced ambitious programs of major structural reforms to mental health service systems[REFSGOHERE].
+However

### 2022-05-06 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
still on intro

--- 2022-04-19 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
@@
 ---
-`r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`
+
+<!-- `r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`  -->
+Mental disorders impose high health, social and economic burdens worldwide [@RN8][@GBD2019].
+Much of this burden is potentially avertable [@RN25], but poorly financed and organised mental health systems are ill-equiped for this challenge[@RN22][@RN23].
+The large and widespread additional mental health burdens recently observed during the COVID pandemic[@20211700] and predicted as a potential future consequence of global heating [@page_howard_2010], highlight the need to improve the resilience and adaptability of these systems.
+To help stem growing demand for mental health services, policymakers have also been encouraged to place greater emphasis on tackling the social determinants of mental disorder[@RN11].
+
+Realising significant improvements in population mental health may in part depend on gaining better understanding of the systems in which mental disorder emerges and is treated [@Fried2020].
+Currently, the theoretical basis for understanding these systems is weak [@RN2111].
+Strikingly, it remains unclear why increased investments in mental health care have yet to discernably reduce the prevalence and burden of mental disorders[@RN26].
+The literature about how the requirements, characteristics and performance of mental health services are shaped by spatiotemporal context is underdeveloped [@RN42].
+There is insufficient evidence to identify the social determinants of mental disorders most amenable to preventative interventions, and for which population sub-groups such interventions would be most effective [@RN43].
+
+Mental health simulation studies rarely explore the features and behaviours of complex systems [@RN73], with mental health economic models predominantly addressesing issues relating to the affordability and value for money of individual programs [@RN34].
+Single purpose models that assume static systems, even when sufficiently robust to be formally incorported into Government resource planning processes, may be inadequate for the decision support needs of policymakers and service planners seeking to successfully identify, prioritise, sequence and target multiple elements of complex reform programs [@PC2020].
+
+Multi-application, dynamic systems modelling approaches can provide insights about inter-dependencies between candidate policy settings that static models of isolated scenarios cannot [@Occhipinti2021].
+However, greater use of these types of models may require adaptation on the part of funders, modellers and decision-makers.
+The complexity of multi-application systems models may make them particularly prone to errors [@Saltelli2019], thus requiring greater investments in model transparency and validation [@Eddy2012].
+These types of models can be highly resource intensive to develop and may also never be truly "finished", instead requiring ongoing updates to remain relevant to evolving decision contexts [@Jenkins2021] and to meet additional feature requests from end-users.
+The development, validation and maintenance of these types of models may be simply too onerous and long term a burden to remain the responsibility of a single modelling team and might benefit from collaborations across multiple modelling teams, and perhaps the general mental health modelling field.
+Similarly, more attention to developing partnerships between modellers and decision-makers across the life-cycle of a modelling project can help ensure multi-purpose models can address priority decision topics and have user-interfaces that meet the needs of non-technical users.
+
+Open source frameworks, which have been recommended for the development of mental health modelling field (Long, 2018), have the potential to help address a number of these challenges.
+Open source approaches can promote common standards and interoperability, improve model transparency and facilitate routine updates to rectify errors, update data and add features.
+They may also have educational value in developing the health systems modelling field (Dunlop, 2017).
+
+However, open source computational models also present a range of conceptual, technical, legal and resourcing issues compared to more traditional approaches to model development.
+
+However, of the three components that comprise a mental health computer simulation model - the conceptual model, the mathematical model and the computational model - only the first two are typically developed and reported in a manner that facilitates reuse, refinement and extension by others.
+This is problematic as the code implementation is where the theory represented by a simulation model is most fully elaborated.
+In the limited cases where code is made publicly available it is typically in the form of programs (an algorithm that performs one task) rather than code libraries (where the primary algorithm is decomponsed into multiple component algorithms, that can be re-used for a potentially large number of other purposes).
+
+```{r echo=F}
+# ISPOR T & V: 
+# a multiapplication model, transparency, validation,
+# For a multiapplication model, transparency, validation,
+# and reporting are ongoing processes. The multiapplica-
+# tion model is described (transparency)24 and validated,25
+# and the descriptions and validations are continuously
+# updated as science and the model evolve.26 In addition,
+# each instantiation of the model is described, validated,
+# and reported as each application is done.27
+```

### 2022-05-06 Markdown/Manuscript/Parent_PDF/Parent_PDF.Rmd
still on intro

@@
   X: NULL
-abstract: "`r paste0(readLines('../Header/abstract.txt'),collapse=' ')`"
+abstract: "There is strong in principle support for open source health economic models, but practical barriers limit their availability.
+We propose a set of principles and standards for the implementation of open source health economic models that are TIMELY - Transparent, Iterative, Modular, Epitomised and Yielding.
+We then describe a software framework that we have developed for developing TIMELY models in youth mental health and illustrate this framework with an open source utility mapping project."
+# abstract: "`r paste0(readLines('../Header/abstract.txt'),collapse=' ')`"
 graphics: yes

### 2022-05-06 setup.R

@@ -13,7 +13,7 @@ X <- Ready4showSynopsis(#background_1L_chr = "Our study is entirely fictional.",
                         keywords_chr = c("open source models","health economics","mental disorders"),
                         outp_formats_chr = "PDF",
                         #sample_desc_1L_chr = "The study sample is fake data that pretends to be young people aged 12 to 25 years who attended Australian primary care services for mental health related needs between November 2019 to August 2020.",
-                        title_1L_chr = "A framework for implementing open source economic models of the systems shaping mental health outcomes in young people")
+                        title_1L_chr = "A framework for developing open source economic models of mental health systems")
 X <- renewSlot(X,
                "authors_r3", 
                {
@@ -37,16 +37,16 @@ X <- renewSlot(X,
                "abstract_args_ls",
                {
                  args_ls <- X@abstract_args_ls
-                 args_ls$abstract_ls <- list(Background = "Open source approaches have the scope to improve the transparency, quality and decision utility of health economic models of mental health systems. ",
-                                             Objectives = "We aimed to develop a conceptual and technical framework for implementing open source mental health systems models and illustrate how it can be applicatied to economic topics in youth mental health.",
-                                             Methods = "We created a software development kit in R to support standardised implementation of mental health systems models. As a worked example, we applied the toolkit to develop open source youth mental health utility mapping models, which we assessed against five principles using 17 standards.",
-                                             Results = "Six R packages and a coding style dataset provide a toolkit for implementing mental health models that are TIMELY - Transparent, Iterative, Modular, Epitomised, Licensed and Yielding. The utility mapping models we developed with this toolkit fully met X and partially met Y TIMELY standards.", 
-                                             Conclusion = "Please fund me",
+                 args_ls$abstract_ls <- list(Summary = "There is strong in principle support for open source health economic models, but practical barriers limit their availability. We propose a set of principles and standards for the implementation of open source health economic models that are TIMELY - Transparent, Iterative, Modular, Epitomised and Yielding. We then describe a software framework that we have developed for developing TIMELY models in youth mental health and illustrate this framework with an open source utility mapping project. ",
+                                             # Objectives = "We aimed to develop a conceptual and technical framework for implementing open source mental health systems models and illustrate how it can be applicatied to economic topics in youth mental health.",
[…]

### 2022-05-06 Markdown/Manuscript/Child_RMDs/Doodles.Rmd
minor tweaks

@@
 However
+
+In the limited cases where code is made publicly available it is typically in the form of programs (an algorithm that performs one task) rather than code libraries (where the primary algorithm is decomponsed into multiple component algorithms, that can be re-used for a potentially large number of other purposes).

### 2022-05-06 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
minor tweaks

@@
 <!-- `r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`  -->
-Mental disorders impose high health, social and economic burdens worldwide [@RN8][@GBD2019].
-Much of this burden is potentially avertable [@RN25], but poorly financed and organised mental health systems are ill-equiped for this challenge[@RN22][@RN23].
+Mental disorders impose high health, social and economic burdens worldwide [@RN8;@GBD2019].
+Much of this burden is potentially avertable [@RN25], but poorly financed and organised mental health systems are ill-equiped for this challenge[@RN22;@RN23].
 The large and widespread additional mental health burdens recently observed during the COVID pandemic[@20211700] and predicted as a potential future consequence of global heating [@page_howard_2010], highlight the need to improve the resilience and adaptability of these systems.
@@
 
-Open source frameworks, which have been recommended for the development of mental health modelling field (Long, 2018), have the potential to help address a number of these challenges.
+Open source frameworks, which have been recommended for the development of mental health modelling field [@RN73], have the potential to help address a number of these challenges.
 Open source approaches can promote common standards and interoperability, improve model transparency and facilitate routine updates to rectify errors, update data and add features.
-They may also have educational value in developing the health systems modelling field (Dunlop, 2017).
-
+They may also have educational value in developing the health systems modelling field [@Dunlop2017].
 However, open source computational models also present a range of conceptual, technical, legal and resourcing issues compared to more traditional approaches to model development.
 
-However, of the three components that comprise a mental health computer simulation model - the conceptual model, the mathematical model and the computational model - only the first two are typically developed and reported in a manner that facilitates reuse, refinement and extension by others.
+- Our project - readyforwhatsnext : open source model of the systems shaping the mental health of young people
+- Lack of guidance on open source health economic models and in particular on recommended frameworks for implementing the computational model.
+- Focus computational model.
+Most in need of novel guidance.
+Also: Of the three components that comprise a mental health computer simulation model - the conceptual model, the mathematical model and the computational model - only the first two are typically developed and reported in a manner that facilitates reuse, refinement and extension by others.
 This is problematic as the code implementation is where the theory represented by a simulation model is most fully elaborated.
-In the limited cases where code is made publicly available it is typically in the form of programs (an algorithm that performs one task) rather than code libraries (where the primary algorithm is decomponsed into multiple component algorithms, that can be re-used for a potentially large number of other purposes).
 

### 2022-05-16 Markdown/Manuscript/Child_RMDs/MS_Body.Rmd
refocus on he

---
title: "Manuscript Body"
description: "Main body of paper"
date: "`r Sys.Date()`"
output: html_document
---

# Introduction

```{r child="../Child_RMDs/MS_Intro_Short.Rmd", echo=FALSE}
```
```{r child="../Child_RMDs/MS_Aims.Rmd", echo=FALSE}
```

<!-- # Methods -->
```{r child="../Child_RMDs/MS_Method.Rmd", echo=FALSE}
```

<!-- # Results -->
```{r child="../Child_RMDs/MS_Results.Rmd", echo=FALSE}
```

# Discussion

```{r child="../Child_RMDs/MS_Discussion.Rmd", echo=FALSE}
```

```{r child="../Child_RMDs/MS_Conclusion.Rmd", echo=FALSE}
```

## Availability of data and materials {-#availability-of-data-and-materials}
```{r child="../Child_RMDs/MS_Available_Data_And_Resources.Rmd", echo=FALSE}
```

## Ethics approval {-}
```{r child="../Child_RMDs/MS_Ethics.Rmd", echo=FALSE}
```

## Funding {-#funding}
```{r child="../Child_RMDs/MS_Funding.Rmd", echo=FALSE}
```

## Conflict of Interest {-#conflict-of-interest}
```{r child="../Child_RMDs/MS_COI.Rmd", echo=FALSE}
```

### 2022-05-16 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
refocus on he

@@
 <!-- `r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`  -->
-Mental disorders impose high health, social and economic burdens worldwide [@RN8;@GBD2019].
-Much of this burden is potentially avertable [@RN25], but poorly financed and organised mental health systems are ill-equiped for this challenge[@RN22;@RN23].
-The large and widespread additional mental health burdens recently observed during the COVID pandemic[@20211700] and predicted as a potential future consequence of global heating [@page_howard_2010], highlight the need to improve the resilience and adaptability of these systems.
-To help stem growing demand for mental health services, policymakers have also been encouraged to place greater emphasis on tackling the social determinants of mental disorder[@RN11].
+Computational models have become an essential tool for healthcare policy development [@Erdemir2020].
+Although influential and widely used, these models routinely contain errors [@Radeva2020], are often poorly reproducible [@Jalali2021; @McManus2019] and may be infrequently updated or revised [@Sampson2017].
+To address these issues, there is increasing in principle support for open source health economics models (OSHEMs) that grant open access to and liberal permission to re-use model source code [@Pouwels2022].
+However, in-practice implementation of OSHEMs remains rare [@Emerson2019].
+Some resistence to adoption centers on....
+[@Padula2017] .
 
-Realising significant improvements in population mental health may in part depend on gaining better understanding of the systems in which mental disorder emerges and is treated [@Fried2020].
-Currently, the theoretical basis for understanding these systems is weak [@RN2111].
-Strikingly, it remains unclear why increased investments in mental health care have yet to discernably reduce the prevalence and burden of mental disorders[@RN26].
-The literature about how the requirements, characteristics and performance of mental health services are shaped by spatiotemporal context is underdeveloped [@RN42].
-There is insufficient evidence to identify the social determinants of mental disorders most amenable to preventative interventions, and for which population sub-groups such interventions would be most effective [@RN43].
+A major shift in how health economic models are implemented.....They may also have educational value in developing the health systems modelling field [@Dunlop2017].
+However, open source computational models also present a range of conceptual, technical, legal and resourcing issues compared to more traditional approaches to model development.
 
-Mental health simulation studies rarely explore the features and behaviours of complex systems [@RN73], with mental health economic models predominantly addressesing issues relating to the affordability and value for money of individual programs [@RN34].
-Single purpose models that assume static systems, even when sufficiently robust to be formally incorported into Government resource planning processes, may be inadequate for the decision support needs of policymakers and service planners seeking to successfully identify, prioritise, sequence and target multiple elements of complex reform programs [@PC2020].
+The health economics field i
 
-Multi-application, dynamic systems modelling approaches can provide insights about inter-dependencies between candidate policy settings that static models of isolated scenarios cannot [@Occhipinti2021].
-However, greater use of these types of models may require adaptation on the part of funders, modellers and decision-makers.
-The complexity of multi-application systems models may make them particularly prone to errors [@Saltelli2019], thus requiring greater investments in model transparency and validation [@Eddy2012].
-These types of models can be highly resource intensive to develop and may also never be truly "finished", instead requiring ongoing updates to remain relevant to evolving decision contexts [@Jenkins2021] and to meet additional feature requests from end-users.
-The development, validation and maintenance of these types of models may be simply too onerous and long term a burden to remain the responsibility of a single modelling team and might benefit from collaborations across multiple modelling teams, and perhaps the general mental health modelling field.
-Similarly, more attention to developing partnerships between modellers and decision-makers across the life-cycle of a modelling project can help ensure multi-purpose models can address priority decision topics and have user-interfaces that meet the needs of non-technical users.
+copyrights, model misuse, confidential data, software, and time/resources [@Wu2019]
+cooperation [@Arnold2010]
+coding framework / guidance [@Alarid2019]
+10 rules [@Erdemir2020]
+Sys review
+Over the last decade there have been
+the potential to increase the transparency, reproducibility and reuse of health economic analyses.
 
@@
 Open source approaches can promote common standards and interoperability, improve model transparency and facilitate routine updates to rectify errors, update data and add features.
-They may also have educational value in developing the health systems modelling field [@Dunlop2017].
-However, open source computational models also present a range of conceptual, technical, legal and resourcing issues compared to more traditional approaches to model development.
 

### 2022-05-16 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
refocus on he

---
title: "MA_Results"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---

```{r child="MS_Tables.Rmd", echo=FALSE}
```
```{r child="MS_Figures.Rmd", echo=FALSE}
```
<!-- Add child RMDs for results content -->

# Motivation
Mental disorders impose high health, social and economic burdens worldwide [@RN8;@GBD2019]. Much of this burden is potentially avertable [@RN25], but poorly financed and organised mental health systems are ill-equiped for this challenge[@RN22;@RN23]. The large and widespread additional mental health burdens recently observed during the COVID pandemic[@20211700] and predicted as a potential future consequence of global heating [@page_howard_2010], highlight the need to improve the resilience and adaptability of these systems. To help stem growing demand for mental health services, policymakers have also been encouraged to place greater emphasis on tackling the social determinants of mental disorder[@RN11].

Realising significant improvements in population mental health may in part depend on gaining better understanding of the systems in which mental disorder emerges and is treated [@Fried2020]. Currently, the theoretical basis for understanding these systems is weak [@RN2111]. Strikingly, it remains unclear why increased investments in mental health care have yet to discernably reduce the prevalence and burden of mental disorders[@RN26].  The literature about how the requirements, characteristics and performance of mental health services are shaped by spatiotemporal context is underdeveloped [@RN42]. There is insufficient evidence to identify the social determinants of mental disorders most amenable to preventative interventions, and for which population sub-groups such interventions would be most effective [@RN43].

Mental health simulation studies rarely explore the features and behaviours of complex systems [@RN73], with mental health economic models predominantly addressing issues relating to the affordability and value for money of individual programs [@RN34]. Single purpose models that assume static systems, even when sufficiently robust to be formally incorporated into Government resource planning processes, may be inadequate for the decision support needs of policymakers and service planners seeking to successfully identify, prioritise, sequence and target multiple elements of complex reform programs [@PC2020].

Multi-application, dynamic systems modelling approaches can provide insights about inter-dependencies between candidate policy settings that static models of isolated scenarios cannot [@Occhipinti2021]. However, greater use of these types of models may require adaptation on the part of funders, modellers and decision-makers. The complexity of multi-application systems models may make them particularly prone to errors [@Saltelli2019], thus requiring greater investments in model transparency and validation [@Eddy2012]. These types of models can be highly resource intensive to develop and may also never be truly "finished", instead requiring ongoing updates to remain relevant to evolving decision contexts [@Jenkins2021] and to meet additional feature requests from end-users. The development, validation and maintenance of these types of models may be simply too onerous and long term a burden to remain the responsibility of a single modelling team and might benefit from collaborations across multiple modelling teams, and perhaps the general mental health modelling field. Similarly, more attention to developing partnerships between modellers and decision-makers across the life-cycle of a modelling project can help ensure multi-purpose models can address priority decision topics and have user-interfaces that meet the needs of non-technical users.

# TIMELY principles and standards

# ready4 Framework

# Application

## readyforwhatsnext

## Worked example

### 2022-05-16 setup.R

@@ -13,7 +13,7 @@ X <- Ready4showSynopsis(#background_1L_chr = "Our study is entirely fictional.",
                         keywords_chr = c("open source models","health economics","mental disorders"),
                         outp_formats_chr = "PDF",
                         #sample_desc_1L_chr = "The study sample is fake data that pretends to be young people aged 12 to 25 years who attended Australian primary care services for mental health related needs between November 2019 to August 2020.",
-                        title_1L_chr = "A framework for developing open source economic models of mental health systems")
+                        title_1L_chr = "A framework for open source computational models of mental health systems")
 X <- renewSlot(X,
                "authors_r3", 
                {

### 2022-05-17 Markdown/Manuscript/Child_RMDs/Doodles.Rmd
intro done

@@
 ---
+
+10 rules [@Erdemir2020]
+.....DARTH
+
+[@Sampson2019] - 
+development of networks of health economists that are working on a particular disease area. 
+f reference models, open-source modelling, or model registries are to be part of the model development process, then standards need to be developed to guide analysts in achieving best practice.
+The availability of guidance can help to create confidence in researchers to pursue transparency.
+Yet, selecting the best standards to use can also be challenging [56].
+Wider uptake—and appropriate use—of standards, by both modellers and journals, should be encouraged, and research should evaluate the suitability of guidance relating to transparency.
+However, transparency depends on the code being well structured and clearly commented and a user or reviewer is required to have knowledge of the language in order to validate, use or adapt the model.
+There is a steep learning curve for analysts unfamiliar with script-based models
+There may also be barriers in the communication of models due to a lack of knowledge for end users.
+However, this can be substantially mitigated with the use of open access interface packages, like the R package Shiny, which can be used to turn an R model into an interactive web application [58].
+This allows a user without any R knowledge to use or, in part, validate the model.
+Collaboration
+----
+@Erdemir2020] - 
+We recommend the use of existing repositories for disseminating code and models.
+
+there is a need for guidance, frameworks and templates
+Guidance needed for implementation. Current transparency guidance not good enough.
+
+ome resistence to adoption centers on.... [@Padula2017] . 
+HE commercial...[@Feenstra2022],
+   author]
+
+A major shift in how health economic models are implemented.....They may also have educational value in developing the health systems modelling field [@Dunlop2017].
+However, open source computational models also present a range of conceptual, technical, legal and resourcing issues compared to more traditional approaches to model development.
+
+The health economics field i
+
+cooperation [@Arnold2010]
+coding framework / guidance [@Alarid2019]
+10 rules [@Erdemir2020]
+Sys review??
+
+Maybe [@Feenstra2022] - 
+Model complexity increases validation needs as does multi-purpose modelling
+conceptual model, input data, computational model, operational model
+International collaboration in validation
+Need for documentation
+Commercial ownership of HE models reduce scope for open-source
+finances, accountability, and ownership barriers to OS
+still not very widespread in HE decision model
+would require more resources, could greatly increase transparency
+distinguishing grades of open source
+Model validation should hence become more structured and standardized, as well as more transparent.
+
+Modular validation - Ghabri, Justifies extensive validation
+Citing Dunlop - HE lagging behind other modelling fields
+
+Australian
+poor validation - ghabri
+
+Over the last decade there have been
+the potential to increase the transparency, reproducibility and reuse of health economic analyses.
+
+Open source frameworks, which have been recommended for the development of mental health modelling field [@RN73], have the potential to help address a number of these challenges.
+Open source approaches can promote common standards and interoperability, improve model transparency and facilitate routine updates to rectify errors, update data and add features.
+
+- Our project - readyforwhatsnext : open source model of the systems shaping the mental health of young people
+- Lack of guidance on open source health economic models and in particular on recommended frameworks for implementing the computational model.
+- Focus computational model.
+Most in need of novel guidance.
+Also: Of the three components that comprise a mental health computer simulation model - the conceptual model, the mathematical model and the computational model - only the first two are typically developed and reported in a manner that facilitates reuse, refinement and extension by others.
+This is problematic as the code implementation is where the theory represented by a simulation model is most fully elaborated.
 

### 2022-05-17 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
intro done

--- 2022-04-19 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
@@
 <!-- Add aims text here -->
+As part of a project to develop an open source model of youth mental health, we have developed a framework that consolidates and refines these and other recommended standards for OSHEMs and provides a set of tools to help implement models that conform to these standards.
+In this paper we describe the rationale for and content of the framework we have developed and illustrate its practical application with a worked example.

### 2022-05-17 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
intro done

@@
 Computational models have become an essential tool for healthcare policy development [@Erdemir2020].
-Although influential and widely used, these models routinely contain errors [@Radeva2020], are often poorly reproducible [@Jalali2021; @McManus2019] and may be infrequently updated or revised [@Sampson2017].
-To address these issues, there is increasing in principle support for open source health economics models (OSHEMs) that grant open access to and liberal permission to re-use model source code [@Pouwels2022].
-However, in-practice implementation of OSHEMs remains rare [@Emerson2019].
-Some resistence to adoption centers on....
-[@Padula2017] .
+Although influential and widely used, these models routinely contain errors [@Radeva2020], are rarely adequately validated [@Ghabri2019], can be difficult to reproduce [@Jalali2021; @McManus2019; @Bermejo2017] and are likely to be infrequently updated or revised [@Sampson2017].
+To help address these issues, there is increasing in principle support for open source health economics models (OSHEMs) that grant open access to and liberal permissions to re-use model source code [@Pouwels2022].
+However, in-practice implementation of OSHEMs remains rare [@Emerson2019; @Michalczyk2018; @Feenstra2022].
+Barriers to adoption include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations [@Pouwels2022; @Wu2019].
+As many health economic models are owned by pharmaceutical companies and consultancies, commercial considerations may also limit adoption of OSHEMs [@Feenstra2022].
 
-A major shift in how health economic models are implemented.....They may also have educational value in developing the health systems modelling field [@Dunlop2017].
-However, open source computational models also present a range of conceptual, technical, legal and resourcing issues compared to more traditional approaches to model development.
-
-The health economics field i
-
-copyrights, model misuse, confidential data, software, and time/resources [@Wu2019]
-cooperation [@Arnold2010]
-coding framework / guidance [@Alarid2019]
-10 rules [@Erdemir2020]
-Sys review
-Over the last decade there have been
-the potential to increase the transparency, reproducibility and reuse of health economic analyses.
-
-Open source frameworks, which have been recommended for the development of mental health modelling field [@RN73], have the potential to help address a number of these challenges.
-Open source approaches can promote common standards and interoperability, improve model transparency and facilitate routine updates to rectify errors, update data and add features.
-
-- Our project - readyforwhatsnext : open source model of the systems shaping the mental health of young people
-- Lack of guidance on open source health economic models and in particular on recommended frameworks for implementing the computational model.
-- Focus computational model.
-Most in need of novel guidance.
-Also: Of the three components that comprise a mental health computer simulation model - the conceptual model, the mathematical model and the computational model - only the first two are typically developed and reported in a manner that facilitates reuse, refinement and extension by others.
-This is problematic as the code implementation is where the theory represented by a simulation model is most fully elaborated.
+There is also a need to develop good practice guidance for implementing OSHEMs [@Sampson2019], which is currently scarce and piecemeal.
+Current health economist best practice guidelines on model transparency was published ten years ago [@Eddy2012] and contained recommendations on technical and non-technical model documentation but not about how model code and data are to be shared.
+More recent and more general guidance recommends the sharing of model code and data using repositories such as GitHub and Zenodo as well as the use of version control systems such as Git across the development lifecycle of a modelling project [@Erdemir2020].
+A coding framework for OSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions[@Alarid2019].
 

### 2022-05-19 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
minor tweaks to mental health section

--- 2022-04-19 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
@@
 <!-- Add aims text here -->
+We have consolidated and refined these and other recommended standards for OSHEMs and developed tools to help implement them as part of a framework for developing an open source model of youth mental health.
+In this paper, we describe our motivation for developing the framework, the rationale for each standard specified in the framework, the toolkits we have developed and a worked example of a modelling project developed with the framework.

### 2022-05-19 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
minor tweaks to mental health section

---
title: "MS_Discussion"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---

MH systems design is not a pharma led project - less concerns about commercial ownership

greater use of these types of models may require adaptation on the part of funders, modellers and decision-makers. T

### 2022-05-19 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
minor tweaks to mental health section

@@
 <!-- `r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`  -->
-Computational models have become an essential tool for healthcare policy development [@Erdemir2020].
+Computational models have become essential tools for healthcare policy development [@Erdemir2020].
 Although influential and widely used, these models routinely contain errors [@Radeva2020], are rarely adequately validated [@Ghabri2019], can be difficult to reproduce [@Jalali2021; @McManus2019; @Bermejo2017] and are likely to be infrequently updated or revised [@Sampson2017].
-To help address these issues, there is increasing in principle support for open source health economics models (OSHEMs) that grant open access to and liberal permissions to re-use model source code [@Pouwels2022].
-However, in-practice implementation of OSHEMs remains rare [@Emerson2019; @Michalczyk2018; @Feenstra2022].
+To help address these issues, there is growing support for greater use of open source health economics models (OSHEMs) that grant open access to and liberal permissions to re-use model source code [@Pouwels2022].
+However, to date actual implementations of OSHEMs remain rare [@Emerson2019; @Michalczyk2018; @Feenstra2022].
 Barriers to adoption include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations [@Pouwels2022; @Wu2019].
-As many health economic models are owned by pharmaceutical companies and consultancies, commercial considerations may also limit adoption of OSHEMs [@Feenstra2022].
+As many health economic models are owned by pharmaceutical companies and consultancies, commercial considerations may also be limiting uptake of OSHEMs [@Feenstra2022].
 
-There is also a need to develop good practice guidance for implementing OSHEMs [@Sampson2019], which is currently scarce and piecemeal.
-Current health economist best practice guidelines on model transparency was published ten years ago [@Eddy2012] and contained recommendations on technical and non-technical model documentation but not about how model code and data are to be shared.
-More recent and more general guidance recommends the sharing of model code and data using repositories such as GitHub and Zenodo as well as the use of version control systems such as Git across the development lifecycle of a modelling project [@Erdemir2020].
+There is also a need to develop good practice guidance for implementing OSHEMs [@Sampson2019].
+Adherence to explicit standards is as essential requirement for health economic modelling [@Erdemir2020], yet guidence for quality implementation of OSHEMs is currently scarce and piecemeal.
+Best practice guidelines on health economic model transparency were published ten years ago [@Eddy2012] and made recommendations on model documentation but notably did not include guidance on the sharing of model code and data.
+More recent and more general modelling guidance [@Erdemir2020] does recommend the sharing of model code and data through existing repositories such as GitHub and Zenodo as well as the use of version control systems such as Git across a project's development lifecycle.
 A coding framework for OSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions[@Alarid2019].

### 2022-05-19 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
intro done
minor tweaks to mental health section

@@
 # Motivation
+
+## Why develop OSHEMs in mental health
+
 Mental disorders impose high health, social and economic burdens worldwide [@RN8;@GBD2019].
-Much of this burden is potentially avertable [@RN25], but poorly financed and organised mental health systems are ill-equiped for this challenge[@RN22;@RN23].
+Much of this burden is potentially avertable [@RN25], but poorly financed and organised mental health systems are ill-equipped for this challenge[@RN22;@RN23].
 The large and widespread additional mental health burdens recently observed during the COVID pandemic[@20211700] and predicted as a potential future consequence of global heating [@page_howard_2010], highlight the need to improve the resilience and adaptability of these systems.
@@
 Realising significant improvements in population mental health may in part depend on gaining better understanding of the systems in which mental disorder emerges and is treated [@Fried2020].
-Currently, the theoretical basis for understanding these systems is weak [@RN2111].
-Strikingly, it remains unclear why increased investments in mental health care have yet to discernably reduce the prevalence and burden of mental disorders[@RN26].
+Computational modelling could play an important role in providing these insights, but this may require significant changes in the way mental health modelling projects are funded, conceptualised and implemented.
+
+Currently, mental health simulation studies rarely explore the features and behaviours of complex systems [@RN73], with mental health economic models predominantly addressing issues relating to the affordability and value for money of individual programs [@RN34].
+Major mental health reform programs will require the identification, prioritisation, sequencing, targeting and monitoring of multiple interdependent initiatives.
+Single purpose models that assume static systems, even when sufficiently robust to be formally incorporated into Government resource planning processes, are therefore likely to be inadequate for the decision support needs of policymakers and service planners [@PC2020].
+Multi-application or reference models [@Afzali2013] that use dynamic systems modelling approaches can provide insights about inter-dependencies between candidate policies and the evolution of the mental health systems planning context [@Occhipinti2021].
+However, as they are intended for multiple-purposes and because propagation errors may be more likely with more complex models [@Saltelli2019] such models require greater investments in model transparency and validation [@Eddy2012; @Feenstra2022].
+
+The development, validation and maintenance of these more complex models may be simply too onerous a burden to remain the responsibility of a single modelling team.
+Developing networks of modellers working on common health conditions [@Sampson2019] and collaborations across multiple modelling teams that include the ability to re-use and extend each others work, can make complex modelling projects more tractable [@Arnold2010].
+Similarly, more attention to developing partnerships between modellers and decision-makers across the life-cycle of a modelling project can help ensure models are appropriately conceptualised and implemented and improve their practical utility as decision aids [@Zabell2021].
+
+Infrastructure and funding is required to support the mental health systems modelling field address some long-term challenges.
+The theoretical basis for understanding complex mental health systems is currently weak [@RN2111].
+Strikingly, it remains unclear why increased investments in mental health care have yet to discernibly reduce the prevalence and burden of mental disorders[@RN26].
 The literature about how the requirements, characteristics and performance of mental health services are shaped by spatiotemporal context is underdeveloped [@RN42].
 There is insufficient evidence to identify the social determinants of mental disorders most amenable to preventative interventions, and for which population sub-groups such interventions would be most effective [@RN43].
+Modelling projects should be resourced to be routinely updated and refined as new evidence emerges and decision contexts change [@Jenkins2021].
 
-Mental health simulation studies rarely explore the features and behaviours of complex systems [@RN73], with mental health economic models predominantly addressing issues relating to the affordability and value for money of individual programs [@RN34].
-Single purpose models that assume static systems, even when sufficiently robust to be formally incorporated into Government resource planning processes, may be inadequate for the decision support needs of policymakers and service planners seeking to successfully identify, prioritise, sequence and target multiple elements of complex reform programs [@PC2020].
-
-Multi-application, dynamic systems modelling approaches can provide insights about inter-dependencies between candidate policy settings that static models of isolated scenarios cannot [@Occhipinti2021].
-However, greater use of these types of models may require adaptation on the part of funders, modellers and decision-makers.
-The complexity of multi-application systems models may make them particularly prone to errors [@Saltelli2019], thus requiring greater investments in model transparency and validation [@Eddy2012].
-These types of models can be highly resource intensive to develop and may also never be truly "finished", instead requiring ongoing updates to remain relevant to evolving decision contexts [@Jenkins2021] and to meet additional feature requests from end-users.
-The development, validation and maintenance of these types of models may be simply too onerous and long term a burden to remain the responsibility of a single modelling team and might benefit from collaborations across multiple modelling teams, and perhaps the general mental health modelling field.
-Similarly, more attention to developing partnerships between modellers and decision-makers across the life-cycle of a modelling project can help ensure multi-purpose models can address priority decision topics and have user-interfaces that meet the needs of non-technical users.
-
-# TIMELY principles and standards
-
-# ready4 Framework
-
-# Application
+Open source approaches and common standards, which have been previously recommended for the development of mental health modelling field [@RN73], have the potential to help address the need for a more transparent, collaborative and sustained approach to mental health system model development.
 
@@
 
-## Worked example
+# Implementation
+
+## Standards
+
+TIMELY
+
+### Transparent Models
+
+### Iterative Models
+
+### Modular Models
+
+### Epitomised Models
+
+### Yielding Models
+
+## Infrastructure
+
+### Technical platforms
+
+### Software Development Kit
+
+## Application
+
+Worked example

### 2022-05-20 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
started on rfwn

--- 2022-04-20 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
@@
 <!-- Add aims text here -->
-In this article, we aim to:
-
-i. Describe a suggested framework for implementing open source mental health systems models comprised of a foundation set of modelling principles and standards and a software development toolkit.
-
-ii. Provide a worked example of applying the framework to developing open source models for mapping psychological measures to health utility in young people.
+We have consolidated and refined these and other recommended standards for OSHEMs as part of a framework for developing an open source model of youth mental health.
+In this paper, we describe our motivation for developing the framework, the rationale for each standard specified in the framework, the software toolkits we have developed to help meet each standard and a worked example of a modelling project developed with the framework.

### 2022-05-20 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
started on rfwn

--- 2022-05-17 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
@@
 <!-- `r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`  -->
-Computational models have become an essential tool for healthcare policy development [@Erdemir2020].
+Computational models have become essential tools for health policy development [@Erdemir2020].
 Although influential and widely used, these models routinely contain errors [@Radeva2020], are rarely adequately validated [@Ghabri2019], can be difficult to reproduce [@Jalali2021; @McManus2019; @Bermejo2017] and are likely to be infrequently updated or revised [@Sampson2017].
-To help address these issues, there is increasing in principle support for open source health economics models (OSHEMs) that grant open access to and liberal permissions to re-use model source code [@Pouwels2022].
-However, in-practice implementation of OSHEMs remains rare [@Emerson2019; @Michalczyk2018; @Feenstra2022].
+To help address these issues, there is growing support for greater use of open source health economics models (OSHEMs) that grant liberal permissions to access and re-use model source code [@Pouwels2022].
+However, to date actual implementations of OSHEMs are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022].
 Barriers to adoption include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations [@Pouwels2022; @Wu2019].
-As many health economic models are owned by pharmaceutical companies and consultancies, commercial considerations may also limit adoption of OSHEMs [@Feenstra2022].
+As many health economic models are owned by pharmaceutical companies and consultancies, commercial considerations may also limit the uptake of OSHEMs [@Feenstra2022].
 
-There is also a need to develop good practice guidance for implementing OSHEMs [@Sampson2019], which is currently scarce and piecemeal.
-Current health economist best practice guidelines on model transparency was published ten years ago [@Eddy2012] and contained recommendations on technical and non-technical model documentation but not about how model code and data are to be shared.
-More recent and more general guidance recommends the sharing of model code and data using repositories such as GitHub and Zenodo as well as the use of version control systems such as Git across the development lifecycle of a modelling project [@Erdemir2020].
+There is also a need to develop good practice recommendations for OSHEMs [@Sampson2019].
+Adherence to explicit standards is as essential requirement for quality health economic model implementaion [@Erdemir2020], but current guidance for OSHEMs is scarce and piecemeal.
+Guidelines on health economic model transparency were published ten years ago [@Eddy2012] and made recommendations on model documentation but notably not on the sharing of model code and data.
+More recent and more general modelling guidance [@Erdemir2020] does recommend the sharing of model code and data through existing repositories such as GitHub [@github2007] and Zenodo [@Zenodo2013] as well as the use of version control systems such as Git [@git20XX].
 A coding framework for OSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions[@Alarid2019].

### 2022-05-20 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
started on rfwn

@@
 
-Realising significant improvements in population mental health may in part depend on gaining better understanding of the systems in which mental disorder emerges and is treated [@Fried2020].
-Computational modelling could play an important role in providing these insights, but this may require significant changes in the way mental health modelling projects are funded, conceptualised and implemented.
+Computational modelling could play an important role in developing policies to improve population mental health but this may require significant changes in the way mental health modelling projects are funded, conceptualised and implemented.
 
@@
 Major mental health reform programs will require the identification, prioritisation, sequencing, targeting and monitoring of multiple interdependent initiatives.
-Single purpose models that assume static systems, even when sufficiently robust to be formally incorporated into Government resource planning processes, are therefore likely to be inadequate for the decision support needs of policymakers and service planners [@PC2020].
+Single purpose models that assume static systems, even when sufficiently robust to be formally incorporated into Government resource planning processes, may be inadequate for the decision support needs of policymakers and service planners [@PC2020].
 Multi-application or reference models [@Afzali2013] that use dynamic systems modelling approaches can provide insights about inter-dependencies between candidate policies and the evolution of the mental health systems planning context [@Occhipinti2021].
@@
 
-Infrastructure and funding is required to support the mental health systems modelling field address some long-term challenges.
-The theoretical basis for understanding complex mental health systems is currently weak [@RN2111].
+The mental health systems modelling field also face a number of challenges that require sustained action over the long term.
+There are significant gaps in our understanding of the systems in which mental disorder emerges and is treated [@Fried2020] and the theoretical basis for understanding complex mental health systems is weak [@RN2111].
 Strikingly, it remains unclear why increased investments in mental health care have yet to discernibly reduce the prevalence and burden of mental disorders[@RN26].
@@
 
-Open source approaches and common standards, which have been previously recommended for the development of mental health modelling field [@RN73], have the potential to help address the need for a more transparent, collaborative and sustained approach to mental health system model development.
+Open source approaches and common standards have the potential to provide more transparent, collaborative and sustained approaches to mental health system model development.
+Open source frameworks have been previously recommended for the development of mental health modelling field [@RN73] but, as with health economics more generally, OSHEMs are rare.
+Currently there is only mental health related model (in Alcohol Use Disorder [@Basu2018]) that is indexed in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019], though a Major Depressive Disorder reference model for the United States [@IVIMDD2022] is currently being developed as part of the Open Value Initiative [@Jansen2019].
 
 ## readyforwhatsnext
+We are currently developing an open source model of the systems shaping the mental health of young people in Victoria, Australia.
+The model is called readyforwhatsnext and development progress is reported on a project website [@rfwn2022].
+The project aims to produce a reference model that can examine multiple potential population level strategies for prevention (in 0-25 year olds) and treatment (in 12-25 year olds) of mental disorders.
+
+Our approach to model development is to undertake a number of discrete modelling projects and progressively link them together by means of a common framework.
+Sub-projects we are currently engaged in include those to develop models of People (synthetic populations of interest describing relevant individual characteristics and their household relationships, choice models for predicting helpseeking behaviour and models to map health psychological measures to health utility), Places (models that synthesise geometry and spatial attribute data to characterise the geographic distribution of relevant demographic, environmental, epidemiological and service infrastructure features) and Platforms (a model to describe the operation of a complex primary youth mental healths service).
+We have previously undertaken scoping work reviewing economic evidence relating to youth mental helth Programs [@RN33] and also aim to integrate this with the model at a future date.
+
+This needs a framework so....
 
@@
 ### Yielding Models
+Shiny tutorial [@SmithR2020]
 

### 2022-05-23 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
minor additions

@@
 We have consolidated and refined these and other recommended standards for OSHEMs as part of a framework for developing an open source model of youth mental health.
-In this paper, we describe our motivation for developing the framework, the rationale for each standard specified in the framework, the software toolkits we have developed to help meet each standard and a worked example of a modelling project developed with the framework.
+In this paper, we describe our motivation for developing the framework, the rationale for each included standard, the software toolkits we have developed to help meet each standard and a worked example of a modelling project developed with the framework.

### 2022-05-23 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
minor additions

@@
 There is also a need to develop good practice recommendations for OSHEMs [@Sampson2019].
-Adherence to explicit standards is as essential requirement for quality health economic model implementaion [@Erdemir2020], but current guidance for OSHEMs is scarce and piecemeal.
-Guidelines on health economic model transparency were published ten years ago [@Eddy2012] and made recommendations on model documentation but notably not on the sharing of model code and data.
-More recent and more general modelling guidance [@Erdemir2020] does recommend the sharing of model code and data through existing repositories such as GitHub [@github2007] and Zenodo [@Zenodo2013] as well as the use of version control systems such as Git [@git20XX].
-A coding framework for OSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions[@Alarid2019].
+Adherence to explicit standards is as essential requirement for quality health economic model implementation [@Erdemir2020], but current guidance for OSHEMs is scarce and piecemeal.
+Guidelines on health economic model transparency were published ten years ago [@Eddy2012] and made recommendations on documenting models but notably not on the sharing of model code and data.
+More recent and more general modelling guidance [@Erdemir2020] recommends the sharing of code and data through platforms such as GitHub [@github2007] and Zenodo [@Zenodo2013] and the use of version control systems such as Git [@git20XX].
+A coding framework for OSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions [@Alarid2019].
 

### 2022-05-23 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
minor additions

@@
 
-Currently, mental health simulation studies rarely explore the features and behaviours of complex systems [@RN73], with mental health economic models predominantly addressing issues relating to the affordability and value for money of individual programs [@RN34].
 Major mental health reform programs will require the identification, prioritisation, sequencing, targeting and monitoring of multiple interdependent initiatives.
-Single purpose models that assume static systems, even when sufficiently robust to be formally incorporated into Government resource planning processes, may be inadequate for the decision support needs of policymakers and service planners [@PC2020].
-Multi-application or reference models [@Afzali2013] that use dynamic systems modelling approaches can provide insights about inter-dependencies between candidate policies and the evolution of the mental health systems planning context [@Occhipinti2021].
+Single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020].
+Currently, mental health economic models predominantly addressing issues relating to the affordability and value for money of individual programs [@RN34] with mental health simulation studies rarely modelling complex systems [@RN73].
+Dynamic systems modelling approaches can provide insights about inter-dependencies between candidate policies and the evolution of the mental health systems planning context [@Occhipinti2021].
+These types of models could be the basis for developing reference models [@Afzali2013] intended for multiple-applications and re-use by multiple modelling teams.
 However, as they are intended for multiple-purposes and because propagation errors may be more likely with more complex models [@Saltelli2019] such models require greater investments in model transparency and validation [@Eddy2012; @Feenstra2022].
 
-The development, validation and maintenance of these more complex models may be simply too onerous a burden to remain the responsibility of a single modelling team.
+The development, validation and maintenance of these more complex models may be simply too onerous a burden for a single modelling team.
 Developing networks of modellers working on common health conditions [@Sampson2019] and collaborations across multiple modelling teams that include the ability to re-use and extend each others work, can make complex modelling projects more tractable [@Arnold2010].
@@
 
-The mental health systems modelling field also face a number of challenges that require sustained action over the long term.
+Modelling projects should be resourced to be routinely updated and refined as new evidence emerges and decision contexts change [@Jenkins2021].
+Sustained long term funding is required for mental health projects to remain current and to enable the mental health modelling field address a number of key challenges.
 There are significant gaps in our understanding of the systems in which mental disorder emerges and is treated [@Fried2020] and the theoretical basis for understanding complex mental health systems is weak [@RN2111].
@@
 There is insufficient evidence to identify the social determinants of mental disorders most amenable to preventative interventions, and for which population sub-groups such interventions would be most effective [@RN43].
-Modelling projects should be resourced to be routinely updated and refined as new evidence emerges and decision contexts change [@Jenkins2021].
 
-Open source approaches and common standards have the potential to provide more transparent, collaborative and sustained approaches to mental health system model development.
-Open source frameworks have been previously recommended for the development of mental health modelling field [@RN73] but, as with health economics more generally, OSHEMs are rare.
-Currently there is only mental health related model (in Alcohol Use Disorder [@Basu2018]) that is indexed in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019], though a Major Depressive Disorder reference model for the United States [@IVIMDD2022] is currently being developed as part of the Open Value Initiative [@Jansen2019].
+Open source frameworks have been previously recommended for the development of mental health modelling field [@RN73] but, as with health economics more generally, OSHEMs remain rare.
+Currently there is only one mental health related model (in Alcohol Use Disorder [@Basu2018]) that is indexed in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019].
+A Major Depressive Disorder reference model for the United States [@IVIMDD2022] is also being developed as part of the Open Value Initiative [@Jansen2019].
+We believe greater support for open source approaches have the potential to provide more transparent, collaborative and sustained approaches to mental health system model development.
 
@@
 Our approach to model development is to undertake a number of discrete modelling projects and progressively link them together by means of a common framework.
-Sub-projects we are currently engaged in include those to develop models of People (synthetic populations of interest describing relevant individual characteristics and their household relationships, choice models for predicting helpseeking behaviour and models to map health psychological measures to health utility), Places (models that synthesise geometry and spatial attribute data to characterise the geographic distribution of relevant demographic, environmental, epidemiological and service infrastructure features) and Platforms (a model to describe the operation of a complex primary youth mental healths service).
-We have previously undertaken scoping work reviewing economic evidence relating to youth mental helth Programs [@RN33] and also aim to integrate this with the model at a future date.
+Sub-projects we are currently engaged in include those to develop models of people (synthetic populations of interest describing relevant individual characteristics and their household relationships, choice models for predicting helpseeking behaviour and models to map health psychological measures to health utility), places (synthesising geometry and spatial attribute data to characterise the geographic distribution of relevant demographic, environmental, epidemiological and service infrastructure features) and platforms (representing the processes and operations of a complex primary youth mental health service).
+We have also previously undertaken scoping work reviewing economic evidence relating to youth mental health programs [@RN33] and plan to integrate this with the model at a future date.
 
-This needs a framework so....
-
-# Implementation
+# Framework
+The framework we have developed consists of a set of standards and supporting toolkit for implementing open source youth mental health models.
 
 ## Standards
+We have identified 15 standards that we believe are important for quality implementations of OSHEMs, each described under one of following six principles that models are TIMELY:
 
-TIMELY
+ - Transparent: people can easily see how a model has been implemented and tested;
+ - Iterative: a model is routinely updated to fix errors, incorporate new data and improve performance;
+ - Modular: multiple models and their components can be combined to explore topics of more extensive scope;
+ - Epitomized: model code is sufficiently generalised to be applied or adapted to other contexts and decision problems;
+ - Licensed: a model's constituent parts and derivative works are persistently re-usable by other modellers; and
+ - Yielding: a model can be deployed as an easy to use and flexible decision aid.
 
@@
 
+(a concatenation of the transparency and validity concepts defined in previous guidance [@Eddy2012])
+
+T1: Permanent, uniquely identified archived copies of model code and data are publicly available in open access online repositories
+
+<!-- T2 MISSING - Merged With T1 -->
+
+T2: Models and their code and data are clearly and consistently documented
+
+T3: Model logic is easy to follow through use of a simple and consistent syntax [abstraction and polymorphism, house style]
+
+T4: Model analyses and reporting are implemented using a literate programming approach
+
+<!-- T6 MISSING - Deleted -->
+
+T5: All parts of a study workflow from raw data ingest through to data processing, analysis, reporting and dissemination of study outputs can be reproduced and/or replicated by third parties using publicly available materials.
+
 ### Iterative Models
+Performance - validity and usefulness
+
+I2: Model code is version controlled
+
+I1: Model code and data use semantic versioning
+
+I3: Model code development uses continuous integration (CI) tools and test units to ensure each new version is quality assured
+
+I4: Deprecation conventions are used to retire old code / data in order to minimise the risk of unintended impacts on downstream dependencies
 
@@
 
+M1: Model code and data are decoupled – each is stored, managed, licensed, disseminated and cited independently
+
+<!-- T2 MISSING - Moved to E -->
+
+M3: Model code defines encapsulating data structures [that can be safely combined].
+
 ### Epitomised Models
+M2: Model code is distributed as code-libraries [compare to analysis and reporting]
+
+E2: Model code defines inheriting data-structures.
+
+E1: Model code deploys a combination of object oriented and functional programming.
+
+### Licensed Models
+copyleft licensing [@copyleft2022] is used to ensure that 
+L1: Model code and data are available for viewing and re-use in open access online repositories under copyleft licensing arrangements.
 
@@
 Shiny tutorial [@SmithR2020]
+Y1: Non- technical users can configure and run models via simple user-interfaces
 
-## Infrastructure
+## Toolkits
 

### 2022-05-24 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
added transparent models section

@@
 Our approach to model development is to undertake a number of discrete modelling projects and progressively link them together by means of a common framework.
-Sub-projects we are currently engaged in include those to develop models of people (synthetic populations of interest describing relevant individual characteristics and their household relationships, choice models for predicting helpseeking behaviour and models to map health psychological measures to health utility), places (synthesising geometry and spatial attribute data to characterise the geographic distribution of relevant demographic, environmental, epidemiological and service infrastructure features) and platforms (representing the processes and operations of a complex primary youth mental health service).
+Sub-projects we are currently engaged in include those to develop models of people (synthetic populations of interest describing relevant individual characteristics and their household relationships, choice models for predicting helpseeking behaviour and models to map psychological measures to health utility), places (synthesising geometry and spatial attribute data to characterise the geographic distribution of relevant demographic, environmental, epidemiological and service infrastructure features) and platforms (representing the processes and operations of a complex primary youth mental health service).
 We have also previously undertaken scoping work reviewing economic evidence relating to youth mental health programs [@RN33] and plan to integrate this with the model at a future date.
@@
 # Framework
-The framework we have developed consists of a set of standards and supporting toolkit for implementing open source youth mental health models.
+The framework we have developed consists of a set of standards and supporting toolkit for implementing an open source youth mental health model.
 
@@
  - Iterative: a model is routinely updated to fix errors, incorporate new data and improve performance;
- - Modular: multiple models and their components can be combined to explore topics of more extensive scope;
+ - Modular: multiple models and their components can be readily combined to explore topics of more extensive scope;
  - Epitomized: model code is sufficiently generalised to be applied or adapted to other contexts and decision problems;
  - Licensed: a model's constituent parts and derivative works are persistently re-usable by other modellers; and
- - Yielding: a model can be deployed as an easy to use and flexible decision aid.
+ - Yielding: a model can be deployed as a flexible and easy to use decision aid.
 
 ### Transparent Models
+Transparency can be facilitated by making model code and data accessible, citable, clear and complete.
+The most efficient way to make model code and data widely accessible may be to use existing open science infrastructure [@Erdemir2020].
+Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage of code and data and generate a Digital Object Identifier (DOI) for each unique item.
+These repositories are a preferable solution for sharing citable code and data than transitory repositories such as corporate websites or GitHub which can be deleted or relocated at any time [@sseditors2022].
+Zenodo includes tools that automate integration with GitHub, which makes ieasy for developers to maintain parallel code repositories - one for disseminating the most up to date in development code and the other for archived code releases.
 
-(a concatenation of the transparency and validity concepts defined in previous guidance [@Eddy2012])
+Model code and data also need to be clearly documented, potentially with different versions for technical and non-technical users [@Eddy2012].
+Developers storing data in a Dataverse installation have access to multiple meta-data fields to document both the dataset as a whole and individual files contained by that dataset.
+In R, code libraries can be documented with the aid of tools such as devtools [@devtools2021], sinew [@sinew2022] and roxygen2 [@roxygen22021] that create manuals that conform to a standardised template, and pkgdown [@pkgdown2022] for creating package websites.
 
-T1: Permanent, uniquely identified archived copies of model code and data are publicly available in open access online repositories
+Code can be made easier to follow through a number of development choices.
+For technical users, use of a consistent and explicit house-style can make it easier to review large bodies of code.
+The high level logic of a program can be made more comprehensible for non-technical users though the use of abstraction, that routinely exposes only simple, top level commands.
+Polymorphsim, where the same high level command (e.g.
+"simulate") can implement multiple different lower level algorithms of the same broad category of task, can further simplify code.
+Literate programming, where computer code is integrated with plain English descriptions of each main step in an analysis workflow, can make code easier for review by both technical and non-technical users.
+
+Finally, transcription errors - mistakes introduced when transferring data between data sources, models and reports - are very common in health economic models [@Radeva2020].
+The risk of these errors might be lower if there was full transparency across all steps in a study workflow.
+Scientific computing tools make it feasible to author programs that reproducibly execute all steps from raw data ingest through data processing, analysis, rendering of a scientific manuscript and dissemination of study outputs in online repositories.
+
+Standards:
+
+- T1: Permanent, uniquely identified archived copies of model code and data are publicly available in open access online repositories
 
@@
 
-T2: Models and their code and data are clearly and consistently documented
+- T2: Models and their code and data are clearly and consistently documented <!-- Was T3 -->
 
-T3: Model logic is easy to follow through use of a simple and consistent syntax [abstraction and polymorphism, house style]
+- T3: Model logic is easy to follow through use of a simple and consistent syntax [abstraction and polymorphism, house style] <!-- Was T4 -->
 
-T4: Model analyses and reporting are implemented using a literate programming approach
+- T4: Model analyses and reporting are implemented using a literate programming approach <!-- Was T5 -->
 
@@
 
-T5: All parts of a study workflow from raw data ingest through to data processing, analysis, reporting and dissemination of study outputs can be reproduced and/or replicated by third parties using publicly available materials.
+- T5: All parts of a study workflow from raw data ingest through to dissemination of study outputs can be reproduced and/or replicated by third parties using publicly available materials.
+<!-- Was T7 -->
 

### 2022-05-24 setup.R

@@ -13,7 +13,7 @@ X <- Ready4showSynopsis(#background_1L_chr = "Our study is entirely fictional.",
                         keywords_chr = c("open source models","health economics","mental disorders"),
                         outp_formats_chr = "PDF",
                         #sample_desc_1L_chr = "The study sample is fake data that pretends to be young people aged 12 to 25 years who attended Australian primary care services for mental health related needs between November 2019 to August 2020.",
-                        title_1L_chr = "A framework for open source computational models of mental health systems")
+                        title_1L_chr = "A framework for an open source economic model of the systems shaping the mental health of young people")
 X <- renewSlot(X,
                "authors_r3", 
                {

### 2022-05-24 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
added Iterative section

@@
 # Framework
-The framework we have developed consists of a set of standards and supporting toolkit for implementing an open source youth mental health model.
+The framework we have developed consists of a set of standards and tools for implementing those standards.
 
 ## Standards
-We have identified 15 standards that we believe are important for quality implementations of OSHEMs, each described under one of following six principles that models are TIMELY:
+We have identified 15 standards that we believe are important for quality implementations of OSHEMs, each described under one of following six principles for making models TIMELY:
 
@@
 ### Iterative Models
-Performance - validity and usefulness
+To avoid OSHEMs going stale - losing validity and usefulness with time, they should be routinely updated.
+A number of tools and approaches can make the process of implementing and curating changes to model code and data more coherent and efficient.
+Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent access to all published versions of a dataset, each uniquely identifiable.
+For code, use of version control tools like Git [@git20XX] can ensure that the entire development history of a project is organised so that each version is distinguishable and retrievable by developers.
+The online platform GitHub [@github2007] can make this version history accessible to anyone.
 
-I2: Model code is version controlled
+GitHub also provides continuous integration [@CI2017] tools that can help make code updates more reliable.
+OSHEM developed in R can take advantage of templates provided by devtools [@devtools2021] and pkgdown [@pkgdown2022] to run GitHub continuous integration checks that each new version of a code library passes multiple quality tests.
+These tests can include those of units (do individual functions produce expected output?), documentation (does documentation render correctly?, can all example workflows be executed?) and installation (can the software be successfully deployed on multiple types of operating system?).
 
-I1: Model code and data use semantic versioning
+Adopting semantic versioning [@semver20xx] conventions can be an efficient way to provide users of model code and data with information about the potential importance of an update.
+For R code, the usethis [@usethis2021] package can be used to partially automate version number increments using the convention Major.Minor.Patch.Development.
+Datasets stored on the Harvard Dataverse use the simpler Major.Minor convention.
+Finally, using deprecation conventions that take an informative and staged approach to retiring old code and data can reduce the risk that model revisions have unintended consequences on third party users.
+The package lifeycle [@lifecycle2021] provides tools for R developers to consistently deprecate their code.
 
-I3: Model code development uses continuous integration (CI) tools and test units to ensure each new version is quality assured
+Standards:
+
+I2: Model code is version controlled <!-- Was I2 -->
+
+I3: Model code development uses continuous integration (CI) tools and test units to ensure each new version is quality assured <!-- Was I3 -->
+
+I1: Model code and data use semantic versioning <!-- Was I1 -->
 

### 2022-05-25 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
tweaks

@@
 Single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020].
-Currently, mental health economic models predominantly addressing issues relating to the affordability and value for money of individual programs [@RN34] with mental health simulation studies rarely modelling complex systems [@RN73].
-Dynamic systems modelling approaches can provide insights about inter-dependencies between candidate policies and the evolution of the mental health systems planning context [@Occhipinti2021].
-These types of models could be the basis for developing reference models [@Afzali2013] intended for multiple-applications and re-use by multiple modelling teams.
+Currently, mental health economic models predominantly address issues relating to the affordability and value for money of individual programs [@RN34] with mental health simulation studies rarely modelling complex systems [@RN73].
+Greater use of dynamic systems modelling approaches could provide new insights about inter-dependencies between candidate policies and the evolution of the mental health systems planning context [@Occhipinti2021].
+These types of models might also be the basis for developing reference models [@Afzali2013] of mental health systems that are intended for multiple-applications and re-use by different modelling teams.
 However, as they are intended for multiple-purposes and because propagation errors may be more likely with more complex models [@Saltelli2019] such models require greater investments in model transparency and validation [@Eddy2012; @Feenstra2022].
@@
 Modelling projects should be resourced to be routinely updated and refined as new evidence emerges and decision contexts change [@Jenkins2021].
-Sustained long term funding is required for mental health projects to remain current and to enable the mental health modelling field address a number of key challenges.
-There are significant gaps in our understanding of the systems in which mental disorder emerges and is treated [@Fried2020] and the theoretical basis for understanding complex mental health systems is weak [@RN2111].
+There are significant deficits in our understanding of the systems in which mental disorder emerges and is treated [@Fried2020] and longer term project horizons could allow mental health models to progressively improve validity as these gaps are addressed.
+Currently, the theoretical basis for understanding complex mental health systems is weak [@RN2111].
 Strikingly, it remains unclear why increased investments in mental health care have yet to discernibly reduce the prevalence and burden of mental disorders[@RN26].
@@
 # Framework
-The framework we have developed consists of a set of standards and tools for implementing those standards.
+The framework we have developed consists of a set of standards for OSHEMs and tools for implementing those standards.
 
 ## Standards
-We have identified 15 standards that we believe are important for quality implementations of OSHEMs, each described under one of following six principles for making models TIMELY:
+We have identified 18 standards that we believe are important for quality implementations of OSHEMs, each described under one of following six principles for making models TIMELY:
 
- - Transparent: people can easily see how a model has been implemented and tested;
- - Iterative: a model is routinely updated to fix errors, incorporate new data and improve performance;
- - Modular: multiple models and their components can be readily combined to explore topics of more extensive scope;
- - Epitomized: model code is sufficiently generalised to be applied or adapted to other contexts and decision problems;
- - Licensed: a model's constituent parts and derivative works are persistently re-usable by other modellers; and
- - Yielding: a model can be deployed as a flexible and easy to use decision aid.
+ - **Transparent**: people can easily see how a model has been implemented and tested;
+ - **Iterative**: a model is routinely updated to fix errors, incorporate new data and improve performance;
+ - **Modular**: multiple models and their components can be readily combined to explore topics of more extensive scope;
+ - **Epitomized**: model code is sufficiently generalised to be applied or adapted to other contexts and decision problems;
+ - **Licensed**: a model's constituent parts and derivative works are persistently re-usable by other modellers; and
+ - **Yielding**: a model can be deployed as a flexible and easy to use decision aid.
 
 ### Transparent Models
-Transparency can be facilitated by making model code and data accessible, citable, clear and complete.
-The most efficient way to make model code and data widely accessible may be to use existing open science infrastructure [@Erdemir2020].
-Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage of code and data and generate a Digital Object Identifier (DOI) for each unique item.
-These repositories are a preferable solution for sharing citable code and data than transitory repositories such as corporate websites or GitHub which can be deleted or relocated at any time [@sseditors2022].
-Zenodo includes tools that automate integration with GitHub, which makes ieasy for developers to maintain parallel code repositories - one for disseminating the most up to date in development code and the other for archived code releases.
+A range of tools and practices are available to help make model code and data accessible, citable and comprehensible.
+The most efficient way to widely disseminate code and data may be to use existing open science infrastructure [@Erdemir2020].
+Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each unique item.
+These repositories are a preferable solution for sharing citable code and data than transitory repositories such as corporate websites or GitHub where items can be deleted or relocated at any time [@sseditors2022].
+Zenodo includes tools that automate integration with GitHub, which makes it easy for developers to maintain parallel code repositories - one for disseminating the most up to date development code and the other for archiving citable code releases.
 
@@
 Developers storing data in a Dataverse installation have access to multiple meta-data fields to document both the dataset as a whole and individual files contained by that dataset.
-In R, code libraries can be documented with the aid of tools such as devtools [@devtools2021], sinew [@sinew2022] and roxygen2 [@roxygen22021] that create manuals that conform to a standardised template, and pkgdown [@pkgdown2022] for creating package websites.
+In R, code libraries can be documented with the aid of tools such as devtools [@devtools2021], sinew [@sinew2022] and roxygen2 [@roxygen2021] that create manuals that conform to a standardised template, and pkgdown [@pkgdown2022] for creating package websites.
 
-Code can be made easier to follow through a number of development choices.
-For technical users, use of a consistent and explicit house-style can make it easier to review large bodies of code.
-The high level logic of a program can be made more comprehensible for non-technical users though the use of abstraction, that routinely exposes only simple, top level commands.
-Polymorphsim, where the same high level command (e.g.
-"simulate") can implement multiple different lower level algorithms of the same broad category of task, can further simplify code.
-Literate programming, where computer code is integrated with plain English descriptions of each main step in an analysis workflow, can make code easier for review by both technical and non-technical users.
+Guidance about how to consistently use of meaningful naming conventions when authoring code is available [@Wilson_2017; @Alarid2019].
+The main logic of a program can also be made comprehensible to even non-technical users though the use of the common practices of abstraction [@8717448], where only simple, high level commands are routinely exposed to reviewers, and polymorphsim [@7181447], where the same command (e.g.
+"simulate") can be reused to implement different algorithms of the same broad type.
+Literate programming, where tools like RMarkdown [@xie2018r] are used to render documents that integrate computer code with plain English descriptions of each step in an analysis workflow, can make code easier to follow by both technical and non-technical users.
 
-Finally, transcription errors - mistakes introduced when transferring data between data sources, models and reports - are very common in health economic models [@Radeva2020].
+Finally, transcription errors - mistakes introduced when transferring data between sources, models and reports - are very common in health economic models [@Radeva2020].
 The risk of these errors might be lower if there was full transparency across all steps in a study workflow.
-Scientific computing tools make it feasible to author programs that reproducibly execute all steps from raw data ingest through data processing, analysis, rendering of a scientific manuscript and dissemination of study outputs in online repositories.
+Scientific computing tools now make it relatively straightforward to author programs that reproducibly execute all steps in data ingest, processing and reporting [@@Wilson_2017].
 
@@
 
-- T1: Permanent, uniquely identified archived copies of model code and data are publicly available in open access online repositories
+- **T1: Permanent, uniquely identified archived copies of model code and data are publicly available in open access online repositories**
 
@@
 
-- T2: Models and their code and data are clearly and consistently documented <!-- Was T3 -->
+- **T2: Models code and data are consistently documented **<!-- Was T3 -->
 
-- T3: Model logic is easy to follow through use of a simple and consistent syntax [abstraction and polymorphism, house style] <!-- Was T4 -->
+- **T3: Model code is easy to follow through use of a simple and consistent syntax**<!-- Was T4 -->
 
-- T4: Model analyses and reporting are implemented using a literate programming approach <!-- Was T5 -->
+- **T4: Model analyses and reporting are implemented using a literate programming approach** <!-- Was T5 -->
 
@@
 
-- T5: All parts of a study workflow from raw data ingest through to dissemination of study outputs can be reproduced and/or replicated by third parties using publicly available materials.
-<!-- Was T7 -->
+- **T5: All parts of a study analysis and reporting workflow can be reproduced and/or replicated by third parties using publicly available materials** <!-- Was T7 -->
 
 ### Iterative Models
-To avoid OSHEMs going stale - losing validity and usefulness with time, they should be routinely updated.
+To avoid OSHEMs going stale - losing validity and usefulness with time - they should be routinely updated.
 A number of tools and approaches can make the process of implementing and curating changes to model code and data more coherent and efficient.
@@
 GitHub also provides continuous integration [@CI2017] tools that can help make code updates more reliable.
-OSHEM developed in R can take advantage of templates provided by devtools [@devtools2021] and pkgdown [@pkgdown2022] to run GitHub continuous integration checks that each new version of a code library passes multiple quality tests.
+OSHEM developed in R can take advantage of templates provided by devtools [@devtools2021] and pkgdown [@pkgdown2022] to run GitHub continuous integration checks to verify that each new version of a code library passes multiple quality tests.
 These tests can include those of units (do individual functions produce expected output?), documentation (does documentation render correctly?, can all example workflows be executed?) and installation (can the software be successfully deployed on multiple types of operating system?).
@@
 Datasets stored on the Harvard Dataverse use the simpler Major.Minor convention.
+
 Finally, using deprecation conventions that take an informative and staged approach to retiring old code and data can reduce the risk that model revisions have unintended consequences on third party users.
@@
 
-I2: Model code is version controlled <!-- Was I2 -->
+- **I2: Model code is version controlled** <!-- Was I2 -->
 
-I3: Model code development uses continuous integration (CI) tools and test units to ensure each new version is quality assured <!-- Was I3 -->
+- **I3: Model code development uses continuous integration (CI) tools and test units to ensure each new version is quality assured**<!-- Was I3 -->
 
-I1: Model code and data use semantic versioning <!-- Was I1 -->
+- **I1: Model code and data use semantic versioning** <!-- Was I1 -->
 
-I4: Deprecation conventions are used to retire old code / data in order to minimise the risk of unintended impacts on downstream dependencies
+- **I4: Deprecation conventions are used to retire old code / data in order to minimise the risk of unintended impacts on downstream dependencies**
 
@@
 
-M1: Model code and data are decoupled – each is stored, managed, licensed, disseminated and cited independently
+- **M1: Model code and data are decoupled – each is stored, managed and disseminated independently** <!-- Modified (lost ref to licensed and cited) -->
 
-<!-- T2 MISSING - Moved to E -->
+- **M2: Model code and data are distributed with explicit citation guidance**<!--Replacement - Old version now merged with E1 -->
 
-M3: Model code defines encapsulating data structures [that can be safely combined].
+- **M3: Model code defines encapsulating data structures**
 
 ### Epitomised Models
-M2: Model code is distributed as code-libraries [compare to analysis and reporting]
 
-E2: Model code defines inheriting data-structures.
+- **E1: Model code is distributed as libraries of functions** [compare to analysis and reporting] <!-- Modified (lost ref to OOP and merged with M2) -->
 
-E1: Model code deploys a combination of object oriented and functional programming.
+- **E2: Model code defines inheriting data-structures**
+
+- **E3: Demonstration data is available to demonstrate generalised applications of model code**
 
@@
 copyleft licensing [@copyleft2022] is used to ensure that
-L1: Model code and data are available for viewing and re-use in open access online repositories under copyleft licensing arrangements.
+
+- **L1: Model code is made available for re-use under either copyleft or more permissive licensing arrangements**
+
+- **L2: Terms of use permit liberal re-use of non-confidential model data, subject to adherence to clearly specified ethical standards**
 
@@
 Shiny tutorial [@SmithR2020]
-Y1: Non- technical users can configure and run models via simple user-interfaces
+
+- **Y1: Non- technical users can configure and run models via simple user-interfaces**
 

### 2022-05-26 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
started epitomised

@@
 ## Standards
-We have identified 18 standards that we believe are important for quality implementations of OSHEMs, each described under one of following six principles for making models TIMELY:
+We have identified 20 standards that we believe are important for quality implementations of OSHEMs, each described under one of following six principles for making models TIMELY:
 
  - **Transparent**: people can easily see how a model has been implemented and tested;
- - **Iterative**: a model is routinely updated to fix errors, incorporate new data and improve performance;
- - **Modular**: multiple models and their components can be readily combined to explore topics of more extensive scope;
- - **Epitomized**: model code is sufficiently generalised to be applied or adapted to other contexts and decision problems;
- - **Licensed**: a model's constituent parts and derivative works are persistently re-usable by other modellers; and
- - **Yielding**: a model can be deployed as a flexible and easy to use decision aid.
+ - **Iterative**: a model is routinely updated to maintain and improve validity;
+ - **Modular**: models and their components can be combined to extend their scope;
+ - **Epitomized**: models can be used in multiple decision contexts;
+ - **Licensed**: a model and its derivatives are persistently re-usable by other modellers; and
+ - **Yielding**: a model can be deployed as a simple, flexible and reliable decision aid.
 
@@
 Model code and data also need to be clearly documented, potentially with different versions for technical and non-technical users [@Eddy2012].
-Developers storing data in a Dataverse installation have access to multiple meta-data fields to document both the dataset as a whole and individual files contained by that dataset.
-In R, code libraries can be documented with the aid of tools such as devtools [@devtools2021], sinew [@sinew2022] and roxygen2 [@roxygen2021] that create manuals that conform to a standardised template, and pkgdown [@pkgdown2022] for creating package websites.
+Developers storing data in a Dataverse installation have access to multiple meta-data fields to document both a data collection and its constituent individual files.
+In R, code manuals and websites can be created with the aid of tools such as devtools [@devtools2021], sinew [@sinew2022], roxygen2 [@roxygen2021] and pkgdown [@pkgdown2022].
 
-Guidance about how to consistently use of meaningful naming conventions when authoring code is available [@Wilson_2017; @Alarid2019].
-The main logic of a program can also be made comprehensible to even non-technical users though the use of the common practices of abstraction [@8717448], where only simple, high level commands are routinely exposed to reviewers, and polymorphsim [@7181447], where the same command (e.g.
+Consistent use of meaningful naming conventions when authoring code is recommended [@Wilson_2017; @Alarid2019].
+The main logic of a program can be made comprehensible to even non-technical users though the use of the common practices of abstraction [@8717448], where only simple, high level commands are routinely exposed to reviewers, and polymorphsim [@7181447], where the same command (e.g.
 "simulate") can be reused to implement different algorithms of the same broad type.
@@
 
+An essential component of quality assuring health economic models is verification - ensuring that calculations are correct and consistent with model specifications [@techver2019].
+One useful concept for informing model users about the extensiveness of verification checks is code coverage [@ERICWONG2010188] - the proportion of model code that has been explicitly tested.
+In R, the testthat [@testthat2011] and covr [@covr2020] tools can be used in conjunction with GitHub to define tests and report coverage metrics.
+
 Finally, transcription errors - mistakes introduced when transferring data between sources, models and reports - are very common in health economic models [@Radeva2020].
 The risk of these errors might be lower if there was full transparency across all steps in a study workflow.
-Scientific computing tools now make it relatively straightforward to author programs that reproducibly execute all steps in data ingest, processing and reporting [@@Wilson_2017].
+Scientific computing tools now make it relatively straightforward to author programs that reproducibly execute all steps in data ingest, processing and reporting [@Wilson_2017].
 
@@
 
-- **T1: Permanent, uniquely identified archived copies of model code and data are publicly available in open access online repositories**
+- **T1: Uniquely identified copies of model code and data are permanently archived in open online repositories**
 
@@
 
-- **T2: Models code and data are consistently documented **<!-- Was T3 -->
+- **T2: Model code and data are documented **<!-- Was T3 -->
 
-- **T3: Model code is easy to follow through use of a simple and consistent syntax**<!-- Was T4 -->
+- **T3: Model code uses a simple and consistent syntax**<!-- Was T4 -->
 
-- **T4: Model analyses and reporting are implemented using a literate programming approach** <!-- Was T5 -->
+- **T4: Model analyses and reporting are implemented using literate programming** <!-- Was T5 -->
 
-<!-- T6 MISSING - Deleted -->
+- **T5: Code coverage is reported** <!-- New, replaces version now moved to T4 -->
 
-- **T5: All parts of a study analysis and reporting workflow can be reproduced and/or replicated by third parties using publicly available materials** <!-- Was T7 -->
+- **T6: All parts of a study analysis and reporting workflow can be reproduced and/or replicated** <!-- Was T7, Replaces Deleted T6 -->
 
@@
 
-GitHub also provides continuous integration [@CI2017] tools that can help make code updates more reliable.
-OSHEM developed in R can take advantage of templates provided by devtools [@devtools2021] and pkgdown [@pkgdown2022] to run GitHub continuous integration checks to verify that each new version of a code library passes multiple quality tests.
-These tests can include those of units (do individual functions produce expected output?), documentation (does documentation render correctly?, can all example workflows be executed?) and installation (can the software be successfully deployed on multiple types of operating system?).
-
 Adopting semantic versioning [@semver20xx] conventions can be an efficient way to provide users of model code and data with information about the potential importance of an update.
@@
 
-Finally, using deprecation conventions that take an informative and staged approach to retiring old code and data can reduce the risk that model revisions have unintended consequences on third party users.
+Continuous integration [@CI2017] tools can help verify that each code update passes multiple quality tests.
+OSHEMs developed in R can take advantage of templates provided by devtools [@devtools2021] and pkgdown [@pkgdown2022] to run continuous integration checks on GitHub.
+These tests can include those of units (do individual functions produce expected output?), documentation (does documentation render correctly?, can all example workflows be executed?) and installation (can the software be successfully deployed on multiple types of operating system?).
+
+Finally, using deprecation conventions that take an informative and staged approach to retiring old code and data reduces the risk that model revisions have unintended consequences on third party users.
 The package lifeycle [@lifecycle2021] provides tools for R developers to consistently deprecate their code.
@@
 
-- **I2: Model code is version controlled** <!-- Was I2 -->
+- **I1: Model code is version controlled** <!-- Was I2 -->
 
-- **I3: Model code development uses continuous integration (CI) tools and test units to ensure each new version is quality assured**<!-- Was I3 -->
+- **I2: Model code and data use semantic versioning** <!-- Was I1 -->
 
-- **I1: Model code and data use semantic versioning** <!-- Was I1 -->
+- **I3: Continuous integration is used to verify model code updates**
 
-- **I4: Deprecation conventions are used to retire old code / data in order to minimise the risk of unintended impacts on downstream dependencies**
+- **I4: Deprecation conventions are used to retire model code and data**
 
 ### Modular Models
+Modular health economic models link multiple self-contained components that can be independently reused and extended by other projects [@Trauer2017;@Urach2013].
 
-- **M1: Model code and data are decoupled – each is stored, managed and disseminated independently** <!-- Modified (lost ref to licensed and cited) -->
+Many types of mental health data are highly sensitive with strict confidentiality requirements.
+For this reason, not all data included in some mental health models can be made widely available for others to re-use.
+A modular approach that ensures that model code and data are decoupled (stored in different files) can help model developers to restrict access to confidential model data, while providing open access to all other model components.
 
-- **M2: Model code and data are distributed with explicit citation guidance**<!--Replacement - Old version now merged with E1 -->
+An important consideration when combining model components (or modules) is to ensure that interactions between two modules do not compromise the validity of either.
+Using the coding practice of encapsulation [@8717448] can help ensure that model modules can be safely combined [ready4oop2022].
 
-- **M3: Model code defines encapsulating data structures**
+Standards:
+
+- **M1: Model code and data are stored and managed separately** <!-- Modified (lost ref to licensed and cited) -->
+
+- **M2: Model code defines encapsulating data structures** <!--Replacement - Old version now merged with E1 -->
 
 ### Epitomised Models
+A key challenge to generalising health economic models is that they are typically developed to inform a decision problem with a highly specific jurisdictional context. However, 
+Modular code is also recommended as good practice for scientific computing more generally [@Wilson_2017].
 
-- **E1: Model code is distributed as libraries of functions** [compare to analysis and reporting] <!-- Modified (lost ref to OOP and merged with M2) -->
+[model functions - compare to analysis and reporting]
+
+Standards:
+
+- **E1: Model code is distributed as libraries of functions**  <!-- Modified (lost ref to OOP and merged with M2) -->
 
@@
 
-- **E3: Demonstration data is available to demonstrate generalised applications of model code**
+- **E3: Test data is available to demonstrate generalised model applications**
 
@@
 
-- **L1: Model code is made available for re-use under either copyleft or more permissive licensing arrangements**
+Standards:
 
-- **L2: Terms of use permit liberal re-use of non-confidential model data, subject to adherence to clearly specified ethical standards**
+- **L1: Model code is made available for re-use under copyleft licenses**
+
+- **L2: Non-confidential model data is available for liberal re-use, subject to adherence clearly specified ethical standards**
+
+- **L3: Model code and data are distributed with citation tools** <!-- New -->
 
@@
 - **Y1: Non- technical users can configure and run models via simple user-interfaces**
+
+- **Y2: Statistical models can be safely, consistently and flexibly deployed using standardised tools**
 
@@
 
-## Application
+# Application
 

### 2022-05-27 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
not working

@@
 ## readyforwhatsnext
-We are currently developing an open source model of the systems shaping the mental health of young people in Victoria, Australia.
-The model is called readyforwhatsnext and development progress is reported on a project website [@rfwn2022].
-The project aims to produce a reference model that can examine multiple potential population level strategies for prevention (in 0-25 year olds) and treatment (in 12-25 year olds) of mental disorders.
+We are currently developing readyforwhatsnext, a reference OSHEM that aims to examine multiple potential population level strategies for promoting mental wellbeing and preventing and treating mental disorders in young people.
 
-Our approach to model development is to undertake a number of discrete modelling projects and progressively link them together by means of a common framework.
-Sub-projects we are currently engaged in include those to develop models of people (synthetic populations of interest describing relevant individual characteristics and their household relationships, choice models for predicting helpseeking behaviour and models to map psychological measures to health utility), places (synthesising geometry and spatial attribute data to characterise the geographic distribution of relevant demographic, environmental, epidemiological and service infrastructure features) and platforms (representing the processes and operations of a complex primary youth mental health service).
-We have also previously undertaken scoping work reviewing economic evidence relating to youth mental health programs [@RN33] and plan to integrate this with the model at a future date.
+Our approach to model development is to undertake a number of discrete modelling projects of the people, places, platforms and programs that shape the mental health and wellbeing of young people and to progressively link them together by means of a common framework.
+To model people we are developing synthetic representations of populations of interest [@DVN/HJXYKQ_2021] that describe relevant individual characteristics and their household relationships, algorithms that map psychological measures to health utility [@Hamilton2021.07.07.21260129] and choice models for predicting the helpseeking behaviour of young people.
+Our in development model of places [@DVN/V3OKZV_2022] aims to synthesise geometry and spatial attribute data to characterise the geographic distribution of relevant demographic, environmental, epidemiological and service infrastructure features and our first model of a service platform will represent the processes and operations of a complex primary youth mental health service.
+We also plan to extend our prior work reviewing economic evidence relating to youth mental health programs [@RN33] so that it can be integrated with the model.
+
+Our initial work on readyforwhatsnext is focused on Victoria, Australia but the framework we are using to develop it is designed to facilitate extension by ourselves and others to different decision contexts.
+Progress is reported on a project website [@rfwn2022].
 
 # Framework
-The framework we have developed consists of a set of standards for OSHEMs and tools for implementing those standards.
+The framework we have developed to implement readyforwhatsnext consists of specified standards for OSHEMs and tools for meeting those standards.
 
@@
  - **Licensed**: a model and its derivatives are persistently re-usable by other modellers; and
- - **Yielding**: a model can be deployed as a simple, flexible and reliable decision aid.
+ - **Yielding**: a model can be reliably deployed as a simple and flexible decision aid.
 
@@
 ### Epitomised Models
-A key challenge to generalising health economic models is that they are typically developed to inform a decision problem with a highly specific jurisdictional context. However, 
-Modular code is also recommended as good practice for scientific computing more generally [@Wilson_2017].
+A key challenge to generalising health economic models is that they are typically developed to inform a decision problem with a highly specific jurisdictional context.
+However, a number of choices about how these models are implemented can significantly increase the re-usability of model code in other contexts.
 
-[model functions - compare to analysis and reporting]
+Writing code as collections of functions (short, self-contained and reusable algorithms that each perform a discrete task) is recommended as good practice for scientific computing [@Wilson_2017].
+When distributed as libraries (for example, as R packages), functions have the potential to be widely re-used, often in contexts very different than those they were originally developed for.
+A special type of function called a method can only be applied to a pre-defined data structure.
+Due to the coding concept of inheritance [@8717448], the more restricted nature of methods can be used to enhance the re-usability of model code in different decision contexts [ready4oop2022].
+For example, when generalising a model developed for the Australian context to a UK context, we could create a data structure that initially inherits all of the methods defined for the Australian model and then write new or replacement methods as needed for the UK model.
+
+Whatever type of functions are written for a modelling project, it is good practice to make available test or toy data to demonstrate their use [@Wilson_2017].
 
@@
 ### Licensed Models
-copyleft licensing [@copyleft2022] is used to ensure that
+```{r}
+# Adapted fom: https://seankross.com/2016/08/02/How-R-Packages-are-Licensed.html
+sorting_hat <- function(student, houses){
+  choice <- purrr::map_lgl(houses, grepl, x = student)
+  if(!any(choice)){
+    return("Other")
+  } else {
+    return((houses[choice])[1])
+  }
+}
+license_table <- table(utils::available.packages()[,"License"])
+names(license_table) %<>%
+  purrr::map_chr(function(x){
+    sorting_hat(x, c("Apache", "Artistic", "CC", "BSD", "MIT", "GPL"))
+  })  
+license_tbl <- as.data.frame(license_table) %>%
+  dplyr::rename(License = Var1) %>%
+  dplyr::group_by(License) %>%
+  dplyr::summarize(Freq = sum(Freq)) %>%
+  dplyr::ungroup() %>%
+  dplyr::arrange(dplyr::desc(Freq))
+licenses <- license_tbl$Freq
+gpl_pc_dbl<- round(license_tbl$Freq[license_tbl$License=="GPL"]/sum(license_tbl$Freq)*100,2) 
+```
+
+To make model code and data widely re-usable by others, it is important to provide users with appropriate and explicit permissions.
+In the context of open source models, there are two broad categories of licensing options.
+Some guidance strongly recommends the use of permissive licensing [@Wilson_2017] that provides users with great flexibility as to the purposes (including commercial) for which the content could be re-used.
+An alternative approach is to use copyleft licenses [@copyleft2022] that can require content users to distribute any derivative works they create under similar open source arrangements.
+
+For code, it may be appropriate to adopt the prevailing open source licensing practice within the programming language being used.
+Applying a previously published algorithm [@kross2016] to analyse the most comprehensive archive of released R packages [@CRAN2022] finds that `$gpl_pc_dbl`% are distributed under various forms of General Public License (GPL) [@GNUGPL2022], a copyleft license.
+
+For data, it may not be sufficient to simply choose a license that is either permissive, for example Public Domain Dedication (CC0) [@cc02022], or copyleft like the Attribution-Share Alike (CC-BY-SA) [@bysa2022].
+Responsible custodianship of some de-identified mental health data may involve using or adapting template terms of use [@sampleterms2022] which have a number of ethical clauses (for example, prohibiting their use in efforts to re-identify research participants).
 
@@
 
-- **L2: Non-confidential model data is available for liberal re-use, subject to adherence clearly specified ethical standards**
+- **L2: Non-confidential model data is available for liberal re-use (subject to additional terms for de-identified human data)**
 
@@
 ### Yielding Models
-Shiny tutorial [@SmithR2020]
+OSHEMs can be time and skills intensive for modellers to develop - but they should be easy for others to use.
 
-- **Y1: Non- technical users can configure and run models via simple user-interfaces**
+Statistical models are a common output of health economic evaluations, but they are often not reported in a format that enables others to confidently and reliably re-use [@Kearns2013].
+Open source approaches can help address this, by disseminating code artefacts that enable easy and appropriate use of a statistical model to make predictions with new data.
+However, great care must be exercised when disseminating such artefacts if they describe models estimated from data on human subjects.
+In the R language, model objects by default typically contain a copy of the source dataset.
+Such dataset copies must therefore be replaced (for example, with fake data) and the amended artefact's predictive performance then retested before any public release of model code artefacts.
 
-- **Y2: Statistical models can be safely, consistently and flexibly deployed using standardised tools**
+Another was to make OSHEMs easier to use is to develop simple user-interfaces for non-technical users.
+In R, such user-interfaces are typically developed with the Shiny package, for which a tutorial aimed at health economists is available [@SmithR2020].
+
+- **Y2: Statistical models can be safely and appropriately reused using standardised toolkits** <!-- New, Replaces Old Y1 (now Y2) -->
+- **Y2: Non-technical users can configure and run models via simple user-interfaces** <!-- Was Y1 -->
 
@@
 
-### Technical platforms
+### Online Repositories
 

### 2022-05-28 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
failing table

@@
 
-Computational modelling could play an important role in developing policies to improve population mental health but this may require significant changes in the way mental health modelling projects are funded, conceptualised and implemented.
+<!-- Computational modelling could play an important role in developing policies to improve population mental health but this may require significant changes in the way mental health modelling projects are funded, conceptualised and implemented.
+-->
 
@@
 These types of models might also be the basis for developing reference models [@Afzali2013] of mental health systems that are intended for multiple-applications and re-use by different modelling teams.
+
 However, as they are intended for multiple-purposes and because propagation errors may be more likely with more complex models [@Saltelli2019] such models require greater investments in model transparency and validation [@Eddy2012; @Feenstra2022].
-
 The development, validation and maintenance of these more complex models may be simply too onerous a burden for a single modelling team.
@@
 - **T1: Uniquely identified copies of model code and data are permanently archived in open online repositories**
-
 <!-- T2 MISSING - Merged With T1 -->
@@
 An important consideration when combining model components (or modules) is to ensure that interactions between two modules do not compromise the validity of either.
-Using the coding practice of encapsulation [@8717448] can help ensure that model modules can be safely combined [ready4oop2022].
+Using the coding practice of encapsulation [@8717448] can help ensure that model modules can be safely combined [@ready4oop2022].
 
@@
 A special type of function called a method can only be applied to a pre-defined data structure.
-Due to the coding concept of inheritance [@8717448], the more restricted nature of methods can be used to enhance the re-usability of model code in different decision contexts [ready4oop2022].
-For example, when generalising a model developed for the Australian context to a UK context, we could create a data structure that initially inherits all of the methods defined for the Australian model and then write new or replacement methods as needed for the UK model.
+Due to the coding concept of inheritance [@8717448], the more restricted nature of methods can be used to enhance the re-usability of model code in different decision contexts [@ready4oop2022].
+For example, when generalising a model developed for the Australian context to a UK context, one could create a class (data structure) that initially inherits all of the methods defined for the Australian model and then write new or replacement methods as needed for the UK model.
 
@@
 For code, it may be appropriate to adopt the prevailing open source licensing practice within the programming language being used.
-Applying a previously published algorithm [@kross2016] to analyse the most comprehensive archive of released R packages [@CRAN2022] finds that `$gpl_pc_dbl`% are distributed under various forms of General Public License (GPL) [@GNUGPL2022], a copyleft license.
+Applying a previously published algorithm [@kross2016] to analyse the most comprehensive archive of released R packages [@CRAN2022] finds that `r `gpl_pc_dbl`% are distributed under various forms of General Public License (GPL) [@GNUGPL2022], a copyleft license.
 
-For data, it may not be sufficient to simply choose a license that is either permissive, for example Public Domain Dedication (CC0) [@cc02022], or copyleft like the Attribution-Share Alike (CC-BY-SA) [@bysa2022].
-Responsible custodianship of some de-identified mental health data may involve using or adapting template terms of use [@sampleterms2022] which have a number of ethical clauses (for example, prohibiting their use in efforts to re-identify research participants).
+For data, it may not be sufficient to simply choose between a permissive license like the Public Domain Dedication (CC0) [@cc02022] or a copyleft option such as the Attribution-Share Alike (CC-BY-SA) [@bysa2022].
+Responsible custodianship of some de-identified mental health data may involve using or adapting template terms of use [@sampleterms2022] which have a number of ethical clauses (for example, prohibiting efforts to re-identify research participants).
+
+Licenses may or may not specify that model re-users must give appropriate acknowledgement to model authors.
+Citation tools can be distributed with each cite individual code or data items to inform re-users of the desired attribution.
+In R, including a CITATION file in the `inst` directory of a package will enable users of that package to retrieve citation information by running a command of the format `citation("Package Name")` in the R console.
+More generally, including a CITATION.cff file at the top level of any software item (including those written in R), will enable GitHub and Zenodo repositories hosting that item to include the relevant information in their citation tools.
+Datasets hosted on Dataverse installations have metadata fields that, once completed by authors, generate citation files for dataset viewers.
 
@@
 
-- **L3: Model code and data are distributed with citation tools** <!-- New -->
+- **L3: Model code and data are distributed with tools to support appropriate citation** <!-- New -->
 
@@
 
-Statistical models are a common output of health economic evaluations, but they are often not reported in a format that enables others to confidently and reliably re-use [@Kearns2013].
-Open source approaches can help address this, by disseminating code artefacts that enable easy and appropriate use of a statistical model to make predictions with new data.
-However, great care must be exercised when disseminating such artefacts if they describe models estimated from data on human subjects.
+Statistical models are a common output of health economic evaluations, but they are often not reported in a format that enables others to confidently and reliably re-use them [@Kearns2013].
+Open source approaches can help address this by disseminating code artefacts that enable easy and appropriate use of a statistical model to make predictions with new data.
+However, great care must be exercised when doing so if models are derived from data on human subjects.
 In the R language, model objects by default typically contain a copy of the source dataset.
-Such dataset copies must therefore be replaced (for example, with fake data) and the amended artefact's predictive performance then retested before any public release of model code artefacts.
+Such dataset copies must therefore be replaced (for example, with fake data) and the amended artefact's predictive performance then retested before any public release.
 
-Another was to make OSHEMs easier to use is to develop simple user-interfaces for non-technical users.
+Another way to make OSHEMs easier to use is to develop simple user-interfaces for non-technical users.
 In R, such user-interfaces are typically developed with the Shiny package, for which a tutorial aimed at health economists is available [@SmithR2020].
+
+Standards:
 
@@
 ## Toolkits
+We have developed a toolkit to help streamline the process of developing OSHEMs that meet the TIMELY standards. The toolkit is comprised of online repositories and software.
 
 ### Online Repositories
+We have created a GitHub organisation (https://github.com/ready4-dev) for in development model code, a Zenodo community (https://zenodo.org/communities/ready4) for citable archived code and a Dataverse on the Harvard Dataverse for model data (https://dataverse.harvard.edu/dataverse/ready4).
 
-### Software Development Kit
+### Software
+We have written six R packages to support the development and curation of model code and data.
+The purpose of each package, the TIMELY standards they support and the existing R packages they depend on are summarised in Table 1.
+
+```{r cpkgs, tab.cap='Software', tab.id = 'cpkgs', echo = F, results = 'asis'}
+      tb <- tibble::tibble(Package = c("ready4","ready4fun"),
+                                                    Version = Package %>%
+                        purrr::map_chr(~utils::packageDescription(.x) %>%
+                                         purrr::pluck("Version")),
+                           Depends = Package %>%
+                         purrr::map(~ {
+                           utils::packageDescription(.x) %>%
+                             `[`(c("Depends", "Imports")) %>%
+                             purrr::map(~{
+                               if(is.null(.x)){
+                                 character(0)
+                               }else{
+                                 .x %>%
+                                   strsplit(",\\n") %>%
+                                   purrr::flatten_chr() %>%
+                                   purrr::map(~strsplit(.x,", ") %>%
+                                                purrr::flatten_chr()) %>%
+                                   purrr::flatten_chr() %>% sort() %>%
+                                   purrr::discard(~startsWith(.x,"R "))
+                               }
+                             }) %>%
+                             purrr::flatten_chr() %>%
+                             unique() %>%
+                             sort() %>%
+                         purrr::map_chr(~{
+                           updated_1L_chr <- stringr::str_replace_all(.x,"\\n"," ")
+                           problem_idx_1L_chr <- stringr::str_locate(updated_1L_chr," ")[1,1] %>%
+                             unname()
+                           if(!is.na(problem_idx_1L_chr))
+                             updated_1L_chr <- updated_1L_chr %>%
+                             stringr::str_sub(end = problem_idx_1L_chr-1)
+                           updated_1L_chr %>% trimws(which = "left")
+                         })
+                         })
+
+                       ) 
+# packages_df <- data.frame(Name = c("ready4", "ready4fun"),
+#                           Purpose = c("Provide framework modules and syntax",
+#                                       "Standardise and partially automate the authoring and documenting of functions."),
+#                           `Supports standard` = c("AAAA","BBB"),
+#                           Depends = c("A","B")) 
+params_ls<-list(output_type_1L_chr="PDF")
+tb  %>%
+    ready4show::print_table(output_type_1L_chr = params_ls$output_type_1L_chr,
+                            caption_1L_chr = knitr::opts_current$get("tab.cap"),
+                            mkdn_tbl_ref_1L_chr = paste0("tab:",knitr::opts_current$get("tab.id")),
+                            use_rdocx_1L_lgl = ifelse(params_ls$output_type_1L_chr=="Word",T,F),
+                            add_to_row_ls = NULL,
+                            sanitize_fn = NULL)
+```
 

### 2022-05-29 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
table 1 rough draft done

@@
 
-```{r child="MS_Tables.Rmd", echo=FALSE}
+```{r child="../Child_RMDs/MS_Tables.Rmd", echo=FALSE}
 ```
-```{r child="MS_Figures.Rmd", echo=FALSE}
+```{r child="../Child_RMDs/MS_Figures.Rmd", echo=FALSE}
 ```
@@
 When distributed as libraries (for example, as R packages), functions have the potential to be widely re-used, often in contexts very different than those they were originally developed for.
-A special type of function called a method can only be applied to a pre-defined data structure.
+A special type of function called a method can only be applied to a pre-defined class of data structure.
 Due to the coding concept of inheritance [@8717448], the more restricted nature of methods can be used to enhance the re-usability of model code in different decision contexts [@ready4oop2022].
-For example, when generalising a model developed for the Australian context to a UK context, one could create a class (data structure) that initially inherits all of the methods defined for the Australian model and then write new or replacement methods as needed for the UK model.
+For example, when generalising a model developed for the Australian context to a UK context, one could create a class that initially inherits all of the methods defined for the Australian model and then write new or replacement methods as needed for the UK model.
 
@@
 
-- **E1: Model code is distributed as libraries of functions**  <!-- Modified (lost ref to OOP and merged with M2) -->
+- **E1: Model code is distributed as libraries of classes and functions**  <!-- Modified (lost ref to OOP and merged with M2) -->
 
@@
   dplyr::arrange(dplyr::desc(Freq))
-licenses <- license_tbl$Freq
-gpl_pc_dbl<- round(license_tbl$Freq[license_tbl$License=="GPL"]/sum(license_tbl$Freq)*100,2) 
+#licenses <- license_tbl$Freq
+gpl_pc_dbl <- round(license_tbl$Freq[license_tbl$License=="GPL"]/sum(license_tbl$Freq)*100,2) 
 ```
@@
 
-- **Y2: Statistical models can be safely and appropriately reused using standardised toolkits** <!-- New, Replaces Old Y1 (now Y2) -->
+- **Y1: Statistical models can be safely and appropriately reused using standardised toolkits** <!-- New, Replaces Old Y1 (now Y2) -->
 - **Y2: Non-technical users can configure and run models via simple user-interfaces** <!-- Was Y1 -->
@@
 
+```{r, child = child_docs_ls$one, echo=FALSE}
+```
+
 ### Software
 We have written six R packages to support the development and curation of model code and data.
-The purpose of each package, the TIMELY standards they support and the existing R packages they depend on are summarised in Table 1.
-
-```{r cpkgs, tab.cap='Software', tab.id = 'cpkgs', echo = F, results = 'asis'}
-      tb <- tibble::tibble(Package = c("ready4","ready4fun"),
-                                                    Version = Package %>%
-                        purrr::map_chr(~utils::packageDescription(.x) %>%
-                                         purrr::pluck("Version")),
-                           Depends = Package %>%
-                         purrr::map(~ {
-                           utils::packageDescription(.x) %>%
-                             `[`(c("Depends", "Imports")) %>%
-                             purrr::map(~{
-                               if(is.null(.x)){
-                                 character(0)
-                               }else{
-                                 .x %>%
-                                   strsplit(",\\n") %>%
-                                   purrr::flatten_chr() %>%
-                                   purrr::map(~strsplit(.x,", ") %>%
-                                                purrr::flatten_chr()) %>%
-                                   purrr::flatten_chr() %>% sort() %>%
-                                   purrr::discard(~startsWith(.x,"R "))
-                               }
-                             }) %>%
-                             purrr::flatten_chr() %>%
-                             unique() %>%
-                             sort() %>%
-                         purrr::map_chr(~{
-                           updated_1L_chr <- stringr::str_replace_all(.x,"\\n"," ")
-                           problem_idx_1L_chr <- stringr::str_locate(updated_1L_chr," ")[1,1] %>%
-                             unname()
-                           if(!is.na(problem_idx_1L_chr))
-                             updated_1L_chr <- updated_1L_chr %>%
-                             stringr::str_sub(end = problem_idx_1L_chr-1)
-                           updated_1L_chr %>% trimws(which = "left")
-                         })
-                         })
-
-                       ) 
-# packages_df <- data.frame(Name = c("ready4", "ready4fun"),
-#                           Purpose = c("Provide framework modules and syntax",
-#                                       "Standardise and partially automate the authoring and documenting of functions."),
-#                           `Supports standard` = c("AAAA","BBB"),
-#                           Depends = c("A","B")) 
-params_ls<-list(output_type_1L_chr="PDF")
-tb  %>%
-    ready4show::print_table(output_type_1L_chr = params_ls$output_type_1L_chr,
-                            caption_1L_chr = knitr::opts_current$get("tab.cap"),
-                            mkdn_tbl_ref_1L_chr = paste0("tab:",knitr::opts_current$get("tab.id")),
-                            use_rdocx_1L_lgl = ifelse(params_ls$output_type_1L_chr=="Word",T,F),
-                            add_to_row_ls = NULL,
-                            sanitize_fn = NULL)
-```
+The package ready4 defines the framework's syntax and a model module template class.
+The ready4class package provides tools for creating self-documenting model module classes, while ready4fun is a toolkit for creating the functions (including methods) that are also self-documenting and written in a consistent house style.
+Model module classes and functions are bundled into R packages with standardised approaches to quality assurance and documentation using the the ready4pack package.
+Tools for creating and managing model data are included in the ready4use package, while tools for the analysis and reporting of models are included in the ready4show package.
+The purpose of each package, the TIMELY standards they support and the third party R packages they depend on are summarised in Table 1.
+<!-- Autogenerate ref -->
 

### 2022-05-30 Markdown/Manuscript/Child_RMDs/Doodles.Rmd
first efforts with t2

@@
 ---
+
+Libraries:
+describing and validating input data [@hamilton_matthew_2022_6084467], 
+scoring health utility data [@hamilton_matthew_2022_6084824], 
+specifying and testing mapping models [@hamilton_matthew_2022_6116701] 
+reporting mapping studies [@gao_caroline_2022_6130155].
+make predictions with new data using another R package [@matthew_p_hamilton_2021_5646669] that we developed
+
+Programs:
+CSP [@hamilton_matthew_2022_6129906]
+Predict [@hamilton_matthew_2022_6416330]
+Make Fakes [@hamilton_matthew_p_2022_6321821]
+
+Sub-routines:
+Ctlg: [@hamilton_matthew_2022_6116385]
+SS: [@matthew_p_hamilton_2022_5976988]
+
+Data
+results / replication [@DVN/DKDIB0_2021]  
+Fake [@DVN/HJXYKQ_2021]
+
+To facilitate appropriate use of the mapping models we developed we created catalogues with detailed information about the performance of all models generated by our study under multiple types of regime (e.g.
+whether: mean or sampled parameter values are used; minimum and maximum constraints are applied to prediction results; the original R model objects or just tables of model coefficients are used).
 

### 2022-05-30 Markdown/Manuscript/Child_RMDs/MS_Conclusion.Rmd
first efforts with t2

@@
 `r ifelse(is.na(params$X@conclusion_1L_chr),"",params$X@conclusion_1L_chr)` 
+<!-- Standards generalisable, Toolkit less os -->

### 2022-05-30 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
first efforts with t2

@@
 <!-- `r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`  -->
-Computational models have become essential tools for health policy development [@Erdemir2020].
+Health economic computational models have become essential tools for health policy development [@dakin2015influence; @Erdemir2020].
 Although influential and widely used, these models routinely contain errors [@Radeva2020], are rarely adequately validated [@Ghabri2019], can be difficult to reproduce [@Jalali2021; @McManus2019; @Bermejo2017] and are likely to be infrequently updated or revised [@Sampson2017].
-To help address these issues, there is growing support for greater use of open source health economics models (OSHEMs) that grant liberal permissions to access and re-use model source code [@Pouwels2022].
+To help address these issues, there is growing support for greater use of open source health economic models (OSHEMs) that grant liberal permissions to access and re-use model source code [@Pouwels2022].
 However, to date actual implementations of OSHEMs are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022].
@@
 
-There is also a need to develop good practice recommendations for OSHEMs [@Sampson2019].
-Adherence to explicit standards is as essential requirement for quality health economic model implementation [@Erdemir2020], but current guidance for OSHEMs is scarce and piecemeal.
+Better guidance about how to implement OSHEMs is required [@Sampson2019].
+Adherence to explicit standards is as essential requirement for modelling in healthcare [@Erdemir2020], but current best practice recommendations for OSHEMs are scarce and piecemeal.
 Guidelines on health economic model transparency were published ten years ago [@Eddy2012] and made recommendations on documenting models but notably not on the sharing of model code and data.

### 2022-05-30 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
first efforts with t2

@@
 -->
+Open source frameworks have been previously recommended for the development of mental health modelling field [@RN73] but, as with health economics more generally, OSHEMs remain rare.
+Currently there is only one mental health related model (in Alcohol Use Disorder [@Basu2018]) that is indexed in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019].
+A Major Depressive Disorder reference model for the United States [@IVIMDD2022] is also being developed as part of the Open Value Initiative [@Jansen2019].
+Greater use of open source approaches could help improve the scope, validity and usefulness of mental health economic models.
 
-Major mental health reform programs will require the identification, prioritisation, sequencing, targeting and monitoring of multiple interdependent initiatives.
+Major mental health reform programs, such as those currently being implemented in Victoria, Australia [@VicRC2021], can involve the identification, prioritisation, sequencing, targeting and monitoring of multiple interdependent initiatives.
 Single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020].
 Currently, mental health economic models predominantly address issues relating to the affordability and value for money of individual programs [@RN34] with mental health simulation studies rarely modelling complex systems [@RN73].
-Greater use of dynamic systems modelling approaches could provide new insights about inter-dependencies between candidate policies and the evolution of the mental health systems planning context [@Occhipinti2021].
-These types of models might also be the basis for developing reference models [@Afzali2013] of mental health systems that are intended for multiple-applications and re-use by different modelling teams.
+Systems modelling approaches, that have been recommended for public health economics more generally [@SQUIRES2016588] and for mental health specifically [@Occhipinti2021], could provide greater insight about inter-dependencies between candidate policies and the dynamic nature of the mental health systems planning context.
+Dynamic systems methods might also be the basis for developing reference models [@Afzali2013] of mental health systems that are intended for multiple-applications and re-use by different modelling teams.
+However, more complex models may be more prone to error [@Saltelli2019] and models designed for multiple purposes require greater investments in model transparency and validation [@Eddy2012; @Feenstra2022].
 
-However, as they are intended for multiple-purposes and because propagation errors may be more likely with more complex models [@Saltelli2019] such models require greater investments in model transparency and validation [@Eddy2012; @Feenstra2022].
-The development, validation and maintenance of these more complex models may be simply too onerous a burden for a single modelling team.
-Developing networks of modellers working on common health conditions [@Sampson2019] and collaborations across multiple modelling teams that include the ability to re-use and extend each others work, can make complex modelling projects more tractable [@Arnold2010].
-Similarly, more attention to developing partnerships between modellers and decision-makers across the life-cycle of a modelling project can help ensure models are appropriately conceptualised and implemented and improve their practical utility as decision aids [@Zabell2021].
-
-Modelling projects should be resourced to be routinely updated and refined as new evidence emerges and decision contexts change [@Jenkins2021].
-There are significant deficits in our understanding of the systems in which mental disorder emerges and is treated [@Fried2020] and longer term project horizons could allow mental health models to progressively improve validity as these gaps are addressed.
+To retain and improve their utility as decision aids, health economic models require updating and refinement as new evidence emerges and decision contexts change [@Jenkins2021].
+There are significant deficits in our understanding of the systems in which mental disorder emerges and is treated [@Fried2020] and longer term project horizons could allow mental health economic models to progressively improve validity as these gaps are addressed.
 Currently, the theoretical basis for understanding complex mental health systems is weak [@RN2111].
@@
 
-Open source frameworks have been previously recommended for the development of mental health modelling field [@RN73] but, as with health economics more generally, OSHEMs remain rare.
-Currently there is only one mental health related model (in Alcohol Use Disorder [@Basu2018]) that is indexed in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019].
-A Major Depressive Disorder reference model for the United States [@IVIMDD2022] is also being developed as part of the Open Value Initiative [@Jansen2019].
-We believe greater support for open source approaches have the potential to provide more transparent, collaborative and sustained approaches to mental health system model development.
+The development, validation and updating of more complex mental health economic models implemented over longer time frames may be too onerous a burden for a single modelling team.
+Developing networks of modellers working on common health conditions has been recommended as a strategy for improving model validity [@Sampson2019] and a some of us are part of a nascent initiate of this type in mental health [@nmhsmn2022].
+Furthermore, collaborations across multiple modelling teams that include the ability to re-use and extend each others work can make complex modelling projects more tractable [@Arnold2010].
+<!-- Add ref to NMHSMN in Australia --> Similarly, developing partnerships between modellers and decision-makers across the life-cycle of a modelling project can help ensure models are appropriately conceptualised and implemented and improve their practical utility as decision aids [@Zabell2021; @SQUIRES2016588].
 
@@
 # Framework
-The framework we have developed to implement readyforwhatsnext consists of specified standards for OSHEMs and tools for meeting those standards.
+The framework we have developed to implement readyforwhatsnext specifies standards for OSHEMs and provides tools for meeting those standards.
 
@@
  - **Modular**: models and their components can be combined to extend their scope;
- - **Epitomized**: models can be used in multiple decision contexts;
- - **Licensed**: a model and its derivatives are persistently re-usable by other modellers; and
- - **Yielding**: a model can be reliably deployed as a simple and flexible decision aid.
+ - **Epitomized**: a model and its components can be used in multiple decision contexts;
+ - **Licensed**: a model, its components and derivatives are persistently re-usable by other modellers; and
+ - **Yielding**: a model can be simply, flexibly and reliably used to inform decision-making.
 
 ### Transparent Models
-A range of tools and practices are available to help make model code and data accessible, citable and comprehensible.
+A range of tools and practices are available to help make model code and data accessible, comprehensible and citable.
 The most efficient way to widely disseminate code and data may be to use existing open science infrastructure [@Erdemir2020].
@@
 Consistent use of meaningful naming conventions when authoring code is recommended [@Wilson_2017; @Alarid2019].
-The main logic of a program can be made comprehensible to even non-technical users though the use of the common practices of abstraction [@8717448], where only simple, high level commands are routinely exposed to reviewers, and polymorphsim [@7181447], where the same command (e.g.
-"simulate") can be reused to implement different algorithms of the same broad type.
-Literate programming, where tools like RMarkdown [@xie2018r] are used to render documents that integrate computer code with plain English descriptions of each step in an analysis workflow, can make code easier to follow by both technical and non-technical users.
+Code can be made easier to follow by using the practices of abstraction [@8717448], where only simple, high level commands are routinely exposed to reviewers, and polymorphsim [@7181447], where the same command (e.g.
+"simulate") can be reused to implement different algorithms of the same type.
+Programs to implement model analyses can be made comprehensible to even non-technical users though the use of literate programming techniques that use tools like RMarkdown [@xie2018r] to render documents that integrate computer code with plain English descriptions.
 
@@
 Datasets stored on the Harvard Dataverse use the simpler Major.Minor convention.
-
 Continuous integration [@CI2017] tools can help verify that each code update passes multiple quality tests.
@@
 
-- **E3: Test data is available to demonstrate generalised model applications**
+- **E3: Test data is available to demonstrate generalised applications of model code**
 
@@
 Citation tools can be distributed with each cite individual code or data items to inform re-users of the desired attribution.
-In R, including a CITATION file in the `inst` directory of a package will enable users of that package to retrieve citation information by running a command of the format `citation("Package Name")` in the R console.
-More generally, including a CITATION.cff file at the top level of any software item (including those written in R), will enable GitHub and Zenodo repositories hosting that item to include the relevant information in their citation tools.
+In R, including a CITATION file in the `inst` directory of a package will enable users of that package to retrieve citation information by running a command of the format `citation("Package Name")` in the R console [@Salmon2021].
+More generally, including a CITATION.cff file at the top level of your code repository will enable GitHub and Zenodo repositories hosting that item to include the relevant information in their citation tools [@Druskat_Citation_File_Format_2021].
 Datasets hosted on Dataverse installations have metadata fields that, once completed by authors, generate citation files for dataset viewers.
@@
 
-- **Y1: Statistical models can be safely and appropriately reused using standardised toolkits** <!-- New, Replaces Old Y1 (now Y2) -->
-- **Y2: Non-technical users can configure and run models via simple user-interfaces** <!-- Was Y1 -->
+- **Y1: Statistical models are distributed with validated tools to support their safe and appropriate re-use** <!-- New, Replaces Old Y1 (now Y2) -->
+- **Y2: Simple user-interfaces allow non-technical users to configure and run models ** <!-- Was Y1 -->
 
-## Toolkits
+## Modelling tools
 We have developed a toolkit to help streamline the process of developing OSHEMs that meet the TIMELY standards. The toolkit is comprised of online repositories and software.
 
-### Online Repositories
-We have created a GitHub organisation (https://github.com/ready4-dev) for in development model code, a Zenodo community (https://zenodo.org/communities/ready4) for citable archived code and a Dataverse on the Harvard Dataverse for model data (https://dataverse.harvard.edu/dataverse/ready4).
+### Framework repositories <!-- Existing ref -->
+We created a GitHub organisation where all framework software source code is stored, documented, version controlled and continuously integrated [@ready4gh2022].
+To store citable archived copies of release copies of our software, we created a Zenodo community [@ready4zen2022].
+Finally, to manage datasets for use in models developed with the framework, we created a dedicated collection within the Harvard Dataverse  [@ready4dv2022].
+
+### Framework software <!-- Novel ref -->
+As a foundation for implementing the framework, we authored a development version R package that defines a novel syntax and a template class for model modules [@ready42022].
+To enable the syntax and module template be applied to modelling projects, we then created five additional development version R packages that provide tools for authoring:
+
+- self-documenting model modules [@ready4class2022];
+
+- self-documenting functions (including methods), written in a consistent house style [@ready4fun2022];
+
+- citable, quality assured R packages [@ready4pack2022];
+
+- model datasets [@ready4use2022];
+
+- model analyses and reports [@ready4show2022].
+
+The six R packages, their primary focus, the TIMELY standards they support and the third party packages they depend on are summarised in Table \@ref(tab:cpkgs).
+When used in conjunction with framework repositories, the six packages currently provide strong support for implementing 17 of the TIMELY standards, weak support for implementing the standards relating to disseminating statistical models (Y1) and user-interface development (Y2) and no support for implementing standard T5 (reporting code coverage).
+Our future development priorities for these packages include adding functionality so that all 20 TIMELY standards are well supported and to then submit production versions of each package for review by and archiving on the Comprehensive R Archive Network (CRAN) [@CRAN2022].
 
@@
 
-### Software
-We have written six R packages to support the development and curation of model code and data.
-The package ready4 defines the framework's syntax and a model module template class.
-The ready4class package provides tools for creating self-documenting model module classes, while ready4fun is a toolkit for creating the functions (including methods) that are also self-documenting and written in a consistent house style.
-Model module classes and functions are bundled into R packages with standardised approaches to quality assurance and documentation using the the ready4pack package.
-Tools for creating and managing model data are included in the ready4use package, while tools for the analysis and reporting of models are included in the ready4show package.
-The purpose of each package, the TIMELY standards they support and the third party R packages they depend on are summarised in Table 1.
-<!-- Autogenerate ref -->
-
 # Application
@@
 Worked example
+
+```{r tab.cap='TIMELY Checklist with utility mapping study worked example', tab.id = 'checklisttb', echo = F, results = 'asis'}
+    #  a <- c("TEST1","TEST2")
+    # b <- c("\\cite{ready4show2022}", "hjhjhj")
+    # tmp <- data.frame(a,b)   
+#     kableExtra::kbl(tmp, booktabs = T, escape = F) %>%
+#  kableExtra::kable_styling(
+#    latex_options = c("striped", "hold_position", "repeat_header")
+#    ) %>%  
+#   kableExtra::column_spec(2, width = "50em") %>%
+# kableExtra::landscape()
+
+checklist_df <- data.frame(Standard = c(paste0("T",1:6, c(" (Publicly archived)",
+                                                          " (Documented)",
+                                                          " (Simple Syntax)",
+                                                          " (Literate programming)",
+                                                          " (Code coverage)",
+                                                          " (Reproducibility")),
+                                        paste0("I",1:4, c(" (Version controlled)",
+                                                          " (Semantic versioning)",
+                                                          " (Continuous integration)",
+                                                          " (Deprecation)")),
+                                        paste0("M",1:2, c(" (Decouple code and data)",
+                                                          " (Encapsulation)")),
+                                        paste0("E",1:3, c(" (Code libraries)",
+                                                          " (Inheritance)",
+                                                          " (Test data)")),
+                                        paste0("L",1:3, c(" (Copyleft for code)",
+                                                          " (Liberal, safe data terms)",
+                                                          " (Citation tools)")),
+                                        paste0("Y",1:2, c(" (Statistical model tools)",
+                                                          " (User-interfaces"))),
+                           Assessment = rep("Met so well it hurts",20),
+                           Description = c("5 libraries [@hamilton_matthew_2022_6084467;@hamilton_matthew_2022_6084824;@hamilton_matthew_2022_6116701;@gao_caroline_2022_6130155;@matthew_p_hamilton_2021_5646669], 3 programs [@hamilton_matthew_2022_6129906;@hamilton_matthew_2022_6416330;@hamilton_matthew_p_2022_6321821], 2 sub-routines [@hamilton_matthew_2022_6116385;@matthew_p_hamilton_2022_5976988] and 2 datasets [@DVN/DKDIB0_2021;@DVN/HJXYKQ_2021]",
+# @hamilton_matthew_2022_6084467;@hamilton_matthew_2022_6084824;@hamilton_matthew_2022_6116701;@gao_caroline_2022_6130155;@matthew_p_hamilton_2021_5646669
+# Programs:
+
+# 
+# Sub-routines:
+
+                                           "XX",
+                                           "XX",
+                                           "XX",
+                                           "XX",
+                                           "XX",
+                                           "XX",
+                                           "XX",
+                                           "XX",
+                                           "XX",
+                                           "XX",
+                                           "XX",
+                                           "XX",
+                                           "XX",
+                                           "XX",
+                                           "XX",
+                                           "XX",
+                                           "XX",
+                                           "XX",
+                                           "XX"))
+
+tb2_nms_chr<-colnames(checklist_df)
+checklist_df <- data.frame(checklist_df[,1],
+                 rep("&nbsp; &nbsp; &nbsp;",nrow(checklist_df)),
+                 checklist_df[,2],
+                 rep("&nbsp; &nbsp; &nbsp;",nrow(checklist_df)),
+                 checklist_df[,3])
+colnames(checklist_df) <- c("","Standard",
+                            "Met?", " ",
+                            tb2_nms_chr[3])
+if(params$X@outp_formats_chr[1] == "Word") {
+  checklist_df %>%
+    ready4show::print_table(output_type_1L_chr = params$X@outp_formats_chr[1],
+                            caption_1L_chr = knitr::opts_current$get("tab.cap"),
+                            mkdn_tbl_ref_1L_chr = paste0("tab:",knitr::opts_current$get("tab.id")),
+                            use_rdocx_1L_lgl = ifelse(params$X@outp_formats_chr[1]=="Word",T,F),
+                            add_to_row_ls = NULL,
+                            sanitize_fn = NULL)
+  }else{
+    checklist_df %>%
+    kableExtra::kbl(format = "markdown",
+                      #escape = F,
+                    caption = knitr::opts_current$get("tab.cap"))
+    # df %>%
+    #   kableExtra::kbl(booktabs = T,
+    #                   caption = knitr::opts_current$get("tab.cap")) %>%
+    #   kableExtra::kable_styling(full_width = F) %>%
+    #   kableExtra::column_spec(9, width = "17em") %>%
+    #   kableExtra::add_header_above(c(" " = 2, "Supports standard" = 6, " "))
+    }
+```

### 2022-05-31 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
table two done

@@
 
-```{r tab.cap='TIMELY Checklist with utility mapping study worked example', tab.id = 'checklisttb', echo = F, results = 'asis'}
+\blandscape
+
+```{r tab.cap='TIMELY Checklist applied to utility mapping study', tab.id = 'checklisttb', echo = F, results = 'asis'}
     #  a <- c("TEST1","TEST2")
@@
 
-checklist_df <- data.frame(Standard = c(paste0("T",1:6, c(" (Publicly archived)",
-                                                          " (Documented)",
-                                                          " (Simple Syntax)",
-                                                          " (Literate programming)",
-                                                          " (Code coverage)",
-                                                          " (Reproducibility")),
-                                        paste0("I",1:4, c(" (Version controlled)",
-                                                          " (Semantic versioning)",
-                                                          " (Continuous integration)",
-                                                          " (Deprecation)")),
-                                        paste0("M",1:2, c(" (Decouple code and data)",
-                                                          " (Encapsulation)")),
-                                        paste0("E",1:3, c(" (Code libraries)",
-                                                          " (Inheritance)",
-                                                          " (Test data)")),
-                                        paste0("L",1:3, c(" (Copyleft for code)",
-                                                          " (Liberal, safe data terms)",
-                                                          " (Citation tools)")),
-                                        paste0("Y",1:2, c(" (Statistical model tools)",
-                                                          " (User-interfaces"))),
-                           Assessment = rep("Met so well it hurts",20),
-                           Description = c("5 libraries [@hamilton_matthew_2022_6084467;@hamilton_matthew_2022_6084824;@hamilton_matthew_2022_6116701;@gao_caroline_2022_6130155;@matthew_p_hamilton_2021_5646669], 3 programs [@hamilton_matthew_2022_6129906;@hamilton_matthew_2022_6416330;@hamilton_matthew_p_2022_6321821], 2 sub-routines [@hamilton_matthew_2022_6116385;@matthew_p_hamilton_2022_5976988] and 2 datasets [@DVN/DKDIB0_2021;@DVN/HJXYKQ_2021]",
-# @hamilton_matthew_2022_6084467;@hamilton_matthew_2022_6084824;@hamilton_matthew_2022_6116701;@gao_caroline_2022_6130155;@matthew_p_hamilton_2021_5646669
-# Programs:
-
-# 
-# Sub-routines:
-
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX"))
+checklist_df <- data.frame(Ref = c(paste0("T",1:6),
+                                        paste0("I",1:4),
+                                        paste0("M",1:2),
+                                        paste0("E",1:3),
+                                        paste0("L",1:3),
+                                        paste0("Y",1:2)),
+                           Standard = c("Publicly archived",
+                                        "Documented",
+                                        "Consistent syntax",
+                                        "Literately programmed",
+                                        "Code coverage",
+                                        "Reproducible",
+                                        "Version controlled",
+                                        "Semanticly versioned",
+                                        "Continuously integrated",
+                                        "Deprecation",
+                                        "Separate code and data",
+                                        "Encapsulated",
+                                        "Libraries",
+                                        "Inheriting",
+                                        "Test data",
+                                        "Copyleft code",
+                                        "Liberal, safe data terms",
+                                        "Citation tools",
+                                        "Prediction tools",
+                                        "User interface"),
+                           Assessment = rep("F",20),
+                           Description = c("5 libraries (youthvars, scorz, specific, TTU and youthu) [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155; @matthew_p_hamilton_2021_5646669], <br> 3 programs [@hamilton_matthew_2022_6129906; @hamilton_matthew_2022_6416330; @hamilton_matthew_p_2022_6321821], 2 sub-routines [@hamilton_matthew_2022_6116385; @matthew_p_hamilton_2022_5976988] and 2 datasets [@DVN/DKDIB0_2021; @DVN/HJXYKQ_2021] are permanently archived with unique identifiers.",
+                                           "All code libraries have documenting websites with URLs that concatenate 'https://ready4-dev.github.io/' and the package name (e.g.
+https://ready4-dev.github.io/youthvars).
+All three Markdown programs are self-documenting, with one [@hamilton_matthew_2022_6129906] including additional instructions in a README file.
+Only one sub-routine [@matthew_p_hamilton_2022_5976988] is documented with a meaningful README file.
+All datasets have meaningful metadata descriptors.",
+                                           "All libraries, programs and sub-routines use the same house style.
+All libraries except [@matthew_p_hamilton_2021_5646669] use framework syntax, as does one program [@hamilton_matthew_2022_6129906].",
+                                           "All programs use literate programming.",
+                                           "No current reporting of code coverage.",
+                                           "All parts of the study workflow from raw data ingest through to data processing, analysis, reporting and dissemination of study outputs can be reproduced (if granted access to source data) or replicated (using supplied synthetic data) with one program [@hamilton_matthew_2022_6129906].",
+                                           "All code is version controlled using Git and GitHub. All source code is available in one of two GitHub organisations [@ready4gh2022; @orygengh2022].",
+                                           "Semantic version is used in all code.
+As no code library has yet been submitted to CRAN, only the development version extensions of each version number have been incremented to date.",
+                                           "All six libraries use continuous integration (CI).
+CI results for each library can be viewed at URL that concatenates 'https://github.com/ready4-dev/' the package name and '/actions' (e.g.
+https://github.com/ready4-dev/youthvars/actions)",
+                                           "Retired code is deprecated using lifecycle package tools (e.g.
+review everything after “## DEPRECATED FNS” in https://github.com/ready4-dev/youthvars/blob/main/data-raw/fns/add.R .
+Package vignettes and datasets are also deprecated e.g.
+https://ready4-dev.github.io/youthvars/articles/Replication_DS.html )",
+                                           "All development code is stored on repos in two GitHub organisations [@ready4gh2022; @orygengh2022] and all archived releases are available in aZenodo community [@ready4zen2022].
+All non-confidential data is stored in repositories within a Harvard Dataverse collection [@ready4dv2022].
+",
+                                           "Four [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155] out of five libraries include encapsulated  modules.
+Examples are the items beginning with Scorz, Specific and Youthvars that are listed in this table: https://ready4-dev.github.io/ready4/articles/V_01.html#current-ready4-framework-modules as well as the S4 classess from the TTU package listed here: https://ready4-dev.github.io/TTU/reference/index.html ",
+                                           "All code libraries include functions.
+The most complete list of functions for each library is available by clicking the 'Manual - Developer (PDF)' link on each package's documentation homepage (see item T2 above).",
+                                           "All modules (see item M2) inherit from the Ready4Module class.",
+                                           "Two synthetic datasets and their data dictionaries are publicly available in a data repository [@DVN/HJXYKQ_2021].
+One (ymh_clinical_tb.RDS) closely resembles the study dataset and was released so that the main study algorithm [@hamilton_matthew_2022_6129906] can be rerun by those without access to the confidential data.
+The other (eq5d_ds_dict.RDS) is deliberately different to the source dataset in both variable naming convention and the concepts used for predictors and outcome measures and was created to demonstrate generalised applications of study algorithms.",
+                                           "All code libraries, programs and sub-routines use GPL-3 licenses. ",
+                                           "Datasets use amended version of template provided by Harvard Dataverse [@sampleterms2022].",
+                                           "All libraries have CITATION file in inst directory. All code repositories have CITATION.cff file. All datasets have citation generating metadata.",
+                                           "Model catalogues (PDF files beginning with 'AAA_TTU_MDL_CTG') describe the predictive performance of all models under a variety of usage regimes and are available in the study results dataset [@DVN/DKDIB0_2021].
+The youthu library [@matthew_p_hamilton_2021_5646669] includes tools for searching for and applyihg models compatible with different types of input data.
+An example program to demonstrate this functionality is available in RMarkdown [@hamilton_matthew_2022_6416330] and rendered PDF formats (the 'Application.pdf' file in the study results dataset [@DVN/DKDIB0_2021]).
+",
+                                           "No Shiny app user interface has yet been developed."))
 
@@
 checklist_df <- data.frame(checklist_df[,1],
-                 rep("&nbsp; &nbsp; &nbsp;",nrow(checklist_df)),
+                 rep("&nbsp; ",nrow(checklist_df)),
                  checklist_df[,2],
-                 rep("&nbsp; &nbsp; &nbsp;",nrow(checklist_df)),
-                 checklist_df[,3])
-colnames(checklist_df) <- c("","Standard",
-                            "Met?", " ",
-                            tb2_nms_chr[3])
+                 rep("&nbsp; &nbsp; &nbsp; &nbsp; ",nrow(checklist_df)),
+                 checklist_df[,3],
+                 rep("&nbsp; ",nrow(checklist_df)),
+                 checklist_df[,4])
+colnames(checklist_df) <- c(" "," ","Standard",#
+                             "   ","Met?","   ",
+                            tb2_nms_chr[4])
 if(params$X@outp_formats_chr[1] == "Word") {
@@
     kableExtra::kbl(format = "markdown",
-                      #escape = F,
+                    booktabs = T,
+                    #escape = T,
                     caption = knitr::opts_current$get("tab.cap")) 
@@
 ```
+
+\elandscape

### 2022-05-31 Markdown/Manuscript/Child_RMDs/MS_Available_Data_And_Resources.Rmd
circulated draft

---
title: "MS_Available_Data_And_Resources"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---

Development versions of all code repositories referenced in this article are available in https://github.com/ready4-dev/ . Archived code releases are available in https://zenodo.org/communities/ready4  .

All data repositories referenced in this article are available in https://dataverse.harvard.edu/dataverse/ready4 .

### 2022-05-31 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
circulated draft

@@
 
-MH systems design is not a pharma led project - less concerns about commercial ownership
+<!-- MH systems design is not a pharma led project - less concerns about commercial ownership -->
 
-greater use of these types of models may require adaptation on the part of funders, modellers and decision-makers. T
+<!-- greater use of these types of models may require adaptation on the part of funders, modellers and decision-makers. T -->

### 2022-05-31 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
circulated draft

@@
 Although influential and widely used, these models routinely contain errors [@Radeva2020], are rarely adequately validated [@Ghabri2019], can be difficult to reproduce [@Jalali2021; @McManus2019; @Bermejo2017] and are likely to be infrequently updated or revised [@Sampson2017].
-To help address these issues, there is growing support for greater use of open source health economic models (OSHEMs) that grant liberal permissions to access and re-use model source code [@Pouwels2022].
+To help address these issues, there is growing support for greater use of open source health economic models (OSHEMs) that grant liberal permissions to access and re-use model source code and data [@Pouwels2022].
 However, to date actual implementations of OSHEMs are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022].

### 2022-05-31 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
circulated draft

--- 2022-05-30 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
@@
 
+```{r child="../Child_RMDs/XX_Funs.Rmd", echo=FALSE}
+```
 ```{r child="../Child_RMDs/MS_Tables.Rmd", echo=FALSE}
@@
 The development, validation and updating of more complex mental health economic models implemented over longer time frames may be too onerous a burden for a single modelling team.
-Developing networks of modellers working on common health conditions has been recommended as a strategy for improving model validity [@Sampson2019] and a some of us are part of a nascent initiate of this type in mental health [@nmhsmn2022].
+Developing networks of modellers working on common health conditions has been recommended as a strategy for improving model validity [@Sampson2019] and some of us are part of a nascent initiate of this type in mental health [@nmhsmn2022].
 Furthermore, collaborations across multiple modelling teams that include the ability to re-use and extend each others work can make complex modelling projects more tractable [@Arnold2010].
@@
 Our approach to model development is to undertake a number of discrete modelling projects of the people, places, platforms and programs that shape the mental health and wellbeing of young people and to progressively link them together by means of a common framework.
-To model people we are developing synthetic representations of populations of interest [@DVN/HJXYKQ_2021] that describe relevant individual characteristics and their household relationships, algorithms that map psychological measures to health utility [@Hamilton2021.07.07.21260129] and choice models for predicting the helpseeking behaviour of young people.
-Our in development model of places [@DVN/V3OKZV_2022] aims to synthesise geometry and spatial attribute data to characterise the geographic distribution of relevant demographic, environmental, epidemiological and service infrastructure features and our first model of a service platform will represent the processes and operations of a complex primary youth mental health service.
-We also plan to extend our prior work reviewing economic evidence relating to youth mental health programs [@RN33] so that it can be integrated with the model.
+To model people we are developing synthetic representations of populations of interest [@DVN/HJXYKQ_2021] that describe relevant individual characteristics and their relationships, algorithms that map psychological measures to health utility [@Hamilton2021.07.07.21260129] and choice models for predicting the helpseeking behaviour of young people.
+Our in development model of places [@DVN/V3OKZV_2022] aims to synthesise geometry and spatial attribute data to characterise the geographic distribution of relevant demographic, environmental, epidemiological and service infrastructure features.
+We are in the early stages of a multi-annual project to develop a service platform model that will represent the processes and operations of a complex primary youth mental health service.
+We also plan to extend and update our prior work reviewing economic evidence relating to youth mental health programs [@RN33] so that it can be integrated with the model.
 
@@
 
-## Standards
+## Framework standards
 We have identified 20 standards that we believe are important for quality implementations of OSHEMs, each described under one of following six principles for making models TIMELY:
@@
 Model code and data also need to be clearly documented, potentially with different versions for technical and non-technical users [@Eddy2012].
-Developers storing data in a Dataverse installation have access to multiple meta-data fields to document both a data collection and its constituent individual files.
+Developers storing data in a Dataverse installation have access to multiple meta-data fields to document both a data collection and its individual constituent files.
 In R, code manuals and websites can be created with the aid of tools such as devtools [@devtools2021], sinew [@sinew2022], roxygen2 [@roxygen2021] and pkgdown [@pkgdown2022].
@@
 ### Licensed Models
-```{r}
-# Adapted fom: https://seankross.com/2016/08/02/How-R-Packages-are-Licensed.html
-sorting_hat <- function(student, houses){
-  choice <- purrr::map_lgl(houses, grepl, x = student)
-  if(!any(choice)){
-    return("Other")
-  } else {
-    return((houses[choice])[1])
-  }
-}
-license_table <- table(utils::available.packages()[,"License"])
-names(license_table) %<>%
-  purrr::map_chr(function(x){
-    sorting_hat(x, c("Apache", "Artistic", "CC", "BSD", "MIT", "GPL"))
-  })  
-license_tbl <- as.data.frame(license_table) %>%
-  dplyr::rename(License = Var1) %>%
-  dplyr::group_by(License) %>%
-  dplyr::summarize(Freq = sum(Freq)) %>%
-  dplyr::ungroup() %>%
-  dplyr::arrange(dplyr::desc(Freq))
-#licenses <- license_tbl$Freq
-gpl_pc_dbl <- round(license_tbl$Freq[license_tbl$License=="GPL"]/sum(license_tbl$Freq)*100,2) 
+```{r echo = F}
+gpl_pc_dbl <- get_license_share("GPL")
 ```
@@
 For code, it may be appropriate to adopt the prevailing open source licensing practice within the programming language being used.
-Applying a previously published algorithm [@kross2016] to analyse the most comprehensive archive of released R packages [@CRAN2022] finds that `r `gpl_pc_dbl`% are distributed under various forms of General Public License (GPL) [@GNUGPL2022], a copyleft license.
+Applying a previously published algorithm [@kross2016] to analyse the most comprehensive archive of released R packages [@CRAN2022] finds that `r gpl_pc_dbl`% are distributed under various forms of General Public License (GPL) [@GNUGPL2022], a copyleft license.
 
@@
 Licenses may or may not specify that model re-users must give appropriate acknowledgement to model authors.
-Citation tools can be distributed with each cite individual code or data items to inform re-users of the desired attribution.
+Citation tools can be distributed with each individual code or data item to inform re-users of the desired attribution.
 In R, including a CITATION file in the `inst` directory of a package will enable users of that package to retrieve citation information by running a command of the format `citation("Package Name")` in the R console [@Salmon2021].
@@
 
-## Modelling tools
+## Framework toolkits
 We have developed a toolkit to help streamline the process of developing OSHEMs that meet the TIMELY standards. The toolkit is comprised of online repositories and software.
@@
 
-- self-documenting model modules [@ready4class2022];
+- documented model modules [@ready4class2022];
 
-- self-documenting functions (including methods), written in a consistent house style [@ready4fun2022];
+- documented functions (including methods), written in a consistent house style [@ready4fun2022];
 
@@
 The six R packages, their primary focus, the TIMELY standards they support and the third party packages they depend on are summarised in Table \@ref(tab:cpkgs).
-When used in conjunction with framework repositories, the six packages currently provide strong support for implementing 17 of the TIMELY standards, weak support for implementing the standards relating to disseminating statistical models (Y1) and user-interface development (Y2) and no support for implementing standard T5 (reporting code coverage).
-Our future development priorities for these packages include adding functionality so that all 20 TIMELY standards are well supported and to then submit production versions of each package for review by and archiving on the Comprehensive R Archive Network (CRAN) [@CRAN2022].
+When used in conjunction with framework repositories, the six packages extending existing R packages to provide strong support for implementing 16 of the TIMELY standards.
+However, the software only weakly supports implementing the standards relating to disseminating statistical models (Y1) and user-interface development (Y2) and does not yet provide any workflow tools to help implement the standards for code coverage (T5) and deprecation conventions (I4).
+Standards not supported or weakly supported by our software can be met with existing developer tools in R and we plan to progressively integrate these third party tools with our own in future releases of our software.
+Another future priority is to submit production versions of each R package for review by and archiving on the Comprehensive R Archive Network (CRAN) [@CRAN2022].
 
@@
 
+\blandscape
+
+```{r, child = child_docs_ls$two, echo=FALSE}
+```
+
+\elandscape
+
 # Application
-
-Worked example
-
-```{r tab.cap='TIMELY Checklist with utility mapping study worked example', tab.id = 'checklisttb', echo = F, results = 'asis'}
-    #  a <- c("TEST1","TEST2")
-    # b <- c("\\cite{ready4show2022}", "hjhjhj")
-    # tmp <- data.frame(a,b)   
-#     kableExtra::kbl(tmp, booktabs = T, escape = F) %>%
-#  kableExtra::kable_styling(
-#    latex_options = c("striped", "hold_position", "repeat_header")
-#    ) %>%  
-#   kableExtra::column_spec(2, width = "50em") %>%
-# kableExtra::landscape()
-
-checklist_df <- data.frame(Standard = c(paste0("T",1:6, c(" (Publicly archived)",
-                                                          " (Documented)",
-                                                          " (Simple Syntax)",
-                                                          " (Literate programming)",
-                                                          " (Code coverage)",
-                                                          " (Reproducibility")),
-                                        paste0("I",1:4, c(" (Version controlled)",
-                                                          " (Semantic versioning)",
-                                                          " (Continuous integration)",
-                                                          " (Deprecation)")),
-                                        paste0("M",1:2, c(" (Decouple code and data)",
-                                                          " (Encapsulation)")),
-                                        paste0("E",1:3, c(" (Code libraries)",
-                                                          " (Inheritance)",
-                                                          " (Test data)")),
-                                        paste0("L",1:3, c(" (Copyleft for code)",
-                                                          " (Liberal, safe data terms)",
-                                                          " (Citation tools)")),
-                                        paste0("Y",1:2, c(" (Statistical model tools)",
-                                                          " (User-interfaces"))),
-                           Assessment = rep("Met so well it hurts",20),
-                           Description = c("5 libraries [@hamilton_matthew_2022_6084467;@hamilton_matthew_2022_6084824;@hamilton_matthew_2022_6116701;@gao_caroline_2022_6130155;@matthew_p_hamilton_2021_5646669], 3 programs [@hamilton_matthew_2022_6129906;@hamilton_matthew_2022_6416330;@hamilton_matthew_p_2022_6321821], 2 sub-routines [@hamilton_matthew_2022_6116385;@matthew_p_hamilton_2022_5976988] and 2 datasets [@DVN/DKDIB0_2021;@DVN/HJXYKQ_2021]",
-# @hamilton_matthew_2022_6084467;@hamilton_matthew_2022_6084824;@hamilton_matthew_2022_6116701;@gao_caroline_2022_6130155;@matthew_p_hamilton_2021_5646669
-# Programs:
-
-# 
-# Sub-routines:
-
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX",
-                                           "XX"))
-
-tb2_nms_chr<-colnames(checklist_df)
-checklist_df <- data.frame(checklist_df[,1],
-                 rep("&nbsp; &nbsp; &nbsp;",nrow(checklist_df)),
-                 checklist_df[,2],
-                 rep("&nbsp; &nbsp; &nbsp;",nrow(checklist_df)),
-                 checklist_df[,3])
-colnames(checklist_df) <- c("","Standard",
-                            "Met?", " ",
-                            tb2_nms_chr[3])
-if(params$X@outp_formats_chr[1] == "Word") {
-  checklist_df %>%
-    ready4show::print_table(output_type_1L_chr = params$X@outp_formats_chr[1],
-                            caption_1L_chr = knitr::opts_current$get("tab.cap"),
-                            mkdn_tbl_ref_1L_chr = paste0("tab:",knitr::opts_current$get("tab.id")),
-                            use_rdocx_1L_lgl = ifelse(params$X@outp_formats_chr[1]=="Word",T,F),
-                            add_to_row_ls = NULL,
-                            sanitize_fn = NULL)
-  }else{
-    checklist_df %>%
-    kableExtra::kbl(format = "markdown",
-                      #escape = F,
-                    caption = knitr::opts_current$get("tab.cap"))
-    # df %>%
-    #   kableExtra::kbl(booktabs = T,
-    #                   caption = knitr::opts_current$get("tab.cap")) %>%
-    #   kableExtra::kable_styling(full_width = F) %>%
-    #   kableExtra::column_spec(9, width = "17em") %>%
-    #   kableExtra::add_header_above(c(" " = 2, "Supports standard" = 6, " "))
-    }
-```
+We used framework toolkits to develop model code and datasets for implementing a utility mapping study [@Hamilton2021.07.07.21260129].
+Table \@ref(tab:checktb) assesses that study against each TIMELY standard, 18 of which the study was able to meet.
+The two current standards where the study falls short are in reporting code coverage and including a user-interface.
+Both these items are current development priorities for our team.

### 2022-05-31 Markdown/Manuscript/Child_RMDs/MS_Tables_2.Rmd
circulated draft

---
title: "Untitled"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
```{r checktb, tab.cap='TIMELY Checklist applied to utility mapping study', tab.id = 'checktb', echo = F, results = 'asis'}
    #  a <- c("TEST1","TEST2")
    # b <- c("\\cite{ready4show2022}", "hjhjhj")
    # tmp <- data.frame(a,b)   
#     kableExtra::kbl(tmp, booktabs = T, escape = F) %>%
#  kableExtra::kable_styling(
#    latex_options = c("striped", "hold_position", "repeat_header")
#    ) %>%  
#   kableExtra::column_spec(2, width = "50em") %>%
# kableExtra::landscape()

checklist_df <- data.frame(Ref = c(paste0("T",1:6),
                                        paste0("I",1:4),
                                        paste0("M",1:2),
                                        paste0("E",1:3),
                                        paste0("L",1:3),
                                        paste0("Y",1:2)),
                           Standard = c("Publicly archived",
                                        "Documented",
                                        "Consistent syntax",
                                        "Literately programmed",
                                        "Code coverage",
                                        "Reproducible",
                                        "Version controlled",
                                        "Semanticly versioned",
                                        "Continuously integrated",
                                        "Deprecation",
                                        "Separate code and data",
                                        "Encapsulated",
                                        "Libraries",
                                        "Inheriting",
                                        "Test data",
                                        "Copyleft code",
                                        "Liberal, safe data terms",
                                        "Citation tools",
                                        "Prediction tools",
                                        "User interface"),
                           Assessment = c("Yes",
                                        "Yes",
                                        "Yes",
                                        "Yes",
                                        "No",
                                        "Yes",
                                        "Yes",
                                        "Yes",
                                        "Yes",
                                        "Yes",
                                        "Yes",
                                        "Yes",
                                        "Yes",
                                        "Yesg",
                                        "Yes",
                                        "Yes",
                                        "Yes",
                                        "Yes",
                                        "Yes",
                                        "No"),
                           Description = c("5 libraries (youthvars, scorz, specific, TTU and youthu) [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155; @matthew_p_hamilton_2021_5646669], <br> 3 programs [@hamilton_matthew_2022_6129906; @hamilton_matthew_2022_6416330; @hamilton_matthew_p_2022_6321821], 2 sub-routines [@hamilton_matthew_2022_6116385; @matthew_p_hamilton_2022_5976988] and 2 datasets [@DVN/DKDIB0_2021; @DVN/HJXYKQ_2021] are permanently archived with unique identifiers.",
                                           "All code libraries have documenting websites with URLs that concatenate 'https://ready4-dev.github.io/' and the package name (e.g. https://ready4-dev.github.io/youthvars). All three Markdown programs are self-documenting, with one [@hamilton_matthew_2022_6129906] including additional instructions in a README file. Only one sub-routine [@matthew_p_hamilton_2022_5976988] is documented with a meaningful README file. All datasets have meaningful metadata descriptors.",
                                           "All libraries, programs and sub-routines use the same house style, which allows most library documentation to be written by algorithms from the ready4fun package [@ready4fun2022]. All libraries except [@matthew_p_hamilton_2021_5646669] use framework syntax, as does one program [@hamilton_matthew_2022_6129906].",
                                           "All programs use literate programming.",
                                           "No current reporting of code coverage.",
                                           "All parts of the study workflow from raw data ingest through to data processing, analysis, reporting and dissemination of study outputs can be reproduced (if granted access to source data) or replicated (using supplied synthetic data) with one program [@hamilton_matthew_2022_6129906].",
                                           "All code is version controlled using Git and GitHub. All source code is available in a GitHub organisation [@ready4gh2022].",
                                           "Semantic version is used in all code. As no code library has yet been submitted to CRAN, only the development version extensions of each version number have been incremented to date.",
                                           "All six libraries use continuous integration (CI). CI results for each library can be viewed at a URL that concatenates 'https://github.com/ready4-dev/', the package name and '/actions' (e.g. https://github.com/ready4-dev/youthvars/actions)",
                                           "Retired code is deprecated using lifecycle package tools (e.g. everything after “## DEPRECATED FNS” in https://github.com/ready4-dev/youthvars/blob/main/data-raw/fns/add.R ). Package vignettes and datasets are also deprecated e.g. https://ready4-dev.github.io/youthvars/articles/Replication_DS.html )",
                                           "All development code is stored on repos in a GitHub organisation [@ready4gh2022] and all archived releases are available in a Zenodo community [@ready4zen2022]. All non-confidential data is stored in repositories within a Harvard Dataverse collection [@ready4dv2022]. ",
                                           "Four [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155] out of five libraries include encapsulated  modules. Examples are the items beginning with Scorz, Specific and Youthvars that are listed in this table: https://ready4-dev.github.io/ready4/articles/V_01.html#current-ready4-framework-modules as well as the S4 classess from the TTU package listed here: https://ready4-dev.github.io/TTU/reference/index.html ",
                                           "All code libraries include functions. The most complete list of functions for each library is available by clicking the 'Manual - Developer (PDF)' link on each package's documentation homepage (see item T2 above).",
                                           "All modules (see item M2) inherit from the Ready4Module class and can be inherited from.",
                                           "Two synthetic datasets and their data dictionaries are publicly available in a data repository [@DVN/HJXYKQ_2021]. One (ymh_clinical_tb.RDS) closely resembles the study dataset and was released so that the main study algorithm [@hamilton_matthew_2022_6129906] can be rerun by those without access to the confidential study dataset. The other (eq5d_ds_dict.RDS) is deliberately different to the source dataset in both variable naming convention and the concepts used for predictors and outcome measures and was created to demonstrate generalised applications of study algorithms.",
                                           "All code libraries, programs and sub-routines use GPL-3 licenses. ",
                                           "Datasets use amended version of template provided by Harvard Dataverse [@sampleterms2022].",
                                           "All libraries have CITATION file in inst directory. All code repositories have a CITATION.cff file. All datasets have citation generating metadata.",
                                           "Model catalogues (PDF files beginning with 'AAA_TTU_MDL_CTG') are available in the study results dataset [@DVN/DKDIB0_2021] and describe the predictive performance of all models under a variety of usage regimes (including when the source dataset in the R model object is replaced with fake data). The youthu library [@matthew_p_hamilton_2021_5646669] includes tools for searching for and applyihg models compatible with different types of input data. An example program to demonstrate this functionality is available in both RMarkdown [@hamilton_matthew_2022_6416330] and rendered PDF formats (the 'Application.pdf' file in the study results dataset [@DVN/DKDIB0_2021]).  ",
                                           "No Shiny app user interface has yet been developed."))

tb2_nms_chr<-colnames(checklist_df)
checklist_df <- data.frame(checklist_df[,1],
                 rep("&nbsp; ",nrow(checklist_df)),
                 checklist_df[,2],
                 rep("&nbsp; &nbsp; &nbsp; &nbsp; ",nrow(checklist_df)),
                 checklist_df[,3],
                 rep("&nbsp; ",nrow(checklist_df)),
                 checklist_df[,4])
colnames(checklist_df) <- c(" "," ","Standard",#
                             "   ","Met?","   ",
                            tb2_nms_chr[4])
if(params$X@outp_formats_chr[1] == "Word") {
  checklist_df %>%
    ready4show::print_table(output_type_1L_chr = params$X@outp_formats_chr[1],
                            caption_1L_chr = knitr::opts_current$get("tab.cap"),
                            mkdn_tbl_ref_1L_chr = paste0("tab:",knitr::opts_current$get("tab.id")),
                            use_rdocx_1L_lgl = ifelse(params$X@outp_formats_chr[1]=="Word",T,F),
                            add_to_row_ls = NULL,
                            sanitize_fn = NULL)
  }else{
    checklist_df %>%
    kableExtra::kbl(format = "markdown",
                    booktabs = T,
                    caption = knitr::opts_current$get("tab.cap")) 
    }
```

### 2022-05-31 Markdown/Manuscript/Child_RMDs/XX_Funs.Rmd
circulated draft

---
title: "XX_Funs"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
```{r echo=FALSE}
library(magrittr)
# Adapted fom: https://seankross.com/2016/08/02/How-R-Packages-are-Licensed.html
sorting_hat <- function(student, houses){
  choice <- purrr::map_lgl(houses, grepl, x = student)
  if(!any(choice)){
    return("Other")
  } else {
    return((houses[choice])[1])
  }
}
get_license_share <- function(license_1L_chr = "GPL"){
  license_table <- table(utils::available.packages()[,"License"])
names(license_table) %<>%
  purrr::map_chr(function(x){
    sorting_hat(x, c("Apache", "Artistic", "CC", "BSD", "MIT", "GPL"))
  })  
license_tbl <- as.data.frame(license_table) %>%
  dplyr::rename(License = Var1) %>%
  dplyr::group_by(License) %>%
  dplyr::summarize(Freq = sum(Freq)) %>%
  dplyr::ungroup() %>%
  dplyr::arrange(dplyr::desc(Freq))
#licenses <- license_tbl$Freq
 share_1L_dbl <- round(license_tbl$Freq[license_tbl$License==license_1L_chr]/sum(license_tbl$Freq)*100,2) 
 return(share_1L_dbl)
}

```

### 2022-05-31 setup.R

@@ -5,10 +5,10 @@ library(bookdown)
 library(rticles)
 X <- Ready4showSynopsis(#background_1L_chr = "Our study is entirely fictional.",
                         coi_1L_chr = "None declared.",
-                        #conclusion_1L_chr = "These fake results are not interesting.",
+                        conclusion_1L_chr = "We have identified a number of standards that we believe are appropriate to implementing quality OSHEMs in youth mental health. Most of these standards are probably relevant to OSHEMs in other health conditions, though some such as the copyleft licensing may be less relevant to modellers using different tools. Our framework toolkits can help support standardised approaches to model development that are important for collaborative and interdependent projects. ",
                         digits_int = 3L,
-                        #ethics_1L_chr = "The study was reviewed and granted approval by Awesome University's Human Research Ethics Committee (1111111.1).",
-                        funding_1L_chr = "The study was funded by Orygen, VicHealth and Victoria University.",
+                        ethics_1L_chr = "Framework development did not involve human subject research and was not ethically reviewed. The worked example of framework application is a previously reported study that was reviewed and granted approval by the University of Melbourne’s Human Research Ethics Committee, and the local Human Ethics and Advisory Group (1645367.1).",
+                        funding_1L_chr = "Framework development was funded by Orygen, VicHealth and Victoria University. The previously reported study used as a worked example was funded by the National Health and Medical Research Council (NHMRC, APP1076940), Orygen and headspace.",
                         #interval_chr = "three months",
                         keywords_chr = c("open source models","health economics","mental disorders"),
                         outp_formats_chr = "PDF",
@@ -37,12 +37,13 @@ X <- renewSlot(X,
                "abstract_args_ls",
                {
                  args_ls <- X@abstract_args_ls
-                 args_ls$abstract_ls <- list(Summary = "There is strong in principle support for open source health economic models, but practical barriers limit their availability. We propose a set of principles and standards for the implementation of open source health economic models that are TIMELY - Transparent, Iterative, Modular, Epitomised and Yielding. We then describe a software framework that we have developed for developing TIMELY models in youth mental health and illustrate this framework with an open source utility mapping project. ",
[…]

### 2022-06-10 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
Sues edits

@@
 <!-- Add aims text here -->
-We have consolidated and refined these and other recommended standards for OSHEMs as part of a framework for developing an open source model of youth mental health.
-In this paper, we describe our motivation for developing the framework, the rationale for each included standard, the software toolkits we have developed to help meet each standard and a worked example of a modelling project developed with the framework.
+We have consolidated and refined these and other recommended guidelines for OSHEMs as part of a framework for developing an open source model of youth mental health.
+In this paper, we describe our motivation for developing the framework, the rationale for each included standard, the software toolkits we have developed to help meet each standard and a worked example of a modelling project developed using this framework.

### 2022-06-10 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
Sues edits

@@
 Better guidance about how to implement OSHEMs is required [@Sampson2019].
-Adherence to explicit standards is as essential requirement for modelling in healthcare [@Erdemir2020], but current best practice recommendations for OSHEMs are scarce and piecemeal.
-Guidelines on health economic model transparency were published ten years ago [@Eddy2012] and made recommendations on documenting models but notably not on the sharing of model code and data.
+Adherence to explicit guidelines is as essential requirement for modelling in healthcare [@Erdemir2020], but current best practice recommendations for OSHEMs are scarce and piecemeal.
+Guidelines on health economic model transparency were published ten years ago [@Eddy2012] and made recommendations on documenting models; however, notably missing were recommendations on the sharing of model code and data.
 More recent and more general modelling guidance [@Erdemir2020] recommends the sharing of code and data through platforms such as GitHub [@github2007] and Zenodo [@Zenodo2013] and the use of version control systems such as Git [@git20XX].
 A coding framework for OSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions [@Alarid2019].
-
-```{r echo=F}
-# ISPOR T & V: 
-# a multiapplication model, transparency, validation,
-# For a multiapplication model, transparency, validation,
-# and reporting are ongoing processes. The multiapplica-
-# tion model is described (transparency)24 and validated,25
-# and the descriptions and validations are continuously
-# updated as science and the model evolve.26 In addition,
-# each instantiation of the model is described, validated,
-# and reported as each application is done.27
-```

### 2022-06-10 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
Sues edits

@@
 Much of this burden is potentially avertable [@RN25], but poorly financed and organised mental health systems are ill-equipped for this challenge[@RN22;@RN23].
-The large and widespread additional mental health burdens recently observed during the COVID pandemic[@20211700] and predicted as a potential future consequence of global heating [@page_howard_2010], highlight the need to improve the resilience and adaptability of these systems.
+The large and widespread additional mental health burdens recently observed during the COVID-19 pandemic[@20211700] and predicted as a potential future consequence of global heating [@page_howard_2010], highlight the need to improve the resilience and adaptability of these systems.
 To help stem growing demand for mental health services, policymakers have also been encouraged to place greater emphasis on tackling the social determinants of mental disorder[@RN11].
@@
 -->
-Open source frameworks have been previously recommended for the development of mental health modelling field [@RN73] but, as with health economics more generally, OSHEMs remain rare.
+Open source frameworks have been recommended for the development of mental health modelling field [@RN73] but, as with health economics more generally, OSHEMs remain rare.
 Currently there is only one mental health related model (in Alcohol Use Disorder [@Basu2018]) that is indexed in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019].
-A Major Depressive Disorder reference model for the United States [@IVIMDD2022] is also being developed as part of the Open Value Initiative [@Jansen2019].
+A Major Depressive Disorder reference model for the United States [@IVIMDD2022] is being developed as part of the Open Value Initiative [@Jansen2019].
 Greater use of open source approaches could help improve the scope, validity and usefulness of mental health economic models.
@@
 Single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020].
-Currently, mental health economic models predominantly address issues relating to the affordability and value for money of individual programs [@RN34] with mental health simulation studies rarely modelling complex systems [@RN73].
+Mental health economic models predominantly address issues relating to the affordability and value for money of individual programs [@RN34] with mental health simulation studies rarely modelling complex dynamic systems [@RN73].
 Systems modelling approaches, that have been recommended for public health economics more generally [@SQUIRES2016588] and for mental health specifically [@Occhipinti2021], could provide greater insight about inter-dependencies between candidate policies and the dynamic nature of the mental health systems planning context.
-Dynamic systems methods might also be the basis for developing reference models [@Afzali2013] of mental health systems that are intended for multiple-applications and re-use by different modelling teams.
+Dynamic systems methods might provide the foundations for developing reference models [@Afzali2013] of mental health systems that are intended for multiple-applications and re-use by different modelling teams.
 However, more complex models may be more prone to error [@Saltelli2019] and models designed for multiple purposes require greater investments in model transparency and validation [@Eddy2012; @Feenstra2022].
@@
 To retain and improve their utility as decision aids, health economic models require updating and refinement as new evidence emerges and decision contexts change [@Jenkins2021].
-There are significant deficits in our understanding of the systems in which mental disorder emerges and is treated [@Fried2020] and longer term project horizons could allow mental health economic models to progressively improve validity as these gaps are addressed.
-Currently, the theoretical basis for understanding complex mental health systems is weak [@RN2111].
-Strikingly, it remains unclear why increased investments in mental health care have yet to discernibly reduce the prevalence and burden of mental disorders[@RN26].
-The literature about how the requirements, characteristics and performance of mental health services are shaped by spatiotemporal context is underdeveloped [@RN42].
-There is insufficient evidence to identify the social determinants of mental disorders most amenable to preventative interventions, and for which population sub-groups such interventions would be most effective [@RN43].
+The significant deficits in our understanding of the systems in which mental disorders emerge and are treated [@Fried2020] suggest that there is ample scope for mental health systems models to progressively improve the validity over time.
+Prospective work could address the weak theoretical underpinnings for understanding complex mental health systems [@RN2111].
+For example, it remains unclear why increased investments in mental health care have yet to discernibly reduce the prevalence and burden of mental disorders[@RN26].
+The literature about how the requirements, characteristics and performance of mental health services are shaped by spatiotemporal context needs to be further developed [@RN42].
+There is also a need for better evidence to identify the social determinants of mental disorders most amenable to preventative interventions, and for which population sub-groups such interventions would be most effective [@RN43].
 
@@
 ## readyforwhatsnext
-We are currently developing readyforwhatsnext, a reference OSHEM that aims to examine multiple potential population level strategies for promoting mental wellbeing and preventing and treating mental disorders in young people.
+We are currently developing **readyforwhatsnext**, a reference OSHEM that aims to examine multiple potential population level strategies for promoting mental wellbeing and preventing and treating mental disorders in young people.
 
 Our approach to model development is to undertake a number of discrete modelling projects of the people, places, platforms and programs that shape the mental health and wellbeing of young people and to progressively link them together by means of a common framework.
-To model people we are developing synthetic representations of populations of interest [@DVN/HJXYKQ_2021] that describe relevant individual characteristics and their relationships, algorithms that map psychological measures to health utility [@Hamilton2021.07.07.21260129] and choice models for predicting the helpseeking behaviour of young people.
-Our in development model of places [@DVN/V3OKZV_2022] aims to synthesise geometry and spatial attribute data to characterise the geographic distribution of relevant demographic, environmental, epidemiological and service infrastructure features.
+To model people we are developing synthetic representations of populations of interest [@DVN/HJXYKQ_2021] that describe relevant individual characteristics and their relationships, algorithms that map psychological measures to health utility [@Hamilton2021.07.07.21260129] and choice models for predicting the helpseeking behaviour of young people [@hamilton_matthew_2022_6627995].
+Our in-development model of places [@DVN/V3OKZV_2022] has the aim of synthesising geometry and spatial attribute data to characterise the geographic distribution of relevant demographic, environmental, epidemiological and service infrastructure features.
 We are in the early stages of a multi-annual project to develop a service platform model that will represent the processes and operations of a complex primary youth mental health service.
-We also plan to extend and update our prior work reviewing economic evidence relating to youth mental health programs [@RN33] so that it can be integrated with the model.
+We also plan to extend and update our prior work reviewing economic evidence relating to youth mental health programs [@RN33] so that it can be integrated with this model.
 
-Our initial work on readyforwhatsnext is focused on Victoria, Australia but the framework we are using to develop it is designed to facilitate extension by ourselves and others to different decision contexts.
+Our initial work on **readyforwhatsnext** is focused on Victoria, Australia but the framework we are using to develop it is designed to facilitate extension by ourselves and others to different decision contexts.
 Progress is reported on a project website [@rfwn2022].
@@
 # Framework
-The framework we have developed to implement readyforwhatsnext specifies standards for OSHEMs and provides tools for meeting those standards.
+The framework we have developed to implement **readyforwhatsnext** specifies standards for OSHEMs and provides tools for meeting those standards.
 
 ## Framework standards
-We have identified 20 standards that we believe are important for quality implementations of OSHEMs, each described under one of following six principles for making models TIMELY:
+We have identified 20 standards that we believe are important for quality implementations of OSHEMs, each described under one of following six principles for making models **TIMELY**:
 
@@
  - **Modular**: models and their components can be combined to extend their scope;
- - **Epitomized**: a model and its components can be used in multiple decision contexts;
+ - **Epitomising**: a model and its components can be used in multiple decision contexts;
  - **Licensed**: a model, its components and derivatives are persistently re-usable by other modellers; and
@@
 OSHEMs developed in R can take advantage of templates provided by devtools [@devtools2021] and pkgdown [@pkgdown2022] to run continuous integration checks on GitHub.
-These tests can include those of units (do individual functions produce expected output?), documentation (does documentation render correctly?, can all example workflows be executed?) and installation (can the software be successfully deployed on multiple types of operating system?).
+These tests can include those of units (do individual functions produce expected output?), documentation (does documentation render correctly?; can all example workflows be executed?) and installation (can the software be successfully deployed on multiple types of operating system?).
 
@@
 
-### Epitomised Models
+### Epitomising Models
 A key challenge to generalising health economic models is that they are typically developed to inform a decision problem with a highly specific jurisdictional context.
@@
 When distributed as libraries (for example, as R packages), functions have the potential to be widely re-used, often in contexts very different than those they were originally developed for.
-A special type of function called a method can only be applied to a pre-defined class of data structure.
+A special type of function, called a method, can only be applied to a pre-defined class of data structure.
 Due to the coding concept of inheritance [@8717448], the more restricted nature of methods can be used to enhance the re-usability of model code in different decision contexts [@ready4oop2022].
@@
 
-The six R packages, their primary focus, the TIMELY standards they support and the third party packages they depend on are summarised in Table \@ref(tab:cpkgs).
+The six R packages, their primary focus, the TIMELY standards they support and the third-party packages they depend on are summarised in Table \@ref(tab:cpkgs).
 When used in conjunction with framework repositories, the six packages extending existing R packages to provide strong support for implementing 16 of the TIMELY standards.
 However, the software only weakly supports implementing the standards relating to disseminating statistical models (Y1) and user-interface development (Y2) and does not yet provide any workflow tools to help implement the standards for code coverage (T5) and deprecation conventions (I4).
-Standards not supported or weakly supported by our software can be met with existing developer tools in R and we plan to progressively integrate these third party tools with our own in future releases of our software.
+Standards not supported or weakly supported by our software can be met with existing developer tools in R and we plan to progressively integrate these third-party tools with our own in future releases of our software.
 Another future priority is to submit production versions of each R package for review by and archiving on the Comprehensive R Archive Network (CRAN) [@CRAN2022].
@@
 # Application
-We used framework toolkits to develop model code and datasets for implementing a utility mapping study [@Hamilton2021.07.07.21260129].
+We used framework toolkits to develop model code and datasets for implementing a utility mapping study that has previously been described [@Hamilton2021.07.07.21260129].
 Table \@ref(tab:checktb) assesses that study against each TIMELY standard, 18 of which the study was able to meet.

### 2022-06-10 Markdown/Manuscript/Child_RMDs/MS_Tables_2.Rmd
Sues edits

@@
 # kableExtra::landscape()
-
 checklist_df <- data.frame(Ref = c(paste0("T",1:6),
@@
                                         "Yes",
-                                        "Yesg",
+                                        "Yes",
                                         "Yes",
@@
                                         "No"),
-                           Description = c("5 libraries (youthvars, scorz, specific, TTU and youthu) [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155; @matthew_p_hamilton_2021_5646669], <br> 3 programs [@hamilton_matthew_2022_6129906; @hamilton_matthew_2022_6416330; @hamilton_matthew_p_2022_6321821], 2 sub-routines [@hamilton_matthew_2022_6116385; @matthew_p_hamilton_2022_5976988] and 2 datasets [@DVN/DKDIB0_2021; @DVN/HJXYKQ_2021] are permanently archived with unique identifiers.",
+                           Description = c("5 libraries (youthvars, scorz, specific, TTU and youthu) [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155; @matthew_p_hamilton_2021_5646669], 3 programs [@hamilton_matthew_2022_6129906; @hamilton_matthew_2022_6416330; @hamilton_matthew_p_2022_6321821], 2 sub-routines [@hamilton_matthew_2022_6116385; @matthew_p_hamilton_2022_5976988] and 2 datasets [@DVN/DKDIB0_2021; @DVN/HJXYKQ_2021] are permanently archived with unique identifiers.",
                                            "All code libraries have documenting websites with URLs that concatenate 'https://ready4-dev.github.io/' and the package name (e.g.
@@
 checklist_df <- data.frame(checklist_df[,1],
-                 rep("&nbsp; ",nrow(checklist_df)),
+                           rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; "),
+                               nrow(checklist_df)),
                            checklist_df[,2],
-                 rep("&nbsp; &nbsp; &nbsp; &nbsp; ",nrow(checklist_df)),
+                           rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp; &nbsp; "),
+                               nrow(checklist_df)),
                            checklist_df[,3],
-                 rep("&nbsp; ",nrow(checklist_df)),
+                           rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; "),
+                               nrow(checklist_df)),
                  checklist_df[,4])
-colnames(checklist_df) <- c(" "," ","Standard",#
-                             "   ","Met?","   ",
+colnames(checklist_df) <- c(ifelse(params$X@outp_formats_chr[1] == "Word","Code"," "),
+                            ifelse(params$X@outp_formats_chr[1] == "Word","YYY"," "),
+                            "Standard",#
+                             ifelse(params$X@outp_formats_chr[1] == "Word","ZZZ","   "),
+                            "Met?",
+                            ifelse(params$X@outp_formats_chr[1] == "Word","AAA","   "),
                             tb2_nms_chr[4])
 if(params$X@outp_formats_chr[1] == "Word") {
-  checklist_df %>%
+  library("flextable")
+  library("ftExtra")
+  checklist_df[,
+               c(1,3,5,7
+                  )] %>%
     ready4show::print_table(output_type_1L_chr = params$X@outp_formats_chr[1],
@@
                             add_to_row_ls = NULL,
-                            sanitize_fn = NULL)
+                            sanitize_fn = NULL) %>%
+  ftExtra::colformat_md()
   }else{

### 2022-06-10 Markdown/Manuscript/Parent_PDF/Parent_PDF.Rmd
Sues edits

@@
 abstract: "There is strong in principle support for open source health economic models, but practical barriers limit their availability.
-We propose a set of principles and standards for the implementation of open source health economic models that are TIMELY - Transparent, Iterative, Modular, Epitomised and Yielding.
+We propose a set of principles and standards for the implementation of open source health economic models that are TIMELY - Transparent, Iterative, Modular, Epitomising and Yielding.
 We then describe a software framework that we have developed for developing TIMELY models in youth mental health and illustrate this framework with an open source utility mapping project."

### 2022-06-10 setup.R

@@ -5,7 +5,7 @@ library(bookdown)
 library(rticles)
 X <- Ready4showSynopsis(#background_1L_chr = "Our study is entirely fictional.",
                         coi_1L_chr = "None declared.",
-                        conclusion_1L_chr = "We have identified a number of standards that we believe are appropriate to implementing quality OSHEMs in youth mental health. Most of these standards are probably relevant to OSHEMs in other health conditions, though some such as the copyleft licensing may be less relevant to modellers using different tools. Our framework toolkits can help support standardised approaches to model development that are important for collaborative and interdependent projects. ",
+                        conclusion_1L_chr = "We have identified a number of standards that we believe are appropriate to implementing quality OSHEMs in youth mental health. Most of these standards are probably relevant to OSHEMs in other health conditions, though some such as the copyleft licensing may be less relevant to modellers using different tools. Our framework toolkits can help support standardised approaches to dynamic systems model development that are important for collaborative and interdependent projects. ",
                         digits_int = 3L,
                         ethics_1L_chr = "Framework development did not involve human subject research and was not ethically reviewed. The worked example of framework application is a previously reported study that was reviewed and granted approval by the University of Melbourne’s Human Research Ethics Committee, and the local Human Ethics and Advisory Group (1645367.1).",
                         funding_1L_chr = "Framework development was funded by Orygen, VicHealth and Victoria University. The previously reported study used as a worked example was funded by the National Health and Medical Research Council (NHMRC, APP1076940), Orygen and headspace.",
@@ -37,10 +37,15 @@ X <- renewSlot(X,
                "abstract_args_ls",
                {
                  args_ls <- X@abstract_args_ls
[…]

### 2022-07-20 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
Dave and Kate's edits

@@
 To help address these issues, there is growing support for greater use of open source health economic models (OSHEMs) that grant liberal permissions to access and re-use model source code and data [@Pouwels2022].
-However, to date actual implementations of OSHEMs are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022].
+However, to date, actual implementations of OSHEMs are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022].
 Barriers to adoption include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations [@Pouwels2022; @Wu2019].
@@
 Better guidance about how to implement OSHEMs is required [@Sampson2019].
-Adherence to explicit guidelines is as essential requirement for modelling in healthcare [@Erdemir2020], but current best practice recommendations for OSHEMs are scarce and piecemeal.
+Adherence to explicit guidelines is an essential requirement for modelling in healthcare [@Erdemir2020], but current best practice recommendations for OSHEMs are scarce and piecemeal.
 Guidelines on health economic model transparency were published ten years ago [@Eddy2012] and made recommendations on documenting models; however, notably missing were recommendations on the sharing of model code and data.
-More recent and more general modelling guidance [@Erdemir2020] recommends the sharing of code and data through platforms such as GitHub [@github2007] and Zenodo [@Zenodo2013] and the use of version control systems such as Git [@git20XX].
+More recent and more general modelling guidance [@Erdemir2020] recommends the sharing of code and data through digital repository services such as GitHub [@github2007] and Zenodo [@Zenodo2013] and the use of version control systems such as Git [@git20XX].
 A coding framework for OSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions [@Alarid2019].

### 2022-07-20 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
Dave and Kate's edits

@@
 Much of this burden is potentially avertable [@RN25], but poorly financed and organised mental health systems are ill-equipped for this challenge[@RN22;@RN23].
-The large and widespread additional mental health burdens recently observed during the COVID-19 pandemic[@20211700] and predicted as a potential future consequence of global heating [@page_howard_2010], highlight the need to improve the resilience and adaptability of these systems.
-To help stem growing demand for mental health services, policymakers have also been encouraged to place greater emphasis on tackling the social determinants of mental disorder[@RN11].
+The large and widespread additional mental health burdens recently observed during the COVID-19 pandemic[@20211700] and predicted as a potential future consequence of climate change [@page_howard_2010], highlight the need to improve the resilience and adaptability of these systems.
+To help stem growing demand for mental health services, policymakers have also been encouraged to place greater emphasis on tackling the social determinants of mental disorders [@RN11].
 
@@
 -->
-Open source frameworks have been recommended for the development of mental health modelling field [@RN73] but, as with health economics more generally, OSHEMs remain rare.
+Open source frameworks have been recommended to develop the mental health modelling field [@RN73] but, as with health economics more generally, OSHEMs remain rare.
 Currently there is only one mental health related model (in Alcohol Use Disorder [@Basu2018]) that is indexed in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019].
-A Major Depressive Disorder reference model for the United States [@IVIMDD2022] is being developed as part of the Open Value Initiative [@Jansen2019].
-Greater use of open source approaches could help improve the scope, validity and usefulness of mental health economic models.
+An open source Major Depressive Disorder reference model for the United States [@IVIMDD2022] is also in development <!-- as part of the Open Value Initiative [@Jansen2019].
+-->Greater use of open source approaches could help improve the scope, validity and usefulness of mental health economic models.
 
-Major mental health reform programs, such as those currently being implemented in Victoria, Australia [@VicRC2021], can involve the identification, prioritisation, sequencing, targeting and monitoring of multiple interdependent initiatives.
+Major mental health reform programs, <!-- such as those currently being implemented in Victoria, Australia [@VicRC2021],  -->can involve the identification, prioritisation, sequencing, targeting and monitoring of multiple interdependent initiatives.
 Single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020].
-Mental health economic models predominantly address issues relating to the affordability and value for money of individual programs [@RN34] with mental health simulation studies rarely modelling complex dynamic systems [@RN73].
+Mental health simulation studies rarely model complex dynamic systems [@RN73] with economic studies predominantly examining the affordability and value for money of individual mental health programs [@RN34].
 Systems modelling approaches, that have been recommended for public health economics more generally [@SQUIRES2016588] and for mental health specifically [@Occhipinti2021], could provide greater insight about inter-dependencies between candidate policies and the dynamic nature of the mental health systems planning context.
@@
 To retain and improve their utility as decision aids, health economic models require updating and refinement as new evidence emerges and decision contexts change [@Jenkins2021].
-The significant deficits in our understanding of the systems in which mental disorders emerge and are treated [@Fried2020] suggest that there is ample scope for mental health systems models to progressively improve the validity over time.
+The significant deficits in our understanding of the systems in which mental disorders emerge and are treated [@Fried2020] suggest that there is ample scope for mental health systems models to progressively improve their validity over time.
 Prospective work could address the weak theoretical underpinnings for understanding complex mental health systems [@RN2111].
 For example, it remains unclear why increased investments in mental health care have yet to discernibly reduce the prevalence and burden of mental disorders[@RN26].
-The literature about how the requirements, characteristics and performance of mental health services are shaped by spatiotemporal context needs to be further developed [@RN42].
+The  literature, and evidence base, regarding how the requirements, characteristics and performance of mental health services are shaped by spatiotemporal context needs to be further developed [@RN42].
 There is also a need for better evidence to identify the social determinants of mental disorders most amenable to preventative interventions, and for which population sub-groups such interventions would be most effective [@RN43].
@@
 Developing networks of modellers working on common health conditions has been recommended as a strategy for improving model validity [@Sampson2019] and some of us are part of a nascent initiate of this type in mental health [@nmhsmn2022].
-Furthermore, collaborations across multiple modelling teams that include the ability to re-use and extend each others work can make complex modelling projects more tractable [@Arnold2010].
-<!-- Add ref to NMHSMN in Australia --> Similarly, developing partnerships between modellers and decision-makers across the life-cycle of a modelling project can help ensure models are appropriately conceptualised and implemented and improve their practical utility as decision aids [@Zabell2021; @SQUIRES2016588].
+Furthermore, collaborations across multiple modelling teams that include the ability to re-use and extend one another's work can make complex modelling projects more tractable [@Arnold2010].
+<!-- Add ref to NMHSMN in Australia --> Similarly, developing partnerships between modellers and decision-makers across the life-cycle of a modelling project can help ensure models are appropriately conceptualised, implemented and have practical utility as decision aids [@Zabell2021; @SQUIRES2016588].
 
@@
 
-Our initial work on **readyforwhatsnext** is focused on Victoria, Australia but the framework we are using to develop it is designed to facilitate extension by ourselves and others to different decision contexts.
+Our initial work on **readyforwhatsnext** is focused on Victoria, Australia but the framework we are using to develop it is designed to facilitate extension by ourselves and others to different jurisdictional decision contexts.
 Progress is reported on a project website [@rfwn2022].
@@
 ## Framework standards
-We have identified 20 standards that we believe are important for quality implementations of OSHEMs, each described under one of following six principles for making models **TIMELY**:
+Based on existing open science guidance and our own experience, we have identified 20 standards that are important for quality implementations of OSHEMs, each described under one of following six principles for making models **TIMELY**:
 
@@
 Consistent use of meaningful naming conventions when authoring code is recommended [@Wilson_2017; @Alarid2019].
-Code can be made easier to follow by using the practices of abstraction [@8717448], where only simple, high level commands are routinely exposed to reviewers, and polymorphsim [@7181447], where the same command (e.g.
+Code can be made easier to follow by using the practices of abstraction [@8717448], where only simple, high level commands are routinely exposed to reviewers, and polymorphism [@7181447], where the same command (e.g.
 "simulate") can be reused to implement different algorithms of the same type.
-Programs to implement model analyses can be made comprehensible to even non-technical users though the use of literate programming techniques that use tools like RMarkdown [@xie2018r] to render documents that integrate computer code with plain English descriptions.
+Programs to implement model analyses can be made comprehensible to even non-technical users through the use of literate programming techniques that use tools like RMarkdown [@xie2018r] to render documents that integrate computer code with plain English descriptions.
 
@@
 Adopting semantic versioning [@semver20xx] conventions can be an efficient way to provide users of model code and data with information about the potential importance of an update.
-For R code, the usethis [@usethis2021] package can be used to partially automate version number increments using the convention Major.Minor.Patch.Development.
+For R code, the usethis [@usethis2021] package can be used to partially automate version number increments using the convention Major.Minor.Patch.Development (e.g.
+ExampleSoftware v1.1.1.1).
 Datasets stored on the Harvard Dataverse use the simpler Major.Minor convention.
+
 Continuous integration [@CI2017] tools can help verify that each code update passes multiple quality tests.
@@
 Modular health economic models link multiple self-contained components that can be independently reused and extended by other projects [@Trauer2017;@Urach2013].
-
 Many types of mental health data are highly sensitive with strict confidentiality requirements.
@@
 Due to the coding concept of inheritance [@8717448], the more restricted nature of methods can be used to enhance the re-usability of model code in different decision contexts [@ready4oop2022].
-For example, when generalising a model developed for the Australian context to a UK context, one could create a class that initially inherits all of the methods defined for the Australian model and then write new or replacement methods as needed for the UK model.
-
-Whatever type of functions are written for a modelling project, it is good practice to make available test or toy data to demonstrate their use [@Wilson_2017].
+For example, when generalising a model developed for the Australian context to a UK context, one could create a class that initially inherits all of the methods defined for the Australian model and then write new or replacement methods as needed for the UK model.Whatever type of functions are written for a modelling project, it is good practice to make available test or toy data to demonstrate their use [@Wilson_2017].
 
@@
 Some guidance strongly recommends the use of permissive licensing [@Wilson_2017] that provides users with great flexibility as to the purposes (including commercial) for which the content could be re-used.
-An alternative approach is to use copyleft licenses [@copyleft2022] that can require content users to distribute any derivative works they create under similar open source arrangements.
+An alternative approach is to use copyleft licenses [@copyleft2022] that can require content users to distribute any derivative works they create under similar open source arrangements.The most suitable approach may differ for code and data.
 
@@
 In the R language, model objects by default typically contain a copy of the source dataset.
-Such dataset copies must therefore be replaced (for example, with fake data) and the amended artefact's predictive performance then retested before any public release.
+Such dataset copies must therefore be replaced (for example, with synthetic data) and the amended artefact's predictive performance then retested before any public release.
 
@@
 The six R packages, their primary focus, the TIMELY standards they support and the third-party packages they depend on are summarised in Table \@ref(tab:cpkgs).
-When used in conjunction with framework repositories, the six packages extending existing R packages to provide strong support for implementing 16 of the TIMELY standards.
+When used in conjunction with framework repositories, the six packages extend existing R packages provide strong support for implementing 16 of the TIMELY standards.
 However, the software only weakly supports implementing the standards relating to disseminating statistical models (Y1) and user-interface development (Y2) and does not yet provide any workflow tools to help implement the standards for code coverage (T5) and deprecation conventions (I4).

### 2022-07-21 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
first attempt at restructure - wip

--- 2022-05-23 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
@@
 <!-- Add aims text here -->
-We have consolidated and refined these and other recommended standards for OSHEMs as part of a framework for developing an open source model of youth mental health.
-In this paper, we describe our motivation for developing the framework, the rationale for each included standard, the software toolkits we have developed to help meet each standard and a worked example of a modelling project developed with the framework.
+We are currently developing **readyforwhatsnext**, a reference OSHEM that aims to examine multiple potential population level strategies for promoting mental wellbeing and preventing and treating mental disorders in young people.
+<!-- We have consolidated and refined these and other recommended guidelines for OSHEMs as part of a framework for developing an open source model of youth mental health.
+-->In this paper, we describe:
+
+- guidelines for quality implementation of OSHEMS;
+- a framework for standardised and reproducible approaches to apply these guidelines to each component of the  **readyforwhatsnext** model; 
+- a worked example of the first **readyforwhatsnext** model component developed using this framework.

### 2022-07-21 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
first attempt at restructure - wip

@@
 <!-- greater use of these types of models may require adaptation on the part of funders, modellers and decision-makers. T -->
+
+# Motivation
+
+## Why develop OSHEMs in mental health
+
+Mental disorders impose high health, social and economic burdens worldwide [@RN8;@GBD2019].
+Much of this burden is potentially avertable [@RN25], but poorly financed and organised mental health systems are ill-equipped for this challenge[@RN22;@RN23].
+The large and widespread additional mental health burdens recently observed during the COVID-19 pandemic[@20211700] and predicted as a potential future consequence of climate change [@page_howard_2010], highlight the need to improve the resilience and adaptability of these systems.
+To help stem growing demand for mental health services, policymakers have also been encouraged to place greater emphasis on tackling the social determinants of mental disorders [@RN11].
+
+Major mental health reform programs, <!-- such as those currently being implemented in Victoria, Australia [@VicRC2021],  -->can involve the identification, prioritisation, sequencing, targeting and monitoring of multiple interdependent initiatives.
+
+The significant deficits in our understanding of the systems in which mental disorders emerge and are treated [@Fried2020] suggest that there is ample scope for mental health systems models to progressively improve their validity over time.
+Prospective work could address the weak theoretical underpinnings for understanding complex mental health systems [@RN2111].
+For example, it remains unclear why increased investments in mental health care have yet to discernibly reduce the prevalence and burden of mental disorders[@RN26].
+The  literature, and evidence base, regarding how the requirements, characteristics and performance of mental health services are shaped by spatiotemporal context needs to be further developed [@RN42].
+There is also a need for better evidence to identify the social determinants of mental disorders most amenable to preventative interventions, and for which population sub-groups such interventions would be most effective [@RN43].
+
+The development, validation and updating of more complex mental health economic models implemented over longer time frames may be too onerous a burden for a single modelling team.
+
+Developing networks of modellers working on common health conditions has been recommended as a strategy for improving model validity [@Sampson2019] and some of us are part of a nascent initiate of this type in mental health [@nmhsmn2022].
+<!-- Add ref to NMHSMN in Australia --> Similarly, developing partnerships between modellers and decision-makers across the life-cycle of a modelling project can help ensure models are appropriately conceptualised, implemented and have practical utility as decision aids [@Zabell2021; @SQUIRES2016588].

### 2022-07-21 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
first attempt at restructure - wip

--- 2022-06-10 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
@@
 ---
-title: "MA_Results"
-author: "Author"
-date: "`r Sys.Date()`"
+title: "MS_Imp_Guidelines"
 output: html_document
+date: '2022-07-21'
 ---
-
-```{r child="../Child_RMDs/XX_Funs.Rmd", echo=FALSE}
-```
-```{r child="../Child_RMDs/MS_Tables.Rmd", echo=FALSE}
-```
-```{r child="../Child_RMDs/MS_Figures.Rmd", echo=FALSE}
-```
-<!-- Add child RMDs for results content -->
-
-# Motivation
-
-## Why develop OSHEMs in mental health
-
-Mental disorders impose high health, social and economic burdens worldwide [@RN8;@GBD2019].
-Much of this burden is potentially avertable [@RN25], but poorly financed and organised mental health systems are ill-equipped for this challenge[@RN22;@RN23].
-The large and widespread additional mental health burdens recently observed during the COVID-19 pandemic[@20211700] and predicted as a potential future consequence of global heating [@page_howard_2010], highlight the need to improve the resilience and adaptability of these systems.
-To help stem growing demand for mental health services, policymakers have also been encouraged to place greater emphasis on tackling the social determinants of mental disorder[@RN11].
-
-<!-- Computational modelling could play an important role in developing policies to improve population mental health but this may require significant changes in the way mental health modelling projects are funded, conceptualised and implemented.
--->
-Open source frameworks have been recommended for the development of mental health modelling field [@RN73] but, as with health economics more generally, OSHEMs remain rare.
-Currently there is only one mental health related model (in Alcohol Use Disorder [@Basu2018]) that is indexed in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019].
-A Major Depressive Disorder reference model for the United States [@IVIMDD2022] is being developed as part of the Open Value Initiative [@Jansen2019].
-Greater use of open source approaches could help improve the scope, validity and usefulness of mental health economic models.
-
-Major mental health reform programs, such as those currently being implemented in Victoria, Australia [@VicRC2021], can involve the identification, prioritisation, sequencing, targeting and monitoring of multiple interdependent initiatives.
-Single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020].
-Mental health economic models predominantly address issues relating to the affordability and value for money of individual programs [@RN34] with mental health simulation studies rarely modelling complex dynamic systems [@RN73].
-Systems modelling approaches, that have been recommended for public health economics more generally [@SQUIRES2016588] and for mental health specifically [@Occhipinti2021], could provide greater insight about inter-dependencies between candidate policies and the dynamic nature of the mental health systems planning context.
-Dynamic systems methods might provide the foundations for developing reference models [@Afzali2013] of mental health systems that are intended for multiple-applications and re-use by different modelling teams.
-However, more complex models may be more prone to error [@Saltelli2019] and models designed for multiple purposes require greater investments in model transparency and validation [@Eddy2012; @Feenstra2022].
-
-To retain and improve their utility as decision aids, health economic models require updating and refinement as new evidence emerges and decision contexts change [@Jenkins2021].
-The significant deficits in our understanding of the systems in which mental disorders emerge and are treated [@Fried2020] suggest that there is ample scope for mental health systems models to progressively improve the validity over time.
-Prospective work could address the weak theoretical underpinnings for understanding complex mental health systems [@RN2111].
-For example, it remains unclear why increased investments in mental health care have yet to discernibly reduce the prevalence and burden of mental disorders[@RN26].
-The literature about how the requirements, characteristics and performance of mental health services are shaped by spatiotemporal context needs to be further developed [@RN42].
-There is also a need for better evidence to identify the social determinants of mental disorders most amenable to preventative interventions, and for which population sub-groups such interventions would be most effective [@RN43].
-
-The development, validation and updating of more complex mental health economic models implemented over longer time frames may be too onerous a burden for a single modelling team.
-Developing networks of modellers working on common health conditions has been recommended as a strategy for improving model validity [@Sampson2019] and some of us are part of a nascent initiate of this type in mental health [@nmhsmn2022].
-Furthermore, collaborations across multiple modelling teams that include the ability to re-use and extend each others work can make complex modelling projects more tractable [@Arnold2010].
-<!-- Add ref to NMHSMN in Australia --> Similarly, developing partnerships between modellers and decision-makers across the life-cycle of a modelling project can help ensure models are appropriately conceptualised and implemented and improve their practical utility as decision aids [@Zabell2021; @SQUIRES2016588].
-
-## readyforwhatsnext
-We are currently developing **readyforwhatsnext**, a reference OSHEM that aims to examine multiple potential population level strategies for promoting mental wellbeing and preventing and treating mental disorders in young people.
-
-Our approach to model development is to undertake a number of discrete modelling projects of the people, places, platforms and programs that shape the mental health and wellbeing of young people and to progressively link them together by means of a common framework.
-To model people we are developing synthetic representations of populations of interest [@DVN/HJXYKQ_2021] that describe relevant individual characteristics and their relationships, algorithms that map psychological measures to health utility [@Hamilton2021.07.07.21260129] and choice models for predicting the helpseeking behaviour of young people [@hamilton_matthew_2022_6627995].
-Our in-development model of places [@DVN/V3OKZV_2022] has the aim of synthesising geometry and spatial attribute data to characterise the geographic distribution of relevant demographic, environmental, epidemiological and service infrastructure features.
-We are in the early stages of a multi-annual project to develop a service platform model that will represent the processes and operations of a complex primary youth mental health service.
-We also plan to extend and update our prior work reviewing economic evidence relating to youth mental health programs [@RN33] so that it can be integrated with this model.
-
-Our initial work on **readyforwhatsnext** is focused on Victoria, Australia but the framework we are using to develop it is designed to facilitate extension by ourselves and others to different decision contexts.
-Progress is reported on a project website [@rfwn2022].
-
-# Framework
-The framework we have developed to implement **readyforwhatsnext** specifies standards for OSHEMs and provides tools for meeting those standards.
-
-## Framework standards
-We have identified 20 standards that we believe are important for quality implementations of OSHEMs, each described under one of following six principles for making models **TIMELY**:
-
- - **Transparent**: people can easily see how a model has been implemented and tested;
- - **Iterative**: a model is routinely updated to maintain and improve validity;
- - **Modular**: models and their components can be combined to extend their scope;
- - **Epitomising**: a model and its components can be used in multiple decision contexts;
- - **Licensed**: a model, its components and derivatives are persistently re-usable by other modellers; and
- - **Yielding**: a model can be simply, flexibly and reliably used to inform decision-making.
-
-### Transparent Models
-A range of tools and practices are available to help make model code and data accessible, comprehensible and citable.
-The most efficient way to widely disseminate code and data may be to use existing open science infrastructure [@Erdemir2020].
-Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each unique item.
-These repositories are a preferable solution for sharing citable code and data than transitory repositories such as corporate websites or GitHub where items can be deleted or relocated at any time [@sseditors2022].
-Zenodo includes tools that automate integration with GitHub, which makes it easy for developers to maintain parallel code repositories - one for disseminating the most up to date development code and the other for archiving citable code releases.
-
-Model code and data also need to be clearly documented, potentially with different versions for technical and non-technical users [@Eddy2012].
-Developers storing data in a Dataverse installation have access to multiple meta-data fields to document both a data collection and its individual constituent files.
-In R, code manuals and websites can be created with the aid of tools such as devtools [@devtools2021], sinew [@sinew2022], roxygen2 [@roxygen2021] and pkgdown [@pkgdown2022].
-
-Consistent use of meaningful naming conventions when authoring code is recommended [@Wilson_2017; @Alarid2019].
-Code can be made easier to follow by using the practices of abstraction [@8717448], where only simple, high level commands are routinely exposed to reviewers, and polymorphsim [@7181447], where the same command (e.g.
-"simulate") can be reused to implement different algorithms of the same type.
-Programs to implement model analyses can be made comprehensible to even non-technical users though the use of literate programming techniques that use tools like RMarkdown [@xie2018r] to render documents that integrate computer code with plain English descriptions.
-
-An essential component of quality assuring health economic models is verification - ensuring that calculations are correct and consistent with model specifications [@techver2019].
-One useful concept for informing model users about the extensiveness of verification checks is code coverage [@ERICWONG2010188] - the proportion of model code that has been explicitly tested.
-In R, the testthat [@testthat2011] and covr [@covr2020] tools can be used in conjunction with GitHub to define tests and report coverage metrics.
-
-Finally, transcription errors - mistakes introduced when transferring data between sources, models and reports - are very common in health economic models [@Radeva2020].
-The risk of these errors might be lower if there was full transparency across all steps in a study workflow.
-Scientific computing tools now make it relatively straightforward to author programs that reproducibly execute all steps in data ingest, processing and reporting [@Wilson_2017].
-
-Standards:
-
-- **T1: Uniquely identified copies of model code and data are permanently archived in open online repositories**
-<!-- T2 MISSING - Merged With T1 -->
-
-- **T2: Model code and data are documented **<!-- Was T3 -->
-
-- **T3: Model code uses a simple and consistent syntax**<!-- Was T4 -->
-
-- **T4: Model analyses and reporting are implemented using literate programming** <!-- Was T5 -->
-
-- **T5: Code coverage is reported** <!-- New, replaces version now moved to T4 -->
-
-- **T6: All parts of a study analysis and reporting workflow can be reproduced and/or replicated** <!-- Was T7, Replaces Deleted T6 -->
-
-### Iterative Models
-To avoid OSHEMs going stale - losing validity and usefulness with time - they should be routinely updated.
-A number of tools and approaches can make the process of implementing and curating changes to model code and data more coherent and efficient.
-Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent access to all published versions of a dataset, each uniquely identifiable.
-For code, use of version control tools like Git [@git20XX] can ensure that the entire development history of a project is organised so that each version is distinguishable and retrievable by developers.
-The online platform GitHub [@github2007] can make this version history accessible to anyone.
-
-Adopting semantic versioning [@semver20xx] conventions can be an efficient way to provide users of model code and data with information about the potential importance of an update.
-For R code, the usethis [@usethis2021] package can be used to partially automate version number increments using the convention Major.Minor.Patch.Development.
-Datasets stored on the Harvard Dataverse use the simpler Major.Minor convention.
-Continuous integration [@CI2017] tools can help verify that each code update passes multiple quality tests.
-OSHEMs developed in R can take advantage of templates provided by devtools [@devtools2021] and pkgdown [@pkgdown2022] to run continuous integration checks on GitHub.
-These tests can include those of units (do individual functions produce expected output?), documentation (does documentation render correctly?; can all example workflows be executed?) and installation (can the software be successfully deployed on multiple types of operating system?).
-
-Finally, using deprecation conventions that take an informative and staged approach to retiring old code and data reduces the risk that model revisions have unintended consequences on third party users.
-The package lifeycle [@lifecycle2021] provides tools for R developers to consistently deprecate their code.
-
-Standards:
-
-- **I1: Model code is version controlled** <!-- Was I2 -->
-
-- **I2: Model code and data use semantic versioning** <!-- Was I1 -->
-
-- **I3: Continuous integration is used to verify model code updates**
-
-- **I4: Deprecation conventions are used to retire model code and data**
-
-### Modular Models
-Modular health economic models link multiple self-contained components that can be independently reused and extended by other projects [@Trauer2017;@Urach2013].
-
-Many types of mental health data are highly sensitive with strict confidentiality requirements.
-For this reason, not all data included in some mental health models can be made widely available for others to re-use.
-A modular approach that ensures that model code and data are decoupled (stored in different files) can help model developers to restrict access to confidential model data, while providing open access to all other model components.
-
-An important consideration when combining model components (or modules) is to ensure that interactions between two modules do not compromise the validity of either.
-Using the coding practice of encapsulation [@8717448] can help ensure that model modules can be safely combined [@ready4oop2022].
-
-Standards:
-
-- **M1: Model code and data are stored and managed separately** <!-- Modified (lost ref to licensed and cited) -->
-
-- **M2: Model code defines encapsulating data structures** <!--Replacement - Old version now merged with E1 -->
-
-### Epitomising Models
-A key challenge to generalising health economic models is that they are typically developed to inform a decision problem with a highly specific jurisdictional context.
-However, a number of choices about how these models are implemented can significantly increase the re-usability of model code in other contexts.
-
-Writing code as collections of functions (short, self-contained and reusable algorithms that each perform a discrete task) is recommended as good practice for scientific computing [@Wilson_2017].
-When distributed as libraries (for example, as R packages), functions have the potential to be widely re-used, often in contexts very different than those they were originally developed for.
-A special type of function, called a method, can only be applied to a pre-defined class of data structure.
-Due to the coding concept of inheritance [@8717448], the more restricted nature of methods can be used to enhance the re-usability of model code in different decision contexts [@ready4oop2022].
-For example, when generalising a model developed for the Australian context to a UK context, one could create a class that initially inherits all of the methods defined for the Australian model and then write new or replacement methods as needed for the UK model.
-
-Whatever type of functions are written for a modelling project, it is good practice to make available test or toy data to demonstrate their use [@Wilson_2017].
-
-Standards:
-
-- **E1: Model code is distributed as libraries of classes and functions**  <!-- Modified (lost ref to OOP and merged with M2) -->
-
-- **E2: Model code defines inheriting data-structures**
-
-- **E3: Test data is available to demonstrate generalised applications of model code**
-
-### Licensed Models
-```{r echo = F}
-gpl_pc_dbl <- get_license_share("GPL")
-```
-
-To make model code and data widely re-usable by others, it is important to provide users with appropriate and explicit permissions.
-In the context of open source models, there are two broad categories of licensing options.
-Some guidance strongly recommends the use of permissive licensing [@Wilson_2017] that provides users with great flexibility as to the purposes (including commercial) for which the content could be re-used.
-An alternative approach is to use copyleft licenses [@copyleft2022] that can require content users to distribute any derivative works they create under similar open source arrangements.
-
-For code, it may be appropriate to adopt the prevailing open source licensing practice within the programming language being used.
-Applying a previously published algorithm [@kross2016] to analyse the most comprehensive archive of released R packages [@CRAN2022] finds that `r gpl_pc_dbl`% are distributed under various forms of General Public License (GPL) [@GNUGPL2022], a copyleft license.
-
-For data, it may not be sufficient to simply choose between a permissive license like the Public Domain Dedication (CC0) [@cc02022] or a copyleft option such as the Attribution-Share Alike (CC-BY-SA) [@bysa2022].
-Responsible custodianship of some de-identified mental health data may involve using or adapting template terms of use [@sampleterms2022] which have a number of ethical clauses (for example, prohibiting efforts to re-identify research participants).
-
-Licenses may or may not specify that model re-users must give appropriate acknowledgement to model authors.
-Citation tools can be distributed with each individual code or data item to inform re-users of the desired attribution.
-In R, including a CITATION file in the `inst` directory of a package will enable users of that package to retrieve citation information by running a command of the format `citation("Package Name")` in the R console [@Salmon2021].
-More generally, including a CITATION.cff file at the top level of your code repository will enable GitHub and Zenodo repositories hosting that item to include the relevant information in their citation tools [@Druskat_Citation_File_Format_2021].
-Datasets hosted on Dataverse installations have metadata fields that, once completed by authors, generate citation files for dataset viewers.
-
-Standards:
-
-- **L1: Model code is made available for re-use under copyleft licenses**
-
-- **L2: Non-confidential model data is available for liberal re-use (subject to additional terms for de-identified human data)**
-
-- **L3: Model code and data are distributed with tools to support appropriate citation** <!-- New -->
-
-### Yielding Models
-OSHEMs can be time and skills intensive for modellers to develop - but they should be easy for others to use.
-
-Statistical models are a common output of health economic evaluations, but they are often not reported in a format that enables others to confidently and reliably re-use them [@Kearns2013].
-Open source approaches can help address this by disseminating code artefacts that enable easy and appropriate use of a statistical model to make predictions with new data.
-However, great care must be exercised when doing so if models are derived from data on human subjects.
-In the R language, model objects by default typically contain a copy of the source dataset.
-Such dataset copies must therefore be replaced (for example, with fake data) and the amended artefact's predictive performance then retested before any public release.
-
-Another way to make OSHEMs easier to use is to develop simple user-interfaces for non-technical users.
-In R, such user-interfaces are typically developed with the Shiny package, for which a tutorial aimed at health economists is available [@SmithR2020].
-
-Standards:
-
-- **Y1: Statistical models are distributed with validated tools to support their safe and appropriate re-use** <!-- New, Replaces Old Y1 (now Y2) -->
-- **Y2: Simple user-interfaces allow non-technical users to configure and run models ** <!-- Was Y1 -->
-
-## Framework toolkits
-We have developed a toolkit to help streamline the process of developing OSHEMs that meet the TIMELY standards. The toolkit is comprised of online repositories and software.
-
-### Framework repositories <!-- Existing ref -->
-We created a GitHub organisation where all framework software source code is stored, documented, version controlled and continuously integrated [@ready4gh2022].
-To store citable archived copies of release copies of our software, we created a Zenodo community [@ready4zen2022].
-Finally, to manage datasets for use in models developed with the framework, we created a dedicated collection within the Harvard Dataverse  [@ready4dv2022].
-
-### Framework software <!-- Novel ref -->
-As a foundation for implementing the framework, we authored a development version R package that defines a novel syntax and a template class for model modules [@ready42022].
-To enable the syntax and module template be applied to modelling projects, we then created five additional development version R packages that provide tools for authoring:
-
-- documented model modules [@ready4class2022];
-
-- documented functions (including methods), written in a consistent house style [@ready4fun2022];
-
-- citable, quality assured R packages [@ready4pack2022];
-
-- model datasets [@ready4use2022];
-
-- model analyses and reports [@ready4show2022].
-
-The six R packages, their primary focus, the TIMELY standards they support and the third-party packages they depend on are summarised in Table \@ref(tab:cpkgs).
-When used in conjunction with framework repositories, the six packages extending existing R packages to provide strong support for implementing 16 of the TIMELY standards.
-However, the software only weakly supports implementing the standards relating to disseminating statistical models (Y1) and user-interface development (Y2) and does not yet provide any workflow tools to help implement the standards for code coverage (T5) and deprecation conventions (I4).
-Standards not supported or weakly supported by our software can be met with existing developer tools in R and we plan to progressively integrate these third-party tools with our own in future releases of our software.
-Another future priority is to submit production versions of each R package for review by and archiving on the Comprehensive R Archive Network (CRAN) [@CRAN2022].
-
-```{r, child = child_docs_ls$one, echo=FALSE}
-```
-
-\blandscape
-
-```{r, child = child_docs_ls$two, echo=FALSE}
-```
-
-\elandscape
 

### 2022-07-21 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
first attempt at restructure - wip

--- 2022-07-20 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
@@
 ---
-title: "MA_Results"
-author: "Author"
-date: "`r Sys.Date()`"
+title: "MS_Imp_Guidelines"
 output: html_document
+date: '2022-07-21'
 ---
 
-```{r child="../Child_RMDs/XX_Funs.Rmd", echo=FALSE}
-```
-```{r child="../Child_RMDs/MS_Tables.Rmd", echo=FALSE}
-```
-```{r child="../Child_RMDs/MS_Figures.Rmd", echo=FALSE}
-```
-<!-- Add child RMDs for results content -->
+## Guidelines for OSHEMs
+Adherence to explicit guidelines is an essential requirement for modelling in healthcare [@Erdemir2020].
+Guidance for implementing OSHEMs remains scarce and piecemeal and needs to be improved [@Sampson2019].
+Guidelines on health economic model transparency were published ten years ago [@Eddy2012] and made recommendations on documenting models; however, notably missing were recommendations on the sharing of model code and data.
+More recent and more general modelling guidance [@Erdemir2020] recommends the sharing of code and data through digital repository services <!-- such as GitHub [@github2007] and Zenodo [@Zenodo2013] --> and the use of version control systems <!-- such as Git [@git20XX].
+-->
 
-# Motivation
-
-## Why develop OSHEMs in mental health
-
-Mental disorders impose high health, social and economic burdens worldwide [@RN8;@GBD2019].
-Much of this burden is potentially avertable [@RN25], but poorly financed and organised mental health systems are ill-equipped for this challenge[@RN22;@RN23].
-The large and widespread additional mental health burdens recently observed during the COVID-19 pandemic[@20211700] and predicted as a potential future consequence of climate change [@page_howard_2010], highlight the need to improve the resilience and adaptability of these systems.
-To help stem growing demand for mental health services, policymakers have also been encouraged to place greater emphasis on tackling the social determinants of mental disorders [@RN11].
-
-<!-- Computational modelling could play an important role in developing policies to improve population mental health but this may require significant changes in the way mental health modelling projects are funded, conceptualised and implemented.
--->
-Open source frameworks have been recommended to develop the mental health modelling field [@RN73] but, as with health economics more generally, OSHEMs remain rare.
-Currently there is only one mental health related model (in Alcohol Use Disorder [@Basu2018]) that is indexed in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019].
-An open source Major Depressive Disorder reference model for the United States [@IVIMDD2022] is also in development <!-- as part of the Open Value Initiative [@Jansen2019].
--->Greater use of open source approaches could help improve the scope, validity and usefulness of mental health economic models.
-
-Major mental health reform programs, <!-- such as those currently being implemented in Victoria, Australia [@VicRC2021],  -->can involve the identification, prioritisation, sequencing, targeting and monitoring of multiple interdependent initiatives.
-Single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020].
-Mental health simulation studies rarely model complex dynamic systems [@RN73] with economic studies predominantly examining the affordability and value for money of individual mental health programs [@RN34].
-Systems modelling approaches, that have been recommended for public health economics more generally [@SQUIRES2016588] and for mental health specifically [@Occhipinti2021], could provide greater insight about inter-dependencies between candidate policies and the dynamic nature of the mental health systems planning context.
-Dynamic systems methods might provide the foundations for developing reference models [@Afzali2013] of mental health systems that are intended for multiple-applications and re-use by different modelling teams.
-However, more complex models may be more prone to error [@Saltelli2019] and models designed for multiple purposes require greater investments in model transparency and validation [@Eddy2012; @Feenstra2022].
-
-To retain and improve their utility as decision aids, health economic models require updating and refinement as new evidence emerges and decision contexts change [@Jenkins2021].
-The significant deficits in our understanding of the systems in which mental disorders emerge and are treated [@Fried2020] suggest that there is ample scope for mental health systems models to progressively improve their validity over time.
-Prospective work could address the weak theoretical underpinnings for understanding complex mental health systems [@RN2111].
-For example, it remains unclear why increased investments in mental health care have yet to discernibly reduce the prevalence and burden of mental disorders[@RN26].
-The  literature, and evidence base, regarding how the requirements, characteristics and performance of mental health services are shaped by spatiotemporal context needs to be further developed [@RN42].
-There is also a need for better evidence to identify the social determinants of mental disorders most amenable to preventative interventions, and for which population sub-groups such interventions would be most effective [@RN43].
-
-The development, validation and updating of more complex mental health economic models implemented over longer time frames may be too onerous a burden for a single modelling team.
-Developing networks of modellers working on common health conditions has been recommended as a strategy for improving model validity [@Sampson2019] and some of us are part of a nascent initiate of this type in mental health [@nmhsmn2022].
-Furthermore, collaborations across multiple modelling teams that include the ability to re-use and extend one another's work can make complex modelling projects more tractable [@Arnold2010].
-<!-- Add ref to NMHSMN in Australia --> Similarly, developing partnerships between modellers and decision-makers across the life-cycle of a modelling project can help ensure models are appropriately conceptualised, implemented and have practical utility as decision aids [@Zabell2021; @SQUIRES2016588].
-
-## readyforwhatsnext
-We are currently developing **readyforwhatsnext**, a reference OSHEM that aims to examine multiple potential population level strategies for promoting mental wellbeing and preventing and treating mental disorders in young people.
-
-Our approach to model development is to undertake a number of discrete modelling projects of the people, places, platforms and programs that shape the mental health and wellbeing of young people and to progressively link them together by means of a common framework.
-To model people we are developing synthetic representations of populations of interest [@DVN/HJXYKQ_2021] that describe relevant individual characteristics and their relationships, algorithms that map psychological measures to health utility [@Hamilton2021.07.07.21260129] and choice models for predicting the helpseeking behaviour of young people [@hamilton_matthew_2022_6627995].
-Our in-development model of places [@DVN/V3OKZV_2022] has the aim of synthesising geometry and spatial attribute data to characterise the geographic distribution of relevant demographic, environmental, epidemiological and service infrastructure features.
-We are in the early stages of a multi-annual project to develop a service platform model that will represent the processes and operations of a complex primary youth mental health service.
-We also plan to extend and update our prior work reviewing economic evidence relating to youth mental health programs [@RN33] so that it can be integrated with this model.
-
-Our initial work on **readyforwhatsnext** is focused on Victoria, Australia but the framework we are using to develop it is designed to facilitate extension by ourselves and others to different jurisdictional decision contexts.
-Progress is reported on a project website [@rfwn2022].
-
-# Framework
-The framework we have developed to implement **readyforwhatsnext** specifies standards for OSHEMs and provides tools for meeting those standards.
-
-## Framework standards
-Based on existing open science guidance and our own experience, we have identified 20 standards that are important for quality implementations of OSHEMs, each described under one of following six principles for making models **TIMELY**:
+Based on existing open science guidance and our own experience, we have identified 20 guidelines for implementations of OSHEMs that are **TIMELY**:
 
@@
  - **Modular**: models and their components can be combined to extend their scope;
- - **Epitomising**: a model and its components can be used in multiple decision contexts;
+ - **Epitomising**: a model code is sufficiently general to be be re-used in multiple decision contexts;
  - **Licensed**: a model, its components and derivatives are persistently re-usable by other modellers; and
- - **Yielding**: a model can be simply, flexibly and reliably used to inform decision-making.
+ - **Yielding**: a model can be simply, flexibly and reliably used as a decision aid.
 
@@
 A range of tools and practices are available to help make model code and data accessible, comprehensible and citable.
-The most efficient way to widely disseminate code and data may be to use existing open science infrastructure [@Erdemir2020].
-Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each unique item.
+The most efficient way to widely disseminate code and data may be to use existing open science infrastructure [@Erdemir2020] to make permanently accessible and uniquely identfied digital artefacts.
+<!-- Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each unique item.
 These repositories are a preferable solution for sharing citable code and data than transitory repositories such as corporate websites or GitHub where items can be deleted or relocated at any time [@sseditors2022].
 Zenodo includes tools that automate integration with GitHub, which makes it easy for developers to maintain parallel code repositories - one for disseminating the most up to date development code and the other for archiving citable code releases.
-
-Model code and data also need to be clearly documented, potentially with different versions for technical and non-technical users [@Eddy2012].
-Developers storing data in a Dataverse installation have access to multiple meta-data fields to document both a data collection and its individual constituent files.
-In R, code manuals and websites can be created with the aid of tools such as devtools [@devtools2021], sinew [@sinew2022], roxygen2 [@roxygen2021] and pkgdown [@pkgdown2022].
-
-Consistent use of meaningful naming conventions when authoring code is recommended [@Wilson_2017; @Alarid2019].
+-->Model code and data also need to be clearly documented, potentially with different versions for technical and non-technical users [@Eddy2012].
+<!-- Developers storing data in a Dataverse installation have access to multiple meta-data fields to document both a data collection and its individual constituent files.
+--><!-- In R, code manuals and websites can be created with the aid of tools such as devtools [@devtools2021], sinew [@sinew2022], roxygen2 [@roxygen2021] and pkgdown [@pkgdown2022].
+-->Consistent use of meaningful naming conventions when authoring code is recommended [@Wilson_2017; @Alarid2019].
 Code can be made easier to follow by using the practices of abstraction [@8717448], where only simple, high level commands are routinely exposed to reviewers, and polymorphism [@7181447], where the same command (e.g.
 "simulate") can be reused to implement different algorithms of the same type.
-Programs to implement model analyses can be made comprehensible to even non-technical users through the use of literate programming techniques that use tools like RMarkdown [@xie2018r] to render documents that integrate computer code with plain English descriptions.
+Programs to implement model analyses can be made comprehensible to even non-technical users through the use of literate programming techniques <!-- that use tools like RMarkdown [@xie2018r]  -->to render documents that integrate computer code with plain English descriptions.
 
@@
 One useful concept for informing model users about the extensiveness of verification checks is code coverage [@ERICWONG2010188] - the proportion of model code that has been explicitly tested.
-In R, the testthat [@testthat2011] and covr [@covr2020] tools can be used in conjunction with GitHub to define tests and report coverage metrics.
-
-Finally, transcription errors - mistakes introduced when transferring data between sources, models and reports - are very common in health economic models [@Radeva2020].
+<!-- In R, the testthat [@testthat2011] and covr [@covr2020] tools can be used in conjunction with GitHub to define tests and report coverage metrics.
+-->Finally, transcription errors - mistakes introduced when transferring data between sources, models and reports - are very common in health economic models [@Radeva2020].
 The risk of these errors might be lower if there was full transparency across all steps in a study workflow.
@@
 
-Standards:
+Guidelines:
 
@@
 To avoid OSHEMs going stale - losing validity and usefulness with time - they should be routinely updated.
-A number of tools and approaches can make the process of implementing and curating changes to model code and data more coherent and efficient.
-Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent access to all published versions of a dataset, each uniquely identifiable.
+Each update of code and data should be uniquely identifiable and retrievable, a goal that can be facilitated by use of version control tools [@Erdemir2020].<!-- A number of tools and approaches can make the process of implementing and curating changes to model code and data more coherent and efficient.
+<!-- Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent access to all published versions of a dataset, each uniquely identifiable.
 For code, use of version control tools like Git [@git20XX] can ensure that the entire development history of a project is organised so that each version is distinguishable and retrievable by developers.
 The online platform GitHub [@github2007] can make this version history accessible to anyone.
-
-Adopting semantic versioning [@semver20xx] conventions can be an efficient way to provide users of model code and data with information about the potential importance of an update.
-For R code, the usethis [@usethis2021] package can be used to partially automate version number increments using the convention Major.Minor.Patch.Development (e.g.
+-->Labeling each change using semantic versioning [@semver20xx] conventions can signal the potential importance of an update to users of model code and data.
+<!-- For R code, the usethis [@usethis2021] package can be used to partially automate version number increments using the convention Major.Minor.Patch.Development (e.g.
 ExampleSoftware v1.1.1.1).
 Datasets stored on the Harvard Dataverse use the simpler Major.Minor convention.
+-->Continuous integration [@CI2017] tools can help verify that each code update passes multiple quality tests.
+<!-- OSHEMs developed in R can take advantage of templates provided by devtools [@devtools2021] and pkgdown [@pkgdown2022] to run continuous integration checks on GitHub.
+--><!-- These tests can include those of units (do individual functions produce expected output?), documentation (does documentation render correctly?; can all example workflows be executed?) and installation (can the software be successfully deployed on multiple types of operating system?).
+-->
+Finally, using deprecation conventions that take an informative and staged approach to retiring old code and data reduces the risk that model revisions have unintended consequences on third party users.
+-->
+<!-- The package lifeycle [@lifecycle2021] provides tools for R developers to consistently deprecate their code. -->
 
-Continuous integration [@CI2017] tools can help verify that each code update passes multiple quality tests.
-OSHEMs developed in R can take advantage of templates provided by devtools [@devtools2021] and pkgdown [@pkgdown2022] to run continuous integration checks on GitHub.
-These tests can include those of units (do individual functions produce expected output?), documentation (does documentation render correctly?; can all example workflows be executed?) and installation (can the software be successfully deployed on multiple types of operating system?).
+Guidelines:
 
-Finally, using deprecation conventions that take an informative and staged approach to retiring old code and data reduces the risk that model revisions have unintended consequences on third party users.
-The package lifeycle [@lifecycle2021] provides tools for R developers to consistently deprecate their code.
-
-Standards:
-
-- **I1: Model code is version controlled** <!-- Was I2 -->
+- **I1: Model code and data are version controlled** <!-- Was I2 -->
 
@@
 A modular approach that ensures that model code and data are decoupled (stored in different files) can help model developers to restrict access to confidential model data, while providing open access to all other model components.
-
 An important consideration when combining model components (or modules) is to ensure that interactions between two modules do not compromise the validity of either.
@@
 Writing code as collections of functions (short, self-contained and reusable algorithms that each perform a discrete task) is recommended as good practice for scientific computing [@Wilson_2017].
-When distributed as libraries (for example, as R packages), functions have the potential to be widely re-used, often in contexts very different than those they were originally developed for.
+When bundled for distribution as libraries<!-- (for example, as R packages) -->, functions have the potential to be widely re-used, often in contexts very different than those they were originally developed for.
 A special type of function, called a method, can only be applied to a pre-defined class of data structure.
@@
 For code, it may be appropriate to adopt the prevailing open source licensing practice within the programming language being used.
-Applying a previously published algorithm [@kross2016] to analyse the most comprehensive archive of released R packages [@CRAN2022] finds that `r gpl_pc_dbl`% are distributed under various forms of General Public License (GPL) [@GNUGPL2022], a copyleft license.
-
-For data, it may not be sufficient to simply choose between a permissive license like the Public Domain Dedication (CC0) [@cc02022] or a copyleft option such as the Attribution-Share Alike (CC-BY-SA) [@bysa2022].
+<!-- Applying a previously published algorithm [@kross2016] to analyse the most comprehensive archive of released R packages [@CRAN2022] finds that `r gpl_pc_dbl`% are distributed under various forms of General Public License (GPL) [@GNUGPL2022], a copyleft license.
+-->For data, it may not be sufficient to simply choose between a permissive license like the Public Domain Dedication (CC0) [@cc02022] or a copyleft option such as the Attribution-Share Alike (CC-BY-SA) [@bysa2022].
 Responsible custodianship of some de-identified mental health data may involve using or adapting template terms of use [@sampleterms2022] which have a number of ethical clauses (for example, prohibiting efforts to re-identify research participants).
-
 Licenses may or may not specify that model re-users must give appropriate acknowledgement to model authors.
 Citation tools can be distributed with each individual code or data item to inform re-users of the desired attribution.
-In R, including a CITATION file in the `inst` directory of a package will enable users of that package to retrieve citation information by running a command of the format `citation("Package Name")` in the R console [@Salmon2021].
+<!-- In R, including a CITATION file in the `inst` directory of a package will enable users of that package to retrieve citation information by running a command of the format `citation("Package Name")` in the R console [@Salmon2021].
 More generally, including a CITATION.cff file at the top level of your code repository will enable GitHub and Zenodo repositories hosting that item to include the relevant information in their citation tools [@Druskat_Citation_File_Format_2021].
 Datasets hosted on Dataverse installations have metadata fields that, once completed by authors, generate citation files for dataset viewers.
+-->
 
-Standards:
+Guidelines:
 
-- **L1: Model code is made available for re-use under copyleft licenses**
+- **L1: Model code is made available for re-use under copyleft or permissive licenses**
 
-- **L2: Non-confidential model data is available for liberal re-use (subject to additional terms for de-identified human data)**
+- **L2: Non-confidential model data is licensed for liberal re-use (subject to additional terms for de-identified human data)**
 
@@
 OSHEMs can be time and skills intensive for modellers to develop - but they should be easy for others to use.
-
 Statistical models are a common output of health economic evaluations, but they are often not reported in a format that enables others to confidently and reliably re-use them [@Kearns2013].
 Open source approaches can help address this by disseminating code artefacts that enable easy and appropriate use of a statistical model to make predictions with new data.
-However, great care must be exercised when doing so if models are derived from data on human subjects.
-In the R language, model objects by default typically contain a copy of the source dataset.
+However, great care must be exercised when doing so if models are derived from data on human subjects as some software artefacts by default contain a copy of the source dataset.
 Such dataset copies must therefore be replaced (for example, with synthetic data) and the amended artefact's predictive performance then retested before any public release.
+Another way to make OSHEMs easier to use is to develop simple user-interfaces for non-technical users.
+<!-- In R, such user-interfaces are typically developed with the Shiny package, for which a tutorial aimed at health economists is available [@SmithR2020]. -->
 
-Another way to make OSHEMs easier to use is to develop simple user-interfaces for non-technical users.
-In R, such user-interfaces are typically developed with the Shiny package, for which a tutorial aimed at health economists is available [@SmithR2020].
-
-Standards:
+Guidelines:
 
@@
 - **Y2: Simple user-interfaces allow non-technical users to configure and run models ** <!-- Was Y1 -->
-
-## Framework toolkits
-We have developed a toolkit to help streamline the process of developing OSHEMs that meet the TIMELY standards. The toolkit is comprised of online repositories and software.
-
-### Framework repositories <!-- Existing ref -->
-We created a GitHub organisation where all framework software source code is stored, documented, version controlled and continuously integrated [@ready4gh2022].
-To store citable archived copies of release copies of our software, we created a Zenodo community [@ready4zen2022].
-Finally, to manage datasets for use in models developed with the framework, we created a dedicated collection within the Harvard Dataverse  [@ready4dv2022].
-
-### Framework software <!-- Novel ref -->
-As a foundation for implementing the framework, we authored a development version R package that defines a novel syntax and a template class for model modules [@ready42022].
-To enable the syntax and module template be applied to modelling projects, we then created five additional development version R packages that provide tools for authoring:
-
-- documented model modules [@ready4class2022];
-
-- documented functions (including methods), written in a consistent house style [@ready4fun2022];
-
-- citable, quality assured R packages [@ready4pack2022];
-
-- model datasets [@ready4use2022];
-
-- model analyses and reports [@ready4show2022].
-
-The six R packages, their primary focus, the TIMELY standards they support and the third-party packages they depend on are summarised in Table \@ref(tab:cpkgs).
-When used in conjunction with framework repositories, the six packages extend existing R packages provide strong support for implementing 16 of the TIMELY standards.
-However, the software only weakly supports implementing the standards relating to disseminating statistical models (Y1) and user-interface development (Y2) and does not yet provide any workflow tools to help implement the standards for code coverage (T5) and deprecation conventions (I4).
-Standards not supported or weakly supported by our software can be met with existing developer tools in R and we plan to progressively integrate these third-party tools with our own in future releases of our software.
-Another future priority is to submit production versions of each R package for review by and archiving on the Comprehensive R Archive Network (CRAN) [@CRAN2022].
-
-```{r, child = child_docs_ls$one, echo=FALSE}
-```
-
-\blandscape
-
-```{r, child = child_docs_ls$two, echo=FALSE}
-```
-
-\elandscape
-
-# Application
-We used framework toolkits to develop model code and datasets for implementing a utility mapping study that has previously been described [@Hamilton2021.07.07.21260129].
-Table \@ref(tab:checktb) assesses that study against each TIMELY standard, 18 of which the study was able to meet.
-The two current standards where the study falls short are in reporting code coverage and including a user-interface.
-Both these items are current development priorities for our team.

### 2022-07-21 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
first attempt at restructure - wip

--- 2022-07-20 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
@@
 ---
-title: "MA_Results"
-author: "Author"
-date: "`r Sys.Date()`"
+title: "MS_Imp_Guidelines"
 output: html_document
+date: '2022-07-21'
 ---
-
-```{r child="../Child_RMDs/XX_Funs.Rmd", echo=FALSE}
-```
-```{r child="../Child_RMDs/MS_Tables.Rmd", echo=FALSE}
-```
-```{r child="../Child_RMDs/MS_Figures.Rmd", echo=FALSE}
-```
-<!-- Add child RMDs for results content -->
-
-# Motivation
-
-## Why develop OSHEMs in mental health
-
-Mental disorders impose high health, social and economic burdens worldwide [@RN8;@GBD2019].
-Much of this burden is potentially avertable [@RN25], but poorly financed and organised mental health systems are ill-equipped for this challenge[@RN22;@RN23].
-The large and widespread additional mental health burdens recently observed during the COVID-19 pandemic[@20211700] and predicted as a potential future consequence of climate change [@page_howard_2010], highlight the need to improve the resilience and adaptability of these systems.
-To help stem growing demand for mental health services, policymakers have also been encouraged to place greater emphasis on tackling the social determinants of mental disorders [@RN11].
-
-<!-- Computational modelling could play an important role in developing policies to improve population mental health but this may require significant changes in the way mental health modelling projects are funded, conceptualised and implemented.
--->
-Open source frameworks have been recommended to develop the mental health modelling field [@RN73] but, as with health economics more generally, OSHEMs remain rare.
-Currently there is only one mental health related model (in Alcohol Use Disorder [@Basu2018]) that is indexed in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019].
-An open source Major Depressive Disorder reference model for the United States [@IVIMDD2022] is also in development <!-- as part of the Open Value Initiative [@Jansen2019].
--->Greater use of open source approaches could help improve the scope, validity and usefulness of mental health economic models.
-
-Major mental health reform programs, <!-- such as those currently being implemented in Victoria, Australia [@VicRC2021],  -->can involve the identification, prioritisation, sequencing, targeting and monitoring of multiple interdependent initiatives.
-Single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020].
-Mental health simulation studies rarely model complex dynamic systems [@RN73] with economic studies predominantly examining the affordability and value for money of individual mental health programs [@RN34].
-Systems modelling approaches, that have been recommended for public health economics more generally [@SQUIRES2016588] and for mental health specifically [@Occhipinti2021], could provide greater insight about inter-dependencies between candidate policies and the dynamic nature of the mental health systems planning context.
-Dynamic systems methods might provide the foundations for developing reference models [@Afzali2013] of mental health systems that are intended for multiple-applications and re-use by different modelling teams.
-However, more complex models may be more prone to error [@Saltelli2019] and models designed for multiple purposes require greater investments in model transparency and validation [@Eddy2012; @Feenstra2022].
-
-To retain and improve their utility as decision aids, health economic models require updating and refinement as new evidence emerges and decision contexts change [@Jenkins2021].
-The significant deficits in our understanding of the systems in which mental disorders emerge and are treated [@Fried2020] suggest that there is ample scope for mental health systems models to progressively improve their validity over time.
-Prospective work could address the weak theoretical underpinnings for understanding complex mental health systems [@RN2111].
-For example, it remains unclear why increased investments in mental health care have yet to discernibly reduce the prevalence and burden of mental disorders[@RN26].
-The  literature, and evidence base, regarding how the requirements, characteristics and performance of mental health services are shaped by spatiotemporal context needs to be further developed [@RN42].
-There is also a need for better evidence to identify the social determinants of mental disorders most amenable to preventative interventions, and for which population sub-groups such interventions would be most effective [@RN43].
-
-The development, validation and updating of more complex mental health economic models implemented over longer time frames may be too onerous a burden for a single modelling team.
-Developing networks of modellers working on common health conditions has been recommended as a strategy for improving model validity [@Sampson2019] and some of us are part of a nascent initiate of this type in mental health [@nmhsmn2022].
-Furthermore, collaborations across multiple modelling teams that include the ability to re-use and extend one another's work can make complex modelling projects more tractable [@Arnold2010].
-<!-- Add ref to NMHSMN in Australia --> Similarly, developing partnerships between modellers and decision-makers across the life-cycle of a modelling project can help ensure models are appropriately conceptualised, implemented and have practical utility as decision aids [@Zabell2021; @SQUIRES2016588].
+<!-- # Framework -->
+<!-- The framework we have developed to implement **readyforwhatsnext** specifies standards for OSHEMs and provides tools for meeting those standards. -->
 
 ## readyforwhatsnext
-We are currently developing **readyforwhatsnext**, a reference OSHEM that aims to examine multiple potential population level strategies for promoting mental wellbeing and preventing and treating mental disorders in young people.
-
 Our approach to model development is to undertake a number of discrete modelling projects of the people, places, platforms and programs that shape the mental health and wellbeing of young people and to progressively link them together by means of a common framework.
@@
 Progress is reported on a project website [@rfwn2022].
-
-# Framework
-The framework we have developed to implement **readyforwhatsnext** specifies standards for OSHEMs and provides tools for meeting those standards.
-
-## Framework standards
-Based on existing open science guidance and our own experience, we have identified 20 standards that are important for quality implementations of OSHEMs, each described under one of following six principles for making models **TIMELY**:
-
- - **Transparent**: people can easily see how a model has been implemented and tested;
- - **Iterative**: a model is routinely updated to maintain and improve validity;
- - **Modular**: models and their components can be combined to extend their scope;
- - **Epitomising**: a model and its components can be used in multiple decision contexts;
- - **Licensed**: a model, its components and derivatives are persistently re-usable by other modellers; and
- - **Yielding**: a model can be simply, flexibly and reliably used to inform decision-making.
-
-### Transparent Models
-A range of tools and practices are available to help make model code and data accessible, comprehensible and citable.
-The most efficient way to widely disseminate code and data may be to use existing open science infrastructure [@Erdemir2020].
-Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each unique item.
-These repositories are a preferable solution for sharing citable code and data than transitory repositories such as corporate websites or GitHub where items can be deleted or relocated at any time [@sseditors2022].
-Zenodo includes tools that automate integration with GitHub, which makes it easy for developers to maintain parallel code repositories - one for disseminating the most up to date development code and the other for archiving citable code releases.
-
-Model code and data also need to be clearly documented, potentially with different versions for technical and non-technical users [@Eddy2012].
-Developers storing data in a Dataverse installation have access to multiple meta-data fields to document both a data collection and its individual constituent files.
-In R, code manuals and websites can be created with the aid of tools such as devtools [@devtools2021], sinew [@sinew2022], roxygen2 [@roxygen2021] and pkgdown [@pkgdown2022].
-
-Consistent use of meaningful naming conventions when authoring code is recommended [@Wilson_2017; @Alarid2019].
-Code can be made easier to follow by using the practices of abstraction [@8717448], where only simple, high level commands are routinely exposed to reviewers, and polymorphism [@7181447], where the same command (e.g.
-"simulate") can be reused to implement different algorithms of the same type.
-Programs to implement model analyses can be made comprehensible to even non-technical users through the use of literate programming techniques that use tools like RMarkdown [@xie2018r] to render documents that integrate computer code with plain English descriptions.
-
-An essential component of quality assuring health economic models is verification - ensuring that calculations are correct and consistent with model specifications [@techver2019].
-One useful concept for informing model users about the extensiveness of verification checks is code coverage [@ERICWONG2010188] - the proportion of model code that has been explicitly tested.
-In R, the testthat [@testthat2011] and covr [@covr2020] tools can be used in conjunction with GitHub to define tests and report coverage metrics.
-
-Finally, transcription errors - mistakes introduced when transferring data between sources, models and reports - are very common in health economic models [@Radeva2020].
-The risk of these errors might be lower if there was full transparency across all steps in a study workflow.
-Scientific computing tools now make it relatively straightforward to author programs that reproducibly execute all steps in data ingest, processing and reporting [@Wilson_2017].
-
-Standards:
-
-- **T1: Uniquely identified copies of model code and data are permanently archived in open online repositories**
-<!-- T2 MISSING - Merged With T1 -->
-
-- **T2: Model code and data are documented **<!-- Was T3 -->
-
-- **T3: Model code uses a simple and consistent syntax**<!-- Was T4 -->
-
-- **T4: Model analyses and reporting are implemented using literate programming** <!-- Was T5 -->
-
-- **T5: Code coverage is reported** <!-- New, replaces version now moved to T4 -->
-
-- **T6: All parts of a study analysis and reporting workflow can be reproduced and/or replicated** <!-- Was T7, Replaces Deleted T6 -->
-
-### Iterative Models
-To avoid OSHEMs going stale - losing validity and usefulness with time - they should be routinely updated.
-A number of tools and approaches can make the process of implementing and curating changes to model code and data more coherent and efficient.
-Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent access to all published versions of a dataset, each uniquely identifiable.
-For code, use of version control tools like Git [@git20XX] can ensure that the entire development history of a project is organised so that each version is distinguishable and retrievable by developers.
-The online platform GitHub [@github2007] can make this version history accessible to anyone.
-
-Adopting semantic versioning [@semver20xx] conventions can be an efficient way to provide users of model code and data with information about the potential importance of an update.
-For R code, the usethis [@usethis2021] package can be used to partially automate version number increments using the convention Major.Minor.Patch.Development (e.g.
-ExampleSoftware v1.1.1.1).
-Datasets stored on the Harvard Dataverse use the simpler Major.Minor convention.
-
-Continuous integration [@CI2017] tools can help verify that each code update passes multiple quality tests.
-OSHEMs developed in R can take advantage of templates provided by devtools [@devtools2021] and pkgdown [@pkgdown2022] to run continuous integration checks on GitHub.
-These tests can include those of units (do individual functions produce expected output?), documentation (does documentation render correctly?; can all example workflows be executed?) and installation (can the software be successfully deployed on multiple types of operating system?).
-
-Finally, using deprecation conventions that take an informative and staged approach to retiring old code and data reduces the risk that model revisions have unintended consequences on third party users.
-The package lifeycle [@lifecycle2021] provides tools for R developers to consistently deprecate their code.
-
-Standards:
-
-- **I1: Model code is version controlled** <!-- Was I2 -->
-
-- **I2: Model code and data use semantic versioning** <!-- Was I1 -->
-
-- **I3: Continuous integration is used to verify model code updates**
-
-- **I4: Deprecation conventions are used to retire model code and data**
-
-### Modular Models
-Modular health economic models link multiple self-contained components that can be independently reused and extended by other projects [@Trauer2017;@Urach2013].
-Many types of mental health data are highly sensitive with strict confidentiality requirements.
-For this reason, not all data included in some mental health models can be made widely available for others to re-use.
-A modular approach that ensures that model code and data are decoupled (stored in different files) can help model developers to restrict access to confidential model data, while providing open access to all other model components.
-
-An important consideration when combining model components (or modules) is to ensure that interactions between two modules do not compromise the validity of either.
-Using the coding practice of encapsulation [@8717448] can help ensure that model modules can be safely combined [@ready4oop2022].
-
-Standards:
-
-- **M1: Model code and data are stored and managed separately** <!-- Modified (lost ref to licensed and cited) -->
-
-- **M2: Model code defines encapsulating data structures** <!--Replacement - Old version now merged with E1 -->
-
-### Epitomising Models
-A key challenge to generalising health economic models is that they are typically developed to inform a decision problem with a highly specific jurisdictional context.
-However, a number of choices about how these models are implemented can significantly increase the re-usability of model code in other contexts.
-
-Writing code as collections of functions (short, self-contained and reusable algorithms that each perform a discrete task) is recommended as good practice for scientific computing [@Wilson_2017].
-When distributed as libraries (for example, as R packages), functions have the potential to be widely re-used, often in contexts very different than those they were originally developed for.
-A special type of function, called a method, can only be applied to a pre-defined class of data structure.
-Due to the coding concept of inheritance [@8717448], the more restricted nature of methods can be used to enhance the re-usability of model code in different decision contexts [@ready4oop2022].
-For example, when generalising a model developed for the Australian context to a UK context, one could create a class that initially inherits all of the methods defined for the Australian model and then write new or replacement methods as needed for the UK model.Whatever type of functions are written for a modelling project, it is good practice to make available test or toy data to demonstrate their use [@Wilson_2017].
-
-Standards:
-
-- **E1: Model code is distributed as libraries of classes and functions**  <!-- Modified (lost ref to OOP and merged with M2) -->
-
-- **E2: Model code defines inheriting data-structures**
-
-- **E3: Test data is available to demonstrate generalised applications of model code**
-
-### Licensed Models
-```{r echo = F}
-gpl_pc_dbl <- get_license_share("GPL")
-```
-
-To make model code and data widely re-usable by others, it is important to provide users with appropriate and explicit permissions.
-In the context of open source models, there are two broad categories of licensing options.
-Some guidance strongly recommends the use of permissive licensing [@Wilson_2017] that provides users with great flexibility as to the purposes (including commercial) for which the content could be re-used.
-An alternative approach is to use copyleft licenses [@copyleft2022] that can require content users to distribute any derivative works they create under similar open source arrangements.The most suitable approach may differ for code and data.
-
-For code, it may be appropriate to adopt the prevailing open source licensing practice within the programming language being used.
-Applying a previously published algorithm [@kross2016] to analyse the most comprehensive archive of released R packages [@CRAN2022] finds that `r gpl_pc_dbl`% are distributed under various forms of General Public License (GPL) [@GNUGPL2022], a copyleft license.
-
-For data, it may not be sufficient to simply choose between a permissive license like the Public Domain Dedication (CC0) [@cc02022] or a copyleft option such as the Attribution-Share Alike (CC-BY-SA) [@bysa2022].
-Responsible custodianship of some de-identified mental health data may involve using or adapting template terms of use [@sampleterms2022] which have a number of ethical clauses (for example, prohibiting efforts to re-identify research participants).
-
-Licenses may or may not specify that model re-users must give appropriate acknowledgement to model authors.
-Citation tools can be distributed with each individual code or data item to inform re-users of the desired attribution.
-In R, including a CITATION file in the `inst` directory of a package will enable users of that package to retrieve citation information by running a command of the format `citation("Package Name")` in the R console [@Salmon2021].
-More generally, including a CITATION.cff file at the top level of your code repository will enable GitHub and Zenodo repositories hosting that item to include the relevant information in their citation tools [@Druskat_Citation_File_Format_2021].
-Datasets hosted on Dataverse installations have metadata fields that, once completed by authors, generate citation files for dataset viewers.
-
-Standards:
-
-- **L1: Model code is made available for re-use under copyleft licenses**
-
-- **L2: Non-confidential model data is available for liberal re-use (subject to additional terms for de-identified human data)**
-
-- **L3: Model code and data are distributed with tools to support appropriate citation** <!-- New -->
-
-### Yielding Models
-OSHEMs can be time and skills intensive for modellers to develop - but they should be easy for others to use.
-
-Statistical models are a common output of health economic evaluations, but they are often not reported in a format that enables others to confidently and reliably re-use them [@Kearns2013].
-Open source approaches can help address this by disseminating code artefacts that enable easy and appropriate use of a statistical model to make predictions with new data.
-However, great care must be exercised when doing so if models are derived from data on human subjects.
-In the R language, model objects by default typically contain a copy of the source dataset.
-Such dataset copies must therefore be replaced (for example, with synthetic data) and the amended artefact's predictive performance then retested before any public release.
-
-Another way to make OSHEMs easier to use is to develop simple user-interfaces for non-technical users.
-In R, such user-interfaces are typically developed with the Shiny package, for which a tutorial aimed at health economists is available [@SmithR2020].
-
-Standards:
-
-- **Y1: Statistical models are distributed with validated tools to support their safe and appropriate re-use** <!-- New, Replaces Old Y1 (now Y2) -->
-- **Y2: Simple user-interfaces allow non-technical users to configure and run models ** <!-- Was Y1 -->
 
@@
 ### Framework software <!-- Novel ref -->
+
+A coding framework for OSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions [@Alarid2019].
+
 As a foundation for implementing the framework, we authored a development version R package that defines a novel syntax and a template class for model modules [@ready42022].
@@
 \elandscape
-
-# Application
-We used framework toolkits to develop model code and datasets for implementing a utility mapping study that has previously been described [@Hamilton2021.07.07.21260129].
-Table \@ref(tab:checktb) assesses that study against each TIMELY standard, 18 of which the study was able to meet.
-The two current standards where the study falls short are in reporting code coverage and including a user-interface.
-Both these items are current development priorities for our team.

### 2022-07-21 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
first attempt at restructure - wip

--- 2022-06-10 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
@@
 To help address these issues, there is growing support for greater use of open source health economic models (OSHEMs) that grant liberal permissions to access and re-use model source code and data [@Pouwels2022].
-However, to date actual implementations of OSHEMs are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022].
-Barriers to adoption include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations [@Pouwels2022; @Wu2019].
+
+Collaborations across multiple modelling teams that include the ability to re-use and extend one another's work can make complex modelling projects more tractable [@Arnold2010].
+Reference models intended for multiple-applications and re-use by different modelling teams have been advocated for [@Afzali2013] but require greater investments in model transparency and validation [@Eddy2012; @Feenstra2022].
+Systems modelling approaches may be particularly relevant to exploring some public health economics topics  [@SQUIRES2016588] but such complex models may be more prone to error [@Saltelli2019].
+To retain and improve their utility as decision aids, health economic models require updating and refinement as new evidence emerges and decision contexts change [@Jenkins2021].
+
+Open source approaches have been recommended to help develop a mental health field that rarely models complex dynamic systems [@RN73].
+Economic studies predominantly examining the affordability and value for money of individual mental health programs [@RN34].
+Yet such single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020; @Occhipinti2021].
+<!-- and for mental health specifically [@Occhipinti2021],  -->
+<!-- could provide greater insight about inter-dependencies between candidate policies and the dynamic nature of the mental health systems planning context.
+Dynamic systems methods might provide the foundations for developing   -->
+<!-- and models designed for multiple purposes r -->
+
+Despite the potential benefits, actual implementations of OSHEMs are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022].
+Currently there is only one mental health related model (in Alcohol Use Disorder [@Basu2018]) that is indexed in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019].
+Other than our own work, we are aware of just one open source mental health reference model - in Major Depressive Disorder - that is currently in development [@IVIMDD2022].
+Barriers to adoption of OSHEMs include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations [@Pouwels2022; @Wu2019].
 As many health economic models are owned by pharmaceutical companies and consultancies, commercial considerations may also limit the uptake of OSHEMs [@Feenstra2022].
 
-Better guidance about how to implement OSHEMs is required [@Sampson2019].
-Adherence to explicit guidelines is as essential requirement for modelling in healthcare [@Erdemir2020], but current best practice recommendations for OSHEMs are scarce and piecemeal.
-Guidelines on health economic model transparency were published ten years ago [@Eddy2012] and made recommendations on documenting models; however, notably missing were recommendations on the sharing of model code and data.
-More recent and more general modelling guidance [@Erdemir2020] recommends the sharing of code and data through platforms such as GitHub [@github2007] and Zenodo [@Zenodo2013] and the use of version control systems such as Git [@git20XX].
-A coding framework for OSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions [@Alarid2019].
+ <!-- as part of the Open Value Initiative [@Jansen2019].  -->
+
+<!-- Computational modelling could play an important role in developing policies to improve population mental health but this may require significant changes in the way mental health modelling projects are funded, conceptualised and implemented.
+-->
+ <!-- but, as with health economics more generally, OSHEMs remain rare.
+Greater use of open source approaches could help improve the scope, validity and usefulness of mental health economic models.
+-->

### 2022-07-21 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
first attempt at restructure - wip

--- 2022-05-31 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
@@
 <!-- Add child RMDs for results content -->
-
-# Motivation
-
-## Why develop OSHEMs in mental health
-
-Mental disorders impose high health, social and economic burdens worldwide [@RN8;@GBD2019].
-Much of this burden is potentially avertable [@RN25], but poorly financed and organised mental health systems are ill-equipped for this challenge[@RN22;@RN23].
-The large and widespread additional mental health burdens recently observed during the COVID pandemic[@20211700] and predicted as a potential future consequence of global heating [@page_howard_2010], highlight the need to improve the resilience and adaptability of these systems.
-To help stem growing demand for mental health services, policymakers have also been encouraged to place greater emphasis on tackling the social determinants of mental disorder[@RN11].
-
-<!-- Computational modelling could play an important role in developing policies to improve population mental health but this may require significant changes in the way mental health modelling projects are funded, conceptualised and implemented.
--->
-Open source frameworks have been previously recommended for the development of mental health modelling field [@RN73] but, as with health economics more generally, OSHEMs remain rare.
-Currently there is only one mental health related model (in Alcohol Use Disorder [@Basu2018]) that is indexed in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019].
-A Major Depressive Disorder reference model for the United States [@IVIMDD2022] is also being developed as part of the Open Value Initiative [@Jansen2019].
-Greater use of open source approaches could help improve the scope, validity and usefulness of mental health economic models.
-
-Major mental health reform programs, such as those currently being implemented in Victoria, Australia [@VicRC2021], can involve the identification, prioritisation, sequencing, targeting and monitoring of multiple interdependent initiatives.
-Single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020].
-Currently, mental health economic models predominantly address issues relating to the affordability and value for money of individual programs [@RN34] with mental health simulation studies rarely modelling complex systems [@RN73].
-Systems modelling approaches, that have been recommended for public health economics more generally [@SQUIRES2016588] and for mental health specifically [@Occhipinti2021], could provide greater insight about inter-dependencies between candidate policies and the dynamic nature of the mental health systems planning context.
-Dynamic systems methods might also be the basis for developing reference models [@Afzali2013] of mental health systems that are intended for multiple-applications and re-use by different modelling teams.
-However, more complex models may be more prone to error [@Saltelli2019] and models designed for multiple purposes require greater investments in model transparency and validation [@Eddy2012; @Feenstra2022].
-
-To retain and improve their utility as decision aids, health economic models require updating and refinement as new evidence emerges and decision contexts change [@Jenkins2021].
-There are significant deficits in our understanding of the systems in which mental disorder emerges and is treated [@Fried2020] and longer term project horizons could allow mental health economic models to progressively improve validity as these gaps are addressed.
-Currently, the theoretical basis for understanding complex mental health systems is weak [@RN2111].
-Strikingly, it remains unclear why increased investments in mental health care have yet to discernibly reduce the prevalence and burden of mental disorders[@RN26].
-The literature about how the requirements, characteristics and performance of mental health services are shaped by spatiotemporal context is underdeveloped [@RN42].
-There is insufficient evidence to identify the social determinants of mental disorders most amenable to preventative interventions, and for which population sub-groups such interventions would be most effective [@RN43].
-
-The development, validation and updating of more complex mental health economic models implemented over longer time frames may be too onerous a burden for a single modelling team.
-Developing networks of modellers working on common health conditions has been recommended as a strategy for improving model validity [@Sampson2019] and some of us are part of a nascent initiate of this type in mental health [@nmhsmn2022].
-Furthermore, collaborations across multiple modelling teams that include the ability to re-use and extend each others work can make complex modelling projects more tractable [@Arnold2010].
-<!-- Add ref to NMHSMN in Australia --> Similarly, developing partnerships between modellers and decision-makers across the life-cycle of a modelling project can help ensure models are appropriately conceptualised and implemented and improve their practical utility as decision aids [@Zabell2021; @SQUIRES2016588].
-
-## readyforwhatsnext
-We are currently developing readyforwhatsnext, a reference OSHEM that aims to examine multiple potential population level strategies for promoting mental wellbeing and preventing and treating mental disorders in young people.
-
-Our approach to model development is to undertake a number of discrete modelling projects of the people, places, platforms and programs that shape the mental health and wellbeing of young people and to progressively link them together by means of a common framework.
-To model people we are developing synthetic representations of populations of interest [@DVN/HJXYKQ_2021] that describe relevant individual characteristics and their relationships, algorithms that map psychological measures to health utility [@Hamilton2021.07.07.21260129] and choice models for predicting the helpseeking behaviour of young people.
-Our in development model of places [@DVN/V3OKZV_2022] aims to synthesise geometry and spatial attribute data to characterise the geographic distribution of relevant demographic, environmental, epidemiological and service infrastructure features.
-We are in the early stages of a multi-annual project to develop a service platform model that will represent the processes and operations of a complex primary youth mental health service.
-We also plan to extend and update our prior work reviewing economic evidence relating to youth mental health programs [@RN33] so that it can be integrated with the model.
-
-Our initial work on readyforwhatsnext is focused on Victoria, Australia but the framework we are using to develop it is designed to facilitate extension by ourselves and others to different decision contexts.
-Progress is reported on a project website [@rfwn2022].
-
-# Framework
-The framework we have developed to implement readyforwhatsnext specifies standards for OSHEMs and provides tools for meeting those standards.
-
-## Framework standards
-We have identified 20 standards that we believe are important for quality implementations of OSHEMs, each described under one of following six principles for making models TIMELY:
-
- - **Transparent**: people can easily see how a model has been implemented and tested;
- - **Iterative**: a model is routinely updated to maintain and improve validity;
- - **Modular**: models and their components can be combined to extend their scope;
- - **Epitomized**: a model and its components can be used in multiple decision contexts;
- - **Licensed**: a model, its components and derivatives are persistently re-usable by other modellers; and
- - **Yielding**: a model can be simply, flexibly and reliably used to inform decision-making.
-
-### Transparent Models
-A range of tools and practices are available to help make model code and data accessible, comprehensible and citable.
-The most efficient way to widely disseminate code and data may be to use existing open science infrastructure [@Erdemir2020].
-Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each unique item.
-These repositories are a preferable solution for sharing citable code and data than transitory repositories such as corporate websites or GitHub where items can be deleted or relocated at any time [@sseditors2022].
-Zenodo includes tools that automate integration with GitHub, which makes it easy for developers to maintain parallel code repositories - one for disseminating the most up to date development code and the other for archiving citable code releases.
-
-Model code and data also need to be clearly documented, potentially with different versions for technical and non-technical users [@Eddy2012].
-Developers storing data in a Dataverse installation have access to multiple meta-data fields to document both a data collection and its individual constituent files.
-In R, code manuals and websites can be created with the aid of tools such as devtools [@devtools2021], sinew [@sinew2022], roxygen2 [@roxygen2021] and pkgdown [@pkgdown2022].
-
-Consistent use of meaningful naming conventions when authoring code is recommended [@Wilson_2017; @Alarid2019].
-Code can be made easier to follow by using the practices of abstraction [@8717448], where only simple, high level commands are routinely exposed to reviewers, and polymorphsim [@7181447], where the same command (e.g.
-"simulate") can be reused to implement different algorithms of the same type.
-Programs to implement model analyses can be made comprehensible to even non-technical users though the use of literate programming techniques that use tools like RMarkdown [@xie2018r] to render documents that integrate computer code with plain English descriptions.
-
-An essential component of quality assuring health economic models is verification - ensuring that calculations are correct and consistent with model specifications [@techver2019].
-One useful concept for informing model users about the extensiveness of verification checks is code coverage [@ERICWONG2010188] - the proportion of model code that has been explicitly tested.
-In R, the testthat [@testthat2011] and covr [@covr2020] tools can be used in conjunction with GitHub to define tests and report coverage metrics.
-
-Finally, transcription errors - mistakes introduced when transferring data between sources, models and reports - are very common in health economic models [@Radeva2020].
-The risk of these errors might be lower if there was full transparency across all steps in a study workflow.
-Scientific computing tools now make it relatively straightforward to author programs that reproducibly execute all steps in data ingest, processing and reporting [@Wilson_2017].
-
-Standards:
-
-- **T1: Uniquely identified copies of model code and data are permanently archived in open online repositories**
-<!-- T2 MISSING - Merged With T1 -->
-
-- **T2: Model code and data are documented **<!-- Was T3 -->
-
-- **T3: Model code uses a simple and consistent syntax**<!-- Was T4 -->
-
-- **T4: Model analyses and reporting are implemented using literate programming** <!-- Was T5 -->
-
-- **T5: Code coverage is reported** <!-- New, replaces version now moved to T4 -->
-
-- **T6: All parts of a study analysis and reporting workflow can be reproduced and/or replicated** <!-- Was T7, Replaces Deleted T6 -->
-
-### Iterative Models
-To avoid OSHEMs going stale - losing validity and usefulness with time - they should be routinely updated.
-A number of tools and approaches can make the process of implementing and curating changes to model code and data more coherent and efficient.
-Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent access to all published versions of a dataset, each uniquely identifiable.
-For code, use of version control tools like Git [@git20XX] can ensure that the entire development history of a project is organised so that each version is distinguishable and retrievable by developers.
-The online platform GitHub [@github2007] can make this version history accessible to anyone.
-
-Adopting semantic versioning [@semver20xx] conventions can be an efficient way to provide users of model code and data with information about the potential importance of an update.
-For R code, the usethis [@usethis2021] package can be used to partially automate version number increments using the convention Major.Minor.Patch.Development.
-Datasets stored on the Harvard Dataverse use the simpler Major.Minor convention.
-Continuous integration [@CI2017] tools can help verify that each code update passes multiple quality tests.
-OSHEMs developed in R can take advantage of templates provided by devtools [@devtools2021] and pkgdown [@pkgdown2022] to run continuous integration checks on GitHub.
-These tests can include those of units (do individual functions produce expected output?), documentation (does documentation render correctly?, can all example workflows be executed?) and installation (can the software be successfully deployed on multiple types of operating system?).
-
-Finally, using deprecation conventions that take an informative and staged approach to retiring old code and data reduces the risk that model revisions have unintended consequences on third party users.
-The package lifeycle [@lifecycle2021] provides tools for R developers to consistently deprecate their code.
-
-Standards:
-
-- **I1: Model code is version controlled** <!-- Was I2 -->
-
-- **I2: Model code and data use semantic versioning** <!-- Was I1 -->
-
-- **I3: Continuous integration is used to verify model code updates**
-
-- **I4: Deprecation conventions are used to retire model code and data**
-
-### Modular Models
-Modular health economic models link multiple self-contained components that can be independently reused and extended by other projects [@Trauer2017;@Urach2013].
-
-Many types of mental health data are highly sensitive with strict confidentiality requirements.
-For this reason, not all data included in some mental health models can be made widely available for others to re-use.
-A modular approach that ensures that model code and data are decoupled (stored in different files) can help model developers to restrict access to confidential model data, while providing open access to all other model components.
-
-An important consideration when combining model components (or modules) is to ensure that interactions between two modules do not compromise the validity of either.
-Using the coding practice of encapsulation [@8717448] can help ensure that model modules can be safely combined [@ready4oop2022].
-
-Standards:
-
-- **M1: Model code and data are stored and managed separately** <!-- Modified (lost ref to licensed and cited) -->
-
-- **M2: Model code defines encapsulating data structures** <!--Replacement - Old version now merged with E1 -->
-
-### Epitomised Models
-A key challenge to generalising health economic models is that they are typically developed to inform a decision problem with a highly specific jurisdictional context.
-However, a number of choices about how these models are implemented can significantly increase the re-usability of model code in other contexts.
-
-Writing code as collections of functions (short, self-contained and reusable algorithms that each perform a discrete task) is recommended as good practice for scientific computing [@Wilson_2017].
-When distributed as libraries (for example, as R packages), functions have the potential to be widely re-used, often in contexts very different than those they were originally developed for.
-A special type of function called a method can only be applied to a pre-defined class of data structure.
-Due to the coding concept of inheritance [@8717448], the more restricted nature of methods can be used to enhance the re-usability of model code in different decision contexts [@ready4oop2022].
-For example, when generalising a model developed for the Australian context to a UK context, one could create a class that initially inherits all of the methods defined for the Australian model and then write new or replacement methods as needed for the UK model.
-
-Whatever type of functions are written for a modelling project, it is good practice to make available test or toy data to demonstrate their use [@Wilson_2017].
-
-Standards:
-
-- **E1: Model code is distributed as libraries of classes and functions**  <!-- Modified (lost ref to OOP and merged with M2) -->
-
-- **E2: Model code defines inheriting data-structures**
-
-- **E3: Test data is available to demonstrate generalised applications of model code**
-
-### Licensed Models
-```{r echo = F}
-gpl_pc_dbl <- get_license_share("GPL")
+```{r child="../Child_RMDs/MS_Imp_Guidelines.Rmd", echo=FALSE}
 ```
-
-To make model code and data widely re-usable by others, it is important to provide users with appropriate and explicit permissions.
-In the context of open source models, there are two broad categories of licensing options.
-Some guidance strongly recommends the use of permissive licensing [@Wilson_2017] that provides users with great flexibility as to the purposes (including commercial) for which the content could be re-used.
-An alternative approach is to use copyleft licenses [@copyleft2022] that can require content users to distribute any derivative works they create under similar open source arrangements.
-
-For code, it may be appropriate to adopt the prevailing open source licensing practice within the programming language being used.
-Applying a previously published algorithm [@kross2016] to analyse the most comprehensive archive of released R packages [@CRAN2022] finds that `r gpl_pc_dbl`% are distributed under various forms of General Public License (GPL) [@GNUGPL2022], a copyleft license.
-
-For data, it may not be sufficient to simply choose between a permissive license like the Public Domain Dedication (CC0) [@cc02022] or a copyleft option such as the Attribution-Share Alike (CC-BY-SA) [@bysa2022].
-Responsible custodianship of some de-identified mental health data may involve using or adapting template terms of use [@sampleterms2022] which have a number of ethical clauses (for example, prohibiting efforts to re-identify research participants).
-
-Licenses may or may not specify that model re-users must give appropriate acknowledgement to model authors.
-Citation tools can be distributed with each individual code or data item to inform re-users of the desired attribution.
-In R, including a CITATION file in the `inst` directory of a package will enable users of that package to retrieve citation information by running a command of the format `citation("Package Name")` in the R console [@Salmon2021].
-More generally, including a CITATION.cff file at the top level of your code repository will enable GitHub and Zenodo repositories hosting that item to include the relevant information in their citation tools [@Druskat_Citation_File_Format_2021].
-Datasets hosted on Dataverse installations have metadata fields that, once completed by authors, generate citation files for dataset viewers.
-
-Standards:
-
-- **L1: Model code is made available for re-use under copyleft licenses**
-
-- **L2: Non-confidential model data is available for liberal re-use (subject to additional terms for de-identified human data)**
-
-- **L3: Model code and data are distributed with tools to support appropriate citation** <!-- New -->
-
-### Yielding Models
-OSHEMs can be time and skills intensive for modellers to develop - but they should be easy for others to use.
-
-Statistical models are a common output of health economic evaluations, but they are often not reported in a format that enables others to confidently and reliably re-use them [@Kearns2013].
-Open source approaches can help address this by disseminating code artefacts that enable easy and appropriate use of a statistical model to make predictions with new data.
-However, great care must be exercised when doing so if models are derived from data on human subjects.
-In the R language, model objects by default typically contain a copy of the source dataset.
-Such dataset copies must therefore be replaced (for example, with fake data) and the amended artefact's predictive performance then retested before any public release.
-
-Another way to make OSHEMs easier to use is to develop simple user-interfaces for non-technical users.
-In R, such user-interfaces are typically developed with the Shiny package, for which a tutorial aimed at health economists is available [@SmithR2020].
-
-Standards:
-
-- **Y1: Statistical models are distributed with validated tools to support their safe and appropriate re-use** <!-- New, Replaces Old Y1 (now Y2) -->
-- **Y2: Simple user-interfaces allow non-technical users to configure and run models ** <!-- Was Y1 -->
-
-## Framework toolkits
-We have developed a toolkit to help streamline the process of developing OSHEMs that meet the TIMELY standards. The toolkit is comprised of online repositories and software.
-
-### Framework repositories <!-- Existing ref -->
-We created a GitHub organisation where all framework software source code is stored, documented, version controlled and continuously integrated [@ready4gh2022].
-To store citable archived copies of release copies of our software, we created a Zenodo community [@ready4zen2022].
-Finally, to manage datasets for use in models developed with the framework, we created a dedicated collection within the Harvard Dataverse  [@ready4dv2022].
-
-### Framework software <!-- Novel ref -->
-As a foundation for implementing the framework, we authored a development version R package that defines a novel syntax and a template class for model modules [@ready42022].
-To enable the syntax and module template be applied to modelling projects, we then created five additional development version R packages that provide tools for authoring:
-
-- documented model modules [@ready4class2022];
-
-- documented functions (including methods), written in a consistent house style [@ready4fun2022];
-
-- citable, quality assured R packages [@ready4pack2022];
-
-- model datasets [@ready4use2022];
-
-- model analyses and reports [@ready4show2022].
-
-The six R packages, their primary focus, the TIMELY standards they support and the third party packages they depend on are summarised in Table \@ref(tab:cpkgs).
-When used in conjunction with framework repositories, the six packages extending existing R packages to provide strong support for implementing 16 of the TIMELY standards.
-However, the software only weakly supports implementing the standards relating to disseminating statistical models (Y1) and user-interface development (Y2) and does not yet provide any workflow tools to help implement the standards for code coverage (T5) and deprecation conventions (I4).
-Standards not supported or weakly supported by our software can be met with existing developer tools in R and we plan to progressively integrate these third party tools with our own in future releases of our software.
-Another future priority is to submit production versions of each R package for review by and archiving on the Comprehensive R Archive Network (CRAN) [@CRAN2022].
-
-```{r, child = child_docs_ls$one, echo=FALSE}
+```{r child="../Child_RMDs/MS_Imp_Toolkit.Rmd", echo=FALSE}
 ```
-
-\blandscape
-
-```{r, child = child_docs_ls$two, echo=FALSE}
+```{r child="../Child_RMDs/MS_Imp_Example.Rmd", echo=FALSE}
 ```
-
-\elandscape
-
-# Application
-We used framework toolkits to develop model code and datasets for implementing a utility mapping study [@Hamilton2021.07.07.21260129].
-Table \@ref(tab:checktb) assesses that study against each TIMELY standard, 18 of which the study was able to meet.
-The two current standards where the study falls short are in reporting code coverage and including a user-interface.
-Both these items are current development priorities for our team.

### 2022-07-22 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
stuck

@@
 
-- guidelines for quality implementation of OSHEMS;
-- a framework for standardised and reproducible approaches to apply these guidelines to each component of the  **readyforwhatsnext** model; 
-- a worked example of the first **readyforwhatsnext** model component developed using this framework.
+- a proposed set of guidelines for quality implementation of OSHEMS;
+- a framework for standardised and reproducible application of these guidelines to the development of the  **readyforwhatsnext** model; 
+- a worked example of the first **readyforwhatsnext** model component developed using the framework.

### 2022-07-22 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
stuck

@@
 
-# Application
 We used framework toolkits to develop model code and datasets for implementing a utility mapping study that has previously been described [@Hamilton2021.07.07.21260129].

### 2022-07-22 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
stuck

@@
 
-## Guidelines for OSHEMs
 Adherence to explicit guidelines is an essential requirement for modelling in healthcare [@Erdemir2020].
@@
 
-### Transparent Models
+## Transparent Models
 A range of tools and practices are available to help make model code and data accessible, comprehensible and citable.
@@
 
-### Iterative Models
+## Iterative Models
 To avoid OSHEMs going stale - losing validity and usefulness with time - they should be routinely updated.
@@
 
-### Modular Models
+## Modular Models
 Modular health economic models link multiple self-contained components that can be independently reused and extended by other projects [@Trauer2017;@Urach2013].
@@
 
-### Epitomising Models
+## Epitomising Models
 A key challenge to generalising health economic models is that they are typically developed to inform a decision problem with a highly specific jurisdictional context.
@@
 
-### Licensed Models
+## Licensed Models
 ```{r echo = F}
@@
 
-### Yielding Models
+## Yielding Models
 OSHEMs can be time and skills intensive for modellers to develop - but they should be easy for others to use.

### 2022-07-22 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
stuck

@@
 <!-- `r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`  -->
-Health economic computational models have become essential tools for health policy development [@dakin2015influence; @Erdemir2020].
+Computational models have become essential tools for health policy development [@dakin2015influence; @Erdemir2020].
 Although influential and widely used, these models routinely contain errors [@Radeva2020], are rarely adequately validated [@Ghabri2019], can be difficult to reproduce [@Jalali2021; @McManus2019; @Bermejo2017] and are likely to be infrequently updated or revised [@Sampson2017].
@@
 
-Collaborations across multiple modelling teams that include the ability to re-use and extend one another's work can make complex modelling projects more tractable [@Arnold2010].
-Reference models intended for multiple-applications and re-use by different modelling teams have been advocated for [@Afzali2013] but require greater investments in model transparency and validation [@Eddy2012; @Feenstra2022].
-Systems modelling approaches may be particularly relevant to exploring some public health economics topics  [@SQUIRES2016588] but such complex models may be more prone to error [@Saltelli2019].
-To retain and improve their utility as decision aids, health economic models require updating and refinement as new evidence emerges and decision contexts change [@Jenkins2021].
+Enabling multiple modelling teams to collaboratively re-use, test and extend one another's work can make complex modelling projects more tractable [@Arnold2010].
+Recommendations to update and refine health economic models as new evidence emerges and decision contexts change [@Jenkins2021], adopt systems modelling approaches for public health economics topics [@SQUIRES2016588] and to develop multiple-application or reference models for re-use by different modelling teams [@Afzali2013] all involve resourcing and quality assurance challenges.
+For example, complex models may be more prone to error [@Saltelli2019] and reference models require greater investments in model transparency and validation [@Eddy2012; @Feenstra2022].
 
-Open source approaches have been recommended to help develop a mental health field that rarely models complex dynamic systems [@RN73].
-Economic studies predominantly examining the affordability and value for money of individual mental health programs [@RN34].
-Yet such single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020; @Occhipinti2021].
+Open source approaches have been recommended to help develop a mental health modelling field that rarely explores complex dynamic systems [@RN73].
+Mental health economic studies predominantly examine the affordability and value for money of individual programs [@RN34].
+Yet single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020; @Occhipinti2021].
 <!-- and for mental health specifically [@Occhipinti2021],  -->

### 2022-07-22 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
stuck

@@
 <!-- Add child RMDs for results content -->
+# Guidelines
 ```{r child="../Child_RMDs/MS_Imp_Guidelines.Rmd", echo=FALSE}
 ```
+# Framework
 ```{r child="../Child_RMDs/MS_Imp_Toolkit.Rmd", echo=FALSE}
 ```
+# Application
 ```{r child="../Child_RMDs/MS_Imp_Example.Rmd", echo=FALSE}

### 2022-07-22 setup.R

@@ -13,7 +13,7 @@ X <- Ready4showSynopsis(#background_1L_chr = "Our study is entirely fictional.",
                         keywords_chr = c("open source models","health economics","mental disorders"),
                         outp_formats_chr = "PDF",
                         #sample_desc_1L_chr = "The study sample is fake data that pretends to be young people aged 12 to 25 years who attended Australian primary care services for mental health related needs between November 2019 to August 2020.",
-                        title_1L_chr = "A framework for an open source economic model of the systems shaping the mental health of young people")
+                        title_1L_chr = "Proposed guidelines for open source health economic models and a framework for applying them in youth mental health")
 X <- renewSlot(X,
                "authors_r3", 
                {

### 2022-07-25 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
fiddling

--- 2022-06-10 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
@@
 <!-- Add aims text here -->
-We have consolidated and refined these and other recommended guidelines for OSHEMs as part of a framework for developing an open source model of youth mental health.
-In this paper, we describe our motivation for developing the framework, the rationale for each included standard, the software toolkits we have developed to help meet each standard and a worked example of a modelling project developed using this framework.
+In this paper, we describe:
+
+- a proposed set of guidelines for implementing OSHEMS;
+- a framework for applying these guidelines to the development of a reference OSHEM in youth mental health; 
+- a worked example of a modelling project developed with the framework.
+
+<!-- We are currently developing **readyforwhatsnext**, a reference OSHEM that aims to examine multiple potential population level strategies for promoting mental wellbeing and preventing and treating mental disorders in young people.
+-->
+<!-- We have consolidated and refined these and other recommended guidelines for OSHEMs as part of a framework for developing an open source model of youth mental health.  -->

### 2022-07-25 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
fiddling

@@
 
-Adherence to explicit guidelines is an essential requirement for modelling in healthcare [@Erdemir2020].
-Guidance for implementing OSHEMs remains scarce and piecemeal and needs to be improved [@Sampson2019].
 Guidelines on health economic model transparency were published ten years ago [@Eddy2012] and made recommendations on documenting models; however, notably missing were recommendations on the sharing of model code and data.
-More recent and more general modelling guidance [@Erdemir2020] recommends the sharing of code and data through digital repository services <!-- such as GitHub [@github2007] and Zenodo [@Zenodo2013] --> and the use of version control systems <!-- such as Git [@git20XX].
--->
-
-Based on existing open science guidance and our own experience, we have identified 20 guidelines for implementations of OSHEMs that are **TIMELY**:
+More recent and more general modelling guidance [@Erdemir2020] recommends the sharing of code and data through digital repository services <!-- such as GitHub [@github2007] and Zenodo [@Zenodo2013] --> and the use of version control systems.
+<!-- such as Git [@git20XX].
+--> Based on these and other existing sources of guidance and our own experience, we propose 20 guidelines for implementing OSHEMs that are **TIMELY**:
 
@@
  - **Modular**: models and their components can be combined to extend their scope;
- - **Epitomising**: a model code is sufficiently general to be be re-used in multiple decision contexts;
+ - **Epitomising**: model code is sufficiently general to be be re-used in multiple decision contexts;
  - **Licensed**: a model, its components and derivatives are persistently re-usable by other modellers; and

### 2022-07-25 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
fiddling

@@
 Computational models have become essential tools for health policy development [@dakin2015influence; @Erdemir2020].
-Although influential and widely used, these models routinely contain errors [@Radeva2020], are rarely adequately validated [@Ghabri2019], can be difficult to reproduce [@Jalali2021; @McManus2019; @Bermejo2017] and are likely to be infrequently updated or revised [@Sampson2017].
-To help address these issues, there is growing support for greater use of open source health economic models (OSHEMs) that grant liberal permissions to access and re-use model source code and data [@Pouwels2022].
+Although influential and widely used, these models routinely contain errors [@Radeva2020], are rarely adequately validated [@Ghabri2019] and can be difficult to reproduce [@Jalali2021; @McManus2019; @Bermejo2017].
+To help address these issues, there is support for greater use of open source health economic models (OSHEMs) that grant liberal permissions to access and re-use model source code and data [@Pouwels2022].
 
-Enabling multiple modelling teams to collaboratively re-use, test and extend one another's work can make complex modelling projects more tractable [@Arnold2010].
-Recommendations to update and refine health economic models as new evidence emerges and decision contexts change [@Jenkins2021], adopt systems modelling approaches for public health economics topics [@SQUIRES2016588] and to develop multiple-application or reference models for re-use by different modelling teams [@Afzali2013] all involve resourcing and quality assurance challenges.
-For example, complex models may be more prone to error [@Saltelli2019] and reference models require greater investments in model transparency and validation [@Eddy2012; @Feenstra2022].
+Complex modelling projects may be more tractable when multiple modelling teams re-use, test and extend one another's work [@Arnold2010].
+OSHEMSs might therefore mitigate some barriers to improving the longevity, quality and impact of health economic models.
+For example,  health economic models should be updated and refined as new evidence emerges and decision contexts change [@Jenkins2021], but this occurs infrequently [@Sampson2017].
+Reference models that can be re-used in multiple health economic modelling projects have been advocated for [@Afzali2013] but require greater investments in model transparency and validation [@Eddy2012; @Feenstra2022].
+<!-- Systems modelling approaches have been recommended for public health economics topics [@SQUIRES2016588] but complex models may be more prone to error [@Saltelli2019].  -->
 
-Open source approaches have been recommended to help develop a mental health modelling field that rarely explores complex dynamic systems [@RN73].
-Mental health economic studies predominantly examine the affordability and value for money of individual programs [@RN34].
-Yet single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020; @Occhipinti2021].
 <!-- and for mental health specifically [@Occhipinti2021],  -->
@@
 
-Despite the potential benefits, actual implementations of OSHEMs are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022].
-Currently there is only one mental health related model (in Alcohol Use Disorder [@Basu2018]) that is indexed in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019].
-Other than our own work, we are aware of just one open source mental health reference model - in Major Depressive Disorder - that is currently in development [@IVIMDD2022].
+Despite the potential benefits of OSHEMs, actual implementations  are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022].
 Barriers to adoption of OSHEMs include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations [@Pouwels2022; @Wu2019].
 As many health economic models are owned by pharmaceutical companies and consultancies, commercial considerations may also limit the uptake of OSHEMs [@Feenstra2022].
+Adherence to good practice guidance is an essential requirement for healthcare modelling [@Erdemir2020], but guidelines for implementing OSHEMs remain scarce, piecemeal and need improving [@Sampson2019].
+
+<!-- Open source approaches have been recommended to help develop the mental health modelling field <!-- that rarely explores complex dynamic systems  -->
+<!-- [@RN73] but only one mental health related model (in Alcohol Use Disorder [@Basu2018]) is indexed in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019].
+Other than our own work, we are aware of just one open source mental health reference model - in Major Depressive Disorder - that is currently in development [@IVIMDD2022].
+-->
+
+<!-- Mental health economic studies predominantly examine the affordability and value for money of individual programs [@RN34].
+Yet single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020; @Occhipinti2021].
+-->
 

### 2022-07-25 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
fiddling

--- 2022-07-21 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
@@
 <!-- Add child RMDs for results content -->
+
+# Guidelines
 ```{r child="../Child_RMDs/MS_Imp_Guidelines.Rmd", echo=FALSE}
 ```
+
+# Framework
 ```{r child="../Child_RMDs/MS_Imp_Toolkit.Rmd", echo=FALSE}
 ```
+
+# Application
 ```{r child="../Child_RMDs/MS_Imp_Example.Rmd", echo=FALSE}

### 2023-01-23 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
Redo with accontable, reusable and updatable themes

--- 2022-07-21 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
@@
 <!-- Add aims text here -->
-We are currently developing **readyforwhatsnext**, a reference OSHEM that aims to examine multiple potential population level strategies for promoting mental wellbeing and preventing and treating mental disorders in young people.
-<!-- We have consolidated and refined these and other recommended guidelines for OSHEMs as part of a framework for developing an open source model of youth mental health.
--->In this paper, we describe:
+In this paper, we introduce a framework for developing youth mental health OSHEMs. Specifically we describe:
 
-- guidelines for quality implementation of OSHEMS;
-- a framework for standardised and reproducible approaches to apply these guidelines to each component of the  **readyforwhatsnext** model; 
-- a worked example of the first **readyforwhatsnext** model component developed using this framework.
+- a set of guidelines for implementing OSHEMs;
+
+- a toolkit for applying these guidelines in youth mental health; and
+
+- a worked example of a modelling project developed with the toolkit.
+
+<!-- We have consolidated and refined these and other recommended guidelines for OSHEMs as part of a framework for developing an open source model of youth mental health.  -->

### 2023-01-23 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
Redo with accontable, reusable and updatable themes

@@
 
+## readyforwhatsnext
+Our approach to model development is to undertake a number of discrete modelling projects of the people, places, platforms and programs that shape the mental health and wellbeing of young people and to progressively link them together by means of a common framework.
+To model people we are developing synthetic representations of populations of interest [@DVN/HJXYKQ_2021] that describe relevant individual characteristics and their relationships, algorithms that map psychological measures to health utility [@Hamilton2021.07.07.21260129] and choice models for predicting the helpseeking behaviour of young people [@hamilton_matthew_2022_6627995].
+Our in-development model of places [@DVN/V3OKZV_2022] has the aim of synthesising geometry and spatial attribute data to characterise the geographic distribution of relevant demographic, environmental, epidemiological and service infrastructure features.
+We are in the early stages of a multi-annual project to develop a service platform model that will represent the processes and operations of a complex primary youth mental health service.
+We also plan to extend and update our prior work reviewing economic evidence relating to youth mental health programs [@RN33] so that it can be integrated with this model.
+
+Our initial work on **readyforwhatsnext** is focused on Victoria, Australia but the framework we are using to develop it is designed to facilitate extension by ourselves and others to different jurisdictional decision contexts.
+Progress is reported on a project website [@rfwn2022].
+
+## Utility mapping
+
 We used framework toolkits to develop model code and datasets for implementing a utility mapping study that has previously been described [@Hamilton2021.07.07.21260129].

### 2023-01-23 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
Redo with accontable, reusable and updatable themes

@@
 <!-- such as Git [@git20XX].
---> Based on these and other existing sources of guidance and our own experience, we propose 20 guidelines for implementing OSHEMs that are **TIMELY**:
+--> Based on these and other existing sources of guidance and our own experience, we propose 20 guidelines for implementing OSHEMs that are **TIMELY** (Transparent, Iterative, Modular, Epitomising, Licensed and Yielding - see Table \@ref(tab:timelygls)).
 
- - **Transparent**: people can easily see how a model has been implemented and tested;
- - **Iterative**: a model is routinely updated to maintain and improve validity;
- - **Modular**: models and their components can be combined to extend their scope;
- - **Epitomising**: model code is sufficiently general to be be re-used in multiple decision contexts;
- - **Licensed**: a model, its components and derivatives are persistently re-usable by other modellers; and
- - **Yielding**: a model can be simply, flexibly and reliably used as a decision aid.
+ <!-- - **Transparent**: people can easily see how a model has been implemented and tested; -->
+ <!-- - **Iterative**: a model is routinely updated to maintain and improve validity; -->
+ <!-- - **Modular**: models and their components can be combined to extend their scope; -->
+ <!-- - **Epitomising**: model code is sufficiently general to be be re-used in multiple decision contexts; -->
+ <!-- - **Licensed**: a model, its components and derivatives are persistently re-usable by other modellers; and -->
+ <!-- - **Yielding**: a model can be simply, flexibly and reliably used as a decision aid. -->
 
-## Transparent Models
-A range of tools and practices are available to help make model code and data accessible, comprehensible and citable.
+```{r, child = child_docs_ls$one, echo=FALSE}
+```
+
+## Transparent models
+A range of tools and practices are available to help make models more transparent.
 The most efficient way to widely disseminate code and data may be to use existing open science infrastructure [@Erdemir2020] to make permanently accessible and uniquely identfied digital artefacts.
@@
 
-Guidelines:
+<!-- Guidelines: -->
 
-- **T1: Uniquely identified copies of model code and data are permanently archived in open online repositories**
-<!-- T2 MISSING - Merged With T1 -->
+<!-- - **T1: Uniquely identified copies of model code and data are permanently archived in open online repositories** -->
+<!-- <!-- T2 MISSING - Merged With T1 -->
 
-- **T2: Model code and data are documented **<!-- Was T3 -->
+<!-- - **T2: Model code and data are documented **<!-- Was T3 -->
 
-- **T3: Model code uses a simple and consistent syntax**<!-- Was T4 -->
+<!-- - **T3: Model code uses a simple and consistent syntax**<!-- Was T4 -->
 
-- **T4: Model analyses and reporting are implemented using literate programming** <!-- Was T5 -->
+<!-- - **T4: Model analyses and reporting are implemented using literate programming** <!-- Was T5 -->
 
-- **T5: Code coverage is reported** <!-- New, replaces version now moved to T4 -->
+<!-- - **T5: Code coverage is reported** <!-- New, replaces version now moved to T4 -->
 
-- **T6: All parts of a study analysis and reporting workflow can be reproduced and/or replicated** <!-- Was T7, Replaces Deleted T6 -->
+<!-- - **T6: All parts of a study analysis and reporting workflow can be reproduced and/or replicated** <!-- Was T7, Replaces Deleted T6 -->
 
-## Iterative Models
+## Iterative models
 To avoid OSHEMs going stale - losing validity and usefulness with time - they should be routinely updated.
@@
 Finally, using deprecation conventions that take an informative and staged approach to retiring old code and data reduces the risk that model revisions have unintended consequences on third party users.
--->
 <!-- The package lifeycle [@lifecycle2021] provides tools for R developers to consistently deprecate their code. -->
 
-Guidelines:
+<!-- Guidelines: -->
 
-- **I1: Model code and data are version controlled** <!-- Was I2 -->
+<!-- - **I1: Model code and data are version controlled** <!-- Was I2 -->
 
-- **I2: Model code and data use semantic versioning** <!-- Was I1 -->
+<!-- - **I2: Model code and data use semantic versioning** <!-- Was I1 -->
 
-- **I3: Continuous integration is used to verify model code updates**
+<!-- - **I3: Continuous integration is used to verify model code updates** -->
 
-- **I4: Deprecation conventions are used to retire model code and data**
+<!-- - **I4: Deprecation conventions are used to retire model code and data** -->
 
-## Modular Models
-Modular health economic models link multiple self-contained components that can be independently reused and extended by other projects [@Trauer2017;@Urach2013].
-Many types of mental health data are highly sensitive with strict confidentiality requirements.
-For this reason, not all data included in some mental health models can be made widely available for others to re-use.
-A modular approach that ensures that model code and data are decoupled (stored in different files) can help model developers to restrict access to confidential model data, while providing open access to all other model components.
+## Modular models
 An important consideration when combining model components (or modules) is to ensure that interactions between two modules do not compromise the validity of either.
@@
 
-Guidelines:
+<!-- Guidelines: -->
 
-- **M1: Model code and data are stored and managed separately** <!-- Modified (lost ref to licensed and cited) -->
+<!-- - **M1: Model code and data are stored and managed separately** <!-- Modified (lost ref to licensed and cited) -->
 
-- **M2: Model code defines encapsulating data structures** <!--Replacement - Old version now merged with E1 -->
+<!-- - **M2: Model code defines encapsulating data structures** <!--Replacement - Old version now merged with E1 -->
 
-## Epitomising Models
+## Epitomising models
 A key challenge to generalising health economic models is that they are typically developed to inform a decision problem with a highly specific jurisdictional context.
@@
 
-Guidelines:
+<!-- Guidelines: -->
 
-- **E1: Model code is distributed as libraries of classes and functions**  <!-- Modified (lost ref to OOP and merged with M2) -->
+<!-- - **E1: Model code is distributed as libraries of classes and functions**  <!-- Modified (lost ref to OOP and merged with M2) -->
 
-- **E2: Model code defines inheriting data-structures**
+<!-- - **E2: Model code defines inheriting data-structures** -->
 
-- **E3: Test data is available to demonstrate generalised applications of model code**
+<!-- - **E3: Test data is available to demonstrate generalised applications of model code** -->
 
-## Licensed Models
+## Licensed models
 ```{r echo = F}
@@
 
-Guidelines:
+<!-- Guidelines: -->
 
-- **L1: Model code is made available for re-use under copyleft or permissive licenses**
+<!-- - **L1: Model code is made available for re-use under copyleft or permissive licenses** -->
 
-- **L2: Non-confidential model data is licensed for liberal re-use (subject to additional terms for de-identified human data)**
+<!-- - **L2: Non-confidential model data is licensed for liberal re-use (subject to additional terms for de-identified human data)** -->
 
-- **L3: Model code and data are distributed with tools to support appropriate citation** <!-- New -->
+<!-- - **L3: Model code and data are distributed with tools to support appropriate citation** <!-- New -->
 
-## Yielding Models
+## Yielding models
 OSHEMs can be time and skills intensive for modellers to develop - but they should be easy for others to use.
@@
 
-Guidelines:
+<!-- Guidelines: -->
 
-- **Y1: Statistical models are distributed with validated tools to support their safe and appropriate re-use** <!-- New, Replaces Old Y1 (now Y2) -->
-- **Y2: Simple user-interfaces allow non-technical users to configure and run models ** <!-- Was Y1 -->
+<!-- - **Y1: Statistical models are distributed with validated tools to support their safe and appropriate re-use** <!-- New, Replaces Old Y1 (now Y2) --> 
+<!-- - **Y2: Simple user-interfaces allow non-technical users to configure and run models ** <!-- Was Y1 -->

### 2023-01-23 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
Redo with accontable, reusable and updatable themes

@@
 
-## readyforwhatsnext
-Our approach to model development is to undertake a number of discrete modelling projects of the people, places, platforms and programs that shape the mental health and wellbeing of young people and to progressively link them together by means of a common framework.
-To model people we are developing synthetic representations of populations of interest [@DVN/HJXYKQ_2021] that describe relevant individual characteristics and their relationships, algorithms that map psychological measures to health utility [@Hamilton2021.07.07.21260129] and choice models for predicting the helpseeking behaviour of young people [@hamilton_matthew_2022_6627995].
-Our in-development model of places [@DVN/V3OKZV_2022] has the aim of synthesising geometry and spatial attribute data to characterise the geographic distribution of relevant demographic, environmental, epidemiological and service infrastructure features.
-We are in the early stages of a multi-annual project to develop a service platform model that will represent the processes and operations of a complex primary youth mental health service.
-We also plan to extend and update our prior work reviewing economic evidence relating to youth mental health programs [@RN33] so that it can be integrated with this model.
-
-Our initial work on **readyforwhatsnext** is focused on Victoria, Australia but the framework we are using to develop it is designed to facilitate extension by ourselves and others to different jurisdictional decision contexts.
-Progress is reported on a project website [@rfwn2022].
-
-## Framework toolkits
 We have developed a toolkit to help streamline the process of developing OSHEMs that meet the TIMELY standards. The toolkit is comprised of online repositories and software.
 
-### Framework repositories <!-- Existing ref -->
+## Repositories <!-- Existing ref -->
 We created a GitHub organisation where all framework software source code is stored, documented, version controlled and continuously integrated [@ready4gh2022].
@@
 
-### Framework software <!-- Novel ref -->
+## Software <!-- Novel ref -->
 
@@
 
-```{r, child = child_docs_ls$one, echo=FALSE}
+```{r, child = child_docs_ls$two, echo=FALSE}
 ```
@@
 
-```{r, child = child_docs_ls$two, echo=FALSE}
+```{r, child = child_docs_ls$three, echo=FALSE}
 ```

### 2023-01-23 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
Redo with accontable, reusable and updatable themes

@@
 <!-- `r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`  -->
-Computational models have become essential tools for health policy development [@dakin2015influence; @Erdemir2020].
-Although influential and widely used, these models routinely contain errors [@Radeva2020], are rarely adequately validated [@Ghabri2019] and can be difficult to reproduce [@Jalali2021; @McManus2019; @Bermejo2017].
-To help address these issues, there is support for greater use of open source health economic models (OSHEMs) that grant liberal permissions to access and re-use model source code and data [@Pouwels2022].
+Computational models, particularly those addressing economic topics, have become essential tools for health policy development [@dakin2015influence; @Erdemir2020].
+Although influential and widely used, health economic models typically have a number of limitations in accountability, reusability and updatability that at best restrict their usefulness and which in some cases may facilitate harmful misuse.
 
-Complex modelling projects may be more tractable when multiple modelling teams re-use, test and extend one another's work [@Arnold2010].
-OSHEMSs might therefore mitigate some barriers to improving the longevity, quality and impact of health economic models.
-For example,  health economic models should be updated and refined as new evidence emerges and decision contexts change [@Jenkins2021], but this occurs infrequently [@Sampson2017].
-Reference models that can be re-used in multiple health economic modelling projects have been advocated for [@Afzali2013] but require greater investments in model transparency and validation [@Eddy2012; @Feenstra2022].
-<!-- Systems modelling approaches have been recommended for public health economics topics [@SQUIRES2016588] but complex models may be more prone to error [@Saltelli2019].  -->
+Accountability limitations of health economic models include inadequate validatation [@Ghabri2019], routinely containing errors [@Radeva2020] and, as with health policy computational models more generally, being difficult to reproduce [@Jalali2021; @McManus2019; @Bermejo2017].
+Furthermore, models reflect the value judgments of their authors [potentially: https://doi.org/10.1177/0040571X221119276] relating to what questions to address, what features of a system to include, the weighting of different types of evidence and the type of stakeholders who are engaged in model design and validation [ESCAPE FROM MODEL LAND reference].
+These values may at times be poorly aligned with those of the people whose lives are most impacted by decisions informed by model analyses [ESCAPE FROM MODEL LAND reference].
+Some health economists have argued that more complex and sophisticated modelling methods are required to adequately explore some public health topics [@SQUIRES2016588].<!-- Systems modelling approaches have been recommended for public health economics topics [@SQUIRES2016588] but.
+-->However, undertaking more ambitious models may accentuate accountability issues.
+More complex models may be more prone to propagation errors [@Saltelli2019].
+The importance of accountability grows as models evolve from relatively simple implementations that address a single question to multipurpose tools [@Eddy2012; @Feenstra2022].
+Transparency about the nature and extent of individual model authorship contributions can be harder to provide in models implemented over longer timeframes with a large team of collaborators [ESCAPE FROM MODEL LAND reference].
+
+<!-- Modellers should be faithful to reaity and values of users DOI: 10.1002/asi.23697 -->
+
+The resource and skills intensive task of model development can be made more tractable when modellers have the opportunity to re-use, test and refine the work of their peers [@Arnold2010].
+However, as many health economic models are owned by pharmaceutical companies and consultancies, commercial considerations can limit the reuse of models and their constituent code and data[@Feenstra2022].
+Many types of health data are highly sensitive with strict confidentiality requirements.
+For this reason, not all data included in some health economic models can be ethically made publicly available.
+Barriers to generalising and transferring health economic studies are often discussed in terms of study conclusions but also relate to model algorithms (can the same model logic be applied in different contexts?) and data (do shared taxonomies exist so that concepts have similar meanings in different jurisdictions?, which model parameters have values / sources that are context specific?) [Expand and add ref: https://link.springer.com/article/10.1186/s12962-021-00294-4, https://doi.org/10.1017/S026646232200321X].
+
+Health economic models should be updated and refined as new evidence emerges and decision contexts change [@Jenkins2021], but this occurs infrequently [@Sampson2017].
+Decision makers are frequently left to rely on economic analyses that become less valid and relevant each year.
+A model can grow stale when changes in the real world, whether sudden (e.g.
+new pandemics) or gradual (e.g.
+demographic), is not represented by corresponding updates to relevant model features.
+Even when the system being modelled remains relatively stable, new research findings may potentially invalidate aspects of a model's original conceptualisation and implementation.
+Funding for health economic modelling projects rarely extends to provision of medium term support for model updates and improvements.
+The career trajectories of health economists can also mitigate against adequate maintenance of a model, it being relatively common for model authors to have moved on from the team that owns the model IP and / or from working on the health condition for which the model was developed.
+
+A potential strategy for improving model accountability, reusability and updatability is to make models modular and open-source.
+<!-- Modularity -->
+<!-- Definition, value - Computational biology https://doi.org/10.1371/journal.pcbi.1009513 -->
+<!-- reusable, interoperable, trans- parent and able to accommodate updates to both data and algorithms - Ecology DOI: 10.1111/2041-210X.14034 -->
+<!-- Brain OS modularity: https://www.frontiersin.org/articles/10.3389/fninf.2022.883223/pdf -->
+A modular approach that ensures that model code and data are decoupled (stored in different files) can help model developers to restrict access to confidential model data, while providing open access to all other model components.
+Modular approaches have been used in a small number of health economic models to link multiple self-contained components that can be independently reused and extended by other projects [@Trauer2017;@Urach2013].
+Developing well validated reference models for re-used in multiple health economic modelling projects has been advocated for [@Afzali2013].
+<!-- Standardized and transferable approaches to health economic modelling have been recommended. [doi:10.1017/S0266462317000666] -->
+
+There appears to be in principle support from many health economists for greater use of open source health economic models (OSHEMs) that grant liberal permissions to access and re-use model source code and data [@Pouwels2022].
+Despite the potential benefits of OSHEMs, actual implementations are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022].
+Barriers to adoption of OSHEMs include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations [@Pouwels2022; @Wu2019].
+Adherence to good practice guidance is an essential requirement for healthcare modelling [@Erdemir2020], but guidelines for implementing OSHEMs remain scarce, piecemeal and need improving [@Sampson2019].
+Open source is more than open access (limited discussion).
+
+<!-- Reducing waste in research is responsibility of research funder: https://doi.org/10.1016/S0140-6736(13)62229-1 -->
+<!-- MH Research priorities (WP3 - Research, WP6 - Economic) https://doi.org/10.1016/S2215-0366(15)00332-6 -->
 
@@
 
-Despite the potential benefits of OSHEMs, actual implementations  are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022].
-Barriers to adoption of OSHEMs include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations [@Pouwels2022; @Wu2019].
-As many health economic models are owned by pharmaceutical companies and consultancies, commercial considerations may also limit the uptake of OSHEMs [@Feenstra2022].
-Adherence to good practice guidance is an essential requirement for healthcare modelling [@Erdemir2020], but guidelines for implementing OSHEMs remain scarce, piecemeal and need improving [@Sampson2019].
-
-<!-- Open source approaches have been recommended to help develop the mental health modelling field <!-- that rarely explores complex dynamic systems  -->
-<!-- [@RN73] but only one mental health related model (in Alcohol Use Disorder [@Basu2018]) is indexed in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019].
+We plan to develop a modular OSHEM of youth mental health.
+Open source approaches have been recommended to help develop the mental health modelling field [@RN73] but only one mental health related model (in Alcohol Use Disorder [@Basu2018]) is currently indexed [RECHECK] in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019].
 Other than our own work, we are aware of just one open source mental health reference model - in Major Depressive Disorder - that is currently in development [@IVIMDD2022].
--->
+<!-- that rarely explores complex dynamic systems  -->
+<!-- [PECUNIA] -->
 
@@
 -->
+
+<!-- CONTEXT: Funders should also support methodological work on context, including the development of reporting templates to facilitate accurate, comprehensive and systematic reporting of context, approaches to evidence synthesis that can capture contextual variation adequately and modelling methods that can leverage the accumulating evidence on contextual variation to predict the reach, implementation and effectiveness of promising interventions in new contexts."
+http://hdl.handle.net/1893/27205-->

### 2023-01-23 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
Redo with accontable, reusable and updatable themes

@@
 
-# Guidelines
+# Guidelines for OSHEMs
 ```{r child="../Child_RMDs/MS_Imp_Guidelines.Rmd", echo=FALSE}
@@
 
-# Framework
+# Modelling Toolkit
 ```{r child="../Child_RMDs/MS_Imp_Toolkit.Rmd", echo=FALSE}

### 2023-01-23 Markdown/Manuscript/Child_RMDs/MS_Tables.Rmd
table 1 rough draft done
circulated draft
Redo with accontable, reusable and updatable themes

@@
 
-```{r child="XX_Funs.Rmd", echo=FALSE}
-```
-
 ```{r echo=FALSE}
@@
   child_docs_ls <- list(one = "../Child_RMDs/MS_Tables_1.RMD",
-                      two = "../Child_RMDs/MS_Tables_2.RMD")
+                        two = "../Child_RMDs/MS_Tables_2.RMD",
+                        three = "../Child_RMDs/MS_Tables_3.RMD")
 }else{

### 2023-01-23 Markdown/Manuscript/Child_RMDs/MS_Tables_3.Rmd
Redo with accontable, reusable and updatable themes

--- 2022-06-10 Markdown/Manuscript/Child_RMDs/MS_Tables_2.Rmd
@@
 One (ymh_clinical_tb.RDS) closely resembles the study dataset and was released so that the main study algorithm [@hamilton_matthew_2022_6129906] can be rerun by those without access to the confidential study dataset.
-The other (eq5d_ds_dict.RDS) is deliberately different to the source dataset in both variable naming convention and the concepts used for predictors and outcome measures and was created to demonstrate generalised applications of study algorithms.",
+The other (eq5d_ds_dict.RDS) is deliberately different to the source dataset in both variable naming convention and the concepts used for predictors and outcome measures.
+It was created to demonstrate generalised applications of study algorithms.",
                                            "All code libraries, programs and sub-routines use GPL-3 licenses. ",
                                            "Datasets use amended version of template provided by Harvard Dataverse [@sampleterms2022].",
-                                           "All libraries have CITATION file in inst directory. All code repositories have a CITATION.cff file. All datasets have citation generating metadata.",
+                                           "All libraries have a CITATION file in  the inst directory. All code repositories have a CITATION.cff file. All datasets have citation generating metadata.",
                                            "Model catalogues (PDF files beginning with 'AAA_TTU_MDL_CTG') are available in the study results dataset [@DVN/DKDIB0_2021] and describe the predictive performance of all models under a variety of usage regimes (including when the source dataset in the R model object is replaced with fake data).
-The youthu library [@matthew_p_hamilton_2021_5646669] includes tools for searching for and applyihg models compatible with different types of input data.
+The youthu library [@matthew_p_hamilton_2021_5646669] includes tools for searching for and applying models compatible with different types of input data.
 An example program to demonstrate this functionality is available in both RMarkdown [@hamilton_matthew_2022_6416330] and rendered PDF formats (the 'Application.pdf' file in the study results dataset [@DVN/DKDIB0_2021]).

### 2023-01-23 R/SAFETY_DEPRECATED.R

@@ -1,0 +1,70 @@
+df <- tibble::tibble(Package = c("ready4",
+                                 "ready4fun",
+                                 "ready4class",
+                                 "ready4pack",
+                                 "ready4use",
+                                 "ready4show"),
+                     # Version = Package %>%
+                     #   purrr::map_chr(~utils::packageDescription(.x) %>%
+                     #                    purrr::pluck("Version")),
+                     Focus = c("Syntax and template",
+                               "Modules",
+                               "Functions",
+                               "Libraries",
+                               "Data",
+                               "Analysis and reporting"),
+                     `T` = c("3","2-3","2-3","1","1-2","2,4,6"), 
+                     I = c("","4","","1-3","",""),
+                     M = c("3","","2","1-2","1",""),
+                     E = c("", "1","1-2","1","3",""),
+                     L = c("","","","1,3","2-3",""),
+                     Y = c("","","","","","1-2"),
+                     `Depends on` = Package %>%
+                       purrr::map(~ {
+                         utils::packageDescription(.x) %>%
+                           `[`(c("Depends", "Imports")) %>%
+                           purrr::map(~{
+                             if(is.null(.x)){
+                               character(0)
+                             }else{
+                               .x %>%
+                                 strsplit(",\\n") %>%
+                                 purrr::flatten_chr() %>%
+                                 purrr::map(~strsplit(.x,", ") %>%
+                                              purrr::flatten_chr()) %>%
+                                 purrr::flatten_chr() %>% sort() %>%
+                                 purrr::discard(~startsWith(.x,"R "))
+                             }
+                           }) %>%
+                           purrr::flatten_chr() %>%
+                           unique() %>%
+                           sort() %>%
+                           purrr::map_chr(~{
+                             updated_1L_chr <- stringr::str_replace_all(.x,"\\n"," ")
+                             problem_idx_1L_chr <- stringr::str_locate(updated_1L_chr," ")[1,1] %>%
+                               unname()
+                             if(!is.na(problem_idx_1L_chr))
+                               updated_1L_chr <- updated_1L_chr %>%
+                               stringr::str_sub(end = problem_idx_1L_chr-1)
+                             updated_1L_chr %>% 
+                               trimws(which = "left") 
[…]

### 2023-01-23 setup.R

@@ -13,7 +13,7 @@ X <- Ready4showSynopsis(#background_1L_chr = "Our study is entirely fictional.",
                         keywords_chr = c("open source models","health economics","mental disorders"),
                         outp_formats_chr = "PDF",
                         #sample_desc_1L_chr = "The study sample is fake data that pretends to be young people aged 12 to 25 years who attended Australian primary care services for mental health related needs between November 2019 to August 2020.",
-                        title_1L_chr = "Proposed guidelines for open source health economic models and a framework for applying them in youth mental health")
+                        title_1L_chr = "A framework for implementing an open source and modular economic model of youth mental health that is accountable, reusable and updatable")
 X <- renewSlot(X,
                "authors_r3", 
                {
@@ -37,18 +37,19 @@ X <- renewSlot(X,
                "abstract_args_ls",
                {
                  args_ls <- X@abstract_args_ls
-                 args_ls$abstract_ls <- list(Summary = "Despite growing support for open source health economic models (OSHEMs), uptake remains limited and better guidance about how to implement them is required. One potential benefit of high quality OSHEMS is the development of more valid, useful and extensive models to inform the design of population mental health strategies. 
-                                             In this article, we describe a framework that we have developed for an OSHEM in youth mental health. 
-                                             The framework includes a set of 20 good practice standards and toolkits for developing models that meet those standards. 
-                                             Framework standards are intended to support the development of OSHEMS that are TIMELY - Transparent (6 standards), Iterative (4 standards), Modular (2 standards), Epitomising (3 standards), Licensed (3 standards) and Yielding (2 standards). 
-                                             Framework toolkits include repositories for model data and code as well as six novel R packages. The R packages provide a novel syntax, template modules and modelling tools for authoring model modules, function libraries, datasets and reports. 
-                                             We discuss the rationale for each standard included in our framework and provide a worked example of the application of the framework to implement a utility mapping study. ",
+                 args_ls$abstract_ls <- list(Summary = "Despite growing support for open source health economic models (OSHEMs), uptake remains limited. 
+                                             The deployment of modular approaches to model development is also relatively underdeveloped compared to other disciplines.
+                                             In this article, we propose a framework for developing a modular OSHEM in youth mental health and describe our preliminary efforts to apply this framework to develop youth specific utility mapping models.
+                                             The framework includes a set of X1 good practice standards and software for implementing a model that is accountable (X2 standards), reusable (X3 standards) and upatable (X4 standards). 
[…]

### 2023-01-24 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
safety

@@
 <!-- Add aims text here -->
-In this paper, we introduce a framework for developing youth mental health OSHEMs. Specifically we describe:
+In this paper, we introduce a framework for developing a modular youth mental health OSHEM. Specifically we describe the framework's:
 
-- a set of guidelines for implementing OSHEMs;
+- good practice standards for implementing a modular OSHEM;
 
-- a toolkit for applying these guidelines in youth mental health; and
+- software toolkit for developing a modular OSHEM consistent with those good practice standards; and
 
-- a worked example of a modelling project developed with the toolkit.
+- application to implementing model modules to support the development and use of utility mapping models.
 

### 2023-01-24 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
safety

--- 2022-07-25 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
@@
 <!-- `r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`  -->
-Computational models have become essential tools for health policy development [@dakin2015influence; @Erdemir2020].
-Although influential and widely used, these models routinely contain errors [@Radeva2020], are rarely adequately validated [@Ghabri2019] and can be difficult to reproduce [@Jalali2021; @McManus2019; @Bermejo2017].
-To help address these issues, there is support for greater use of open source health economic models (OSHEMs) that grant liberal permissions to access and re-use model source code and data [@Pouwels2022].
+Computational models, particularly those addressing economic topics, have become essential tools for health policy development [@dakin2015influence; @Erdemir2020].
+Although influential and widely used, health economic models typically have a number of limitations that at best restrict their usefulness and which in some cases may facilitate harmful misuse.
 
-Complex modelling projects may be more tractable when multiple modelling teams re-use, test and extend one another's work [@Arnold2010].
-OSHEMSs might therefore mitigate some barriers to improving the longevity, quality and impact of health economic models.
-For example,  health economic models should be updated and refined as new evidence emerges and decision contexts change [@Jenkins2021], but this occurs infrequently [@Sampson2017].
-Reference models that can be re-used in multiple health economic modelling projects have been advocated for [@Afzali2013] but require greater investments in model transparency and validation [@Eddy2012; @Feenstra2022].
-<!-- Systems modelling approaches have been recommended for public health economics topics [@SQUIRES2016588] but complex models may be more prone to error [@Saltelli2019].  -->
+There is a strong case for making health economists more accountable for the appropriate use and social acceptability of their models.
+Users of models should be able to assess their adequacy for a particular purpose [@thompson2019escape].
+This goal is difficult to achieve in the current context of the poor reproducibility [@Jalali2021; @McManus2019; @Bermejo2017] and frequently insufficient validation [@Ghabri2019] of health economic models.
+Value judgments strongly shape health economic analyses, yet are rarely made explicit, omissions that may lead to socially unacceptable policy recommendations [@duckett2022journey].
+A modelling team's value judgments about what questions to address, the most important features of a system to represent and the weighting of different types of evidence may be poorly aligned with those of the people impacted by decisions informed by model analyses [@thompson2022escape].
+As health economic models adopt more sophisticated techniques, the need for accountability grows.
+More complex models may be more prone to propagation errors [@Saltelli2019] and models designed to address multiple questions should be expected to meet more onerous verification and validation obligations [@Eddy2012; @Feenstra2022].
+The nature and extent of individual model authorship contributions may be less clear in models implemented over longer time-frames with a large and changing group of collaborators [@thompson2022].
+
+<!-- Many health economic models are released with errors [@Radeva2020]. -->
+<!-- As modelling methods have become more sophisticated, some have argued that more complex models are required to adequately explore certain types of public health topics [@SQUIRES2016588].  -->
+
+<!-- Accountability for both the scientific quality and social acceptability of health economic models can be improved.  -->
+<!-- Modellers should be faithful to reaity and values of users DOI: 10.1002/asi.23697 -->
+
+Collaborative approaches that encourage re-use of models by other modellers can help make modelling pojects more tractable [@Arnold2010].
+However, as many health economic models are owned by pharmaceutical companies and consultancies, commercial considerations can limit the reuse of models and their constituent code and data [@Feenstra2022].
+Not all data included in health economic models can be ethically made publicly available due to privacy and confidentiality requirements.
+Transferring a health economic model developed for one jurisdiction for application in another will involve retaining some features and updating others [@barbieri2010international].
+Use of concepts with standardised meanings across jurisdictions [@garcia2021cost], supplying context specific data as replaceable data-packs and distributing source code under licenses that allow derivative works are all steps that can enhance model transferability.
+<!-- [https://doi.org/10.1017/S026646232200321X].  -->
+
+Health economic models should be updated and refined as new evidence emerges and decision contexts change [@Jenkins2021], but this occurs infrequently [@Sampson2017].
+Decision makers are frequently left to rely on economic analyses that become less valid and relevant each year.
+A model can grow stale when changes in the real world, whether sudden (e.g.
+new pandemics) or gradual (e.g.
+demographic), is not represented by corresponding updates to relevant model features.
+Even when the system being modelled remains relatively stable, new research findings may potentially invalidate aspects of a model's original conceptualisation and implementation.
+Funding for health economic modelling projects rarely extend to provision of medium term support for model updates and improvements.
+The career trajectories of health economists can also mitigate against adequate maintenance of a model, it being relatively common for model authors to have moved on from the team that owns the model and / or from working on the health condition for which the model was developed.
+
+A potential strategy for improving model accountability, reusability and updatability is to make models both modular and open-source.
+<!-- Modularity -->
+<!-- Definition, value - Computational biology https://doi.org/10.1371/journal.pcbi.1009513 -->
+<!-- reusable, interoperable, trans- parent and able to accommodate updates to both data and algorithms - Ecology DOI: 10.1111/2041-210X.14034 -->
+<!-- Brain OS modularity: https://www.frontiersin.org/articles/10.3389/fninf.2022.883223/pdf -->
+
+A modular approach to model building involves models being constructed by combining multiple replaceable sub-models (modules) [@pan2021modular].
+When used as model sub-components, modules communicate with other modules but they can be also run independently [@barros2023empowering].
+Advantages of modular models include feasibility (large projects are broken into smaller tasks, with each component independently developed and tested) and flexibility (making it easier to selectively replace or update specific parts of a model and to scale up or down the level of granularity) [@pan2021modular].
+Modular approaches are currently being used to facilitate the development of complex computational models in disciplines such as biology [@pan2021modular], neuroscience [@frazier2022robust] and ecology [@barros2023empowering].
+Although the related and enabling concept of reusable reference models has been recommended in health economics [@Afzali2013], peer reviewed studies describing modular health economic models remain relatively rare, though examples exist in tuberculosis [@Trauer2017] and cardiology [@Urach2013].
+
+<!-- A modular approach that ensures that model code and data are decoupled (stored in different files) can help model developers to restrict access to confidential model data, while providing open access to all other model components.
+-->
+
+<!-- Standardized and transferable approaches to health economic modelling have been recommended. [doi:10.1017/S0266462317000666] -->
+The benefits of modular models can be enhanced if multiple modelling teams have the capacity to contribute and use model modules.
+To facilitate this, modular models may be implemented as open source projects that grant liberal permissions to access and re-use model source code and data [@pan2021modular; @barros2023empowering; @frazier2022robust].
+Although there appears to be in principle support from many health economists for greater use of open source health economic models (OSHEMs)  [@Pouwels2022], actual implementations are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022].
+Barriers to adoption of OSHEMs include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations [@Pouwels2022; @Wu2019].
+Adherence to good practice guidance is an essential requirement for healthcare modelling [@Erdemir2020], but guidelines for implementing OSHEMs remain scarce, piecemeal and need improving [@Sampson2019].
+
+<!-- Open source is more than open access (limited discussion). -->
+<!-- Reducing waste in research is responsibility of research funder: https://doi.org/10.1016/S0140-6736(13)62229-1 -->
+<!-- MH Research priorities (WP3 - Research, WP6 - Economic) https://doi.org/10.1016/S2215-0366(15)00332-6 -->
 
@@
 -->
+
+<!-- CONTEXT: Funders should also support methodological work on context, including the development of reporting templates to facilitate accurate, comprehensive and systematic reporting of context, approaches to evidence synthesis that can capture contextual variation adequately and modelling methods that can leverage the accumulating evidence on contextual variation to predict the reach, implementation and effectiveness of promising interventions in new contexts." -->
+
+ <!-- http://hdl.handle.net/1893/27205-->

### 2023-01-24 Reports/Manuscript/Manuscript.tex
safety

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{float}
\let\origfigure\figure
\let\endorigfigure\endfigure
\renewenvironment{figure}[1][2] {
    \expandafter\origfigure\expandafter[H]
} {
    \endorigfigure
}
\usepackage{lscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}
\usepackage[none]{hyphenat}
\usepackage[export]{adjustbox}
\usepackage{multirow}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={A framework for implementing an open source and modular economic model of youth mental health that is accountable, reusable and updatable},
  pdfauthor={Matthew P Hamilton1,2,; Caroline X Gao1,3,2; Glen Wiesner4; Kate M Filia1,3; Jana M Menssink1,3; Petra Plencnerova5; David Baker1,3; Patrick D McGorry1,3; Alexandra Parker6; Jonathan Karnon7; Sue M Cotton1,3; Cathrine Mihalopoulos2},
  pdfkeywords={open source models, health economics, mental disorders},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{A framework for implementing an open source and modular economic model of youth mental health that is accountable, reusable and updatable}
\author{Matthew P Hamilton\textsuperscript{1,2,*} \and Caroline X Gao\textsuperscript{1,3,2} \and Glen Wiesner\textsuperscript{4} \and Kate M Filia\textsuperscript{1,3} \and Jana M Menssink\textsuperscript{1,3} \and Petra Plencnerova\textsuperscript{5} \and David Baker\textsuperscript{1,3} \and Patrick D McGorry\textsuperscript{1,3} \and Alexandra Parker\textsuperscript{6} \and Jonathan Karnon\textsuperscript{7} \and Sue M Cotton\textsuperscript{1,3} \and Cathrine Mihalopoulos\textsuperscript{2}}
\date{}

\begin{document}
\maketitle
\begin{abstract}
\textbf{Summary: } Compared to other disciplines, health economics rarely uses modular approaches to model development that facilitate re-use of model components. Although interest in open source health economic models (OSHEMs) is growing, uptake remains limited. We propose a framework for a modular OSHEM in youth mental health. The framework includes of set of X1 good practice standards for implementing a model that is accountable (X2 standards), reusable (X3 standards) and upatable (X4 standards). We provide a rationale for each standard. The framework also includes software toolkit of six R packages for authoring model modules (data structures and algorithms), supplying those modules with data and using the modules to implement reproducible modelling analyses. We describe an early application of the framework to developing utility mapping models that meet X5 standards. We discuss the potential benefits and challenges of extending this initial work to develop a more extensive model for undertaking economic analyses in youth mental health. \newline \newline \textbf{Code: } Visit \url{https://www.ready4-dev.com} for more information about how to find, install and apply the framework and model. \newline \newline
\end{abstract}

\textsuperscript{1} Orygen, Parkville, Australia\\
\textsuperscript{2} School of Public Health and Preventive Medicine, Monash University, Clayton, Australia\\
\textsuperscript{3} Centre for Youth Mental Health; The University of Melbourne, Parkville, Australia\\
\textsuperscript{4} Heart Foundation, Melbourne, Australia\\
\textsuperscript{5} headspace National Youth Mental Health Foundation, Melbourne, Australia\\
\textsuperscript{6} Victoria University, Footscray, Australia\\
\textsuperscript{7} Flinders University, Adelaide, Australia

\textsuperscript{*} Correspondence: \href{mailto:matthew.hamilton@orygen.org.au}{Matthew P Hamilton \textless{}\href{mailto:matthew.hamilton@orygen.org.au}{\nolinkurl{matthew.hamilton@orygen.org.au}}\textgreater{}}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Computational models, particularly those addressing economic topics, have become essential tools for health policy development {[}1,2{]}. Although influential and widely used, health economic models typically have a number of limitations that at best restrict their usefulness and which in some cases may facilitate harmful misuse.

There is a strong case for making health economists more accountable for the appropriate use and social acceptability of their models. Users of models should be able to assess their adequacy for a particular purpose {[}3{]}. This goal is difficult to achieve in the current context of the poor reproducibility {[}4--6{]} and frequently insufficient validation {[}7{]} of health economic models. Value judgments strongly shape health economic analyses, yet are rarely made explicit, omissions that may lead to socially unacceptable policy recommendations {[}8{]}. A modelling team's value judgments about what questions to address, the most important features of a system to represent and the weighting of different types of evidence may be poorly aligned with those of the people impacted by decisions informed by model analyses {[}9{]}. As health economic models adopt more sophisticated techniques, the need for accountability grows. More complex models may be more prone to propagation errors {[}10{]} and models designed to address multiple questions should be expected to meet more onerous verification and validation obligations {[}11,12{]}. The nature and extent of individual model authorship contributions may be less clear in models implemented over longer time-frames with a large and changing group of collaborators {[}\textbf{thompson2022?}{]}.

Collaborative approaches that encourage re-use of models by other modellers can help make modelling pojects more tractable {[}13{]}. However, as many health economic models are owned by pharmaceutical companies and consultancies, commercial considerations can limit the reuse of models and their constituent code and data {[}12{]}. Not all data included in health economic models can be ethically made publicly available due to privacy and confidentiality requirements. Transferring a health economic model developed for one jurisdiction for application in another will involve retaining some features and updating others {[}14{]}. Use of concepts with standardised meanings across jurisdictions {[}15{]}, supplying context specific data as replaceable data-packs and distributing source code under licenses that allow derivative works are all steps that can enhance model transferability.

Health economic models should be updated and refined as new evidence emerges and decision contexts change {[}16{]}, but this occurs infrequently {[}17{]}. Decision makers are frequently left to rely on economic analyses that become less valid and relevant each year. A model can grow stale when changes in the real world, whether sudden (e.g.~new pandemics) or gradual (e.g.~demographic), is not represented by corresponding updates to relevant model features. Even when the system being modelled remains relatively stable, new research findings may potentially invalidate aspects of a model's original conceptualisation and implementation. Funding for health economic modelling projects rarely extend to provision of medium term support for model updates and improvements. The career trajectories of health economists can also mitigate against adequate maintenance of a model, it being relatively common for model authors to have moved on from the team that owns the model and / or from working on the health condition for which the model was developed.

A potential strategy for improving model accountability, reusability and updatability is to make models both modular and open-source.

A modular approach to model building involves models being constructed by combining multiple replaceable sub-models (modules) {[}18{]}. When used as model sub-components, modules communicate with other modules but they can be also run independently {[}19{]}. Advantages of modular models include feasibility (large projects are broken into smaller tasks, with each component independently developed and tested) and flexibility (making it easier to selectively replace or update specific parts of a model and to scale up or down the level of granularity) {[}18{]}. Modular approaches are currently being used to facilitate the development of complex computational models in disciplines such as biology {[}18{]}, neuroscience {[}20{]} and ecology {[}19{]}. Although the related and enabling concept of reusable reference models has been recommended in health economics {[}21{]}, peer reviewed studies describing modular health economic models remain relatively rare, though examples exist in tuberculosis {[}22{]} and cardiology {[}23{]}.

The benefits of modular models can be enhanced if multiple modelling teams have the capacity to contribute and use model modules. To facilitate this, modular models may be implemented as open source projects that grant liberal permissions to access and re-use model source code and data {[}18--20{]}. Although there appears to be in principle support from many health economists for greater use of open source health economic models (OSHEMs) {[}24{]}, actual implementations are rare {[}12,25,26{]}. Barriers to adoption of OSHEMs include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations {[}24,27{]}. Adherence to good practice guidance is an essential requirement for healthcare modelling {[}2{]}, but guidelines for implementing OSHEMs remain scarce, piecemeal and need improving {[}28{]}.

We plan to develop a modular OSHEM of youth mental health. Open source approaches have been recommended to help develop the mental health modelling field {[}29{]} but only one mental health related model (in Alcohol Use Disorder {[}30{]}) is currently indexed {[}RECHECK{]} in the Open Source Models Clearinghouse {[}25,31{]}. Other than our own work, we are aware of just one open source mental health reference model - in Major Depressive Disorder - that is currently in development {[}32{]}.

In this paper, we introduce a framework for developing a modular youth mental health OSHEM. Specifically we describe the framework's:

\begin{itemize}
\item
  good practice standards for implementing a modular OSHEM;
\item
  software toolkit for developing a modular OSHEM consistent with those good practice standards; and
\item
  application to implementing model modules to support the development and use of utility mapping models.
\end{itemize}

\hypertarget{guidelines-for-oshems}{%
\section{Guidelines for OSHEMs}\label{guidelines-for-oshems}}

Guidelines on health economic model transparency were published ten years ago {[}11{]} and made recommendations on documenting models; however, notably missing were recommendations on the sharing of model code and data. More recent and more general modelling guidance {[}2{]} recommends the sharing of code and data through digital repository services and the use of version control systems. Based on these and other existing sources of guidance and our own experience, we propose 20 guidelines for implementing OSHEMs that are \textbf{TIMELY} (Transparent, Iterative, Modular, Epitomising, Licensed and Yielding - see Table @ref(tab:timelygls)).

\begin{table}

\caption{(\#tab:timelygls)TIMELY Guidelines for OSHEMs}
\centering
\begin{tabular}[t]{>{}ll>{\raggedright\arraybackslash}p{35em}}
\toprule
Characteristic & Guideline & Meaning\\
\midrule
\addlinespace[0.3em]
\multicolumn{3}{l}{\textbf{Transparent - people can easily see how a model has been implemented and tested}}\\
\hspace{1em}\textbf{} & T1 & Uniquely identified copies of model code and data are permanently archived in open online repositories\\
\hspace{1em}\textbf{} & T2 & Model code and data are documented\\
\hspace{1em}\textbf{} & T3 & Model code uses a simple and consistent syntax\\
\hspace{1em}\textbf{} & T4 & Model analyses and reporting are implemented using literate programming\\
\hspace{1em}\textbf{} & T5 & Code coverage is reported\\
\hspace{1em}\textbf{} & T6 & All parts of a study analysis and reporting workflow can be reproduced and/or replicated\\
\addlinespace[0.3em]
\multicolumn{3}{l}{\textbf{Iterative - a model is routinely updated to maintain and improve validity}}\\
\hspace{1em}\textbf{} & I1 & Model code and data are version controlled\\
\hspace{1em}\textbf{} & I2 & Model code and data use semantic versioning\\
\hspace{1em}\textbf{} & I3 & Continuous integration is used to verify model code updates\\
\hspace{1em}\textbf{} & I4 & Deprecation conventions are used to retire model code and data\\
\addlinespace[0.3em]
\multicolumn{3}{l}{\textbf{Modular - models and their components can be combined to extend their scope}}\\
\hspace{1em}\textbf{} & M1 & Model code and data are stored and managed separately\\
\hspace{1em}\textbf{} & M2 & Model code defines encapsulating data structures\\
\addlinespace[0.3em]
\multicolumn{3}{l}{\textbf{Epitomising - model code can be re-used in other decision contexts}}\\
\hspace{1em}\textbf{} & E1 & Model code is distributed as libraries of classes and functions\\
\hspace{1em}\textbf{} & E2 & Model code defines inheriting data-structures\\
\hspace{1em}\textbf{} & E3 & Test data is available to demonstrate generalised applications of model code\\
\addlinespace[0.3em]
\multicolumn{3}{l}{\textbf{Licensed - a model and its components are persistently re-usable by other modellers}}\\
\hspace{1em}\textbf{} & L1 & Model code is made available for re-use under copyleft or permissive licenses\\
\hspace{1em}\textbf{} & L2 & Non-confidential model data is licensed for liberal re-use (subject to additional terms for de-identified human data)\\
\hspace{1em}\textbf{} & L3 & Model code and data are distributed with tools to support appropriate citation\\
\addlinespace[0.3em]
\multicolumn{3}{l}{\textbf{Yielding - a model can be simply, flexibly and reliably used as a decision aid}}\\
\hspace{1em}\textbf{} & Y1 & Models are distributed with validated tools to support their safe and appropriate re-use\\
\hspace{1em}\textbf{} & Y2 & Simple user-interfaces allow non-technical users to configure and run models\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{transparent-models}{%
\subsection{Transparent models}\label{transparent-models}}

A range of tools and practices are available to help make models more transparent. The most efficient way to widely disseminate code and data may be to use existing open science infrastructure {[}2{]} to make permanently accessible and uniquely identfied digital artefacts. Model code and data also need to be clearly documented, potentially with different versions for technical and non-technical users {[}11{]}. Consistent use of meaningful naming conventions when authoring code is recommended {[}33,34{]}. Code can be made easier to follow by using the practices of abstraction {[}35{]}, where only simple, high level commands are routinely exposed to reviewers, and polymorphism {[}36{]}, where the same command (e.g.~``simulate'') can be reused to implement different algorithms of the same type. Programs to implement model analyses can be made comprehensible to even non-technical users through the use of literate programming techniques to render documents that integrate computer code with plain English descriptions.

An essential component of quality assuring health economic models is verification - ensuring that calculations are correct and consistent with model specifications {[}37{]}. One useful concept for informing model users about the extensiveness of verification checks is code coverage {[}38{]} - the proportion of model code that has been explicitly tested. Finally, transcription errors - mistakes introduced when transferring data between sources, models and reports - are very common in health economic models {[}39{]}. The risk of these errors might be lower if there was full transparency across all steps in a study workflow. Scientific computing tools now make it relatively straightforward to author programs that reproducibly execute all steps in data ingest, processing and reporting {[}33{]}.

\hypertarget{iterative-models}{%
\subsection{Iterative models}\label{iterative-models}}

To avoid OSHEMs going stale - losing validity and usefulness with time - they should be routinely updated. Each update of code and data should be uniquely identifiable and retrievable, a goal that can be facilitated by use of version control tools {[}2{]}.Labeling each change using semantic versioning {[}40{]} conventions can signal the potential importance of an update to users of model code and data. Continuous integration {[}41{]} tools can help verify that each code update passes multiple quality tests.
Finally, using deprecation conventions that take an informative and staged approach to retiring old code and data reduces the risk that model revisions have unintended consequences on third party users.\\

\hypertarget{modular-models}{%
\subsection{Modular models}\label{modular-models}}

An important consideration when combining model components (or modules) is to ensure that interactions between two modules do not compromise the validity of either. Using the coding practice of encapsulation {[}35{]} can help ensure that model modules can be safely combined {[}42{]}.

\hypertarget{epitomising-models}{%
\subsection{Epitomising models}\label{epitomising-models}}

A key challenge to generalising health economic models is that they are typically developed to inform a decision problem with a highly specific jurisdictional context. However, a number of choices about how these models are implemented can significantly increase the re-usability of model code in other contexts.

Writing code as collections of functions (short, self-contained and reusable algorithms that each perform a discrete task) is recommended as good practice for scientific computing {[}33{]}. When bundled for distribution as libraries, functions have the potential to be widely re-used, often in contexts very different than those they were originally developed for. A special type of function, called a method, can only be applied to a pre-defined class of data structure. Due to the coding concept of inheritance {[}35{]}, the more restricted nature of methods can be used to enhance the re-usability of model code in different decision contexts {[}42{]}. For example, when generalising a model developed for the Australian context to a UK context, one could create a class that initially inherits all of the methods defined for the Australian model and then write new or replacement methods as needed for the UK model.Whatever type of functions are written for a modelling project, it is good practice to make available test or toy data to demonstrate their use {[}33{]}.

\hypertarget{licensed-models}{%
\subsection{Licensed models}\label{licensed-models}}

To make model code and data widely re-usable by others, it is important to provide users with appropriate and explicit permissions. In the context of open source models, there are two broad categories of licensing options. Some guidance strongly recommends the use of permissive licensing {[}33{]} that provides users with great flexibility as to the purposes (including commercial) for which the content could be re-used. An alternative approach is to use copyleft licenses {[}43{]} that can require content users to distribute any derivative works they create under similar open source arrangements.The most suitable approach may differ for code and data.

For code, it may be appropriate to adopt the prevailing open source licensing practice within the programming language being used. For data, it may not be sufficient to simply choose between a permissive license like the Public Domain Dedication (CC0) {[}44{]} or a copyleft option such as the Attribution-Share Alike (CC-BY-SA) {[}45{]}. Responsible custodianship of some de-identified mental health data may involve using or adapting template terms of use {[}46{]} which have a number of ethical clauses (for example, prohibiting efforts to re-identify research participants). Licenses may or may not specify that model re-users must give appropriate acknowledgement to model authors. Citation tools can be distributed with each individual code or data item to inform re-users of the desired attribution.

\hypertarget{yielding-models}{%
\subsection{Yielding models}\label{yielding-models}}

OSHEMs can be time and skills intensive for modellers to develop - but they should be easy for others to use. Statistical models are a common output of health economic evaluations, but they are often not reported in a format that enables others to confidently and reliably re-use them {[}47{]}. Open source approaches can help address this by disseminating code artefacts that enable easy and appropriate use of a statistical model to make predictions with new data. However, great care must be exercised when doing so if models are derived from data on human subjects as some software artefacts by default contain a copy of the source dataset. Such dataset copies must therefore be replaced (for example, with synthetic data) and the amended artefact's predictive performance then retested before any public release. Another way to make OSHEMs easier to use is to develop simple user-interfaces for non-technical users.

\hypertarget{modelling-toolkit}{%
\section{Modelling Toolkit}\label{modelling-toolkit}}

We have developed a toolkit to help streamline the process of developing OSHEMs that meet the TIMELY standards. The toolkit is comprised of online repositories and software.

\hypertarget{repositories}{%
\subsection{\texorpdfstring{Repositories }{Repositories }}\label{repositories}}

We created a GitHub organisation where all framework software source code is stored, documented, version controlled and continuously integrated {[}48{]}. To store citable archived copies of release copies of our software, we created a Zenodo community {[}49{]}. Finally, to manage datasets for use in models developed with the framework, we created a dedicated collection within the Harvard Dataverse {[}50{]}.

\hypertarget{software}{%
\subsection{\texorpdfstring{Software }{Software }}\label{software}}

A coding framework for OSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions {[}34{]}.

As a foundation for implementing the framework, we authored a development version R package that defines a novel syntax and a template class for model modules {[}51{]}. To enable the syntax and module template be applied to modelling projects, we then created five additional development version R packages that provide tools for authoring:

\begin{itemize}
\item
  documented model modules {[}52{]};
\item
  documented functions (including methods), written in a consistent house style {[}53{]};
\item
  citable, quality assured R packages {[}54{]};
\item
  model datasets {[}55{]};
\item
  model analyses and reports {[}56{]}.
\end{itemize}

The six R packages, their primary focus, the TIMELY standards they support and the third-party packages they depend on are summarised in Table @ref(tab:cpkgs). When used in conjunction with framework repositories, the six packages extend existing R packages provide strong support for implementing 16 of the TIMELY standards. However, the software only weakly supports implementing the standards relating to disseminating statistical models (Y1) and user-interface development (Y2) and does not yet provide any workflow tools to help implement the standards for code coverage (T5) and deprecation conventions (I4). Standards not supported or weakly supported by our software can be met with existing developer tools in R and we plan to progressively integrate these third-party tools with our own in future releases of our software. Another future priority is to submit production versions of each R package for review by and archiving on the Comprehensive R Archive Network (CRAN) {[}57{]}.

\begin{table}

\caption{(\#tab:cpkgs)Framework software to enable the readyforwhatsnext model to meet TIMELY guidelines}
\centering
\begin{tabular}[t]{ll>{}l>{\raggedright\arraybackslash}m{24em}}
\toprule
Package & Focus & Guideline      & Depends on these R packages\\
\midrule
\includegraphics[valign=M,width=1.9cm,raise=4mm]{../Data/images/ready4_logo.png} & Syntax & T3           M3 & assertthat bib2df dataverse dplyr fs Hmisc kableExtra knitr lifecycle magrittr methods natmanager piggyback purrr readr readxl rlang rmarkdown rvest stats stringi stringr testit testthat tibble tidyRSS tools utils zen4R\\
\includegraphics[valign=M,width=1.9cm,raise=4mm]{../Data/images/ready4fun_logo.png} & Functions & T2-3             E1 & desc devtools dplyr generics gert Hmisc knitr lifecycle lubridate magrittr methods piggyback pkgdown purrr readxl ready4 ready4show ready4use rlang sinew stats stringi stringr testit testthat tibble tidyr tools usethis utils xfun\\
\includegraphics[valign=M,width=1.9cm,raise=4mm]{../Data/images/ready4class_logo.png} & Modules & T2-3         M2   E1-2 & devtools dplyr fs gtools Hmisc knitr lifecycle magrittr methods purrr ready4 ready4fun ready4show rlang stats stringi stringr testit testthat tibble tidyr usethis utils\\
\includegraphics[valign=M,width=1.9cm,raise=4mm]{../Data/images/ready4pack_logo.png} & Libraries & T1      I1-3  M1-2 E1   L1,3 & dataverse dplyr knitr lifecycle magrittr methods purrr ready4 ready4class ready4fun rlang stringr testthat tibble tidyr utils\\
\includegraphics[valign=M,width=1.9cm,raise=4mm]{../Data/images/ready4use_logo.png} & Data & T1-2         M1   E3   L2-3 & data.table dataverse dplyr fs Hmisc knitr lifecycle magrittr methods piggyback purrr readxl ready4 ready4show rlang stats stringi stringr testit testthat tibble tidyr utils\\
\addlinespace
\includegraphics[valign=M,width=1.9cm,raise=4mm]{../Data/images/ready4show_logo.png} & Reporting & T2,4,6                           Y1-2 & dataverse DescTools dplyr flextable grDevices here Hmisc kableExtra knitr knitrBootstrap lifecycle magrittr methods officer purrr ready4 rlang rmarkdown stringi stringr testthat tibble tidyr utils xtable\\
\bottomrule
\end{tabular}
\end{table}

\blandscape

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0040}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0094}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0335}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0375}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0067}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0094}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.8995}}@{}}
\caption{(\#tab:checktb)TIMELY Checklist applied to utility mapping study}\tabularnewline
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Standard
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Met?
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Description
\end{minipage} \\
\midrule()
\endfirsthead
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Standard
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Met?
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Description
\end{minipage} \\
\midrule()
\endhead
T1 & ~ & Publicly archived & ~ ~ ~ ~ & Yes & ~ & 5 libraries (youthvars, scorz, specific, TTU and youthu) {[}58--62{]}, 3 programs {[}63--65{]}, 2 sub-routines {[}66,67{]} and 2 datasets {[}68,69{]} are permanently archived with unique identifiers. \\
T2 & ~ & Documented & ~ ~ ~ ~ & Yes & ~ & All code libraries have documenting websites with URLs that concatenate `\url{https://ready4-dev.github.io/}' and the package name (e.g.~\url{https://ready4-dev.github.io/youthvars}). All three Markdown programs are self-documenting, with one {[}63{]} including additional instructions in a README file. Only one sub-routine {[}67{]} is documented with a meaningful README file. All datasets have meaningful metadata descriptors. \\
T3 & ~ & Consistent syntax & ~ ~ ~ ~ & Yes & ~ & All libraries, programs and sub-routines use the same house style, which allows most library documentation to be written by algorithms from the ready4fun package {[}53{]}. All libraries except {[}62{]} use framework syntax, as does one program {[}63{]}. \\
T4 & ~ & Literately programmed & ~ ~ ~ ~ & Yes & ~ & All programs use literate programming. \\
T5 & ~ & Code coverage & ~ ~ ~ ~ & No & ~ & No current reporting of code coverage. \\
T6 & ~ & Reproducible & ~ ~ ~ ~ & Yes & ~ & All parts of the study workflow from raw data ingest through to data processing, analysis, reporting and dissemination of study outputs can be reproduced (if granted access to source data) or replicated (using supplied synthetic data) with one program {[}63{]}. \\
I1 & ~ & Version controlled & ~ ~ ~ ~ & Yes & ~ & All code is version controlled using Git and GitHub. All source code is available in a GitHub organisation {[}48{]}. \\
I2 & ~ & Semanticly versioned & ~ ~ ~ ~ & Yes & ~ & Semantic version is used in all code. As no code library has yet been submitted to CRAN, only the development version extensions of each version number have been incremented to date. \\
I3 & ~ & Continuously integrated & ~ ~ ~ ~ & Yes & ~ & All six libraries use continuous integration (CI). CI results for each library can be viewed at a URL that concatenates `\url{https://github.com/ready4-dev/}', the package name and `/actions' (e.g.~\url{https://github.com/ready4-dev/youthvars/actions}) \\
I4 & ~ & Deprecation & ~ ~ ~ ~ & Yes & ~ & Retired code is deprecated using lifecycle package tools (e.g.~everything after ``\#\# DEPRECATED FNS'' in \url{https://github.com/ready4-dev/youthvars/blob/main/data-raw/fns/add.R} ). Package vignettes and datasets are also deprecated e.g.~\url{https://ready4-dev.github.io/youthvars/articles/Replication_DS.html} ) \\
M1 & ~ & Separate code and data & ~ ~ ~ ~ & Yes & ~ & All development code is stored on repos in a GitHub organisation {[}48{]} and all archived releases are available in a Zenodo community {[}49{]}. All non-confidential data is stored in repositories within a Harvard Dataverse collection {[}50{]}. \\
M2 & ~ & Encapsulated & ~ ~ ~ ~ & Yes & ~ & Four {[}58--61{]} out of five libraries include encapsulated modules. Examples are the items beginning with Scorz, Specific and Youthvars that are listed in this table: \url{https://ready4-dev.github.io/ready4/articles/V_01.html\#current-ready4-framework-modules} as well as the S4 classess from the TTU package listed here: \url{https://ready4-dev.github.io/TTU/reference/index.html} \\
E1 & ~ & Libraries & ~ ~ ~ ~ & Yes & ~ & All code libraries include functions. The most complete list of functions for each library is available by clicking the `Manual - Developer (PDF)' link on each package's documentation homepage (see item T2 above). \\
E2 & ~ & Inheriting & ~ ~ ~ ~ & Yes & ~ & All modules (see item M2) inherit from the Ready4Module class and can be inherited from. \\
E3 & ~ & Test data & ~ ~ ~ ~ & Yes & ~ & Two synthetic datasets and their data dictionaries are publicly available in a data repository {[}69{]}. One (ymh\_clinical\_tb.RDS) closely resembles the study dataset and was released so that the main study algorithm {[}63{]} can be rerun by those without access to the confidential study dataset. The other (eq5d\_ds\_dict.RDS) is deliberately different to the source dataset in both variable naming convention and the concepts used for predictors and outcome measures. It was created to demonstrate generalised applications of study algorithms. \\
L1 & ~ & Copyleft code & ~ ~ ~ ~ & Yes & ~ & All code libraries, programs and sub-routines use GPL-3 licenses. \\
L2 & ~ & Liberal, safe data terms & ~ ~ ~ ~ & Yes & ~ & Datasets use amended version of template provided by Harvard Dataverse {[}46{]}. \\
L3 & ~ & Citation tools & ~ ~ ~ ~ & Yes & ~ & All libraries have a CITATION file in the inst directory. All code repositories have a CITATION.cff file. All datasets have citation generating metadata. \\
Y1 & ~ & Prediction tools & ~ ~ ~ ~ & Yes & ~ & Model catalogues (PDF files beginning with `AAA\_TTU\_MDL\_CTG') are available in the study results dataset {[}68{]} and describe the predictive performance of all models under a variety of usage regimes (including when the source dataset in the R model object is replaced with fake data). The youthu library {[}62{]} includes tools for searching for and applying models compatible with different types of input data. An example program to demonstrate this functionality is available in both RMarkdown {[}64{]} and rendered PDF formats (the `Application.pdf' file in the study results dataset {[}68{]}). \\
Y2 & ~ & User interface & ~ ~ ~ ~ & No & ~ & No Shiny app user interface has yet been developed. \\
\bottomrule()
\end{longtable}

\elandscape

\hypertarget{application}{%
\section{Application}\label{application}}

\hypertarget{readyforwhatsnext}{%
\subsection{readyforwhatsnext}\label{readyforwhatsnext}}

Our approach to model development is to undertake a number of discrete modelling projects of the people, places, platforms and programs that shape the mental health and wellbeing of young people and to progressively link them together by means of a common framework. To model people we are developing synthetic representations of populations of interest {[}69{]} that describe relevant individual characteristics and their relationships, algorithms that map psychological measures to health utility {[}70{]} and choice models for predicting the helpseeking behaviour of young people {[}71{]}. Our in-development model of places {[}72{]} has the aim of synthesising geometry and spatial attribute data to characterise the geographic distribution of relevant demographic, environmental, epidemiological and service infrastructure features. We are in the early stages of a multi-annual project to develop a service platform model that will represent the processes and operations of a complex primary youth mental health service. We also plan to extend and update our prior work reviewing economic evidence relating to youth mental health programs {[}73{]} so that it can be integrated with this model.

Our initial work on \textbf{readyforwhatsnext} is focused on Victoria, Australia but the framework we are using to develop it is designed to facilitate extension by ourselves and others to different jurisdictional decision contexts. Progress is reported on a project website {[}74{]}.

\hypertarget{utility-mapping}{%
\subsection{Utility mapping}\label{utility-mapping}}

We used framework toolkits to develop model code and datasets for implementing a utility mapping study that has previously been described {[}70{]}. Table @ref(tab:checktb) assesses that study against each TIMELY standard, 18 of which the study was able to meet. The two current standards where the study falls short are in reporting code coverage and including a user-interface. Both these items are current development priorities for our team.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

Mental disorders impose high health, social and economic burdens worldwide {[}75,76{]}. Much of this burden is potentially avertable {[}77{]}, but poorly financed and organised mental health systems are ill-equipped for this challenge{[}78,79{]}. The large and widespread additional mental health burdens recently observed during the COVID-19 pandemic{[}80{]} and predicted as a potential future consequence of climate change {[}81{]}, highlight the need to improve the resilience and adaptability of these systems. To help stem growing demand for mental health services, policymakers have also been encouraged to place greater emphasis on tackling the social determinants of mental disorders {[}82{]}.

Major mental health reform programs, can involve the identification, prioritisation, sequencing, targeting and monitoring of multiple interdependent initiatives.

The significant deficits in our understanding of the systems in which mental disorders emerge and are treated {[}83{]} suggest that there is ample scope for mental health systems models to progressively improve their validity over time. Prospective work could address the weak theoretical underpinnings for understanding complex mental health systems {[}84{]}. For example, it remains unclear why increased investments in mental health care have yet to discernibly reduce the prevalence and burden of mental disorders{[}85{]}. The literature, and evidence base, regarding how the requirements, characteristics and performance of mental health services are shaped by spatiotemporal context needs to be further developed {[}86{]}. There is also a need for better evidence to identify the social determinants of mental disorders most amenable to preventative interventions, and for which population sub-groups such interventions would be most effective {[}87{]}.

The development, validation and updating of more complex mental health economic models implemented over longer time frames may be too onerous a burden for a single modelling team.

Developing networks of modellers working on common health conditions has been recommended as a strategy for improving model validity {[}28{]} and some of us are part of a nascent initiate of this type in mental health {[}88{]}.
Similarly, developing partnerships between modellers and decision-makers across the life-cycle of a modelling project can help ensure models are appropriately conceptualised, implemented and have practical utility as decision aids {[}89,90{]}.

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

We have identified a number of standards that we believe are appropriate to implementing quality OSHEMs in youth mental health. Most of these standards are probably relevant to OSHEMs in other health conditions, though some such as the copyleft licensing may be less relevant to modellers using different tools. Our framework toolkits can help support standardised approaches to dynamic systems model development that are important for collaborative and interdependent projects.\\

\hypertarget{acknowledgement}{%
\subsection{Acknowledgement}\label{acknowledgement}}

The authors would like to acknowledge the contribution of John Gillam who provided advisory input to this research.

\hypertarget{availability-of-data-and-materials}{%
\subsection*{Availability of data and materials}\label{availability-of-data-and-materials}}
\addcontentsline{toc}{subsection}{Availability of data and materials}

Development versions of all code repositories referenced in this article are available in \url{https://github.com/ready4-dev/} . Archived code releases are available in \url{https://zenodo.org/communities/ready4} .

All data repositories referenced in this article are available in \url{https://dataverse.harvard.edu/dataverse/ready4} .

\hypertarget{ethics-approval}{%
\subsection*{Ethics approval}\label{ethics-approval}}
\addcontentsline{toc}{subsection}{Ethics approval}

Framework development did not involve human subject research and was not ethically reviewed. The worked example of framework application is a previously reported study that was reviewed and granted approval by the University of Melbourne's Human Research Ethics Committee, and the local Human Ethics and Advisory Group (1645367.1).

\hypertarget{funding}{%
\subsection*{Funding}\label{funding}}
\addcontentsline{toc}{subsection}{Funding}

Framework development was funded by Orygen, VicHealth and Victoria University. The previously reported study used as a worked example was funded by the National Health and Medical Research Council (NHMRC, APP1076940), Orygen and headspace.

\hypertarget{conflict-of-interest}{%
\subsection*{Conflict of Interest}\label{conflict-of-interest}}
\addcontentsline{toc}{subsection}{Conflict of Interest}

None declared.

\newpage

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-dakin2015influence}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{Dakin H, Devlin N, Feng Y, Rice N, O'Neill P, Parkin D. The influence of cost-effectiveness and other factors on nice decisions. Health economics. Wiley Online Library; 2015;24: 1256--1271. }

\leavevmode\vadjust pre{\hypertarget{ref-Erdemir2020}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Erdemir A, Mulugeta L, Ku JP, Drach A, Horner M, Morrison TM, et al. Credible practice of modeling and simulation in healthcare: Ten rules from a multidisciplinary perspective. Journal of translational medicine. 2020;18: 369. doi:\href{https://doi.org/10.1186/s12967-020-02540-4}{10.1186/s12967-020-02540-4}}

\leavevmode\vadjust pre{\hypertarget{ref-thompson2019escape}{}}%
\CSLLeftMargin{3. }%
\CSLRightInline{Thompson EL, Smith LA. Escape from model-land. Economics. De Gruyter Open Access; 2019;13. }

\leavevmode\vadjust pre{\hypertarget{ref-Jalali2021}{}}%
\CSLLeftMargin{4. }%
\CSLRightInline{Jalali MS, DiGennaro C, Guitar A, Lew K, Rahmandad H. Evolution and reproducibility of simulation modeling in epidemiology and health policy over half a century. Epidemiologic Reviews. 2021;43: 166--175. doi:\href{https://doi.org/10.1093/epirev/mxab006}{10.1093/epirev/mxab006}}

\leavevmode\vadjust pre{\hypertarget{ref-McManus2019}{}}%
\CSLLeftMargin{5. }%
\CSLRightInline{McManus E, Turner D, Sach T. Can you repeat that? Exploring the definition of a successful model replication in health economics. Pharmacoeconomics. 2019;37: 1371--1381. doi:\href{https://doi.org/10.1007/s40273-019-00836-y}{10.1007/s40273-019-00836-y}}

\leavevmode\vadjust pre{\hypertarget{ref-Bermejo2017}{}}%
\CSLLeftMargin{6. }%
\CSLRightInline{Bermejo I, Tappenden P, Youn J-H. Replicating health economic models: Firm foundations or a house of cards? PharmacoEconomics. 2017;35: 1113--1121. doi:\href{https://doi.org/10.1007/s40273-017-0553-x}{10.1007/s40273-017-0553-x}}

\leavevmode\vadjust pre{\hypertarget{ref-Ghabri2019}{}}%
\CSLLeftMargin{7. }%
\CSLRightInline{Ghabri S, Stevenson M, Möller J, Caro JJ. Trusting the results of model-based economic analyses: Is there a pragmatic validation solution? Pharmacoeconomics. 2019;37: 1--6. doi:\href{https://doi.org/10.1007/s40273-018-0711-9}{10.1007/s40273-018-0711-9}}

\leavevmode\vadjust pre{\hypertarget{ref-duckett2022journey}{}}%
\CSLLeftMargin{8. }%
\CSLRightInline{Duckett S. A journey towards a theology of health economics and healthcare funding. Theology. SAGE Publications Sage UK: London, England; 2022;125: 326--334. }

\leavevmode\vadjust pre{\hypertarget{ref-thompson2022escape}{}}%
\CSLLeftMargin{9. }%
\CSLRightInline{Thompson E. Escape from model land: How mathematical models can lead us astray and what we can do about it. New Yourk: Basic Books; 2022. }

\leavevmode\vadjust pre{\hypertarget{ref-Saltelli2019}{}}%
\CSLLeftMargin{10. }%
\CSLRightInline{Saltelli A. A short comment on statistical versus mathematical modelling. Nature Communications. 2019;10: 3870. doi:\href{https://doi.org/10.1038/s41467-019-11865-8}{10.1038/s41467-019-11865-8}}

\leavevmode\vadjust pre{\hypertarget{ref-Eddy2012}{}}%
\CSLLeftMargin{11. }%
\CSLRightInline{Eddy DM, Hollingworth W, Caro JJ, Tsevat J, McDonald KM, Wong JB. Model transparency and validation: A report of the ISPOR-SMDM modeling good research practices task force-7. Med Decis Making. 2012;32: 733--43. doi:\href{https://doi.org/10.1177/0272989x12454579}{10.1177/0272989x12454579}}

\leavevmode\vadjust pre{\hypertarget{ref-Feenstra2022}{}}%
\CSLLeftMargin{12. }%
\CSLRightInline{Feenstra T, Corro-Ramos I, Hamerlijnck D, Voorn G van, Ghabri S. Four aspects affecting health economic decision models and their validation. PharmacoEconomics. 2022;40: 241--248. doi:\href{https://doi.org/10.1007/s40273-021-01110-w}{10.1007/s40273-021-01110-w}}

\leavevmode\vadjust pre{\hypertarget{ref-Arnold2010}{}}%
\CSLLeftMargin{13. }%
\CSLRightInline{Arnold RJG, Ekins S. Time for cooperation in health economics among the modelling community. PharmacoEconomics. 2010;28: 609--613. doi:\href{https://doi.org/10.2165/11537580-000000000-00000}{10.2165/11537580-000000000-00000}}

\leavevmode\vadjust pre{\hypertarget{ref-barbieri2010international}{}}%
\CSLLeftMargin{14. }%
\CSLRightInline{Barbieri M, Drummond M, Rutten F, Cook J, Glick HA, Lis J, et al. What do international pharmacoeconomic guidelines say about economic data transferability? Value in Health. Elsevier; 2010;13: 1028--1037. }

\leavevmode\vadjust pre{\hypertarget{ref-garcia2021cost}{}}%
\CSLLeftMargin{15. }%
\CSLRightInline{Garcı́a-Mochón L, Rovira Forns J, Espin J. Cost transferability problems in economic evaluation as a framework for an european health care and social costs database. Cost Effectiveness and Resource Allocation. Springer; 2021;19: 1--12. }

\leavevmode\vadjust pre{\hypertarget{ref-Jenkins2021}{}}%
\CSLLeftMargin{16. }%
\CSLRightInline{Jenkins DA, Martin GP, Sperrin M, Riley RD, Debray TPA, Collins GS, et al. Continual updating and monitoring of clinical prediction models: Time for dynamic prediction systems? Diagnostic and Prognostic Research. 2021;5: 1. doi:\href{https://doi.org/10.1186/s41512-020-00090-3}{10.1186/s41512-020-00090-3}}

\leavevmode\vadjust pre{\hypertarget{ref-Sampson2017}{}}%
\CSLLeftMargin{17. }%
\CSLRightInline{Sampson CJ, Wrightson T. Model registration: A call to action. PharmacoEconomics - Open. 2017;1: 73--77. doi:\href{https://doi.org/10.1007/s41669-017-0019-2}{10.1007/s41669-017-0019-2}}

\leavevmode\vadjust pre{\hypertarget{ref-pan2021modular}{}}%
\CSLLeftMargin{18. }%
\CSLRightInline{Pan M, Gawthrop PJ, Cursons J, Crampin EJ. Modular assembly of dynamic models in systems biology. PLoS computational biology. Public Library of Science San Francisco, CA USA; 2021;17: e1009513. }

\leavevmode\vadjust pre{\hypertarget{ref-barros2023empowering}{}}%
\CSLLeftMargin{19. }%
\CSLRightInline{Barros C, Luo Y, Chubaty AM, Eddy IM, Micheletti T, Boisvenue C, et al. Empowering ecological modellers with a PERFICT workflow: Seamlessly linking data, parameterisation, prediction, validation and visualisation. Methods in Ecology and Evolution. Wiley Online Library; 2023; }

\leavevmode\vadjust pre{\hypertarget{ref-frazier2022robust}{}}%
\CSLLeftMargin{20. }%
\CSLRightInline{Frazier-Logue N, Wang J, Wang Z, Sodums D, Khosla A, Samson AD, et al. A robust modular automated neuroimaging pipeline for model inputs to TheVirtualBrain. Frontiers in Neuroinformatics. Frontiers Media SA; 2022;16: 883223. }

\leavevmode\vadjust pre{\hypertarget{ref-Afzali2013}{}}%
\CSLLeftMargin{21. }%
\CSLRightInline{Afzali HH, Karnon J, Merlin T. Improving the accuracy and comparability of model-based economic evaluations of health technologies for reimbursement decisions: A methodological framework for the development of reference models. Med Decis Making. 2013;33: 325--32. doi:\href{https://doi.org/10.1177/0272989x12458160}{10.1177/0272989x12458160}}

\leavevmode\vadjust pre{\hypertarget{ref-Trauer2017}{}}%
\CSLLeftMargin{22. }%
\CSLRightInline{Trauer JM, Ragonnet R, Doan TN, McBryde ES. Modular programming for tuberculosis control, the {``AuTuMN''} platform. BMC Infectious Diseases. 2017;17: 546. doi:\href{https://doi.org/10.1186/s12879-017-2648-6}{10.1186/s12879-017-2648-6}}

\leavevmode\vadjust pre{\hypertarget{ref-Urach2013}{}}%
\CSLLeftMargin{23. }%
\CSLRightInline{Urach C, Zauner G, Endel G, Wilbacher I, Breitenecker F. A modular simulation model for assessing interventions for abdominal aortic aneurysms. 2013 winter simulations conference (WSC). 2013. pp. 66--76. doi:\href{https://doi.org/10.1109/WSC.2013.6721408}{10.1109/WSC.2013.6721408}}

\leavevmode\vadjust pre{\hypertarget{ref-Pouwels2022}{}}%
\CSLLeftMargin{24. }%
\CSLRightInline{Pouwels X, Sampson CJ, Arnold RJG. Opportunities and barriers to the development and use of open source health economic models: A survey. Value Health. 2022;25: 473--479. doi:\href{https://doi.org/10.1016/j.jval.2021.10.001}{10.1016/j.jval.2021.10.001}}

\leavevmode\vadjust pre{\hypertarget{ref-Emerson2019}{}}%
\CSLLeftMargin{25. }%
\CSLRightInline{Emerson J, Bacon R, Kent A, Neumann PJ, Cohen JT. Publication of decision model source code: Attitudes of health economics authors. PharmacoEconomics. 2019;37: 1409--1410. doi:\href{https://doi.org/10.1007/s40273-019-00796-3}{10.1007/s40273-019-00796-3}}

\leavevmode\vadjust pre{\hypertarget{ref-Michalczyk2018}{}}%
\CSLLeftMargin{26. }%
\CSLRightInline{Michalczyk J, Clay E, Pochopien M, Aballea S. PRM123 - AN OVERVIEW OF OPEN-SOURCE MODELS IN HEALTH ECONOMICS. Value in Health. 2018;21: S377. doi:\href{https://doi.org/10.1016/j.jval.2018.09.2243}{10.1016/j.jval.2018.09.2243}}

\leavevmode\vadjust pre{\hypertarget{ref-Wu2019}{}}%
\CSLLeftMargin{27. }%
\CSLRightInline{Wu EQ, Zhou Z-Y, Xie J, Metallo C, Thokala P. Transparency in health economic modeling: Options, issues and potential solutions. PharmacoEconomics. 2019;37: 1349--1354. doi:\href{https://doi.org/10.1007/s40273-019-00842-0}{10.1007/s40273-019-00842-0}}

\leavevmode\vadjust pre{\hypertarget{ref-Sampson2019}{}}%
\CSLLeftMargin{28. }%
\CSLRightInline{Sampson CJ, Arnold R, Bryan S, Clarke P, Ekins S, Hatswell A, et al. Transparency in decision modelling: What, why, who and how? PharmacoEconomics. 2019;37: 1355--1369. doi:\href{https://doi.org/10.1007/s40273-019-00819-z}{10.1007/s40273-019-00819-z}}

\leavevmode\vadjust pre{\hypertarget{ref-RN73}{}}%
\CSLLeftMargin{29. }%
\CSLRightInline{Long KM, Meadows GN. Simulation modelling in mental health: A systematic review. Journal of Simulation. 2017; doi:\href{https://doi.org/10.1057/s41273-017-0062-0}{10.1057/s41273-017-0062-0}}

\leavevmode\vadjust pre{\hypertarget{ref-Basu2018}{}}%
\CSLLeftMargin{30. }%
\CSLRightInline{Clearinghouse C. Basu, kim: Alcohol use disorder {[}Internet{]}. OSF; 2018. Available: \href{https://osf.io/jvayu}{osf.io/jvayu}}

\leavevmode\vadjust pre{\hypertarget{ref-OSMC_20xx}{}}%
\CSLLeftMargin{31. }%
\CSLRightInline{Evaluation of Value C for the, Health R in. Open-source model clearinghouse {[}Internet{]}. Tufts Medical Center; Available: \url{http://ghcearegistry.org/orchard/open-source-model-clearinghouse}}

\leavevmode\vadjust pre{\hypertarget{ref-IVIMDD2022}{}}%
\CSLLeftMargin{32. }%
\CSLRightInline{Innovation T, Initiative V. IVI-MDD value model {[}Internet{]}. 2022. Available: \url{https://www.thevalueinitiative.org/ivi-mdd-value-model/}}

\leavevmode\vadjust pre{\hypertarget{ref-Wilson_2017}{}}%
\CSLLeftMargin{33. }%
\CSLRightInline{Wilson JAC Greg AND Bryan. Good enough practices in scientific computing. PLOS Computational Biology. Public Library of Science; 2017;13: 1--20. doi:\href{https://doi.org/10.1371/journal.pcbi.1005510}{10.1371/journal.pcbi.1005510}}

\leavevmode\vadjust pre{\hypertarget{ref-Alarid2019}{}}%
\CSLLeftMargin{34. }%
\CSLRightInline{Alarid-Escudero F, Krijkamp EM, Pechlivanoglou P, Jalal H, Kao S-YZ, Yang A, et al. A need for change! A coding framework for improving transparency in decision modeling. PharmacoEconomics. 2019;37: 1329--1339. doi:\href{https://doi.org/10.1007/s40273-019-00837-x}{10.1007/s40273-019-00837-x}}

\leavevmode\vadjust pre{\hypertarget{ref-8717448}{}}%
\CSLLeftMargin{35. }%
\CSLRightInline{Hourani H, Wasmi H, Alrawashdeh T. A code complexity model of object oriented programming (OOP). 2019 IEEE jordan international joint conference on electrical engineering and information technology (JEEIT). 2019. pp. 560--564. doi:\href{https://doi.org/10.1109/JEEIT.2019.8717448}{10.1109/JEEIT.2019.8717448}}

\leavevmode\vadjust pre{\hypertarget{ref-7181447}{}}%
\CSLLeftMargin{36. }%
\CSLRightInline{Milojkovic N, Caracciolo A, Lungu MF, Nierstrasz O, Röthlisberger D, Robbes R. Polymorphism in the spotlight: Studying its prevalence in java and smalltalk. 2015 IEEE 23rd international conference on program comprehension. 2015. pp. 186--195. doi:\href{https://doi.org/10.1109/ICPC.2015.29}{10.1109/ICPC.2015.29}}

\leavevmode\vadjust pre{\hypertarget{ref-techver2019}{}}%
\CSLLeftMargin{37. }%
\CSLRightInline{Büyükkaramikli NC, Rutten-van Mölken MPMH, Severens JL, Al M. TECH-VER: A verification checklist to reduce errors in models and improve their credibility. PharmacoEconomics. 2019;37: 1391--1408. doi:\href{https://doi.org/10.1007/s40273-019-00844-y}{10.1007/s40273-019-00844-y}}

\leavevmode\vadjust pre{\hypertarget{ref-ERICWONG2010188}{}}%
\CSLLeftMargin{38. }%
\CSLRightInline{Eric Wong W, Debroy V, Choi B. A family of code coverage-based heuristics for effective fault localization. Journal of Systems and Software. 2010;83: 188--208. doi:\url{https://doi.org/10.1016/j.jss.2009.09.037}}

\leavevmode\vadjust pre{\hypertarget{ref-Radeva2020}{}}%
\CSLLeftMargin{39. }%
\CSLRightInline{Radeva D, Hopkin G, Mossialos E, Borrill J, Osipenko L, Naci H. Assessment of technical errors and validation processes in economic models submitted by the company for NICE technology appraisals. International Journal of Technology Assessment in Health Care. 2020;36: 311--316. doi:\href{https://doi.org/10.1017/S0266462320000422}{10.1017/S0266462320000422}}

\leavevmode\vadjust pre{\hypertarget{ref-semver20xx}{}}%
\CSLLeftMargin{40. }%
\CSLRightInline{Preston-Werner T. Semantic versioning 2.0.0 {[}Internet{]}. 2022. Available: \url{https://semver.org}}

\leavevmode\vadjust pre{\hypertarget{ref-CI2017}{}}%
\CSLLeftMargin{41. }%
\CSLRightInline{Shahin M, Ali Babar M, Zhu L. Continuous integration, delivery and deployment: A systematic review on approaches, tools, challenges and practices. IEEE Access. 2017;5: 3909--3943. doi:\href{https://doi.org/10.1109/ACCESS.2017.2685629}{10.1109/ACCESS.2017.2685629}}

\leavevmode\vadjust pre{\hypertarget{ref-ready4oop2022}{}}%
\CSLLeftMargin{42. }%
\CSLRightInline{Hamilton M. Apply an object-oriented paradigm to computational models of mental health systems {[}Internet{]}. 2022. Available: \url{https://ready4-dev.github.io/ready4/articles/V_03.html}}

\leavevmode\vadjust pre{\hypertarget{ref-copyleft2022}{}}%
\CSLLeftMargin{43. }%
\CSLRightInline{Foundation TFS. What is copyleft? {[}Internet{]}. Available: \url{https://www.gnu.org/copyleft/}}

\leavevmode\vadjust pre{\hypertarget{ref-cc02022}{}}%
\CSLLeftMargin{44. }%
\CSLRightInline{Commons C. CC0 1.0 universal {[}Internet{]}. 2022. Available: \url{https://creativecommons.org/publicdomain/zero/1.0/legalcode}}

\leavevmode\vadjust pre{\hypertarget{ref-bysa2022}{}}%
\CSLLeftMargin{45. }%
\CSLRightInline{Commons C. Attribution-ShareAlike 4.0 international {[}Internet{]}. 2022. Available: \url{https://creativecommons.org/licenses/by-sa/4.0/legalcode}}

\leavevmode\vadjust pre{\hypertarget{ref-sampleterms2022}{}}%
\CSLLeftMargin{46. }%
\CSLRightInline{Quantitative Social Science I for. Sample data usage agreement {[}Internet{]}. 2022. Available: \url{https://support.dataverse.harvard.edu/sample-data-usage-agreement}}

\leavevmode\vadjust pre{\hypertarget{ref-Kearns2013}{}}%
\CSLLeftMargin{47. }%
\CSLRightInline{Kearns B, Ara R, Wailoo A, Manca A, Alava MH, Abrams K, et al. Good practice guidelines for the use of statistical regression models in economic evaluations. PharmacoEconomics. 2013;31: 643--652. doi:\href{https://doi.org/10.1007/s40273-013-0069-y}{10.1007/s40273-013-0069-y}}

\leavevmode\vadjust pre{\hypertarget{ref-ready4gh2022}{}}%
\CSLLeftMargin{48. }%
\CSLRightInline{Orygen. ready4: A suite of authoring, modelling and prediction tools for exploring topics in young people's mental health {[}Internet{]}. 2022. Available: \url{https://github.com/ready4-dev/}}

\leavevmode\vadjust pre{\hypertarget{ref-ready4zen2022}{}}%
\CSLLeftMargin{49. }%
\CSLRightInline{Orygen. ready4: Open and modular mental health systems models {[}Internet{]}. 2022. Available: \url{https://zenodo.org/communities/ready4}}

\leavevmode\vadjust pre{\hypertarget{ref-ready4dv2022}{}}%
\CSLLeftMargin{50. }%
\CSLRightInline{Orygen. ready4: Open and modular mental health systems models {[}Internet{]}. 2022. Available: \url{https://dataverse.harvard.edu/dataverse/ready4)}}

\leavevmode\vadjust pre{\hypertarget{ref-ready42022}{}}%
\CSLLeftMargin{51. }%
\CSLRightInline{Hamilton MP. ready4: Implement open science computational models of mental health systems {[}Internet{]}. 2021. doi:\href{https://doi.org/10.5281/zenodo.5606250}{10.5281/zenodo.5606250}}

\leavevmode\vadjust pre{\hypertarget{ref-ready4class2022}{}}%
\CSLLeftMargin{52. }%
\CSLRightInline{Hamilton M, Wiesner G. ready4class: Author Ready4 framework modules {[}Internet{]}. 2022. doi:\href{https://doi.org/10.5281/zenodo.5640313}{10.5281/zenodo.5640313}}

\leavevmode\vadjust pre{\hypertarget{ref-ready4fun2022}{}}%
\CSLLeftMargin{53. }%
\CSLRightInline{Hamilton M, Wiesner G. ready4fun: Author and document functions that extend the Ready4 framework {[}Internet{]}. 2022. doi:\href{https://doi.org/10.5281/zenodo.5611779}{10.5281/zenodo.5611779}}

\leavevmode\vadjust pre{\hypertarget{ref-ready4pack2022}{}}%
\CSLLeftMargin{54. }%
\CSLRightInline{Hamilton M. ready4pack: Author r packages that extend the Ready4 framework {[}Internet{]}. 2022. doi:\href{https://doi.org/10.5281/zenodo.5644322}{10.5281/zenodo.5644322}}

\leavevmode\vadjust pre{\hypertarget{ref-ready4use2022}{}}%
\CSLLeftMargin{55. }%
\CSLRightInline{Hamilton M, Wiesner G. ready4use: Author, label and share Ready4 framework datasets {[}Internet{]}. 2022. doi:\href{https://doi.org/10.5281/zenodo.5644336}{10.5281/zenodo.5644336}}

\leavevmode\vadjust pre{\hypertarget{ref-ready4show2022}{}}%
\CSLLeftMargin{56. }%
\CSLRightInline{Hamilton M, Wiesner G. ready4show: Author literate programs to share insights from applying the Ready4 framework {[}Internet{]}. 2022. doi:\href{https://doi.org/10.5281/zenodo.5644568}{10.5281/zenodo.5644568}}

\leavevmode\vadjust pre{\hypertarget{ref-CRAN2022}{}}%
\CSLLeftMargin{57. }%
\CSLRightInline{Statistical Computing RF for. The comprehensive r archive network {[}Internet{]}. 2022. Available: \url{https://cran.r-project.org}}

\leavevmode\vadjust pre{\hypertarget{ref-hamilton_matthew_2022_6084467}{}}%
\CSLLeftMargin{58. }%
\CSLRightInline{Hamilton M, Gao C. {youthvars: Describe and Validate Youth Mental Health Datasets} {[}Internet{]}. Zenodo; 2022. doi:\href{https://doi.org/10.5281/zenodo.6084467}{10.5281/zenodo.6084467}}

\leavevmode\vadjust pre{\hypertarget{ref-hamilton_matthew_2022_6084824}{}}%
\CSLLeftMargin{59. }%
\CSLRightInline{Hamilton M, Gao C. Scorz: Score questionnaire item responses {[}Internet{]}. Zenodo; 2022. doi:\href{https://doi.org/10.5281/zenodo.6084824}{10.5281/zenodo.6084824}}

\leavevmode\vadjust pre{\hypertarget{ref-hamilton_matthew_2022_6116701}{}}%
\CSLLeftMargin{60. }%
\CSLRightInline{Hamilton M, Gao C. {specific: Specify Candidate Models for Representing Mental Health Systems} {[}Internet{]}. Zenodo; 2022. doi:\href{https://doi.org/10.5281/zenodo.6116701}{10.5281/zenodo.6116701}}

\leavevmode\vadjust pre{\hypertarget{ref-gao_caroline_2022_6130155}{}}%
\CSLLeftMargin{61. }%
\CSLRightInline{Gao C, Hamilton M. {TTU: Implement Transfer to Utility Mapping Algorithms} {[}Internet{]}. Zenodo; 2022. doi:\href{https://doi.org/10.5281/zenodo.6130155}{10.5281/zenodo.6130155}}

\leavevmode\vadjust pre{\hypertarget{ref-matthew_p_hamilton_2021_5646669}{}}%
\CSLLeftMargin{62. }%
\CSLRightInline{Hamilton MP, Gao CX. Youthu: Transform youth outcomes to health utility predictions {[}Internet{]}. Zenodo; 2022. doi:\href{https://doi.org/10.5281/zenodo.6210978}{10.5281/zenodo.6210978}}

\leavevmode\vadjust pre{\hypertarget{ref-hamilton_matthew_2022_6129906}{}}%
\CSLLeftMargin{63. }%
\CSLRightInline{Hamilton M, Gao C. {Complete study program to reproduce all steps from data ingest through to results dissemination for a study to map mental health measures to AQoL-6D health utility} {[}Internet{]}. Zenodo; 2022. doi:\href{https://doi.org/10.5281/zenodo.6212704}{10.5281/zenodo.6212704}}

\leavevmode\vadjust pre{\hypertarget{ref-hamilton_matthew_2022_6416330}{}}%
\CSLLeftMargin{64. }%
\CSLRightInline{Hamilton M, Gao C. {aqol6dmap\_use: Apply AQoL-6D Utility Mapping Models To New Data} {[}Internet{]}. Zenodo; 2022. doi:\href{https://doi.org/10.5281/zenodo.6416330}{10.5281/zenodo.6416330}}

\leavevmode\vadjust pre{\hypertarget{ref-hamilton_matthew_p_2022_6321821}{}}%
\CSLLeftMargin{65. }%
\CSLRightInline{Hamilton MP. {aqol6dmap\_fakes: Generate fake input data for an AQoL-6D mapping study} {[}Internet{]}. Zenodo; 2022. doi:\href{https://doi.org/10.5281/zenodo.6321821}{10.5281/zenodo.6321821}}

\leavevmode\vadjust pre{\hypertarget{ref-hamilton_matthew_2022_6116385}{}}%
\CSLLeftMargin{66. }%
\CSLRightInline{Hamilton M. {ttu\_mdl\_ctlg: Generate a template utility mapping (transfer to utility) model catalogue} {[}Internet{]}. Zenodo; 2022. doi:\href{https://doi.org/10.5281/zenodo.6116385}{10.5281/zenodo.6116385}}

\leavevmode\vadjust pre{\hypertarget{ref-matthew_p_hamilton_2022_5976988}{}}%
\CSLLeftMargin{67. }%
\CSLRightInline{Hamilton MP. {ready4-dev/ttu\_lng\_ss: Create a Draft Scientific Manuscript For A Utility Mapping Study} {[}Internet{]}. Zenodo; 2022. doi:\href{https://doi.org/10.5281/zenodo.5976988}{10.5281/zenodo.5976988}}

\leavevmode\vadjust pre{\hypertarget{ref-DVNux2fDKDIB0_2021}{}}%
\CSLLeftMargin{68. }%
\CSLRightInline{Hamilton MP, Gao CX, Filia KM, Menssink JM, Sharmin S, Telford N, et al. {Transfer to AQoL-6D Utility Mapping Algorithms} {[}Internet{]}. Harvard Dataverse; 2021. doi:\href{https://doi.org/10.7910/DVN/DKDIB0}{10.7910/DVN/DKDIB0}}

\leavevmode\vadjust pre{\hypertarget{ref-DVNux2fHJXYKQ_2021}{}}%
\CSLLeftMargin{69. }%
\CSLRightInline{Hamilton MP. {Synthetic (fake) youth mental health datasets and data dictionaries} {[}Internet{]}. Harvard Dataverse; 2021. doi:\href{https://doi.org/10.7910/DVN/HJXYKQ}{10.7910/DVN/HJXYKQ}}

\leavevmode\vadjust pre{\hypertarget{ref-Hamilton2021.07.07.21260129}{}}%
\CSLLeftMargin{70. }%
\CSLRightInline{Hamilton MP, Gao CX, Filia KM, Menssink JM, Sharmin S, Telford N, et al. Predicting quality adjusted life years in young people attending primary mental health services. medRxiv. Cold Spring Harbor Laboratory Press; 2021; doi:\href{https://doi.org/10.1101/2021.07.07.21260129}{10.1101/2021.07.07.21260129}}

\leavevmode\vadjust pre{\hypertarget{ref-hamilton_matthew_2022_6627995}{}}%
\CSLLeftMargin{71. }%
\CSLRightInline{Hamilton M. {dce\_sa\_design: An R Markdown program to create the experimental design for a Discrete Choice Experiment (DCE) exploring online help seeking in socially anxious young people} {[}Internet{]}. Zenodo; 2022. doi:\href{https://doi.org/10.5281/zenodo.6627995}{10.5281/zenodo.6627995}}

\leavevmode\vadjust pre{\hypertarget{ref-DVNux2fV3OKZV_2022}{}}%
\CSLLeftMargin{72. }%
\CSLRightInline{Hamilton M. {Springtides reports for Local Government Areas in the North West of Melbourne} {[}Internet{]}. Harvard Dataverse; 2022. doi:\href{https://doi.org/10.7910/DVN/V3OKZV}{10.7910/DVN/V3OKZV}}

\leavevmode\vadjust pre{\hypertarget{ref-RN33}{}}%
\CSLLeftMargin{73. }%
\CSLRightInline{Hamilton MP, Hetrick SE, Mihalopoulos C, Baker D, Browne V, Chanen AM, et al. Identifying attributes of care that may improve cost-effectiveness in the youth mental health service system. Med J Aust. 2017;207: S27--S37. doi:\href{https://doi.org/10.5694/mja17.00972}{10.5694/mja17.00972}}

\leavevmode\vadjust pre{\hypertarget{ref-rfwn2022}{}}%
\CSLLeftMargin{74. }%
\CSLRightInline{Orygen. ready4-dev - documenting the development of an open souce youth mental health systems model {[}Internet{]}. Available: \url{https://ready4-dev.com/}}

\leavevmode\vadjust pre{\hypertarget{ref-RN8}{}}%
\CSLLeftMargin{75. }%
\CSLRightInline{Bloom DE, Cafiero ET, Jané-Llopis E, Abrahams-Gessel S, Bloom LR, Fathima S, et al. The global economic burden of noncommunicable diseases. 91-93 route de la Capite,CH-1223 Cologny/Geneva,Switzerland: World Economic Forum.; 2011. }

\leavevmode\vadjust pre{\hypertarget{ref-GBD2019}{}}%
\CSLLeftMargin{76. }%
\CSLRightInline{Global, regional, and national burden of 12 mental disorders in 204 countries and territories, 1990\&\#x2013;2019: A systematic analysis for the global burden of disease study 2019. The Lancet Psychiatry. 2022;9: 137--150. doi:\href{https://doi.org/10.1016/S2215-0366(21)00395-3}{10.1016/S2215-0366(21)00395-3}}

\leavevmode\vadjust pre{\hypertarget{ref-RN25}{}}%
\CSLLeftMargin{77. }%
\CSLRightInline{Chisholm D, Sweeny K, Sheehan P, Rasmussen B, Smit F, Cuijpers P, et al. Scaling-up treatment of depression and anxiety: A global return on investment analysis. The Lancet Psychiatry. 2016; doi:\href{https://doi.org/10.1016/s2215-0366(16)30024-4}{10.1016/s2215-0366(16)30024-4}}

\leavevmode\vadjust pre{\hypertarget{ref-RN22}{}}%
\CSLLeftMargin{78. }%
\CSLRightInline{Saxena S, Thornicroft G, Knapp M, Whiteford H. Resources for mental health: Scarcity, inequity, and inefficiency. The Lancet. 370: 878--889. doi:\href{https://doi.org/10.1016/S0140-6736(07)61239-2}{10.1016/S0140-6736(07)61239-2}}

\leavevmode\vadjust pre{\hypertarget{ref-RN23}{}}%
\CSLLeftMargin{79. }%
\CSLRightInline{Whiteford H, Ferrari A, Degenhardt L. Global burden of disease studies: Implications for mental and substance use disorders. Health Affairs. 2016;35: 1114--1120. doi:\href{https://doi.org/10.1377/hlthaff.2016.0082}{10.1377/hlthaff.2016.0082}}

\leavevmode\vadjust pre{\hypertarget{ref-20211700}{}}%
\CSLLeftMargin{80. }%
\CSLRightInline{Santomauro DF, Mantilla Herrera AM, Shadid J, Zheng P, Ashbaugh C, Pigott DM, et al. Global prevalence and burden of depressive and anxiety disorders in 204 countries and territories in 2020 due to the COVID-19 pandemic. The Lancet. 2021;398: 1700--1712. doi:\url{https://doi.org/10.1016/S0140-6736(21)02143-7}}

\leavevmode\vadjust pre{\hypertarget{ref-page_howard_2010}{}}%
\CSLLeftMargin{81. }%
\CSLRightInline{Page LA, Howard LM. The impact of climate change on mental health (but will mental health be discussed at copenhagen?). Psychological Medicine. Cambridge University Press; 2010;40: 177--180. doi:\href{https://doi.org/10.1017/S0033291709992169}{10.1017/S0033291709992169}}

\leavevmode\vadjust pre{\hypertarget{ref-RN11}{}}%
\CSLLeftMargin{82. }%
\CSLRightInline{Organization WH, Foundation CG. Social determinants of mental health. Geneva: World Health Organization; 2014. }

\leavevmode\vadjust pre{\hypertarget{ref-Fried2020}{}}%
\CSLLeftMargin{83. }%
\CSLRightInline{Fried EI, Robinaugh DJ. Systems all the way down: Embracing complexity in mental health research. BMC Medicine. 2020;18: 205. doi:\href{https://doi.org/10.1186/s12916-020-01668-w}{10.1186/s12916-020-01668-w}}

\leavevmode\vadjust pre{\hypertarget{ref-RN2111}{}}%
\CSLLeftMargin{84. }%
\CSLRightInline{Langellier BA, Yang Y, Purtle J, Nelson KL, Stankov I, Diez Roux AV. Complex systems approaches to understand drivers of mental health and inform mental health policy: A systematic review. Administration And Policy In Mental Health. 2018; doi:\href{https://doi.org/10.1007/s10488-018-0887-5}{10.1007/s10488-018-0887-5}}

\leavevmode\vadjust pre{\hypertarget{ref-RN26}{}}%
\CSLLeftMargin{85. }%
\CSLRightInline{Jorm AF, Patten SB, Brugha TS, Mojtabai R. Has increased provision of treatment reduced the prevalence of common mental disorders? Review of the evidence from four countries. World psychiatry : official journal of the World Psychiatric Association (WPA). 2017;16: 90--99. doi:\href{https://doi.org/10.1002/wps.20388}{10.1002/wps.20388}}

\leavevmode\vadjust pre{\hypertarget{ref-RN42}{}}%
\CSLLeftMargin{86. }%
\CSLRightInline{Furst MA, Gandré C, Romero López-Alberca C, Salvador-Carulla L. Healthcare ecosystems research in mental health: A scoping review of methods to describe the context of local care delivery. BMC Health Services Research. 2019;19: 173. doi:\href{https://doi.org/10.1186/s12913-019-4005-5}{10.1186/s12913-019-4005-5}}

\leavevmode\vadjust pre{\hypertarget{ref-RN43}{}}%
\CSLLeftMargin{87. }%
\CSLRightInline{Alegría M, NeMoyer A, Falgàs Bagué I, Wang Y, Alvarez K. Social determinants of mental health: Where we are and where we need to go. Current Psychiatry Reports. 2018;20: 95--95. doi:\href{https://doi.org/10.1007/s11920-018-0969-9}{10.1007/s11920-018-0969-9}}

\leavevmode\vadjust pre{\hypertarget{ref-nmhsmn2022}{}}%
\CSLLeftMargin{88. }%
\CSLRightInline{Mental Health Research QC for. National mental health systems modelling network {[}Internet{]}. 2022. Available: \url{https://qcmhr.org/research/research-streams/mental-health-services-research/national-mental-health-systems-modelling-network/}}

\leavevmode\vadjust pre{\hypertarget{ref-Zabell2021}{}}%
\CSLLeftMargin{89. }%
\CSLRightInline{Zabell T, Long KM, Scott D, Hope J, McLoughlin I, Enticott J. Engaging healthcare staff and stakeholders in healthcare simulation modeling to better translate research into health impact: A systematic review. Frontiers in Health Services. 2021;1. doi:\href{https://doi.org/10.3389/frhs.2021.644831}{10.3389/frhs.2021.644831}}

\leavevmode\vadjust pre{\hypertarget{ref-SQUIRES2016588}{}}%
\CSLLeftMargin{90. }%
\CSLRightInline{Squires H, Chilcott J, Akehurst R, Burr J, Kelly MP. A framework for developing the structure of public health economic models. Value in Health. 2016;19: 588--601. doi:\url{https://doi.org/10.1016/j.jval.2016.02.011}}

\end{CSLReferences}

\newpage
\appendix
\counterwithin{figure}{section}
\counterwithin{table}{section}

\end{document}

### 2023-01-24 setup.R

@@ -37,14 +37,14 @@ X <- renewSlot(X,
                "abstract_args_ls",
                {
                  args_ls <- X@abstract_args_ls
-                 args_ls$abstract_ls <- list(Summary = "Despite growing support for open source health economic models (OSHEMs), uptake remains limited. 
-                                             The deployment of modular approaches to model development is also relatively underdeveloped compared to other disciplines.
-                                             In this article, we propose a framework for developing a modular OSHEM in youth mental health and describe our preliminary efforts to apply this framework to develop youth specific utility mapping models.
-                                             The framework includes a set of X1 good practice standards and software for implementing a model that is accountable (X2 standards), reusable (X3 standards) and upatable (X4 standards). 
+                 args_ls$abstract_ls <- list(Summary = "Compared to other disciplines, health economics rarely uses modular approaches to model development that facilitate re-use of model components. 
+                                             Although interest in open source health economic models (OSHEMs) is growing, uptake remains limited.
+                                             We propose a framework for a modular OSHEM in youth mental health.
+                                             The framework includes of set of X1 good practice standards for implementing a model that is accountable (X2 standards), reusable (X3 standards) and upatable (X4 standards). 
                                              We provide a rationale for each standard.
-                                             The framework also includes a software toolkit comprised of six novel R packages for authoring models, supplying those models with data and using those models to implement reproducible analyses. 
-                                             We describe an early application of this toolkit to developing utility mapping models that meet X5 framework standards. 
-                                             We discuss the potential benefits and challenges of extending this initial work to develop a more extensive model for undertaking economic evaluations in youth mental health.",
+                                             The framework also includes software toolkit of six R packages for authoring model modules (data structures and algorithms), supplying those modules with data and using the modules to implement reproducible modelling analyses. 
+                                             We describe an early application of the framework to developing utility mapping models that meet X5 standards. 
+                                             We discuss the potential benefits and challenges of extending this initial work to develop a more extensive model for undertaking economic analyses in youth mental health.",
                                              # Objectives = "We aimed to develop a conceptual and technical framework for implementing open source mental health systems models and illustrate how it can be applicatied to economic topics in youth mental health.",
                                              # Methods = "We created a software development kit in R to support standardised implementation of mental health systems models. As a worked example, we applied the toolkit to develop open source youth mental health utility mapping models, which we assessed against five principles using 17 standards.",
[…]

### 2023-01-24 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
end of day

@@
 More complex models may be more prone to propagation errors [@Saltelli2019] and models designed to address multiple questions should be expected to meet more onerous verification and validation obligations [@Eddy2012; @Feenstra2022].
-The nature and extent of individual model authorship contributions may be less clear in models implemented over longer time-frames with a large and changing group of collaborators [@thompson2022].
+The nature and extent of individual model authorship contributions may be less clear in models implemented over longer time-frames with a large and changing group of collaborators [@thompson2022escape].
 
@@
 <!-- As modelling methods have become more sophisticated, some have argued that more complex models are required to adequately explore certain types of public health topics [@SQUIRES2016588].  -->
-
 <!-- Accountability for both the scientific quality and social acceptability of health economic models can be improved.  -->
@@
 Use of concepts with standardised meanings across jurisdictions [@garcia2021cost], supplying context specific data as replaceable data-packs and distributing source code under licenses that allow derivative works are all steps that can enhance model transferability.
+
 <!-- [https://doi.org/10.1017/S026646232200321X].  -->

### 2023-01-25 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
up to fw

--- 2023-01-23 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
@@
 <!-- Add aims text here -->
-In this paper, we introduce a framework for developing youth mental health OSHEMs. Specifically we describe:
+In this paper, we introduce a framework for developing a modular youth mental health MOSHEM. Specifically we:
 
-- a set of guidelines for implementing OSHEMs;
+(i) describe a framework that is comprised of:
+  - a set of standards for implementing a MOSHEM; and
+  - a modelling toolkit (repositories and software) to author MOSHEM modules, supply them with data and undertake reproducible analyses consistent with those standards.
 
-- a toolkit for applying these guidelines in youth mental health; and
-
-- a worked example of a modelling project developed with the toolkit.
+(ii) provide a worked example of how we used the framework to develop and apply MOSHEM modules for utility mapping.
 

### 2023-01-25 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
up to fw

@@
 
-Guidelines on health economic model transparency were published ten years ago [@Eddy2012] and made recommendations on documenting models; however, notably missing were recommendations on the sharing of model code and data.
-More recent and more general modelling guidance [@Erdemir2020] recommends the sharing of code and data through digital repository services <!-- such as GitHub [@github2007] and Zenodo [@Zenodo2013] --> and the use of version control systems.
-<!-- such as Git [@git20XX].
---> Based on these and other existing sources of guidance and our own experience, we propose 20 guidelines for implementing OSHEMs that are **TIMELY** (Transparent, Iterative, Modular, Epitomising, Licensed and Yielding - see Table \@ref(tab:timelygls)).
+Based on published guidance on computational modelling in health economics and other disciplines and our own experience, we have identified 20 standards that we believe are important for implementing a MOSHEM that is accountable (seven standards), reusable (nine standards) and updatable (four standards).
+The standards are specified in Table \@ref(tab:timelygls) and are discussed below.
 
@@
 
-## Transparent models
-A range of tools and practices are available to help make models more transparent.
-The most efficient way to widely disseminate code and data may be to use existing open science infrastructure [@Erdemir2020] to make permanently accessible and uniquely identfied digital artefacts.
-<!-- Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each unique item.
-These repositories are a preferable solution for sharing citable code and data than transitory repositories such as corporate websites or GitHub where items can be deleted or relocated at any time [@sseditors2022].
-Zenodo includes tools that automate integration with GitHub, which makes it easy for developers to maintain parallel code repositories - one for disseminating the most up to date development code and the other for archiving citable code releases.
--->Model code and data also need to be clearly documented, potentially with different versions for technical and non-technical users [@Eddy2012].
-<!-- Developers storing data in a Dataverse installation have access to multiple meta-data fields to document both a data collection and its individual constituent files.
---><!-- In R, code manuals and websites can be created with the aid of tools such as devtools [@devtools2021], sinew [@sinew2022], roxygen2 [@roxygen2021] and pkgdown [@pkgdown2022].
--->Consistent use of meaningful naming conventions when authoring code is recommended [@Wilson_2017; @Alarid2019].
+### Standards for an accountable MOSHEM
+Guidance on transparency in health economic modelling published over ten years ago [@Eddy2012] made recommendations on documenting models but notably did not include recommendations on sharing model code and data.
+However, more recent and multidisciplinary healthcare modelling guidance [@Erdemir2020] recommends using existing digital repository services to these types of digital model artefacts.
+Some types of repository such as GitHub [@github2007] provide tools for disseminating work in progress code and providing highly transparent records of the complete development history and individual authorship contributions of a software project, while others such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each code and data collection.
+
+Model code and data should be clearly documented, potentially with different versions for technical and non-technical users [@Eddy2012].
+<!-- nd --> Consistent use of meaningful naming conventions when authoring code is recommended [@Wilson_2017; @Alarid2019].
 Code can be made easier to follow by using the practices of abstraction [@8717448], where only simple, high level commands are routinely exposed to reviewers, and polymorphism [@7181447], where the same command (e.g.
 "simulate") can be reused to implement different algorithms of the same type.
-Programs to implement model analyses can be made comprehensible to even non-technical users through the use of literate programming techniques <!-- that use tools like RMarkdown [@xie2018r]  -->to render documents that integrate computer code with plain English descriptions.
+Programs to implement model analyses can be made comprehensible to even non-technical users through the use of literate programming techniques <!-- that use tools like RMarkdown [@xie2018r]  -->that integrate computer code with plain English descriptions.
 
@@
 <!-- In R, the testthat [@testthat2011] and covr [@covr2020] tools can be used in conjunction with GitHub to define tests and report coverage metrics.
--->Finally, transcription errors - mistakes introduced when transferring data between sources, models and reports - are very common in health economic models [@Radeva2020].
+-->Transcription errors - mistakes introduced when transferring data between sources, models and reports - are very common in health economic models [@Radeva2020].
 The risk of these errors might be lower if there was full transparency across all steps in a study workflow.
 Scientific computing tools now make it relatively straightforward to author programs that reproducibly execute all steps in data ingest, processing and reporting [@Wilson_2017].
+
+Code and data should be distributed with tools that make it easy for potential users to appropriately cite each model artefact.
 
@@
 
-## Iterative models
-To avoid OSHEMs going stale - losing validity and usefulness with time - they should be routinely updated.
-Each update of code and data should be uniquely identifiable and retrievable, a goal that can be facilitated by use of version control tools [@Erdemir2020].<!-- A number of tools and approaches can make the process of implementing and curating changes to model code and data more coherent and efficient.
+<!-- - **L3: Model code and data are distributed with tools to support appropriate citation** <!-- New -->
+
+<!-- and the use of version control systems. <!-- such as Git [@git20XX].  -->  
+<!-- Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each unique item.
+These repositories are a preferable solution for sharing citable code and data than transitory repositories such as corporate websites or GitHub where items can be deleted or relocated at any time [@sseditors2022].
+Zenodo includes tools that automate integration with GitHub, which makes it easy for developers to maintain parallel code repositories - one for disseminating the most up to date development code and the other for archiving citable code releases.
+--> <!-- Developers storing data in a Dataverse installation have access to multiple meta-data fields to document both a data collection and its individual constituent files.
+--><!-- In R, code manuals and websites can be created with the aid of tools such as devtools [@devtools2021], sinew [@sinew2022], roxygen2 [@roxygen2021] and pkgdown [@pkgdown2022].
+-->
+
+### Standards for a reusable MOSHEM
+<!-- ## Licensed models -->
+```{r echo = F}
+gpl_pc_dbl <- get_license_share("GPL")
+```
+
+To make model code and data widely re-usable by others, it is important to provide users with appropriate and explicit permissions.
+In the context of open source models, there are two broad categories of licensing options.
+Some guidance strongly recommends the use of permissive licensing [@Wilson_2017] that provides users with great flexibility as to the purposes (including commercial) for which the content could be re-used.
+An alternative approach is to use copyleft licenses [@copyleft2022] that can require content users to distribute any derivative works they create under similar open source arrangements.
+For code, it may be appropriate to adopt the prevailing open source licensing practice within the programming language being used.
+For data, it may not be sufficient to simply choose between a permissive license like the Public Domain Dedication (CC0) [@cc02022] or a copyleft option such as the Attribution-Share Alike (CC-BY-SA) [@bysa2022].
+In addition to ensuring that data is ethically appropriate for disseminate in open access repositories, responsible custodianship of some de-identified or aggregated data may involve using or adapting template terms of use [@sampleterms2022] which have a number of ethical clauses (for example, prohibiting efforts to re-identify research participants).
+
+Storing and managing model code and data separately, can make it easier to apply models to different decision contexts and, when necessary, to selectively restrict access to data that are confidential, while disseminating all other model artefacts.
+Clear distinctions should be made between model modules (code that defines abstract data structures and the algorithms that can be applied to data described by these structures), model datasets (digital information such as parameter values, unit records, etc) and model analyses (code that specifies the data to be supplied to modules and selects which module algorithms to apply to that data).
+
+The coding practice of encapsulation [@8717448] can be used to help ensure that model modules can be safely combined [@ready4oop2022].
+In some cases, combining modules may mean new versions of modules have to be created that account for their effects on each other.
+The coding concept of inheritance [@8717448] can be used to efficiently achieve this objective as well as to facilitate selective editing of modules when transferring models to different decision contexts [@ready4oop2022].
+Writing algorithms as collections of functions (short, self-contained and reusable software routines that each perform a discrete task) is recommended as good practice for scientific computing [@Wilson_2017].
+Functions to implement model algorithms can be associated with module data structures (also known as a class) via a special type of function called a method.
+Model modules of a similar type or purpose can be efficiently distributed and documented by bundling them as code libraries.
+It is good practice to make available test or toy data to demonstrate the use of model algorithms [@Wilson_2017].
+
+<!-- When bundled for distribution as libraries<!-- (for example, as R packages) -->
+<!-- , functions have the potential to be widely re-used, often in contexts very different than those they were originally developed for.  --> 
+<!-- A special type of function, called a method, can only be applied to a pre-defined class of data structure.  -->
+
+<!-- ## Yielding models --><!-- MOSHEMs can be time and skills intensive for modellers to develop - but they should be easy for others to use.  -->
+Statistical models are a common output of health economic evaluations, but they are often not reported in a format that enables others to confidently and reliably re-use them [@Kearns2013].
+Open source approaches can help address this by disseminating code artefacts that enable easy and appropriate use of a statistical model to make predictions with new data.
+However, great care must be exercised when doing so if models are derived from data on human subjects as some software artefacts by default contain a copy of the source dataset.
+Such dataset copies must therefore be replaced (for example, with synthetic data) and the amended artefact's predictive performance then retested before any public release.
+Another way to make MOSHEMs easier to use is to develop simple user-interfaces for non-technical users.
+In the open source R language, such user-interfaces are typically developed with the Shiny package, for which a tutorial aimed at health economists is available [@SmithR2020].
+
+<!-- Applying a previously published algorithm [@kross2016] to analyse the most comprehensive archive of released R packages [@CRAN2022] finds that `r gpl_pc_dbl`% are distributed under various forms of General Public License (GPL) [@GNUGPL2022], a copyleft license.
+-->
+<!-- In R, including a CITATION file in the `inst` directory of a package will enable users of that package to retrieve citation information by running a command of the format `citation("Package Name")` in the R console [@Salmon2021].
+More generally, including a CITATION.cff file at the top level of your code repository will enable GitHub and Zenodo repositories hosting that item to include the relevant information in their citation tools [@Druskat_Citation_File_Format_2021].
+Datasets hosted on Dataverse installations have metadata fields that, once completed by authors, generate citation files for dataset viewers.
+-->
+
+<!-- A key challenge to generalising health economic models is that they are typically developed to inform a decision problem with a highly specific jurisdictional context.
+However, a number of choices about how these models are implemented can significantly increase the re-usability of model code in other contexts.
+-->
+<!-- For example, when generalising a model developed for the Australian context to a UK context, one could create a class that initially inherits all of the methods defined for the Australian model and then write new or replacement methods as needed for the UK model.
+-->
+<!-- Guidelines: -->
+
+<!-- - **L1: Model code is made available for re-use under copyleft or permissive licenses** -->
+
+<!-- - **L2: Non-confidential model data is licensed for liberal re-use (subject to additional terms for de-identified human data)** -->
+
+<!-- - **E2: Model code defines inheriting data-structures** --> <!-- Order changed-->
+
+<!-- - **E1: Model code is distributed as libraries of classes and functions**  <!-- Modified (lost ref to OOP and merged with M2) -->
+
+<!-- - **E3: Test data is available to demonstrate generalised applications of model code** -->
+
+<!-- - **M1: Model code and data are stored and managed separately** <!-- Modified (lost ref to licensed and cited) -->
+
+<!-- - **M2: Model code defines encapsulating data structures** <!--Replacement - Old version now merged with E1 -->
+
+<!-- - **Y1: Statistical models are distributed with validated tools to support their safe and appropriate re-use** <!-- New, Replaces Old Y1 (now Y2) --> 
+<!-- - **Y2: Simple user-interfaces allow non-technical users to configure and run models ** <!-- Was Y1 -->
+
+### Standards for an updatable MOSHEM
+To avoid MOSHEMs going stale - losing validity and usefulness with time - they should be routinely updated.
+Each update of code and data should be uniquely identifiable and retrievable, a goal that can be facilitated by use of version control tools [@Erdemir2020].
+Labeling each change using semantic versioning [@semver20xx] conventions can signal the potential importance of an update to users of model code and data.
+Continuous integration [@CI2017] tools can help verify that each code update passes multiple quality tests.
+Finally, using deprecation conventions that take an informative and staged approach to retiring old code and data reduces the risk that model revisions have unintended consequences on third party users.
+
+<!-- A number of tools and approaches can make the process of implementing and curating changes to model code and data more coherent and efficient.
 <!-- Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent access to all published versions of a dataset, each uniquely identifiable.
@@
 The online platform GitHub [@github2007] can make this version history accessible to anyone.
--->Labeling each change using semantic versioning [@semver20xx] conventions can signal the potential importance of an update to users of model code and data.
+-->
+
 <!-- For R code, the usethis [@usethis2021] package can be used to partially automate version number increments using the convention Major.Minor.Patch.Development (e.g.
@@
 Datasets stored on the Harvard Dataverse use the simpler Major.Minor convention.
--->Continuous integration [@CI2017] tools can help verify that each code update passes multiple quality tests.
-<!-- OSHEMs developed in R can take advantage of templates provided by devtools [@devtools2021] and pkgdown [@pkgdown2022] to run continuous integration checks on GitHub.
+-->
+<!-- MOSHEMs developed in R can take advantage of templates provided by devtools [@devtools2021] and pkgdown [@pkgdown2022] to run continuous integration checks on GitHub.
 --><!-- These tests can include those of units (do individual functions produce expected output?), documentation (does documentation render correctly?; can all example workflows be executed?) and installation (can the software be successfully deployed on multiple types of operating system?).
 -->
-Finally, using deprecation conventions that take an informative and staged approach to retiring old code and data reduces the risk that model revisions have unintended consequences on third party users.
+
 <!-- The package lifeycle [@lifecycle2021] provides tools for R developers to consistently deprecate their code. -->
@@
 <!-- - **I4: Deprecation conventions are used to retire model code and data** -->
-
-## Modular models
-An important consideration when combining model components (or modules) is to ensure that interactions between two modules do not compromise the validity of either.
-Using the coding practice of encapsulation [@8717448] can help ensure that model modules can be safely combined [@ready4oop2022].
-
-<!-- Guidelines: -->
-
-<!-- - **M1: Model code and data are stored and managed separately** <!-- Modified (lost ref to licensed and cited) -->
-
-<!-- - **M2: Model code defines encapsulating data structures** <!--Replacement - Old version now merged with E1 -->
-
-## Epitomising models
-A key challenge to generalising health economic models is that they are typically developed to inform a decision problem with a highly specific jurisdictional context.
-However, a number of choices about how these models are implemented can significantly increase the re-usability of model code in other contexts.
-
-Writing code as collections of functions (short, self-contained and reusable algorithms that each perform a discrete task) is recommended as good practice for scientific computing [@Wilson_2017].
-When bundled for distribution as libraries<!-- (for example, as R packages) -->, functions have the potential to be widely re-used, often in contexts very different than those they were originally developed for.
-A special type of function, called a method, can only be applied to a pre-defined class of data structure.
-Due to the coding concept of inheritance [@8717448], the more restricted nature of methods can be used to enhance the re-usability of model code in different decision contexts [@ready4oop2022].
-For example, when generalising a model developed for the Australian context to a UK context, one could create a class that initially inherits all of the methods defined for the Australian model and then write new or replacement methods as needed for the UK model.Whatever type of functions are written for a modelling project, it is good practice to make available test or toy data to demonstrate their use [@Wilson_2017].
-
-<!-- Guidelines: -->
-
-<!-- - **E1: Model code is distributed as libraries of classes and functions**  <!-- Modified (lost ref to OOP and merged with M2) -->
-
-<!-- - **E2: Model code defines inheriting data-structures** -->
-
-<!-- - **E3: Test data is available to demonstrate generalised applications of model code** -->
-
-## Licensed models
-```{r echo = F}
-gpl_pc_dbl <- get_license_share("GPL")
-```
-
-To make model code and data widely re-usable by others, it is important to provide users with appropriate and explicit permissions.
-In the context of open source models, there are two broad categories of licensing options.
-Some guidance strongly recommends the use of permissive licensing [@Wilson_2017] that provides users with great flexibility as to the purposes (including commercial) for which the content could be re-used.
-An alternative approach is to use copyleft licenses [@copyleft2022] that can require content users to distribute any derivative works they create under similar open source arrangements.The most suitable approach may differ for code and data.
-
-For code, it may be appropriate to adopt the prevailing open source licensing practice within the programming language being used.
-<!-- Applying a previously published algorithm [@kross2016] to analyse the most comprehensive archive of released R packages [@CRAN2022] finds that `r gpl_pc_dbl`% are distributed under various forms of General Public License (GPL) [@GNUGPL2022], a copyleft license.
--->For data, it may not be sufficient to simply choose between a permissive license like the Public Domain Dedication (CC0) [@cc02022] or a copyleft option such as the Attribution-Share Alike (CC-BY-SA) [@bysa2022].
-Responsible custodianship of some de-identified mental health data may involve using or adapting template terms of use [@sampleterms2022] which have a number of ethical clauses (for example, prohibiting efforts to re-identify research participants).
-Licenses may or may not specify that model re-users must give appropriate acknowledgement to model authors.
-Citation tools can be distributed with each individual code or data item to inform re-users of the desired attribution.
-<!-- In R, including a CITATION file in the `inst` directory of a package will enable users of that package to retrieve citation information by running a command of the format `citation("Package Name")` in the R console [@Salmon2021].
-More generally, including a CITATION.cff file at the top level of your code repository will enable GitHub and Zenodo repositories hosting that item to include the relevant information in their citation tools [@Druskat_Citation_File_Format_2021].
-Datasets hosted on Dataverse installations have metadata fields that, once completed by authors, generate citation files for dataset viewers.
--->
-
-<!-- Guidelines: -->
-
-<!-- - **L1: Model code is made available for re-use under copyleft or permissive licenses** -->
-
-<!-- - **L2: Non-confidential model data is licensed for liberal re-use (subject to additional terms for de-identified human data)** -->
-
-<!-- - **L3: Model code and data are distributed with tools to support appropriate citation** <!-- New -->
-
-## Yielding models
-OSHEMs can be time and skills intensive for modellers to develop - but they should be easy for others to use.
-Statistical models are a common output of health economic evaluations, but they are often not reported in a format that enables others to confidently and reliably re-use them [@Kearns2013].
-Open source approaches can help address this by disseminating code artefacts that enable easy and appropriate use of a statistical model to make predictions with new data.
-However, great care must be exercised when doing so if models are derived from data on human subjects as some software artefacts by default contain a copy of the source dataset.
-Such dataset copies must therefore be replaced (for example, with synthetic data) and the amended artefact's predictive performance then retested before any public release.
-Another way to make OSHEMs easier to use is to develop simple user-interfaces for non-technical users.
-<!-- In R, such user-interfaces are typically developed with the Shiny package, for which a tutorial aimed at health economists is available [@SmithR2020]. -->
-
-<!-- Guidelines: -->
-
-<!-- - **Y1: Statistical models are distributed with validated tools to support their safe and appropriate re-use** <!-- New, Replaces Old Y1 (now Y2) --> 
-<!-- - **Y2: Simple user-interfaces allow non-technical users to configure and run models ** <!-- Was Y1 -->

### 2023-01-25 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
up to fw

@@
 <!-- # Framework -->
-<!-- The framework we have developed to implement **readyforwhatsnext** specifies standards for OSHEMs and provides tools for meeting those standards. -->
+<!-- The framework we have developed to implement **readyforwhatsnext** specifies standards for MOSHEMs and provides tools for meeting those standards. -->
 
-We have developed a toolkit to help streamline the process of developing OSHEMs that meet the TIMELY standards. The toolkit is comprised of online repositories and software.
+We have developed a toolkit to help streamline the process of developing and using MOSHEMs that meet the standards listed in Table \@ref(tab:timelygls).
+The toolkit is comprised of online repositories and software.
 
@@
 We created a GitHub organisation where all framework software source code is stored, documented, version controlled and continuously integrated [@ready4gh2022].
-To store citable archived copies of release copies of our software, we created a Zenodo community [@ready4zen2022].
+That was linked to an account we set up at code codecov [@codecov_2022] for tracking our unit tests and the Zenodo community [@ready4zen2022] we created to store citable archived copies of release copies of our software.
 Finally, to manage datasets for use in models developed with the framework, we created a dedicated collection within the Harvard Dataverse  [@ready4dv2022].
@@
 
-A coding framework for OSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions [@Alarid2019].
+<!-- A coding framework for MOSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions [@Alarid2019]. -->
 
-As a foundation for implementing the framework, we authored a development version R package that defines a novel syntax and a template class for model modules [@ready42022].
+As a foundation for implementing our framework, we authored a development version R package that defines a template class for model module data structures [@ready42022] and a novel syntax for implementing the algorithms that will be attached to model modules.
 To enable the syntax and module template be applied to modelling projects, we then created five additional development version R packages that provide tools for authoring:
 
-- documented model modules [@ready4class2022];
+- documented model module data-structures [@ready4class2022];
 
@@
 
-- citable, quality assured R packages [@ready4pack2022];
+- citable, quality assured module libraries [@ready4pack2022];
 
@@
 
-The six R packages, their primary focus, the TIMELY standards they support and the third-party packages they depend on are summarised in Table \@ref(tab:cpkgs).
-When used in conjunction with framework repositories, the six packages extend existing R packages provide strong support for implementing 16 of the TIMELY standards.
-However, the software only weakly supports implementing the standards relating to disseminating statistical models (Y1) and user-interface development (Y2) and does not yet provide any workflow tools to help implement the standards for code coverage (T5) and deprecation conventions (I4).
+The six R packages, their primary focus, the framework standards they support and the third-party packages they depend on are summarised in Table \@ref(tab:cpkgs).
+When used in conjunction with framework repositories, the six packages extend existing R packages provide strong support for implementing 17 of the framework standards.
+However, the software only weakly supports implementing the standards relating to disseminating statistical models (Y1) and user-interface development (Y2) and does not yet provide any workflow tools to help implement the standard for deprecation conventions (I4).
 Standards not supported or weakly supported by our software can be met with existing developer tools in R and we plan to progressively integrate these third-party tools with our own in future releases of our software.

### 2023-01-25 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
up to fw

@@
 This goal is difficult to achieve in the current context of the poor reproducibility [@Jalali2021; @McManus2019; @Bermejo2017] and frequently insufficient validation [@Ghabri2019] of health economic models.
-Value judgments strongly shape health economic analyses, yet are rarely made explicit, omissions that may lead to socially unacceptable policy recommendations [@duckett2022journey].
+Many health economic models are released with undeclared errors [@Radeva2020].
+The value judgments that strongly shape health economic analyses are rarely made explicit, omissions that may lead to socially unacceptable policy recommendations [@duckett2022journey].
 A modelling team's value judgments about what questions to address, the most important features of a system to represent and the weighting of different types of evidence may be poorly aligned with those of the people impacted by decisions informed by model analyses [@thompson2022escape].
@@
 
-<!-- Many health economic models are released with errors [@Radeva2020]. -->
 <!-- As modelling methods have become more sophisticated, some have argued that more complex models are required to adequately explore certain types of public health topics [@SQUIRES2016588].  -->
@@
 
-Collaborative approaches that encourage re-use of models by other modellers can help make modelling pojects more tractable [@Arnold2010].
+The resource and skills intensive undertaking of modelling could be made more tractable if it was easier for health economists to re-use each other's models [@Arnold2010].
 However, as many health economic models are owned by pharmaceutical companies and consultancies, commercial considerations can limit the reuse of models and their constituent code and data [@Feenstra2022].
-Not all data included in health economic models can be ethically made publicly available due to privacy and confidentiality requirements.
-Transferring a health economic model developed for one jurisdiction for application in another will involve retaining some features and updating others [@barbieri2010international].
-Use of concepts with standardised meanings across jurisdictions [@garcia2021cost], supplying context specific data as replaceable data-packs and distributing source code under licenses that allow derivative works are all steps that can enhance model transferability.
+Legal and ethical issues such as privacy and confidentiality requirements further limit public release of some model artefacts [@Pouwels2022].
+Transferring a health economic model developed for one jurisdiction for application in another typically involves retaining some features and updating others [@barbieri2010international].
+However, models do not always make implementation choices (for example, use of concepts with standardised meanings across jurisdictions<!-- [@garcia2021cost] -->, supplying context specific data as replaceable data-packs and distributing source code under licenses that allow derivative works) that facilitate model transferability.
 
@@
 Health economic models should be updated and refined as new evidence emerges and decision contexts change [@Jenkins2021], but this occurs infrequently [@Sampson2017].
-Decision makers are frequently left to rely on economic analyses that become less valid and relevant each year.
-A model can grow stale when changes in the real world, whether sudden (e.g.
+Funding for health economic modelling projects rarely extend to provision of medium term support for model updates and improvements.
+The career trajectories of health economists can also mitigate against adequate maintenance of a model, it being relatively common for model authors to have moved on from the team that owns the model and / or from working on the health condition for which the model was developed.
+<!-- Decision makers are frequently left to rely on economic analyses that become less valid and relevant each year.A model can grow stale when changes in the real world, whether sudden (e.g.
 new pandemics) or gradual (e.g.
@@
 Even when the system being modelled remains relatively stable, new research findings may potentially invalidate aspects of a model's original conceptualisation and implementation.
-Funding for health economic modelling projects rarely extend to provision of medium term support for model updates and improvements.
-The career trajectories of health economists can also mitigate against adequate maintenance of a model, it being relatively common for model authors to have moved on from the team that owns the model and / or from working on the health condition for which the model was developed.
+-->
 
@@
 
-A modular approach to model building involves models being constructed by combining multiple replaceable sub-models (modules) [@pan2021modular].
-When used as model sub-components, modules communicate with other modules but they can be also run independently [@barros2023empowering].
+A modular model is constructed from multiple reusable and replaceable sub-models (modules) [@pan2021modular].
+Modules can share inputs and outputs with other modules or can be run as independent models [@barros2023empowering].
 Advantages of modular models include feasibility (large projects are broken into smaller tasks, with each component independently developed and tested) and flexibility (making it easier to selectively replace or update specific parts of a model and to scale up or down the level of granularity) [@pan2021modular].
 Modular approaches are currently being used to facilitate the development of complex computational models in disciplines such as biology [@pan2021modular], neuroscience [@frazier2022robust] and ecology [@barros2023empowering].
-Although the related and enabling concept of reusable reference models has been recommended in health economics [@Afzali2013], peer reviewed studies describing modular health economic models remain relatively rare, though examples exist in tuberculosis [@Trauer2017] and cardiology [@Urach2013].
-
-<!-- A modular approach that ensures that model code and data are decoupled (stored in different files) can help model developers to restrict access to confidential model data, while providing open access to all other model components.
--->
+In health economics the related and enabling concept of reference models has been recommended [@Afzali2013], but peer reviewed studies describing modular health economic models remain relatively rare, though examples exist in infectious disease [@Trauer2017] and cardiology [@Urach2013].
 
 <!-- Standardized and transferable approaches to health economic modelling have been recommended. [doi:10.1017/S0266462317000666] -->
-The benefits of modular models can be enhanced if multiple modelling teams have the capacity to contribute and use model modules.
-To facilitate this, modular models may be implemented as open source projects that grant liberal permissions to access and re-use model source code and data [@pan2021modular; @barros2023empowering; @frazier2022robust].
+Modular models provide an opportunity for multiple modelling teams to contribute to, test and reuse models.
+To enhance this capacity, modular models may be implemented as open source projects that give others liberal permissions to access and use model source code and data [@pan2021modular; @barros2023empowering; @frazier2022robust].
 Although there appears to be in principle support from many health economists for greater use of open source health economic models (OSHEMs)  [@Pouwels2022], actual implementations are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022].
@@
 
-We plan to develop a modular OSHEM of youth mental health.
+We plan to develop a modular OSHEM (MOSHEM) of youth mental health that is accountable, reusable and updatable.
 Open source approaches have been recommended to help develop the mental health modelling field [@RN73] but only one mental health related model (in Alcohol Use Disorder [@Basu2018]) is currently indexed [RECHECK] in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019].
-Other than our own work, we are aware of just one open source mental health reference model - in Major Depressive Disorder - that is currently in development [@IVIMDD2022].
+We  are aware of just one other open source mental health model - a reference model in Major Depressive Disorder - that is currently in development [@IVIMDD2022].
+
 <!-- that rarely explores complex dynamic systems  -->

### 2023-01-25 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
up to fw

--- 2022-07-25 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
@@
 <!-- Add child RMDs for results content -->
+# Framework
+<!-- Modular and open source models from other disciplines are enabled by standardisation and software.  -->
+To help us implement a MOSHEM in youth mental health, we have developed a framework that:
 
-# Guidelines
+- specifies a set of standards for MOSHEM development and use; and
+
+- provides a modelling toolkit (repositories and software) for authoring model modules, managing data and implementing reproducible analyses consistent with those standards.
+
+## Standards
 ```{r child="../Child_RMDs/MS_Imp_Guidelines.Rmd", echo=FALSE}
@@
 
-# Framework
+## Modelling toolkit
 ```{r child="../Child_RMDs/MS_Imp_Toolkit.Rmd", echo=FALSE}

### 2023-01-25 Markdown/Manuscript/Child_RMDs/MS_Tables_3.Rmd
up to fw

@@
 ---
-```{r checktb, tab.cap='TIMELY Checklist applied to utility mapping study', tab.id = 'checktb', echo = F, results = 'asis'}
+
+```{r checktb, tab.cap='Framework checklist applied to utility mapping study', tab.id = 'checktb', echo = F, results = 'asis'}
     #  a <- c("TEST1","TEST2")
@@
 # kableExtra::landscape()
-checklist_df <- data.frame(Ref = c(paste0("T",1:6),
-                                        paste0("I",1:4),
-                                        paste0("M",1:2),
-                                        paste0("E",1:3),
-                                        paste0("L",1:3),
-                                        paste0("Y",1:2)),
-                           Standard = c("Publicly archived",
-                                        "Documented",
-                                        "Consistent syntax",
-                                        "Literately programmed",
+checklist_df <- data.frame(Ref = c(paste0("A",1:7),#paste0("T",1:6),paste0("I",1:4),paste0("M",1:2),paste0("E",1:3),paste0("L",1:3), paste0("Y",1:2)
+                                   paste0("R",1:9),
+                                   paste0("U",1:4)),
+                           Standard = c("Public",
+                                        "Documentation",
+                                        "Syntax",
+                                        "Literate programming",
                                         "Code coverage",
-                                        "Reproducible",
+                                        "Reproducibility",
+                                        "Citation tools",#
+                                        # Reuse
+                                        "Code licenses",
+                                        "Data terms",
+                                        "Separation",
+                                        "Encapsulated, inheriting",
+                                        "Functions",
+                                        "Libraries",
+                                        "Test data",
+                                        "Prediction tools",
+                                        "User interface",
+                                        ## Updatable
                                         "Version controlled",
@@
                                         "Continuously integrated",
-                                        "Deprecation",
-                                        "Separate code and data",
-                                        "Encapsulated",
-                                        "Libraries",
-                                        "Inheriting",
-                                        "Test data",
-                                        "Copyleft code",
-                                        "Liberal, safe data terms",
-                                        "Citation tools",
-                                        "Prediction tools",
-                                        "User interface"),
+                                        "Deprecation"
+                                       ),
                            Assessment = c("Yes",
@@
                                         "Yes",
+                                        # Reuse
+                                        "Yes",
+                                        "Yes",
+                                        "Yes",
+                                        "Yes", # "Yes",
                                         "Yes",
@@
                                         "Yes",
+                                        "No",
+                                        ## Updatable
                                         "Yes",
@@
                                         "Yes",
-                                        "Yes",
-                                        "Yes",
-                                        "Yes",
-                                        "Yes",
-                                        "Yes",
-                                        "No"),
-                           Description = c("5 libraries (youthvars, scorz, specific, TTU and youthu) [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155; @matthew_p_hamilton_2021_5646669], 3 programs [@hamilton_matthew_2022_6129906; @hamilton_matthew_2022_6416330; @hamilton_matthew_p_2022_6321821], 2 sub-routines [@hamilton_matthew_2022_6116385; @matthew_p_hamilton_2022_5976988] and 2 datasets [@DVN/DKDIB0_2021; @DVN/HJXYKQ_2021] are permanently archived with unique identifiers.",
+                                        "Yes"
+                                        ),
+                           Description = c("Development and archived code for 5 libraries (youthvars, scorz, specific, TTU and youthu) [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155; @matthew_p_hamilton_2021_5646669], 3 programs [@hamilton_matthew_2022_6129906; @hamilton_matthew_2022_6416330; @hamilton_matthew_p_2022_6321821], 2 sub-routines [@hamilton_matthew_2022_6116385; @matthew_p_hamilton_2022_5976988] and 2 datasets [@DVN/DKDIB0_2021; @DVN/HJXYKQ_2021] are available.
+See https://www.ready4-dev.com/docs/getting-started/software/libraries/types/module/ (for libraries), https://www.ready4-dev.com/docs/getting-started/software/executables/programs/ (for programs) and https://www.ready4-dev.com/docs/getting-started/software/executables/subroutines/",
                                            "All code libraries have documenting websites with URLs that concatenate 'https://ready4-dev.github.io/' and the package name (e.g.
@@
                                            "All parts of the study workflow from raw data ingest through to data processing, analysis, reporting and dissemination of study outputs can be reproduced (if granted access to source data) or replicated (using supplied synthetic data) with one program [@hamilton_matthew_2022_6129906].",
+                                           "All libraries have a CITATION file in  the inst directory. All code repositories have a CITATION.cff file. All datasets have citation generating metadata.",
+                                           # Reuse
+                                           "All code libraries, programs and sub-routines use GPL-3 licenses. ",
+                                           "Datasets use amended version of template provided by Harvard Dataverse [@sampleterms2022].",
+                                           "All development code is stored on repos in a GitHub organisation [@ready4gh2022] and all archived releases are available in a Zenodo community [@ready4zen2022].
+All non-confidential data is stored in repositories within a Harvard Dataverse collection [@ready4dv2022].
+",
+                                           "Four [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155] out of five libraries include encapsulating and inheriting modules.
+See: https://www.ready4-dev.com/docs/model/finding-modules/ ",
+                                           "All code libraries include functions.
+The most complete list of functions for each library is available by clicking the 'Manual - Developer (PDF)' link on each package's documentation homepage (see item T2 above)",
+                                           "All module data-structures and algorithms are distributed as code libraries",
+                                            "Two synthetic datasets and their data dictionaries are publicly available in a data repository [@DVN/HJXYKQ_2021].
+One (ymh_clinical_tb.RDS) closely resembles the study dataset and was released so that the main study algorithm [@hamilton_matthew_2022_6129906] can be rerun by those without access to the confidential study dataset.
+The other (eq5d_ds_dict.RDS) is deliberately different to the source dataset in both variable naming convention and the concepts used for predictors and outcome measures.
+It was created to demonstrate generalised applications of study algorithms.",                                           #
+                                           "Model catalogues (PDF files beginning with 'AAA_TTU_MDL_CTG') are available in the study results dataset [@DVN/DKDIB0_2021] and describe the predictive performance of all models under a variety of usage regimes (including when the source dataset in the R model object is replaced with fake data).
+The youthu library [@matthew_p_hamilton_2021_5646669] includes tools for searching for and applying models compatible with different types of input data.
+An example program to demonstrate this functionality is available in both RMarkdown [@hamilton_matthew_2022_6416330] and rendered PDF formats (the 'Application.pdf' file in the study results dataset [@DVN/DKDIB0_2021]).
+",
+                                           "No Shiny app user interface has yet been developed.",
+                                        ## Updatable
                                            "All code is version controlled using Git and GitHub. All source code is available in a GitHub organisation [@ready4gh2022].",
@@
 Package vignettes and datasets are also deprecated e.g.
-https://ready4-dev.github.io/youthvars/articles/Replication_DS.html )",
-                                           "All development code is stored on repos in a GitHub organisation [@ready4gh2022] and all archived releases are available in a Zenodo community [@ready4zen2022].
-All non-confidential data is stored in repositories within a Harvard Dataverse collection [@ready4dv2022].
-",
-                                           "Four [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155] out of five libraries include encapsulated  modules.
-Examples are the items beginning with Scorz, Specific and Youthvars that are listed in this table: https://ready4-dev.github.io/ready4/articles/V_01.html#current-ready4-framework-modules as well as the S4 classess from the TTU package listed here: https://ready4-dev.github.io/TTU/reference/index.html ",
-                                           "All code libraries include functions.
-The most complete list of functions for each library is available by clicking the 'Manual - Developer (PDF)' link on each package's documentation homepage (see item T2 above).",
-                                           "All modules (see item M2) inherit from the Ready4Module class and can be inherited from.",
-                                           "Two synthetic datasets and their data dictionaries are publicly available in a data repository [@DVN/HJXYKQ_2021].
-One (ymh_clinical_tb.RDS) closely resembles the study dataset and was released so that the main study algorithm [@hamilton_matthew_2022_6129906] can be rerun by those without access to the confidential study dataset.
-The other (eq5d_ds_dict.RDS) is deliberately different to the source dataset in both variable naming convention and the concepts used for predictors and outcome measures.
-It was created to demonstrate generalised applications of study algorithms.",
-                                           "All code libraries, programs and sub-routines use GPL-3 licenses. ",
-                                           "Datasets use amended version of template provided by Harvard Dataverse [@sampleterms2022].",
-                                           "All libraries have a CITATION file in  the inst directory. All code repositories have a CITATION.cff file. All datasets have citation generating metadata.",
-                                           "Model catalogues (PDF files beginning with 'AAA_TTU_MDL_CTG') are available in the study results dataset [@DVN/DKDIB0_2021] and describe the predictive performance of all models under a variety of usage regimes (including when the source dataset in the R model object is replaced with fake data).
-The youthu library [@matthew_p_hamilton_2021_5646669] includes tools for searching for and applying models compatible with different types of input data.
-An example program to demonstrate this functionality is available in both RMarkdown [@hamilton_matthew_2022_6416330] and rendered PDF formats (the 'Application.pdf' file in the study results dataset [@DVN/DKDIB0_2021]).
-",
-                                           "No Shiny app user interface has yet been developed."))
+https://ready4-dev.github.io/youthvars/articles/Replication_DS.html )"
+                                          ))
 

### 2023-01-25 setup.R

@@ -13,7 +13,7 @@ X <- Ready4showSynopsis(#background_1L_chr = "Our study is entirely fictional.",
                         keywords_chr = c("open source models","health economics","mental disorders"),
                         outp_formats_chr = "PDF",
                         #sample_desc_1L_chr = "The study sample is fake data that pretends to be young people aged 12 to 25 years who attended Australian primary care services for mental health related needs between November 2019 to August 2020.",
-                        title_1L_chr = "A framework for implementing an open source and modular economic model of youth mental health that is accountable, reusable and updatable")
+                        title_1L_chr = "A framework for implementing a modular open source health economic model (MOSHEM) in youth mental health that is accountable, reusable and updatable")
 X <- renewSlot(X,
                "authors_r3", 
                {
@@ -37,14 +37,13 @@ X <- renewSlot(X,
                "abstract_args_ls",
                {
                  args_ls <- X@abstract_args_ls
-                 args_ls$abstract_ls <- list(Summary = "Compared to other disciplines, health economics rarely uses modular approaches to model development that facilitate re-use of model components. 
-                                             Although interest in open source health economic models (OSHEMs) is growing, uptake remains limited.
-                                             We propose a framework for a modular OSHEM in youth mental health.
-                                             The framework includes of set of X1 good practice standards for implementing a model that is accountable (X2 standards), reusable (X3 standards) and upatable (X4 standards). 
+                 args_ls$abstract_ls <- list(Summary = "Health economists make limited use of the modular and open source approaches to model building that other disciplines use to make modelling projects more transparent, efficient and sustainable. 
+                                             We propose a framework for a modular open source health economic model (MOSHEM) in youth mental health.
+                                             The framework includes of set of 20 standards for implementing a MOSHEM that is accountable (seven standards), reusable (nine standards) and updatable (four standards). 
                                              We provide a rationale for each standard.
-                                             The framework also includes software toolkit of six R packages for authoring model modules (data structures and algorithms), supplying those modules with data and using the modules to implement reproducible modelling analyses. 
-                                             We describe an early application of the framework to developing utility mapping models that meet X5 standards. 
-                                             We discuss the potential benefits and challenges of extending this initial work to develop a more extensive model for undertaking economic analyses in youth mental health.",
+                                             The framework also includes software toolkit of six R packages for authoring MOSHEM modules (data structures and algorithms), supplying those modules with data and using the modules to implement reproducible modelling analyses. 
[…]

### 2023-01-26 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
working on discussion

@@
 
-<!-- Add aims text here -->
 In this paper, we introduce a framework for developing a modular youth mental health MOSHEM. Specifically we:
@@
 (ii) provide a worked example of how we used the framework to develop and apply MOSHEM modules for utility mapping.
-
-<!-- We have consolidated and refined these and other recommended guidelines for OSHEMs as part of a framework for developing an open source model of youth mental health.  -->

### 2023-01-26 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
stuck
safety
up to fw
working on discussion

@@
 
-<!-- MH systems design is not a pharma led project - less concerns about commercial ownership -->
+In this article we introduced a framework that we developed to help us implement a MOSHEM in youth mental health.
+We outlined the standards for accountable, reusable and updatable models specified by that framework and the modelling toolkit we created to help the youth mental health MOSHEM we are developing to meet those standards.
+We also provided an overview of the initial set of model modules we developed with the framework to implement a utility mapping study and summarised the extent to which the outputs of that study adheres to framework standards.
 
-<!-- greater use of these types of models may require adaptation on the part of funders, modellers and decision-makers. T -->
+The work we have described raises a number of issues relating to the future development of a youth mental health MOSHEM, for health economists interested in undertaking other MOSHEMS and for health research funders.
 
-# Motivation
-
-## Why develop OSHEMs in mental health
-
+## Implications for the development of a youth mental helath MOSHEM
+<!-- ### Implications for our modelling team -->
 Mental disorders impose high health, social and economic burdens worldwide [@RN8;@GBD2019].
 Much of this burden is potentially avertable [@RN25], but poorly financed and organised mental health systems are ill-equipped for this challenge[@RN22;@RN23].
-The large and widespread additional mental health burdens recently observed during the COVID-19 pandemic[@20211700] and predicted as a potential future consequence of climate change [@page_howard_2010], highlight the need to improve the resilience and adaptability of these systems.
+There is therefore an opportunity for economic research to help identify mental health reforms of significant potential public benefit.
+To date, economic studies in mental health have predominantly examined the affordability and value for money of individual programs [@RN34].
+This economic evaluation work is an essential prerequisite for developing economically sustainable mental health reform plans, but it needs to be accompanied by and integrated with a broader program of economic research.
+The classification system developed by Wagstaff and Culyer [@wagstaff2012four] identified twelve categories of health economic research.
+In addition to the economic evaluation category, we have prioritised the following areas for the future development of modules for our MOSHEM:
+
+- health and its value [utility and choice],
+
+- demand for health and health care,
+
+- determinants of health and ill-health,
+
+- supply of health services,
+
+- efficiency and equity,
+
+In economic evaluation, 
+<!-- Yet single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020; @Occhipinti2021].  -->
+
+<!-- The large and widespread additional mental health burdens recently observed during the COVID-19 pandemic[@20211700] and predicted as a potential future consequence of climate change [@page_howard_2010], highlight the need to improve the resilience and adaptability of these systems.
 To help stem growing demand for mental health services, policymakers have also been encouraged to place greater emphasis on tackling the social determinants of mental disorders [@RN11].
+-->
 
+ - Aims of our model (multi-purpose, focused on systems reform)
+ - Addressing wagstaff areas ()
+ - Adequacy of current methods / our capacity (errors / impact)
+ - One shot at big changes
+ - Opportunities for others to leverage and enhance
+ - Our analysis - do it in stages, be transparent, continually improve, get help, be flexible (modelling toolkit / monolithic model), have a framework
+
+ - Strengths (comparisons to existing work, benefits to ourselves and others)
+
+ - Limitations (technical, not behavioural / institutional solution)
+
+<!-- A coding framework for MOSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions [@Alarid2019]. -->
+<!-- Our approach to model development is to undertake a number of discrete modelling projects of the people, places, platforms and programs that shape the mental health and wellbeing of young people and to progressively link them together by means of a common framework.
+To model people we are developing synthetic representations of populations of interest [@DVN/HJXYKQ_2021] that describe relevant individual characteristics and their relationships, algorithms that map psychological measures to health utility [@Hamilton2021.07.07.21260129] and choice models for predicting the helpseeking behaviour of young people [@hamilton_matthew_2022_6627995].
+Our in-development model of places [@DVN/V3OKZV_2022] has the aim of synthesising geometry and spatial attribute data to characterise the geographic distribution of relevant demographic, environmental, epidemiological and service infrastructure features.
+We are in the early stages of a multi-annual project to develop a service platform model that will represent the processes and operations of a complex primary youth mental health service.
+We also plan to extend and update our prior work reviewing economic evidence relating to youth mental health programs [@RN33] so that it can be integrated with this model.
+Our initial work on **readyforwhatsnext** is focused on Victoria, Australia but the framework we are using to develop it is designed to facilitate extension by ourselves and others to different jurisdictional decision contexts.
+Progress is reported on a project website [@rfwn2022].
+-->
 Major mental health reform programs, <!-- such as those currently being implemented in Victoria, Australia [@VicRC2021],  -->can involve the identification, prioritisation, sequencing, targeting and monitoring of multiple interdependent initiatives.
@@
 
+<!-- ### Implications for potential users of and contributors to our model -->
+
+Another future priority is to submit production versions of each R package for review by and archiving on the Comprehensive R Archive Network (CRAN) [@CRAN2022].
 Developing networks of modellers working on common health conditions has been recommended as a strategy for improving model validity [@Sampson2019] and some of us are part of a nascent initiate of this type in mental health [@nmhsmn2022].
+
 <!-- Add ref to NMHSMN in Australia --> Similarly, developing partnerships between modellers and decision-makers across the life-cycle of a modelling project can help ensure models are appropriately conceptualised, implemented and have practical utility as decision aids [@Zabell2021; @SQUIRES2016588].
+
+- Community building (feasibility)
+<!-- Open source is more than open access (limited discussion). -->
+- Funding contingent directions - replications / transfers
+
+## Implications for health economists
+<!-- Standardized and transferable approaches to health economic modelling have been recommended. [doi:10.1017/S0266462317000666] -->
+<!-- As modelling methods have become more sophisticated, some have argued that more complex models are required to adequately explore certain types of public health topics [@SQUIRES2016588].  -->
+<!-- Modellers should be faithful to reaity and values of users DOI: 10.1002/asi.23697 -->
+<!-- transferability - [https://doi.org/10.1017/S026646232200321X].  -->
+Output by health economists [@pitt2016economic; @wagstaff2012four; @munoz2020health]
+
+## Implications for research funders
+<!-- Reducing waste in research is responsibility of research funder: https://doi.org/10.1016/S0140-6736(13)62229-1 -->
+<!-- MH Research priorities (WP3 - Research, WP6 - Economic) https://doi.org/10.1016/S2215-0366(15)00332-6 -->
+<!-- http://hdl.handle.net/1893/27205--><!-- CONTEXT: Funders should also support methodological work on context, including the development of reporting templates to facilitate accurate, comprehensive and systematic reporting of context, approaches to evidence synthesis that can capture contextual variation adequately and modelling methods that can leverage the accumulating evidence on contextual variation to predict the reach, implementation and effectiveness of promising interventions in new contexts." -->
+
+- unreasonable to expect more accountability without more resources
+
+<!-- greater use of these types of models may require adaptation on the part of funders, modellers and decision-makers. T -->
+
+<!-- Link to Wagstaff - Demand forecasting, valuation of health and healthcare, economic evaluation, utility mapping?? -->
+
+<!-- # Motivation -->
+
+<!-- ## Why develop OSHEMs in mental health -->
+
+<!-- Decision makers are frequently left to rely on economic analyses that become less valid and relevant each year.
+A model can grow stale when changes in the real world, whether sudden (e.g.
+new pandemics) or gradual (e.g.
+demographic), is not represented by corresponding updates to relevant model features.
+Even when the system being modelled remains relatively stable, new research findings may potentially invalidate aspects of a model's original conceptualisation and implementation.
+-->
+
+<!-- that rarely explores complex dynamic systems  -->
+<!-- [PECUNIA] -->
+
+<!-- Computational modelling could play an important role in developing policies to improve population mental health but this may require significant changes in the way mental health modelling projects are funded, conceptualised and implemented.
+-->
+ <!-- but, as with health economics more generally, OSHEMs remain rare.
+Greater use of open source approaches could help improve the scope, validity and usefulness of mental health economic models.
+-->
+
+<!-- Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each unique item.
+These repositories are a preferable solution for sharing citable code and data than transitory repositories such as corporate websites or GitHub where items can be deleted or relocated at any time [@sseditors2022].
+Zenodo includes tools that automate integration with GitHub, which makes it easy for developers to maintain parallel code repositories - one for disseminating the most up to date development code and the other for archiving citable code releases.
+--> <!-- Developers storing data in a Dataverse installation have access to multiple meta-data fields to document both a data collection and its individual constituent files.
+--><!-- In R, code manuals and websites can be created with the aid of tools such as devtools [@devtools2021], sinew [@sinew2022], roxygen2 [@roxygen2021] and pkgdown [@pkgdown2022].
+-->
+
+<!-- and the use of version control systems. <!-- such as Git [@git20XX].  -->
+
+<!-- Applying a previously published algorithm [@kross2016] to analyse the most comprehensive archive of released R packages [@CRAN2022] finds that `r gpl_pc_dbl`% are distributed under various forms of General Public License (GPL) [@GNUGPL2022], a copyleft license.
+-->
+<!-- In R, including a CITATION file in the `inst` directory of a package will enable users of that package to retrieve citation information by running a command of the format `citation("Package Name")` in the R console [@Salmon2021].
+More generally, including a CITATION.cff file at the top level of your code repository will enable GitHub and Zenodo repositories hosting that item to include the relevant information in their citation tools [@Druskat_Citation_File_Format_2021].
+Datasets hosted on Dataverse installations have metadata fields that, once completed by authors, generate citation files for dataset viewers.
+-->
+
+<!-- A key challenge to generalising health economic models is that they are typically developed to inform a decision problem with a highly specific jurisdictional context.
+However, a number of choices about how these models are implemented can significantly increase the re-usability of model code in other contexts.
+-->
+<!-- For example, when generalising a model developed for the Australian context to a UK context, one could create a class that initially inherits all of the methods defined for the Australian model and then write new or replacement methods as needed for the UK model.
+-->
+
+<!-- A number of tools and approaches can make the process of implementing and curating changes to model code and data more coherent and efficient.
+<!-- Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent access to all published versions of a dataset, each uniquely identifiable.
+For code, use of version control tools like Git [@git20XX] can ensure that the entire development history of a project is organised so that each version is distinguishable and retrievable by developers.
+The online platform GitHub [@github2007] can make this version history accessible to anyone.
+-->
+
+<!-- For R code, the usethis [@usethis2021] package can be used to partially automate version number increments using the convention Major.Minor.Patch.Development (e.g.
+ExampleSoftware v1.1.1.1).
+Datasets stored on the Harvard Dataverse use the simpler Major.Minor convention.
+-->
+<!-- MOSHEMs developed in R can take advantage of templates provided by devtools [@devtools2021] and pkgdown [@pkgdown2022] to run continuous integration checks on GitHub.
+--><!-- These tests can include those of units (do individual functions produce expected output?), documentation (does documentation render correctly?; can all example workflows be executed?) and installation (can the software be successfully deployed on multiple types of operating system?).
+-->
+<!-- MH systems design is not a pharma led project - less concerns about commercial ownership -->
+
+<!-- and for mental health specifically [@Occhipinti2021],  -->
+<!-- could provide greater insight about inter-dependencies between candidate policies and the dynamic nature of the mental health systems planning context.
+Dynamic systems methods might provide the foundations for developing   -->
+<!-- and models designed for multiple purposes r -->
+
+ <!-- as part of the Open Value Initiative [@Jansen2019].  -->

### 2023-01-26 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
working on discussion

--- 2022-07-22 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
@@
 
-We used framework toolkits to develop model code and datasets for implementing a utility mapping study that has previously been described [@Hamilton2021.07.07.21260129].
-Table \@ref(tab:checktb) assesses that study against each TIMELY standard, 18 of which the study was able to meet.
-The two current standards where the study falls short are in reporting code coverage and including a user-interface.
-Both these items are current development priorities for our team.
+We applied the framework to develop modules for developing utility mapping models, supplying those modules with data and implementing utility mapping analyses.
+The study for which these tools were developed and which applied them to developing utility mapping models for a clinical mental health sample of young people has been previously described [@Hamilton2021.07.07.21260129].
+The outputs we authored using the framework's modelling toolkit include:
+
+ - development version module libraries for describing and validating youth mental health human record datasets [@hamilton_matthew_2022_6084467], scoring health utility [@hamilton_matthew_2022_6084824], specifying utility mapping models [@hamilton_matthew_2022_6116701] and implementing reproducible utility mapping studies [@gao_caroline_2022_6130155];
+
+ - a development version library of functions for finding and using utility mapping models developed with these tools [@matthew_p_hamilton_2021_5646669];
+
+ - data collections of synthetic populations for testing model modules [@DVN/HJXYKQ_2021] and study input and results data [@DVN/DKDIB0_2021];
+
+ - programs for replicating all steps from data ingest to manuscript reporting [@hamilton_matthew_2022_6129906], applying utility mapping models to new data [@hamilton_matthew_2022_6416330] and generating a synthetic representation of the study dataset [@hamilton_matthew_p_2022_6321821];
+
+ - subroutines for creating a catalogue of utility mapping models [@hamilton_matthew_2022_6116385] and generating a draft scientific manuscript [@matthew_p_hamilton_2022_5976988] for studies implemented with these modules.
+
+When we assesses these study outputs against each framework standard, we conclude that 18 standards were wholly or mostly met (see Table \@ref(tab:checktb)).
+The two standards where the study outputs currently fall short are in reporting code coverage and including a user-interface.
+Both these items are scheduled to be addressed when we release production versions of the code libraries.

### 2023-01-26 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
working on discussion

@@
 The standards are specified in Table \@ref(tab:timelygls) and are discussed below.
-
- <!-- - **Transparent**: people can easily see how a model has been implemented and tested; -->
- <!-- - **Iterative**: a model is routinely updated to maintain and improve validity; -->
- <!-- - **Modular**: models and their components can be combined to extend their scope; -->
- <!-- - **Epitomising**: model code is sufficiently general to be be re-used in multiple decision contexts; -->
- <!-- - **Licensed**: a model, its components and derivatives are persistently re-usable by other modellers; and -->
- <!-- - **Yielding**: a model can be simply, flexibly and reliably used as a decision aid. -->
 
@@
 Model code and data should be clearly documented, potentially with different versions for technical and non-technical users [@Eddy2012].
-<!-- nd --> Consistent use of meaningful naming conventions when authoring code is recommended [@Wilson_2017; @Alarid2019].
+Consistent use of meaningful naming conventions when authoring code is recommended [@Wilson_2017; @Alarid2019].
 Code can be made easier to follow by using the practices of abstraction [@8717448], where only simple, high level commands are routinely exposed to reviewers, and polymorphism [@7181447], where the same command (e.g.
 "simulate") can be reused to implement different algorithms of the same type.
-Programs to implement model analyses can be made comprehensible to even non-technical users through the use of literate programming techniques <!-- that use tools like RMarkdown [@xie2018r]  -->that integrate computer code with plain English descriptions.
+Programs to implement model analyses can be made comprehensible to even non-technical users through the use of literate programming techniques and tools like RMarkdown [@xie2018r] that integrate computer code with plain English descriptions.
 
@@
 
-<!-- Guidelines: -->
-
-<!-- - **T1: Uniquely identified copies of model code and data are permanently archived in open online repositories** -->
-<!-- <!-- T2 MISSING - Merged With T1 -->
-
-<!-- - **T2: Model code and data are documented **<!-- Was T3 -->
-
-<!-- - **T3: Model code uses a simple and consistent syntax**<!-- Was T4 -->
-
-<!-- - **T4: Model analyses and reporting are implemented using literate programming** <!-- Was T5 -->
-
-<!-- - **T5: Code coverage is reported** <!-- New, replaces version now moved to T4 -->
-
-<!-- - **T6: All parts of a study analysis and reporting workflow can be reproduced and/or replicated** <!-- Was T7, Replaces Deleted T6 -->
-
-<!-- - **L3: Model code and data are distributed with tools to support appropriate citation** <!-- New -->
-
-<!-- and the use of version control systems. <!-- such as Git [@git20XX].  -->  
-<!-- Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each unique item.
-These repositories are a preferable solution for sharing citable code and data than transitory repositories such as corporate websites or GitHub where items can be deleted or relocated at any time [@sseditors2022].
-Zenodo includes tools that automate integration with GitHub, which makes it easy for developers to maintain parallel code repositories - one for disseminating the most up to date development code and the other for archiving citable code releases.
---> <!-- Developers storing data in a Dataverse installation have access to multiple meta-data fields to document both a data collection and its individual constituent files.
---><!-- In R, code manuals and websites can be created with the aid of tools such as devtools [@devtools2021], sinew [@sinew2022], roxygen2 [@roxygen2021] and pkgdown [@pkgdown2022].
--->
-
 ### Standards for a reusable MOSHEM
-<!-- ## Licensed models -->
 ```{r echo = F}
@@
 
-Storing and managing model code and data separately, can make it easier to apply models to different decision contexts and, when necessary, to selectively restrict access to data that are confidential, while disseminating all other model artefacts.
-Clear distinctions should be made between model modules (code that defines abstract data structures and the algorithms that can be applied to data described by these structures), model datasets (digital information such as parameter values, unit records, etc) and model analyses (code that specifies the data to be supplied to modules and selects which module algorithms to apply to that data).
+Storing model code and data in separate files and locations (as opposed to hard coding - embedding data into source code) can make it easier to apply models to different decision contexts and, when necessary, to selectively restrict access to data that are confidential, while disseminating all other model artefacts.
+Clear distinctions should be made between model modules (code that defines abstract data structures and the algorithms that can be applied to data described by these structures), model datasets (digital information such as parameter values, unit records, etc) and model analyses (code that links model datasets to model modules and specifies the algorithms to apply to the data associated with each module).
 
-The coding practice of encapsulation [@8717448] can be used to help ensure that model modules can be safely combined [@ready4oop2022].
-In some cases, combining modules may mean new versions of modules have to be created that account for their effects on each other.
+The coding practice of encapsulation [@8717448] can be used to help ensure that model modules continue to work as intended even when they are combined [@ready4oop2022].
+In some cases, combining modules may mean new versions of modules have to be created to better account for interaction effects.
 The coding concept of inheritance [@8717448] can be used to efficiently achieve this objective as well as to facilitate selective editing of modules when transferring models to different decision contexts [@ready4oop2022].
@@
 
-<!-- When bundled for distribution as libraries<!-- (for example, as R packages) -->
-<!-- , functions have the potential to be widely re-used, often in contexts very different than those they were originally developed for.  --> 
-<!-- A special type of function, called a method, can only be applied to a pre-defined class of data structure.  -->
-
-<!-- ## Yielding models --><!-- MOSHEMs can be time and skills intensive for modellers to develop - but they should be easy for others to use.  -->
 Statistical models are a common output of health economic evaluations, but they are often not reported in a format that enables others to confidently and reliably re-use them [@Kearns2013].
@@
 
-<!-- Applying a previously published algorithm [@kross2016] to analyse the most comprehensive archive of released R packages [@CRAN2022] finds that `r gpl_pc_dbl`% are distributed under various forms of General Public License (GPL) [@GNUGPL2022], a copyleft license.
--->
-<!-- In R, including a CITATION file in the `inst` directory of a package will enable users of that package to retrieve citation information by running a command of the format `citation("Package Name")` in the R console [@Salmon2021].
-More generally, including a CITATION.cff file at the top level of your code repository will enable GitHub and Zenodo repositories hosting that item to include the relevant information in their citation tools [@Druskat_Citation_File_Format_2021].
-Datasets hosted on Dataverse installations have metadata fields that, once completed by authors, generate citation files for dataset viewers.
--->
-
-<!-- A key challenge to generalising health economic models is that they are typically developed to inform a decision problem with a highly specific jurisdictional context.
-However, a number of choices about how these models are implemented can significantly increase the re-usability of model code in other contexts.
--->
-<!-- For example, when generalising a model developed for the Australian context to a UK context, one could create a class that initially inherits all of the methods defined for the Australian model and then write new or replacement methods as needed for the UK model.
--->
-<!-- Guidelines: -->
-
-<!-- - **L1: Model code is made available for re-use under copyleft or permissive licenses** -->
-
-<!-- - **L2: Non-confidential model data is licensed for liberal re-use (subject to additional terms for de-identified human data)** -->
-
-<!-- - **E2: Model code defines inheriting data-structures** --> <!-- Order changed-->
-
-<!-- - **E1: Model code is distributed as libraries of classes and functions**  <!-- Modified (lost ref to OOP and merged with M2) -->
-
-<!-- - **E3: Test data is available to demonstrate generalised applications of model code** -->
-
-<!-- - **M1: Model code and data are stored and managed separately** <!-- Modified (lost ref to licensed and cited) -->
-
-<!-- - **M2: Model code defines encapsulating data structures** <!--Replacement - Old version now merged with E1 -->
-
-<!-- - **Y1: Statistical models are distributed with validated tools to support their safe and appropriate re-use** <!-- New, Replaces Old Y1 (now Y2) --> 
-<!-- - **Y2: Simple user-interfaces allow non-technical users to configure and run models ** <!-- Was Y1 -->
-
 ### Standards for an updatable MOSHEM
@@
 Each update of code and data should be uniquely identifiable and retrievable, a goal that can be facilitated by use of version control tools [@Erdemir2020].
-Labeling each change using semantic versioning [@semver20xx] conventions can signal the potential importance of an update to users of model code and data.
+
+Potential users of model code and data should be able to easily identify which version is most appropriate to their needs.
+Using semantic versioning [@semver20xx] conventions can signal the potential importance of an update to users of model code and data.
+Also informative is to clearly label the type of code hosted in a repository as either:
+
+- "development" (typically the most comprehensive and up to date source code, but potentially not yet sufficiently well documented and tested for potential users to apply to purposes other than testing);
+
+- "production" (code that has been released with a view to it being applied to its stated purposes and therefore typically required to meet defined documentation and testing standards); or
+
+- "archive" (permanent copies of code at key milestones in its development - potentially useful if seeking to use older versions of code to reproduce analyses).
+
 Continuous integration [@CI2017] tools can help verify that each code update passes multiple quality tests.
 Finally, using deprecation conventions that take an informative and staged approach to retiring old code and data reduces the risk that model revisions have unintended consequences on third party users.
-
-<!-- A number of tools and approaches can make the process of implementing and curating changes to model code and data more coherent and efficient.
-<!-- Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent access to all published versions of a dataset, each uniquely identifiable.
-For code, use of version control tools like Git [@git20XX] can ensure that the entire development history of a project is organised so that each version is distinguishable and retrievable by developers.
-The online platform GitHub [@github2007] can make this version history accessible to anyone.
--->
-
-<!-- For R code, the usethis [@usethis2021] package can be used to partially automate version number increments using the convention Major.Minor.Patch.Development (e.g.
-ExampleSoftware v1.1.1.1).
-Datasets stored on the Harvard Dataverse use the simpler Major.Minor convention.
--->
-<!-- MOSHEMs developed in R can take advantage of templates provided by devtools [@devtools2021] and pkgdown [@pkgdown2022] to run continuous integration checks on GitHub.
---><!-- These tests can include those of units (do individual functions produce expected output?), documentation (does documentation render correctly?; can all example workflows be executed?) and installation (can the software be successfully deployed on multiple types of operating system?).
--->
-
-<!-- The package lifeycle [@lifecycle2021] provides tools for R developers to consistently deprecate their code. -->
-
-<!-- Guidelines: -->
-
-<!-- - **I1: Model code and data are version controlled** <!-- Was I2 -->
-
-<!-- - **I2: Model code and data use semantic versioning** <!-- Was I1 -->
-
-<!-- - **I3: Continuous integration is used to verify model code updates** -->
-
-<!-- - **I4: Deprecation conventions are used to retire model code and data** -->
+The package lifeycle [@lifecycle2021] provides tools for R developers to consistently deprecate their code.

### 2023-01-26 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
working on discussion

--- 2023-01-23 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
@@
 ---
-<!-- # Framework -->
-<!-- The framework we have developed to implement **readyforwhatsnext** specifies standards for OSHEMs and provides tools for meeting those standards. -->
 
-We have developed a toolkit to help streamline the process of developing OSHEMs that meet the TIMELY standards. The toolkit is comprised of online repositories and software.
+We developed a toolkit to help us develop and use a MOSHEM that meets the standards listed in Table \@ref(tab:timelygls). The toolkit is comprised of online repositories and software.
 
 ## Repositories <!-- Existing ref -->
-We created a GitHub organisation where all framework software source code is stored, documented, version controlled and continuously integrated [@ready4gh2022].
-To store citable archived copies of release copies of our software, we created a Zenodo community [@ready4zen2022].
-Finally, to manage datasets for use in models developed with the framework, we created a dedicated collection within the Harvard Dataverse  [@ready4dv2022].
+We created a GitHub organisation (a collection of code repositories) where all our development code is stored and version controlled [@ready4gh2022].
+We linked our GitHub organisation to an account we established at codecov [@codecov_2022] to track our code coverage.
+We configured the repositories in our GitHub organisation to use GitHub actions to support continuous integration.
+
+For hosting documentation websites for the code libraries we create, we enabled GitHub Pages in each library's repository.
+We also developed a consolidated project documentation website (https://www.ready4-dev.com), using the Hugo framework [@hugo_2023] and Docsy theme [@docsy_2023].
+To host that website we established an account with Netlify [@netlify_2023] and linked that service to our GitHub organisation so that the website would automatically update whenever the source code in its GitHub repository was edited.
+
+We also created a Zenodo community [@ready4zen2022] - a collection of permanent, unbiquely identified repositories.
+We then linked our Zenodo community and GitHub organisation so that every time we create a new "release" in a GitHub repository, a copy of that code is automatically created on Zenodo with a DOI.
+Finally, to manage model datasets, we created a dedicated collection within the Harvard Dataverse installation [@ready4dv2022].
 
 ## Software <!-- Novel ref -->
+We created six development version R libraries to help us author model modules, supply them with data and implement reproducible modelling analyses.
+The six libraries, their primary focus, the standards they support and the third-party packages they depend on are summarised in Table \@ref(tab:cpkgs).
 
-A coding framework for OSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions [@Alarid2019].
+The foundation for our MOSHEM is provided by the ready4 library [@ready42022] that defines a template module (using R's S4 type class) from which all model module data structures will inherit features and a novel syntax for implementing the algorithms attached to model modules.
+The ready4 library also contains tools for retrieving web based information on model modules, datasets and analysis programs and for partially automating updates to the project website.
 
-As a foundation for implementing the framework, we authored a development version R package that defines a novel syntax and a template class for model modules [@ready42022].
-To enable the syntax and module template be applied to modelling projects, we then created five additional development version R packages that provide tools for authoring:
+Three R libraries are designed to standardise and partially automate workflows for authoring new model modules.
+The ready4pack library [@ready4pack2022] provides tools for authoring module libraries that are:
 
-- documented model modules [@ready4class2022];
+- documented (with a website, a manual itemising selected contents and a manual itemising all contents);
 
-- documented functions (including methods), written in a consistent house style [@ready4fun2022];
+- licensed (with GPL-3 by default);
 
-- citable, quality assured R packages [@ready4pack2022];
+- easily citable (citation information can be retrieved within an R session or from hosting repositories); and
 
-- model datasets [@ready4use2022];
+- quality assured (triggering continuous integration workflows, including any unit tests created by module library authors).
 
-- model analyses and reports [@ready4show2022].
+The ready4pack library is designed to integrate with our GitHub organisation and depends on the other two module authoring libraries.
+Methods from the ready4fun library [@ready4fun2022] are used to verify that functions for implementing module algorithms are written in a consistent house style and to use their standardised format to automatically generate basic documentation for each function.
+Methods from the ready4class [@ready4class2022] library are used to streamline and standardise the authoring of module data-structures.
+Like ready4fun, the ready4class library uses standardised naming conventions to automatically generate basic documentation for each module data-structure.
 
-The six R packages, their primary focus, the TIMELY standards they support and the third-party packages they depend on are summarised in Table \@ref(tab:cpkgs).
-When used in conjunction with framework repositories, the six packages extend existing R packages provide strong support for implementing 16 of the TIMELY standards.
-However, the software only weakly supports implementing the standards relating to disseminating statistical models (Y1) and user-interface development (Y2) and does not yet provide any workflow tools to help implement the standards for code coverage (T5) and deprecation conventions (I4).
-Standards not supported or weakly supported by our software can be met with existing developer tools in R and we plan to progressively integrate these third-party tools with our own in future releases of our software.
-Another future priority is to submit production versions of each R package for review by and archiving on the Comprehensive R Archive Network (CRAN) [@CRAN2022].
+The ready4use [@ready4use2022] library contains modules for ingesting model datasets from online repositories (hosted on a Dataverse installation or on GitHub), labelling model datasets and sharing model datasets via online repositories.
+The ready4show library [@ready4show2022] contains tools to help author analyses programs that are either self-documenting or which trigger the creation of a scientific summary.
+
+When used in conjunction with repositories, the six R libraries provide strong support for implementing 17 framework standards.
+However, the software only weakly supports implementing the standards relating to safe dissemination of statistical models (R8) and user-interface development (R9) and does not yet provide any workflow tools to help implement the standard for deprecation conventions (U4).
+Standards not supported or weakly supported by our software can be met with existing developer tools in R.
 

### 2023-01-26 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
working on discussion

@@
 
-<!-- As modelling methods have become more sophisticated, some have argued that more complex models are required to adequately explore certain types of public health topics [@SQUIRES2016588].  -->
-<!-- Accountability for both the scientific quality and social acceptability of health economic models can be improved.  -->
-<!-- Modellers should be faithful to reaity and values of users DOI: 10.1002/asi.23697 -->
-
 The resource and skills intensive undertaking of modelling could be made more tractable if it was easier for health economists to re-use each other's models [@Arnold2010].
@@
 
-<!-- [https://doi.org/10.1017/S026646232200321X].  -->
-
 Health economic models should be updated and refined as new evidence emerges and decision contexts change [@Jenkins2021], but this occurs infrequently [@Sampson2017].
@@
 The career trajectories of health economists can also mitigate against adequate maintenance of a model, it being relatively common for model authors to have moved on from the team that owns the model and / or from working on the health condition for which the model was developed.
-<!-- Decision makers are frequently left to rely on economic analyses that become less valid and relevant each year.A model can grow stale when changes in the real world, whether sudden (e.g.
-new pandemics) or gradual (e.g.
-demographic), is not represented by corresponding updates to relevant model features.
-Even when the system being modelled remains relatively stable, new research findings may potentially invalidate aspects of a model's original conceptualisation and implementation.
--->
 
 A potential strategy for improving model accountability, reusability and updatability is to make models both modular and open-source.
-<!-- Modularity -->
-<!-- Definition, value - Computational biology https://doi.org/10.1371/journal.pcbi.1009513 -->
-<!-- reusable, interoperable, trans- parent and able to accommodate updates to both data and algorithms - Ecology DOI: 10.1111/2041-210X.14034 -->
-<!-- Brain OS modularity: https://www.frontiersin.org/articles/10.3389/fninf.2022.883223/pdf -->
 
@@
 
-<!-- Standardized and transferable approaches to health economic modelling have been recommended. [doi:10.1017/S0266462317000666] -->
 Modular models provide an opportunity for multiple modelling teams to contribute to, test and reuse models.
@@
 
-<!-- Open source is more than open access (limited discussion). -->
-<!-- Reducing waste in research is responsibility of research funder: https://doi.org/10.1016/S0140-6736(13)62229-1 -->
-<!-- MH Research priorities (WP3 - Research, WP6 - Economic) https://doi.org/10.1016/S2215-0366(15)00332-6 -->
-
-<!-- and for mental health specifically [@Occhipinti2021],  -->
-<!-- could provide greater insight about inter-dependencies between candidate policies and the dynamic nature of the mental health systems planning context.
-Dynamic systems methods might provide the foundations for developing   -->
-<!-- and models designed for multiple purposes r -->
-
 We plan to develop a modular OSHEM (MOSHEM) of youth mental health that is accountable, reusable and updatable.
@@
 We  are aware of just one other open source mental health model - a reference model in Major Depressive Disorder - that is currently in development [@IVIMDD2022].
-
-<!-- that rarely explores complex dynamic systems  -->
-<!-- [PECUNIA] -->
-
-<!-- Mental health economic studies predominantly examine the affordability and value for money of individual programs [@RN34].
-Yet single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020; @Occhipinti2021].
--->
-
- <!-- as part of the Open Value Initiative [@Jansen2019].  -->
-
-<!-- Computational modelling could play an important role in developing policies to improve population mental health but this may require significant changes in the way mental health modelling projects are funded, conceptualised and implemented.
--->
- <!-- but, as with health economics more generally, OSHEMs remain rare.
-Greater use of open source approaches could help improve the scope, validity and usefulness of mental health economic models.
--->
-
-<!-- CONTEXT: Funders should also support methodological work on context, including the development of reporting templates to facilitate accurate, comprehensive and systematic reporting of context, approaches to evidence synthesis that can capture contextual variation adequately and modelling methods that can leverage the accumulating evidence on contextual variation to predict the reach, implementation and effectiveness of promising interventions in new contexts." -->
-
- <!-- http://hdl.handle.net/1893/27205-->

### 2023-01-26 Markdown/Manuscript/Child_RMDs/MS_Tables_2.Rmd
working on discussion

--- 2022-05-31 Markdown/Manuscript/Child_RMDs/MS_Tables_2.Rmd
@@
 ---
-title: "Untitled"
+title: "Predr_Cors"
 author: "Author"
@@
 ---
-```{r checktb, tab.cap='TIMELY Checklist applied to utility mapping study', tab.id = 'checktb', echo = F, results = 'asis'}
-    #  a <- c("TEST1","TEST2")
-    # b <- c("\\cite{ready4show2022}", "hjhjhj")
-    # tmp <- data.frame(a,b)   
-#     kableExtra::kbl(tmp, booktabs = T, escape = F) %>%
-#  kableExtra::kable_styling(
-#    latex_options = c("striped", "hold_position", "repeat_header")
-#    ) %>%  
-#   kableExtra::column_spec(2, width = "50em") %>%
-# kableExtra::landscape()
+```{r cpkgs, tab.cap='Modelling toolkit R packages for developing and using MOSHEMs that meet framework standards', tab.id = 'cpkgs', echo = F, results = 'asis'}
+library(kableExtra)  
+df <- tibble::tibble(Package = c("ready4",
+                                       "ready4fun",
+                                       "ready4class",
+                                       "ready4pack",
+                                       "ready4use",
+                                       "ready4show"),
+                           # Version = Package %>%
+                           #   purrr::map_chr(~utils::packageDescription(.x) %>%
+                           #                    purrr::pluck("Version")),
+                           Focus = c("Foundation",
+                                     "Module algorithms",
+                                     "Module structures",
+                                     "Module libraries",
+                                     "Datasets",
+                                     "Analyses"),
+                           A = c("3","2-3","2","1-2,5,7","1-2,7","4,6"), 
+                           R = c("4","5","4-5","1,3,6","3,7",""),
+                           U = c("","","","1-3","1",""),
+                           # E = c("", "1","1-2","1","3",""),
+                           # L = c("","","","1,3","2-3",""),
+                           # Y = c("","","","","","1-2"),
+                           `Depends on` = Package %>%
+                             purrr::map(~ {
+                               utils::packageDescription(.x) %>%
+                                 `[`(c("Depends", "Imports")) %>%
+                                 purrr::map(~{
+                                   if(is.null(.x)){
+                                     character(0)
+                                     }else{
+                                       .x %>%
+                                         strsplit(",\\n") %>%
+                                         purrr::flatten_chr() %>%
+                                         purrr::map(~strsplit(.x,", ") %>%
+                                                      purrr::flatten_chr()) %>%
+                                         purrr::flatten_chr() %>% sort() %>%
+                                         purrr::discard(~startsWith(.x,"R "))
+                                       }
+                                   }) %>%
+                                 purrr::flatten_chr() %>%
+                                 unique() %>%
+                                 sort() %>%
+                                 purrr::map_chr(~{
+                                   updated_1L_chr <- stringr::str_replace_all(.x,"\\n"," ")
+                                   problem_idx_1L_chr <- stringr::str_locate(updated_1L_chr," ")[1,1] %>%
+                                     unname()
+                                   if(!is.na(problem_idx_1L_chr))
+                                     updated_1L_chr <- updated_1L_chr %>%
+                                     stringr::str_sub(end = problem_idx_1L_chr-1)
+                                   updated_1L_chr %>% 
+                                     trimws(which = "left") 
+                                   })
+                               }) %>% 
+                             purrr::map_chr (~ .x %>% paste0(collapse = " "))) %>% 
+  as.data.frame() 
+    df$Ref <- c("@ready42022",
+                    "@ready4fun2022",
+                    "@ready4class2022",
+                    "@ready4pack2022",
+                    "@ready4use2022",
+                    "@ready4show2022")
+df <- df %>%
+  dplyr::mutate(Standard = purrr::pmap_chr(df,
+                                           ~paste0("A",
+                                                  ..3,
+                                                  paste0(rep("&nbsp;",
+                                                      2+max(nchar(df[,3]))-nchar(..3)),
+                                                      collapse = ""#
+                                                      ),
+                                                  ifelse(..4=="","","R"),
+                                                  ..4,
+                                                  paste0(rep("&nbsp;",
+                                                      2+max(nchar(df[,4]))-nchar(..4)),
+                                                      collapse = ""#
+                                                      ),
+                                                  ifelse(..5=="","","U"),
+                                                  ..5,
+                                                  paste0(rep("&nbsp;",
+                                                      1+max(nchar(df[,5]))-nchar(..5)),
+                                                      collapse = ""#
+                                                      )#,
+                                                  # ifelse(..6=="","","E"),
+                                                  # ..6,
+                                                  # paste0(rep("&nbsp;",
+                                                  #     1+max(nchar(df[,6]))-nchar(..6)),
+                                                  #     collapse = ""#
+                                                  #     ),
+                                                  # ifelse(..7=="","","L"),
+                                                  # ..7,
+                                                  # # paste0(rep("&nbsp;",
+                                                  # #     1+max(nchar(df[,7]))-nchar(..7)),
+                                                  # #     collapse = ""#
+                                                  # #     ),
+                                                  # ifelse(..8=="","","&nbsp; &nbsp; &nbsp; &nbsp; Y"),
+                                                  # ..8,
+                                                  # paste0(rep("&nbsp;",
+                                                  #     1+max(nchar(df[,8]))-nchar(..8)),
+                                                  #     collapse = ""#
+                                                  #     )
+                                                  ))) %>%
 
-checklist_df <- data.frame(Ref = c(paste0("T",1:6),
-                                        paste0("I",1:4),
-                                        paste0("M",1:2),
-                                        paste0("E",1:3),
-                                        paste0("L",1:3),
-                                        paste0("Y",1:2)),
-                           Standard = c("Publicly archived",
-                                        "Documented",
-                                        "Consistent syntax",
-                                        "Literately programmed",
-                                        "Code coverage",
-                                        "Reproducible",
-                                        "Version controlled",
-                                        "Semanticly versioned",
-                                        "Continuously integrated",
-                                        "Deprecation",
-                                        "Separate code and data",
-                                        "Encapsulated",
-                                        "Libraries",
-                                        "Inheriting",
-                                        "Test data",
-                                        "Copyleft code",
-                                        "Liberal, safe data terms",
-                                        "Citation tools",
-                                        "Prediction tools",
-                                        "User interface"),
-                           Assessment = c("Yes",
-                                        "Yes",
-                                        "Yes",
-                                        "Yes",
-                                        "No",
-                                        "Yes",
-                                        "Yes",
-                                        "Yes",
-                                        "Yes",
-                                        "Yes",
-                                        "Yes",
-                                        "Yes",
-                                        "Yes",
-                                        "Yesg",
-                                        "Yes",
-                                        "Yes",
-                                        "Yes",
-                                        "Yes",
-                                        "Yes",
-                                        "No"),
-                           Description = c("5 libraries (youthvars, scorz, specific, TTU and youthu) [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155; @matthew_p_hamilton_2021_5646669], <br> 3 programs [@hamilton_matthew_2022_6129906; @hamilton_matthew_2022_6416330; @hamilton_matthew_p_2022_6321821], 2 sub-routines [@hamilton_matthew_2022_6116385; @matthew_p_hamilton_2022_5976988] and 2 datasets [@DVN/DKDIB0_2021; @DVN/HJXYKQ_2021] are permanently archived with unique identifiers.",
-                                           "All code libraries have documenting websites with URLs that concatenate 'https://ready4-dev.github.io/' and the package name (e.g.
-https://ready4-dev.github.io/youthvars).
-All three Markdown programs are self-documenting, with one [@hamilton_matthew_2022_6129906] including additional instructions in a README file.
-Only one sub-routine [@matthew_p_hamilton_2022_5976988] is documented with a meaningful README file.
-All datasets have meaningful metadata descriptors.",
-                                           "All libraries, programs and sub-routines use the same house style, which allows most library documentation to be written by algorithms from the ready4fun package [@ready4fun2022].
-All libraries except [@matthew_p_hamilton_2021_5646669] use framework syntax, as does one program [@hamilton_matthew_2022_6129906].",
-                                           "All programs use literate programming.",
-                                           "No current reporting of code coverage.",
-                                           "All parts of the study workflow from raw data ingest through to data processing, analysis, reporting and dissemination of study outputs can be reproduced (if granted access to source data) or replicated (using supplied synthetic data) with one program [@hamilton_matthew_2022_6129906].",
-                                           "All code is version controlled using Git and GitHub. All source code is available in a GitHub organisation [@ready4gh2022].",
-                                           "Semantic version is used in all code.
-As no code library has yet been submitted to CRAN, only the development version extensions of each version number have been incremented to date.",
-                                           "All six libraries use continuous integration (CI).
-CI results for each library can be viewed at a URL that concatenates 'https://github.com/ready4-dev/', the package name and '/actions' (e.g.
-https://github.com/ready4-dev/youthvars/actions)",
-                                           "Retired code is deprecated using lifecycle package tools (e.g.
-everything after “## DEPRECATED FNS” in https://github.com/ready4-dev/youthvars/blob/main/data-raw/fns/add.R ).
-Package vignettes and datasets are also deprecated e.g.
-https://ready4-dev.github.io/youthvars/articles/Replication_DS.html )",
-                                           "All development code is stored on repos in a GitHub organisation [@ready4gh2022] and all archived releases are available in a Zenodo community [@ready4zen2022].
-All non-confidential data is stored in repositories within a Harvard Dataverse collection [@ready4dv2022].
-",
-                                           "Four [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155] out of five libraries include encapsulated  modules.
-Examples are the items beginning with Scorz, Specific and Youthvars that are listed in this table: https://ready4-dev.github.io/ready4/articles/V_01.html#current-ready4-framework-modules as well as the S4 classess from the TTU package listed here: https://ready4-dev.github.io/TTU/reference/index.html ",
-                                           "All code libraries include functions.
-The most complete list of functions for each library is available by clicking the 'Manual - Developer (PDF)' link on each package's documentation homepage (see item T2 above).",
-                                           "All modules (see item M2) inherit from the Ready4Module class and can be inherited from.",
-                                           "Two synthetic datasets and their data dictionaries are publicly available in a data repository [@DVN/HJXYKQ_2021].
-One (ymh_clinical_tb.RDS) closely resembles the study dataset and was released so that the main study algorithm [@hamilton_matthew_2022_6129906] can be rerun by those without access to the confidential study dataset.
-The other (eq5d_ds_dict.RDS) is deliberately different to the source dataset in both variable naming convention and the concepts used for predictors and outcome measures and was created to demonstrate generalised applications of study algorithms.",
-                                           "All code libraries, programs and sub-routines use GPL-3 licenses. ",
-                                           "Datasets use amended version of template provided by Harvard Dataverse [@sampleterms2022].",
-                                           "All libraries have CITATION file in inst directory. All code repositories have a CITATION.cff file. All datasets have citation generating metadata.",
-                                           "Model catalogues (PDF files beginning with 'AAA_TTU_MDL_CTG') are available in the study results dataset [@DVN/DKDIB0_2021] and describe the predictive performance of all models under a variety of usage regimes (including when the source dataset in the R model object is replaced with fake data).
-The youthu library [@matthew_p_hamilton_2021_5646669] includes tools for searching for and applyihg models compatible with different types of input data.
-An example program to demonstrate this functionality is available in both RMarkdown [@hamilton_matthew_2022_6416330] and rendered PDF formats (the 'Application.pdf' file in the study results dataset [@DVN/DKDIB0_2021]).
-",
-                                           "No Shiny app user interface has yet been developed."))
+  dplyr::select(Package,
+                Ref,
+                Focus,
+                Standard,
+                `Depends on`)
 
-tb2_nms_chr<-colnames(checklist_df)
-checklist_df <- data.frame(checklist_df[,1],
-                 rep("&nbsp; ",nrow(checklist_df)),
-                 checklist_df[,2],
-                 rep("&nbsp; &nbsp; &nbsp; &nbsp; ",nrow(checklist_df)),
-                 checklist_df[,3],
-                 rep("&nbsp; ",nrow(checklist_df)),
-                 checklist_df[,4])
-colnames(checklist_df) <- c(" "," ","Standard",#
-                             "   ","Met?","   ",
-                            tb2_nms_chr[4])
+names_chr <- names(df)
+df <- data.frame(df[,1],
+                 rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp;"),
+                     nrow(df)),
+                 df[,2:3],
+                 rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp;")
+                     ,nrow(df)),
+                 df[,4],
+                 #rep("&nbsp; &nbsp; &nbsp;",nrow(df)),
+                 df[,5])
+colnames(df) <- c("Package",
+                  ifelse(params$X@outp_formats_chr[1] == "Word","XXX"," "),
+                  "Ref", "Focus", 
+                  ifelse(params$X@outp_formats_chr[1] == "Word","YYY"," "),
+                  "Standard     ",# " ",
+                  "Depends on these R libraries")
+#df$Package <- "![](../Data/images/ready4.png){ width=10% }"#"\\includegraphics[valign=T,scale=2.5,raise=2mm]{../Data/images/ready4.png}"
+df$`Standard     `  <- df$`Standard     ` %>% stringr::str_replace_all("&nbsp;"," ")
 if(params$X@outp_formats_chr[1] == "Word") {
-  checklist_df %>%
+  library("flextable")
+  library("ftExtra")
+  df[,c(1,3:4,6:7)] %>%
     ready4show::print_table(output_type_1L_chr = params$X@outp_formats_chr[1],
@@
                             add_to_row_ls = NULL,
-                            sanitize_fn = NULL)
+                            sanitize_fn = NULL) %>%
+    ftExtra::colformat_md()
   }else{
-    checklist_df %>%
-    kableExtra::kbl(format = "markdown",
-                    booktabs = T,
-                    caption = knitr::opts_current$get("tab.cap")) 
+    df$Ref<-NULL
+    #df$Package <- ""
+    df$Package  <- df$Package %>% 
+                      purrr::map_chr(~paste0("\\includegraphics[valign=M,width=1.9cm,raise=4mm]{../Data/images/",.x,"_logo.png}"))#scale=0.4,raise=3mm]
+    # df$Package <- "\\includegraphics[valign=M,scale=0.08,raise=3mm]{../Data/images/ready4.png}"
+    df[,c(1,3,5:6)]   %>%
+    # kableExtra::kbl(format = "markdown",
+    #                   escape = F,
+    #                 caption = knitr::opts_current$get("tab.cap"))
+      kableExtra::kbl(booktabs = T, 
+                      escape = F,
+                      caption = knitr::opts_current$get("tab.cap")) %>%
+      kableExtra::kable_paper(full_width = F) %>%
+      kableExtra::column_spec(3,latex_valign = "m") %>%
+      # kableExtra::column_spec(1, 
+      #                         image = kableExtra::spec_image(rep("../Data/images/ready4.png",nrow(df)), 
+      #                                                           150, 150)) %>%
+      kableExtra::column_spec(4, width = "24em",latex_valign = "m")
     }

### 2023-01-26 Markdown/Manuscript/Child_RMDs/MS_Tables_3.Rmd
working on discussion

@@
                                         "Version controlled",
-                                        "Semanticly versioned",
+                                        "Semantic versioning",
                                         "Continuously integrated",
@@
                                         ),
-                           Description = c("Development and archived code for 5 libraries (youthvars, scorz, specific, TTU and youthu) [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155; @matthew_p_hamilton_2021_5646669], 3 programs [@hamilton_matthew_2022_6129906; @hamilton_matthew_2022_6416330; @hamilton_matthew_p_2022_6321821], 2 sub-routines [@hamilton_matthew_2022_6116385; @matthew_p_hamilton_2022_5976988] and 2 datasets [@DVN/DKDIB0_2021; @DVN/HJXYKQ_2021] are available.
-See https://www.ready4-dev.com/docs/getting-started/software/libraries/types/module/ (for libraries), https://www.ready4-dev.com/docs/getting-started/software/executables/programs/ (for programs) and https://www.ready4-dev.com/docs/getting-started/software/executables/subroutines/",
-                                           "All code libraries have documenting websites with URLs that concatenate 'https://ready4-dev.github.io/' and the package name (e.g.
+                           Description = c("Datasets are available at https://doi.org/10.7910/DVN/DKDIB0 and https://doi.org/10.7910/DVN/HJXYKQ.
+For details of where to find Development and Archive code see: https://www.ready4-dev.com/docs/getting-started/software/libraries/types/module/  https://www.ready4-dev.com/docs/getting-started/software/executables/programs/  https://www.ready4-dev.com/docs/getting-started/software/executables/subroutines/ ",
+                                           "All code libraries have documenting websites with URLs that concatenate 'https://ready4-dev.github.io/' and the library name (e.g.
 https://ready4-dev.github.io/youthvars).
@@
 All datasets have meaningful metadata descriptors.",
-                                           "All libraries, programs and sub-routines use the same house style, which allows most library documentation to be written by algorithms from the ready4fun package [@ready4fun2022].
+                                           "All libraries are authored with ready4pack [@ready4pack2022] to ensure a consistent house style.
 All libraries except [@matthew_p_hamilton_2021_5646669] use framework syntax, as does one program [@hamilton_matthew_2022_6129906].",
@@
                                            "All parts of the study workflow from raw data ingest through to data processing, analysis, reporting and dissemination of study outputs can be reproduced (if granted access to source data) or replicated (using supplied synthetic data) with one program [@hamilton_matthew_2022_6129906].",
-                                           "All libraries have a CITATION file in  the inst directory. All code repositories have a CITATION.cff file. All datasets have citation generating metadata.",
+                                           "All libraries can return citation details when running R's 'citation' function. All code and data repositories have tools to generate citation details.",
                                            # Reuse
@@
                                            "All code libraries include functions.
-The most complete list of functions for each library is available by clicking the 'Manual - Developer (PDF)' link on each package's documentation homepage (see item T2 above)",
-                                           "All module data-structures and algorithms are distributed as code libraries",
+The most complete list of functions for each library is available by clicking the 'Manual - Developer (PDF)' link on each package's documentation homepage (see item A2 above)",
+                                           "All module data-structures and algorithms are distributed as code libraries.",
                                            "Two synthetic datasets and their data dictionaries are publicly available in a data repository [@DVN/HJXYKQ_2021].
@@
 ",
-                                           "No Shiny app user interface has yet been developed.",
+                                           "No user interface has yet been developed.",
                                         ## Updatable
                                            "All code is version controlled using Git and GitHub. All source code is available in a GitHub organisation [@ready4gh2022].",
-                                           "Semantic version is used in all code.
+                                           "Semantic versioning is used in all code.
 As no code library has yet been submitted to CRAN, only the development version extensions of each version number have been incremented to date.",
                                            "All six libraries use continuous integration (CI).
-CI results for each library can be viewed at a URL that concatenates 'https://github.com/ready4-dev/', the package name and '/actions' (e.g.
+CI results for each library can be viewed at a URL that concatenates 'https://github.com/ready4-dev/', the library name and '/actions' (e.g.
 https://github.com/ready4-dev/youthvars/actions)",
-                                           "Retired code is deprecated using lifecycle package tools (e.g.
+                                           "Retired code is deprecated using tools from the lifecycle R library (e.g.
 everything after “## DEPRECATED FNS” in https://github.com/ready4-dev/youthvars/blob/main/data-raw/fns/add.R ).

### 2023-01-26 setup.R

@@ -5,10 +5,10 @@ library(bookdown)
 library(rticles)
 X <- Ready4showSynopsis(#background_1L_chr = "Our study is entirely fictional.",
                         coi_1L_chr = "None declared.",
-                        conclusion_1L_chr = "We have identified a number of standards that we believe are appropriate to implementing quality OSHEMs in youth mental health. Most of these standards are probably relevant to OSHEMs in other health conditions, though some such as the copyleft licensing may be less relevant to modellers using different tools. Our framework toolkits can help support standardised approaches to dynamic systems model development that are important for collaborative and interdependent projects. ",
+                        #conclusion_1L_chr = "We have identified a number of standards that we believe are appropriate to implementing quality OSHEMs in youth mental health. Most of these standards are probably relevant to OSHEMs in other health conditions, though some such as the copyleft licensing may be less relevant to modellers using different tools. Our framework toolkits can help support standardised approaches to dynamic systems model development that are important for collaborative and interdependent projects. ",
                         digits_int = 3L,
-                        ethics_1L_chr = "Framework development did not involve human subject research and was not ethically reviewed. The worked example of framework application is a previously reported study that was reviewed and granted approval by the University of Melbourne’s Human Research Ethics Committee, and the local Human Ethics and Advisory Group (1645367.1).",
-                        funding_1L_chr = "Framework development was funded by Orygen, VicHealth and Victoria University. The previously reported study used as a worked example was funded by the National Health and Medical Research Council (NHMRC, APP1076940), Orygen and headspace.",
+                        ethics_1L_chr = "Framework development did not involve human subject research and was not ethically reviewed. The utility mapping worked example is a previously reported study that was reviewed and granted approval by the University of Melbourne’s Human Research Ethics Committee, and the local Human Ethics and Advisory Group (1645367.1).",
+                        funding_1L_chr = "Framework development was funded by Orygen, VicHealth and Victoria University. The utility mapping study used as a worked example was funded by the National Health and Medical Research Council (NHMRC, APP1076940), Orygen and headspace.",
                         #interval_chr = "three months",
                         keywords_chr = c("open source models","health economics","mental disorders"),
                         outp_formats_chr = "PDF",
@@ -37,11 +37,11 @@ X <- renewSlot(X,
                "abstract_args_ls",
                {
                  args_ls <- X@abstract_args_ls
-                 args_ls$abstract_ls <- list(Summary = "Health economists make limited use of the modular and open source approaches to model building that other disciplines use to make modelling projects more transparent, efficient and sustainable. 
[…]

### 2023-01-26 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
discussion wip

@@
 
-In this article we introduced a framework that we developed to help us implement a MOSHEM in youth mental health.
-We outlined the standards for accountable, reusable and updatable models specified by that framework and the modelling toolkit we created to help the youth mental health MOSHEM we are developing to meet those standards.
-We also provided an overview of the initial set of model modules we developed with the framework to implement a utility mapping study and summarised the extent to which the outputs of that study adheres to framework standards.
+In this article we introduced a framework that we developed to help us implement a MOSHEM in youth mental health that is accountable, reusable and updatable.
+We outlined the standards for MOSHEMs specified by that framework and described the modelling toolkit we for applying those standards to model development and use.
+We also provided an overview of an initial set of MOSHEM modules we developed with the framework an applied to implement a utility mapping study and reviewed the modules, datasets and analyses from that study against framework standards.
 
@@
 ## Implications for the development of a youth mental helath MOSHEM
-<!-- ### Implications for our modelling team -->
 Mental disorders impose high health, social and economic burdens worldwide [@RN8;@GBD2019].
 Much of this burden is potentially avertable [@RN25], but poorly financed and organised mental health systems are ill-equipped for this challenge[@RN22;@RN23].
-There is therefore an opportunity for economic research to help identify mental health reforms of significant potential public benefit.
+There is therefore an opportunity for health economists to undertake work in mental health of significant potential public benefit.
 To date, economic studies in mental health have predominantly examined the affordability and value for money of individual programs [@RN34].
-This economic evaluation work is an essential prerequisite for developing economically sustainable mental health reform plans, but it needs to be accompanied by and integrated with a broader program of economic research.
-The classification system developed by Wagstaff and Culyer [@wagstaff2012four] identified twelve categories of health economic research.
-In addition to the economic evaluation category, we have prioritised the following areas for the future development of modules for our MOSHEM:
+This economic evaluation work is an essential prerequisite for developing economically sustainable mental health reform plans, but needs to be accompanied by and integrated with a broader program of economic research.
 
-- health and its value [utility and choice],
+We hope that the MOSHEM we are developing will facilitate a synthesis of multiple strands of economic research in youth mental health.
+Initially, we aim to undertake modelling research in four of the twelve domains of health economics from the classification system developed by Wagstaff and Culyer [@wagstaff2012four] :
 
-- demand for health and health care,
+- health and its value (utility mapping models);
 
-- determinants of health and ill-health,
+- determinants of health and ill-health (models for creating rich and representative synthetic household populations from survey data);
 
-- supply of health services,
+- demand for health and health care (spatial epidemiology and help-seeking choice models); and
 
-- efficiency and equity,
+- supply of health services (a model of primary mental health care services).
 
-In economic evaluation, 
-<!-- Yet single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020; @Occhipinti2021].  -->
+We then want to be able to flexibly combine these models to answer questions in two other domains:
 
-<!-- The large and widespread additional mental health burdens recently observed during the COVID-19 pandemic[@20211700] and predicted as a potential future consequence of climate change [@page_howard_2010], highlight the need to improve the resilience and adaptability of these systems.
-To help stem growing demand for mental health services, policymakers have also been encouraged to place greater emphasis on tackling the social determinants of mental disorders [@RN11].
--->
+- efficiency and equity (optimising targeting of care and assessing the distributional impacts of candidate policies); and
 
- - Aims of our model (multi-purpose, focused on systems reform)
- - Addressing wagstaff areas ()
- - Adequacy of current methods / our capacity (errors / impact)
- - One shot at big changes
- - Opportunities for others to leverage and enhance
- - Our analysis - do it in stages, be transparent, continually improve, get help, be flexible (modelling toolkit / monolithic model), have a framework
+- economic evaluation (assessing cost-utility of competing policy options).
 
- - Strengths (comparisons to existing work, benefits to ourselves and others)
+When planning how to undertake and synthesise this program of work, we became concerned with issues relating to validity and granularity.
+We know that mistakes are easy to make in individual health economic modelling projects [@Radeva2020], an issue that is likely to be compounded when combining multiple projects.
+Similarly, the likelihood of certain types of error can increase if a model is too simple or too complex [@Saltelli2019], so the level of granularity appropriate for one model application may be ill-suited to another.
+These concerns led us to seeking an approach that was both open source (to provide the transparency that makes it easier for errors to be uncovered) and modular (to facilitate interchangeability between representations of different levels of granularity).
+However, because MOSHEMs are not common in health economics, we were unable to identify one up to date and consolidated source of guidance about how to undertake this work.
+We developed the framework's standards to fill this gap, choosing the framing of standards rather than guidelines because standardisation is an essential enabler of the interoperable and collaborative features of MOSHEMS.
+The framework's standards make explicit our goal to implement an accountable, reusable and updatable MOSHEM and provide a mechanism to assess how well this goal is being met.
+We have partially automated many of the steps for meeting those standards through the tools we developed for the framework's modelling toolkit and have been able to demonstrate the practical application of this toolkit through its use in implementing a utility mapping study [@Hamilton2021.07.07.21260129].
+This toolkit is expected to be a source of significant efficiency savings as we implement other projects in the current phase of development of our youth mental health MOSHEM.
 
- - Limitations (technical, not behavioural / institutional solution)
+ <!-- - One shot at big changes -->
+ <!-- - Our analysis - do it in stages, be transparent, continually improve, get help, be flexible (modelling toolkit / monolithic model), have a framework -->
+ <!-- A coding framework for MOSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions [@Alarid2019]. -->
 
-<!-- A coding framework for MOSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions [@Alarid2019]. -->
-<!-- Our approach to model development is to undertake a number of discrete modelling projects of the people, places, platforms and programs that shape the mental health and wellbeing of young people and to progressively link them together by means of a common framework.
-To model people we are developing synthetic representations of populations of interest [@DVN/HJXYKQ_2021] that describe relevant individual characteristics and their relationships, algorithms that map psychological measures to health utility [@Hamilton2021.07.07.21260129] and choice models for predicting the helpseeking behaviour of young people [@hamilton_matthew_2022_6627995].
-Our in-development model of places [@DVN/V3OKZV_2022] has the aim of synthesising geometry and spatial attribute data to characterise the geographic distribution of relevant demographic, environmental, epidemiological and service infrastructure features.
-We are in the early stages of a multi-annual project to develop a service platform model that will represent the processes and operations of a complex primary youth mental health service.
-We also plan to extend and update our prior work reviewing economic evidence relating to youth mental health programs [@RN33] so that it can be integrated with this model.
-Our initial work on **readyforwhatsnext** is focused on Victoria, Australia but the framework we are using to develop it is designed to facilitate extension by ourselves and others to different jurisdictional decision contexts.
-Progress is reported on a project website [@rfwn2022].
--->
-Major mental health reform programs, <!-- such as those currently being implemented in Victoria, Australia [@VicRC2021],  -->can involve the identification, prioritisation, sequencing, targeting and monitoring of multiple interdependent initiatives.
+However, the framework represents a technical capacity and is not a behavioural outcome.
+Having features to facilitate accountability, reuse and updating does not guarantee being that our OSHEM will be meaningfully held accountable, reused and updated.
+Making code and data publicly available may make limited impact on error detection unless third parties begin to use these artefacts in their own projects.
+Currently all the framework and module libraries we have developed are available only as "development" releases.
+Further development, testing and documenting before we submit production versions of each library to the Comprehensive R Archive Network (CRAN) [@CRAN2022].
+Having these libraries available on CRAN is a likely prerequisite of significant levels of reuse.
 
-The significant deficits in our understanding of the systems in which mental disorders emerge and are treated [@Fried2020] suggest that there is ample scope for mental health systems models to progressively improve their validity over time.
-Prospective work could address the weak theoretical underpinnings for understanding complex mental health systems [@RN2111].
-For example, it remains unclear why increased investments in mental health care have yet to discernibly reduce the prevalence and burden of mental disorders[@RN26].
-The  literature, and evidence base, regarding how the requirements, characteristics and performance of mental health services are shaped by spatiotemporal context needs to be further developed [@RN42].
-There is also a need for better evidence to identify the social determinants of mental disorders most amenable to preventative interventions, and for which population sub-groups such interventions would be most effective [@RN43].
+Estimating the potential uptake of these tools is difficult.
+Mental health topics accounted for about 268 of 2829 (10%) economic evaluations undertaken during 26 month period in 2012-2014 identified in a previous review [@pitt2016economic].
 
-The development, validation and updating of more complex mental health economic models implemented over longer time frames may be too onerous a burden for a single modelling team.
-
-<!-- ### Implications for potential users of and contributors to our model -->
-
-Another future priority is to submit production versions of each R package for review by and archiving on the Comprehensive R Archive Network (CRAN) [@CRAN2022].
 Developing networks of modellers working on common health conditions has been recommended as a strategy for improving model validity [@Sampson2019] and some of us are part of a nascent initiate of this type in mental health [@nmhsmn2022].
@@
 <!-- ## Why develop OSHEMs in mental health -->
+
+Major mental health reform programs, <!-- such as those currently being implemented in Victoria, Australia [@VicRC2021],  -->can involve the identification, prioritisation, sequencing, targeting and monitoring of multiple interdependent initiatives.
+
+The significant deficits in our understanding of the systems in which mental disorders emerge and are treated [@Fried2020] suggest that there is ample scope for mental health systems models to progressively improve their validity over time.
+Prospective work could address the weak theoretical underpinnings for understanding complex mental health systems [@RN2111].
+For example, it remains unclear why increased investments in mental health care have yet to discernibly reduce the prevalence and burden of mental disorders[@RN26].
+The  literature, and evidence base, regarding how the requirements, characteristics and performance of mental health services are shaped by spatiotemporal context needs to be further developed [@RN42].
+There is also a need for better evidence to identify the social determinants of mental disorders most amenable to preventative interventions, and for which population sub-groups such interventions would be most effective [@RN43].
+
+The development, validation and updating of more complex mental health economic models implemented over longer time frames may be too onerous a burden for a single modelling team.
 
@@
  <!-- as part of the Open Value Initiative [@Jansen2019].  -->
+
+ <!-- Yet single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020; @Occhipinti2021].  -->
+<!-- The large and widespread additional mental health burdens recently observed during the COVID-19 pandemic[@20211700] and predicted as a potential future consequence of climate change [@page_howard_2010], highlight the need to improve the resilience and adaptability of these systems.
+To help stem growing demand for mental health services, policymakers have also been encouraged to place greater emphasis on tackling the social determinants of mental disorders [@RN11].
+-->
+
+<!-- Our approach to model development is to undertake a number of discrete modelling projects of the people, places, platforms and programs that shape the mental health and wellbeing of young people and to progressively link them together by means of a common framework.
+To model people we are developing synthetic representations of populations of interest [@DVN/HJXYKQ_2021] that describe relevant individual characteristics and their relationships, algorithms that map psychological measures to health utility [@Hamilton2021.07.07.21260129] and choice models for predicting the helpseeking behaviour of young people [@hamilton_matthew_2022_6627995].
+Our in-development model of places [@DVN/V3OKZV_2022] has the aim of synthesising geometry and spatial attribute data to characterise the geographic distribution of relevant demographic, environmental, epidemiological and service infrastructure features.
+We are in the early stages of a multi-annual project to develop a service platform model that will represent the processes and operations of a complex primary youth mental health service.
+We also plan to extend and update our prior work reviewing economic evidence relating to youth mental health programs [@RN33] so that it can be integrated with this model.
+Our initial work on **readyforwhatsnext** is focused on Victoria, Australia but the framework we are using to develop it is designed to facilitate extension by ourselves and others to different jurisdictional decision contexts.
+Progress is reported on a project website [@rfwn2022].
+-->

### 2023-01-28 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
moved items from disucussion to introduction

@@
 
-In this paper, we introduce a framework for developing a modular youth mental health MOSHEM. Specifically we:
+In this paper, we introduce a framework for developing the ready4 MOSHEM. Specifically we:
 
@@
 
-(ii) provide a worked example of how we used the framework to develop and apply MOSHEM modules for utility mapping.
+(ii) provide a worked example of how we used the framework to develop and apply ready4 modules for utility mapping.

### 2023-01-28 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
moved items from disucussion to introduction

@@
 
-In this article we introduced a framework that we developed to help us implement a MOSHEM in youth mental health that is accountable, reusable and updatable.
-We outlined the standards for MOSHEMs specified by that framework and described the modelling toolkit we for applying those standards to model development and use.
-We also provided an overview of an initial set of MOSHEM modules we developed with the framework an applied to implement a utility mapping study and reviewed the modules, datasets and analyses from that study against framework standards.
+In this article we introduced a framework that we developed to help us implement ready4 - a MOSHEM in youth mental health.
+We outlined framework standards for an accountable, reusable and updatable MOSHEM and described the modelling toolkit we for applying those standards to the development and use of ready4.
+We also provided an overview of an initial set of ready4 modules that we developed with the framework and which we applied to implement a utility mapping study in a clinical mental health sample of young people.
+We reviewed the modules, datasets and analyses generated by that study against framework standards.
 
-The work we have described raises a number of issues relating to the future development of a youth mental health MOSHEM, for health economists interested in undertaking other MOSHEMS and for health research funders.
+The strengths.
+limitations and issues raised by this work can be discussed in terms of relevance to future development of the ready4 MOSHEM, to health economists interested in undertaking other MOSHEMS and to funders of health economic research.
 
-## Implications for the development of a youth mental helath MOSHEM
-Mental disorders impose high health, social and economic burdens worldwide [@RN8;@GBD2019].
-Much of this burden is potentially avertable [@RN25], but poorly financed and organised mental health systems are ill-equipped for this challenge[@RN22;@RN23].
-There is therefore an opportunity for health economists to undertake work in mental health of significant potential public benefit.
-To date, economic studies in mental health have predominantly examined the affordability and value for money of individual programs [@RN34].
-This economic evaluation work is an essential prerequisite for developing economically sustainable mental health reform plans, but needs to be accompanied by and integrated with a broader program of economic research.
+## Implications for the development of the ready4 MOSHEM
+Open source approaches have been recommended to help develop the mental health modelling field [@RN73] but only one mental health related model (in Alcohol Use Disorder [@Basu2018]) is currently indexed [RECHECK] in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019].
+We  are aware of just one other open source mental health model - a reference model in Major Depressive Disorder - that is currently in development [@IVIMDD2022].
 
-We hope that the MOSHEM we are developing will facilitate a synthesis of multiple strands of economic research in youth mental health.
-Initially, we aim to undertake modelling research in four of the twelve domains of health economics from the classification system developed by Wagstaff and Culyer [@wagstaff2012four] :
+One of the main novel contributions of the framework we have developed is that it declares an explicit set of standards for the implementation and use of a MOSHEM.
+Standardisation is an essential enabler of workflow automation, module interoperability, and transferability of methods<!-- and efficient collaboration  -->.
+The framework's modelling toolkit has enabled us to partially automate workflows for authoring, documenting and disseminating ready4 modules, datasets and analyses.
+The modelling toolkit's practical utility has been demonstrated through its application in creating all ready4 components used in a utility mapping study [@Hamilton2021.07.07.21260129] and the automation it facilitates makes the development and curation of a large and growing number of ready4 digital assets more tractable.
+The interoperability of the ready4 modules we have developed today is demonstrated in multiple example literate programs on the ready4 documentation website [@rfwn2022] and in the program used to implement the utility mapping analysis [@hamilton_matthew_2022_6129906].
 
-- health and its value (utility mapping models);
-
-- determinants of health and ill-health (models for creating rich and representative synthetic household populations from survey data);
-
-- demand for health and health care (spatial epidemiology and help-seeking choice models); and
-
-- supply of health services (a model of primary mental health care services).
-
-We then want to be able to flexibly combine these models to answer questions in two other domains:
-
-- efficiency and equity (optimising targeting of care and assessing the distributional impacts of candidate policies); and
-
-- economic evaluation (assessing cost-utility of competing policy options).
-
-When planning how to undertake and synthesise this program of work, we became concerned with issues relating to validity and granularity.
-We know that mistakes are easy to make in individual health economic modelling projects [@Radeva2020], an issue that is likely to be compounded when combining multiple projects.
-Similarly, the likelihood of certain types of error can increase if a model is too simple or too complex [@Saltelli2019], so the level of granularity appropriate for one model application may be ill-suited to another.
-These concerns led us to seeking an approach that was both open source (to provide the transparency that makes it easier for errors to be uncovered) and modular (to facilitate interchangeability between representations of different levels of granularity).
-However, because MOSHEMs are not common in health economics, we were unable to identify one up to date and consolidated source of guidance about how to undertake this work.
-We developed the framework's standards to fill this gap, choosing the framing of standards rather than guidelines because standardisation is an essential enabler of the interoperable and collaborative features of MOSHEMS.
-The framework's standards make explicit our goal to implement an accountable, reusable and updatable MOSHEM and provide a mechanism to assess how well this goal is being met.
-We have partially automated many of the steps for meeting those standards through the tools we developed for the framework's modelling toolkit and have been able to demonstrate the practical application of this toolkit through its use in implementing a utility mapping study [@Hamilton2021.07.07.21260129].
-This toolkit is expected to be a source of significant efficiency savings as we implement other projects in the current phase of development of our youth mental health MOSHEM.
+The framework's standards also provide a mechanism to assess the extent to which ready4 meets explicit accountability, reusability and updatability goals.
 

### 2023-01-28 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
moved items from disucussion to introduction

@@
 
-We developed a toolkit to help us develop and use a MOSHEM that meets the standards listed in Table \@ref(tab:timelygls). The toolkit is comprised of online repositories and software.
+We developed a toolkit to help us develop and use ready4 modules, datasets and analyses that meet the standards listed in Table \@ref(tab:timelygls).
+The toolkit is comprised of online repositories and software.
 
@@
 For hosting documentation websites for the code libraries we create, we enabled GitHub Pages in each library's repository.
-We also developed a consolidated project documentation website (https://www.ready4-dev.com), using the Hugo framework [@hugo_2023] and Docsy theme [@docsy_2023].
+We also developed a consolidated project documentation website [@rfwn2022], using the Hugo framework [@hugo_2023] and Docsy theme [@docsy_2023].
 To host that website we established an account with Netlify [@netlify_2023] and linked that service to our GitHub organisation so that the website would automatically update whenever the source code in its GitHub repository was edited.
@@
 
-The foundation for our MOSHEM is provided by the ready4 library [@ready42022] that defines a template module (using R's S4 type class) from which all model module data structures will inherit features and a novel syntax for implementing the algorithms attached to model modules.
+The foundation for ready4 is provided by a library called ready4 [@ready42022] that defines a template module (using R's S4 type class) from which all model module data structures will inherit features and a novel syntax for implementing the algorithms attached to model modules.
 The ready4 library also contains tools for retrieving web based information on model modules, datasets and analysis programs and for partially automating updates to the project website.
@@
 
-The ready4use [@ready4use2022] library contains modules for ingesting model datasets from online repositories (hosted on a Dataverse installation or on GitHub), labelling model datasets and sharing model datasets via online repositories.
+The ready4use library  [@ready4use2022] contains modules for ingesting model datasets from online repositories (hosted on a Dataverse installation or on GitHub), labelling model datasets and sharing model datasets via online repositories.
 The ready4show library [@ready4show2022] contains tools to help author analyses programs that are either self-documenting or which trigger the creation of a scientific summary.

### 2023-01-28 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
moved items from disucussion to introduction

@@
 
-We plan to develop a modular OSHEM (MOSHEM) of youth mental health that is accountable, reusable and updatable.
-Open source approaches have been recommended to help develop the mental health modelling field [@RN73] but only one mental health related model (in Alcohol Use Disorder [@Basu2018]) is currently indexed [RECHECK] in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019].
-We  are aware of just one other open source mental health model - a reference model in Major Depressive Disorder - that is currently in development [@IVIMDD2022].
+Our interest in modular and open source source approaches developed when we began seeking am appropriate framework for undertaking and validly synthesising diverse types of economic research in mental health.
+Mental disorders impose high health, social and economic burdens worldwide [@RN8;@GBD2019].
+Much of this burden is potentially avertable [@RN25], but poorly financed and organised mental health systems are ill-equipped for this challenge [@RN22;@RN23].
+A substantial economic literature already exists to assess the affordability and value for money of mental health interventions [@RN34].
+This economic evaluation work is an essential prerequisite for improving allocative efficiency in mental health, but could be of greater value to systems planners if integrated with a broader program of economic research.
+
+We are developing ready4, a modular OSHEM (MOSHEM) on the mental health of young people aged 12 to 25 that we are initially applying to four of the twelve domains of health economics identified by Wagstaff and Culyer [@wagstaff2012four]:
+<!-- There is therefore an opportunity for health economists to undertake mental health research of significant potential public benefit. -->
+
+- *health and its value* (our projects: utility mapping models);
+
+- *determinants of health and ill-health* (our projects: models for creating rich and representative synthetic household populations from survey data);
+
+- *demand for health and health care* (our projects: spatial epidemiology and help-seeking choice models); and
+
+- *supply of health services* (our projects: a model of primary mental health care services).
+
+Once these projects are completed, our aim is to flexibly combine these models to answer questions in two additional Wagstaff and Culyer domains:
+
+- *efficiency and equity* (our goal: assess the distributional impacts and identify the optimal targeting of care provision); and
+
+- *economic evaluation* (our goal: assess the cost-utility of competing policy options).
+
+Standardisation is an essential enabler of workflow automation, module interoperability, and transferability of methods<!-- and efficient collaboration  -->.
+
+<!-- When planning how to undertake and synthesise this program of work, we became concerned with issues relating to accountability, reusability and updatability.
+If mistakes are common in individual health economic modelling projects [@Radeva2020], then combining multiple projects may be particularly error prone.
+The risk of errors may also depend on whether a model is too simple or too complex [@Saltelli2019], so the level of granularity appropriate for one model application may be ill-suited to another.
+Undertaking a multiannual program of interdependent work raises the risk that models developed in the first phase of a project may need to be updated by the time the project is approaching conclusion.
+-->
+
+<!-- These concerns led us to seek the MOSHEM approach that provides the transparency to make it easier for errors to be uncovered, the adaptability to fix these errors and the flexibility to facilitate interchangeability between representations of different levels of granularity.
+-->

### 2023-01-29 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
minor tweaks

@@
 
-In this paper, we introduce a framework for developing the ready4 MOSHEM. Specifically we:
+In this paper, we:
 
-(i) describe a framework that is comprised of:
-  - a set of standards for implementing a MOSHEM; and
-  - a modelling toolkit (repositories and software) to author MOSHEM modules, supply them with data and undertake reproducible analyses consistent with those standards.
+(i) describe a framework comprised of:
+  - a set of standards for implementing an accountable, reusable and updatable MOSHEM; and
+  - a modelling toolkit (online repositories and software) for applying those standards to the authoring of ready4 modules, datasets and analyses.
 

### 2023-01-29 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
minor tweaks

@@
 In this article we introduced a framework that we developed to help us implement ready4 - a MOSHEM in youth mental health.
-We outlined framework standards for an accountable, reusable and updatable MOSHEM and described the modelling toolkit we for applying those standards to the development and use of ready4.
-We also provided an overview of an initial set of ready4 modules that we developed with the framework and which we applied to implement a utility mapping study in a clinical mental health sample of young people.
+We outlined framework standards for an accountable, reusable and updatable MOSHEM and described the modelling toolkit we created for applying those standards to the development and use of ready4.
+We also provided an overview of an initial set of ready4 modules developed with the framework to implement a utility mapping study.
 We reviewed the modules, datasets and analyses generated by that study against framework standards.
 
-The strengths.
-limitations and issues raised by this work can be discussed in terms of relevance to future development of the ready4 MOSHEM, to health economists interested in undertaking other MOSHEMS and to funders of health economic research.
+The strengths, limitations and issues raised by this work can be discussed in terms of relevance to future development of ready4, to health economists interested in undertaking other MOSHEMS and to funders of health economic research.
 
 ## Implications for the development of the ready4 MOSHEM
-Open source approaches have been recommended to help develop the mental health modelling field [@RN73] but only one mental health related model (in Alcohol Use Disorder [@Basu2018]) is currently indexed [RECHECK] in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019].
-We  are aware of just one other open source mental health model - a reference model in Major Depressive Disorder - that is currently in development [@IVIMDD2022].
-
 One of the main novel contributions of the framework we have developed is that it declares an explicit set of standards for the implementation and use of a MOSHEM.
-Standardisation is an essential enabler of workflow automation, module interoperability, and transferability of methods<!-- and efficient collaboration  -->.
-The framework's modelling toolkit has enabled us to partially automate workflows for authoring, documenting and disseminating ready4 modules, datasets and analyses.
+A practical benefit of specifying these standards is that it enabled us to develop a modelling toolkit to partially automate workflows for authoring, documenting and disseminating ready4 modules, datasets and analyses.
 The modelling toolkit's practical utility has been demonstrated through its application in creating all ready4 components used in a utility mapping study [@Hamilton2021.07.07.21260129] and the automation it facilitates makes the development and curation of a large and growing number of ready4 digital assets more tractable.
@@
 The framework's standards also provide a mechanism to assess the extent to which ready4 meets explicit accountability, reusability and updatability goals.
+
+Open source approaches have been recommended to help develop the mental health modelling field [@RN73] but only one mental health related model (in Alcohol Use Disorder [@Basu2018]) is currently indexed [RECHECK] in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019].
+We  are aware of just one other open source mental health model - a reference model in Major Depressive Disorder - that is currently in development [@IVIMDD2022].
 

### 2023-01-29 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
minor tweaks

@@
 
-We are developing ready4, a modular OSHEM (MOSHEM) on the mental health of young people aged 12 to 25 that we are initially applying to four of the twelve domains of health economics identified by Wagstaff and Culyer [@wagstaff2012four]:
+We are developing ready4 (https://www.ready4-dev.com), a modular OSHEM (MOSHEM) on the mental health of young people aged 12 to 25.
+We are initially applying ready4 to four of the twelve domains of health economics identified by Wagstaff and Culyer [@wagstaff2012four]:
 <!-- There is therefore an opportunity for health economists to undertake mental health research of significant potential public benefit. -->
@@
 
-Standardisation is an essential enabler of workflow automation, module interoperability, and transferability of methods<!-- and efficient collaboration  -->.
+To undertake this work we first needed to develop a framework for standardisation.
+Standardisation is an essential enabler of automation, collaboration, interoperability and transferability in modular and open source approaches.
+However, MOSHEMs remain rare and is unclear what standards are most appropriate to specify.
+A MOSHEMs is a computational modelling project, so standards developed for ready4 will need to be verified and implemented by software, some of which will need to be developed for this specific purpose.
 

### 2023-01-30 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
wip on discussion

@@
   - a set of standards for implementing an accountable, reusable and updatable MOSHEM; and
-  - a modelling toolkit (online repositories and software) for applying those standards to the authoring of ready4 modules, datasets and analyses.
+  - a modelling toolkit (online repositories and software) for applying those standards to the authoring of ready4 modules, datasets and analyses; and
 

### 2023-01-30 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
wip on discussion

@@
 
-The strengths, limitations and issues raised by this work can be discussed in terms of relevance to future development of ready4, to health economists interested in undertaking other MOSHEMS and to funders of health economic research.
+The work we have described has implications for the future development of the ready4 model and highlights a number of issues for health economists and funders of health economic research.
 
 ## Implications for the development of the ready4 MOSHEM
-One of the main novel contributions of the framework we have developed is that it declares an explicit set of standards for the implementation and use of a MOSHEM.
-A practical benefit of specifying these standards is that it enabled us to develop a modelling toolkit to partially automate workflows for authoring, documenting and disseminating ready4 modules, datasets and analyses.
-The modelling toolkit's practical utility has been demonstrated through its application in creating all ready4 components used in a utility mapping study [@Hamilton2021.07.07.21260129] and the automation it facilitates makes the development and curation of a large and growing number of ready4 digital assets more tractable.
-The interoperability of the ready4 modules we have developed today is demonstrated in multiple example literate programs on the ready4 documentation website [@rfwn2022] and in the program used to implement the utility mapping analysis [@hamilton_matthew_2022_6129906].
-
+The most direct implication of the development of the framework is that it makes it feasible for us to implement ready4 as a MOSHEM.
+The standards specified by the framework make it possible to partially automate workflows for developing and applying ready4 through use of the framework's modelling toolkit.
 The framework's standards also provide a mechanism to assess the extent to which ready4 meets explicit accountability, reusability and updatability goals.
+We have demonstrated the practical utility of the modelling toolkit by applying it to authoring, documenting and disseminating ready4 module libraries  [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155; @matthew_p_hamilton_2021_5646669]], datasets [@DVN/HJXYKQ_2021; @DVN/DKDIB0_2021]; analyses [@hamilton_matthew_2022_6129906; @hamilton_matthew_2022_6416330; @hamilton_matthew_p_2022_6321821] and reporting templates [@hamilton_matthew_2022_6116385; @matthew_p_hamilton_2022_5976988] used in a utility mapping study [@Hamilton2021.07.07.21260129].
+The automation (described in more detail on the project documentation website [@rfwn2022]) of significant sections of the workflows used in creating and sharing these artefacts has the potential to generate significant efficiencies as we extend ready4 to model help-seeking choice, spatial epidemiology, household populations and primary mental health services.
+The interoperability of the ready4 modules we have developed with the modelling toolkit is demonstrated in the program used to implement the utility mapping analysis [@hamilton_matthew_2022_6129906] and in multiple example literate programs published on the ready4 documentation website [@rfwn2022].
+We have used some of these example programs in conjunction with toy data [@DVN/HJXYKQ_2021] to illustrate the potential for ready4 modules to facilitate study replication and transferability.
 
@@
 Having these libraries available on CRAN is a likely prerequisite of significant levels of reuse.
+
+<!-- Is it desirable for this to become default authoring tool or better to be replication tool. -->
 

### 2023-01-30 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
wip on discussion

@@
 
-We applied the framework to develop modules for developing utility mapping models, supplying those modules with data and implementing utility mapping analyses.
-The study for which these tools were developed and which applied them to developing utility mapping models for a clinical mental health sample of young people has been previously described [@Hamilton2021.07.07.21260129].
-The outputs we authored using the framework's modelling toolkit include:
+We applied the framework to develop ready4 modules for developing utility mapping models, supplying those modules with data and implementing utility mapping analyses.
+These tools were created to develop utility mapping models for a clinical mental health sample of young people in a study that has been previously described [@Hamilton2021.07.07.21260129].
+The framework's modelling toolkit created the following ready artefacts:
 
@@
 
-When we assesses these study outputs against each framework standard, we conclude that 18 standards were wholly or mostly met (see Table \@ref(tab:checktb)).
+When we assesses these study outputs against each framework standard, we conclude that 18 out of 20 standards were wholly or mostly met (see Table \@ref(tab:checktb)).
 The two standards where the study outputs currently fall short are in reporting code coverage and including a user-interface.

### 2023-01-30 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
wip on discussion

@@
 
-Based on published guidance on computational modelling in health economics and other disciplines and our own experience, we have identified 20 standards that we believe are important for implementing a MOSHEM that is accountable (seven standards), reusable (nine standards) and updatable (four standards).
+Based on published guidance on computational modelling in health economics and other disciplines as well as our own experience in developing ready4, we have identified 20 standards that we believe are important for implementing a MOSHEM that is accountable (seven standards), reusable (nine standards) and updatable (four standards).
 The standards are specified in Table \@ref(tab:timelygls) and are discussed below.
@@
 
-Storing model code and data in separate files and locations (as opposed to hard coding - embedding data into source code) can make it easier to apply models to different decision contexts and, when necessary, to selectively restrict access to data that are confidential, while disseminating all other model artefacts.
-Clear distinctions should be made between model modules (code that defines abstract data structures and the algorithms that can be applied to data described by these structures), model datasets (digital information such as parameter values, unit records, etc) and model analyses (code that links model datasets to model modules and specifies the algorithms to apply to the data associated with each module).
+Storing model code and data in separate files and locations (as opposed to hard coding - embedding data into source code) can make it easier to apply models to different decision contexts and to selectively restrict access to data that are confidential, while disseminating all other model artefacts.
+Clear distinctions should be made between model modules (code that defines abstract data structures and the algorithms that can be applied to data described by these structures), model datasets (digital information such as parameter values, unit records, etc) and model analyses (code that links model datasets to model modules and specifies the algorithms to apply to data associated with each module).
 
-The coding practice of encapsulation [@8717448] can be used to help ensure that model modules continue to work as intended even when they are combined [@ready4oop2022].
+The coding practice of encapsulation [@8717448] can be used to help ensure that model modules continue to work as intended when they are combined [@ready4oop2022].
 In some cases, combining modules may mean new versions of modules have to be created to better account for interaction effects.
@@
 Another way to make MOSHEMs easier to use is to develop simple user-interfaces for non-technical users.
-In the open source R language, such user-interfaces are typically developed with the Shiny package, for which a tutorial aimed at health economists is available [@SmithR2020].
 
@@
 Finally, using deprecation conventions that take an informative and staged approach to retiring old code and data reduces the risk that model revisions have unintended consequences on third party users.
-The package lifeycle [@lifecycle2021] provides tools for R developers to consistently deprecate their code.

### 2023-01-30 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
wip on discussion

@@
 
-- licensed (with GPL-3 by default);
+- licensed (using GNU GPL-3 [@GNUGPL2022] by default);
 
@@
 
-- quality assured (triggering continuous integration workflows, including any unit tests created by module library authors).
+- quality assured (each update triggers continuous integration workflows, including any unit tests created by module library authors).
 
-The ready4pack library is designed to integrate with our GitHub organisation and depends on the other two module authoring libraries.
-Methods from the ready4fun library [@ready4fun2022] are used to verify that functions for implementing module algorithms are written in a consistent house style and to use their standardised format to automatically generate basic documentation for each function.
+The ready4pack library is designed to integrate with our GitHub organisation and depends on two other module authoring libraries.
+Methods from the ready4fun library [@ready4fun2022] are used to verify that functions for implementing module algorithms are written in a consistent house style.
+The standardised format is then used by ready4fun to automatically generate basic documentation for each function.
 Methods from the ready4class [@ready4class2022] library are used to streamline and standardise the authoring of module data-structures.
-Like ready4fun, the ready4class library uses standardised naming conventions to automatically generate basic documentation for each module data-structure.
+Like ready4fun, the ready4class library uses standardised code implementation to automatically generate basic documentation for each module data-structure.
 
@@
 
-When used in conjunction with repositories, the six R libraries provide strong support for implementing 17 framework standards.
-However, the software only weakly supports implementing the standards relating to safe dissemination of statistical models (R8) and user-interface development (R9) and does not yet provide any workflow tools to help implement the standard for deprecation conventions (U4).
-Standards not supported or weakly supported by our software can be met with existing developer tools in R.
+When used in conjunction with repositories, the six R libraries provide strong support for implementing 17 out of 20 framework standards.
+Standards relating to safe dissemination of statistical models (R8), user-interface development (R9) and deprecation conventions (U4) are better met through using existing third party R libraries.
+Preparing statistical models for dissemination can be accomplished with standard R data management tools like the dplyr [@dplyr2022] and purrr [@dplyr2022] libraries.
+User-interfaces are typically developed with the shiny [@shiny2022] library, for which a tutorial aimed at health economists is available [@SmithR2020].
+The library lifeycle [@lifecycle2021] provides tools for R developers to consistently deprecate their code.
 

### 2023-01-30 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
wip on discussion

@@
 Standardisation is an essential enabler of automation, collaboration, interoperability and transferability in modular and open source approaches.
-However, MOSHEMs remain rare and is unclear what standards are most appropriate to specify.
-A MOSHEMs is a computational modelling project, so standards developed for ready4 will need to be verified and implemented by software, some of which will need to be developed for this specific purpose.
+However, we are not aware of any appropriate single source of guidance about what standards should be specified for MOSHEMs.
+To be deployed in computational models, the standards specified for ready4 will need to be implemented by software, some of which will need to be developed for this specific purpose.
 

### 2023-01-30 Markdown/Manuscript/Child_RMDs/MS_Tables_2.Rmd
wip on discussion

@@
 ---
-```{r cpkgs, tab.cap='Modelling toolkit R packages for developing and using MOSHEMs that meet framework standards', tab.id = 'cpkgs', echo = F, results = 'asis'}
+```{r cpkgs, tab.cap='Modelling toolkit R libraries for developing and using MOSHEMs that meet framework standards', tab.id = 'cpkgs', echo = F, results = 'asis'}
 library(kableExtra)  

### 2023-01-30 Markdown/Manuscript/Child_RMDs/MS_Tables_3.Rmd
wip on discussion

@@
                                            "Datasets use amended version of template provided by Harvard Dataverse [@sampleterms2022].",
-                                           "All development code is stored on repos in a GitHub organisation [@ready4gh2022] and all archived releases are available in a Zenodo community [@ready4zen2022].
-All non-confidential data is stored in repositories within a Harvard Dataverse collection [@ready4dv2022].
+                                           "All development code is stored on repos in a GitHub organisation [@ready4gh2022] and all archived code releases are available in a Zenodo community [@ready4zen2022].
+All non-confidential data are stored in repositories within a Harvard Dataverse collection [@ready4dv2022].
 ",
@@
                                            "All code libraries include functions.
-The most complete list of functions for each library is available by clicking the 'Manual - Developer (PDF)' link on each package's documentation homepage (see item A2 above)",
-                                           "All module data-structures and algorithms are distributed as code libraries.",
+The most complete list of functions for each library is available by clicking the 'Manual - Developer (PDF)' link on each package's documentation homepage (see item A2 above).
+The relationship between functions can be illustrated using an app: https://www.ready4-dev.com/docs/getting-started/software/libraries/dependencies/",
+                                           "All module data-structures and algorithms are distributed as five code libraries [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155; @matthew_p_hamilton_2021_5646669].",
                                            "Two synthetic datasets and their data dictionaries are publicly available in a data repository [@DVN/HJXYKQ_2021].
@@
                                         ## Updatable
-                                           "All code is version controlled using Git and GitHub. All source code is available in a GitHub organisation [@ready4gh2022].",
+                                           "All code is version controlled using git [@git20XX] and GitHub [@github2007]. All source code is available in a GitHub organisation [@ready4gh2022].",
                                            "Semantic versioning is used in all code.
-As no code library has yet been submitted to CRAN, only the development version extensions of each version number have been incremented to date.",
-                                           "All six libraries use continuous integration (CI).
+As no code library has yet been submitted to CRAN [@CRAN2022], only the development version extensions of each version number have been incremented to date.",
+                                           "All five libraries use continuous integration (CI).
 CI results for each library can be viewed at a URL that concatenates 'https://github.com/ready4-dev/', the library name and '/actions' (e.g.
 https://github.com/ready4-dev/youthvars/actions)",
-                                           "Retired code is deprecated using tools from the lifecycle R library (e.g.
+                                           "Retired code is deprecated using tools from the lifecycle R library [lifecycle2021] (e.g.
 everything after “## DEPRECATED FNS” in https://github.com/ready4-dev/youthvars/blob/main/data-raw/fns/add.R ).

### 2023-01-30 setup.R

@@ -38,17 +38,17 @@ X <- renewSlot(X,
                {
                  args_ls <- X@abstract_args_ls
                  args_ls$abstract_ls <- list(Summary = "Health economists make limited use of the modular and open source approaches to model building that other disciplines use to make large modelling projects more transparent, efficient and sustainable. 
-                                             We propose a framework for a modular open source health economic model (MOSHEM) in youth mental health.
+                                             We propose a framework for developing a modular open source health economic model (MOSHEM) in youth mental health called ready4.
                                              The framework includes of set of 20 standards for implementing a MOSHEM that is accountable (seven standards), reusable (nine standards) and updatable (four standards). 
                                              We provide a rationale for each standard.
-                                             The framework also includes a modelling toolkit of open access repositories and six R packages for authoring MOSHEM modules (data structures and algorithms), supplying those modules with data and using the modules to implement reproducible modelling analyses. 
+                                             The framework also includes a modelling toolkit of open access repositories and six R libraries for authoring ready4 modules (data structures and algorithms), supplying those modules with data and using the modules to implement reproducible modelling analyses. 
                                              We describe an early application of the framework to developing utility mapping models that currently meet 18 framework standards. 
-                                             We discuss the potential benefits and challenges of extending this initial work to develop a more extensive MOSHEM for undertaking a range of economic analyses in youth mental health.",
+                                             We discuss the potential benefits and challenges of extending ready4 in order to undertake and synthesise diverse economic modelling studies in youth mental health and highlight some broader implications for health economists and research funders.",
                                              # Objectives = "We aimed to develop a conceptual and technical framework for implementing open source mental health systems models and illustrate how it can be applicatied to economic topics in youth mental health.",
                                              # Methods = "We created a software development kit in R to support standardised implementation of mental health systems models. As a worked example, we applied the toolkit to develop open source youth mental health utility mapping models, which we assessed against five principles using 17 standards.",
                                              # Results = "Six R packages and a coding style dataset provide a toolkit for implementing mental health models that are TIMELY - Transparent, Iterative, Modular, Epitomising, Licensed and Yielding. The utility mapping models we developed with this toolkit fully met X and partially met Y TIMELY standards.", 
                                              # Conclusion = "Please fund me",
-                                             Code = "Visit https://www.ready4-dev.com for more information about how to find, install and apply the framework and model.")
+                                             Code = "Visit https://www.ready4-dev.com for more information about how to find, install and apply ready4.")
                  args_ls
                  }
                )

### 2023-01-31 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
section 2 of disc

--- 2023-01-29 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
@@
 
-In this paper, we:
+In this paper, we describe:
 
-(i) describe a framework comprised of:
+(i) the ready4 framework, that is comprised of:
   - a set of standards for implementing an accountable, reusable and updatable MOSHEM; and
-  - a modelling toolkit (online repositories and software) for applying those standards to the authoring of ready4 modules, datasets and analyses.
+  - a modelling toolkit (online repositories and software) for applying those standards to the authoring of MOSHEM modules, datasets and analyses; and
 
-(ii) provide a worked example of how we used the framework to develop and apply ready4 modules for utility mapping.
+(ii) how we used the ready4 framework to develop and apply modules for utility mapping.

### 2023-01-31 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
section 2 of disc

--- 2023-01-29 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
@@
 
-In this article we introduced a framework that we developed to help us implement ready4 - a MOSHEM in youth mental health.
-We outlined framework standards for an accountable, reusable and updatable MOSHEM and described the modelling toolkit we created for applying those standards to the development and use of ready4.
-We also provided an overview of an initial set of ready4 modules developed with the framework to implement a utility mapping study.
+In this article we described a framework that we developed to help us implement ready4 - a MOSHEM in youth mental health.
+We outlined framework standards for an accountable, reusable and updatable MOSHEM and described the modelling toolkit we created for applying those standards to the development and use of the ready4 MOSHEM.
+We also provided an overview of an initial set of MOSHEM modules developed with the framework to implement a utility mapping study.
 We reviewed the modules, datasets and analyses generated by that study against framework standards.
+The work we have described has potential implications for the development of the ready4 MOSHEM and for health economic modelling in mental health and highlights more general issues for health economic modellers and funders of health economic research.
 
-The strengths, limitations and issues raised by this work can be discussed in terms of relevance to future development of ready4, to health economists interested in undertaking other MOSHEMS and to funders of health economic research.
+## Implications for implementing ready4
+The most direct implication of the development of the ready4 framework is that it makes it feasible for us to implement a MOSHEM in youth mental health.
+The standards specified by the framework have enabled us to partially automate workflows for developing and applying ready4 through use of the framework's modelling toolkit.
+We have demonstrated the practical utility of the modelling toolkit by applying it to authoring, documenting and disseminating ready4 module libraries  [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155], datasets [@DVN/HJXYKQ_2021; @DVN/DKDIB0_2021]; analyses [@hamilton_matthew_2022_6129906; @hamilton_matthew_2022_6416330; @hamilton_matthew_p_2022_6321821], reporting templates [@hamilton_matthew_2022_6116385; @matthew_p_hamilton_2022_5976988] and prediction tools  @matthew_p_hamilton_2021_5646669] used in a utility mapping study [@Hamilton2021.07.07.21260129].
+The standardised and partially automated workflows used in creating and sharing these artefacts has the potential to generate significant efficiencies as we apply the ready4 framework to undertaking new studies.
 
-## Implications for the development of the ready4 MOSHEM
-One of the main novel contributions of the framework we have developed is that it declares an explicit set of standards for the implementation and use of a MOSHEM.
-A practical benefit of specifying these standards is that it enabled us to develop a modelling toolkit to partially automate workflows for authoring, documenting and disseminating ready4 modules, datasets and analyses.
-The modelling toolkit's practical utility has been demonstrated through its application in creating all ready4 components used in a utility mapping study [@Hamilton2021.07.07.21260129] and the automation it facilitates makes the development and curation of a large and growing number of ready4 digital assets more tractable.
-The interoperability of the ready4 modules we have developed today is demonstrated in multiple example literate programs on the ready4 documentation website [@rfwn2022] and in the program used to implement the utility mapping analysis [@hamilton_matthew_2022_6129906].
+We have also been able to demonstrate the interoperability of the initial ready4 modules developed with the modelling toolkit.
+The program used to implement the utility mapping analysis [@hamilton_matthew_2022_6129906] combines modules from four module libraries ([@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155]) and two framework libraries [@ready4use2022; @ready4show2022].
+Example literate programs published on the ready4 documentation website [@rfwn2022] use toy data [@DVN/HJXYKQ_2021] to illustrate the potential for ready4 modules to facilitate study replication and transferability.
+The framework's standards also provide a mechanism for to assess the extent to which the ready4 MOSHEM meets explicit accountability, reusability and updatability goals.
 
-The framework's standards also provide a mechanism to assess the extent to which ready4 meets explicit accountability, reusability and updatability goals.
+However, having features that facilitate accountability, reuse and updating is not the same as being accountable, reused and updated.
+If diverse groups of stakeholders do not review model components, suggest improvements and develop alternatives, then little progress is made towards enhancing model legitimacy.
+Similarly, making code and data publicly available does not guarantee that others will know of the existence of these tools, trust their validity and find them easy to use.
+Without reuse, errors in model aretefacts are more likely to remain undetected.
+Even when errors are detected, they still need to be fixed, but maintaining code and data requires ongoing resourcing through a combination of centralised infrastructure and an active open source community.
 
-Open source approaches have been recommended to help develop the mental health modelling field [@RN73] but only one mental health related model (in Alcohol Use Disorder [@Basu2018]) is currently indexed [RECHECK] in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019].
+Currently all the framework and module libraries we have developed are available only as "development" releases.
+An early priority for us is to undertake the additional development, testing and documenting of these libraries so that we can submit production versions of each library to CRAN [@CRAN2022].
+Making these libraries available on CRAN is a likely prerequisite of high levels of reuse.
+Similarly, completing our current work program will create new tools for modelling help-seeking choice, spatial epidemiology, household populations and primary mental health services that may enhance the potential usefulness of the ready4 MOSHEM to health economists working in youth mental health.
+
+## Implications for economic modelling in mental health
+Open source approaches have been recommended to help develop the mental health modelling field [@RN73] but only one mental health related model (in Alcohol Use Disorder [@Basu2018]) is currently indexed in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019].
 We are aware of just one other open source mental health model - a reference model in Major Depressive Disorder - that is currently in development [@IVIMDD2022].
+Of the known barriers to adoption of open source models by health economists (including issues like intellectual property and confidentiality [@Pouwels2022; @Wu2019]), our experience suggests that the enormous effort that is required to prepare model code and data for public release in formats that facilitate appropriate reuse by third parties and to maintain and improve these artefacts may be the biggest challenge.
+
+Automated tools such as those we developed in our modelling toolkit can help reduce the burden of some of these tasks.
+However, we think the current low rates of adoption by health economists of open source approaches [@Emerson2019; @Michalczyk2018; @Feenstra2022] (which in turn facilitate the collaboration that make modular models more attractive) is unlikely to change soon without significant and strategic changes by research funders.
+The incentive structures that health economists work within do not promote the investment of significantly more time on each study to enable peers to reuse their work.
+
+Reducing waste in research is a responsibility of research funders [@chalmers2014increase] and the poor reproducibility [@Jalali2021; @McManus2019; @Bermejo2017], limited reusability [@Emerson2019; @Michalczyk2018; @Feenstra2022] and uncertain validity [@Ghabri2019; @Radeva2020] of health economic models is wasteful.
+Approximately 4,000 mental health focused economic evaluation reports were produced between 2000 to 2019 [@RN34].
+The intellectual asset represented by this literature could be very substantial if many of the models described in these reports could be brought (and kept) up to date and made available in formats that maximised transferability to diverse decision contexts.
+We believe that modular and open source approaches would be well suited to accomplishing this goal and that the framework we have developed could act as an early prototype for solving some of the technical challenges of this task.
+Ideally such a programme of research would be resourced to be sustained over the medium to long term and to engage a diverse network of investigators, contributors and advisers from high, middle and low income countries.
+
+In addition to extracting more value from the existing health economic knowledge base in mental health, there is an opportunity for research funders to shape how future health economic models in mental health are undertaken.
+Mental health topics accounted for about 268 of 2829 (10%) peer reviewed economic evaluations undertaken during 26 month period in 2012-2014 identified in a previous review [@pitt2016economic].
+There is also likely to a substantial annual output of economic research in mental health that focuses on the other 11 domains identified by Wagstaff and Culyer [@wagstaff2012four].
+
+Providing adequate levels of funding to support MOSHEMs, fostering skills, supplying infrastructure (t)
+
+Developing networks of modellers working on common health conditions has been recommended as a strategy for improving model validity [@Sampson2019] and some of us are part of a nascent initiate of this type in mental health [@whiteford_bagheri_2022].
+Collaboration between teams of health economists can make some complex modelling projects more feasible [@Arnold2010] and the significant deficits in our understanding of the systems in which mental disorders emerge and are treated [@Fried2020] suggest that there are a number of candidate topics in mental health that might benefit from pooling of efforts.
+The weak theoretical underpinnings for understanding complex mental health systems [@RN2111] may be a place to start.
+It remains unclear why increased investments in mental health care have yet to discernibly reduce the prevalence and burden of mental disorders[@RN26].
+The  literature, and evidence base, regarding how the requirements, characteristics and performance of mental health services are shaped by spatiotemporal context needs to be further developed [@RN42].
+There is also a need for better evidence to identify the social determinants of mental disorders most amenable to preventative interventions, and for which population sub-groups such interventions would be most effective [@RN43].
+
+<!-- MH Research priorities (WP3 - Research, WP6 - Economic) https://doi.org/10.1016/S2215-0366(15)00332-6 -->
+<!-- http://hdl.handle.net/1893/27205--><!-- CONTEXT: Funders should also support methodological work on context, including the development of reporting templates to facilitate accurate, comprehensive and systematic reporting of context, approaches to evidence synthesis that can capture contextual variation adequately and modelling methods that can leverage the accumulating evidence on contextual variation to predict the reach, implementation and effectiveness of promising interventions in new contexts." --
+
+<!-- the framework represents a technical capacity rather than a behavioural outcome.  -->
+
+<!-- (described in more detail on the project documentation website [@rfwn2022])  -->
 
@@
  <!-- - Our analysis - do it in stages, be transparent, continually improve, get help, be flexible (modelling toolkit / monolithic model), have a framework -->
- <!-- A coding framework for MOSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions [@Alarid2019]. -->
+ <!-- A coding framework for OSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions [@Alarid2019]. -->
 
-However, the framework represents a technical capacity and is not a behavioural outcome.
-Having features to facilitate accountability, reuse and updating does not guarantee being that our OSHEM will be meaningfully held accountable, reused and updated.
-Making code and data publicly available may make limited impact on error detection unless third parties begin to use these artefacts in their own projects.
-Currently all the framework and module libraries we have developed are available only as "development" releases.
-Further development, testing and documenting before we submit production versions of each library to the Comprehensive R Archive Network (CRAN) [@CRAN2022].
-Having these libraries available on CRAN is a likely prerequisite of significant levels of reuse.
+<!-- Is it desirable for this to become default authoring tool or better to be replication tool. -->
 
 Estimating the potential uptake of these tools is difficult.
-Mental health topics accounted for about 268 of 2829 (10%) economic evaluations undertaken during 26 month period in 2012-2014 identified in a previous review [@pitt2016economic].
-
-Developing networks of modellers working on common health conditions has been recommended as a strategy for improving model validity [@Sampson2019] and some of us are part of a nascent initiate of this type in mental health [@nmhsmn2022].
 
@@
 <!-- Reducing waste in research is responsibility of research funder: https://doi.org/10.1016/S0140-6736(13)62229-1 -->
-<!-- MH Research priorities (WP3 - Research, WP6 - Economic) https://doi.org/10.1016/S2215-0366(15)00332-6 -->
-<!-- http://hdl.handle.net/1893/27205--><!-- CONTEXT: Funders should also support methodological work on context, including the development of reporting templates to facilitate accurate, comprehensive and systematic reporting of context, approaches to evidence synthesis that can capture contextual variation adequately and modelling methods that can leverage the accumulating evidence on contextual variation to predict the reach, implementation and effectiveness of promising interventions in new contexts." -->
+>
 
@@
 Major mental health reform programs, <!-- such as those currently being implemented in Victoria, Australia [@VicRC2021],  -->can involve the identification, prioritisation, sequencing, targeting and monitoring of multiple interdependent initiatives.
-
-The significant deficits in our understanding of the systems in which mental disorders emerge and are treated [@Fried2020] suggest that there is ample scope for mental health systems models to progressively improve their validity over time.
-Prospective work could address the weak theoretical underpinnings for understanding complex mental health systems [@RN2111].
-For example, it remains unclear why increased investments in mental health care have yet to discernibly reduce the prevalence and burden of mental disorders[@RN26].
-The  literature, and evidence base, regarding how the requirements, characteristics and performance of mental health services are shaped by spatiotemporal context needs to be further developed [@RN42].
-There is also a need for better evidence to identify the social determinants of mental disorders most amenable to preventative interventions, and for which population sub-groups such interventions would be most effective [@RN43].
 

### 2023-01-31 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
section 2 of disc

@@
 
-We applied the framework to develop ready4 modules for developing utility mapping models, supplying those modules with data and implementing utility mapping analyses.
-These tools were created to develop utility mapping models for a clinical mental health sample of young people in a study that has been previously described [@Hamilton2021.07.07.21260129].
-The framework's modelling toolkit created the following ready artefacts:
+We applied the ready4 framework to develop an initial set of MOSHEM modules, supplying those modules with data and implementing analyses.
+These tools were created as part of a previously described study [@Hamilton2021.07.07.21260129] to develop utility mapping models appropriate for use in samples of young people presenting to primary mental health services.
+The ready4 framework's modelling toolkit created the following artefacts:
 
@@
 
-When we assesses these study outputs against each framework standard, we conclude that 18 out of 20 standards were wholly or mostly met (see Table \@ref(tab:checktb)).
+We assess that these study outputs either wholly or mostly meet 18 out of 20 framework standards(see Table \@ref(tab:checktb)).
 The two standards where the study outputs currently fall short are in reporting code coverage and including a user-interface.

### 2023-01-31 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
section 2 of disc

@@
 
-Based on published guidance on computational modelling in health economics and other disciplines as well as our own experience in developing ready4, we have identified 20 standards that we believe are important for implementing a MOSHEM that is accountable (seven standards), reusable (nine standards) and updatable (four standards).
+Based on published guidance on computational modelling in health economics and other disciplines as well as our own experience, we have identified 20 standards that we believe are important for implementing a MOSHEM that is accountable (seven standards), reusable (nine standards) and updatable (four standards).
 The standards are specified in Table \@ref(tab:timelygls) and are discussed below.
@@
 
-The coding practice of encapsulation [@8717448] can be used to help ensure that model modules continue to work as intended when they are combined [@ready4oop2022].
+The software development practice of encapsulation [@8717448] can be used to help ensure that model modules continue to work as intended when they are combined [@ready4oop2022].
 In some cases, combining modules may mean new versions of modules have to be created to better account for interaction effects.
-The coding concept of inheritance [@8717448] can be used to efficiently achieve this objective as well as to facilitate selective editing of modules when transferring models to different decision contexts [@ready4oop2022].
+The concept of inheritance [@8717448] can be used to write code that efficiently achieves this objective as well as to facilitate selective editing of modules when transferring models to different decision contexts [@ready4oop2022].
 Writing algorithms as collections of functions (short, self-contained and reusable software routines that each perform a discrete task) is recommended as good practice for scientific computing [@Wilson_2017].
-Functions to implement model algorithms can be associated with module data structures (also known as a class) via a special type of function called a method.
+Functions to implement model algorithms can be associated with data structures (also known as a class) via a special type of function called a method.
 Model modules of a similar type or purpose can be efficiently distributed and documented by bundling them as code libraries.
@@
 
-Statistical models are a common output of health economic evaluations, but they are often not reported in a format that enables others to confidently and reliably re-use them [@Kearns2013].
+Statistical models are a common output of health economic evaluations, but they are often not reported in a format that enables others to confidently and reliably re-use them for out of sample prediction [@Kearns2013].
 Open source approaches can help address this by disseminating code artefacts that enable easy and appropriate use of a statistical model to make predictions with new data.
@@
 To avoid MOSHEMs going stale - losing validity and usefulness with time - they should be routinely updated.
-Each update of code and data should be uniquely identifiable and retrievable, a goal that can be facilitated by use of version control tools [@Erdemir2020].
+Each update of code and data should be uniquely identifiable and retrievable, a goal that can be facilitated by use of version control tools [@Erdemir2020] such as [@git20XX].
 

### 2023-01-31 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
section 2 of disc

@@
 
-We developed a toolkit to help us develop and use ready4 modules, datasets and analyses that meet the standards listed in Table \@ref(tab:timelygls).
+We developed a toolkit to help us develop and use MOSHEM modules, datasets and analyses that meet the standards listed in Table \@ref(tab:timelygls).
 The toolkit is comprised of online repositories and software.
@@
 We configured the repositories in our GitHub organisation to use GitHub actions to support continuous integration.
+Some of the continuous integration checks we have defined assess each library's compliance with policies specified by the Comprehensive R Archive Network (CRAN) [@CRAN2022], to which we plan submitting future production releases.
 
 For hosting documentation websites for the code libraries we create, we enabled GitHub Pages in each library's repository.
-We also developed a consolidated project documentation website [@rfwn2022], using the Hugo framework [@hugo_2023] and Docsy theme [@docsy_2023].
+We also developed a consolidated and versioned project documentation website [@rfwn2022], using the Hugo framework [@hugo_2023] and Docsy theme [@docsy_2023].
 To host that website we established an account with Netlify [@netlify_2023] and linked that service to our GitHub organisation so that the website would automatically update whenever the source code in its GitHub repository was edited.
 
-We also created a Zenodo community [@ready4zen2022] - a collection of permanent, unbiquely identified repositories.
+We also created a Zenodo community [@ready4zen2022] - a collection of permanent, uniquely identified repositories.
 We then linked our Zenodo community and GitHub organisation so that every time we create a new "release" in a GitHub repository, a copy of that code is automatically created on Zenodo with a DOI.
@@
 
-The foundation for ready4 is provided by a library called ready4 [@ready42022] that defines a template module (using R's S4 type class) from which all model module data structures will inherit features and a novel syntax for implementing the algorithms attached to model modules.
+A library called ready4 [@ready42022] defines a template module (using R's S4 type class) from which all model module data structures will inherit features and a novel syntax for implementing the algorithms attached to model modules.
 The ready4 library also contains tools for retrieving web based information on model modules, datasets and analysis programs and for partially automating updates to the project website.
@@
 Three R libraries are designed to standardise and partially automate workflows for authoring new model modules.
-The ready4pack library [@ready4pack2022] provides tools for authoring module libraries that are:
+The ready4pack library [@ready4pack2022] is designed to integrate with our GitHub organisation and provides tools for authoring module libraries that are:
 
@@
 
-The ready4pack library is designed to integrate with our GitHub organisation and depends on two other module authoring libraries.
+The ready4pack library depends on two other module authoring libraries.
 Methods from the ready4fun library [@ready4fun2022] are used to verify that functions for implementing module algorithms are written in a consistent house style.
-The standardised format is then used by ready4fun to automatically generate basic documentation for each function.
-Methods from the ready4class [@ready4class2022] library are used to streamline and standardise the authoring of module data-structures.
-Like ready4fun, the ready4class library uses standardised code implementation to automatically generate basic documentation for each module data-structure.
+That standardised format is then used by ready4fun methods to automatically generate basic documentation for each function.
+Methods from the ready4class [@ready4class2022] library are used to streamline and standardise the authoring of module data structures and the linking of methods to these data structures.
+Like ready4fun, the ready4class library uses standardised code implementation to automatically generate basic documentation for each module data structure.
 

### 2023-01-31 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
section 2 of disc

--- 2023-01-29 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
@@
 Advantages of modular models include feasibility (large projects are broken into smaller tasks, with each component independently developed and tested) and flexibility (making it easier to selectively replace or update specific parts of a model and to scale up or down the level of granularity) [@pan2021modular].
-Modular approaches are currently being used to facilitate the development of complex computational models in disciplines such as biology [@pan2021modular], neuroscience [@frazier2022robust] and ecology [@barros2023empowering].
+Modular approaches are currently being used to facilitate the development of complex computational models in disciplines such as biology [@pan2021modular], ecology [@barros2023empowering] and neuroscience [@frazier2022robust].
 In health economics the related and enabling concept of reference models has been recommended [@Afzali2013], but peer reviewed studies describing modular health economic models remain relatively rare, though examples exist in infectious disease [@Trauer2017] and cardiology [@Urach2013].
@@
 
-- *determinants of health and ill-health* (our projects: models for creating rich and representative synthetic household populations from survey data);
+- *determinants of health and ill-health* (our projects: models for creating synthetic household populations with key risk and protective factors for mental disorders);
 
@@
 
-- *economic evaluation* (our goal: assess the cost-utility of competing policy options).
+- *economic evaluation* (our goal: assess the cost-utility of competing policy options for improving the mental health of young people).
 
-To undertake this work we first needed to develop a framework for standardisation.
 Standardisation is an essential enabler of automation, collaboration, interoperability and transferability in modular and open source approaches.
-However, MOSHEMs remain rare and is unclear what standards are most appropriate to specify.
-A MOSHEMs is a computational modelling project, so standards developed for ready4 will need to be verified and implemented by software, some of which will need to be developed for this specific purpose.
+An early requirement to implement ready4 is therefore to identify an appropriate set of standards.
+However, we are not aware of any consolidated source of guidance about recommended standards for MOSHEMs.
+Once identified, the standards specified for ready4 will need to be implemented by software, some of which will require custom development.
 

### 2023-01-31 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
wip on discussion
section 2 of disc

@@
 <!-- Add child RMDs for results content -->
-# Framework
+# The ready4 framework
 <!-- Modular and open source models from other disciplines are enabled by standardisation and software.  -->
-To help us implement a MOSHEM in youth mental health, we have developed a framework that:
+To enable us to implement ready4, we have developed a framework that:
 

### 2023-01-31 Markdown/Manuscript/Child_RMDs/MS_Tables_3.Rmd
section 2 of disc

@@
 One (ymh_clinical_tb.RDS) closely resembles the study dataset and was released so that the main study algorithm [@hamilton_matthew_2022_6129906] can be rerun by those without access to the confidential study dataset.
-The other (eq5d_ds_dict.RDS) is deliberately different to the source dataset in both variable naming convention and the concepts used for predictors and outcome measures.
-It was created to demonstrate generalised applications of study algorithms.",                                           #
+The other (eq5d_ds_tb.Rds) is deliberately different to the source dataset in both variable naming convention and the concepts used for predictors and outcome measures.
+It was created to demonstrate the transferability of study algorithms.",                                           #
                                            "Model catalogues (PDF files beginning with 'AAA_TTU_MDL_CTG') are available in the study results dataset [@DVN/DKDIB0_2021] and describe the predictive performance of all models under a variety of usage regimes (including when the source dataset in the R model object is replaced with fake data).
@@
 https://github.com/ready4-dev/youthvars/actions)",
-                                           "Retired code is deprecated using tools from the lifecycle R library [lifecycle2021] (e.g.
+                                           "Retired code is deprecated using tools from the lifecycle R library [@lifecycle2021] (e.g.
 everything after “## DEPRECATED FNS” in https://github.com/ready4-dev/youthvars/blob/main/data-raw/fns/add.R ).

### 2023-01-31 setup.R

@@ -13,7 +13,7 @@ X <- Ready4showSynopsis(#background_1L_chr = "Our study is entirely fictional.",
                         keywords_chr = c("open source models","health economics","mental disorders"),
                         outp_formats_chr = "PDF",
                         #sample_desc_1L_chr = "The study sample is fake data that pretends to be young people aged 12 to 25 years who attended Australian primary care services for mental health related needs between November 2019 to August 2020.",
-                        title_1L_chr = "A framework for implementing a modular open source health economic model (MOSHEM) in youth mental health that is accountable, reusable and updatable")
+                        title_1L_chr = "The ready4 framework for implementing a modular open source health economic model (MOSHEM) in youth mental health that is accountable, reusable and updatable")
 X <- renewSlot(X,
                "authors_r3", 
                {

### 2023-01-31 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
edits up to mid discussion

@@
 
-(i) the ready4 framework, that is comprised of:
-  - a set of standards for implementing an accountable, reusable and updatable MOSHEM; and
-  - a modelling toolkit (online repositories and software) for applying those standards to the authoring of MOSHEM modules, datasets and analyses; and
+(i) a framework that specifies MOSHEM standards and provides the tools to implement them; and
 
-(ii) how we used the ready4 framework to develop and apply modules for utility mapping.
+(ii) the application of that framework to develop and use an initial set of ready4 modules in a utility mapping study.

### 2023-01-31 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
edits up to mid discussion

@@
 We reviewed the modules, datasets and analyses generated by that study against framework standards.
-The work we have described has potential implications for the development of the ready4 MOSHEM and for health economic modelling in mental health and highlights more general issues for health economic modellers and funders of health economic research.
+The work we have described has potential implications for the development of the ready4 MOSHEM and for health economic modelling in mental health.
+A number of issues have more general relevance to health economic modellers and funders of health economic research.
 
@@
 We have demonstrated the practical utility of the modelling toolkit by applying it to authoring, documenting and disseminating ready4 module libraries  [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155], datasets [@DVN/HJXYKQ_2021; @DVN/DKDIB0_2021]; analyses [@hamilton_matthew_2022_6129906; @hamilton_matthew_2022_6416330; @hamilton_matthew_p_2022_6321821], reporting templates [@hamilton_matthew_2022_6116385; @matthew_p_hamilton_2022_5976988] and prediction tools  @matthew_p_hamilton_2021_5646669] used in a utility mapping study [@Hamilton2021.07.07.21260129].
-The standardised and partially automated workflows used in creating and sharing these artefacts has the potential to generate significant efficiencies as we apply the ready4 framework to undertaking new studies.
+The standardised and partially automated workflows used in creating and sharing these artefacts has the potential to generate significant efficiencies as we apply the ready4 framework to undertaking new economic studies.
 
@@
 Example literate programs published on the ready4 documentation website [@rfwn2022] use toy data [@DVN/HJXYKQ_2021] to illustrate the potential for ready4 modules to facilitate study replication and transferability.
-The framework's standards also provide a mechanism for to assess the extent to which the ready4 MOSHEM meets explicit accountability, reusability and updatability goals.
+As demonstrated by the checklist we developed (Table \@ref(tab:checktb)), our framework's standards also provide a mechanism for to assess the extent to which the ready4 MOSHEM meets explicit objectives.
 
@@
 
-Currently all the framework and module libraries we have developed are available only as "development" releases.
+To progress from a technical capability to behavioural outcomes, both our framework and MOSHEM need further work.
+Currently all the framework and model module libraries we have developed are available only as "development" releases.
 An early priority for us is to undertake the additional development, testing and documenting of these libraries so that we can submit production versions of each library to CRAN [@CRAN2022].
-Making these libraries available on CRAN is a likely prerequisite of high levels of reuse.
-Similarly, completing our current work program will create new tools for modelling help-seeking choice, spatial epidemiology, household populations and primary mental health services that may enhance the potential usefulness of the ready4 MOSHEM to health economists working in youth mental health.
+Making R libraries available on CRAN is normally a prerequisite for high levels of reuse.
+
+The transferability claims we make for our existing modules are to date supported only by example programs using toy data.
+Our future work aims to address this with real world studies that apply modules to different concepts and contexts.
+Our current work program also aims to create new ready4 modules for modelling help-seeking choice, spatial epidemiology, household populations and primary mental health services that we hope will provide others with more reasons to use ready4 and contribute to its development.
+To facilitate code contributions by third parties, our libraries for authoring modules [@ready4pack2022: @ready4fun2022; @ready4use2022] require some additional development to make them easier to use by third parties without knowledge of the naming and directory strucuture conventions we use in authoring code.
+
+<!-- Real applications would be better given importance. -->
 
@@
 We are aware of just one other open source mental health model - a reference model in Major Depressive Disorder - that is currently in development [@IVIMDD2022].
-Of the known barriers to adoption of open source models by health economists (including issues like intellectual property and confidentiality [@Pouwels2022; @Wu2019]), our experience suggests that the enormous effort that is required to prepare model code and data for public release in formats that facilitate appropriate reuse by third parties and to maintain and improve these artefacts may be the biggest challenge.
+Of the known barriers to adoption of open source models by health economists (including issues like intellectual property and confidentiality [@Pouwels2022; @Wu2019]), our experience suggests that the biggest challenges may be the enormous effort required to first prepare model code and data for public release in formats that facilitate appropriate reuse by third parties and to then maintain and contunually improve potentially large numbers of digital artefacts.
 
-Automated tools such as those we developed in our modelling toolkit can help reduce the burden of some of these tasks.
-However, we think the current low rates of adoption by health economists of open source approaches [@Emerson2019; @Michalczyk2018; @Feenstra2022] (which in turn facilitate the collaboration that make modular models more attractive) is unlikely to change soon without significant and strategic changes by research funders.
-The incentive structures that health economists work within do not promote the investment of significantly more time on each study to enable peers to reuse their work.
+Automated tools such as those we developed in our modelling toolkit can help reduce the burden associated with some of these tasks.
+However, we think the current low rates of adoption by health economists of open source approaches [@Emerson2019; @Michalczyk2018; @Feenstra2022] (which in turn facilitate the collaboration that make modular models more attractive) will only change slowly unless there is significant and strategic investments made by research funders.
+Currently, the incentive structures for health economists do not promote dedicating large quantities of time to enabling peers to reuse their work.
 
@@
 Approximately 4,000 mental health focused economic evaluation reports were produced between 2000 to 2019 [@RN34].
-The intellectual asset represented by this literature could be very substantial if many of the models described in these reports could be brought (and kept) up to date and made available in formats that maximised transferability to diverse decision contexts.
+The intellectual asset represented by this literature could be very substantial if many of the models described in these reports could be brought and kept up to date and made available in formats that maximised transferability to diverse decision contexts.
 We believe that modular and open source approaches would be well suited to accomplishing this goal and that the framework we have developed could act as an early prototype for solving some of the technical challenges of this task.
@@
 Providing adequate levels of funding to support MOSHEMs, fostering skills, supplying infrastructure (t)
+
+<!-- Resilience of open source project needs multiple maintainers -->
 
@@
 <!-- (described in more detail on the project documentation website [@rfwn2022])  -->
+<!-- Sustained funding -->
 
@@
 - Funding contingent directions - replications / transfers
+
+<!-- Diversify skills - move to tools means software engineering, -->
+<!-- More collaboration -->
+<!-- Role for SIGs -->
+<!-- Make grant proposals that give funders the opportunity to fund this work. -->
+<!-- Share some code and data at small scale. -->
 

### 2023-01-31 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
edits up to mid discussion

@@
 
-We applied the ready4 framework to develop an initial set of MOSHEM modules, supplying those modules with data and implementing analyses.
-These tools were created as part of a previously described study [@Hamilton2021.07.07.21260129] to develop utility mapping models appropriate for use in samples of young people presenting to primary mental health services.
+We applied the framework to develop an initial set of ready4 modules, supply those modules with data and implement modelling analyses.
+These outputs were created as part of a previously described study [@Hamilton2021.07.07.21260129] to develop utility mapping models appropriate for use in samples of young people presenting to primary mental health services.
 The ready4 framework's modelling toolkit created the following artefacts:
@@
 
-We assess that these study outputs either wholly or mostly meet 18 out of 20 framework standards(see Table \@ref(tab:checktb)).
+We created a checklist (Table \@ref(tab:checktb)) that we used to assess the extent to which study outputs met framework standards.
+We assessed these outputs as wholly or mostly meeting 18 out of 20 standards.
 The two standards where the study outputs currently fall short are in reporting code coverage and including a user-interface.

### 2023-01-31 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
edits up to mid discussion

@@
 Guidance on transparency in health economic modelling published over ten years ago [@Eddy2012] made recommendations on documenting models but notably did not include recommendations on sharing model code and data.
-However, more recent and multidisciplinary healthcare modelling guidance [@Erdemir2020] recommends using existing digital repository services to these types of digital model artefacts.
-Some types of repository such as GitHub [@github2007] provide tools for disseminating work in progress code and providing highly transparent records of the complete development history and individual authorship contributions of a software project, while others such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each code and data collection.
+However, more recent and multidisciplinary healthcare modelling guidance [@Erdemir2020] recommends using existing digital repository services to make these types of digital model artefacts publicly available.
+Some repositories such as GitHub [@github2007] provide tools for disseminating work in progress code and providing highly transparent records of the complete development history and individual authorship contributions of a software project.
+Other repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each code and data collection.
 
@@
 Open source approaches can help address this by disseminating code artefacts that enable easy and appropriate use of a statistical model to make predictions with new data.
-However, great care must be exercised when doing so if models are derived from data on human subjects as some software artefacts by default contain a copy of the source dataset.
-Such dataset copies must therefore be replaced (for example, with synthetic data) and the amended artefact's predictive performance then retested before any public release.
+However, great care must be exercised when publicly releasing model aretefacts  derived from data on human subjects as they may by default embed a copy of the source dataset.
+Sensitive dataset copies must therefore be replaced (for example, with synthetic data) and the amended artefact's predictive performance then retested before any public release.
 Another way to make MOSHEMs easier to use is to develop simple user-interfaces for non-technical users.
@@
 To avoid MOSHEMs going stale - losing validity and usefulness with time - they should be routinely updated.
-Each update of code and data should be uniquely identifiable and retrievable, a goal that can be facilitated by use of version control tools [@Erdemir2020] such as [@git20XX].
+Each update of code and data should be uniquely identifiable and retrievable, a goal that can be facilitated by use of version control tools [@Erdemir2020] such as git [@git20XX].
 
-Potential users of model code and data should be able to easily identify which version is most appropriate to their needs.
+Potential users of model code and data should be able to easily identify the appropriateness of a version to their needs.
 Using semantic versioning [@semver20xx] conventions can signal the potential importance of an update to users of model code and data.
-Also informative is to clearly label the type of code hosted in a repository as either:
+Also informative is to clearly label the type of code versions hosted in a repository as either:
 
-- "development" (typically the most comprehensive and up to date source code, but potentially not yet sufficiently well documented and tested for potential users to apply to purposes other than testing);
+- "development" - typically the most comprehensive and up to date source code, but potentially not yet sufficiently well documented and tested for potential users to apply to purposes other than testing;
 
-- "production" (code that has been released with a view to it being applied to its stated purposes and therefore typically required to meet defined documentation and testing standards); or
+- "production" - code that has been released with a view to it being applied to its stated purposes and therefore typically required to meet defined documentation and testing standards; or
 
-- "archive" (permanent copies of code at key milestones in its development - potentially useful if seeking to use older versions of code to reproduce analyses).
+- "archive" - permanent copies of code at key milestones in its development that can aid study reproductions by making available the version of code used in a specific analysis.
 
-Continuous integration [@CI2017] tools can help verify that each code update passes multiple quality tests.
-Finally, using deprecation conventions that take an informative and staged approach to retiring old code and data reduces the risk that model revisions have unintended consequences on third party users.
+Continuous integration [@CI2017] tools can help verify that each code update continues to pass a standardised battery of quality tests.
+Finally, using deprecation conventions that take an informative and staged approach to retiring old code and data reduces the risk of model revisions having unintended consequences on third party users.

### 2023-01-31 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
edits up to mid discussion

@@
 We created a GitHub organisation (a collection of code repositories) where all our development code is stored and version controlled [@ready4gh2022].
-We linked our GitHub organisation to an account we established at codecov [@codecov_2022] to track our code coverage.
 We configured the repositories in our GitHub organisation to use GitHub actions to support continuous integration.
 Some of the continuous integration checks we have defined assess each library's compliance with policies specified by the Comprehensive R Archive Network (CRAN) [@CRAN2022], to which we plan submitting future production releases.
+To track our code coverage, we linked our GitHub organisation to an account we established at codecov [@codecov_2022].
 
-For hosting documentation websites for the code libraries we create, we enabled GitHub Pages in each library's repository.
-We also developed a consolidated and versioned project documentation website [@rfwn2022], using the Hugo framework [@hugo_2023] and Docsy theme [@docsy_2023].
+We enabled GitHub Pages in each repository we used for code library development to facilitate the creation and hosting of library documentation websites.
+We also developed a consolidated and versioned project documentation website [@rfwn2022] using the Hugo framework [@hugo_2023] and Docsy theme [@docsy_2023].
 To host that website we established an account with Netlify [@netlify_2023] and linked that service to our GitHub organisation so that the website would automatically update whenever the source code in its GitHub repository was edited.
@@
 We also created a Zenodo community [@ready4zen2022] - a collection of permanent, uniquely identified repositories.
-We then linked our Zenodo community and GitHub organisation so that every time we create a new "release" in a GitHub repository, a copy of that code is automatically created on Zenodo with a DOI.
+We then linked our Zenodo community and GitHub organisation so that every time we specify a version of code in one of our GitHub repositories as a "release", a copy of that code is automatically created on Zenodo with a DOI.
 Finally, to manage model datasets, we created a dedicated collection within the Harvard Dataverse installation [@ready4dv2022].
@@
 ## Software <!-- Novel ref -->
-We created six development version R libraries to help us author model modules, supply them with data and implement reproducible modelling analyses.
+We created six development version R libraries to help us author model modules, supply those modules with data and implement reproducible modelling analyses.
 The six libraries, their primary focus, the standards they support and the third-party packages they depend on are summarised in Table \@ref(tab:cpkgs).
 
-A library called ready4 [@ready42022] defines a template module (using R's S4 type class) from which all model module data structures will inherit features and a novel syntax for implementing the algorithms attached to model modules.
-The ready4 library also contains tools for retrieving web based information on model modules, datasets and analysis programs and for partially automating updates to the project website.
+A library called ready4 [@ready42022] defines a template module (using R's S4 class system) from which all model module data structures will inherit features and a novel syntax for attaching algorithms to those data structures.
+The ready4 library also contains tools for retrieving web based information on model modules, datasets and analysis programs and for partially automating updates to the project documentation website.
 
@@
 
-When used in conjunction with repositories, the six R libraries provide strong support for implementing 17 out of 20 framework standards.
+When used in conjunction with toolkit repositories, the six R libraries provide support for implementing 17 out of 20 framework standards (Table \@ref(tab:timelygls)).
 Standards relating to safe dissemination of statistical models (R8), user-interface development (R9) and deprecation conventions (U4) are better met through using existing third party R libraries.

### 2023-01-31 setup.R

@@ -13,7 +13,7 @@ X <- Ready4showSynopsis(#background_1L_chr = "Our study is entirely fictional.",
                         keywords_chr = c("open source models","health economics","mental disorders"),
                         outp_formats_chr = "PDF",
                         #sample_desc_1L_chr = "The study sample is fake data that pretends to be young people aged 12 to 25 years who attended Australian primary care services for mental health related needs between November 2019 to August 2020.",
-                        title_1L_chr = "The ready4 framework for implementing a modular open source health economic model (MOSHEM) in youth mental health that is accountable, reusable and updatable")
+                        title_1L_chr = "Framework for implementing a modular open source health economic model (MOSHEM) in youth mental health that is accountable, reusable and updatable")
 X <- renewSlot(X,
                "authors_r3", 
                {
@@ -37,7 +37,7 @@ X <- renewSlot(X,
                "abstract_args_ls",
                {
                  args_ls <- X@abstract_args_ls
-                 args_ls$abstract_ls <- list(Summary = "Health economists make limited use of the modular and open source approaches to model building that other disciplines use to make large modelling projects more transparent, efficient and sustainable. 
+                 args_ls$abstract_ls <- list(Summary = "Health economists make limited use of the modular and open source approaches to model building that other disciplines use for collaborative development of complex modelling projects. 
                                              We propose a framework for developing a modular open source health economic model (MOSHEM) in youth mental health called ready4.
                                              The framework includes of set of 20 standards for implementing a MOSHEM that is accountable (seven standards), reusable (nine standards) and updatable (four standards). 
                                              We provide a rationale for each standard.

### 2023-02-01 Markdown/Manuscript/Child_RMDs/MS_Conclusion.Rmd
draft for selected co-author circulation

--- 2022-04-19 Markdown/Manuscript/Child_RMDs/MS_Conclusion.Rmd
@@
 `r ifelse(is.na(params$X@conclusion_1L_chr),"",params$X@conclusion_1L_chr)` 
+We have developed a framework for undertaking a MOSHEM in youth mental health and demonstrated its use by applying it to undertake a utility mapping study.
+We intend using this framework to undertake and synthesise multiple types of economic research.
+With further development the framework could be applied to extracting greater value from existing economic models in mental health and to facilitate collaborations between health economists and other stakeholders to address complex mental health modelling challenges.
+Although MOSHEMs provide a promising opportunity to advance the health economcis field, action from funders is required to realise this potential.

### 2023-02-01 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
draft for selected co-author circulation

@@
 Similarly, making code and data publicly available does not guarantee that others will know of the existence of these tools, trust their validity and find them easy to use.
-Without reuse, errors in model aretefacts are more likely to remain undetected.
+Without reuse, errors in model artefacts are more likely to remain undetected.
 Even when errors are detected, they still need to be fixed, but maintaining code and data requires ongoing resourcing through a combination of centralised infrastructure and an active open source community.
@@
 An early priority for us is to undertake the additional development, testing and documenting of these libraries so that we can submit production versions of each library to CRAN [@CRAN2022].
-Making R libraries available on CRAN is normally a prerequisite for high levels of reuse.
+Making an R library available on CRAN is normally a prerequisite for a high level of use.
 
@@
 Our current work program also aims to create new ready4 modules for modelling help-seeking choice, spatial epidemiology, household populations and primary mental health services that we hope will provide others with more reasons to use ready4 and contribute to its development.
-To facilitate code contributions by third parties, our libraries for authoring modules [@ready4pack2022: @ready4fun2022; @ready4use2022] require some additional development to make them easier to use by third parties without knowledge of the naming and directory strucuture conventions we use in authoring code.
-
-<!-- Real applications would be better given importance. -->
+To facilitate code contributions by third parties, our libraries for authoring modules [@ready4pack2022: @ready4fun2022; @ready4use2022] require some additional development to make them easier to use by third parties without knowledge of the naming and directory structure conventions we use in authoring code.
 
@@
 We are aware of just one other open source mental health model - a reference model in Major Depressive Disorder - that is currently in development [@IVIMDD2022].
-Of the known barriers to adoption of open source models by health economists (including issues like intellectual property and confidentiality [@Pouwels2022; @Wu2019]), our experience suggests that the biggest challenges may be the enormous effort required to first prepare model code and data for public release in formats that facilitate appropriate reuse by third parties and to then maintain and contunually improve potentially large numbers of digital artefacts.
+Of the known barriers to adoption of open source models by health economists (including issues like intellectual property and confidentiality [@Pouwels2022; @Wu2019]), our experience suggests that the biggest challenges may be the enormous effort required to first prepare model code and data for public release in formats that facilitate appropriate reuse by third parties and to then maintain and continually improve potentially large numbers of digital artefacts.
 
@@
 However, we think the current low rates of adoption by health economists of open source approaches [@Emerson2019; @Michalczyk2018; @Feenstra2022] (which in turn facilitate the collaboration that make modular models more attractive) will only change slowly unless there is significant and strategic investments made by research funders.
-Currently, the incentive structures for health economists do not promote dedicating large quantities of time to enabling peers to reuse their work.
+Currently, incentive structures for health economists do not promote the dedication of large quantities of time to enable peers to reuse their work.<!-- MH Research priorities (WP3 - Research, WP6 - Economic) https://doi.org/10.1016/S2215-0366(15)00332-6 -->
 
@@
 Approximately 4,000 mental health focused economic evaluation reports were produced between 2000 to 2019 [@RN34].
-The intellectual asset represented by this literature could be very substantial if many of the models described in these reports could be brought and kept up to date and made available in formats that maximised transferability to diverse decision contexts.
+The intellectual asset represented by this literature could be enhanced if many of the models described in these reports could be brought and kept up to date and made available in formats that maximised transferability to diverse decision contexts.
 We believe that modular and open source approaches would be well suited to accomplishing this goal and that the framework we have developed could act as an early prototype for solving some of the technical challenges of this task.
-Ideally such a programme of research would be resourced to be sustained over the medium to long term and to engage a diverse network of investigators, contributors and advisers from high, middle and low income countries.
+Ideally such a program of research would be resourced to be sustained over the medium to long term and to engage a diverse network of investigators, contributors and advisers from high, middle and low income countries.
 
 In addition to extracting more value from the existing health economic knowledge base in mental health, there is an opportunity for research funders to shape how future health economic models in mental health are undertaken.
-Mental health topics accounted for about 268 of 2829 (10%) peer reviewed economic evaluations undertaken during 26 month period in 2012-2014 identified in a previous review [@pitt2016economic].
-There is also likely to a substantial annual output of economic research in mental health that focuses on the other 11 domains identified by Wagstaff and Culyer [@wagstaff2012four].
-
-Providing adequate levels of funding to support MOSHEMs, fostering skills, supplying infrastructure (t)
-
-<!-- Resilience of open source project needs multiple maintainers -->
+Mental health topics accounted for 268 of the 2829 (10%) peer reviewed economic evaluations undertaken during 26 month period in 2012-2014 identified by a review [@pitt2016economic].
+The ongoing annual output of economic research in mental health that focuses on the other 11 domains identified by Wagstaff and Culyer [@wagstaff2012four] is probably also substantial.
+Funders should provide support for the projects and infrastructure to promote greater collaboration, interoperability, transferability and maintenance of future mental health modelling projects.
 
@@
 
-<!-- MH Research priorities (WP3 - Research, WP6 - Economic) https://doi.org/10.1016/S2215-0366(15)00332-6 -->
+Ideally health economists would explore these complex topics in partnership with modellers from other disciplines (in particular epidemiology and health services research) and a wide range of stakeholders such as other researchers, policymakers, service planners and community members.
+Modular and open source approaches would facilitate such investigations by breaking down ambitious and long term goals into manageable time-bound discrete projects, each progressed by different teams.
+To facilitate such an approach, a common framework of standards and tools would be needed.
+To be suitable for such a task our framework would need additional development, with its overall architecture reviewed for scalability and suitability and to provide better integration with and use of other open source languages (particularly python) and repositories.
+Whatever MOSHEM infrastructure is developed, its resilience would depend on a community of open source contributors sufficiently large and active to ensure that all core modules are maintained even after their original authors cease their involvement.
+
+## General issues for health economists and health research funders
+Some of the issues we have discussed in the context of the development of our model or health economic modelling in mental health are potentially relevant to health economists and funders of health economic research more generally.
+Proactive measures by funders to encourage more accountable, reusable and updatable health economic models is not a need confined to mental health.
+For example, funders have been encouraged to support methodological innovation to improve model transferability [@craig2018taking].
+However, funders also need credible proposals to support and this is an area for health economists interested in MOSHEMs to prioritize.
+Health economists could use existing and new special interest groups to identify opportunities and enablers of more collaborative approaches to model development, potentially as the basis for future funding proposals.
+
+Adopting MOSHEMs will expand the type of skillset typically engaged in health economic modelling projects, with a much greater role for data-scientists, software engineers and online community builders.
+The requirement for these roles should be incorporated into project proposals.
+Not all efforts by health economists to promote MOSHEMs need to depend on the decisions of research funders.
+Releasing selected subsets of unmaintained model artefacts in open source repositories is still better than not providing access to any code and data and can typically be accomplished within existing project budgets.
+Developing knowledge and skills of MOSHEMS can be advanced by making small contributions (e.g.
+improvements to documentation, code contributions) to open source projects.
+Our project website [@rfwn2022] includes details of multiple ways to contribute to ready4.
+
+<!-- Estimating the potential uptake of these tools is difficult.  -->
+<!-- Open source is more than open access (limited discussion). -->
+ <!-- A coding framework for OSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions [@Alarid2019]. -->
 <!-- http://hdl.handle.net/1893/27205--><!-- CONTEXT: Funders should also support methodological work on context, including the development of reporting templates to facilitate accurate, comprehensive and systematic reporting of context, approaches to evidence synthesis that can capture contextual variation adequately and modelling methods that can leverage the accumulating evidence on contextual variation to predict the reach, implementation and effectiveness of promising interventions in new contexts." --
-
-<!-- the framework represents a technical capacity rather than a behavioural outcome.  -->
 
@@
  <!-- - Our analysis - do it in stages, be transparent, continually improve, get help, be flexible (modelling toolkit / monolithic model), have a framework -->
- <!-- A coding framework for OSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions [@Alarid2019]. -->
-
-<!-- Is it desirable for this to become default authoring tool or better to be replication tool. -->
-
-Estimating the potential uptake of these tools is difficult.
-
-<!-- Add ref to NMHSMN in Australia --> Similarly, developing partnerships between modellers and decision-makers across the life-cycle of a modelling project can help ensure models are appropriately conceptualised, implemented and have practical utility as decision aids [@Zabell2021; @SQUIRES2016588].
-
-- Community building (feasibility)
-<!-- Open source is more than open access (limited discussion). -->
-- Funding contingent directions - replications / transfers
-
 <!-- Diversify skills - move to tools means software engineering, -->
@@
 
-## Implications for health economists
 <!-- Standardized and transferable approaches to health economic modelling have been recommended. [doi:10.1017/S0266462317000666] -->
@@
 <!-- transferability - [https://doi.org/10.1017/S026646232200321X].  -->
-Output by health economists [@pitt2016economic; @wagstaff2012four; @munoz2020health]
+<!-- Output by health economists [@pitt2016economic; @wagstaff2012four; @munoz2020health] -->
+<!-- - Can develop guidelines and funding proposals, make small amounts of artefacts online -->
 
-## Implications for research funders
 <!-- Reducing waste in research is responsibility of research funder: https://doi.org/10.1016/S0140-6736(13)62229-1 -->
->
-
-- unreasonable to expect more accountability without more resources
 
@@
 
-Major mental health reform programs, <!-- such as those currently being implemented in Victoria, Australia [@VicRC2021],  -->can involve the identification, prioritisation, sequencing, targeting and monitoring of multiple interdependent initiatives.
+<!-- Major mental health reform programs, <!-- such as those currently being implemented in Victoria, Australia [@VicRC2021],  -->
+<!-- can involve the identification, prioritisation, sequencing, targeting and monitoring of multiple interdependent initiatives.   -->
 
-The development, validation and updating of more complex mental health economic models implemented over longer time frames may be too onerous a burden for a single modelling team.
+<!-- The development, validation and updating of more complex mental health economic models implemented over longer time frames may be too onerous a burden for a single modelling team.  -->
 
@@
  <!-- as part of the Open Value Initiative [@Jansen2019].  -->
-
+<!-- Similarly, developing partnerships between modellers and decision-makers across the life-cycle of a modelling project can help ensure models are appropriately conceptualised, implemented and have practical utility as decision aids [@Zabell2021; @SQUIRES2016588].
+-->
  <!-- Yet single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020; @Occhipinti2021].  -->

### 2023-02-01 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
draft for selected co-author circulation

@@
 Open source approaches can help address this by disseminating code artefacts that enable easy and appropriate use of a statistical model to make predictions with new data.
-However, great care must be exercised when publicly releasing model aretefacts  derived from data on human subjects as they may by default embed a copy of the source dataset.
+However, great care must be exercised when publicly releasing model artefacts derived from data on human subjects as they may by default embed a copy of the source dataset.
 Sensitive dataset copies must therefore be replaced (for example, with synthetic data) and the amended artefact's predictive performance then retested before any public release.

### 2023-02-01 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
edits up to mid discussion
draft for selected co-author circulation

@@
 There is a strong case for making health economists more accountable for the appropriate use and social acceptability of their models.
-Users of models should be able to assess their adequacy for a particular purpose [@thompson2019escape].
+Potential users of models should be able to assess their adequacy for a particular purpose [@thompson2019escape].
 This goal is difficult to achieve in the current context of the poor reproducibility [@Jalali2021; @McManus2019; @Bermejo2017] and frequently insufficient validation [@Ghabri2019] of health economic models.
@@
 
-Our interest in modular and open source source approaches developed when we began seeking am appropriate framework for undertaking and validly synthesising diverse types of economic research in mental health.
+Our interest in modular and open source approaches developed when we began seeking am appropriate framework for undertaking and validly synthesising diverse types of economic research in mental health.
 Mental disorders impose high health, social and economic burdens worldwide [@RN8;@GBD2019].

### 2023-02-01 Markdown/Manuscript/Child_RMDs/MS_Tables_2.Rmd
draft for selected co-author circulation

--- 2023-01-26 Markdown/Manuscript/Child_RMDs/MS_Tables_2.Rmd
@@
   as.data.frame() 
+if(params$X@outp_formats_chr[1] != "Word"){
       df$Ref <- c("@ready42022",
@@
                     "@ready4show2022")
+}else{
+  df$Ref <- ""
+}
+
 df <- df %>%

### 2023-02-01 setup.R

@@ -37,17 +37,17 @@ X <- renewSlot(X,
                "abstract_args_ls",
                {
                  args_ls <- X@abstract_args_ls
-                 args_ls$abstract_ls <- list(Summary = "Health economists make limited use of the modular and open source approaches to model building that other disciplines use for collaborative development of complex modelling projects. 
+                 args_ls$abstract_ls <- list(Summary = "Health economists make limited use of the modular and open source approaches that other disciplines use for collaborative development of complex models. 
                                              We propose a framework for developing a modular open source health economic model (MOSHEM) in youth mental health called ready4.
                                              The framework includes of set of 20 standards for implementing a MOSHEM that is accountable (seven standards), reusable (nine standards) and updatable (four standards). 
                                              We provide a rationale for each standard.
-                                             The framework also includes a modelling toolkit of open access repositories and six R libraries for authoring ready4 modules (data structures and algorithms), supplying those modules with data and using the modules to implement reproducible modelling analyses. 
-                                             We describe an early application of the framework to developing utility mapping models that currently meet 18 framework standards. 
-                                             We discuss the potential benefits and challenges of extending ready4 in order to undertake and synthesise diverse economic modelling studies in youth mental health and highlight some broader implications for health economists and research funders.",
+                                             The framework also includes a modelling toolkit of open access repositories and six R libraries for authoring MOSHEM modules, supplying those modules with data and implementing reproducible modelling analyses. 
+                                             We describe an early application of the framework to implementing a utility mapping study and detail how the MOSHEM components produced by that study meet 18 framework standards. 
+                                             We discuss how the framework will enable us to undertake and synthesise diverse economic modelling studies in youth mental health and highlight some broader implications for undertaking MOSHEMs to explore mental health and other topics.",
                                              # Objectives = "We aimed to develop a conceptual and technical framework for implementing open source mental health systems models and illustrate how it can be applicatied to economic topics in youth mental health.",
                                              # Methods = "We created a software development kit in R to support standardised implementation of mental health systems models. As a worked example, we applied the toolkit to develop open source youth mental health utility mapping models, which we assessed against five principles using 17 standards.",
[…]

### 2023-04-19 Markdown/Manuscript/Child_RMDs/Clippings.Rmd
first pass and updated bib

--- 2023-02-01 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
@@
 ---
-title: "MS_Discussion"
-author: "Author"
-date: "`r Sys.Date()`"
+title: "Clippings"
 output: html_document
+date: "2023-04-18"
 ---
+
+#################################
+
+Computational models, particularly those addressing economic topics, have become essential tools for health policy development [@dakin2015influence; @Erdemir2020].
+Although influential and widely used, health economic models typically have a number of limitations that at best restrict their usefulness and which in some cases may facilitate harmful misuse.
+
+There is a strong case for making health economists more accountable for the appropriate use and social acceptability of their models.
+Potential users of models should be able to assess their adequacy for a particular purpose [@thompson2019escape].
+This goal is difficult to achieve in the current context of the poor reproducibility [@Jalali2021; @McManus2019; @Bermejo2017] and frequently insufficient validation [@Ghabri2019] of health economic models.
+Many health economic models are released with undeclared errors [@Radeva2020].
+The value judgments that strongly shape health economic analyses are rarely made explicit, omissions that may lead to socially unacceptable policy recommendations [@duckett2022journey].
+A modelling team's value judgments about what questions to address, the most important features of a system to represent and the weighting of different types of evidence may be poorly aligned with those of the people impacted by decisions informed by model analyses [@thompson2022escape].
+As health economic models adopt more sophisticated techniques, the need for accountability grows.
+More complex models may be more prone to propagation errors [@Saltelli2019] and models designed to address multiple questions should be expected to meet more onerous verification and validation obligations [@Eddy2012; @Feenstra2022].
+The nature and extent of individual model authorship contributions may be less clear in models implemented over longer time-frames with a large and changing group of collaborators [@thompson2022escape].
+
+The resource and skills intensive undertaking of modelling could be made more tractable if it was easier for health economists to re-use each other's models [@Arnold2010].
+However, as many health economic models are owned by pharmaceutical companies and consultancies, commercial considerations can limit the reuse of models and their constituent code and data [@Feenstra2022].
+Legal and ethical issues such as privacy and confidentiality requirements further limit public release of some model artefacts [@Pouwels2022].
+Transferring a health economic model developed for one jurisdiction for application in another typically involves retaining some features and updating others [@barbieri2010international].
+However, models do not always make implementation choices (for example, use of concepts with standardised meanings across jurisdictions<!-- [@garcia2021cost] -->, supplying context specific data as replaceable data-packs and distributing source code under licenses that allow derivative works) that facilitate model transferability.
+
+Health economic models should be updated and refined as new evidence emerges and decision contexts change [@Jenkins2021], but this occurs infrequently [@Sampson2017].
+Funding for health economic modelling projects rarely extend to provision of medium term support for model updates and improvements.
+The career trajectories of health economists can also mitigate against adequate maintenance of a model, it being relatively common for model authors to have moved on from the team that owns the model and / or from working on the health condition for which the model was developed.
+
+A potential strategy for improving model accountability, reusability and updatability is to make models both modular and open-source.
+
+A modular model is constructed from multiple reusable and replaceable sub-models (modules) [@pan2021modular].
+Modules can share inputs and outputs with other modules or can be run as independent models [@barros2023empowering].
+Advantages of modular models include feasibility (large projects are broken into smaller tasks, with each component independently developed and tested) and flexibility (making it easier to selectively replace or update specific parts of a model and to scale up or down the level of granularity) [@pan2021modular].
+Modular approaches are currently being used to facilitate the development of complex computational models in disciplines such as biology [@pan2021modular], ecology [@barros2023empowering] and neuroscience [@frazier2022robust].
+In health economics the related and enabling concept of reference models has been recommended [@Afzali2013], but peer reviewed studies describing modular health economic models remain relatively rare, though examples exist in infectious disease [@Trauer2017] and cardiology [@Urach2013].
+
+Modular models provide an opportunity for multiple modelling teams to contribute to, test and reuse models.
+To enhance this capacity, modular models may be implemented as open source projects that give others liberal permissions to access and use model source code and data [@pan2021modular; @barros2023empowering; @frazier2022robust].
+Although there appears to be in principle support from many health economists for greater use of open source health economic models (OSHEMs)  [@Pouwels2022], actual implementations are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022].
+Barriers to adoption of OSHEMs include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations [@Pouwels2022; @Wu2019].
+Adherence to good practice guidance is an essential requirement for healthcare modelling [@Erdemir2020], but guidelines for implementing OSHEMs remain scarce, piecemeal and need improving [@Sampson2019].
+
+Our interest in modular and open source approaches developed when we began seeking am appropriate framework for undertaking and validly synthesising diverse types of economic research in mental health.
+Mental disorders impose high health, social and economic burdens worldwide [@RN8;@GBD2019].
+Much of this burden is potentially avertable [@RN25], but poorly financed and organised mental health systems are ill-equipped for this challenge [@RN22;@RN23].
+A substantial economic literature already exists to assess the affordability and value for money of mental health interventions [@RN34].
+This economic evaluation work is an essential prerequisite for improving allocative efficiency in mental health, but could be of greater value to systems planners if integrated with a broader program of economic research.
+
+We are developing ready4 (https://www.ready4-dev.com), a modular OSHEM (MOSHEM) on the mental health of young people aged 12 to 25.
+We are initially applying ready4 to four of the twelve domains of health economics identified by Wagstaff and Culyer [@wagstaff2012four]:
+<!-- There is therefore an opportunity for health economists to undertake mental health research of significant potential public benefit. -->
+
+- *health and its value* (our projects: utility mapping models);
+
+- *determinants of health and ill-health* (our projects: models for creating synthetic household populations with key risk and protective factors for mental disorders);
+
+- *demand for health and health care* (our projects: spatial epidemiology and help-seeking choice models); and
+
+- *supply of health services* (our projects: a model of primary mental health care services).
+
+Once these projects are completed, our aim is to flexibly combine these models to answer questions in two additional Wagstaff and Culyer domains:
+
+- *efficiency and equity* (our goal: assess the distributional impacts and identify the optimal targeting of care provision); and
+
+- *economic evaluation* (our goal: assess the cost-utility of competing policy options for improving the mental health of young people).
+
+Standardisation is an essential enabler of automation, collaboration, interoperability and transferability in modular and open source approaches.
+An early requirement to implement ready4 is therefore to identify an appropriate set of standards.
+However, we are not aware of any consolidated source of guidance about recommended standards for MOSHEMs.
+Once identified, the standards specified for ready4 will need to be implemented by software, some of which will require custom development.
+
+<!-- When planning how to undertake and synthesise this program of work, we became concerned with issues relating to accountability, reusability and updatability.
+If mistakes are common in individual health economic modelling projects [@Radeva2020], then combining multiple projects may be particularly error prone.
+The risk of errors may also depend on whether a model is too simple or too complex [@Saltelli2019], so the level of granularity appropriate for one model application may be ill-suited to another.
+Undertaking a multiannual program of interdependent work raises the risk that models developed in the first phase of a project may need to be updated by the time the project is approaching conclusion.
+-->
+
+<!-- These concerns led us to seek the MOSHEM approach that provides the transparency to make it easier for errors to be uncovered, the adaptability to fix these errors and the flexibility to facilitate interchangeability between representations of different levels of granularity.
+-->
+
+### Standards for an accountable MOSHEM
+Guidance on transparency in health economic modelling published over ten years ago [@Eddy2012] made recommendations on documenting models but notably did not include recommendations on sharing model code and data.
+However, more recent and multidisciplinary healthcare modelling guidance [@Erdemir2020] recommends using existing digital repository services to make these types of digital model artefacts publicly available.
+Some repositories such as GitHub [@github2007] provide tools for disseminating work in progress code and providing highly transparent records of the complete development history and individual authorship contributions of a software project.
+Other repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each code and data collection.
+
+Model code and data should be clearly documented, potentially with different versions for technical and non-technical users [@Eddy2012].
+Consistent use of meaningful naming conventions when authoring code is recommended [@Wilson_2017; @Alarid2019].
+Code can be made easier to follow by using the practices of abstraction [@8717448], where only simple, high level commands are routinely exposed to reviewers, and polymorphism [@7181447], where the same command (e.g.
+"simulate") can be reused to implement different algorithms of the same type.
+Programs to implement model analyses can be made comprehensible to even non-technical users through the use of literate programming techniques and tools like RMarkdown [@xie2018r] that integrate computer code with plain English descriptions.
+
+An essential component of quality assuring health economic models is verification - ensuring that calculations are correct and consistent with model specifications [@techver2019].
+One useful concept for informing model users about the extensiveness of verification checks is code coverage [@ERICWONG2010188] - the proportion of model code that has been explicitly tested.
+<!-- In R, the testthat [@testthat2011] and covr [@covr2020] tools can be used in conjunction with GitHub to define tests and report coverage metrics.
+-->Transcription errors - mistakes introduced when transferring data between sources, models and reports - are very common in health economic models [@Radeva2020].
+The risk of these errors might be lower if there was full transparency across all steps in a study workflow.
+Scientific computing tools now make it relatively straightforward to author programs that reproducibly execute all steps in data ingest, processing and reporting [@Wilson_2017].
+
+Code and data should be distributed with tools that make it easy for potential users to appropriately cite each model artefact.
+
+### Standards for a reusable MOSHEM
+```{r echo = F}
+gpl_pc_dbl <- get_license_share("GPL")
+```
+To make model code and data widely re-usable by others, it is important to provide users with appropriate and explicit permissions.
+In the context of open source models, there are two broad categories of licensing options.
+Some guidance strongly recommends the use of permissive licensing [@Wilson_2017] that provides users with great flexibility as to the purposes (including commercial) for which the content could be re-used.
+An alternative approach is to use copyleft licenses [@copyleft2022] that can require content users to distribute any derivative works they create under similar open source arrangements.
+For code, it may be appropriate to adopt the prevailing open source licensing practice within the programming language being used.
+For data, it may not be sufficient to simply choose between a permissive license like the Public Domain Dedication (CC0) [@cc02022] or a copyleft option such as the Attribution-Share Alike (CC-BY-SA) [@bysa2022].
+In addition to ensuring that data is ethically appropriate for disseminate in open access repositories, responsible custodianship of some de-identified or aggregated data may involve using or adapting template terms of use [@sampleterms2022] which have a number of ethical clauses (for example, prohibiting efforts to re-identify research participants).
+
+Storing model code and data in separate files and locations (as opposed to hard coding - embedding data into source code) can make it easier to apply models to different decision contexts and to selectively restrict access to data that are confidential, while disseminating all other model artefacts.
+Clear distinctions should be made between model modules (code that defines abstract data structures and the algorithms that can be applied to data described by these structures), model datasets (digital information such as parameter values, unit records, etc) and model analyses (code that links model datasets to model modules and specifies the algorithms to apply to data associated with each module).
+
+The software development practice of encapsulation [@8717448] can be used to help ensure that model modules continue to work as intended when they are combined [@ready4oop2022].
+In some cases, combining modules may mean new versions of modules have to be created to better account for interaction effects.
+The concept of inheritance [@8717448] can be used to write code that efficiently achieves this objective as well as to facilitate selective editing of modules when transferring models to different decision contexts [@ready4oop2022].
+Writing algorithms as collections of functions (short, self-contained and reusable software routines that each perform a discrete task) is recommended as good practice for scientific computing [@Wilson_2017].
+Functions to implement model algorithms can be associated with data structures (also known as a class) via a special type of function called a method.
+Model modules of a similar type or purpose can be efficiently distributed and documented by bundling them as code libraries.
+It is good practice to make available test or toy data to demonstrate the use of model algorithms [@Wilson_2017].
+
+Statistical models are a common output of health economic evaluations, but they are often not reported in a format that enables others to confidently and reliably re-use them for out of sample prediction [@Kearns2013].
+Open source approaches can help address this by disseminating code artefacts that enable easy and appropriate use of a statistical model to make predictions with new data.
+However, great care must be exercised when publicly releasing model artefacts derived from data on human subjects as they may by default embed a copy of the source dataset.
+Sensitive dataset copies must therefore be replaced (for example, with synthetic data) and the amended artefact's predictive performance then retested before any public release.
+Another way to make MOSHEMs easier to use is to develop simple user-interfaces for non-technical users.
+
+### Standards for an updatable MOSHEM
+To avoid MOSHEMs going stale - losing validity and usefulness with time - they should be routinely updated.
+Each update of code and data should be uniquely identifiable and retrievable, a goal that can be facilitated by use of version control tools [@Erdemir2020] such as git [@git20XX].
+
+Potential users of model code and data should be able to easily identify the appropriateness of a version to their needs.
+Using semantic versioning [@semver20xx] conventions can signal the potential importance of an update to users of model code and data.
+Also informative is to clearly label the type of code versions hosted in a repository as either:
+
+- "development" - typically the most comprehensive and up to date source code, but potentially not yet sufficiently well documented and tested for potential users to apply to purposes other than testing;
+
+- "production" - code that has been released with a view to it being applied to its stated purposes and therefore typically required to meet defined documentation and testing standards; or
+
+- "archive" - permanent copies of code at key milestones in its development that can aid study reproductions by making available the version of code used in a specific analysis.
+
+Continuous integration [@CI2017] tools can help verify that each code update continues to pass a standardised battery of quality tests.
+Finally, using deprecation conventions that take an informative and staged approach to retiring old code and data reduces the risk of model revisions having unintended consequences on third party users.
+
+We developed a toolkit to help us develop and use MOSHEM modules, datasets and analyses that meet the standards listed in Table \@ref(tab:timelygls).
+The toolkit is comprised of online repositories and software.
+
+## Repositories <!-- Existing ref -->
+We created a GitHub organisation (a collection of code repositories) where all our development code is stored and version controlled [@ready4gh2022].
+We configured the repositories in our GitHub organisation to use GitHub actions to support continuous integration.
+Some of the continuous integration checks we have defined assess each library's compliance with policies specified by the Comprehensive R Archive Network (CRAN) [@CRAN2022], to which we plan submitting future production releases.
+To track our code coverage, we linked our GitHub organisation to an account we established at codecov [@codecov_2022].
+
+We enabled GitHub Pages in each repository we used for code library development to facilitate the creation and hosting of library documentation websites.
+We also developed a consolidated and versioned project documentation website [@rfwn2022] using the Hugo framework [@hugo_2023] and Docsy theme [@docsy_2023].
+To host that website we established an account with Netlify [@netlify_2023] and linked that service to our GitHub organisation so that the website would automatically update whenever the source code in its GitHub repository was edited.
+
+We also created a Zenodo community [@ready4zen2022] - a collection of permanent, uniquely identified repositories.
+We then linked our Zenodo community and GitHub organisation so that every time we specify a version of code in one of our GitHub repositories as a "release", a copy of that code is automatically created on Zenodo with a DOI.
+Finally, to manage model datasets, we created a dedicated collection within the Harvard Dataverse installation [@ready4dv2022].
+
+## Software <!-- Novel ref -->
+We created six development version R libraries to help us author model modules, supply those modules with data and implement reproducible modelling analyses.
+The six libraries, their primary focus, the standards they support and the third-party packages they depend on are summarised in Table \@ref(tab:cpkgs).
+
+A library called ready4 [@ready42022] defines a template module (using R's S4 class system) from which all model module data structures will inherit features and a novel syntax for attaching algorithms to those data structures.
+The ready4 library also contains tools for retrieving web based information on model modules, datasets and analysis programs and for partially automating updates to the project documentation website.
+
+Three R libraries are designed to standardise and partially automate workflows for authoring new model modules.
+The ready4pack library [@ready4pack2022] is designed to integrate with our GitHub organisation and provides tools for authoring module libraries that are:
+
+- documented (with a website, a manual itemising selected contents and a manual itemising all contents);
+
+- licensed (using GNU GPL-3 [@GNUGPL2022] by default);
+
+- easily citable (citation information can be retrieved within an R session or from hosting repositories); and
+
+- quality assured (each update triggers continuous integration workflows, including any unit tests created by module library authors).
+
+The ready4pack library depends on two other module authoring libraries.
+Methods from the ready4fun library [@ready4fun2022] are used to verify that functions for implementing module algorithms are written in a consistent house style.
+That standardised format is then used by ready4fun methods to automatically generate basic documentation for each function.
+Methods from the ready4class [@ready4class2022] library are used to streamline and standardise the authoring of module data structures and the linking of methods to these data structures.
+Like ready4fun, the ready4class library uses standardised code implementation to automatically generate basic documentation for each module data structure.
+
+The ready4use library  [@ready4use2022] contains modules for ingesting model datasets from online repositories (hosted on a Dataverse installation or on GitHub), labelling model datasets and sharing model datasets via online repositories.
+The ready4show library [@ready4show2022] contains tools to help author analyses programs that are either self-documenting or which trigger the creation of a scientific summary.
+
+When used in conjunction with toolkit repositories, the six R libraries provide support for implementing 17 out of 20 framework standards (Table \@ref(tab:timelygls)).
+Standards relating to safe dissemination of statistical models (R8), user-interface development (R9) and deprecation conventions (U4) are better met through using existing third party R libraries.
+Preparing statistical models for dissemination can be accomplished with standard R data management tools like the dplyr [@dplyr2022] and purrr [@dplyr2022] libraries.
+User-interfaces are typically developed with the shiny [@shiny2022] library, for which a tutorial aimed at health economists is available [@SmithR2020].
+The library lifecycle [@lifecycle2021] provides tools for R developers to consistently deprecate their code.
+
+We applied the framework to develop an initial set of ready4 modules, supply those modules with data and implement modelling analyses.
+These outputs were created as part of a previously described study [@Hamilton2021.07.07.21260129] to develop utility mapping models appropriate for use in samples of young people presenting to primary mental health services.
+The ready4 framework's modelling toolkit created the following artefacts:
+
+ - development version module libraries for describing and validating youth mental health human record datasets [@hamilton_matthew_2022_6084467], scoring health utility [@hamilton_matthew_2022_6084824], specifying utility mapping models [@hamilton_matthew_2022_6116701] and implementing reproducible utility mapping studies [@gao_caroline_2022_6130155];
+
+ - a development version library of functions for finding and using utility mapping models developed with these tools [@matthew_p_hamilton_2021_5646669];
+
+ - data collections of synthetic populations for testing model modules [@DVN/HJXYKQ_2021] and study input and results data [@DVN/DKDIB0_2021];
+
+ - programs for replicating all steps from data ingest to manuscript reporting [@hamilton_matthew_2022_6129906], applying utility mapping models to new data [@hamilton_matthew_2022_6416330] and generating a synthetic representation of the study dataset [@hamilton_matthew_p_2022_6321821];
+
+ - subroutines for creating a catalogue of utility mapping models [@hamilton_matthew_2022_6116385] and generating a draft scientific manuscript [@matthew_p_hamilton_2022_5976988] for studies implemented with these modules.
+
+We created a checklist (Table \@ref(tab:checktb)) that we used to assess the extent to which study outputs met framework standards.
+We assessed these outputs as wholly or mostly meeting 18 out of 20 standards.
+The two standards where the study outputs currently fall short are in reporting code coverage and including a user-interface.
+Both these items are scheduled to be addressed when we release production versions of the code libraries.
 

### 2023-04-19 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
first pass and updated bib

@@
 In this paper, we describe:
-
-(i) a framework that specifies MOSHEM standards and provides the tools to implement them; and
-
-(ii) the application of that framework to develop and use an initial set of ready4 modules in a utility mapping study.
+(i)	a set of ethical responsibilities for CHEM developers and criteria for assessing responsible CHEM implementations;
+(ii)	a prototype software framework for the ethical implementation of CHEMs; and
+(iii)	use of the software framework to develop a computational economic model in youth mental health, with an initial focus on outcome valuation.

### 2023-04-19 Markdown/Manuscript/Child_RMDs/MS_Conclusion.Rmd
first pass and updated bib

--- 2022-04-19 Markdown/Manuscript/Child_RMDs/MS_Conclusion.Rmd
@@
 `r ifelse(is.na(params$X@conclusion_1L_chr),"",params$X@conclusion_1L_chr)` 
+We have identified criteria that can be used to systematically assess extent to which the computational implementation of health economic models adheres to the ethical goals of transparency, reusability and updatability.
+We have developed an open-source software framework that can support the ethical computational implementation of economic models in youth mental health.
+Our framework can be used as a prototype for developing future software frameworks to support ethical implementation of CHEMs.

### 2023-04-19 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
first pass and updated bib

--- 2023-01-31 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
@@
 
-In this article we described a framework that we developed to help us implement ready4 - a MOSHEM in youth mental health.
-We outlined framework standards for an accountable, reusable and updatable MOSHEM and described the modelling toolkit we created for applying those standards to the development and use of the ready4 MOSHEM.
-We also provided an overview of an initial set of MOSHEM modules developed with the framework to implement a utility mapping study.
-We reviewed the modules, datasets and analyses generated by that study against framework standards.
-The work we have described has potential implications for the development of the ready4 MOSHEM and for health economic modelling in mental health and highlights more general issues for health economic modellers and funders of health economic research.
+Ethical practice is a core expectation of health researchers and computational methods underpin most quantitive research, yet an understanding of what constitutes ethical computational modelling practice in health is underdeveloped [@10.3389/fpubh.2017.00068].
+The modeller responsibilities, enabling model attributes and model implementation assessment criteria that we propose can help address this gap.
 
-## Implications for implementing ready4
-The most direct implication of the development of the ready4 framework is that it makes it feasible for us to implement a MOSHEM in youth mental health.
-The standards specified by the framework have enabled us to partially automate workflows for developing and applying ready4 through use of the framework's modelling toolkit.
-We have demonstrated the practical utility of the modelling toolkit by applying it to authoring, documenting and disseminating ready4 module libraries  [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155], datasets [@DVN/HJXYKQ_2021; @DVN/DKDIB0_2021]; analyses [@hamilton_matthew_2022_6129906; @hamilton_matthew_2022_6416330; @hamilton_matthew_p_2022_6321821], reporting templates [@hamilton_matthew_2022_6116385; @matthew_p_hamilton_2022_5976988] and prediction tools  @matthew_p_hamilton_2021_5646669] used in a utility mapping study [@Hamilton2021.07.07.21260129].
-The standardised and partially automated workflows used in creating and sharing these artefacts has the potential to generate significant efficiencies as we apply the ready4 framework to undertaking new studies.
+The ethical responsibilities and enabling model attributes we describe have both commonalities and distinctive features compared to a previous ethical framework for computational modelling in public health [@10.3389/fpubh.2017.00068].
+The authors of that framework propose 13 questions to evaluate ethical risk across the four criteria of independence, transparency, benficience and justice.
+Their descriptions of the four criteria at least partially map to either our proposed modeler responsibilities (“justice” to “social acceptability”, “independence” to “adequacy for purpose” and “beneficience” to “beneficial impact”) or enabling model attributes (“transparency”).
+However, while our six assessment criteria are specific to three attributes (TRU) of the computational implementation of the model, the prior ethical framework includes questions relevant to the the conceptual and mathematical models and the potential impacts of model use.
+Examples of these more general evaluation questions include (for the justice criterion) “is any lack of knowledge about important parameters attributable to uncertainty or variability?” and (for the beneficience criterion) “if a policy is based on the model evidence, is it more likely to be effective and beneficial than a decision made in the absence of the model?”.
+The less numerous and more focused assessment criteria we propose may potentially be more tractable to implement in reviews of models authored by third parties and as the basis for designing software frameworks to support ethical computational model implementation.
 
-We have also been able to demonstrate the interoperability of the initial ready4 modules developed with the modelling toolkit.
-The program used to implement the utility mapping analysis [@hamilton_matthew_2022_6129906] combines modules from four module libraries ([@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155]) and two framework libraries [@ready4use2022; @ready4show2022].
-Example literate programs published on the ready4 documentation website [@rfwn2022] use toy data [@DVN/HJXYKQ_2021] to illustrate the potential for ready4 modules to facilitate study replication and transferability.
-The framework's standards also provide a mechanism for to assess the extent to which the ready4 MOSHEM meets explicit accountability, reusability and updatability goals.
+Currently, many if not most existing CHEMs are insufficiently transparent [@Jalali2021; @McManus2019; @Bermejo2017; @Ghabri2019], reusable [@Feenstra2022; @Emerson2019] and updatable [@Sampson2017; @10.3389/fpubh.2022.899874]].
+There appears to be in-principle support from health economists to address these practice shortfalls through greater use of for open-source approaches [@Pouwels2022] that are currently rarely implemented [@Feenstra2022; @Emerson2019].
+Existing incentive structures for health economists generally do not promote facilitating peers to reuse their work.
+Currently, it takes “an extraordinary amount of idealism” to dedicate the substantial time and resources required to author, test, document and maintain even fragile prototype research software that could instead be used to write scientific manuscripts [@anzt2020environment].
 
-However, having features that facilitate accountability, reuse and updating is not the same as being accountable, reused and updated.
-If diverse groups of stakeholders do not review model components, suggest improvements and develop alternatives, then little progress is made towards enhancing model legitimacy.
-Similarly, making code and data publicly available does not guarantee that others will know of the existence of these tools, trust their validity and find them easy to use.
-Without reuse, errors in model aretefacts are more likely to remain undetected.
-Even when errors are detected, they still need to be fixed, but maintaining code and data requires ongoing resourcing through a combination of centralised infrastructure and an active open source community.
+Reducing waste in research is a core responsibility of research funders [@chalmers2014increase] and funding the development of CHEMs that are not adequately understood, reused or updated is wasteful.
+Previously recommended strategies for more beneficial health economic research investments include support for harmonized ethical standards for model development [@10.3389/fpubh.2017.00068], methodological innovation to improve model transferability  [@craig2018taking], networks of modellers working on common health conditions [@Sampson2019], and  centralized infrastructure such as open source model repositories [@Pouwels2022] and a standard platform for model implementations [@Ghabri2019].
+Development of software frameworks to support ethical CHEM implementations could enable and enhance each of these strategies.
 
-Currently all the framework and module libraries we have developed are available only as "development" releases.
-An early priority for us is to undertake the additional development, testing and documenting of these libraries so that we can submit production versions of each library to CRAN [@CRAN2022].
-Making these libraries available on CRAN is a likely prerequisite of high levels of reuse.
-Similarly, completing our current work program will create new tools for modelling help-seeking choice, spatial epidemiology, household populations and primary mental health services that may enhance the potential usefulness of the ready4 MOSHEM to health economists working in youth mental health.
+As illustrated by Table \@ref(tab:checktb), we have developed a software framework that can help us to author a youth mental health model that largely satisfy our TRU criteria.
+However, we believe our software framework is currently too fragile to be anything more than a prototype for supporting the development needs other modelling teams and projects.
+A major reason for this distinction is that our software framework was developed with the needs of only one group of developers in mind – ourselves.
+We currently lack the resources required to adequately implement strategies to target factors such as user enjoyment, usability, active user-community and supporting resources that influence adoption of software frameworks [@myllarniemi2018development].
 
-## Implications for economic modelling in mental health
-Open source approaches have been recommended to help develop the mental health modelling field [@RN73] but only one mental health related model (in Alcohol Use Disorder [@Basu2018]) is currently indexed in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019].
-We are aware of just one other open source mental health model - a reference model in Major Depressive Disorder - that is currently in development [@IVIMDD2022].
-Of the known barriers to adoption of open source models by health economists (including issues like intellectual property and confidentiality [@Pouwels2022; @Wu2019]), our experience suggests that the enormous effort that is required to prepare model code and data for public release in formats that facilitate appropriate reuse by third parties and to maintain and improve these artefacts may be the biggest challenge.
+Our prototype framework has a number of features that subsequent work to develop ethical software frameworks may find useful to incorporate.
+Firstly, developing a software framework to work within an existing and widely used open source programming language such as R or python, can keep framework scope relatively narrow (making it more tractable to develop, maintain and learn) while readily leveraging and coherently integrate other modelling tools written in that language (e.g.
+the dependency libraries we list in Table \@ref(tab:cpkgs)).
+Secondly, implementation that combines both object oriented and functional programming paradigms can avail of the modular and syntactical simplicity benefits of the former, while limiting needless bundling of code artefacts (a limitation of object oriented approaches famously described as: “you wanted a banana but what you got was a gorilla holding the banana” [@seibel2009joe]).
+Thirdly, a sensible trade-off needs to be found between transparent code implementation (which requires clear and sufficiently detailed documentation) and Agile Software Development (for which a foundational principle is prioritizing the development of working code over writing documentation [@beck2001manifesto]).
+Our software framework makes this trade off by enforcing the use of consistent code naming conventions and file organisation which in turn enables automated generation of simple documentation at every code update.
+All model data-structures and algorithms are therefore always documented (at least minimally, with machine authored content), meaning model developers have a requirement to write customized documentation less frequently.
 
-Automated tools such as those we developed in our modelling toolkit can help reduce the burden of some of these tasks.
-However, we think the current low rates of adoption by health economists of open source approaches [@Emerson2019; @Michalczyk2018; @Feenstra2022] (which in turn facilitate the collaboration that make modular models more attractive) is unlikely to change soon without significant and strategic changes by research funders.
-The incentive structures that health economists work within do not promote the investment of significantly more time on each study to enable peers to reuse their work.
-
-Reducing waste in research is a responsibility of research funders [@chalmers2014increase] and the poor reproducibility [@Jalali2021; @McManus2019; @Bermejo2017], limited reusability [@Emerson2019; @Michalczyk2018; @Feenstra2022] and uncertain validity [@Ghabri2019; @Radeva2020] of health economic models is wasteful.
-Approximately 4,000 mental health focused economic evaluation reports were produced between 2000 to 2019 [@RN34].
-The intellectual asset represented by this literature could be very substantial if many of the models described in these reports could be brought (and kept) up to date and made available in formats that maximised transferability to diverse decision contexts.
-We believe that modular and open source approaches would be well suited to accomplishing this goal and that the framework we have developed could act as an early prototype for solving some of the technical challenges of this task.
-Ideally such a programme of research would be resourced to be sustained over the medium to long term and to engage a diverse network of investigators, contributors and advisers from high, middle and low income countries.
-
-In addition to extracting more value from the existing health economic knowledge base in mental health, there is an opportunity for research funders to shape how future health economic models in mental health are undertaken.
-Mental health topics accounted for about 268 of 2829 (10%) peer reviewed economic evaluations undertaken during 26 month period in 2012-2014 identified in a previous review [@pitt2016economic].
-There is also likely to a substantial annual output of economic research in mental health that focuses on the other 11 domains identified by Wagstaff and Culyer [@wagstaff2012four].
-
-Providing adequate levels of funding to support MOSHEMs, fostering skills, supplying infrastructure (t)
-
-Developing networks of modellers working on common health conditions has been recommended as a strategy for improving model validity [@Sampson2019] and some of us are part of a nascent initiate of this type in mental health [@whiteford_bagheri_2022].
-Collaboration between teams of health economists can make some complex modelling projects more feasible [@Arnold2010] and the significant deficits in our understanding of the systems in which mental disorders emerge and are treated [@Fried2020] suggest that there are a number of candidate topics in mental health that might benefit from pooling of efforts.
-The weak theoretical underpinnings for understanding complex mental health systems [@RN2111] may be a place to start.
-It remains unclear why increased investments in mental health care have yet to discernibly reduce the prevalence and burden of mental disorders[@RN26].
-The  literature, and evidence base, regarding how the requirements, characteristics and performance of mental health services are shaped by spatiotemporal context needs to be further developed [@RN42].
-There is also a need for better evidence to identify the social determinants of mental disorders most amenable to preventative interventions, and for which population sub-groups such interventions would be most effective [@RN43].
-
-<!-- MH Research priorities (WP3 - Research, WP6 - Economic) https://doi.org/10.1016/S2215-0366(15)00332-6 -->
-<!-- http://hdl.handle.net/1893/27205--><!-- CONTEXT: Funders should also support methodological work on context, including the development of reporting templates to facilitate accurate, comprehensive and systematic reporting of context, approaches to evidence synthesis that can capture contextual variation adequately and modelling methods that can leverage the accumulating evidence on contextual variation to predict the reach, implementation and effectiveness of promising interventions in new contexts." --
-
-<!-- the framework represents a technical capacity rather than a behavioural outcome.  -->
-
-<!-- (described in more detail on the project documentation website [@rfwn2022])  -->
-
- <!-- - One shot at big changes -->
- <!-- - Our analysis - do it in stages, be transparent, continually improve, get help, be flexible (modelling toolkit / monolithic model), have a framework -->
- <!-- A coding framework for OSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions [@Alarid2019]. -->
-
-<!-- Is it desirable for this to become default authoring tool or better to be replication tool. -->
-
-Estimating the potential uptake of these tools is difficult.
-
-<!-- Add ref to NMHSMN in Australia --> Similarly, developing partnerships between modellers and decision-makers across the life-cycle of a modelling project can help ensure models are appropriately conceptualised, implemented and have practical utility as decision aids [@Zabell2021; @SQUIRES2016588].
-
-- Community building (feasibility)
-<!-- Open source is more than open access (limited discussion). -->
-- Funding contingent directions - replications / transfers
-
-## Implications for health economists
-<!-- Standardized and transferable approaches to health economic modelling have been recommended. [doi:10.1017/S0266462317000666] -->
-<!-- As modelling methods have become more sophisticated, some have argued that more complex models are required to adequately explore certain types of public health topics [@SQUIRES2016588].  -->
-<!-- Modellers should be faithful to reaity and values of users DOI: 10.1002/asi.23697 -->
-<!-- transferability - [https://doi.org/10.1017/S026646232200321X].  -->
-Output by health economists [@pitt2016economic; @wagstaff2012four; @munoz2020health]
-
-## Implications for research funders
-<!-- Reducing waste in research is responsibility of research funder: https://doi.org/10.1016/S0140-6736(13)62229-1 -->
->
-
-- unreasonable to expect more accountability without more resources
-
-<!-- greater use of these types of models may require adaptation on the part of funders, modellers and decision-makers. T -->
-
-<!-- Link to Wagstaff - Demand forecasting, valuation of health and healthcare, economic evaluation, utility mapping?? -->
-
-<!-- # Motivation -->
-
-<!-- ## Why develop OSHEMs in mental health -->
-
-Major mental health reform programs, <!-- such as those currently being implemented in Victoria, Australia [@VicRC2021],  -->can involve the identification, prioritisation, sequencing, targeting and monitoring of multiple interdependent initiatives.
-
-The development, validation and updating of more complex mental health economic models implemented over longer time frames may be too onerous a burden for a single modelling team.
-
-<!-- Decision makers are frequently left to rely on economic analyses that become less valid and relevant each year.
-A model can grow stale when changes in the real world, whether sudden (e.g.
-new pandemics) or gradual (e.g.
-demographic), is not represented by corresponding updates to relevant model features.
-Even when the system being modelled remains relatively stable, new research findings may potentially invalidate aspects of a model's original conceptualisation and implementation.
--->
-
-<!-- that rarely explores complex dynamic systems  -->
-<!-- [PECUNIA] -->
-
-<!-- Computational modelling could play an important role in developing policies to improve population mental health but this may require significant changes in the way mental health modelling projects are funded, conceptualised and implemented.
--->
- <!-- but, as with health economics more generally, OSHEMs remain rare.
-Greater use of open source approaches could help improve the scope, validity and usefulness of mental health economic models.
--->
-
-<!-- Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each unique item.
-These repositories are a preferable solution for sharing citable code and data than transitory repositories such as corporate websites or GitHub where items can be deleted or relocated at any time [@sseditors2022].
-Zenodo includes tools that automate integration with GitHub, which makes it easy for developers to maintain parallel code repositories - one for disseminating the most up to date development code and the other for archiving citable code releases.
---> <!-- Developers storing data in a Dataverse installation have access to multiple meta-data fields to document both a data collection and its individual constituent files.
---><!-- In R, code manuals and websites can be created with the aid of tools such as devtools [@devtools2021], sinew [@sinew2022], roxygen2 [@roxygen2021] and pkgdown [@pkgdown2022].
--->
-
-<!-- and the use of version control systems. <!-- such as Git [@git20XX].  -->
-
-<!-- Applying a previously published algorithm [@kross2016] to analyse the most comprehensive archive of released R packages [@CRAN2022] finds that `r gpl_pc_dbl`% are distributed under various forms of General Public License (GPL) [@GNUGPL2022], a copyleft license.
--->
-<!-- In R, including a CITATION file in the `inst` directory of a package will enable users of that package to retrieve citation information by running a command of the format `citation("Package Name")` in the R console [@Salmon2021].
-More generally, including a CITATION.cff file at the top level of your code repository will enable GitHub and Zenodo repositories hosting that item to include the relevant information in their citation tools [@Druskat_Citation_File_Format_2021].
-Datasets hosted on Dataverse installations have metadata fields that, once completed by authors, generate citation files for dataset viewers.
--->
-
-<!-- A key challenge to generalising health economic models is that they are typically developed to inform a decision problem with a highly specific jurisdictional context.
-However, a number of choices about how these models are implemented can significantly increase the re-usability of model code in other contexts.
--->
-<!-- For example, when generalising a model developed for the Australian context to a UK context, one could create a class that initially inherits all of the methods defined for the Australian model and then write new or replacement methods as needed for the UK model.
--->
-
-<!-- A number of tools and approaches can make the process of implementing and curating changes to model code and data more coherent and efficient.
-<!-- Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent access to all published versions of a dataset, each uniquely identifiable.
-For code, use of version control tools like Git [@git20XX] can ensure that the entire development history of a project is organised so that each version is distinguishable and retrievable by developers.
-The online platform GitHub [@github2007] can make this version history accessible to anyone.
--->
-
-<!-- For R code, the usethis [@usethis2021] package can be used to partially automate version number increments using the convention Major.Minor.Patch.Development (e.g.
-ExampleSoftware v1.1.1.1).
-Datasets stored on the Harvard Dataverse use the simpler Major.Minor convention.
--->
-<!-- MOSHEMs developed in R can take advantage of templates provided by devtools [@devtools2021] and pkgdown [@pkgdown2022] to run continuous integration checks on GitHub.
---><!-- These tests can include those of units (do individual functions produce expected output?), documentation (does documentation render correctly?; can all example workflows be executed?) and installation (can the software be successfully deployed on multiple types of operating system?).
--->
-<!-- MH systems design is not a pharma led project - less concerns about commercial ownership -->
-
-<!-- and for mental health specifically [@Occhipinti2021],  -->
-<!-- could provide greater insight about inter-dependencies between candidate policies and the dynamic nature of the mental health systems planning context.
-Dynamic systems methods might provide the foundations for developing   -->
-<!-- and models designed for multiple purposes r -->
-
- <!-- as part of the Open Value Initiative [@Jansen2019].  -->
-
- <!-- Yet single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020; @Occhipinti2021].  -->
-<!-- The large and widespread additional mental health burdens recently observed during the COVID-19 pandemic[@20211700] and predicted as a potential future consequence of climate change [@page_howard_2010], highlight the need to improve the resilience and adaptability of these systems.
-To help stem growing demand for mental health services, policymakers have also been encouraged to place greater emphasis on tackling the social determinants of mental disorders [@RN11].
--->
-
-<!-- Our approach to model development is to undertake a number of discrete modelling projects of the people, places, platforms and programs that shape the mental health and wellbeing of young people and to progressively link them together by means of a common framework.
-To model people we are developing synthetic representations of populations of interest [@DVN/HJXYKQ_2021] that describe relevant individual characteristics and their relationships, algorithms that map psychological measures to health utility [@Hamilton2021.07.07.21260129] and choice models for predicting the helpseeking behaviour of young people [@hamilton_matthew_2022_6627995].
-Our in-development model of places [@DVN/V3OKZV_2022] has the aim of synthesising geometry and spatial attribute data to characterise the geographic distribution of relevant demographic, environmental, epidemiological and service infrastructure features.
-We are in the early stages of a multi-annual project to develop a service platform model that will represent the processes and operations of a complex primary youth mental health service.
-We also plan to extend and update our prior work reviewing economic evidence relating to youth mental health programs [@RN33] so that it can be integrated with this model.
-Our initial work on **readyforwhatsnext** is focused on Victoria, Australia but the framework we are using to develop it is designed to facilitate extension by ourselves and others to different jurisdictional decision contexts.
-Progress is reported on a project website [@rfwn2022].
--->
+A future software framework for ethical CHEMs would ideally incorporate a base set of features useful to developers of computational models across all domains of public health, with the capability for community-led extensions that are tailored to the needs of modellers focused on specific health-conditions.

### 2023-04-19 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
first pass and updated bib

--- 2023-01-31 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
@@
 
-We applied the ready4 framework to develop an initial set of MOSHEM modules, supplying those modules with data and implementing analyses.
-These tools were created as part of a previously described study [@Hamilton2021.07.07.21260129] to develop utility mapping models appropriate for use in samples of young people presenting to primary mental health services.
-The ready4 framework's modelling toolkit created the following artefacts:
+##	Economic topics
+Currently, we are using the ready4 software framework to develop, apply and share youth mental health computational models in four of the twelve domains of health economics identified by Wagstaff and Culyer [@wagstaff2012four]:
+
+-	health and its value (our projects: utility mapping models);
+
+-	determinants of health and ill-health (our projects: models for creating synthetic household populations with key risk and protective factors for mental disorders);
+
+-	demand for health and health care (our projects: spatial epidemiology and help-seeking choice models); and
+
+-	supply of health services (our projects: a model of primary mental health care services).
+
+Once these projects are completed, our aim is to flexibly combine these models as modules of a multi-purpose model (also called “ready4”) to answer questions in two additional Wagstaff and Culyer domains:
+
+-	efficiency and equity (our goal: assess the distributional impacts and identify the optimal targeting of care provision); and
+
+-	economic evaluation (our goal: assess the cost-utility of competing policy options for improving the mental health of young people).
+
+## Case study: Utility mapping
+Our initial application of the ready4 software framework was to undertake a previously described study [@Hamilton2021.07.07.21260129] to develop utility mapping models for use in samples of young people presenting to primary mental health services.
+The ready4 software framework was used to develop CHEM modules, supply those modules with data and implement modelling analyses, creating the following artefacts:
 
@@
 
-We assess that these study outputs either wholly or mostly meet 18 out of 20 framework standards(see Table \@ref(tab:checktb)).
-The two standards where the study outputs currently fall short are in reporting code coverage and including a user-interface.
-Both these items are scheduled to be addressed when we release production versions of the code libraries.
+We created a checklist (Table \@ref(tab:checktb)) that we used to subjectively assess these study outputs against TRU criteria.
+For each criterion, we provided a global assessment of whether it was met using the responses “yes”, “no” or “partial”.
+We believe the outputs from our utility mapping study may be assessable as having satisfactorily met four of the six criteria (T1, T2, R2 and U1) and to have partially met two criteria (R1 and U2).
+The main shortcomings that we identified when applying the assessment criteria were the need for additional development before the CHEM modules would be sufficiently generalizable for valid application in datasets that measure health utility with different instruments and a general lack of unit testing.
+
+##	Model documentation 
+We developed a versioned model documentation website (www.ready4-dev.com) that provides guidance to model developers on how to use and contribute improvements to the ready4 software framework and model.
+The documentation website was developed using the Hugo framework [@hugo_2023], Docsy theme [@docsy_2023] and Algolia DocSearch [@algoliadocsearch_2023] and is hosted using the Netlify [@netlify_2023] service.
+We used functions from the ready4 R library to partially automate website updates relating to available CHEM modules, datasets and analysis programs.
+We linked our Netlify account to our GitHub organisation so that the project website would automatically update whenever the source code in its GitHub repository was edited.
+
+\blandscape
+
+```{r, child = child_docs_ls$three, echo=FALSE}
+```
+
+\elandscape

### 2023-04-19 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
first pass and updated bib

--- 2023-01-31 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
@@
 
-Based on published guidance on computational modelling in health economics and other disciplines as well as our own experience, we have identified 20 standards that we believe are important for implementing a MOSHEM that is accountable (seven standards), reusable (nine standards) and updatable (four standards).
-The standards are specified in Table \@ref(tab:timelygls) and are discussed below.
+We considered prior literature on modelling practice, our own professional experience and the needs of our project, to identify three core ethical responsibilities of CHEM developers, three attributes of CHEMs that enable fulfilment of these responsibilities and six criteria (two for each model attribute) for assessing ethical CHEM implementations.
+
+## Ethical responsibilities of CHEM developers 
+We believe that health economists have ethical responsibilities relating to the social acceptability, adequacy for purpose and beneficial impact of their computational models.
+
+Misalignment between the values of model developers and those of the population groups affected by decisions based on their models presents significant ethical risks [@thompson2022escape; @duckett2022journey].
+The value judgments of model developers influence the assumptions, selection of model features and standards for evidence that shape the CHEM development process [@HARVARD2020112975].
+These value judgments are rarely made explicit, omissions that may lead to socially unacceptable policy recommendations [@duckett2022journey].
+For example, to reduce the risk of inequitable policy implementation, it may be important for of a model to predict the benefits of harms of an intervention for different sub-populations [@10.3389/fpubh.2017.00068], but model developers may prefer to allocate a project budget to implementing other model features [@thompson2022escape].
+
+Health economists have duties both to take sufficient care that a CHEM is adequate for the explicit purpose for which it was developed and to provide potential third party users with the means of assessing its adequacy for their proposed purposes [@Erdemir2020; @Feenstra2022; @thompson2019escape; @10.3389/fpubh.2017.00068].
+However, it is common for CHEMs to have serious methodological flaws [@carletto_zanuzzi_sammarco_russo_2020; @WONDER2015467]; insufficient validation [@Ghabri2019; @kolovos2017model; @haji2013model], poor reproducibility [@Jalali2021; @McManus2019; @Bermejo2017]; and undeclared errors [@Radeva2020].
+
+Even an acceptable and adequate CHEM will have limited beneficial impact if it not much used, if it is mis-used or when its acceptability and adequacy rapidly decay.
+The scientific goals of generalisability (application without adaptation) and transferability (selective reuse and/or modification of model components) [@RN39] are advanced when models are appropriately reused in new contexts.
+Reuse of models as components of other models can also make model implementation more efficient [@Arnold2010; @garcia2021cost].
+
+Common barriers to model re-use include commercial and legal considerations [@Feenstra2022; @Pouwels2022], as well as challenges related to model transferability across jurisdictions [@garcia2021cost].
+The temporal window for valid application of CHEMs is often limited by implementation choices that rarely facilitate routine updates [@Sampson2017].
+Without ongoing maintenance, a model may become less reliable with time [@garcia2021cost], deterioration that model users may be unaware of, and has a growing risk of being deployed for purposes for which it is poorly suited [@calder2018computational].
+
+##	Criteria for assessing ethical CHEM implementation
+The acceptability, adequacy and public benefit responsibilities for CHEM developers are easier to state than to measure.
+It may therefore be pragmatic for assessment criteria for ethical modelling practice to instead be based on measurable attributes of the models themselves.
+As described in Table \@ref(tab:timelygls),  we believe that implementing CHEMs that are transparent, reusable and updatable (TRU) can enable modellers to meet their ethical obligations.
+We therefore selected these model attributes to use as the basis for deriving ethical assessment criteria.
 
@@
 
-### Standards for an accountable MOSHEM
-Guidance on transparency in health economic modelling published over ten years ago [@Eddy2012] made recommendations on documenting models but notably did not include recommendations on sharing model code and data.
-However, more recent and multidisciplinary healthcare modelling guidance [@Erdemir2020] recommends using existing digital repository services to these types of digital model artefacts.
-Some types of repository such as GitHub [@github2007] provide tools for disseminating work in progress code and providing highly transparent records of the complete development history and individual authorship contributions of a software project, while others such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each code and data collection.
+Transparency has been recommended as a core criterion for assessing ethical public health modelling practice [@10.3389/fpubh.2017.00068].
+Guidance on transparency in health economic modelling recommended that model code and data should be clearly documented, potentially with different versions for technical and non-technical users [@Eddy2012].
+Notably, the same guidelines, published over ten years ago, did not include recommendations on sharing model code and data.
+However, more recent guidance recommends publicly dissemination of healthcare model artefacts using online repository services [@Erdemir2020].
+Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each code and data collection.
+An essential component of quality assuring health economic models is verification - ensuring that calculations are correct and consistent with model specifications [@techver2019].
+The extensiveness of verification checks in models implemented as software projects can be reported using the concept of code coverage [@ERICWONG2010188] - the proportion of model code that has been explicitly tested.
+Tests should ideally combine both unit tests (to verify that small, isolated sections of code produce the correct output when run independently) and acceptance tests (to verify that the correct output is produced when multiple code components are run together to perform tasks that meet core user-requirements [@martin2003agile]).
+The nature and extent of individual model authorship contributions can become unclear when models are implemented over longer time-frames with a large and changing group of collaborators [@thompson2022escape].
+This issue can be addressed by use of online repository services such as GitHub [@github2007], that provide citation tools and can transparently record all individual code contributions to a modelling project over its lifecycle.
 
-Model code and data should be clearly documented, potentially with different versions for technical and non-technical users [@Eddy2012].
-Consistent use of meaningful naming conventions when authoring code is recommended [@Wilson_2017; @Alarid2019].
-Code can be made easier to follow by using the practices of abstraction [@8717448], where only simple, high level commands are routinely exposed to reviewers, and polymorphism [@7181447], where the same command (e.g.
-"simulate") can be reused to implement different algorithms of the same type.
-Programs to implement model analyses can be made comprehensible to even non-technical users through the use of literate programming techniques and tools like RMarkdown [@xie2018r] that integrate computer code with plain English descriptions.
+Assessment criteria for a transparent CHEM:
 
-An essential component of quality assuring health economic models is verification - ensuring that calculations are correct and consistent with model specifications [@techver2019].
-One useful concept for informing model users about the extensiveness of verification checks is code coverage [@ERICWONG2010188] - the proportion of model code that has been explicitly tested.
-<!-- In R, the testthat [@testthat2011] and covr [@covr2020] tools can be used in conjunction with GitHub to define tests and report coverage metrics.
--->Transcription errors - mistakes introduced when transferring data between sources, models and reports - are very common in health economic models [@Radeva2020].
-The risk of these errors might be lower if there was full transparency across all steps in a study workflow.
-Scientific computing tools now make it relatively straightforward to author programs that reproducibly execute all steps in data ingest, processing and reporting [@Wilson_2017].
+-	T1: All model code, non-confidential data and testing procedures and outcomes are available in open access repositories.
 
-Code and data should be distributed with tools that make it easy for potential users to appropriately cite each model artefact.
+-	T2: It is easy to see who developed and tested each part of the model and to identify the modelling team’s assumptions, judgments and theories about model development and use.
 
-### Standards for a reusable MOSHEM
-```{r echo = F}
-gpl_pc_dbl <- get_license_share("GPL")
-```
+Making a CHEM’s code, data and documentation publicly available is helpful but insufficient for promoting model re-use.
+The choices that CHEM developers make about model implementation and licensing will also shape who can use a model and for what purposes.
+Using open-source development platforms and licenses can aid both generalizability and transferability.
+Compared to using commercial modelling software, authoring CHEMs in an open-source language like R [@RCORE2022] makes it easier to store model algorithms and data in distinct files and locations (as opposed to hard coding - embedding data such as parameter values into source code) which facilitates selective modification of model components.
+This benefit can be further enhanced if model developers adopt a modular approach, in which a model is constructed from multiple reusable and replaceable sub-models (modules) [@pan2021modular].
+To grant permissions to others to use, test and adapt models and their components, health economists can avail of two broad categories of open source licensing options.
+Some guidance strongly recommends the use of permissive licensing [@Wilson_2017] that provides users with great flexibility as to the purposes (including commercial) for which content can be re-used.
+An alternative approach is to use copyleft licenses [@copyleft2022] that can require content users to distribute any derivative works they create under similar open-source arrangements.
 
-To make model code and data widely re-usable by others, it is important to provide users with appropriate and explicit permissions.
-In the context of open source models, there are two broad categories of licensing options.
-Some guidance strongly recommends the use of permissive licensing [@Wilson_2017] that provides users with great flexibility as to the purposes (including commercial) for which the content could be re-used.
-An alternative approach is to use copyleft licenses [@copyleft2022] that can require content users to distribute any derivative works they create under similar open source arrangements.
-For code, it may be appropriate to adopt the prevailing open source licensing practice within the programming language being used.
-For data, it may not be sufficient to simply choose between a permissive license like the Public Domain Dedication (CC0) [@cc02022] or a copyleft option such as the Attribution-Share Alike (CC-BY-SA) [@bysa2022].
-In addition to ensuring that data is ethically appropriate for disseminate in open access repositories, responsible custodianship of some de-identified or aggregated data may involve using or adapting template terms of use [@sampleterms2022] which have a number of ethical clauses (for example, prohibiting efforts to re-identify research participants).
+Assessment criteria for a reusable CHEM:
 
-Storing model code and data in separate files and locations (as opposed to hard coding - embedding data into source code) can make it easier to apply models to different decision contexts and to selectively restrict access to data that are confidential, while disseminating all other model artefacts.
-Clear distinctions should be made between model modules (code that defines abstract data structures and the algorithms that can be applied to data described by these structures), model datasets (digital information such as parameter values, unit records, etc) and model analyses (code that links model datasets to model modules and specifies the algorithms to apply to data associated with each module).
+-	R1: Model code and data are implemented to facilitate both generalizability and transferability.
 
-The software development practice of encapsulation [@8717448] can be used to help ensure that model modules continue to work as intended when they are combined [@ready4oop2022].
-In some cases, combining modules may mean new versions of modules have to be created to better account for interaction effects.
-The concept of inheritance [@8717448] can be used to write code that efficiently achieves this objective as well as to facilitate selective editing of modules when transferring models to different decision contexts [@ready4oop2022].
-Writing algorithms as collections of functions (short, self-contained and reusable software routines that each perform a discrete task) is recommended as good practice for scientific computing [@Wilson_2017].
-Functions to implement model algorithms can be associated with data structures (also known as a class) via a special type of function called a method.
-Model modules of a similar type or purpose can be efficiently distributed and documented by bundling them as code libraries.
-It is good practice to make available test or toy data to demonstrate the use of model algorithms [@Wilson_2017].
+-	R2: Terms of use allow anyone to reuse model code and non-confidential data, in whole or in part, without charge, and for purposes that include the creation of derivative works.
 
-Statistical models are a common output of health economic evaluations, but they are often not reported in a format that enables others to confidently and reliably re-use them for out of sample prediction [@Kearns2013].
-Open source approaches can help address this by disseminating code artefacts that enable easy and appropriate use of a statistical model to make predictions with new data.
-However, great care must be exercised when doing so if models are derived from data on human subjects as some software artefacts by default contain a copy of the source dataset.
-Such dataset copies must therefore be replaced (for example, with synthetic data) and the amended artefact's predictive performance then retested before any public release.
-Another way to make MOSHEMs easier to use is to develop simple user-interfaces for non-technical users.
+To remain valid for longer, models should be continually updated and refined as new evidence emerges and healthcare systems evolve [@Jenkins2021; @@garcia2021cost]].
+Ensuring that a model is regular reviewed to identify and implement required improvements is a receommended defence against model validity decay [@calder2018computational].
+Key enablers of sustainable maintenance of open source research software are committed, adequately resourced core development team and active user community [@info:doi/10.2196/20028].
+Currently, the core development team for a CHEM will be typically be funded to produce a project end-point deliverable whose specifications are well defined early in the project.
+For more complex and multi-purpose CHEMs, particularly those designed to be incorporated into decision support systems, it may be better for development teams to adopt Agile Software Development [@beck2001manifesto], an approach that has been recommended for complex public health software projects [@10.3389/fpubh.2022.899874].
+An Agile model will be less clearly specified in the initial project plan, but will instead continually develop in response to the requirements and feedback of users, who are provided with an initial, simplified working version of the model at the earliest feasible opportunity.
+Online communities can be an efficient means of engaging model users in testing each version of a model, identifying issues and suggesting improvements.
+Services such as GitHub [@github2007] provide collaborative code development tools [@MERGEL2015464] that help elicit, integrate and reconcile contributions from multiple contributors and to ensure each update is uniquely identifiable and retrievable.
+It is important that verification checks are rerun with each model update, a task that can be automated using the software development practice of Continuous Integration [@CI2017].
+The risk of model revisions having unintended consequences for third party users can be mitigated through the use of deprecation conventions [@zhou2016api] that take an informative and staged approach to retiring outdated model code and data.
 
-### Standards for an updatable MOSHEM
-To avoid MOSHEMs going stale - losing validity and usefulness with time - they should be routinely updated.
-Each update of code and data should be uniquely identifiable and retrievable, a goal that can be facilitated by use of version control tools [@Erdemir2020] such as [@git20XX].
+Assessment criteria for an updatable CHEM:
 
-Potential users of model code and data should be able to easily identify which version is most appropriate to their needs.
-Using semantic versioning [@semver20xx] conventions can signal the potential importance of an update to users of model code and data.
-Also informative is to clearly label the type of code hosted in a repository as either:
+-	U1: Resources and infrastructure are in place to support sustained development, testing, maintenance and version control of a model in collaboration with model users.
 
-- "development" (typically the most comprehensive and up to date source code, but potentially not yet sufficiently well documented and tested for potential users to apply to purposes other than testing);
-
-- "production" (code that has been released with a view to it being applied to its stated purposes and therefore typically required to meet defined documentation and testing standards); or
-
-- "archive" (permanent copies of code at key milestones in its development - potentially useful if seeking to use older versions of code to reproduce analyses).
-
-Continuous integration [@CI2017] tools can help verify that each code update passes multiple quality tests.
-Finally, using deprecation conventions that take an informative and staged approach to retiring old code and data reduces the risk that model revisions have unintended consequences on third party users.
+-	U2: Each new release of a model is retested, with changes implemented to minimize disruptions for existing model users.

### 2023-04-19 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
draft for selected co-author circulation
first pass and updated bib

@@
 
-We developed a toolkit to help us develop and use MOSHEM modules, datasets and analyses that meet the standards listed in Table \@ref(tab:timelygls).
-The toolkit is comprised of online repositories and software.
+To support the collaborative development of CHEMs that meet TRU assessment criteria, we have created a prototype software framework called ready4.
+We have designed this framework as a lightweight extension to existing software development infrastructure that could be used to implement CHEMs that are both open-source (for transparency and reusability) and modular (for reusability and updatability).
 
-## Repositories <!-- Existing ref -->
-We created a GitHub organisation (a collection of code repositories) where all our development code is stored and version controlled [@ready4gh2022].
-We configured the repositories in our GitHub organisation to use GitHub actions to support continuous integration.
-Some of the continuous integration checks we have defined assess each library's compliance with policies specified by the Comprehensive R Archive Network (CRAN) [@CRAN2022], to which we plan submitting future production releases.
-To track our code coverage, we linked our GitHub organisation to an account we established at codecov [@codecov_2022].
+## 	Framework libraries 
+To work within the popular open-source programming environment R [@RCORE2022], the ready4 software framework is implemented as six development version R code libraries.
+The R libraries collectively provide model developers with tools to combine R's functional and object-oriented programming paradigms [@10.1214/13-STS452] in authoring CHEMs, supplying those CHEMs with data and using CHEMs to implement reproducible modelling analyses.
+The six novel libraries and the preexisting third-party R libraries they depend on are summarised in Table \@ref(tab:cpkgs).
 
-We enabled GitHub Pages in each repository we used for code library development to facilitate the creation and hosting of library documentation websites.
-We also developed a consolidated and versioned project documentation website [@rfwn2022] using the Hugo framework [@hugo_2023] and Docsy theme [@docsy_2023].
-To host that website we established an account with Netlify [@netlify_2023] and linked that service to our GitHub organisation so that the website would automatically update whenever the source code in its GitHub repository was edited.
+Standardization and interoperability are core requirements of implementing a modular approach.
+Model modules need to be able to share inputs and outputs with each other and to be run as independent models [@barros2023empowering].
+Each CHEM module authored with the ready4 framework will include both a data structure (specifying the required properties of data that can validly be supplied to a module) and a set of algorithms (specifying the operations that can be performed on data contained in a module instance).
+The foundational framework library, called ready4, defines a template module data structure (using R’s S4 class system) from which all CHEM module data structures will be created and a novel syntax that enable module algorithms to be consistently named.
+The ready4 library also contains tools for retrieving web based information on model modules, datasets and analysis programs authored with the framework and for partially automating updates to a project documentation website.
 
-We also created a Zenodo community [@ready4zen2022] - a collection of permanent, uniquely identified repositories.
-We then linked our Zenodo community and GitHub organisation so that every time we specify a version of code in one of our GitHub repositories as a "release", a copy of that code is automatically created on Zenodo with a DOI.
-Finally, to manage model datasets, we created a dedicated collection within the Harvard Dataverse installation [@ready4dv2022].
+Three R libraries are designed to help standardize workflows for authoring, documenting, testing and disseminating new model modules.
+The ready4pack library is designed to integrate with GitHub and provides tools for authoring model modules and desseminating them as themed bundles in R libraries libraries that are:
 
-## Software <!-- Novel ref -->
-We created six development version R libraries to help us author model modules, supply those modules with data and implement reproducible modelling analyses.
-The six libraries, their primary focus, the standards they support and the third-party packages they depend on are summarised in Table \@ref(tab:cpkgs).
+-	documented (with a website, a PDF manual itemising selected contents and a PDF manual itemising all contents);
 
-A library called ready4 [@ready42022] defines a template module (using R's S4 class system) from which all model module data structures will inherit features and a novel syntax for attaching algorithms to those data structures.
-The ready4 library also contains tools for retrieving web based information on model modules, datasets and analysis programs and for partially automating updates to the project documentation website.
-
-Three R libraries are designed to standardise and partially automate workflows for authoring new model modules.
-The ready4pack library [@ready4pack2022] is designed to integrate with our GitHub organisation and provides tools for authoring module libraries that are:
-
-- documented (with a website, a manual itemising selected contents and a manual itemising all contents);
-
-- licensed (using GNU GPL-3 [@GNUGPL2022] by default);
+-	licensed (using the copyleft GNU GPL-3 [66] by default);
 
@@
 
-- quality assured (each update triggers continuous integration workflows, including any unit tests created by module library authors).
+-	quality assured (each update triggers continuous integration workflows, including any acceptance and unit tests created by module library authors).
 
 The ready4pack library depends on two other module authoring libraries.
-Methods from the ready4fun library [@ready4fun2022] are used to verify that functions for implementing module algorithms are written in a consistent house style.
-That standardised format is then used by ready4fun methods to automatically generate basic documentation for each function.
-Methods from the ready4class [@ready4class2022] library are used to streamline and standardise the authoring of module data structures and the linking of methods to these data structures.
-Like ready4fun, the ready4class library uses standardised code implementation to automatically generate basic documentation for each module data structure.
+Writing model algorithms as collections of functions (short, self-contained and reusable software routines that each perform a discrete task), has been recommended as good practice for scientific computing [@Wilson_2017].
+The ready4fun library contains tools for authoring functions in a consistent house style that automatically generates basic documentation for each function.
+Functions to implement model algorithms can be associated with a module via a special type of function called a method.
+Tools from the ready4class library can help streamline and standardise the authoring of module data structures and their associated methods and to automatically generate basic documentation for each module.
 
-The ready4use library  [@ready4use2022] contains modules for ingesting model datasets from online repositories (hosted on a Dataverse installation or on GitHub), labelling model datasets and sharing model datasets via online repositories.
-The ready4show library [@ready4show2022] contains tools to help author analyses programs that are either self-documenting or which trigger the creation of a scientific summary.
-
-When used in conjunction with toolkit repositories, the six R libraries provide support for implementing 17 out of 20 framework standards (Table \@ref(tab:timelygls)).
-Standards relating to safe dissemination of statistical models (R8), user-interface development (R9) and deprecation conventions (U4) are better met through using existing third party R libraries.
-Preparing statistical models for dissemination can be accomplished with standard R data management tools like the dplyr [@dplyr2022] and purrr [@dplyr2022] libraries.
-User-interfaces are typically developed with the shiny [@shiny2022] library, for which a tutorial aimed at health economists is available [@SmithR2020].
-The library lifeycle [@lifecycle2021] provides tools for R developers to consistently deprecate their code.
+The ready4use library contains tools for supplying model modules with data stored in online repositories (hosted on a Dataverse installation or on GitHub), labelling these datasets and then sharing them via online repositories.
+The ready4show library contains tools to help author R Markdown programs that combine model modules and datasets to undertake analyses.
+These programs are either self-documenting (code is easy to understand and integrated with plain English explanations of what it does) or trigger the creation of separate documents (e.g.
+a scientific manuscript).
 
@@
 
-\blandscape
+##	Framework integration with online services 
+Our software framework needs to be used in conjunction with a number of online services.
+To facilitate its application to our youth mental health project, we established and configured accounts with these required services (see Availability of data and materials).
 
-```{r, child = child_docs_ls$three, echo=FALSE}
-```
-
-\elandscape
+We created a GitHub organisation (a collection of code repositories) where all code (libraries, programs and sub-routines) that we author with the framework is stored and version controlled.
+We configured individual repositories in our GitHub organisation that are used for code library projects to use GitHub actions to implement continuous integration.
+By default, code libraries authored with our framework will use continuous integration to assess compliance with policies specified by the Comprehensive R Archive Network (CRAN) [@CRAN2022].
+To track our code coverage, we linked our GitHub organisation to an account we established at codecov [@codecov_2022].
+To facilitate the creation and hosting of documentation websites, we enabled GitHub Pages in each repository we used for code library development.
+We also created a Zenodo community - a collection of permanent, uniquely identified repositories.
+We then linked our Zenodo community and GitHub organisation so that every time we specify a version of code in one of our GitHub repositories as a “release”, a copy of that code is automatically created on Zenodo with a DOI.
+Finally, to manage model datasets, we created a dedicated collection within the Harvard Dataverse installation.

### 2023-04-19 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
first pass and updated bib

--- 2023-01-30 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
@@
 <!-- `r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`  -->
-Computational models, particularly those addressing economic topics, have become essential tools for health policy development [@dakin2015influence; @Erdemir2020].
-Although influential and widely used, health economic models typically have a number of limitations that at best restrict their usefulness and which in some cases may facilitate harmful misuse.
 
-There is a strong case for making health economists more accountable for the appropriate use and social acceptability of their models.
-Users of models should be able to assess their adequacy for a particular purpose [@thompson2019escape].
-This goal is difficult to achieve in the current context of the poor reproducibility [@Jalali2021; @McManus2019; @Bermejo2017] and frequently insufficient validation [@Ghabri2019] of health economic models.
-Many health economic models are released with undeclared errors [@Radeva2020].
-The value judgments that strongly shape health economic analyses are rarely made explicit, omissions that may lead to socially unacceptable policy recommendations [@duckett2022journey].
-A modelling team's value judgments about what questions to address, the most important features of a system to represent and the weighting of different types of evidence may be poorly aligned with those of the people impacted by decisions informed by model analyses [@thompson2022escape].
-As health economic models adopt more sophisticated techniques, the need for accountability grows.
-More complex models may be more prone to propagation errors [@Saltelli2019] and models designed to address multiple questions should be expected to meet more onerous verification and validation obligations [@Eddy2012; @Feenstra2022].
-The nature and extent of individual model authorship contributions may be less clear in models implemented over longer time-frames with a large and changing group of collaborators [@thompson2022escape].
+Health economics is a discipline concerned with problems that arise due to scarce resources, such as how to value health and healthcare, allocate healthcare budgets and configure health services [@wagstaff2012four].
+In seeking to solve these problems, health economists typically use models which are simplified and selective representations of systems that are believed to influence human health.
+These representations can be described in words and pictures (a conceptual model), in equations (a mathematical model) or in computer code (a computational model).
+The predictions reported in health economic studies are typically generated by the execution of a computer program which applies a computational model to compatible data inputs (e.g., parameter values) and performs a sequence of numeric calculations.
 
-The resource and skills intensive undertaking of modelling could be made more tractable if it was easier for health economists to re-use each other's models [@Arnold2010].
-However, as many health economic models are owned by pharmaceutical companies and consultancies, commercial considerations can limit the reuse of models and their constituent code and data [@Feenstra2022].
-Legal and ethical issues such as privacy and confidentiality requirements further limit public release of some model artefacts [@Pouwels2022].
-Transferring a health economic model developed for one jurisdiction for application in another typically involves retaining some features and updating others [@barbieri2010international].
-However, models do not always make implementation choices (for example, use of concepts with standardised meanings across jurisdictions<!-- [@garcia2021cost] -->, supplying context specific data as replaceable data-packs and distributing source code under licenses that allow derivative works) that facilitate model transferability.
+Computational models are now widely used to inform health policy and system design [@dakin2015influence; @Erdemir2020; @LO2022100570; @Christene006827].
+This level of influence has concomitant ethical responsibilities for model developers that are often poorly understood and inadequately fulfilled [@10.3389/fpubh.2017.00068; @pliakos2021ethics; @thompson2022escape; @calder2018computational].
 
-Health economic models should be updated and refined as new evidence emerges and decision contexts change [@Jenkins2021], but this occurs infrequently [@Sampson2017].
-Funding for health economic modelling projects rarely extend to provision of medium term support for model updates and improvements.
-The career trajectories of health economists can also mitigate against adequate maintenance of a model, it being relatively common for model authors to have moved on from the team that owns the model and / or from working on the health condition for which the model was developed.
+Computational health economic models (CHEMs) can be implemented using specialized commercial software or authored as bespoke software projects in a programming language.
+Advantage of commercial modelling tools are simplicity and ease of use, but a software development approach facilitates development of models that may be more realistic, transparent, reusable and adaptable [@incerti2019r].
+For CHEMs that are implemented as software projects, a major early decision is selection of an appropriate software framework.
+A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users [@myllarniemi2018development].
+Advantages of using software frameworks include facilitating code reuse and extension, promoting good programming practice and the capability to provide enhanced functionality and performance without additional effort by developers [@edwin2014software].
+However, software frameworks can be challenging and time consuming to create [@edwin2014software] and then difficult for others to learn, often requiring developers to undergo specialist training [@myllarniemi2018development].
+There is also a risk that a software framework may become excessively complex over time [@edwin2014software].
 
-A potential strategy for improving model accountability, reusability and updatability is to make models both modular and open-source.
-
-A modular model is constructed from multiple reusable and replaceable sub-models (modules) [@pan2021modular].
-Modules can share inputs and outputs with other modules or can be run as independent models [@barros2023empowering].
-Advantages of modular models include feasibility (large projects are broken into smaller tasks, with each component independently developed and tested) and flexibility (making it easier to selectively replace or update specific parts of a model and to scale up or down the level of granularity) [@pan2021modular].
-Modular approaches are currently being used to facilitate the development of complex computational models in disciplines such as biology [@pan2021modular], neuroscience [@frazier2022robust] and ecology [@barros2023empowering].
-In health economics the related and enabling concept of reference models has been recommended [@Afzali2013], but peer reviewed studies describing modular health economic models remain relatively rare, though examples exist in infectious disease [@Trauer2017] and cardiology [@Urach2013].
-
-Modular models provide an opportunity for multiple modelling teams to contribute to, test and reuse models.
-To enhance this capacity, modular models may be implemented as open source projects that give others liberal permissions to access and use model source code and data [@pan2021modular; @barros2023empowering; @frazier2022robust].
-Although there appears to be in principle support from many health economists for greater use of open source health economic models (OSHEMs)  [@Pouwels2022], actual implementations are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022].
-Barriers to adoption of OSHEMs include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations [@Pouwels2022; @Wu2019].
-Adherence to good practice guidance is an essential requirement for healthcare modelling [@Erdemir2020], but guidelines for implementing OSHEMs remain scarce, piecemeal and need improving [@Sampson2019].
-
-Our interest in modular and open source source approaches developed when we began seeking am appropriate framework for undertaking and validly synthesising diverse types of economic research in mental health.
-Mental disorders impose high health, social and economic burdens worldwide [@RN8;@GBD2019].
-Much of this burden is potentially avertable [@RN25], but poorly financed and organised mental health systems are ill-equipped for this challenge [@RN22;@RN23].
-A substantial economic literature already exists to assess the affordability and value for money of mental health interventions [@RN34].
-This economic evaluation work is an essential prerequisite for improving allocative efficiency in mental health, but could be of greater value to systems planners if integrated with a broader program of economic research.
-
-We are developing ready4 (https://www.ready4-dev.com), a modular OSHEM (MOSHEM) on the mental health of young people aged 12 to 25.
-We are initially applying ready4 to four of the twelve domains of health economics identified by Wagstaff and Culyer [@wagstaff2012four]:
-<!-- There is therefore an opportunity for health economists to undertake mental health research of significant potential public benefit. -->
-
-- *health and its value* (our projects: utility mapping models);
-
-- *determinants of health and ill-health* (our projects: models for creating rich and representative synthetic household populations from survey data);
-
-- *demand for health and health care* (our projects: spatial epidemiology and help-seeking choice models); and
-
-- *supply of health services* (our projects: a model of primary mental health care services).
-
-Once these projects are completed, our aim is to flexibly combine these models to answer questions in two additional Wagstaff and Culyer domains:
-
-- *efficiency and equity* (our goal: assess the distributional impacts and identify the optimal targeting of care provision); and
-
-- *economic evaluation* (our goal: assess the cost-utility of competing policy options).
-
-To undertake this work we first needed to develop a framework for standardisation.
-Standardisation is an essential enabler of automation, collaboration, interoperability and transferability in modular and open source approaches.
-However, we are not aware of any appropriate single source of guidance about what standards should be specified for MOSHEMs.
-To be deployed in computational models, the standards specified for ready4 will need to be implemented by software, some of which will need to be developed for this specific purpose.
-
-<!-- When planning how to undertake and synthesise this program of work, we became concerned with issues relating to accountability, reusability and updatability.
-If mistakes are common in individual health economic modelling projects [@Radeva2020], then combining multiple projects may be particularly error prone.
-The risk of errors may also depend on whether a model is too simple or too complex [@Saltelli2019], so the level of granularity appropriate for one model application may be ill-suited to another.
-Undertaking a multiannual program of interdependent work raises the risk that models developed in the first phase of a project may need to be updated by the time the project is approaching conclusion.
--->
-
-<!-- These concerns led us to seek the MOSHEM approach that provides the transparency to make it easier for errors to be uncovered, the adaptability to fix these errors and the flexibility to facilitate interchangeability between representations of different levels of granularity.
--->
+We are developing a model to explore multiple economic questions relating to the mental health of young people aged 12 to 25.
+When making choices about how to implement this model computationally, we wished to facilitate ethical development and use.
+However, we are not aware of any software framework for implementing CHEMs that adhere to explicitly stated ethical requirements.

### 2023-04-19 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
first pass and updated bib

--- 2023-01-23 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
@@
 
-# Guidelines for OSHEMs
+## Ethical requirements and assessment criteria
 ```{r child="../Child_RMDs/MS_Imp_Guidelines.Rmd", echo=FALSE}
@@
 
-# Modelling Toolkit
+## Software framework
 ```{r child="../Child_RMDs/MS_Imp_Toolkit.Rmd", echo=FALSE}

### 2023-04-19 setup.R

@@ -5,15 +5,15 @@ library(bookdown)
 library(rticles)
 X <- Ready4showSynopsis(#background_1L_chr = "Our study is entirely fictional.",
                         coi_1L_chr = "None declared.",
-                        #conclusion_1L_chr = "We have identified a number of standards that we believe are appropriate to implementing quality OSHEMs in youth mental health. Most of these standards are probably relevant to OSHEMs in other health conditions, though some such as the copyleft licensing may be less relevant to modellers using different tools. Our framework toolkits can help support standardised approaches to dynamic systems model development that are important for collaborative and interdependent projects. ",
+                        #conclusion_1L_chr = "We have identified criteria that can be used to systematically assess extent to which the computational implementation of health economic models adheres to the ethical goals of transparency, reusability and updatability. We have developed an open-source software framework that can support the ethical computational implementation of economic models in youth mental health. Our framework can be used as a prototype for developing future software frameworks to support ethical implementation of CHEMs.",
                         digits_int = 3L,
-                        ethics_1L_chr = "Framework development did not involve human subject research and was not ethically reviewed. The utility mapping worked example is a previously reported study that was reviewed and granted approval by the University of Melbourne’s Human Research Ethics Committee, and the local Human Ethics and Advisory Group (1645367.1).",
-                        funding_1L_chr = "Framework development was funded by Orygen, VicHealth and Victoria University. The utility mapping study used as a worked example was funded by the National Health and Medical Research Council (NHMRC, APP1076940), Orygen and headspace.",
+                        ethics_1L_chr = "Software framework development did not involve human subject research and was not ethically reviewed. The utility mapping worked example is a previously reported study that was reviewed and granted approval by the University of Melbourne’s Human Research Ethics Committee, and the local Human Ethics and Advisory Group (1645367.1).",
+                        funding_1L_chr = "Software framework development was funded by Orygen, VicHealth, Victoria University and an Australian Government Research Training Program (RTP) Scholarship . The utility mapping study used as a worked example was funded by the National Health and Medical Research Council (NHMRC, APP1076940), Orygen and headspace.",
                         #interval_chr = "three months",
                         keywords_chr = c("open source models","health economics","mental disorders"),
                         outp_formats_chr = "PDF",
                         #sample_desc_1L_chr = "The study sample is fake data that pretends to be young people aged 12 to 25 years who attended Australian primary care services for mental health related needs between November 2019 to August 2020.",
[…]

### 2023-07-27 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
reworked abstract

@@
 
-To remain valid for longer, models should be continually updated and refined as new evidence emerges and healthcare systems evolve [@Jenkins2021; @@garcia2021cost]].
+To remain valid for longer, models should be continually updated and refined as new evidence emerges and healthcare systems evolve [@Jenkins2021; @@garcia2021cost].
 Ensuring that a model is regular reviewed to identify and implement required improvements is a receommended defence against model validity decay [@calder2018computational].

### 2023-07-27 setup.R

@@ -13,7 +13,7 @@ X <- Ready4showSynopsis(#background_1L_chr = "Our study is entirely fictional.",
                         keywords_chr = c("open source models","health economics","mental disorders"),
                         outp_formats_chr = "PDF",
                         #sample_desc_1L_chr = "The study sample is fake data that pretends to be young people aged 12 to 25 years who attended Australian primary care services for mental health related needs between November 2019 to August 2020.",
-                        title_1L_chr = "A prototype software framework for ethical implementation of computational economic models and its early application in youth mental health")
+                        title_1L_chr = "A prototype software framework for transparent, reusable and updatable health economic models")
 X <- renewSlot(X,
                "authors_r3", 
                {
@@ -37,13 +37,15 @@ X <- renewSlot(X,
                "abstract_args_ls",
                {
                  args_ls <- X@abstract_args_ls
-                 args_ls$abstract_ls <- list(Summary = "Understanding of what constitutes ethical computational implementation of health economic models is underdeveloped and software frameworks to facilitate such implementations are required. 
-                                             We propose criteria for assessing the ethical implementation of computational health economic models (CHEMs), describe a novel prototype software framework for developing CHEMs that meet these criteria and outline how we are using this software framework to develop and synthesise multiple economic models in youth mental health. 
-                                             We propose a total of six assessment criteria – two each for enabling transparent, reusable and updatable (TRU) CHEMs. 
-                                             The software framework is comprised of six R libraries that provide a toolkit for authoring CHEMs, supplying CHEMs with data and using CHEMs to implementing reproducible modelling analyses. 
-                                             The framework libraries integrate with existing online services for collaborative software development and data archiving. One of the initial applications of the software framework was to develop and apply utility mapping models in youth mental health. 
-                                             We assess the utility mapping CHEM as wholly meeting four of our ethical assessment criteria and partially meeting the remaining two criteria. 
-                                             We discuss how the ethical assessment criteria we have identified and the software framework we have developed can inform future work to develop understanding and implementation of ethical computational modelling practice in health economics.",
+                 args_ls$abstract_ls <- list(Summary = "Computers are tools that are now essential to the work of health economists. 
+                                             However, the ethical dimensions of alternative approaches to the computational implementation of health economic models are poorly understood. 
+                                             There is a corresponding need for technical infrastructure that can better facilitate implementations of computational health economic models (CHEMs) that meet explicit ethical standards. 
[…]

### 2023-08-01 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
working my way through supervisors comments

--- 2023-01-31 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
@@
 In this paper, we describe:
-
-(i) a framework that specifies MOSHEM standards and provides the tools to implement them; and
-
-(ii) the application of that framework to develop and use an initial set of ready4 modules in a utility mapping study.
+(i)	criteria for assessing ethical CHEM implementations;
+(ii) a prototype software framework for the ethical implementation of CHEMs; and
+(iii)	use of the software framework to develop a computational economic model in youth mental health, with an initial focus on outcome valuation.

### 2023-08-01 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
working my way through supervisors comments

@@
 
+<!-- Talk about DARTH (https://doi.org/10.1007/s40273-019-00837-x )/ BCEA -->
 Ethical practice is a core expectation of health researchers and computational methods underpin most quantitive research, yet an understanding of what constitutes ethical computational modelling practice in health is underdeveloped [@10.3389/fpubh.2017.00068].
@@
 Currently, many if not most existing CHEMs are insufficiently transparent [@Jalali2021; @McManus2019; @Bermejo2017; @Ghabri2019], reusable [@Feenstra2022; @Emerson2019] and updatable [@Sampson2017; @10.3389/fpubh.2022.899874]].
-There appears to be in-principle support from health economists to address these practice shortfalls through greater use of for open-source approaches [@Pouwels2022] that are currently rarely implemented [@Feenstra2022; @Emerson2019].
-Existing incentive structures for health economists generally do not promote facilitating peers to reuse their work.
+<!-- DELETION --> Existing incentive structures for health economists generally do not promote facilitating peers to reuse their work.
 Currently, it takes “an extraordinary amount of idealism” to dedicate the substantial time and resources required to author, test, document and maintain even fragile prototype research software that could instead be used to write scientific manuscripts [@anzt2020environment].

### 2023-08-01 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
working my way through supervisors comments

@@
 
-We considered prior literature on modelling practice, our own professional experience and the needs of our project, to identify three core ethical responsibilities of CHEM developers, three attributes of CHEMs that enable fulfilment of these responsibilities and six criteria (two for each model attribute) for assessing ethical CHEM implementations.
+We considered prior literature on modelling practice, our own professional experience and the needs of our youth mental health modelling project, to identify core ethical responsibilities of CHEM developers, attributes of CHEMs that support fulfilment of these responsibilities and criteria against which these attributes can be assessed.
 
 ## Ethical responsibilities of CHEM developers 
-We believe that health economists have ethical responsibilities relating to the social acceptability, adequacy for purpose and beneficial impact of their computational models.
+Health economists have ethical responsibilities relating to the social acceptability, adequacy for purpose and beneficial impact of CHEMs.
 
 Misalignment between the values of model developers and those of the population groups affected by decisions based on their models presents significant ethical risks [@thompson2022escape; @duckett2022journey].
-The value judgments of model developers influence the assumptions, selection of model features and standards for evidence that shape the CHEM development process [@HARVARD2020112975].
+The value judgments of model developers influence the assumptions, selection of model features and standards for evidence that shape the model development process [@HARVARD2020112975].
 These value judgments are rarely made explicit, omissions that may lead to socially unacceptable policy recommendations [@duckett2022journey].
-For example, to reduce the risk of inequitable policy implementation, it may be important for of a model to predict the benefits of harms of an intervention for different sub-populations [@10.3389/fpubh.2017.00068], but model developers may prefer to allocate a project budget to implementing other model features [@thompson2022escape].
+Key choices about the computational implementation of health economic models depend on these value judgments (see Table \@ref(tab:proscons)) and these choices in turn influence the extent to which model implementations are readily adaptable by third parties with alternative value judgments.
+<!-- For example, to reduce the risk of inequitable policy implementation, it may be important for of a model to predict the benefits of harms of an intervention for different sub-populations [@10.3389/fpubh.2017.00068], but model developers may prefer to allocate a project budget to implementing other model features [@thompson2022escape].
+-->
 
-Health economists have duties both to take sufficient care that a CHEM is adequate for the explicit purpose for which it was developed and to provide potential third party users with the means of assessing its adequacy for their proposed purposes [@Erdemir2020; @Feenstra2022; @thompson2019escape; @10.3389/fpubh.2017.00068].
-However, it is common for CHEMs to have serious methodological flaws [@carletto_zanuzzi_sammarco_russo_2020; @WONDER2015467]; insufficient validation [@Ghabri2019; @kolovos2017model; @haji2013model], poor reproducibility [@Jalali2021; @McManus2019; @Bermejo2017]; and undeclared errors [@Radeva2020].
+Model developers have duties both to take sufficient care that a model is adequate for the explicit purpose for which it was developed and to provide potential third party users with the means of assessing its adequacy for their proposed purposes [@Erdemir2020; @Feenstra2022; @thompson2019escape; @10.3389/fpubh.2017.00068].
+It is common for health economic models to have serious methodological flaws [@carletto_zanuzzi_sammarco_russo_2020; @WONDER2015467]; insufficient validation [@Ghabri2019; @kolovos2017model; @haji2013model], poor reproducibility [@Jalali2021; @McManus2019; @Bermejo2017]; and undeclared errors [@Radeva2020].
+Appropriate computational implementation choices can help address many of these shortcomings, for example by automating quality assurance checks and facilitating manual reviews by third parties.
 
-Even an acceptable and adequate CHEM will have limited beneficial impact if it not much used, if it is mis-used or when its acceptability and adequacy rapidly decay.
+A health economic model will have limited public benefit if it not much used, if it is mis-used or when its acceptability and adequacy rapidly decay.
 The scientific goals of generalisability (application without adaptation) and transferability (selective reuse and/or modification of model components) [@RN39] are advanced when models are appropriately reused in new contexts.
-Reuse of models as components of other models can also make model implementation more efficient [@Arnold2010; @garcia2021cost].
+Reuse of models as components of other models can also make model implementation more efficient [@Arnold2010; @garcia2021cost] but the reusability of models is significantly shaped by computational implementation choices such as how model code and data are authored, documented, licensed and disseminated.
+Currently, health economic models are rarely implemented computationally in a manner that facilitates routine updates [@Sampson2017], thus limiting the temporal window within which a CHEM can be validly applied.
+Without ongoing maintenance, a CHEM risks becoming less reliable with time [@garcia2021cost] and is at risk of being deployed for purposes for which it is poorly suited [@calder2018computational].
+<!-- Common barriers to model re-use include commercial and legal considerations [@Feenstra2022; @Pouwels2022], as well as challenges related to model transferability across jurisdictions [@garcia2021cost].
+-->
 
-Common barriers to model re-use include commercial and legal considerations [@Feenstra2022; @Pouwels2022], as well as challenges related to model transferability across jurisdictions [@garcia2021cost].
-The temporal window for valid application of CHEMs is often limited by implementation choices that rarely facilitate routine updates [@Sampson2017].
-Without ongoing maintenance, a model may become less reliable with time [@garcia2021cost], deterioration that model users may be unaware of, and has a growing risk of being deployed for purposes for which it is poorly suited [@calder2018computational].
-
-##	Criteria for assessing ethical CHEM implementation
-The acceptability, adequacy and public benefit responsibilities for CHEM developers are easier to state than to measure.
-It may therefore be pragmatic for assessment criteria for ethical modelling practice to instead be based on measurable attributes of the models themselves.
+##	Sssessing ethical CHEM implementations
+The acceptability, adequacy and public benefit responsibilities of health economic modellers are easier to state than to measure.
+We have therefore focused our assessment criteria for ethical modelling practice on measurable attributes of computational model implementations.
 As described in Table \@ref(tab:timelygls),  we believe that implementing CHEMs that are transparent, reusable and updatable (TRU) can enable modellers to meet their ethical obligations.
@@
 
-```{r, child = child_docs_ls$one, echo=FALSE}
+```{r, child = child_docs_ls$two, echo=FALSE}
 ```
 
-Transparency has been recommended as a core criterion for assessing ethical public health modelling practice [@10.3389/fpubh.2017.00068].
+**Transparency** has been recommended as a core criterion for assessing ethical public health modelling practice [@10.3389/fpubh.2017.00068].
 Guidance on transparency in health economic modelling recommended that model code and data should be clearly documented, potentially with different versions for technical and non-technical users [@Eddy2012].
@@
 
-Assessment criteria for a transparent CHEM:
+The **transparency** of a CHEM implementation can be assessed against the criteria:
 
@@
 
--	T2: It is easy to see who developed and tested each part of the model and to identify the modelling team’s assumptions, judgments and theories about model development and use.
+-	T2: It is easy to see who developed and tested each part of the CHEM and to identify the modelling team’s assumptions, judgments and theories about CHEM development and use.
 
-Making a CHEM’s code, data and documentation publicly available is helpful but insufficient for promoting model re-use.
-The choices that CHEM developers make about model implementation and licensing will also shape who can use a model and for what purposes.
-Using open-source development platforms and licenses can aid both generalizability and transferability.
-Compared to using commercial modelling software, authoring CHEMs in an open-source language like R [@RCORE2022] makes it easier to store model algorithms and data in distinct files and locations (as opposed to hard coding - embedding data such as parameter values into source code) which facilitates selective modification of model components.
+Model **reusability** is the second attribute that we identified as being core to ethical CHEM implementations.
+Making a CHEM’s code, data and documentation publicly available is now considered “gold-standard” practice but is not sufficient to promote model re-use.
+Computational implementations that store model algorithms and data in distinct files and locations (as opposed to embedding data such as parameter values into source code) facilitate selective modification of model components.
+Writing model algorithms as collections of functions (short, self-contained and reusable software routines that each perform a discrete task), has been recommended as good practice for scientific computing [@Wilson_2017] and can facilitate model generalisability.
+The concept of inheritance [@8717448], a feature of object-oriented programming, facilitates selective editing of algorithms when transferring models to different decision contexts [@ready4oop2022].
 This benefit can be further enhanced if model developers adopt a modular approach, in which a model is constructed from multiple reusable and replaceable sub-models (modules) [@pan2021modular].
@@
 An alternative approach is to use copyleft licenses [@copyleft2022] that can require content users to distribute any derivative works they create under similar open-source arrangements.
-
-Assessment criteria for a reusable CHEM:
+<!-- Compared to using commercial modelling software, authoring CHEMs in an open-source language like R [@RCORE2022] makes it easier to -->
+<!-- Using open-source development platforms and licenses can aid both generalizability and transferability. -->
+<!-- The choices that CHEM developers make about model implementation and licensing will also shape who can use a model and for what purposes.  -->
+The **reusability** of a CHEM implementation can be assessed against the criteria:
 

### 2023-08-01 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
working my way through supervisors comments

@@
 The ready4pack library depends on two other module authoring libraries.
-Writing model algorithms as collections of functions (short, self-contained and reusable software routines that each perform a discrete task), has been recommended as good practice for scientific computing [@Wilson_2017].
-The ready4fun library contains tools for authoring functions in a consistent house style that automatically generates basic documentation for each function.
+<!-- MOVED CONTENT -->The ready4fun library contains tools for authoring functions in a consistent house style that automatically generates basic documentation for each function.
 Functions to implement model algorithms can be associated with a module via a special type of function called a method.

### 2023-08-01 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
working my way through supervisors comments

@@
 In seeking to solve these problems, health economists typically use models which are simplified and selective representations of systems that are believed to influence human health.
-These representations can be described in words and pictures (a conceptual model), in equations (a mathematical model) or in computer code (a computational model).
-The predictions reported in health economic studies are typically generated by the execution of a computer program which applies a computational model to compatible data inputs (e.g., parameter values) and performs a sequence of numeric calculations.
+A health economic model should be capable of being described using three isomorphic representational approaches - words and figures (a conceptual model), equations (a mathematical model) and computer code (a computational model).
+Health economic scientific manuscripts typically focus on describing conceptual and mathematical model representations.
+However, the predictions reported in health economic studies are now almost always generated by the execution of a computer program that applies a computational model to compatible data inputs (e.g., parameter values) and performs a sequence of numeric calculations.
+Although health economists report strong interest in making the computational implementation of their models more transparent and accessible [@Pouwels2022], open-source model implementations remain rare [@Feenstra2022; @Emerson2019].
 
+Computational health economic models (CHEMs) can be implemented using specialized commercial software or authored as software development projects in a programming language such as Python [@python2009] or R [@RCORE202].
+Advantages of commercial modelling tools are simplicity and ease of use, but a software development approach may facilitate development of computational models that are more realistic, transparent, reusable and adaptable [@incerti2019r].
+Which approach is most appropriate for a health economic modelling project to adopt may depend on both modelling team value judgments and the resource and time constraints within which projects need to be implemented (see Table \@ref(tab:proscons)).
+
+```{r, child = child_docs_ls$one, echo=FALSE}
+```
+<!-- on considerations such as model comprehensiveness, generalisability, reproducibility and transferability -->
+For CHEMs that are implemented as software development projects, a major early decision is the selection of an appropriate software framework.
+A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users [@myllarniemi2018development].
+A software framework provides a foundation for developing software applications with shared resources, e.g., algorithms and data files, that can be modified to suit specific needs.
+Software frameworks have widely been developed and implemented in computer science, for example, PyTorch [@PyTorch2019] for machine learning using Python.
+
+Advantages of using software frameworks include facilitating code reuse and extension, promoting good programming practice and the capability to provide enhanced functionality and performance without additional effort by developers [@edwin2014software].
+However, software frameworks can be challenging and time consuming to create [@edwin2014software] and then difficult for others to learn, often requiring model developers to undergo specialist training [@myllarniemi2018development].
+There is also a risk that a software framework may become excessively complex over time [@edwin2014software].
+
+<!-- We are developing a model to explore multiple economic questions relating to the mental health of young people aged 12 to 25.   -->
+<!-- When making choices about how to implement this health economic model computationally, we wished to facilitate ethical development and use. -->
 Computational models are now widely used to inform health policy and system design [@dakin2015influence; @Erdemir2020; @LO2022100570; @Christene006827].
 This level of influence has concomitant ethical responsibilities for model developers that are often poorly understood and inadequately fulfilled [@10.3389/fpubh.2017.00068; @pliakos2021ethics; @thompson2022escape; @calder2018computational].
-
-Computational health economic models (CHEMs) can be implemented using specialized commercial software or authored as bespoke software projects in a programming language.
-Advantage of commercial modelling tools are simplicity and ease of use, but a software development approach facilitates development of models that may be more realistic, transparent, reusable and adaptable [@incerti2019r].
-For CHEMs that are implemented as software projects, a major early decision is selection of an appropriate software framework.
-A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users [@myllarniemi2018development].
-Advantages of using software frameworks include facilitating code reuse and extension, promoting good programming practice and the capability to provide enhanced functionality and performance without additional effort by developers [@edwin2014software].
-However, software frameworks can be challenging and time consuming to create [@edwin2014software] and then difficult for others to learn, often requiring developers to undergo specialist training [@myllarniemi2018development].
-There is also a risk that a software framework may become excessively complex over time [@edwin2014software].
-
-We are developing a model to explore multiple economic questions relating to the mental health of young people aged 12 to 25.
-When making choices about how to implement this model computationally, we wished to facilitate ethical development and use.
-However, we are not aware of any software framework for implementing CHEMs that adhere to explicitly stated ethical requirements.
+There is limited guidance on software frameworks for implementing CHEMs that adhere to explicitly stated ethical requirements.

### 2023-08-01 Markdown/Manuscript/Child_RMDs/MS_Tables.Rmd
working my way through supervisors comments

@@
                         two = "../Child_RMDs/MS_Tables_2.RMD",
-                        three = "../Child_RMDs/MS_Tables_3.RMD")
+                        three = "../Child_RMDs/MS_Tables_3.RMD",
+                        four = "../Child_RMDs/MS_Tables_4.RMD")
 }else{
     child_docs_ls <- list(one = NULL,
-                      two = NULL)
+                      two = NULL,
+                      three = NULL,
+                      four = NULL)
 }

### 2023-08-01 Markdown/Manuscript/Child_RMDs/MS_Tables_2.Rmd
working my way through supervisors comments

--- 2023-01-26 Markdown/Manuscript/Child_RMDs/MS_Tables_2.Rmd
@@
 ---
-```{r cpkgs, tab.cap='Modelling toolkit R packages for developing and using MOSHEMs that meet framework standards', tab.id = 'cpkgs', echo = F, results = 'asis'}
+```{r timelygls, tab.cap='Framework standards', tab.id = 'timelygls', echo = F, results = 'asis'}
 library(kableExtra)  
-df <- tibble::tibble(Package = c("ready4",
-                                       "ready4fun",
-                                       "ready4class",
-                                       "ready4pack",
-                                       "ready4use",
-                                       "ready4show"),
-                           # Version = Package %>%
-                           #   purrr::map_chr(~utils::packageDescription(.x) %>%
-                           #                    purrr::pluck("Version")),
-                           Focus = c("Foundation",
-                                     "Module algorithms",
-                                     "Module structures",
-                                     "Module libraries",
-                                     "Datasets",
-                                     "Analyses"),
-                           A = c("3","2-3","2","1-2,5,7","1-2,7","4,6"), 
-                           R = c("4","5","4-5","1,3,6","3,7",""),
-                           U = c("","","","1-3","1",""),
-                           # E = c("", "1","1-2","1","3",""),
-                           # L = c("","","","1,3","2-3",""),
-                           # Y = c("","","","","","1-2"),
-                           `Depends on` = Package %>%
-                             purrr::map(~ {
-                               utils::packageDescription(.x) %>%
-                                 `[`(c("Depends", "Imports")) %>%
-                                 purrr::map(~{
-                                   if(is.null(.x)){
-                                     character(0)
-                                     }else{
-                                       .x %>%
-                                         strsplit(",\\n") %>%
-                                         purrr::flatten_chr() %>%
-                                         purrr::map(~strsplit(.x,", ") %>%
-                                                      purrr::flatten_chr()) %>%
-                                         purrr::flatten_chr() %>% sort() %>%
-                                         purrr::discard(~startsWith(.x,"R "))
-                                       }
-                                   }) %>%
-                                 purrr::flatten_chr() %>%
-                                 unique() %>%
-                                 sort() %>%
-                                 purrr::map_chr(~{
-                                   updated_1L_chr <- stringr::str_replace_all(.x,"\\n"," ")
-                                   problem_idx_1L_chr <- stringr::str_locate(updated_1L_chr," ")[1,1] %>%
-                                     unname()
-                                   if(!is.na(problem_idx_1L_chr))
-                                     updated_1L_chr <- updated_1L_chr %>%
-                                     stringr::str_sub(end = problem_idx_1L_chr-1)
-                                   updated_1L_chr %>% 
-                                     trimws(which = "left") 
-                                   })
-                               }) %>% 
-                             purrr::map_chr (~ .x %>% paste0(collapse = " "))) %>% 
-  as.data.frame() 
-    df$Ref <- c("@ready42022",
-                    "@ready4fun2022",
-                    "@ready4class2022",
-                    "@ready4pack2022",
-                    "@ready4use2022",
-                    "@ready4show2022")
-df <- df %>%
-  dplyr::mutate(Standard = purrr::pmap_chr(df,
-                                           ~paste0("A",
-                                                  ..3,
-                                                  paste0(rep("&nbsp;",
-                                                      2+max(nchar(df[,3]))-nchar(..3)),
-                                                      collapse = ""#
+df <- data.frame(`Objective` = rep("",20),
+  # `Models are` = c(rep("Transparent",6),
+  #                                 rep("Iterative",4),
+  #                                 rep("Modular",2),
+  #                                 rep("Epitomising",3),
+  #                                 rep("Licensed",3),
+  #                                 rep("Yielding",2)),
+  #                Goal = c(rep("people can easily see how a model has been implemented and tested",6),
+  #                         rep("a model is routinely updated to maintain and improve validity",4),
+  #                         rep("models and their components can be combined to extend their scope",2),
+  #                         rep("model code is sufficiently general to be be re-used in multiple decision contexts",3),
+  #                         rep("a model, its components and derivatives are persistently re-usable by other modeller",3),
+  #                         rep("a model can be simply, flexibly and reliably used as a decision aid",2)),
+                 Standard = c(paste0("A",#"T", 
+                                      1:7
                                       ),
-                                                  ifelse(..4=="","","R"),
-                                                  ..4,
-                                                  paste0(rep("&nbsp;",
-                                                      2+max(nchar(df[,4]))-nchar(..4)),
-                                                      collapse = ""#
+                               paste0("R",1:9),# paste0("M",1:2),
+                               # paste0("E",1:3),
+                               # paste0("L",1:3),
+                               # paste0("Y",1:2),
+                               paste0("U",#"I",
+                                      1:4)
                                ),
-                                                  ifelse(..5=="","","U"),
-                                                  ..5,
-                                                  paste0(rep("&nbsp;",
-                                                      1+max(nchar(df[,5]))-nchar(..5)),
-                                                      collapse = ""#
-                                                      )#,
-                                                  # ifelse(..6=="","","E"),
-                                                  # ..6,
-                                                  # paste0(rep("&nbsp;",
-                                                  #     1+max(nchar(df[,6]))-nchar(..6)),
-                                                  #     collapse = ""#
-                                                  #     ),
-                                                  # ifelse(..7=="","","L"),
-                                                  # ..7,
-                                                  # # paste0(rep("&nbsp;",
-                                                  # #     1+max(nchar(df[,7]))-nchar(..7)),
-                                                  # #     collapse = ""#
-                                                  # #     ),
-                                                  # ifelse(..8=="","","&nbsp; &nbsp; &nbsp; &nbsp; Y"),
-                                                  # ..8,
-                                                  # paste0(rep("&nbsp;",
-                                                  #     1+max(nchar(df[,8]))-nchar(..8)),
-                                                  #     collapse = ""#
-                                                  #     )
-                                                  ))) %>%
-
-  dplyr::select(Package,
-                Ref,
-                Focus,
-                Standard,
-                `Depends on`)
-
-names_chr <- names(df)
-df <- data.frame(df[,1],
-                 rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp;"),
-                     nrow(df)),
-                 df[,2:3],
-                 rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp;")
-                     ,nrow(df)),
-                 df[,4],
-                 #rep("&nbsp; &nbsp; &nbsp;",nrow(df)),
-                 df[,5])
-colnames(df) <- c("Package",
-                  ifelse(params$X@outp_formats_chr[1] == "Word","XXX"," "),
-                  "Ref", "Focus", 
-                  ifelse(params$X@outp_formats_chr[1] == "Word","YYY"," "),
-                  "Standard     ",# " ",
-                  "Depends on these R libraries")
-#df$Package <- "![](../Data/images/ready4.png){ width=10% }"#"\\includegraphics[valign=T,scale=2.5,raise=2mm]{../Data/images/ready4.png}"
-df$`Standard     `  <- df$`Standard     ` %>% stringr::str_replace_all("&nbsp;"," ")
+                 Meaning = c(
+                   "Open online repositories are used to permanently archive, uniquely identify and transparently record authorship and development history of model code and data.",#T1
+                   # T2 MISSING - Merged With T1
+                   "Model code and data are documented.",#<T2, Was T3
+                   "Model code uses consistent and abstracted syntax.",# T3, Was T4 -->
+                   "Literate programming is used to implement model analyses.",#T4,Was T5
+                   "Model code coverage is reported.", #T5, New, replaces version now moved to T4 
+                   "All parts of a study analysis and reporting workflow can be reproduced and/or replicated.", #T6, was T7, Replaces Deleted T6 
+                   "Model code and data are distributed with tools to support appropriate citation.",#*L3: New, new location
+                   "Model code is made available for re-use under copyleft or permissive licenses.",#L1: **
+                   "Non-confidential model data is licensed for liberal re-use (potentially subject to ethical use terms).",#L2
+                   "Model code and data are stored and managed separately.",#*M1: Modified (lost ref to licensed and cited) 
+                   "Model code uses encapsulation and inheritence for data structures.",#*M2: Replacement - Old version now merged with E1 # And with E2: "Modules are inheriting data-structures.",#E2
+                   "Model code uses functions to implement algorithms.",#E1: Modified (lost ref to OOP and merged with M2) -->
+                   "Model code is distributed as code libraries.",
+                   "Test data is available to demonstrate the transferability of model code.",#E3: **
+                   # OLD CITATION
+                   "Statistical models are distributed with tools for making out of sample predictions.",#*Y1: New, Replaces Old Y1 (now Y2)
+                   "User-interfaces allow non-technical users to configure and use models.",#Y2: Was Y1     
+                   "Model code and data are version controlled.",#*I1, Was I2 
+                   "The signficiance and status of code and data updates are indicated with semantic versioning and release types.",#I2, Was I1 
+                   "Continuous integration is used to verify model code updates.",#I3 
+                   "Deprecation conventions are used to retire model code and data."#**I4 
+                 ),
+                 check.names = F)
 if(params$X@outp_formats_chr[1] == "Word") {
@@
   library("ftExtra")
-  df[,c(1,3:4,6:7)] %>%
+  df %>%
     ready4show::print_table(output_type_1L_chr = params$X@outp_formats_chr[1],
@@
   }else{
-    df$Ref<-NULL
-    #df$Package <- ""
-    df$Package  <- df$Package %>% 
-                      purrr::map_chr(~paste0("\\includegraphics[valign=M,width=1.9cm,raise=4mm]{../Data/images/",.x,"_logo.png}"))#scale=0.4,raise=3mm]
-    # df$Package <- "\\includegraphics[valign=M,scale=0.08,raise=3mm]{../Data/images/ready4.png}"
-    df[,c(1,3,5:6)]   %>%
-    # kableExtra::kbl(format = "markdown",
-    #                   escape = F,
-    #                 caption = knitr::opts_current$get("tab.cap"))
+    df %>%
       kableExtra::kbl(booktabs = T, 
@@
       kableExtra::kable_paper(full_width = F) %>%
-      kableExtra::column_spec(3,latex_valign = "m") %>%
-      # kableExtra::column_spec(1, 
-      #                         image = kableExtra::spec_image(rep("../Data/images/ready4.png",nrow(df)), 
-      #                                                           150, 150)) %>%
-      kableExtra::column_spec(4, width = "24em",latex_valign = "m")
+      kableExtra::column_spec(1, bold=T) %>%
+      # kableExtra::collapse_rows(columns = 1) %>%
+      kableExtra::column_spec(3, width = "35em") %>%
+      kableExtra::pack_rows("Accountable - it is easy to see who developed, tested and applied a model and how they did it.",1,7) %>%
+      kableExtra::pack_rows("Updatable - a model and its components are maintained and continuously improved.",17,20) %>%
+      # kableExtra::pack_rows("Modular - models and their components can be combined to extend their scope",11,12) %>%
+      # kableExtra::pack_rows("Epitomising - model code can be re-used in other decision contexts",13,15) %>%
+      kableExtra::pack_rows("Reusable - a model and its components can be used in other models and by other modellers.",8,16) #%>%
+      # kableExtra::pack_rows("Yielding - a model can be simply, flexibly and reliably used as a decision aid",19,20)
+
     }

### 2023-08-01 Markdown/Manuscript/Child_RMDs/MS_Tables_4.Rmd
working my way through supervisors comments

--- 2023-01-31 Markdown/Manuscript/Child_RMDs/MS_Tables_3.Rmd
@@
 The relationship between functions can be illustrated using an app: https://www.ready4-dev.com/docs/getting-started/software/libraries/dependencies/",
-                                           "All module data-structures and algorithms are distributed as five code libraries [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155; @matthew_p_hamilton_2021_5646669].",
+                                           "All module data-structures and algorithms are distributed as code libraries [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155; @matthew_p_hamilton_2021_5646669].",
                                            "Two synthetic datasets and their data dictionaries are publicly available in a data repository [@DVN/HJXYKQ_2021].

### 2023-08-01 Markdown/Manuscript/Parent_PDF/Parent_PDF.Rmd
working my way through supervisors comments

--- 2022-04-19 Markdown/Manuscript/Parent_PDF/Parent_PDF.Rmd
@@
   X: NULL
-abstract: "`r paste0(readLines('../Header/abstract.txt'),collapse=' ')`"
+abstract: "TO BE REPLACED"
+# abstract: "`r paste0(readLines('../Header/abstract.txt'),collapse=' ')`"
 graphics: yes

### 2023-08-01 setup.R

@@ -38,11 +38,11 @@ X <- renewSlot(X,
                {
                  args_ls <- X@abstract_args_ls
                  args_ls$abstract_ls <- list(Summary = "Computers are tools that are now essential to the work of health economists. 
-                                             However, the ethical dimensions of alternative approaches to the computational implementation of health economic models are poorly understood. 
-                                             There is a corresponding need for technical infrastructure that can better facilitate implementations of computational health economic models (CHEMs) that meet explicit ethical standards. 
+                                             However, the ethical dimensions of how health economic models are implemented computationally are poorly understood. 
+                                             Explicit ethical standards for computational health economic models (CHEMs) and the technical infrastructure to facilitate implementations of that meet those standards are required. 
                                              We propose six criteria for assessing ethical implementation of CHEMs – two each for the three domains of transparency, reusability and updatability. 
                                              To facilitate the implementation of CHEMs that meet these criteria, we developed a novel prototype software framework in the open source programming language R. 
-                                             The framework comprises six code libraries that collectively provide a toolkit for authoring CHEMs, supplying them with data and using them to undertake reproducible analyses.  
+                                             The framework comprises six code libraries that collectively provide a toolkit for authoring CHEMs, supplying them with data and using them to undertake generalisable and transferable analyses.  
                                              The framework supports integrations with existing digital services for collaborative software development and data archiving. We are currently applying the software framework to develop and apply utility mapping models in youth mental health. 
                                              We assess the first set of utility mapping CHEMs that we have developed with the framework as wholly meeting both transparency criteria (open access code and data and clarity about author contributions and beliefs), one reusability criteria (liberal terms of use) and one updatability criteria (infrastructure for model maintenance) and partially meeting the two remaining criteria for transparency (supports generalisability and transferability) and updatability (retesting and deprecation).  
                                              The assessment criteria and the software framework we have developed can inform future work to understand and improve ethical computational implementations of health economic models.",

### 2023-08-14 Markdown/Manuscript/Child_RMDs/MS_Body.Rmd
circulated draft
stuck
Redo with accontable, reusable and updatable themes
up to fw
updated intro

@@
 ---
+
+```{r child="../Child_RMDs/XX_Funs.Rmd", echo=FALSE}
+```
+```{r child="../Child_RMDs/MS_Tables.Rmd", echo=FALSE}
+```
+```{r child="../Child_RMDs/MS_Figures.Rmd", echo=FALSE}
+```
+<!-- Add child RMDs for results content -->
 
@@
 
+# Conclusion
+
 ```{r child="../Child_RMDs/MS_Conclusion.Rmd", echo=FALSE}
 ```
+
+## Acknowledgement {-}
+The authors would like to acknowledge the contribution of John Gillam who provided advisory input to this research.
 

### 2023-08-14 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
updated intro

@@
 
-**Transparency** has been recommended as a core criterion for assessing ethical public health modelling practice [@10.3389/fpubh.2017.00068].
+**Transparency** has been  as a core identified as a core feature of ethical public health modelling practice [@10.3389/fpubh.2017.00068].
 Guidance on transparency in health economic modelling recommended that model code and data should be clearly documented, potentially with different versions for technical and non-technical users [@Eddy2012].
@@
 
-Model **reusability** is the second attribute that we identified as being core to ethical CHEM implementations.
-Making a CHEM’s code, data and documentation publicly available is now considered “gold-standard” practice but is not sufficient to promote model re-use.
-Computational implementations that store model algorithms and data in distinct files and locations (as opposed to embedding data such as parameter values into source code) facilitate selective modification of model components.
-Writing model algorithms as collections of functions (short, self-contained and reusable software routines that each perform a discrete task), has been recommended as good practice for scientific computing [@Wilson_2017] and can facilitate model generalisability.
-The concept of inheritance [@8717448], a feature of object-oriented programming, facilitates selective editing of algorithms when transferring models to different decision contexts [@ready4oop2022].
-This benefit can be further enhanced if model developers adopt a modular approach, in which a model is constructed from multiple reusable and replaceable sub-models (modules) [@pan2021modular].
+Model **reusability** is the second attribute that we identify as being core to ethical CHEM implementations.
+Making a CHEM’s code, data and documentation publicly available is increasingly considered good practice, yet is not sufficient to promote model re-use.
+Writing model algorithms as collections of functions (short, self-contained and reusable software routines that each perform a discrete task), is good scientific computing practice [@Wilson_2017] and facilitates model reuse without adaptation (generalisability).
+To support reuse with adaptation (transferability), computational implementations can store model code and data in distinct files and locations (as opposed to embedding data such as parameter values into source code).
+Transferability can also be advanced through the use of object-oriented programming approaches [@ready4oop2022] that take advantage of the concept of inheritance [@8717448] to allow models to be first duplicated and then selectively modified.
+Generalisability and transferability are further enhanced if computational implementations adopt a modular approach, in which a model is constructed from multiple independently reusable and replaceable sub-models (modules) [@pan2021modular].
 To grant permissions to others to use, test and adapt models and their components, health economists can avail of two broad categories of open source licensing options.
@@
 <!-- The choices that CHEM developers make about model implementation and licensing will also shape who can use a model and for what purposes.  -->
+<!-- are relatively easier to selectively modify. -->
 The **reusability** of a CHEM implementation can be assessed against the criteria:
 
--	R1: Model code and data are implemented to facilitate both generalizability and transferability.
+-	R1: Model code and data are implemented to facilitate both generalisability and transferability.
 
@@
 
-To remain valid for longer, models should be continually updated and refined as new evidence emerges and healthcare systems evolve [@Jenkins2021; @@garcia2021cost].
-Ensuring that a model is regular reviewed to identify and implement required improvements is a receommended defence against model validity decay [@calder2018computational].
-Key enablers of sustainable maintenance of open source research software are committed, adequately resourced core development team and active user community [@info:doi/10.2196/20028].
-Currently, the core development team for a CHEM will be typically be funded to produce a project end-point deliverable whose specifications are well defined early in the project.
+Models should be **updatable** so that they remain valid for longer, evolving as new evidence emerges and the systems being modelled change [@Jenkins2021; @@garcia2021cost].
+Ensuring that a model is regularly reviewed to identify and implement required improvements is a recommended defense against model validity decay [@calder2018computational].
+Sustainable maintenance of open source research software requires both a core development team and an active user community [@info:doi/10.2196/20028].
+Online communities can be an efficient means of engaging model users in testing each version of a model, identifying issues and suggesting improvements.
+Services such as GitHub [@github2007] provide collaborative code development tools [@MERGEL2015464] that help elicit, integrate and reconcile contributions from multiple contributors and to ensure each update is uniquely identifiable and retrievable.
+It is also important that verification checks are rerun with each model update, a task that can be automated using the software development practice of Continuous Integration [@CI2017].
+The risk of model revisions having unintended consequences for third party users can be mitigated through the use of deprecation conventions [@zhou2016api] that take an informative and staged approach to retiring outdated model code and data.
+<!-- Currently, the core development team for a CHEM will be typically be funded to produce a project end-point deliverable whose specifications are well defined early in the project.
 For more complex and multi-purpose CHEMs, particularly those designed to be incorporated into decision support systems, it may be better for development teams to adopt Agile Software Development [@beck2001manifesto], an approach that has been recommended for complex public health software projects [@10.3389/fpubh.2022.899874].
 An Agile model will be less clearly specified in the initial project plan, but will instead continually develop in response to the requirements and feedback of users, who are provided with an initial, simplified working version of the model at the earliest feasible opportunity.
-Online communities can be an efficient means of engaging model users in testing each version of a model, identifying issues and suggesting improvements.
-Services such as GitHub [@github2007] provide collaborative code development tools [@MERGEL2015464] that help elicit, integrate and reconcile contributions from multiple contributors and to ensure each update is uniquely identifiable and retrievable.
-It is important that verification checks are rerun with each model update, a task that can be automated using the software development practice of Continuous Integration [@CI2017].
-The risk of model revisions having unintended consequences for third party users can be mitigated through the use of deprecation conventions [@zhou2016api] that take an informative and staged approach to retiring outdated model code and data.
+-->
 
-Assessment criteria for an updatable CHEM:
+The **updatability** of a CHEM implementation can be assessed against the criteria:
 
--	U1: Resources and infrastructure are in place to support sustained development, testing, maintenance and version control of a model in collaboration with model users.
+-	U1: Technical infrastructure is in place to support sustained development, testing, maintenance and version control of a model in collaboration with model users.
 

### 2023-08-14 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
updated intro

@@
 
-To support the collaborative development of CHEMs that meet TRU assessment criteria, we have created a prototype software framework called ready4.
-We have designed this framework as a lightweight extension to existing software development infrastructure that could be used to implement CHEMs that are both open-source (for transparency and reusability) and modular (for reusability and updatability).
+To support the development of CHEMs that meet TRU assessment criteria, we have created a prototype software framework called ready4.
+We have designed this framework to enable ethical computational implementations of health economic models that are both open-source (for transparency and reusability) and modular (for reusability and updatability).
+The framework aims to support the standardization and interoperability that are core enablers of implementing a modular and open source approaches.
+Model modules need to be able to share inputs and outputs with each other and to be run as independent models [@barros2023empowering], even when these modules are authored by different teams.
 
 ## 	Framework libraries 
-To work within the popular open-source programming environment R [@RCORE2022], the ready4 software framework is implemented as six development version R code libraries.
-The R libraries collectively provide model developers with tools to combine R's functional and object-oriented programming paradigms [@10.1214/13-STS452] in authoring CHEMs, supplying those CHEMs with data and using CHEMs to implement reproducible modelling analyses.
-The six novel libraries and the preexisting third-party R libraries they depend on are summarised in Table \@ref(tab:cpkgs).
+To work within the popular open-source programming language R [@RCORE2022], the ready4 software framework is implemented as R code libraries.
 
-Standardization and interoperability are core requirements of implementing a modular approach.
-Model modules need to be able to share inputs and outputs with each other and to be run as independent models [@barros2023empowering].
-Each CHEM module authored with the ready4 framework will include both a data structure (specifying the required properties of data that can validly be supplied to a module) and a set of algorithms (specifying the operations that can be performed on data contained in a module instance).
+The R language supports functional and object-oriented programming paradigms [@10.1214/13-STS452].
+Both these paradigms are used in the ready4 framework to provide tools for authoring CHEMs, supplying those CHEMs with data and using CHEMs to implement reproducible modelling analyses.
+<!-- Each CHEM module authored with the ready4 framework will include both a data structure (specifying the required properties of data that can validly be supplied to a module) and a set of algorithms (specifying the operations that can be performed on data contained in a module instance).
+-->
+
+As R is an open source language, each new R library typically depends on a number of other R libraries that have been written by third parties.
+As the number of third party dependencies of an R library grows so does the fragility of that library (e.g.
+the library may cease to work as intended due to changes in one of its dependency libraries).
+To reduce the fragility of our framework we implemented it as multiple R libraries rather than one R library.
+In total we authored six novel R libraries to implement the ready4 framework, all of which have distinct purposes and depend on have unique third-party R library dependencies (Table \@ref(tab:cpkgs)).
+<!-- development version -->
+
 The foundational framework library, called ready4, defines a template module data structure (using R’s S4 class system) from which all CHEM module data structures will be created and a novel syntax that enable module algorithms to be consistently named.

### 2023-08-14 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
updated intro

--- 2023-04-19 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
@@
 In seeking to solve these problems, health economists typically use models which are simplified and selective representations of systems that are believed to influence human health.
-These representations can be described in words and pictures (a conceptual model), in equations (a mathematical model) or in computer code (a computational model).
-The predictions reported in health economic studies are typically generated by the execution of a computer program which applies a computational model to compatible data inputs (e.g., parameter values) and performs a sequence of numeric calculations.
+A health economic model should be capable of being described using words and figures (a conceptual model), equations (a mathematical model) and computer code (a computational model).
+Health economic scientific manuscripts typically describe a model using its conceptual and mathematical representations but report results that have been generated by applying the computational model.
+The conceptual, mathematical and computational representations of a model are assumed to be isomorphic.
+Independent assessment of the validity of this assumption depends in part on the approach taken to computational model implementation and dissemination.
 
-Computational models are now widely used to inform health policy and system design [@dakin2015influence; @Erdemir2020; @LO2022100570; @Christene006827].
-This level of influence has concomitant ethical responsibilities for model developers that are often poorly understood and inadequately fulfilled [@10.3389/fpubh.2017.00068; @pliakos2021ethics; @thompson2022escape; @calder2018computational].
+<!-- the execution of a computer program that applies a computational model to compatible data inputs (e.g., parameter values) and performs a sequence of numeric calculations. -->
+<!-- the predictions reported in health economic studies are now almost always -->
 
-Computational health economic models (CHEMs) can be implemented using specialized commercial software or authored as bespoke software projects in a programming language.
-Advantage of commercial modelling tools are simplicity and ease of use, but a software development approach facilitates development of models that may be more realistic, transparent, reusable and adaptable [@incerti2019r].
-For CHEMs that are implemented as software projects, a major early decision is selection of an appropriate software framework.
+Computational health economic models (CHEMs) can be implemented using specialized commercial software or authored as software development projects in an open-source programming language such as Python [@python2009] or R [@RCORE2022].
+Advantages of commercial modelling tools include simplicity and ease of use, but a software development approach may facilitate computational models that are more transparent, reusable and adaptable [@incerti2019r].
+The most appropriate approach for a specific CHEM project may depend on both the desired features of the model being developed and the resource and time constraints within which the project needs to be delivered (see Table \@ref(tab:proscons)).
+Although health economists report strong interest in making CHEMs more transparent and accessible [@Pouwels2022], open-source CHEMs remain rare [@Feenstra2022; @Emerson2019].
+
+```{r, child = child_docs_ls$one, echo=FALSE}
+```
+<!-- on considerations such as model comprehensiveness, generalisability, reproducibility and transferability -->
+A major early decision in open-source CHEM projects is the selection of an appropriate software framework.
 A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users [@myllarniemi2018development].
+A software framework provides a foundation for developing multiple software applications with shared resources, e.g., code and data files, that can be modified to suit specific needs.
+Software frameworks have widely been developed and implemented in data science, for example, PyTorch [@PyTorch2019] for machine learning using Python.
+
 Advantages of using software frameworks include facilitating code reuse and extension, promoting good programming practice and the capability to provide enhanced functionality and performance without additional effort by developers [@edwin2014software].
-However, software frameworks can be challenging and time consuming to create [@edwin2014software] and then difficult for others to learn, often requiring developers to undergo specialist training [@myllarniemi2018development].
+However, software frameworks can be challenging and time consuming to create [@edwin2014software] and then difficult for others to learn, often requiring model developers to undergo specialist training [@myllarniemi2018development].
 There is also a risk that a software framework may become excessively complex over time [@edwin2014software].
 
-We are developing a model to explore multiple economic questions relating to the mental health of young people aged 12 to 25.
-When making choices about how to implement this model computationally, we wished to facilitate ethical development and use.
-However, we are not aware of any software framework for implementing CHEMs that adhere to explicitly stated ethical requirements.
+<!-- We are developing a model to explore multiple economic questions relating to the mental health of young people aged 12 to 25.   -->
+<!-- When making choices about how to implement this health economic model computationally, we wished to facilitate ethical development and use. -->
+A high-level software framework using R has previously been developed with the primary aim of improving the transparency of CHEMs [@alarid2019need].
+Novel software frameworks may be necessary to facilitate CHEM implementations that meet broader ethical criteria.
+The ethical responsibilities of computational modellers are often poorly understood and inadequately fulfilled [@10.3389/fpubh.2017.00068; @pliakos2021ethics; @thompson2022escape; @calder2018computational].
+Guidance on developing, selecting and using software frameworks for ethical CHEM implementations is scarce.
+
+<!-- Transparency has been proposed as one of the core ethical responsibilities of public health computational modellers [@10.3389/fpubh.2017.00068].  -->
+
+<!-- Although computational models are widely used to inform health policy and system design [@dakin2015influence; @Erdemir2020; @LO2022100570; @Christene006827], -->

### 2023-08-14 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
working my way through supervisors comments
updated intro

@@
 
-```{r child="../Child_RMDs/XX_Funs.Rmd", echo=FALSE}
-```
-```{r child="../Child_RMDs/MS_Tables.Rmd", echo=FALSE}
-```
-```{r child="../Child_RMDs/MS_Figures.Rmd", echo=FALSE}
-```
-<!-- Add child RMDs for results content -->
-
-## Ethical requirements and assessment criteria
+## Assessing ethical computational implementations
 ```{r child="../Child_RMDs/MS_Imp_Guidelines.Rmd", echo=FALSE}

### 2023-08-14 Markdown/Manuscript/Parent_PDF/Parent_PDF.Rmd
updated intro

@@
   bookdown::pdf_book: 
-    base_format: rticles::arxiv_article
+    base_format: rticles::springer_article # rticles::arxiv_article
     includes:
@@
       - '--lua-filter=../Filters/author-info-blocks.lua'
-  bookdown::pdf_document2: 
-    includes:
-      in_header: preamble.tex
-    pandoc_args: 
-      - "--metadata-file=../Header/header_common.yaml"
-      - '--lua-filter=../Filters/scholarly-metadata.lua'
-      - '--lua-filter=../Filters/author-info-blocks.lua'
-    toc: no
-## CUSTOM_AUTHORS_PLACEHOLDER ##
+  # bookdown::pdf_document2: 
+  #   includes:
+  #     in_header: preamble.tex
+  #   pandoc_args: 
+  #     - "--metadata-file=../Header/header_common.yaml"
+  #     - '--lua-filter=../Filters/scholarly-metadata.lua'
+  #     - '--lua-filter=../Filters/author-info-blocks.lua'
+  #   toc: no
+  #   keep_tex: true
+
 params:
@@
 graphics: yes
-csl: plos.csl
+#csl: plos.csl
+title: REPLACE ME
+titlerunning: TEMPORARY
+authorrunning: Hamilton, Gao, Wiesner et al.
+thanks: | 
+    The study was funded by ADD DETAILS HERE. 
+keywords: one, two, three, four, five, six
+#PACS: 
+#- PAC1
+#- superPAC
+
+# MSC:
+# - MSC code 1
+# - MSC code 2
+classoptions: 
+  - sn-basic      
+  # - Numbered      # Optional: Use numbered references instead of namedate references (only for sn-nature, sn-basic, sn-vancouver, sn-chicago, sn-mathphys or sn-nature)
+  # - referee       # Optional: Use double line spacing 
+  # - lineno        # Optional: Add line numbers
+  # - iicol         # Optional: Double column layour
+#biblio-style: spbasic
+# bibstyle options spbasic(default), spphys, spmpsci
+# header-includes:
+# - \usepackage{booktabs}
+# - \usepackage{longtable}
+# - \usepackage{array}
+# - \usepackage{multirow}
+# - \usepackage{wrapfig}
+# - \usepackage{float}
+# - \usepackage{colortbl}
+# - \usepackage{pdflscape}
+# - \usepackage{tabu}
+# - \usepackage{threeparttable}
+# - \usepackage[normalem]{ulem}
+# - \usepackage{threeparttablex}
+# - \usepackage{makecell}
 ---

### 2023-08-14 Markdown/Manuscript/Parent_PDF/Springer/Example/Example.tex
updated intro

%Version 2.1 April 2023
% See section 11 of the User Manual for version history
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                 %%
%% Please do not use \input{...} to include other tex files.       %%
%% Submit your LaTeX manuscript as one .tex document.              %%
%%                                                                 %%
%% All additional figures and files should be attached             %%
%% separately and not embedded in the \TeX\ document itself.       %%
%%                                                                 %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[sn-basic,pdflatex]{sn-jnl}

%%%% Standard Packages
%%<additional latex packages if required can be included here>

\usepackage{graphicx}%
\usepackage{multirow}%
\usepackage{amsmath,amssymb,amsfonts}%
\usepackage{amsthm}%
\usepackage{mathrsfs}%
\usepackage[title]{appendix}%
\usepackage{xcolor}%
\usepackage{textcomp}%
\usepackage{manyfoot}%
\usepackage{booktabs}%
\usepackage{algorithm}%
\usepackage{algorithmicx}%
\usepackage{algpseudocode}%
\usepackage{listings}%
%%%%

%%%%%=============================================================================%%%%
%%%%  Remarks: This template is provided to aid authors with the preparation
%%%%  of original research articles intended for submission to journals published
%%%%  by Springer Nature. The guidance has been prepared in partnership with
%%%%  production teams to conform to Springer Nature technical requirements.
%%%%  Editorial and presentation requirements differ among journal portfolios and
%%%%  research disciplines. You may find sections in this template are irrelevant
%%%%  to your work and are empowered to omit any such section if allowed by the
%%%%  journal you intend to submit to. The submission guidelines and policies
%%%%  of the journal take precedence. A detailed User Manual is available in the
%%%%  template package for technical guidance.
%%%%%=============================================================================%%%%

%% Per the spinger doc, new theorem styles can be included using built in style, 
%% but it seems the don't work so commented below
%\theoremstyle{thmstyleone}%
\newtheorem{theorem}{Theorem}%  meant for continuous numbers
%%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
%% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
\newtheorem{proposition}[theorem]{Proposition}%
%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.

%% \theoremstyle{thmstyletwo}%
\theoremstyle{remark}
\newtheorem{example}{Example}%
\newtheorem{remark}{Remark}%

%% \theoremstyle{thmstylethree}%
\theoremstyle{definition}
\newtheorem{definition}{Definition}%

\raggedbottom

% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\begin{document}

\title[Article Title runing]{Article Title}

%%=============================================================%%
%% Prefix	-> \pfx{Dr}
%% GivenName	-> \fnm{Joergen W.}
%% Particle	-> \spfx{van der} -> surname prefix
%% FamilyName	-> \sur{Ploeg}
%% Suffix	-> \sfx{IV}
%% NatureName	-> \tanm{Poet Laureate} -> Title after name
%% Degrees	-> \dgr{MSc, PhD}
%% \author*[1,2]{\pfx{Dr} \fnm{Joergen W.} \spfx{van der} \sur{Ploeg} \sfx{IV} \tanm{Poet Laureate}
%%                 \dgr{MSc, PhD}}\email{iauthor@gmail.com}
%%=============================================================%%

\author*[1,2]{\pfx{Dr.} \fnm{Leading} \spfx{van} \sur{Author} \sfx{III} \tanm{Poet
Laureate} \dgr{MSc,
PhD}}\email{\href{mailto:abc@def}{\nolinkurl{abc@def}}}

\author[2]{\fnm{Second} \sur{Author} }

  \affil*[1]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\city{City}, \country{Country}, \postcode{100190}, \state{State}, \street{Street}}}
  \affil*[2]{\orgname{Other Organisation}}

\abstract{\textbf{Purpose}: The abstract serves both as a general
introduction to the topic and as a brief, non-technical summary of the
main results and their implications. The abstract must not include
subheadings (unless expressly permitted in the journal's Instructions to
Authors), equations or citations. As a guide the abstract should not
exceed 200 words. Most journals do not set a hard limit however authors
are advised to check the author instructions for the journal they are
submitting to.

\textbf{Methods:} The abstract serves both as a general introduction to
the topic and as a brief, non-technical summary of the main results and
their implications. The abstract must not include subheadings (unless
expressly permitted in the journal's Instructions to Authors), equations
or citations. As a guide the abstract should not exceed 200 words. Most
journals do not set a hard limit however authors are advised to check
the author instructions for the journal they are submitting to.

\textbf{Results:} The abstract serves both as a general introduction to
the topic and as a brief, non-technical summary of the main results and
their implications. The abstract must not include subheadings (unless
expressly permitted in the journal's Instructions to Authors), equations
or citations. As a guide the abstract should not exceed 200 words. Most
journals do not set a hard limit however authors are advised to check
the author instructions for the journal they are submitting to.

\textbf{Conclusion:} The abstract serves both as a general introduction
to the topic and as a brief, non-technical summary of the main results
and their implications. The abstract must not include subheadings
(unless expressly permitted in the journal's Instructions to Authors),
equations or citations. As a guide the abstract should not exceed 200
words. Most journals do not set a hard limit however authors are advised
to check the author instructions for the journal they are submitting
to.\}}

\keywords{key, dictionary, word}

\pacs[JEL Classification]{D8, H51}
\pacs[MSC Classification]{35A01, 65L10}

\maketitle

\hypertarget{sec1}{%
\section{Introduction}\label{sec1}}

The Introduction section, of referenced text \citet{bib1} expands on the
background of the work (some overlap with the Abstract is acceptable).
The introduction should not include subheadings.

Springer Nature does not impose a strict layout as standard however
authors are advised to check the individual requirements for the journal
they are planning to submit to as there may be journal-level
preferences. When preparing your text please also be aware that some
stylistic choices are not supported in full text XML (publication
version), including coloured font. These will not be replicated in the
typeset article if it is accepted.

\hypertarget{sec2}{%
\section{Results}\label{sec2}}

Sample body text. Sample body text. Sample body text. Sample body text.
Sample body text. Sample body text. Sample body text. Sample body text.

\hypertarget{sec3}{%
\section{This is an example for first level head---section
head}\label{sec3}}

\hypertarget{subsec2}{%
\subsection{This is an example for second level head---subsection
head}\label{subsec2}}

\hypertarget{subsubsec2}{%
\subsubsection{This is an example for third level head---subsubsection
head}\label{subsubsec2}}

Sample body text. Sample body text. Sample body text. Sample body text.
Sample body text. Sample body text. Sample body text.

\hypertarget{sec4}{%
\section{Equations}\label{sec4}}

Equations in \LaTeX~can either be inline or on-a-line by itself
(``display equations''). For inline equations use the \texttt{\$...\$}
commands. E.g.: The equation \(H\psi = E \psi\) is written via the
command \texttt{\$H\ \textbackslash{}psi\ =\ E\ \textbackslash{}psi\$}.

For display equations (with auto generated equation numbers) one can use
the equation or align environments:

\begin{equation}
\|\tilde{X}(k)\|^2 \leq\frac{\sum\limits_{i=1}^{p}\left\|\tilde{Y}_i(k)\right\|^2+\sum\limits_{j=1}^{q}\left\|\tilde{Z}_j(k)\right\|^2 }{p+q}.\label{eq1}
\end{equation}

where, \begin{align}
D_\mu &=  \partial_\mu - ig \frac{\lambda^a}{2} A^a_\mu \nonumber \\
F^a_{\mu\nu} &= \partial_\mu A^a_\nu - \partial_\nu A^a_\mu + g f^{abc} A^b_\mu A^a_\nu \label{eq2}
\end{align}

Notice the use of \texttt{\textbackslash{}nonumber} in the align
environment at the end of each line, except the last, so as not to
produce equation numbers on lines where no equation numbers are
required. The \texttt{\textbackslash{}label\{\}} command should only be
used at the last line of an align environment where
\texttt{\textbackslash{}nonumber} is not used.

\begin{equation}
Y_\infty = \left( \frac{m}{\textrm{GeV}} \right)^{-3}
    \left[ 1 + \frac{3 \ln(m/\textrm{GeV})}{15}
    + \frac{\ln(c_2/5)}{15} \right]
\end{equation}

The class file also supports the use of
\texttt{\textbackslash{}mathbb\{\}},
\texttt{\textbackslash{}mathscr\{\}} and
\texttt{\textbackslash{}mathcal\{\}} commands. As such
\texttt{\textbackslash{}mathbb\{R\}},
\texttt{\textbackslash{}mathscr\{R\}} and
\texttt{\textbackslash{}mathcal\{R\}} produces \(\mathbb{R}\),
\(\mathscr{R}\) and \(\mathcal{R}\) respectively (refer
Subsubsection~\ref{subsubsec2}).

\hypertarget{sec5}{%
\section{Tables}\label{sec5}}

Tables can be inserted via the normal \texttt{knitr::kable()} function
or other table-generating packages.

\begin{table}

\caption{\label{tab:tab1}Caption text}
\centering
\begin{tabular}[t]{r|r}
\hline
temperature & pressure\\
\hline
0 & 0.0002\\
\hline
20 & 0.0012\\
\hline
40 & 0.0060\\
\hline
60 & 0.0300\\
\hline
80 & 0.0900\\
\hline
100 & 0.2700\\
\hline
\end{tabular}
\end{table}

Tables can also be inserted via the normal table and tabular
environment. To put footnotes inside tables you should use
\texttt{\textbackslash{}footnotetext{[}{]}\{...\}} tag. The footnote
appears just below the table itself (refer
Tables\textasciitilde{}\ref{tab1} and \ref{tab2}). For the corresponding
footnotemark use \texttt{\textbackslash{}footnotemark{[}...{]}}

\begin{table}[h]
\caption{Caption text}\label{tab1}%
\begin{tabular}{@{}llll@{}}
\toprule
Column 1 & Column 2  & Column 3 & Column 4\\
\midrule
row 1    & data 1   & data 2  & data 3  \\
row 2    & data 4   & data 5\footnotemark[1]  & data 6  \\
row 3    & data 7   & data 8  & data 9\footnotemark[2]  \\
\botrule
\end{tabular}
\footnotetext{Source: This is an example of table footnote. This is an example of table footnote.}
\footnotetext[1]{Example for a first table footnote. This is an example of table footnote.}
\footnotetext[2]{Example for a second table footnote. This is an example of table footnote.}
\end{table}

\noindent The input format for the above table is as follows:

\begin{verbatim}
\begin{table}[<placement-specifier>]
\caption{<table-caption>}\label{<table-label>}%
\begin{tabular}{@{}llll@{}}
\toprule
Column 1 & Column 2 & Column 3 & Column 4\\
\midrule
row 1 & data 1 & data 2  & data 3 \\
row 2 & data 4 & data 5\footnotemark[1] & data 6 \\
row 3 & data 7 & data 8  & data 9\footnotemark[2]\\
\botrule
\end{tabular}
\footnotetext{Source: This is an example of table footnote.
This is an example of table footnote.}
\footnotetext[1]{Example for a first table footnote.
This is an example of table footnote.}
\footnotetext[2]{Example for a second table footnote.
This is an example of table footnote.}
\end{table}
\end{verbatim}

\begin{table}[h]
\caption{Example of a lengthy table which is set to full textwidth}\label{tab2}
\begin{tabular*}{\textwidth}{@{\extracolsep\fill}lcccccc}
\toprule%
& \multicolumn{3}{@{}c@{}}{Element 1\footnotemark[1]} & \multicolumn{3}{@{}c@{}}{Element 2\footnotemark[2]} \\\cmidrule{2-4}\cmidrule{5-7}%
Project & Energy & $\sigma_{calc}$ & $\sigma_{expt}$ & Energy & $\sigma_{calc}$ & $\sigma_{expt}$ \\
\midrule
Element 3  & 990 A & 1168 & $1547\pm12$ & 780 A & 1166 & $1239\pm100$\\
Element 4  & 500 A & 961  & $922\pm10$  & 900 A & 1268 & $1092\pm40$\\
\botrule
\end{tabular*}
\footnotetext{Note: This is an example of table footnote. This is an example of table footnote this is an example of table footnote this is an example of~table footnote this is an example of table footnote.}
\footnotetext[1]{Example for a first table footnote.}
\footnotetext[2]{Example for a second table footnote.}
\end{table}

\vfill\eject

In case of double column layout, tables which do not fit in single
column width should be set to full text width. For this, you need to use
\texttt{\textbackslash{}begin\{table*\}} \texttt{...}
\texttt{\textbackslash{}end\{table*\}} instead of
\texttt{\textbackslash{}begin\{table\}} \texttt{...}
\texttt{\textbackslash{}end\{table\}} environment. Lengthy tables which
do not fit in textwidth should be set as rotated table. For this, you
need to use \texttt{\textbackslash{}begin\{sidewaystable\}} \texttt{...}
\texttt{\textbackslash{}end\{sidewaystable\}} instead of
\texttt{\textbackslash{}begin\{table*\}} \texttt{...}
\texttt{\textbackslash{}end\{table*\}} environment. This environment
puts tables rotated to single column width. For tables rotated to double
column width, use \texttt{\textbackslash{}begin\{sidewaystable*\}}
\texttt{...} \texttt{\textbackslash{}end\{sidewaystable*\}}.

\begin{sidewaystable}
\caption{Tables which are too long to fit, should be written using the "sidewaystable" environment as shown here}\label{tab3}
\begin{tabular*}{\textheight}{@{\extracolsep\fill}lcccccc}
\toprule%
& \multicolumn{3}{@{}c@{}}{Element 1\footnotemark[1]}& \multicolumn{3}{@{}c@{}}{Element\footnotemark[2]} \\\cmidrule{2-4}\cmidrule{5-7}%
Projectile & Energy & $\sigma_{calc}$ & $\sigma_{expt}$ & Energy & $\sigma_{calc}$ & $\sigma_{expt}$ \\
\midrule
Element 3 & 990 A & 1168 & $1547\pm12$ & 780 A & 1166 & $1239\pm100$ \\
Element 4 & 500 A & 961  & $922\pm10$  & 900 A & 1268 & $1092\pm40$ \\
Element 5 & 990 A & 1168 & $1547\pm12$ & 780 A & 1166 & $1239\pm100$ \\
Element 6 & 500 A & 961  & $922\pm10$  & 900 A & 1268 & $1092\pm40$ \\
\botrule
\end{tabular*}
\footnotetext{Note: This is an example of table footnote this is an example of table footnote this is an example of table footnote this is an example of~table footnote this is an example of table footnote.}
\footnotetext[1]{This is an example of table footnote.}
\end{sidewaystable}

\hypertarget{sec6}{%
\section{Figures}\label{sec6}}

As per the \LaTeX~standards you need to use eps images for
\LaTeX~compilation and \texttt{pdf/jpg/png} images for \texttt{PDFLaTeX}
compilation. Use the \texttt{dev} knitr option to use the approrpate
format. This is one of the major difference between \LaTeX~and
\texttt{PDFLaTeX}. Each image should be from a single input .eps/vector
image file. Avoid using subfigures. The command for inserting images for
\LaTeX~and \texttt{PDFLaTeX} can be generalized. The package used to
insert images in \texttt{LaTeX/PDFLaTeX} is the graphicx package.
Figures can be inserted via the normal figure environment as shown in
the below example:

\begin{figure}
\includegraphics{Example_files/figure-latex/fig1-1} \caption{This is an example of a caption}\label{fig:fig1}
\end{figure}

\hypertarget{sec7}{%
\section{Algorithms, Program codes and Listings}\label{sec7}}

Packages \texttt{algorithm}, \texttt{algorithmicx} and
\texttt{algpseudocode} are used for setting algorithms in \LaTeX~using
the format:

\begin{verbatim}
\begin{algorithm}
\caption{<alg-caption>}\label{<alg-label>}
\begin{algorithmic}[1]
. . .
\end{algorithmic}
\end{algorithm}
\end{verbatim}

You may refer above listed package documentations for more details
before setting \texttt{algorithm} environment. For program codes, the
``program'' package is required and the command to be used is
\texttt{\textbackslash{}begin\{program\}} \texttt{...}
\texttt{\textbackslash{}end\{program\}}. A fast exponentiation
procedure:

Similarly, for \texttt{listings}, use the \texttt{listings} package.
\texttt{\textbackslash{}begin\{lstlisting\}} \texttt{...}
\texttt{\textbackslash{}end\{lstlisting\}} is used to set environments
similar to \texttt{verbatim} environment. Refer to the
\texttt{lstlisting} package documentation for more details.

A fast exponentiation procedure:

\lstset{texcl=true,basicstyle=\small\sf,commentstyle=\small\rm,mathescape=true,escapeinside={(*}{*)}}
\begin{lstlisting}
begin
  for $i:=1$ to $10$ step $1$ do
      expt($2,i$);  
      newline() od                (*\textrm{Comments will be set flush to the right margin}*)
where
proc expt($x,n$) $\equiv$
  $z:=1$;
  do if $n=0$ then exit fi;
     do if odd($n$) then exit fi;                 
        comment: (*\textrm{This is a comment statement;}*)
        $n:=n/2$; $x:=x*x$ od;
     { $n>0$ };
     $n:=n-1$; $z:=z*x$ od;
  print($z$). 
end
\end{lstlisting}

\begin{algorithm}
\caption{Calculate $y = x^n$}\label{algo1}
\begin{algorithmic}[1]
\Require $n \geq 0 \vee x \neq 0$
\Ensure $y = x^n$ 
\State $y \Leftarrow 1$
\If{$n < 0$}\label{algln2}
        \State $X \Leftarrow 1 / x$
        \State $N \Leftarrow -n$
\Else
        \State $X \Leftarrow x$
        \State $N \Leftarrow n$
\EndIf
\While{$N \neq 0$}
        \If{$N$ is even}
            \State $X \Leftarrow X \times X$
            \State $N \Leftarrow N / 2$
        \Else[$N$ is odd]
            \State $y \Leftarrow y \times X$
            \State $N \Leftarrow N - 1$
        \EndIf
\EndWhile
\end{algorithmic}
\end{algorithm}

\begin{minipage}{\hsize}

\lstset{frame=single,framexleftmargin=-1pt,framexrightmargin=-17pt,framesep=12pt,linewidth=0.98\textwidth,language=pascal}

\begin{lstlisting}
for i:=maxint to 0 do begin \{ do nothing \} end; Write(`Case
insensitive'); Write(`Pascal keywords.');

\end{lstlisting}

\end{minipage}

\hypertarget{sec8}{%
\section{Cross referencing}\label{sec8}}

Figures and tables are labeled with a prefix (fig or tab, respectively)
plus the chunk label. Other environments such as equation and align can
be labelled via the \texttt{\textbackslash{}label\{\#label\}} command
inside or just below the \texttt{\textbackslash{}caption\{\}} command.
You can then use the label for cross-reference. As an example, consider
the chunk label declared for Figure~\ref{fig:fig1} which is fig1. To
cross-reference it, use the command
\texttt{Figure\ \textbackslash{}ref\{fig:fig1\}}, for which it comes up
as ``Figure~\ref{fig:fig1}''.

To reference line numbers in an algorithm, consider the label declared
for the line number 2 of Algorithm~\ref{algo1} is
\texttt{\textbackslash{}label\{algln2\}}. To cross-reference it, use the
command \texttt{\textbackslash{}ref\{algln2\}} for which it comes up as
line~\ref{algln2} of Algorithm~\ref{algo1}.

\hypertarget{subsec7}{%
\subsection{Details on reference citations}\label{subsec7}}

For citations of references, use~\citet{bib1} or \citep{bib2}.

\hypertarget{sec10}{%
\section{Examples for theorem like environments}\label{sec10}}

The documentclass for springer \texttt{sn-jnl.cls} contains 3 styling
that you can use to set new default for theorems and proofs type

\begin{description}
\item[\texttt{thmstyleone}]
Numbered, theorem head in bold font and theorem text in italic style
\item[\texttt{thmstyletwo}]
Numbered, theorem head in roman font and theorem text in italic style
\item[\texttt{thmstylethree}]
Numbered, theorem head in bold font and theorem text in roman style
\end{description}

For mathematics journals, theorem styles can be included as shown in the
following examples.

\begin{theorem}
Example theorem text. Example theorem text. Example theorem text.
Example theorem text. Example theorem text. Example theorem text.
Example theorem text. Example theorem text. Example theorem text.
Example theorem text. Example theorem text.

\end{theorem}

To add labels and subheadings, use LaTeX notation

\begin{theorem}[Theorem subhead]\label{thm1}
Example theorem text. Example theorem text. Example theorem text.
Example theorem text. Example theorem text. Example theorem text.
Example theorem text. Example theorem text. Example theorem text.
Example theorem text. Example theorem text.

\end{theorem}

Other environments are proposition, example, remark, definition, proof
and quote

Sample body text. Sample body text. Sample body text. Sample body text.
Sample body text. Sample body text. Sample body text. Sample body text.

\begin{proposition}
Example proposition text. Example proposition text. Example proposition
text. Example proposition text. Example proposition text. Example
proposition text. Example proposition text. Example proposition text.
Example proposition text. Example proposition text.

\end{proposition}

Sample body text. Sample body text. Sample body text. Sample body text.
Sample body text. Sample body text. Sample body text. Sample body text.

\begin{example}
Phasellus adipiscing semper elit. Proin fermentum massa ac quam. Sed
diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas
lacinia. Nam ipsum ligula, eleifend at, accumsan nec, suscipit a, ipsum.
Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem.

\end{example}

Sample body text. Sample body text. Sample body text. Sample body text.
Sample body text. Sample body text. Sample body text. Sample body text.

\begin{remark}
Phasellus adipiscing semper elit. Proin fermentum massa ac quam. Sed
diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas
lacinia. Nam ipsum ligula, eleifend at, accumsan nec, suscipit a, ipsum.
Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem.

\end{remark}

Sample body text. Sample body text. Sample body text. Sample body text.
Sample body text. Sample body text. Sample body text. Sample body text.

\begin{definition}[Definition sub head]
Example definition text. Example definition text. Example definition
text. Example definition text. Example definition text. Example
definition text. Example definition text. Example definition text.

\end{definition}

Additionally a predefined ``proof'' environment is available. This
prints a ``Proof'' head in italic font style and the ``body text'' in
roman font style with an open square at the end of each proof
environment.

\begin{proof}
Example for proof text. Example for proof text. Example for proof text.
Example for proof text. Example for proof text. Example for proof text.
Example for proof text. Example for proof text. Example for proof text.
Example for proof text.

\end{proof}

Sample body text. Sample body text. Sample body text. Sample body text.
Sample body text. Sample body text. Sample body text. Sample body text.

\hypertarget{sec11}{%
\section{Methods}\label{sec11}}

Topical subheadings are allowed. Authors must ensure that their Methods
section includes adequate experimental and characterization data
necessary for others in the field to reproduce their work. Authors are
encouraged to include RIIDs where appropriate.

\textbf{Ethical approval declarations} (only required where applicable)
Any article reporting experiment/s carried out on
(i)\textasciitilde live vertebrate (or higher invertebrates),
(ii)\textasciitilde humans or (iii)\textasciitilde human samples must
include an unambiguous statement within the methods section that meets
the following requirements:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Approval: a statement which confirms that all experimental protocols
  were approved by a named institutional and/or licensing committee.
  Please identify the approving body in the methods section
\item
  Accordance: a statement explicitly saying that the methods were
  carried out in accordance with the relevant guidelines and regulations
\item
  Informed consent (for experiments involving humans or human tissue
  samples): include a statement confirming that informed consent was
  obtained from all participants and/or their legal guardian/s
\end{enumerate}

If your manuscript includes potentially identifying patient/participant
information, or if it describes human transplantation research, or if it
reports results of a clinical trial then additional information will be
required. Please visit
(\url{https://www.nature.com/nature-research/editorial-policies}) for
Nature Portfolio journals,
(\url{https://www.springer.com/gp/authors-editors/journal-author/journal-author-helpdesk/publishing-ethics/14214})
for Springer Nature journals, or
(\url{https://www.biomedcentral.com/getpublished/editorial-policies/\#ethics+and+consent})
for BMC.

\hypertarget{sec12}{%
\section{Discussion}\label{sec12}}

Discussions should be brief and focused. In some disciplines use of
Discussion or `Conclusion' is interchangeable. It is not mandatory to
use both. Some journals prefer a section `Results and Discussion'
followed by a section `Conclusion'. Please refer to Journal-level
guidance for any specific requirements.

\hypertarget{sec13}{%
\section{Conclusion}\label{sec13}}

Conclusions may be used to restate your hypothesis or research question,
restate your major findings, explain the relevance and the added value
of your work, highlight any limitations of your study, describe future
directions for research and recommendations.

In some disciplines use of Discussion or `Conclusion' is
interchangeable. It is not mandatory to use both. Please refer to
Journal-level guidance for any specific requirements.

\backmatter

\bmhead{Supplementary information}

If your article has accompanying supplementary file/s please state so
here.

Authors reporting data from electrophoretic gels and blots should supply
the full unprocessed scans for key as part of their Supplementary
information. This may be requested by the editorial team/s if it is
missing.

Please refer to Journal-level guidance for any specific requirements.

\bmhead{Acknowledgments}

Acknowledgments are not compulsory. Where included they should be brief.
Grant or contribution numbers may be acknowledged.

Please refer to Journal-level guidance for any specific requirements.

\hypertarget{declarations}{%
\section*{Declarations}\label{declarations}}
\addcontentsline{toc}{section}{Declarations}

Some journals require declarations to be submitted in a standardised
format. Please check the Instructions for Authors of the journal to
which you are submitting to see if you need to complete this section. If
yes, your manuscript must contain the following sections under the
heading `Declarations':

\begin{itemize}
\tightlist
\item
  Funding
\item
  Conflict of interest/Competing interests (check journal-specific
  guidelines for which heading to use)
\item
  Ethics approval
\item
  Consent to participate
\item
  Consent for publication
\item
  Availability of data and materials
\item
  Code availability
\item
  Authors' contributions
\end{itemize}

\noindent If any of the sections are not relevant to your manuscript,
please include the heading and write `Not applicable' for that section.

\begin{flushleft}
Editorial Policies for:

\noindent Springer journals and proceedings:
\url{https://www.springer.com/gp/editorial-policies}

\noindent Nature Portfolio journals:
\url{https://www.nature.com/nature-research/editorial-policies}

\noindent \textit{Scientific Reports}:
\url{https://www.nature.com/srep/journal-policies/editorial-policies}

\noindent BMC journals:
\url{https://www.biomedcentral.com/getpublished/editorial-policies}

\end{flushleft}

\begin{appendices}

\hypertarget{secA1}{%
\section{Section title of first appendix}\label{secA1}}

An appendix contains supplementary information that is not an essential
part of the text itself but which may be helpful in providing a more
comprehensive understanding of the research problem or it is information
that is too cumbersome to be included in the body of the paper.

For submissions to Nature Portfolio Journals please use the heading
``Extended Data''.

\end{appendices}

\bibliography{bibliography.bib}

\end{document}

### 2023-08-14 Markdown/Manuscript/Parent_PDF/Test.Rmd
updated intro

---
# Supported options: 
#   sn-nature:       Style for submissions to Nature Portfolio journals
#   sn-basic:        Basic Springer Nature Reference Style/Chemistry Reference Style
#   sn-mathphys:     Math and Physical Sciences Reference Style
#   sn-aps:          American Physical Society (APS) Reference Style
#   sn-vancouver:    Vancouver Reference Style
#   sn-apa:          APA Reference Style 
#   sn-chicago:      Chicago-based Humanities Reference Style
#   default:         Default

classoptions: 
  - sn-basic      
  # - Numbered      # Optional: Use numbered references instead of namedate references (only for sn-nature, sn-basic, sn-vancouver, sn-chicago, sn-mathphys or sn-nature)
  # - referee       # Optional: Use double line spacing 
  # - lineno        # Optional: Add line numbers
  # - iicol         # Optional: Double column layour

title: Article Title
titlerunning: Article Title runing

authors: 
  - prefix: Dr.
    firstname: Leading
    particle: van 
    lastname: Author
    suffix: III
    naturename: Poet Laureate
    degrees: MSc, PhD
    email: abc@def
    affiliation: [1,2]
    corresponding: TRUE
    equalcont: These authors contributed equally to this work.

  - firstname: Second
    lastname: Author
    affiliation: 2
    equalcont: These authors contributed equally to this work.

affiliations:
  - number: 1
    corresponding: TRUE
    info:
      orgdiv: Department
      orgname: Organization
    address:
        street: Street
        city: City
        postcode: 100190
        state: State
        country: Country
  - number: 2
    corresponding: TRUE
    info:
      orgname: Other Organisation

keywords:
  - key
  - dictionary
  - word

pacs: 
  jel:
    - "D8"
    - "H51"
  msc:
    - "35A01"
    - "65L10"

# Sample for unstructured abstract 
# abstract: |
#   The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications. Authors are advised to check the author instructions for the journal they are submitting to for word limits and if structural elements like subheadings, citations, or equations are permitted.

# Sample for structured abstract
abstract: |
  **Purpose**: The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications. The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations. As a guide the abstract should not exceed 200 words. Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.

  **Methods:** The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications. The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations. As a guide the abstract should not exceed 200 words. Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.

  **Results:** The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications. The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations. As a guide the abstract should not exceed 200 words. Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.

  **Conclusion:** The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications. The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations. As a guide the abstract should not exceed 200 words. Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.}

bibliography: ../Data/references.bib

# header-includes: |
#   %% Per the spinger doc, new theorem styles can be included using built in style, 
#   %% but it seems the don't work so commented below
#   %\theoremstyle{thmstyleone}%
#   \newtheorem{theorem}{Theorem}%  meant for continuous numbers
#   %%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
#   %% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
#   \newtheorem{proposition}[theorem]{Proposition}%
#   %%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.
# 
#   %% \theoremstyle{thmstyletwo}%
#   \theoremstyle{remark}
#   \newtheorem{example}{Example}%
#   \newtheorem{remark}{Remark}%
# 
#   %% \theoremstyle{thmstylethree}%
#   \theoremstyle{definition}
#   \newtheorem{definition}{Definition}%
params:
  X: NULL
# output: 
#   bookdown::pdf_book: 
#     base_format: rticles::springer_article # rticles::arxiv_article
#     includes:
#       in_header: preamble.tex
output: rticles::springer_article
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage[normalem]{ulem}
- \usepackage{threeparttablex}
- \usepackage{makecell}
---

```{r echo = F}
## NOTE: EDITED TEMPLATE FILE To Add rotating and multirow packages as per:
# https://stackoverflow.com/questions/31503418/how-to-add-a-latex-package-to-r-journal-template-from-rticle-package-in-r
library(ready4show)
options(tinytex.verbose = TRUE)
library(xtable)
options(xtable.floating = FALSE)
options(xtable.timestamp = "")
```
TEST

### 2023-08-14 Markdown/Manuscript/Parent_PDF/Test.tex
updated intro

--- 2023-08-14 Markdown/Manuscript/Parent_PDF/Springer/Example/Example.tex
@@
 
-%% Per the spinger doc, new theorem styles can be included using built in style, 
-%% but it seems the don't work so commented below
-%\theoremstyle{thmstyleone}%
-\newtheorem{theorem}{Theorem}%  meant for continuous numbers
-%%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
-%% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
-\newtheorem{proposition}[theorem]{Proposition}%
-%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.
-
-%% \theoremstyle{thmstyletwo}%
-\theoremstyle{remark}
-\newtheorem{example}{Example}%
-\newtheorem{remark}{Remark}%
-
-%% \theoremstyle{thmstylethree}%
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}%
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage[normalem]{ulem}
+\usepackage{threeparttablex}
+\usepackage{makecell}
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
 
@@
 
-\hypertarget{sec1}{%
-\section{Introduction}\label{sec1}}
+TEST
 
-The Introduction section, of referenced text \citet{bib1} expands on the
-background of the work (some overlap with the Abstract is acceptable).
-The introduction should not include subheadings.
-
-Springer Nature does not impose a strict layout as standard however
-authors are advised to check the individual requirements for the journal
-they are planning to submit to as there may be journal-level
-preferences. When preparing your text please also be aware that some
-stylistic choices are not supported in full text XML (publication
-version), including coloured font. These will not be replicated in the
-typeset article if it is accepted.
-
-\hypertarget{sec2}{%
-\section{Results}\label{sec2}}
-
-Sample body text. Sample body text. Sample body text. Sample body text.
-Sample body text. Sample body text. Sample body text. Sample body text.
-
-\hypertarget{sec3}{%
-\section{This is an example for first level head---section
-head}\label{sec3}}
-
-\hypertarget{subsec2}{%
-\subsection{This is an example for second level head---subsection
-head}\label{subsec2}}
-
-\hypertarget{subsubsec2}{%
-\subsubsection{This is an example for third level head---subsubsection
-head}\label{subsubsec2}}
-
-Sample body text. Sample body text. Sample body text. Sample body text.
-Sample body text. Sample body text. Sample body text.
-
-\hypertarget{sec4}{%
-\section{Equations}\label{sec4}}
-
-Equations in \LaTeX~can either be inline or on-a-line by itself
-(``display equations''). For inline equations use the \texttt{\$...\$}
-commands. E.g.: The equation \(H\psi = E \psi\) is written via the
-command \texttt{\$H\ \textbackslash{}psi\ =\ E\ \textbackslash{}psi\$}.
-
-For display equations (with auto generated equation numbers) one can use
-the equation or align environments:
-
-\begin{equation}
-\|\tilde{X}(k)\|^2 \leq\frac{\sum\limits_{i=1}^{p}\left\|\tilde{Y}_i(k)\right\|^2+\sum\limits_{j=1}^{q}\left\|\tilde{Z}_j(k)\right\|^2 }{p+q}.\label{eq1}
-\end{equation}
-
-where, \begin{align}
-D_\mu &=  \partial_\mu - ig \frac{\lambda^a}{2} A^a_\mu \nonumber \\
-F^a_{\mu\nu} &= \partial_\mu A^a_\nu - \partial_\nu A^a_\mu + g f^{abc} A^b_\mu A^a_\nu \label{eq2}
-\end{align}
-
-Notice the use of \texttt{\textbackslash{}nonumber} in the align
-environment at the end of each line, except the last, so as not to
-produce equation numbers on lines where no equation numbers are
-required. The \texttt{\textbackslash{}label\{\}} command should only be
-used at the last line of an align environment where
-\texttt{\textbackslash{}nonumber} is not used.
-
-\begin{equation}
-Y_\infty = \left( \frac{m}{\textrm{GeV}} \right)^{-3}
-    \left[ 1 + \frac{3 \ln(m/\textrm{GeV})}{15}
-    + \frac{\ln(c_2/5)}{15} \right]
-\end{equation}
-
-The class file also supports the use of
-\texttt{\textbackslash{}mathbb\{\}},
-\texttt{\textbackslash{}mathscr\{\}} and
-\texttt{\textbackslash{}mathcal\{\}} commands. As such
-\texttt{\textbackslash{}mathbb\{R\}},
-\texttt{\textbackslash{}mathscr\{R\}} and
-\texttt{\textbackslash{}mathcal\{R\}} produces \(\mathbb{R}\),
-\(\mathscr{R}\) and \(\mathcal{R}\) respectively (refer
-Subsubsection~\ref{subsubsec2}).
-
-\hypertarget{sec5}{%
-\section{Tables}\label{sec5}}
-
-Tables can be inserted via the normal \texttt{knitr::kable()} function
-or other table-generating packages.
-
-\begin{table}
-
-\caption{\label{tab:tab1}Caption text}
-\centering
-\begin{tabular}[t]{r|r}
-\hline
-temperature & pressure\\
-\hline
-0 & 0.0002\\
-\hline
-20 & 0.0012\\
-\hline
-40 & 0.0060\\
-\hline
-60 & 0.0300\\
-\hline
-80 & 0.0900\\
-\hline
-100 & 0.2700\\
-\hline
-\end{tabular}
-\end{table}
-
-Tables can also be inserted via the normal table and tabular
-environment. To put footnotes inside tables you should use
-\texttt{\textbackslash{}footnotetext{[}{]}\{...\}} tag. The footnote
-appears just below the table itself (refer
-Tables\textasciitilde{}\ref{tab1} and \ref{tab2}). For the corresponding
-footnotemark use \texttt{\textbackslash{}footnotemark{[}...{]}}
-
-\begin{table}[h]
-\caption{Caption text}\label{tab1}%
-\begin{tabular}{@{}llll@{}}
-\toprule
-Column 1 & Column 2  & Column 3 & Column 4\\
-\midrule
-row 1    & data 1   & data 2  & data 3  \\
-row 2    & data 4   & data 5\footnotemark[1]  & data 6  \\
-row 3    & data 7   & data 8  & data 9\footnotemark[2]  \\
-\botrule
-\end{tabular}
-\footnotetext{Source: This is an example of table footnote. This is an example of table footnote.}
-\footnotetext[1]{Example for a first table footnote. This is an example of table footnote.}
-\footnotetext[2]{Example for a second table footnote. This is an example of table footnote.}
-\end{table}
-
-\noindent The input format for the above table is as follows:
-
-\begin{verbatim}
-\begin{table}[<placement-specifier>]
-\caption{<table-caption>}\label{<table-label>}%
-\begin{tabular}{@{}llll@{}}
-\toprule
-Column 1 & Column 2 & Column 3 & Column 4\\
-\midrule
-row 1 & data 1 & data 2  & data 3 \\
-row 2 & data 4 & data 5\footnotemark[1] & data 6 \\
-row 3 & data 7 & data 8  & data 9\footnotemark[2]\\
-\botrule
-\end{tabular}
-\footnotetext{Source: This is an example of table footnote.
-This is an example of table footnote.}
-\footnotetext[1]{Example for a first table footnote.
-This is an example of table footnote.}
-\footnotetext[2]{Example for a second table footnote.
-This is an example of table footnote.}
-\end{table}
-\end{verbatim}
-
-\begin{table}[h]
-\caption{Example of a lengthy table which is set to full textwidth}\label{tab2}
-\begin{tabular*}{\textwidth}{@{\extracolsep\fill}lcccccc}
-\toprule%
-& \multicolumn{3}{@{}c@{}}{Element 1\footnotemark[1]} & \multicolumn{3}{@{}c@{}}{Element 2\footnotemark[2]} \\\cmidrule{2-4}\cmidrule{5-7}%
-Project & Energy & $\sigma_{calc}$ & $\sigma_{expt}$ & Energy & $\sigma_{calc}$ & $\sigma_{expt}$ \\
-\midrule
-Element 3  & 990 A & 1168 & $1547\pm12$ & 780 A & 1166 & $1239\pm100$\\
-Element 4  & 500 A & 961  & $922\pm10$  & 900 A & 1268 & $1092\pm40$\\
-\botrule
-\end{tabular*}
-\footnotetext{Note: This is an example of table footnote.
-This is an example of table footnote this is an example of table footnote this is an example of~table footnote this is an example of table footnote.}
-\footnotetext[1]{Example for a first table footnote.}
-\footnotetext[2]{Example for a second table footnote.}
-\end{table}
-
-\vfill\eject
-
-In case of double column layout, tables which do not fit in single
-column width should be set to full text width. For this, you need to use
-\texttt{\textbackslash{}begin\{table*\}} \texttt{...}
-\texttt{\textbackslash{}end\{table*\}} instead of
-\texttt{\textbackslash{}begin\{table\}} \texttt{...}
-\texttt{\textbackslash{}end\{table\}} environment. Lengthy tables which
-do not fit in textwidth should be set as rotated table. For this, you
-need to use \texttt{\textbackslash{}begin\{sidewaystable\}} \texttt{...}
-\texttt{\textbackslash{}end\{sidewaystable\}} instead of
-\texttt{\textbackslash{}begin\{table*\}} \texttt{...}
-\texttt{\textbackslash{}end\{table*\}} environment. This environment
-puts tables rotated to single column width. For tables rotated to double
-column width, use \texttt{\textbackslash{}begin\{sidewaystable*\}}
-\texttt{...} \texttt{\textbackslash{}end\{sidewaystable*\}}.
-
-\begin{sidewaystable}
-\caption{Tables which are too long to fit, should be written using the "sidewaystable" environment as shown here}\label{tab3}
-\begin{tabular*}{\textheight}{@{\extracolsep\fill}lcccccc}
-\toprule%
-& \multicolumn{3}{@{}c@{}}{Element 1\footnotemark[1]}& \multicolumn{3}{@{}c@{}}{Element\footnotemark[2]} \\\cmidrule{2-4}\cmidrule{5-7}%
-Projectile & Energy & $\sigma_{calc}$ & $\sigma_{expt}$ & Energy & $\sigma_{calc}$ & $\sigma_{expt}$ \\
-\midrule
-Element 3 & 990 A & 1168 & $1547\pm12$ & 780 A & 1166 & $1239\pm100$ \\
-Element 4 & 500 A & 961  & $922\pm10$  & 900 A & 1268 & $1092\pm40$ \\
-Element 5 & 990 A & 1168 & $1547\pm12$ & 780 A & 1166 & $1239\pm100$ \\
-Element 6 & 500 A & 961  & $922\pm10$  & 900 A & 1268 & $1092\pm40$ \\
-\botrule
-\end{tabular*}
-\footnotetext{Note: This is an example of table footnote this is an example of table footnote this is an example of table footnote this is an example of~table footnote this is an example of table footnote.}
-\footnotetext[1]{This is an example of table footnote.}
-\end{sidewaystable}
-
-\hypertarget{sec6}{%
-\section{Figures}\label{sec6}}
-
-As per the \LaTeX~standards you need to use eps images for
-\LaTeX~compilation and \texttt{pdf/jpg/png} images for \texttt{PDFLaTeX}
-compilation. Use the \texttt{dev} knitr option to use the approrpate
-format. This is one of the major difference between \LaTeX~and
-\texttt{PDFLaTeX}. Each image should be from a single input .eps/vector
-image file. Avoid using subfigures. The command for inserting images for
-\LaTeX~and \texttt{PDFLaTeX} can be generalized. The package used to
-insert images in \texttt{LaTeX/PDFLaTeX} is the graphicx package.
-Figures can be inserted via the normal figure environment as shown in
-the below example:
-
-\begin{figure}
-\includegraphics{Example_files/figure-latex/fig1-1} \caption{This is an example of a caption}\label{fig:fig1}
-\end{figure}
-
-\hypertarget{sec7}{%
-\section{Algorithms, Program codes and Listings}\label{sec7}}
-
-Packages \texttt{algorithm}, \texttt{algorithmicx} and
-\texttt{algpseudocode} are used for setting algorithms in \LaTeX~using
-the format:
-
-\begin{verbatim}
-\begin{algorithm}
-\caption{<alg-caption>}\label{<alg-label>}
-\begin{algorithmic}[1]
-. . .
-\end{algorithmic}
-\end{algorithm}
-\end{verbatim}
-
-You may refer above listed package documentations for more details
-before setting \texttt{algorithm} environment. For program codes, the
-``program'' package is required and the command to be used is
-\texttt{\textbackslash{}begin\{program\}} \texttt{...}
-\texttt{\textbackslash{}end\{program\}}. A fast exponentiation
-procedure:
-
-Similarly, for \texttt{listings}, use the \texttt{listings} package.
-\texttt{\textbackslash{}begin\{lstlisting\}} \texttt{...}
-\texttt{\textbackslash{}end\{lstlisting\}} is used to set environments
-similar to \texttt{verbatim} environment. Refer to the
-\texttt{lstlisting} package documentation for more details.
-
-A fast exponentiation procedure:
-
-\lstset{texcl=true,basicstyle=\small\sf,commentstyle=\small\rm,mathescape=true,escapeinside={(*}{*)}}
-\begin{lstlisting}
-begin
-  for $i:=1$ to $10$ step $1$ do
-      expt($2,i$);  
-      newline() od                (*\textrm{Comments will be set flush to the right margin}*)
-where
-proc expt($x,n$) $\equiv$
-  $z:=1$;
-  do if $n=0$ then exit fi;
-     do if odd($n$) then exit fi;                 
-        comment: (*\textrm{This is a comment statement;}*)
-        $n:=n/2$; $x:=x*x$ od;
-     { $n>0$ };
-     $n:=n-1$; $z:=z*x$ od;
-  print($z$). 
-end
-\end{lstlisting}
-
-\begin{algorithm}
-\caption{Calculate $y = x^n$}\label{algo1}
-\begin{algorithmic}[1]
-\Require $n \geq 0 \vee x \neq 0$
-\Ensure $y = x^n$ 
-\State $y \Leftarrow 1$
-\If{$n < 0$}\label{algln2}
-        \State $X \Leftarrow 1 / x$
-        \State $N \Leftarrow -n$
-\Else
-        \State $X \Leftarrow x$
-        \State $N \Leftarrow n$
-\EndIf
-\While{$N \neq 0$}
-        \If{$N$ is even}
-            \State $X \Leftarrow X \times X$
-            \State $N \Leftarrow N / 2$
-        \Else[$N$ is odd]
-            \State $y \Leftarrow y \times X$
-            \State $N \Leftarrow N - 1$
-        \EndIf
-\EndWhile
-\end{algorithmic}
-\end{algorithm}
-
-\begin{minipage}{\hsize}
-
-\lstset{frame=single,framexleftmargin=-1pt,framexrightmargin=-17pt,framesep=12pt,linewidth=0.98\textwidth,language=pascal}
-
-\begin{lstlisting}
-for i:=maxint to 0 do begin \{ do nothing \} end; Write(`Case
-insensitive'); Write(`Pascal keywords.');
-
-\end{lstlisting}
-
-\end{minipage}
-
-\hypertarget{sec8}{%
-\section{Cross referencing}\label{sec8}}
-
-Figures and tables are labeled with a prefix (fig or tab, respectively)
-plus the chunk label. Other environments such as equation and align can
-be labelled via the \texttt{\textbackslash{}label\{\#label\}} command
-inside or just below the \texttt{\textbackslash{}caption\{\}} command.
-You can then use the label for cross-reference. As an example, consider
-the chunk label declared for Figure~\ref{fig:fig1} which is fig1. To
-cross-reference it, use the command
-\texttt{Figure\ \textbackslash{}ref\{fig:fig1\}}, for which it comes up
-as ``Figure~\ref{fig:fig1}''.
-
-To reference line numbers in an algorithm, consider the label declared
-for the line number 2 of Algorithm~\ref{algo1} is
-\texttt{\textbackslash{}label\{algln2\}}. To cross-reference it, use the
-command \texttt{\textbackslash{}ref\{algln2\}} for which it comes up as
-line~\ref{algln2} of Algorithm~\ref{algo1}.
-
-\hypertarget{subsec7}{%
-\subsection{Details on reference citations}\label{subsec7}}
-
-For citations of references, use~\citet{bib1} or \citep{bib2}.
-
-\hypertarget{sec10}{%
-\section{Examples for theorem like environments}\label{sec10}}
-
-The documentclass for springer \texttt{sn-jnl.cls} contains 3 styling
-that you can use to set new default for theorems and proofs type
-
-\begin{description}
-\item[\texttt{thmstyleone}]
-Numbered, theorem head in bold font and theorem text in italic style
-\item[\texttt{thmstyletwo}]
-Numbered, theorem head in roman font and theorem text in italic style
-\item[\texttt{thmstylethree}]
-Numbered, theorem head in bold font and theorem text in roman style
-\end{description}
-
-For mathematics journals, theorem styles can be included as shown in the
-following examples.
-
-\begin{theorem}
-Example theorem text. Example theorem text. Example theorem text.
-Example theorem text. Example theorem text. Example theorem text.
-Example theorem text. Example theorem text. Example theorem text.
-Example theorem text. Example theorem text.
-
-\end{theorem}
-
-To add labels and subheadings, use LaTeX notation
-
-\begin{theorem}[Theorem subhead]\label{thm1}
-Example theorem text. Example theorem text. Example theorem text.
-Example theorem text. Example theorem text. Example theorem text.
-Example theorem text. Example theorem text. Example theorem text.
-Example theorem text. Example theorem text.
-
-\end{theorem}
-
-Other environments are proposition, example, remark, definition, proof
-and quote
-
-Sample body text. Sample body text. Sample body text. Sample body text.
-Sample body text. Sample body text. Sample body text. Sample body text.
-
-\begin{proposition}
-Example proposition text. Example proposition text. Example proposition
-text. Example proposition text. Example proposition text. Example
-proposition text. Example proposition text. Example proposition text.
-Example proposition text. Example proposition text.
-
-\end{proposition}
-
-Sample body text. Sample body text. Sample body text. Sample body text.
-Sample body text. Sample body text. Sample body text. Sample body text.
-
-\begin{example}
-Phasellus adipiscing semper elit. Proin fermentum massa ac quam. Sed
-diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas
-lacinia. Nam ipsum ligula, eleifend at, accumsan nec, suscipit a, ipsum.
-Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem.
-
-\end{example}
-
-Sample body text. Sample body text. Sample body text. Sample body text.
-Sample body text. Sample body text. Sample body text. Sample body text.
-
-\begin{remark}
-Phasellus adipiscing semper elit. Proin fermentum massa ac quam. Sed
-diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas
-lacinia. Nam ipsum ligula, eleifend at, accumsan nec, suscipit a, ipsum.
-Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem.
-
-\end{remark}
-
-Sample body text. Sample body text. Sample body text. Sample body text.
-Sample body text. Sample body text. Sample body text. Sample body text.
-
-\begin{definition}[Definition sub head]
-Example definition text. Example definition text. Example definition
-text. Example definition text. Example definition text. Example
-definition text. Example definition text. Example definition text.
-
-\end{definition}
-
-Additionally a predefined ``proof'' environment is available. This
-prints a ``Proof'' head in italic font style and the ``body text'' in
-roman font style with an open square at the end of each proof
-environment.
-
-\begin{proof}
-Example for proof text. Example for proof text. Example for proof text.
-Example for proof text. Example for proof text. Example for proof text.
-Example for proof text. Example for proof text. Example for proof text.
-Example for proof text.
-
-\end{proof}
-
-Sample body text. Sample body text. Sample body text. Sample body text.
-Sample body text. Sample body text. Sample body text. Sample body text.
-
-\hypertarget{sec11}{%
-\section{Methods}\label{sec11}}
-
-Topical subheadings are allowed. Authors must ensure that their Methods
-section includes adequate experimental and characterization data
-necessary for others in the field to reproduce their work. Authors are
-encouraged to include RIIDs where appropriate.
-
-\textbf{Ethical approval declarations} (only required where applicable)
-Any article reporting experiment/s carried out on
-(i)\textasciitilde live vertebrate (or higher invertebrates),
-(ii)\textasciitilde humans or (iii)\textasciitilde human samples must
-include an unambiguous statement within the methods section that meets
-the following requirements:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\item
-  Approval: a statement which confirms that all experimental protocols
-  were approved by a named institutional and/or licensing committee.
-  Please identify the approving body in the methods section
-\item
-  Accordance: a statement explicitly saying that the methods were
-  carried out in accordance with the relevant guidelines and regulations
-\item
-  Informed consent (for experiments involving humans or human tissue
-  samples): include a statement confirming that informed consent was
-  obtained from all participants and/or their legal guardian/s
-\end{enumerate}
-
-If your manuscript includes potentially identifying patient/participant
-information, or if it describes human transplantation research, or if it
-reports results of a clinical trial then additional information will be
-required. Please visit
-(\url{https://www.nature.com/nature-research/editorial-policies}) for
-Nature Portfolio journals,
-(\url{https://www.springer.com/gp/authors-editors/journal-author/journal-author-helpdesk/publishing-ethics/14214})
-for Springer Nature journals, or
-(\url{https://www.biomedcentral.com/getpublished/editorial-policies/\#ethics+and+consent})
-for BMC.
-
-\hypertarget{sec12}{%
-\section{Discussion}\label{sec12}}
-
-Discussions should be brief and focused. In some disciplines use of
-Discussion or `Conclusion' is interchangeable. It is not mandatory to
-use both. Some journals prefer a section `Results and Discussion'
-followed by a section `Conclusion'. Please refer to Journal-level
-guidance for any specific requirements.
-
-\hypertarget{sec13}{%
-\section{Conclusion}\label{sec13}}
-
-Conclusions may be used to restate your hypothesis or research question,
-restate your major findings, explain the relevance and the added value
-of your work, highlight any limitations of your study, describe future
-directions for research and recommendations.
-
-In some disciplines use of Discussion or `Conclusion' is
-interchangeable. It is not mandatory to use both. Please refer to
-Journal-level guidance for any specific requirements.
-
-\backmatter
-
-\bmhead{Supplementary information}
-
-If your article has accompanying supplementary file/s please state so
-here.
-
-Authors reporting data from electrophoretic gels and blots should supply
-the full unprocessed scans for key as part of their Supplementary
-information. This may be requested by the editorial team/s if it is
-missing.
-
-Please refer to Journal-level guidance for any specific requirements.
-
-\bmhead{Acknowledgments}
-
-Acknowledgments are not compulsory. Where included they should be brief.
-Grant or contribution numbers may be acknowledged.
-
-Please refer to Journal-level guidance for any specific requirements.
-
-\hypertarget{declarations}{%
-\section*{Declarations}\label{declarations}}
-\addcontentsline{toc}{section}{Declarations}
-
-Some journals require declarations to be submitted in a standardised
-format. Please check the Instructions for Authors of the journal to
-which you are submitting to see if you need to complete this section. If
-yes, your manuscript must contain the following sections under the
-heading `Declarations':
-
-\begin{itemize}
-\tightlist
-\item
-  Funding
-\item
-  Conflict of interest/Competing interests (check journal-specific
-  guidelines for which heading to use)
-\item
-  Ethics approval
-\item
-  Consent to participate
-\item
-  Consent for publication
-\item
-  Availability of data and materials
-\item
-  Code availability
-\item
-  Authors' contributions
-\end{itemize}
-
-\noindent If any of the sections are not relevant to your manuscript,
-please include the heading and write `Not applicable' for that section.
-
-\begin{flushleft}
-Editorial Policies for:
-
-\noindent Springer journals and proceedings:
-\url{https://www.springer.com/gp/editorial-policies}
-
-\noindent Nature Portfolio journals:
-\url{https://www.nature.com/nature-research/editorial-policies}
-
-\noindent \textit{Scientific Reports}:
-\url{https://www.nature.com/srep/journal-policies/editorial-policies}
-
-\noindent BMC journals:
-\url{https://www.biomedcentral.com/getpublished/editorial-policies}
-
-\end{flushleft}
-
-\begin{appendices}
-
-\hypertarget{secA1}{%
-\section{Section title of first appendix}\label{secA1}}
-
-An appendix contains supplementary information that is not an essential
-part of the text itself but which may be helpful in providing a more
-comprehensive understanding of the research problem or it is information
-that is too cumbersome to be included in the body of the paper.
-
-For submissions to Nature Portfolio Journals please use the heading
-``Extended Data''.
-
-\end{appendices}
-
-\bibliography{bibliography.bib}
+\bibliography{../Data/references.bib}
 

### 2023-08-14 setup.R

@@ -54,6 +54,8 @@ X <- renewSlot(X,
                  args_ls
                  }
                )
+X@tables_in_body_lgl <- F
+#X@rmd_fl_nms_ls$PDF <- "TEST"#"Parent_PDF"
 # authorData(X) # Update ready4show so that default is to not overwrite Child_RMDs / only overwrite header and abstract
 # Pause for interactivity
 # Make manual edits of Markdown files
@@ -62,6 +64,6 @@ authorReport(X, consent_1L_chr = "Y")
 ##
 Y <- X
 Y@outp_formats_chr <- "Word"
-Y@tables_in_body_lgl <- F
+# Y@tables_in_body_lgl <- F
 authorReport(Y)
 # Pause for interactivity

### 2023-08-15 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
working way through frameworks

@@
 
-We considered prior literature on modelling practice, our own professional experience and the needs of our youth mental health modelling project, to identify core ethical responsibilities of CHEM developers, attributes of CHEMs that support fulfilment of these responsibilities and criteria against which these attributes can be assessed.
+We considered prior literature on modelling practice, our own professional experience and the needs of modelling projects we are undertaking to identify some core ethical responsibilities of CHEM developers, attributes of CHEMs that can support fulfillment of these responsibilities and criteria against which these attributes can be assessed.
 
-## Ethical responsibilities of CHEM developers 
+### Ethical responsibilities of CHEM developers 
 Health economists have ethical responsibilities relating to the social acceptability, adequacy for purpose and beneficial impact of CHEMs.
@@
 
-##	Sssessing ethical CHEM implementations
+### CHEM attributes associated with ethical modelling practice
 The acceptability, adequacy and public benefit responsibilities of health economic modellers are easier to state than to measure.
@@
 
-**Transparency** has been  as a core identified as a core feature of ethical public health modelling practice [@10.3389/fpubh.2017.00068].
+**Transparency** has been identified as a core feature of ethical public health modelling practice [@10.3389/fpubh.2017.00068].
 Guidance on transparency in health economic modelling recommended that model code and data should be clearly documented, potentially with different versions for technical and non-technical users [@Eddy2012].
@@
 This issue can be addressed by use of online repository services such as GitHub [@github2007], that provide citation tools and can transparently record all individual code contributions to a modelling project over its lifecycle.
-
-The **transparency** of a CHEM implementation can be assessed against the criteria:
-
--	T1: All model code, non-confidential data and testing procedures and outcomes are available in open access repositories.
-
--	T2: It is easy to see who developed and tested each part of the CHEM and to identify the modelling team’s assumptions, judgments and theories about CHEM development and use.
 
@@
 <!-- are relatively easier to selectively modify. -->
-The **reusability** of a CHEM implementation can be assessed against the criteria:
 
--	R1: Model code and data are implemented to facilitate both generalisability and transferability.
-
--	R2: Terms of use allow anyone to reuse model code and non-confidential data, in whole or in part, without charge, and for purposes that include the creation of derivative works.
-
-Models should be **updatable** so that they remain valid for longer, evolving as new evidence emerges and the systems being modelled change [@Jenkins2021; @@garcia2021cost].
+Models should be **updatable** so that they remain valid for longer, evolving as new evidence emerges and the systems being modelled change [@Jenkins2021; @garcia2021cost].
 Ensuring that a model is regularly reviewed to identify and implement required improvements is a recommended defense against model validity decay [@calder2018computational].
@@
 
-The **updatability** of a CHEM implementation can be assessed against the criteria:
+###	Assessment criteria
+For each model attribute, we identified only assessment criteria that can be met with existing technical solutions and which therefore have the potential to be facilitated by software frameworks.
 
--	U1: Technical infrastructure is in place to support sustained development, testing, maintenance and version control of a model in collaboration with model users.
+How **transparent** a CHEM is can be assessed against the criteria:
 
--	U2: Each new release of a model is retested, with changes implemented to minimize disruptions for existing model users.
+-	**T1**: All model code, non-confidential data and testing procedures and outcomes are available in open access repositories.
+
+-	**T2**: It is easy to see who developed and tested each part of the CHEM and to identify the modelling team’s assumptions, judgments and theories about CHEM development and use.
+
+How **reusable** a CHEM is can be assessed against the criteria:
+
+-	**R1**: Model code and data are implemented to facilitate both generalisability and transferability.
+
+-	**R2**: Terms of use allow anyone to reuse model code and non-confidential data, in whole or in part, without charge, and for purposes that include the creation of derivative works.
+
+How **updatable** a CHEM is can be assessed against the criteria:
+
+-	**U1**: Technical infrastructure is in place to support version control and collaboration with model users in the maintenance of a model.
+
+-	**U2**: Each new release of a model is retested, with changes implemented to minimize disruptions for existing model users.

### 2023-08-15 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
working way through frameworks

@@
 A health economic model should be capable of being described using words and figures (a conceptual model), equations (a mathematical model) and computer code (a computational model).
-Health economic scientific manuscripts typically describe a model using its conceptual and mathematical representations but report results that have been generated by applying the computational model.
+Health economic scientific manuscripts typically describe a model using its conceptual and mathematical representations but report results that have been generated by its computational representation (i.e., through execution of a computer program that applies the computational model to selected input data).
 The conceptual, mathematical and computational representations of a model are assumed to be isomorphic.
-Independent assessment of the validity of this assumption depends in part on the approach taken to computational model implementation and dissemination.
+Independent assessment of the validity of this assumption depends in part on how a computational model has been authored and shared.
 
@@
 Computational health economic models (CHEMs) can be implemented using specialized commercial software or authored as software development projects in an open-source programming language such as Python [@python2009] or R [@RCORE2022].
-Advantages of commercial modelling tools include simplicity and ease of use, but a software development approach may facilitate computational models that are more transparent, reusable and adaptable [@incerti2019r].
-The most appropriate approach for a specific CHEM project may depend on both the desired features of the model being developed and the resource and time constraints within which the project needs to be delivered (see Table \@ref(tab:proscons)).
-Although health economists report strong interest in making CHEMs more transparent and accessible [@Pouwels2022], open-source CHEMs remain rare [@Feenstra2022; @Emerson2019].
+Advantages of commercial modelling tools include simplicity and ease of use, but an open-source software development approach may facilitate computational models that are more transparent, reusable and updatable [@incerti2019r; @Pouwels2022].
+The most appropriate implementation choice for a specific CHEM project may depend on both desired model features and the resource and time constraints within which the project needs to be delivered (see Table \@ref(tab:proscons)).
 
@@
 <!-- When making choices about how to implement this health economic model computationally, we wished to facilitate ethical development and use. -->
-A high-level software framework using R has previously been developed with the primary aim of improving the transparency of CHEMs [@alarid2019need].
-Novel software frameworks may be necessary to facilitate CHEM implementations that meet broader ethical criteria.
+A high-level software framework for implementing open-source CHEMs in R has previously been developed with the primary aim of improving model transparency [@alarid2019need].
+However, open-source CHEMs remain rare [@Feenstra2022; @Emerson2019], and novel software frameworks may be necessary help health economists fulfill a broader set of ethical modelling practice requirements.
 The ethical responsibilities of computational modellers are often poorly understood and inadequately fulfilled [@10.3389/fpubh.2017.00068; @pliakos2021ethics; @thompson2022escape; @calder2018computational].
-Guidance on developing, selecting and using software frameworks for ethical CHEM implementations is scarce.
+Ideally, a novel software framework for CHEMs would also address some of the barriers preventing health economists adopting open-source approaches.
+The main barriers identified in a 2020 survey of health economists concern updating models, legal considerations, transferring model data, the platforms or languages in which models are developed, the level of public access required, lack of interest from decision-makers, model generalisability and confidentiality and security considerations [@Pouwels2022].
+
+<!-- Guidance on developing, selecting and using software frameworks for ethical CHEM implementations is scarce. -->
 

### 2023-08-15 setup.R

@@ -65,5 +65,5 @@ authorReport(X, consent_1L_chr = "Y")
 Y <- X
 Y@outp_formats_chr <- "Word"
 # Y@tables_in_body_lgl <- F
-authorReport(Y)
+authorReport(Y, consent_1L_chr = "Y")
 # Pause for interactivity

### 2023-08-15 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
working my way through supervisors comments
up to framework

@@
 
-##	Model documentation 
-We developed a versioned model documentation website (www.ready4-dev.com) that provides guidance to model developers on how to use and contribute improvements to the ready4 software framework and model.
-The documentation website was developed using the Hugo framework [@hugo_2023], Docsy theme [@docsy_2023] and Algolia DocSearch [@algoliadocsearch_2023] and is hosted using the Netlify [@netlify_2023] service.
-We used functions from the ready4 R library to partially automate website updates relating to available CHEM modules, datasets and analysis programs.
-We linked our Netlify account to our GitHub organisation so that the project website would automatically update whenever the source code in its GitHub repository was edited.
-
 \blandscape
 
-```{r, child = child_docs_ls$three, echo=FALSE}
+```{r, child = child_docs_ls$four, echo=FALSE}
 ```

### 2023-08-15 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
up to framework

@@
 
-To support the development of CHEMs that meet TRU assessment criteria, we have created a prototype software framework called ready4.
-We have designed this framework to enable ethical computational implementations of health economic models that are both open-source (for transparency and reusability) and modular (for reusability and updatability).
+To support the development of CHEMs that meet TRU assessment criteria, we have created a prototype software framework called ready4 that works within the popular open-source programming language R [@RCORE2022].
+The ready4 software framework is implemented as a combination of R code libraries and online services and is supported by a documentation website.
+<!-- We have designed this framework to enable ethical computational implementations of health economic models that are both open-source (for transparency and reusability) and modular (for reusability and updatability).
 The framework aims to support the standardization and interoperability that are core enablers of implementing a modular and open source approaches.
-Model modules need to be able to share inputs and outputs with each other and to be run as independent models [@barros2023empowering], even when these modules are authored by different teams.
-
-## 	Framework libraries 
-To work within the popular open-source programming language R [@RCORE2022], the ready4 software framework is implemented as R code libraries.
-
-The R language supports functional and object-oriented programming paradigms [@10.1214/13-STS452].
-Both these paradigms are used in the ready4 framework to provide tools for authoring CHEMs, supplying those CHEMs with data and using CHEMs to implement reproducible modelling analyses.
-<!-- Each CHEM module authored with the ready4 framework will include both a data structure (specifying the required properties of data that can validly be supplied to a module) and a set of algorithms (specifying the operations that can be performed on data contained in a module instance).
 -->
 
-As R is an open source language, each new R library typically depends on a number of other R libraries that have been written by third parties.
-As the number of third party dependencies of an R library grows so does the fragility of that library (e.g.
+### R libraries 
+A library in the R language will typically depend on multiple other R libraries, each of which may have different authors.
+As the number of third-party dependencies of an R library grows so does the fragility of that library (e.g.
 the library may cease to work as intended due to changes in one of its dependency libraries).
 To reduce the fragility of our framework we implemented it as multiple R libraries rather than one R library.
-In total we authored six novel R libraries to implement the ready4 framework, all of which have distinct purposes and depend on have unique third-party R library dependencies (Table \@ref(tab:cpkgs)).
-<!-- development version -->
+In total we authored six novel R libraries to implement the ready4 framework, all of which have distinct purposes and dependencies (Table \@ref(tab:cpkgs)).
 
-The foundational framework library, called ready4, defines a template module data structure (using R’s S4 class system) from which all CHEM module data structures will be created and a novel syntax that enable module algorithms to be consistently named.
-The ready4 library also contains tools for retrieving web based information on model modules, datasets and analysis programs authored with the framework and for partially automating updates to a project documentation website.
+One framework library provides the **foundation** for implementing CHEMs that are modular and open-source.
+Modular models are comprised of modules that are able to share inputs and outputs with each other and to be run as independent models [@barros2023empowering].
+To be implemented as open-source projects modules authored by different teams must be interoperable.
+The foundation library facilitates these objectives by defining a template module data structure (using R’s S4 class system) from which all model module data structures will be created and a novel syntax that enable module algorithms to be consistently named.
+The foundation library also contains tools for retrieving web-based information on model modules, datasets and analysis programs authored with the framework and for partially automating updates to a project documentation website.
 
-Three R libraries are designed to help standardize workflows for authoring, documenting, testing and disseminating new model modules.
-The ready4pack library is designed to integrate with GitHub and provides tools for authoring model modules and desseminating them as themed bundles in R libraries libraries that are:
+Three framework libraries are designed to help standardize workflows for **authoring modules**.
+The R language supports functional and object-oriented programming paradigms [@10.1214/13-STS452].
+Both these paradigms are used in the ready4 framework, each facilitated by a dedicated authoring library.
+The first module authoring library contains tools for writing functions in a consistent house style and then using the resulting standardised naming conventions to automatically generate basic documentation for each function.
+The second module authoring library contains tools to help streamline and standardise the authoring of module data structures using the framework's module template and for associating methods (a special type of function) with each module.
+The second module authoring library also supports the automatic generation of basic documentation for each new module.
+The third module authoring library provides tools for disseminating themed bundles of model modules as R libraries that are:
 
--	documented (with a website, a PDF manual itemising selected contents and a PDF manual itemising all contents);
+-	documented (with a website and PDF manuals);
 
@@
 
--	quality assured (each update triggers continuous integration workflows, including any acceptance and unit tests created by module library authors).
+-	quality assured (each update triggers GitHub continuous integration workflows, including any acceptance and unit tests created by module library authors).
 
-The ready4pack library depends on two other module authoring libraries.
-<!-- MOVED CONTENT -->The ready4fun library contains tools for authoring functions in a consistent house style that automatically generates basic documentation for each function.
-Functions to implement model algorithms can be associated with a module via a special type of function called a method.
-Tools from the ready4class library can help streamline and standardise the authoring of module data structures and their associated methods and to automatically generate basic documentation for each module.
+<!-- Functions to implement model algorithms can be associated with a module via . -->
 
-The ready4use library contains tools for supplying model modules with data stored in online repositories (hosted on a Dataverse installation or on GitHub), labelling these datasets and then sharing them via online repositories.
-The ready4show library contains tools to help author R Markdown programs that combine model modules and datasets to undertake analyses.
-These programs are either self-documenting (code is easy to understand and integrated with plain English explanations of what it does) or trigger the creation of separate documents (e.g.
+<!-- to provide tools for authoring CHEMs, supplying those CHEMs with data and using CHEMs to implement reproducible modelling analyses. -->
+
+<!-- The ready4pack library depends on two other module authoring libraries. <!-- MOVED CONTENT --> -->
+
+<!-- Each CHEM module authored with the ready4 framework will include both a data structure (specifying the required properties of data that can validly be supplied to a module) and a set of algorithms (specifying the operations that can be performed on data contained in a module instance).
+-->
+
+<!-- development version -->
+
+A library for **authoring datasets** contains tools for supplying model modules with data stored in online repositories (hosted on a Dataverse installation or on GitHub), labelling these datasets and then sharing them via online repositories.
+A library for **authoring analyses** contains tools to help author R Markdown programs that combine model modules and datasets to undertake analyses.
+These analysis programs authored with this library can be either self-documenting (code is easy to understand and integrated with plain English explanations of what it does) or trigger the creation of separate documents (e.g.
 a scientific manuscript).
@@
 
-##	Framework integration with online services 
+###	Online services 
 Our software framework needs to be used in conjunction with a number of online services. 
-To facilitate its application to our youth mental health project, we established and configured accounts with these required services (see Availability of data and materials).
+<!-- To facilitate its application to our youth mental health project, we established and configured accounts with these required services (see Availability of data and materials). -->
 
@@
 To facilitate the creation and hosting of documentation websites, we enabled GitHub Pages in each repository we used for code library development.
+
 We also created a Zenodo community - a collection of permanent, uniquely identified repositories.
@@
 Finally, to manage model datasets, we created a dedicated collection within the Harvard Dataverse installation.
+
+###	Documentation website
+We developed a framework documentation website (www.ready4-dev.com) that provides guidance to model developers on how to use and contribute improvements to the ready4 software framework and models developed with it.
+The documentation website is versioned, which means documentation relating to prior versions of framework software can be archived, retrieved and viewed.
+
+The documentation website was developed using the Hugo framework [@hugo_2023], Docsy theme [@docsy_2023] and Algolia DocSearch [@algoliadocsearch_2023] and is hosted using the Netlify [@netlify_2023] service.
+We used functions from our foundation framework library to partially automate website updates relating to available CHEM modules, datasets and analysis programs.
+We linked our Netlify account to our GitHub organisation so that the project website would automatically update whenever the source code in its GitHub repository was edited.

### 2023-08-15 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
up to framework

@@
 A high-level software framework for implementing open-source CHEMs in R has previously been developed with the primary aim of improving model transparency [@alarid2019need].
-However, open-source CHEMs remain rare [@Feenstra2022; @Emerson2019], and novel software frameworks may be necessary help health economists fulfill a broader set of ethical modelling practice requirements.
+However, open-source CHEMs remain rare [@Feenstra2022; @Emerson2019], and novel software frameworks may be necessary to help health economists fulfill a broader set of ethical modelling practice requirements.
 The ethical responsibilities of computational modellers are often poorly understood and inadequately fulfilled [@10.3389/fpubh.2017.00068; @pliakos2021ethics; @thompson2022escape; @calder2018computational].

### 2023-08-16 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
tweaks to content prior to example

--- 2023-01-31 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
@@
 
-(i) a framework that specifies MOSHEM standards and provides the tools to implement them; and
+(i)	criteria for assessing ethical CHEM implementations;
 
-(ii) the application of that framework to develop and use an initial set of ready4 modules in a utility mapping study.
+(ii) a prototype software framework for the ethical implementation of CHEMs; and
+
+(iii)	use of the software framework to develop an open-source CHEM in youth mental health, with an initial focus on outcome valuation.

### 2023-08-16 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
tweaks to content prior to example

@@
 
-We considered prior literature on modelling practice, our own professional experience and the needs of modelling projects we are undertaking to identify some core ethical responsibilities of CHEM developers, attributes of CHEMs that can support fulfillment of these responsibilities and criteria against which these attributes can be assessed.
+We considered prior literature on modelling practice, our own professional experience and the needs of modelling projects we are undertaking to identify: (i) some core ethical responsibilities of CHEM developers; (ii) attributes of CHEMs that can suggest fulfillment of these responsibilities; and (iii) criteria against which these attributes can be assessed.
 
 ### Ethical responsibilities of CHEM developers 
-Health economists have ethical responsibilities relating to the social acceptability, adequacy for purpose and beneficial impact of CHEMs.
+We suggest that three core ethical responsibilities of health economic modellers are to make **socially acceptable** value judgments in planning a CHEM project, to ensure that implementation of a CHEM is **fit for purpose** and to promote **socially beneficial** use of the CHEM over its release lifecycle.
+There is significant scope for health economists to improve fulfilment of each of these responsibilities.
 
-Misalignment between the values of model developers and those of the population groups affected by decisions based on their models presents significant ethical risks [@thompson2022escape; @duckett2022journey].
-The value judgments of model developers influence the assumptions, selection of model features and standards for evidence that shape the model development process [@HARVARD2020112975].
+Misalignment between the values of computational model developers and those of the population groups affected by decisions based on their models presents significant ethical risks [@thompson2022escape; @duckett2022journey].
+The value judgments of CHEM developers influence the assumptions, selection of model features and standards for evidence that shape the model development process [@HARVARD2020112975].
 These value judgments are rarely made explicit, omissions that may lead to socially unacceptable policy recommendations [@duckett2022journey].
-Key choices about the computational implementation of health economic models depend on these value judgments (see Table \@ref(tab:proscons)) and these choices in turn influence the extent to which model implementations are readily adaptable by third parties with alternative value judgments.
+Ideally, it should be straightforward for CHEMs to be modified to reflect alternative value judgments.
+However, such adaptability depends in part on the approach taken to computational model implementation (see Table \@ref(tab:proscons)).
+
 <!-- For example, to reduce the risk of inequitable policy implementation, it may be important for of a model to predict the benefits of harms of an intervention for different sub-populations [@10.3389/fpubh.2017.00068], but model developers may prefer to allocate a project budget to implementing other model features [@thompson2022escape].
@@
 
-Model developers have duties both to take sufficient care that a model is adequate for the explicit purpose for which it was developed and to provide potential third party users with the means of assessing its adequacy for their proposed purposes [@Erdemir2020; @Feenstra2022; @thompson2019escape; @10.3389/fpubh.2017.00068].
-It is common for health economic models to have serious methodological flaws [@carletto_zanuzzi_sammarco_russo_2020; @WONDER2015467]; insufficient validation [@Ghabri2019; @kolovos2017model; @haji2013model], poor reproducibility [@Jalali2021; @McManus2019; @Bermejo2017]; and undeclared errors [@Radeva2020].
+Computational modellers have duties both to take sufficient care that a computational model is adequate for the explicit purpose for which it was developed and to provide potential third-party users with the means of assessing its adequacy for their proposed purposes [@Erdemir2020; @Feenstra2022; @thompson2019escape; @10.3389/fpubh.2017.00068].
+However, it is common for health economic models to have serious methodological flaws [@carletto_zanuzzi_sammarco_russo_2020; @WONDER2015467]; insufficient validation [@Ghabri2019; @kolovos2017model; @haji2013model], poor reproducibility [@Jalali2021; @McManus2019; @Bermejo2017]; and undeclared errors [@Radeva2020].
 Appropriate computational implementation choices can help address many of these shortcomings, for example by automating quality assurance checks and facilitating manual reviews by third parties.
@@
 A health economic model will have limited public benefit if it not much used, if it is mis-used or when its acceptability and adequacy rapidly decay.
-The scientific goals of generalisability (application without adaptation) and transferability (selective reuse and/or modification of model components) [@RN39] are advanced when models are appropriately reused in new contexts.
-Reuse of models as components of other models can also make model implementation more efficient [@Arnold2010; @garcia2021cost] but the reusability of models is significantly shaped by computational implementation choices such as how model code and data are authored, documented, licensed and disseminated.
+Reuse of CHEMs as components of other models can potentially make model development more efficient [@Arnold2010; @garcia2021cost].
+However, health economic models face challenges related to transferability across jurisdictions [@garcia2021cost] that create barriers to reuse.
+Without ongoing maintenance, a CHEM risks becoming less reliable with time [@garcia2021cost] and is at risk of being deployed for purposes for which it is poorly suited [@calder2018computational].
 Currently, health economic models are rarely implemented computationally in a manner that facilitates routine updates [@Sampson2017], thus limiting the temporal window within which a CHEM can be validly applied.
-Without ongoing maintenance, a CHEM risks becoming less reliable with time [@garcia2021cost] and is at risk of being deployed for purposes for which it is poorly suited [@calder2018computational].
+<!-- Reuse of models as components of other models can also make model implementation more efficient [@Arnold2010; @garcia2021cost] but the reusability of models is significantly shaped by computational implementation choices such as how model code and data are authored, documented, licensed and disseminated.
+-->
+
 <!-- Common barriers to model re-use include commercial and legal considerations [@Feenstra2022; @Pouwels2022], as well as challenges related to model transferability across jurisdictions [@garcia2021cost].
@@
 ### CHEM attributes associated with ethical modelling practice
-The acceptability, adequacy and public benefit responsibilities of health economic modellers are easier to state than to measure.
-We have therefore focused our assessment criteria for ethical modelling practice on measurable attributes of computational model implementations.
-As described in Table \@ref(tab:timelygls),  we believe that implementing CHEMs that are transparent, reusable and updatable (TRU) can enable modellers to meet their ethical obligations.
+The responsibilities of health economic modellers for the planning, implementation and use of CHEMs are easier to state than to measure.
+We have therefore focused our assessment criteria for ethical modelling practice on measurable attributes of CHEMs.
+As described in Table \@ref(tab:timelygls),  we believe that CHEMs that are **transparent**, **reusable** and **updatable** (TRU) suggest that their creators have met a number of core ethical obligations.
 We therefore selected these model attributes to use as the basis for deriving ethical assessment criteria.
@@
 
-**Transparency** has been identified as a core feature of ethical public health modelling practice [@10.3389/fpubh.2017.00068].
+Transparency has been identified as a core feature of ethical public health modelling practice [@10.3389/fpubh.2017.00068].
 Guidance on transparency in health economic modelling recommended that model code and data should be clearly documented, potentially with different versions for technical and non-technical users [@Eddy2012].
@@
 
-Model **reusability** is the second attribute that we identify as being core to ethical CHEM implementations.
+Model reusability is the second attribute that we identify as signaling an ethical CHEM implementation.
 Making a CHEM’s code, data and documentation publicly available is increasingly considered good practice, yet is not sufficient to promote model re-use.
-Writing model algorithms as collections of functions (short, self-contained and reusable software routines that each perform a discrete task), is good scientific computing practice [@Wilson_2017] and facilitates model reuse without adaptation (generalisability).
-To support reuse with adaptation (transferability), computational implementations can store model code and data in distinct files and locations (as opposed to embedding data such as parameter values into source code).
-Transferability can also be advanced through the use of object-oriented programming approaches [@ready4oop2022] that take advantage of the concept of inheritance [@8717448] to allow models to be first duplicated and then selectively modified.
-Generalisability and transferability are further enhanced if computational implementations adopt a modular approach, in which a model is constructed from multiple independently reusable and replaceable sub-models (modules) [@pan2021modular].
+Key concepts in health economic model reuse include generalisability (application without adaptation) and transferability (selective reuse and/or modification of model components) [@RN39].
+Writing model algorithms as collections of functions (short, self-contained and reusable software routines that each perform a discrete task), is good scientific computing practice [@Wilson_2017] and facilitates model generalisability.
+Transferability is promoted by computational implementations that store model code and data in distinct files and locations (as opposed to embedding data such as parameter values into source code).
+Object-oriented programming approaches include a concept of inheritance [@8717448] that can allow models to be first duplicated and then selectively modified [@ready4oop2022].
+Modular computational implementations construct models from multiple independently reusable and replaceable sub-models (modules) [@pan2021modular].
 To grant permissions to others to use, test and adapt models and their components, health economists can avail of two broad categories of open source licensing options.
@@
 
-Models should be **updatable** so that they remain valid for longer, evolving as new evidence emerges and the systems being modelled change [@Jenkins2021; @garcia2021cost].
+Models should be updatable so that they remain valid for longer, evolving as new evidence emerges and the systems being modelled change [@Jenkins2021; @garcia2021cost].
 Ensuring that a model is regularly reviewed to identify and implement required improvements is a recommended defense against model validity decay [@calder2018computational].
@@
 Services such as GitHub [@github2007] provide collaborative code development tools [@MERGEL2015464] that help elicit, integrate and reconcile contributions from multiple contributors and to ensure each update is uniquely identifiable and retrievable.
-It is also important that verification checks are rerun with each model update, a task that can be automated using the software development practice of Continuous Integration [@CI2017].
+It is also important that verification checks are rerun with each model update, a task that can be automated using the software development practice of continuous integration [@CI2017].
 The risk of model revisions having unintended consequences for third party users can be mitigated through the use of deprecation conventions [@zhou2016api] that take an informative and staged approach to retiring outdated model code and data.
@@
 ###	Assessment criteria
-For each model attribute, we identified only assessment criteria that can be met with existing technical solutions and which therefore have the potential to be facilitated by software frameworks.
+For each attribute that suggests ethical CHEM implementations, we identified assessment criteria that can be met using existing technical solutions and which therefore have the potential to be facilitated by software frameworks.
 

### 2023-08-16 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
tweaks to content prior to example

@@
 
-<!-- The ready4pack library depends on two other module authoring libraries. <!-- MOVED CONTENT --> -->
+<!-- The ready4pack library depends on two other module authoring libraries. <!-- MOVED CONTENT -->
 
@@
 A library for **authoring datasets** contains tools for supplying model modules with data stored in online repositories (hosted on a Dataverse installation or on GitHub), labelling these datasets and then sharing them via online repositories.
-A library for **authoring analyses** contains tools to help author R Markdown programs that combine model modules and datasets to undertake analyses.
+A library for **authoring analyses** contains tools to help author programs that combine model modules and datasets to undertake analyses.
 These analysis programs authored with this library can be either self-documenting (code is easy to understand and integrated with plain English explanations of what it does) or trigger the creation of separate documents (e.g.
@@
 ###	Online services 
-Our software framework needs to be used in conjunction with a number of online services. 
+Our framework libraries are designed to be used in conjunction with a number of online services. 
 <!-- To facilitate its application to our youth mental health project, we established and configured accounts with these required services (see Availability of data and materials). -->

### 2023-08-16 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
tweaks to content prior to example

--- 2023-08-15 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
@@
 Advantages of commercial modelling tools include simplicity and ease of use, but an open-source software development approach may facilitate computational models that are more transparent, reusable and updatable [@incerti2019r; @Pouwels2022].
-The most appropriate implementation choice for a specific CHEM project may depend on both desired model features and the resource and time constraints within which the project needs to be delivered (see Table \@ref(tab:proscons)).
+The decision about what type of implementation to choose for a specific CHEM project needs to balance both desired model features and the resource and time constraints within which the project needs to be delivered (see Table \@ref(tab:proscons)).
 
@@
 <!-- on considerations such as model comprehensiveness, generalisability, reproducibility and transferability -->
-A major early decision in open-source CHEM projects is the selection of an appropriate software framework.
+For open-source CHEM projects, a major consideration in is the selection of an appropriate software framework.
 A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users [@myllarniemi2018development].
@@
 <!-- When making choices about how to implement this health economic model computationally, we wished to facilitate ethical development and use. -->
+The ethical responsibilities of computational modellers are often poorly understood and inadequately fulfilled [@10.3389/fpubh.2017.00068; @pliakos2021ethics; @thompson2022escape; @calder2018computational].
+Guidance on developing, selecting and using software frameworks for ethical CHEM implementations is scarce.
 A high-level software framework for implementing open-source CHEMs in R has previously been developed with the primary aim of improving model transparency [@alarid2019need].
-However, open-source CHEMs remain rare [@Feenstra2022; @Emerson2019], and novel software frameworks may be necessary help health economists fulfill a broader set of ethical modelling practice requirements.
-The ethical responsibilities of computational modellers are often poorly understood and inadequately fulfilled [@10.3389/fpubh.2017.00068; @pliakos2021ethics; @thompson2022escape; @calder2018computational].
-Ideally, a novel software framework for CHEMs would also address some of the barriers preventing health economists adopting open-source approaches.
-The main barriers identified in a 2020 survey of health economists concern updating models, legal considerations, transferring model data, the platforms or languages in which models are developed, the level of public access required, lack of interest from decision-makers, model generalisability and confidentiality and security considerations [@Pouwels2022].
+However, open-source CHEMs remain rare [@Feenstra2022; @Emerson2019], and novel software frameworks may be necessary to help health economists fulfill a broader set of ethical responsibilities.
+Ideally, software frameworks for ethical CHEMs would provide tools that address known barriers to ethical computational modelling practice.
+The main barriers to open-source CHEMs identified in a 2020 survey of health economists concern updating models, legal considerations, transferring model data, the platforms or languages in which models are developed, the level of public access required, lack of interest from decision-makers, model generalisability and confidentiality and security considerations [@Pouwels2022].
 
-<!-- Guidance on developing, selecting and using software frameworks for ethical CHEM implementations is scarce. -->
+<!--  -->
 

### 2023-08-16 Markdown/Manuscript/Child_RMDs/MS_Cndl_Tabs_Not_In_Body.Rmd
about to start on updating example

---
title: "MS_Cndl_Child_Not_In_Body"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---

\newpage
`r if(!is.null(child_tabs_1L_chr)){"## Tables and figures {-}"}`

```{r, child = '../Child_RMDs/MS_Tables_1.Rmd', echo=FALSE}
```
\newpage
```{r, child = '../Child_RMDs/MS_Tables_2.Rmd', echo=FALSE}
```
\newpage
```{r, child = '../Child_RMDs/MS_Tables_3.Rmd', echo=FALSE}
```
\newpage
```{r, child = '../Child_RMDs/MS_Tables_4.Rmd', echo=FALSE}
```

### 2023-08-16 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
about to start on updating example

@@
 
-### Ethical responsibilities of CHEM developers 
-We suggest that three core ethical responsibilities of health economic modellers are to make **socially acceptable** value judgments in planning a CHEM project, to ensure that implementation of a CHEM is **fit for purpose** and to promote **socially beneficial** use of the CHEM over its release lifecycle.
+## Ethical responsibilities of CHEM developers 
+We suggest that three core ethical responsibilities of health economic modellers are to make **socially acceptable** value judgments when planning a CHEM project, to ensure that implementation of a CHEM is **fit for purpose** and to promote **socially beneficial** use of the CHEM once it is released.
 There is significant scope for health economists to improve fulfilment of each of these responsibilities.
@@
 
-### CHEM attributes associated with ethical modelling practice
-The responsibilities of health economic modellers for the planning, implementation and use of CHEMs are easier to state than to measure.
-We have therefore focused our assessment criteria for ethical modelling practice on measurable attributes of CHEMs.
-As described in Table \@ref(tab:timelygls),  we believe that CHEMs that are **transparent**, **reusable** and **updatable** (TRU) suggest that their creators have met a number of core ethical obligations.
+## CHEM attributes associated with ethical modelling practice
+Health economist responsibilities during the planning, implementation and use of CHEMs are easier to state than to measure.
+However, aspects of ethical modelling practice may be inferred from measurable attributes of CHEMs.
+As described in Table \@ref(tab:timelygls),  we believe that the creators of transparent, reusable and updatable (TRU) CHEMs are likely to have fulfilled a number of their ethical obligations.
 We therefore selected these model attributes to use as the basis for deriving ethical assessment criteria.
@@
 
-Transparency has been identified as a core feature of ethical public health modelling practice [@10.3389/fpubh.2017.00068].
-Guidance on transparency in health economic modelling recommended that model code and data should be clearly documented, potentially with different versions for technical and non-technical users [@Eddy2012].
-Notably, the same guidelines, published over ten years ago, did not include recommendations on sharing model code and data.
-However, more recent guidance recommends publicly dissemination of healthcare model artefacts using online repository services [@Erdemir2020].
-Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each code and data collection.
-An essential component of quality assuring health economic models is verification - ensuring that calculations are correct and consistent with model specifications [@techver2019].
-The extensiveness of verification checks in models implemented as software projects can be reported using the concept of code coverage [@ERICWONG2010188] - the proportion of model code that has been explicitly tested.
+Taking steps to make computational models **transparent** is an important part of ethical public health modelling practice [@10.3389/fpubh.2017.00068].
+Guidance on transparency in health economic modelling recommended that model code and data should be clearly documented [@Eddy2012].
+Notably, the same guidelines, published over ten years ago, did not recommend sharing model code and data.
+However, more recent healthcare modelling guidance does recommend publicly dissemination of such artefacts [@Erdemir2020].
+Online repository services such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each code and data collection.
+Ensuring that calculations are correct and consistent with model specifications is an essential part of CHEM quality assurance [@techver2019].
+The extensiveness of such verification checks can be reported using the concept of code coverage [@ERICWONG2010188] - the proportion of model code that has been explicitly tested.
 Tests should ideally combine both unit tests (to verify that small, isolated sections of code produce the correct output when run independently) and acceptance tests (to verify that the correct output is produced when multiple code components are run together to perform tasks that meet core user-requirements [@martin2003agile]).
@@
 
-Model reusability is the second attribute that we identify as signaling an ethical CHEM implementation.
+A CHEM that is **reusable** also signals ethical modelling practice.
 Making a CHEM’s code, data and documentation publicly available is increasingly considered good practice, yet is not sufficient to promote model re-use.
 Key concepts in health economic model reuse include generalisability (application without adaptation) and transferability (selective reuse and/or modification of model components) [@RN39].
-Writing model algorithms as collections of functions (short, self-contained and reusable software routines that each perform a discrete task), is good scientific computing practice [@Wilson_2017] and facilitates model generalisability.
-Transferability is promoted by computational implementations that store model code and data in distinct files and locations (as opposed to embedding data such as parameter values into source code).
-Object-oriented programming approaches include a concept of inheritance [@8717448] that can allow models to be first duplicated and then selectively modified [@ready4oop2022].
-Modular computational implementations construct models from multiple independently reusable and replaceable sub-models (modules) [@pan2021modular].
+Writing model algorithms as collections of functions (short, self-contained and reusable software routines that each perform a discrete task) is good scientific computing practice [@Wilson_2017] and promotes selective reuse.
+Computational implementations that store model code and data in distinct files and locations (as opposed to embedding data such as parameter values into source code) are easier to selectively modify.
+Object-oriented programming approaches incorporate a concept called inheritance [@8717448] that can allow duplicate models to be created and selectively modified.
+Modular models are constructed from multiple independently reusable and replaceable sub-models (modules) [@pan2021modular].
 To grant permissions to others to use, test and adapt models and their components, health economists can avail of two broad categories of open source licensing options.
@@
 
-Models should be updatable so that they remain valid for longer, evolving as new evidence emerges and the systems being modelled change [@Jenkins2021; @garcia2021cost].
+Models should be **updatable** so that they remain valid for longer, evolving as new evidence emerges and the systems being modelled change [@Jenkins2021; @garcia2021cost].
 Ensuring that a model is regularly reviewed to identify and implement required improvements is a recommended defense against model validity decay [@calder2018computational].
@@
 
-###	Assessment criteria
+##	Assessment criteria
 For each attribute that suggests ethical CHEM implementations, we identified assessment criteria that can be met using existing technical solutions and which therefore have the potential to be facilitated by software frameworks.

### 2023-08-16 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
about to start on updating example

@@
 
-To support the development of CHEMs that meet TRU assessment criteria, we have created a prototype software framework called ready4 that works within the popular open-source programming language R [@RCORE2022].
-The ready4 software framework is implemented as a combination of R code libraries and online services and is supported by a documentation website.
+To support the development of CHEMs that meet TRU assessment criteria, we have created a prototype software framework called ready4.
+The software framework aims to provide a toolkit for: (i) enabling modular implementation of CHEMs; (ii) authoring and documenting CHEM modules; (iii) managing the labelling and transfer of CHEM input and output data; and (iv) authoring reproducible analyses that apply CHEMs to compatible data.
+
+To achieve these goals, we have implemented the software framework as R [@RCORE2022] code libraries that integrate with a number of online services and which are supported by a documentation website.
 <!-- We have designed this framework to enable ethical computational implementations of health economic models that are both open-source (for transparency and reusability) and modular (for reusability and updatability).
@@
 
-### R libraries 
+## R libraries 
 A library in the R language will typically depend on multiple other R libraries, each of which may have different authors.
@@
 
-One framework library provides the **foundation** for implementing CHEMs that are modular and open-source.
-Modular models are comprised of modules that are able to share inputs and outputs with each other and to be run as independent models [@barros2023empowering].
-To be implemented as open-source projects modules authored by different teams must be interoperable.
-The foundation library facilitates these objectives by defining a template module data structure (using R’s S4 class system) from which all model module data structures will be created and a novel syntax that enable module algorithms to be consistently named.
+One framework library provides a **foundation for modular CHEM implementations**.
+In modular model implementations, modules need to be able to share inputs and outputs with each other and to be run as independent models [@barros2023empowering].
+To achieve this, the foundation framework library defines a template module (using R’s S4 class system), which can be used to create other modules with a common set of inherited properties.
+One of these inherited properties is a novel syntax of 15 core commands that enable module algorithms to be consistently named.
 The foundation library also contains tools for retrieving web-based information on model modules, datasets and analysis programs authored with the framework and for partially automating updates to a project documentation website.
 
-Three framework libraries are designed to help standardize workflows for **authoring modules**.
+Three framework libraries are designed to help streamline and standardise workflows for **authoring CHEM modules** from the template module.
 The R language supports functional and object-oriented programming paradigms [@10.1214/13-STS452].
-Both these paradigms are used in the ready4 framework, each facilitated by a dedicated authoring library.
-The first module authoring library contains tools for writing functions in a consistent house style and then using the resulting standardised naming conventions to automatically generate basic documentation for each function.
-The second module authoring library contains tools to help streamline and standardise the authoring of module data structures using the framework's module template and for associating methods (a special type of function) with each module.
-The second module authoring library also supports the automatic generation of basic documentation for each new module.
-The third module authoring library provides tools for disseminating themed bundles of model modules as R libraries that are:
+Authoring with each of these paradigms is facilitated by a dedicated CHEM module authoring library.
+The first module authoring library contains tools for writing functions in a consistent house style and then using the standardised naming conventions of that house style to automatically generate basic documentation for each function.
+The second module authoring library contains tools to help streamline and standardise the authoring of novel CHEM modules with distinctive properties and for associating novel algorithms with these modules using the framework's syntax.
+The second module authoring library also supports the automatic generation of basic documentation for each new CHEM module.
+The third module authoring library provides tools for disseminating themed bundles of CHEM modules as R libraries that are:
 
@@
 
--	quality assured (each update triggers GitHub continuous integration workflows, including any acceptance and unit tests created by module library authors).
+-	quality assured (each update triggers continuous integration workflows, including any acceptance and unit tests created by module library authors).
 
@@
 
-A library for **authoring datasets** contains tools for supplying model modules with data stored in online repositories (hosted on a Dataverse installation or on GitHub), labelling these datasets and then sharing them via online repositories.
-A library for **authoring analyses** contains tools to help author programs that combine model modules and datasets to undertake analyses.
-These analysis programs authored with this library can be either self-documenting (code is easy to understand and integrated with plain English explanations of what it does) or trigger the creation of separate documents (e.g.
+A library for **managing CHEM data** contains tools for supplying CHEM modules with input data ingested from local (i.e.
+a user's computer) or remote (online repositories) locations, labelling CHEM module datasets and exporting CHEM module data to online repositories.
+A library for **authoring reproducible analyses** contains tools to help write programs that apply CHEM modules to compatible datasets for the purpose of undertaking health economic analyses.
+These analysis programs can be either self-documenting (code is integrated with plain English explanations of what it does) or trigger the creation of separate documents (e.g.
 a scientific manuscript).
@@
 
-###	Online services 
-Our framework libraries are designed to be used in conjunction with a number of online services. 
+##	Online services 
+Framework libraries are designed to be used in conjunction with a number of third-party online services that we established and configured accounts with. 
 <!-- To facilitate its application to our youth mental health project, we established and configured accounts with these required services (see Availability of data and materials). -->
@@
 To track our code coverage, we linked our GitHub organisation to an account we established at codecov [@codecov_2022].
-To facilitate the creation and hosting of documentation websites, we enabled GitHub Pages in each repository we used for code library development.
+To facilitate the creation and hosting of documentation websites, we enabled GitHub Pages in each repository used for code library development.
 
@@
 
-###	Documentation website
+##	Documentation website
 We developed a framework documentation website (www.ready4-dev.com) that provides guidance to model developers on how to use and contribute improvements to the ready4 software framework and models developed with it.
@@
 We used functions from our foundation framework library to partially automate website updates relating to available CHEM modules, datasets and analysis programs.
-We linked our Netlify account to our GitHub organisation so that the project website would automatically update whenever the source code in its GitHub repository was edited.
+We linked our Netlify account to our GitHub organisation so that the project website would automatically update whenever its  source code (publicly available in a GitHub repository) was edited.

### 2023-08-16 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
working way through frameworks
about to start on updating example

@@
 
-## Assessing ethical computational implementations
+# Assessing ethical CHEM implementations
 ```{r child="../Child_RMDs/MS_Imp_Guidelines.Rmd", echo=FALSE}
@@
 
-## Software framework
+# Software framework
 ```{r child="../Child_RMDs/MS_Imp_Toolkit.Rmd", echo=FALSE}

### 2023-08-16 Markdown/Manuscript/Child_RMDs/MS_Tables.Rmd
about to start on updating example

--- 2023-01-23 Markdown/Manuscript/Child_RMDs/MS_Tables.Rmd
@@
 if(params$X@tables_in_body_lgl){
-  child_docs_ls <- list(one = "../Child_RMDs/MS_Tables_1.RMD",
-                        two = "../Child_RMDs/MS_Tables_2.RMD",
-                        three = "../Child_RMDs/MS_Tables_3.RMD")
+  child_docs_ls <- list(one = "../Child_RMDs/MS_Tables_1.Rmd",
+                        two = "../Child_RMDs/MS_Tables_2.Rmd",
+                        three = "../Child_RMDs/MS_Tables_3.Rmd",
+                        four = "../Child_RMDs/MS_Tables_4.Rmd")
 }else{
     child_docs_ls <- list(one = NULL,
-                      two = NULL)
+                          two = NULL,
+                          three = NULL,
+                          four = NULL)
 }

### 2023-10-08 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
wip

@@
 
-(i)	criteria for assessing ethical CHEM implementations;
+(i)	proposed criteria for assessing ethical CHEM implementations;
 
@@
 
-(iii)	use of the software framework to develop an open-source CHEM in youth mental health, with an initial focus on outcome valuation.
+(iii)	how the software framework is being used to develop an open-source CHEM in youth mental health, with an initial focus on valuing health outcomes.

### 2023-10-08 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
wip

@@
 <!-- Talk about DARTH (https://doi.org/10.1007/s40273-019-00837-x )/ BCEA -->
-Ethical practice is a core expectation of health researchers and computational methods underpin most quantitive research, yet an understanding of what constitutes ethical computational modelling practice in health is underdeveloped [@10.3389/fpubh.2017.00068].
+Ethical practice is a core expectation of health researchers and computational methods underpin most quantitative research, yet an understanding of what constitutes ethical computational modelling practice in health is underdeveloped [@10.3389/fpubh.2017.00068].
 The modeller responsibilities, enabling model attributes and model implementation assessment criteria that we propose can help address this gap.
@@
 The ethical responsibilities and enabling model attributes we describe have both commonalities and distinctive features compared to a previous ethical framework for computational modelling in public health [@10.3389/fpubh.2017.00068].
-The authors of that framework propose 13 questions to evaluate ethical risk across the four criteria of independence, transparency, benficience and justice.
-Their descriptions of the four criteria at least partially map to either our proposed modeler responsibilities (“justice” to “social acceptability”, “independence” to “adequacy for purpose” and “beneficience” to “beneficial impact”) or enabling model attributes (“transparency”).
-However, while our six assessment criteria are specific to three attributes (TRU) of the computational implementation of the model, the prior ethical framework includes questions relevant to the the conceptual and mathematical models and the potential impacts of model use.
-Examples of these more general evaluation questions include (for the justice criterion) “is any lack of knowledge about important parameters attributable to uncertainty or variability?” and (for the beneficience criterion) “if a policy is based on the model evidence, is it more likely to be effective and beneficial than a decision made in the absence of the model?”.
+The authors of that framework propose 13 questions to evaluate ethical risk across the four criteria of independence, transparency, beneficence and justice.
+Their descriptions of the four criteria at least partially map to either our proposed modeler responsibilities (“justice” to “social acceptability”, “independence” to “adequacy for purpose” and “beneficence” to “beneficial impact”) or enabling model attributes (“transparency”).
+However, while our six assessment criteria are specific to three attributes (TRU) of the computational implementation of the model, the prior ethical framework includes questions relevant to the conceptual and mathematical models and the potential impacts of model use.
+Examples of these more general evaluation questions include (for the justice criterion) “is any lack of knowledge about important parameters attributable to uncertainty or variability?” and (for the beneficence criterion) “if a policy is based on the model evidence, is it more likely to be effective and beneficial than a decision made in the absence of the model?”.
 The less numerous and more focused assessment criteria we propose may potentially be more tractable to implement in reviews of models authored by third parties and as the basis for designing software frameworks to support ethical computational model implementation.
@@
 <!-- DELETION --> Existing incentive structures for health economists generally do not promote facilitating peers to reuse their work.
-Currently, it takes “an extraordinary amount of idealism” to dedicate the substantial time and resources required to author, test, document and maintain even fragile prototype research software that could instead be used to write scientific manuscripts [@anzt2020environment].
+Currently, it can take “an extraordinary amount of idealism” to commit to authoring and maintaining research software [@anzt2020environment].
 
@@
 the dependency libraries we list in Table \@ref(tab:cpkgs)).
-Secondly, implementation that combines both object oriented and functional programming paradigms can avail of the modular and syntactical simplicity benefits of the former, while limiting needless bundling of code artefacts (a limitation of object oriented approaches famously described as: “you wanted a banana but what you got was a gorilla holding the banana” [@seibel2009joe]).
+Secondly, implementation that combines both object oriented and functional programming paradigms can avail of the modular and syntactical simplicity benefits of the former, while limiting needless bundling of code artefacts.
 Thirdly, a sensible trade-off needs to be found between transparent code implementation (which requires clear and sufficiently detailed documentation) and Agile Software Development (for which a foundational principle is prioritizing the development of working code over writing documentation [@beck2001manifesto]).

### 2023-10-08 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
about to start on updating example
wip

@@
 
+<!-- Add intro text -->
+We plan on using the ready4 software framework to implement multiple transparent, reusable and updatable CHEMs in youth mental health (see Figure \@ref(fig:fig1)).
+Some initial outputs from this work are publicly available.
+
+```{r, child = child_figs_ls$fig1, echo=FALSE}
+```
+
 ##	Economic topics
-Currently, we are using the ready4 software framework to develop, apply and share youth mental health computational models in four of the twelve domains of health economics identified by Wagstaff and Culyer [@wagstaff2012four]:
+Currently, we are using the ready4 software framework to develop, apply and share youth mental health CHEMs in four of the twelve domains of health economics identified by Wagstaff and Culyer [@wagstaff2012four]:
 
@@
 
--	supply of health services (our projects: a model of primary mental health care services).
+-	supply of health services (our projects: a model of primary mental health care services for young people).
 
-Once these projects are completed, our aim is to flexibly combine these models as modules of a multi-purpose model (also called “ready4”) to answer questions in two additional Wagstaff and Culyer domains:
+Potential future directions are to supplement this work with CHEMs in two additional Wagstaff and Culyer domains of public health (to model the impact of selected fiscal policy and regulation options on young people's mental health) and human resources (to model the supply and behaviours of the youth mental health workforce).
+Our ultimate aim is to flexibly combining all our CHEMs in analyses that help answer questions in two additional Wagstaff and Culyer domains:
 
--	efficiency and equity (our goal: assess the distributional impacts and identify the optimal targeting of care provision); and
+-	efficiency and equity (our goal: assess the distributional impacts and identify the optimal targeting of youth mental health interventions); and
 
@@
 
-## Case study: Utility mapping
-Our initial application of the ready4 software framework was to undertake a previously described study [@Hamilton2021.07.07.21260129] to develop utility mapping models for use in samples of young people presenting to primary mental health services.
-The ready4 software framework was used to develop CHEM modules, supply those modules with data and implement modelling analyses, creating the following artefacts:
+Although principally interested in using our CHEMs to answer policy questions relating to the mental health of young people in Australia, we want to facilitate CHEM transferability to other jurisdictions.
+Our CHEMs are therefore being derived from and applied to real data (which can be assumption, empirical or simulated, so long as it is appropriate for use in analysis intended to inform decision-making) from Australia.
+Additionally, we plan for all our CHEMs to be distributed with toy (fake) data to help demonstrate the potential use of these CHEMS in other decision contexts.
+
+## Case study: health and its value
+We have previously described [@Hamilton2021.07.07.21260129] a study to develop utility mapping models for use in samples of young people presenting to primary mental health services.
+The ready4 software framework was used in that study to develop CHEM modules, supply those modules with data and implement modelling analyses, creating the following artefacts:
 
@@
 
- - data collections of synthetic populations for testing model modules [@DVN/HJXYKQ_2021] and study input and results data [@DVN/DKDIB0_2021];
+ - collections of real data (study input and results [@DVN/DKDIB0_2021]) and fake data (synthetic populations for testing model modules [@DVN/HJXYKQ_2021]);
 
- - programs for replicating all steps from data ingest to manuscript reporting [@hamilton_matthew_2022_6129906], applying utility mapping models to new data [@hamilton_matthew_2022_6416330] and generating a synthetic representation of the study dataset [@hamilton_matthew_p_2022_6321821];
+ - programs for replicating all steps from data ingest to manuscript reporting [@hamilton_matthew_2022_6129906], applying utility mapping models to new data [@hamilton_matthew_2022_6416330] and generating a synthetic representation of the study dataset [@hamilton_matthew_p_2022_6321821]; and
 
@@
 For each criterion, we provided a global assessment of whether it was met using the responses “yes”, “no” or “partial”.
-We believe the outputs from our utility mapping study may be assessable as having satisfactorily met four of the six criteria (T1, T2, R2 and U1) and to have partially met two criteria (R1 and U2).
-The main shortcomings that we identified when applying the assessment criteria were the need for additional development before the CHEM modules would be sufficiently generalizable for valid application in datasets that measure health utility with different instruments and a general lack of unit testing.
+We believe the outputs from our utility mapping study may be assessable as having satisfactorily met five of the six criteria (T1, T2, R1, R2 and U1) and to have partially met one criterion (U2).
+The main shortcomings that we identified when applying the assessment criteria was that we have yet to adequately implement unit testing of the R libraries we authored as part of this study.
 

### 2023-10-08 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
wip

@@
 
-We considered prior literature on modelling practice, our own professional experience and the needs of modelling projects we are undertaking to identify: (i) some core ethical responsibilities of CHEM developers; (ii) attributes of CHEMs that can suggest fulfillment of these responsibilities; and (iii) criteria against which these attributes can be assessed.
+We considered prior literature on modelling practice and our own professional experience to identify: (i) some core ethical responsibilities of CHEM developers; (ii) attributes of CHEMs that can suggest fulfillment of these responsibilities; and (iii) criteria against which these attributes can be assessed.
 
 ## Ethical responsibilities of CHEM developers 
-We suggest that three core ethical responsibilities of health economic modellers are to make **socially acceptable** value judgments when planning a CHEM project, to ensure that implementation of a CHEM is **fit for purpose** and to promote **socially beneficial** use of the CHEM once it is released.
+For simplicity, we sought to identify one overarching ethical responsibility for modellers at each distinct phase of a CHEM project.
+As CHEMs are implemented as software, software development lifecycle (SDLC) models may provide an appropriate basis for identifying the main phases of a CHEM project.
+There are multiple SDLC models, each taking a different approach to the number, naming, definition, sequencing and iteration of project phases [@ruparelia2010software].
+However, components of most SDLC models can broadly be mapped to the concepts of *planning* (in which software requirements and design specification are agreed), *development* (in which software is authored and tested) and *deployment* (in which software is made available as production ready tools for end-users).
+We contend that ethical responsibilities of computational modellers identified in prior literature [@10.3389/fpubh.2017.00068; @pliakos2021ethics; @thompson2022escape; @calder2018computational] can be summarised under the following three overarching goals (one for each phase):
+
+- **make socially acceptable value judgments** (when planning CHEM projects);
+
+- **ensure model fitness for purpose** (when developing CHEMs); and
+
+- **promote socially beneficial use of models** (once CHEMs have been deployed).
+
 There is significant scope for health economists to improve fulfilment of each of these responsibilities.
@@
 Computational implementations that store model code and data in distinct files and locations (as opposed to embedding data such as parameter values into source code) are easier to selectively modify.
-Object-oriented programming approaches incorporate a concept called inheritance [@8717448] that can allow duplicate models to be created and selectively modified.
-Modular models are constructed from multiple independently reusable and replaceable sub-models (modules) [@pan2021modular].
-To grant permissions to others to use, test and adapt models and their components, health economists can avail of two broad categories of open source licensing options.
+Modular implementations construct models from multiple independently reusable and replaceable sub-models (modules) [@pan2021modular].
+The programming concept inheritance [@8717448], deployed in object-oriented programming approaches, can facilitate the duplication and selective modification of models.
+Granting permissions to others to use, test and adapt models and their components, can be facilitated by two broad categories of open source licenses.
 Some guidance strongly recommends the use of permissive licensing [@Wilson_2017] that provides users with great flexibility as to the purposes (including commercial) for which content can be re-used.
@@
 ##	Assessment criteria
-For each attribute that suggests ethical CHEM implementations, we identified assessment criteria that can be met using existing technical solutions and which therefore have the potential to be facilitated by software frameworks.
+For each CHEM attribute that suggests ethical CHEM modelling practice, we identified assessment criteria that have the potential to be met with the assistance of software frameworks.
 

### 2023-10-08 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
wip

@@
 ## R libraries 
-A library in the R language will typically depend on multiple other R libraries, each of which may have different authors.
+A library in the R language will typically depend on multiple other R libraries, all of which potentially having different authors.
 As the number of third-party dependencies of an R library grows so does the fragility of that library (e.g.
@@
 In modular model implementations, modules need to be able to share inputs and outputs with each other and to be run as independent models [@barros2023empowering].
-To achieve this, the foundation framework library defines a template module (using R’s S4 class system), which can be used to create other modules with a common set of inherited properties.
-One of these inherited properties is a novel syntax of 15 core commands that enable module algorithms to be consistently named.
-The foundation library also contains tools for retrieving web-based information on model modules, datasets and analysis programs authored with the framework and for partially automating updates to a project documentation website.
+To achieve this, the foundation framework library defines a template CHEM module (using R’s S4 class system), which can be used to create other CHEM modules with a common set of inherited properties.
+One of these inherited properties is a novel syntax of 15 core commands that enable CHEM module algorithms to be consistently named.
+The foundation library also contains tools for retrieving web-based information on CHEM modules, datasets and analysis programs authored with the framework and for partially automating updates to a project documentation website.
 
@@
 Authoring with each of these paradigms is facilitated by a dedicated CHEM module authoring library.
-The first module authoring library contains tools for writing functions in a consistent house style and then using the standardised naming conventions of that house style to automatically generate basic documentation for each function.
-The second module authoring library contains tools to help streamline and standardise the authoring of novel CHEM modules with distinctive properties and for associating novel algorithms with these modules using the framework's syntax.
-The second module authoring library also supports the automatic generation of basic documentation for each new CHEM module.
-The third module authoring library provides tools for disseminating themed bundles of CHEM modules as R libraries that are:
+One module authoring library contains tools for writing functions in a consistent house style and then using the standardised naming conventions of that house style to automatically generate basic documentation for each function.
+A second module authoring library contains tools to help streamline and standardise the authoring and documenting of novel CHEM modules.
+A third module authoring library provides tools for disseminating themed bundles of CHEM modules as R libraries that are:
 
@@
 
-We created a GitHub organisation (a collection of code repositories) where all code (libraries, programs and sub-routines) that we author with the framework is stored and version controlled.
-We configured individual repositories in our GitHub organisation that are used for code library projects to use GitHub actions to implement continuous integration.
+We created a GitHub organisation (a collection of code repositories) where code (libraries, programs and sub-routines) that we author for and with the framework is stored and version controlled.
+We configured individual repositories in our GitHub organisation to use GitHub actions to implement continuous integration.
 By default, code libraries authored with our framework will use continuous integration to assess compliance with policies specified by the Comprehensive R Archive Network (CRAN) [@CRAN2022].

### 2023-10-08 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
wip

@@
 The conceptual, mathematical and computational representations of a model are assumed to be isomorphic.
-Independent assessment of the validity of this assumption depends in part on how a computational model has been authored and shared.
+However, the ease of independently assessing the validity of this assumption depends in part on how a health economic model has been implemented computationally.
 
@@
 
-Computational health economic models (CHEMs) can be implemented using specialized commercial software or authored as software development projects in an open-source programming language such as Python [@python2009] or R [@RCORE2022].
+Computational health economic models (CHEMs) can be implemented using specialised commercial modelling software or authored as software development projects in an open-source programming language such as Python [@python2009] or R [@RCORE2022].
 Advantages of commercial modelling tools include simplicity and ease of use, but an open-source software development approach may facilitate computational models that are more transparent, reusable and updatable [@incerti2019r; @Pouwels2022].
-The decision about what type of implementation to choose for a specific CHEM project needs to balance both desired model features and the resource and time constraints within which the project needs to be delivered (see Table \@ref(tab:proscons)).
+The decision about what implementation approach to adopt needs to balance both modelling team value judgments about priority model features and the resource and time constraints within which a CHEM project needs to be delivered (see Table \@ref(tab:proscons)).
 
@@
 <!-- on considerations such as model comprehensiveness, generalisability, reproducibility and transferability -->
-For open-source CHEM projects, a major consideration in is the selection of an appropriate software framework.
+For open-source software projects, a major consideration is the selection of an appropriate software framework.
 A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users [@myllarniemi2018development].
-A software framework provides a foundation for developing multiple software applications with shared resources, e.g., code and data files, that can be modified to suit specific needs.
+A software framework provides a foundation for developing multiple software applications with shared resources (e.g., code and data files), that can be modified to suit specific needs.
 Software frameworks have widely been developed and implemented in data science, for example, PyTorch [@PyTorch2019] for machine learning using Python.
@@
 <!-- When making choices about how to implement this health economic model computationally, we wished to facilitate ethical development and use. -->
-The ethical responsibilities of computational modellers are often poorly understood and inadequately fulfilled [@10.3389/fpubh.2017.00068; @pliakos2021ethics; @thompson2022escape; @calder2018computational].
-Guidance on developing, selecting and using software frameworks for ethical CHEM implementations is scarce.
+The ethical responsibilities of computational modellers seeking to inform policy decisions are often poorly understood and inadequately fulfilled [@10.3389/fpubh.2017.00068; @pliakos2021ethics; @thompson2022escape; @calder2018computational].
+Within the health economics discipline, open-source CHEMs remain rare [@Feenstra2022; @Emerson2019].
+The main barriers to open-source CHEMs identified in a 2020 survey of health economists concern challenges relating to updating models, legal considerations, transferring model data, the platforms or languages in which models are developed, the level of public access required, lack of interest from decision-makers, model generalisability and confidentiality and security considerations [@Pouwels2022].
+
+There is a potential role for software frameworks to help health economic modellers overcome some of these barriers.
 A high-level software framework for implementing open-source CHEMs in R has previously been developed with the primary aim of improving model transparency [@alarid2019need].
-However, open-source CHEMs remain rare [@Feenstra2022; @Emerson2019], and novel software frameworks may be necessary to help health economists fulfill a broader set of ethical responsibilities.
-Ideally, software frameworks for ethical CHEMs would provide tools that address known barriers to ethical computational modelling practice.
-The main barriers to open-source CHEMs identified in a 2020 survey of health economists concern updating models, legal considerations, transferring model data, the platforms or languages in which models are developed, the level of public access required, lack of interest from decision-makers, model generalisability and confidentiality and security considerations [@Pouwels2022].
+Ideally, software frameworks would facilitate fulfillment of a broader set of ethical responsibilities.
+However, guidance on developing, selecting and using software frameworks for ethical CHEM implementations is scarce.
 

### 2023-10-08 Markdown/Manuscript/Child_RMDs/MS_Tables_2.Rmd
wip

@@
 ---
-```{r timelygls, tab.cap='Framework standards', tab.id = 'timelygls', echo = F, results = 'asis'}
+```{r timelygls, tab.cap='How transparent, reusable and updatable (TRU) computational health economic models (CHEMs) suggest ethical modelling practice', tab.id = 'timelygls', echo = F, results = 'asis'}
 library(kableExtra)  

### 2023-10-08 Markdown/Manuscript/Child_RMDs/MS_Tables_3.Rmd
wip

--- 2023-01-26 Markdown/Manuscript/Child_RMDs/MS_Tables_3.Rmd
@@
 ---
+```{r cpkgs, tab.cap='Software framework R libraries', tab.id = 'cpkgs', echo = F, results = 'asis'}
+library(kableExtra)  
+df <- tibble::tibble(Package = c("ready4",
+                                       "ready4fun",
+                                       "ready4class",
+                                       "ready4pack",
+                                       "ready4use",
+                                       "ready4show"),
+                           # Version = Package %>%
+                           #   purrr::map_chr(~utils::packageDescription(.x) %>%
+                           #                    purrr::pluck("Version")),
+                           Focus = c("Foundation",
+                                     "Module algorithms",
+                                     "Module structures",
+                                     "Module libraries",
+                                     "Datasets",
+                                     "Analyses"),
+                           A = c("3","2-3","2","1-2,5,7","1-2,7","4,6"), 
+                           R = c("4","5","4-5","1,3,6","3,7",""),
+                           U = c("","","","1-3","1",""),
+                           # E = c("", "1","1-2","1","3",""),
+                           # L = c("","","","1,3","2-3",""),
+                           # Y = c("","","","","","1-2"),
+                           `Depends on` = Package %>%
+                             purrr::map(~ {
+                               utils::packageDescription(.x) %>%
+                                 `[`(c("Depends", "Imports")) %>%
+                                 purrr::map(~{
+                                   if(is.null(.x)){
+                                     character(0)
+                                     }else{
+                                       .x %>%
+                                         strsplit(",\\n") %>%
+                                         purrr::flatten_chr() %>%
+                                         purrr::map(~strsplit(.x,", ") %>%
+                                                      purrr::flatten_chr()) %>%
+                                         purrr::flatten_chr() %>% sort() %>%
+                                         purrr::discard(~startsWith(.x,"R "))
+                                       }
+                                   }) %>%
+                                 purrr::flatten_chr() %>%
+                                 unique() %>%
+                                 sort() %>%
+                                 purrr::map_chr(~{
+                                   updated_1L_chr <- stringr::str_replace_all(.x,"\\n"," ")
+                                   problem_idx_1L_chr <- stringr::str_locate(updated_1L_chr," ")[1,1] %>%
+                                     unname()
+                                   if(!is.na(problem_idx_1L_chr))
+                                     updated_1L_chr <- updated_1L_chr %>%
+                                     stringr::str_sub(end = problem_idx_1L_chr-1)
+                                   updated_1L_chr %>% 
+                                     trimws(which = "left") 
+                                   })
+                               }) %>% 
+                             purrr::map_chr (~ .x %>% paste0(collapse = " "))) %>% 
+  as.data.frame() 
+if(params$X@outp_formats_chr[1] != "Word"){
+      df$Ref <- c(rep("",6)
+       # "@ready42022","@ready4fun2022","@ready4class2022","@ready4pack2022","@ready4use2022","@ready4show2022"
+                  )
+}else{
+  df$Ref <- ""
+}
 
-```{r checktb, tab.cap='Framework checklist applied to utility mapping study', tab.id = 'checktb', echo = F, results = 'asis'}
-    #  a <- c("TEST1","TEST2")
-    # b <- c("\\cite{ready4show2022}", "hjhjhj")
-    # tmp <- data.frame(a,b)   
-#     kableExtra::kbl(tmp, booktabs = T, escape = F) %>%
-#  kableExtra::kable_styling(
-#    latex_options = c("striped", "hold_position", "repeat_header")
-#    ) %>%  
-#   kableExtra::column_spec(2, width = "50em") %>%
-# kableExtra::landscape()
-checklist_df <- data.frame(Ref = c(paste0("A",1:7),#paste0("T",1:6),paste0("I",1:4),paste0("M",1:2),paste0("E",1:3),paste0("L",1:3), paste0("Y",1:2)
-                                   paste0("R",1:9),
-                                   paste0("U",1:4)),
-                           Standard = c("Public",
-                                        "Documentation",
-                                        "Syntax",
-                                        "Literate programming",
-                                        "Code coverage",
-                                        "Reproducibility",
-                                        "Citation tools",#
-                                        # Reuse
-                                        "Code licenses",
-                                        "Data terms",
-                                        "Separation",
-                                        "Encapsulated, inheriting",
-                                        "Functions",
-                                        "Libraries",
-                                        "Test data",
-                                        "Prediction tools",
-                                        "User interface",
-                                        ## Updatable
-                                        "Version controlled",
-                                        "Semantic versioning",
-                                        "Continuously integrated",
-                                        "Deprecation"
+df <- df %>%
+  dplyr::mutate(Standard = purrr::pmap_chr(df,
+                                           ~paste0("A",
+                                                  ..3,
+                                                  paste0(rep("&nbsp;",
+                                                      2+max(nchar(df[,3]))-nchar(..3)),
+                                                      collapse = ""#
                                                       ),
-                           Assessment = c("Yes",
-                                        "Yes",
-                                        "Yes",
-                                        "Yes",
-                                        "No",
-                                        "Yes",
-                                        "Yes",
-                                        # Reuse
-                                        "Yes",
-                                        "Yes",
-                                        "Yes",
-                                        "Yes", # "Yes",
-                                        "Yes",
-                                        "Yes",
-                                        "Yes",
-                                        "Yes",
-                                        "No",
-                                        ## Updatable
-                                        "Yes",
-                                        "Yes",
-                                        "Yes",
-                                        "Yes"
+                                                  ifelse(..4=="","","R"),
+                                                  ..4,
+                                                  paste0(rep("&nbsp;",
+                                                      2+max(nchar(df[,4]))-nchar(..4)),
+                                                      collapse = ""#
                                                       ),
-                           Description = c("Datasets are available at https://doi.org/10.7910/DVN/DKDIB0 and https://doi.org/10.7910/DVN/HJXYKQ.
-For details of where to find Development and Archive code see: https://www.ready4-dev.com/docs/getting-started/software/libraries/types/module/  https://www.ready4-dev.com/docs/getting-started/software/executables/programs/  https://www.ready4-dev.com/docs/getting-started/software/executables/subroutines/ ",
-                                           "All code libraries have documenting websites with URLs that concatenate 'https://ready4-dev.github.io/' and the library name (e.g.
-https://ready4-dev.github.io/youthvars).
-All three Markdown programs are self-documenting, with one [@hamilton_matthew_2022_6129906] including additional instructions in a README file.
-Only one sub-routine [@matthew_p_hamilton_2022_5976988] is documented with a meaningful README file.
-All datasets have meaningful metadata descriptors.",
-                                           "All libraries are authored with ready4pack [@ready4pack2022] to ensure a consistent house style.
-All libraries except [@matthew_p_hamilton_2021_5646669] use framework syntax, as does one program [@hamilton_matthew_2022_6129906].",
-                                           "All programs use literate programming.",
-                                           "No current reporting of code coverage.",
-                                           "All parts of the study workflow from raw data ingest through to data processing, analysis, reporting and dissemination of study outputs can be reproduced (if granted access to source data) or replicated (using supplied synthetic data) with one program [@hamilton_matthew_2022_6129906].",
-                                           "All libraries can return citation details when running R's 'citation' function. All code and data repositories have tools to generate citation details.",
-                                           # Reuse
-                                           "All code libraries, programs and sub-routines use GPL-3 licenses. ",
-                                           "Datasets use amended version of template provided by Harvard Dataverse [@sampleterms2022].",
-                                           "All development code is stored on repos in a GitHub organisation [@ready4gh2022] and all archived releases are available in a Zenodo community [@ready4zen2022].
-All non-confidential data is stored in repositories within a Harvard Dataverse collection [@ready4dv2022].
-",
-                                           "Four [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155] out of five libraries include encapsulating and inheriting modules.
-See: https://www.ready4-dev.com/docs/model/finding-modules/ ",
-                                           "All code libraries include functions.
-The most complete list of functions for each library is available by clicking the 'Manual - Developer (PDF)' link on each package's documentation homepage (see item A2 above)",
-                                           "All module data-structures and algorithms are distributed as code libraries.",
-                                           "Two synthetic datasets and their data dictionaries are publicly available in a data repository [@DVN/HJXYKQ_2021].
-One (ymh_clinical_tb.RDS) closely resembles the study dataset and was released so that the main study algorithm [@hamilton_matthew_2022_6129906] can be rerun by those without access to the confidential study dataset.
-The other (eq5d_ds_dict.RDS) is deliberately different to the source dataset in both variable naming convention and the concepts used for predictors and outcome measures.
-It was created to demonstrate generalised applications of study algorithms.",                                           #
-                                           "Model catalogues (PDF files beginning with 'AAA_TTU_MDL_CTG') are available in the study results dataset [@DVN/DKDIB0_2021] and describe the predictive performance of all models under a variety of usage regimes (including when the source dataset in the R model object is replaced with fake data).
-The youthu library [@matthew_p_hamilton_2021_5646669] includes tools for searching for and applying models compatible with different types of input data.
-An example program to demonstrate this functionality is available in both RMarkdown [@hamilton_matthew_2022_6416330] and rendered PDF formats (the 'Application.pdf' file in the study results dataset [@DVN/DKDIB0_2021]).
-",
-                                           "No user interface has yet been developed.",
-                                        ## Updatable
-                                           "All code is version controlled using Git and GitHub. All source code is available in a GitHub organisation [@ready4gh2022].",
-                                           "Semantic versioning is used in all code.
-As no code library has yet been submitted to CRAN, only the development version extensions of each version number have been incremented to date.",
-                                           "All six libraries use continuous integration (CI).
-CI results for each library can be viewed at a URL that concatenates 'https://github.com/ready4-dev/', the library name and '/actions' (e.g.
-https://github.com/ready4-dev/youthvars/actions)",
-                                           "Retired code is deprecated using tools from the lifecycle R library (e.g.
-everything after “## DEPRECATED FNS” in https://github.com/ready4-dev/youthvars/blob/main/data-raw/fns/add.R ).
-Package vignettes and datasets are also deprecated e.g.
-https://ready4-dev.github.io/youthvars/articles/Replication_DS.html )"
-                                          ))
+                                                  ifelse(..5=="","","U"),
+                                                  ..5,
+                                                  paste0(rep("&nbsp;",
+                                                      1+max(nchar(df[,5]))-nchar(..5)),
+                                                      collapse = ""#
+                                                      )#,
+                                                  # ifelse(..6=="","","E"),
+                                                  # ..6,
+                                                  # paste0(rep("&nbsp;",
+                                                  #     1+max(nchar(df[,6]))-nchar(..6)),
+                                                  #     collapse = ""#
+                                                  #     ),
+                                                  # ifelse(..7=="","","L"),
+                                                  # ..7,
+                                                  # # paste0(rep("&nbsp;",
+                                                  # #     1+max(nchar(df[,7]))-nchar(..7)),
+                                                  # #     collapse = ""#
+                                                  # #     ),
+                                                  # ifelse(..8=="","","&nbsp; &nbsp; &nbsp; &nbsp; Y"),
+                                                  # ..8,
+                                                  # paste0(rep("&nbsp;",
+                                                  #     1+max(nchar(df[,8]))-nchar(..8)),
+                                                  #     collapse = ""#
+                                                  #     )
+                                                  ))) %>%
 
-tb2_nms_chr<-colnames(checklist_df)
-checklist_df <- data.frame(checklist_df[,1],
-                           rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; "),
-                               nrow(checklist_df)),
-                           checklist_df[,2],
-                           rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp; &nbsp; "),
-                               nrow(checklist_df)),
-                           checklist_df[,3],
-                           rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; "),
-                               nrow(checklist_df)),
-                 checklist_df[,4])
-colnames(checklist_df) <- c(ifelse(params$X@outp_formats_chr[1] == "Word","Code"," "),
+  dplyr::select(Package,
+                Ref,
+                Focus,
+                Standard,
+                `Depends on`)
+
+names_chr <- names(df)
+df <- data.frame(df[,1],
+                 rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp;"),
+                     nrow(df)),
+                 df[,2:3],
+                 rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp;")
+                     ,nrow(df)),
+                 df[,4],
+                 #rep("&nbsp; &nbsp; &nbsp;",nrow(df)),
+                 df[,5])
+colnames(df) <- c("Package",
+                  ifelse(params$X@outp_formats_chr[1] == "Word","XXX"," "),
+                  "Ref", "Focus", 
                   ifelse(params$X@outp_formats_chr[1] == "Word","YYY"," "),
-                            "Standard",#
-                             ifelse(params$X@outp_formats_chr[1] == "Word","ZZZ","   "),
-                            "Met?",
-                            ifelse(params$X@outp_formats_chr[1] == "Word","AAA","   "),
-                            tb2_nms_chr[4])
+                  "Standard     ",# " ",
+                  "Depends on these R libraries")
+#df$Package <- "![](../Data/images/ready4.png){ width=10% }"#"\\includegraphics[valign=T,scale=2.5,raise=2mm]{../Data/images/ready4.png}"
+df$`Standard     `  <- df$`Standard     ` %>% stringr::str_replace_all("&nbsp;"," ")
 if(params$X@outp_formats_chr[1] == "Word") {
@@
   library("ftExtra")
-  checklist_df[,
-               c(1,3,5,7
-                  )] %>%
+  df[,c(1,3:4,6:7)] %>%
     ready4show::print_table(output_type_1L_chr = params$X@outp_formats_chr[1],
@@
   }else{
-    checklist_df %>%
-    kableExtra::kbl(format = "markdown",
-                    booktabs = T,
-                    caption = knitr::opts_current$get("tab.cap")) 
+    df$Ref<-NULL
+    #df$Package <- ""
+    df$Package  <- df$Package %>% 
+                      purrr::map_chr(~paste0("\\includegraphics[valign=M,width=1.9cm,raise=4mm]{../Data/images/",.x,"_logo.png}"))#scale=0.4,raise=3mm]
+    # df$Package <- "\\includegraphics[valign=M,scale=0.08,raise=3mm]{../Data/images/ready4.png}"
+    df[,c(1,3,5:6)]   %>%
+    # kableExtra::kbl(format = "markdown",
+    #                   escape = F,
+    #                 caption = knitr::opts_current$get("tab.cap"))
+      kableExtra::kbl(booktabs = T, 
+                      escape = F,
+                      caption = knitr::opts_current$get("tab.cap")) %>%
+      kableExtra::kable_paper(full_width = F) %>%
+      kableExtra::column_spec(3,latex_valign = "m") %>%
+      # kableExtra::column_spec(1, 
+      #                         image = kableExtra::spec_image(rep("../Data/images/ready4.png",nrow(df)), 
+      #                                                           150, 150)) %>%
+      kableExtra::column_spec(4, width = "24em",latex_valign = "m")
     }

### 2023-10-08 Markdown/Manuscript/Child_RMDs/MS_Tables_4.Rmd
wip

@@
 
-```{r checktb, tab.cap='Framework checklist applied to utility mapping study', tab.id = 'checktb', echo = F, results = 'asis'}
-    #  a <- c("TEST1","TEST2")
-    # b <- c("\\cite{ready4show2022}", "hjhjhj")
-    # tmp <- data.frame(a,b)   
-#     kableExtra::kbl(tmp, booktabs = T, escape = F) %>%
-#  kableExtra::kable_styling(
-#    latex_options = c("striped", "hold_position", "repeat_header")
-#    ) %>%  
-#   kableExtra::column_spec(2, width = "50em") %>%
-# kableExtra::landscape()
-checklist_df <- data.frame(Ref = c(paste0("A",1:7),#paste0("T",1:6),paste0("I",1:4),paste0("M",1:2),paste0("E",1:3),paste0("L",1:3), paste0("Y",1:2)
-                                   paste0("R",1:9),
-                                   paste0("U",1:4)),
-                           Standard = c("Public",
-                                        "Documentation",
-                                        "Syntax",
-                                        "Literate programming",
-                                        "Code coverage",
-                                        "Reproducibility",
-                                        "Citation tools",#
-                                        # Reuse
-                                        "Code licenses",
-                                        "Data terms",
-                                        "Separation",
-                                        "Encapsulated, inheriting",
-                                        "Functions",
-                                        "Libraries",
-                                        "Test data",
-                                        "Prediction tools",
-                                        "User interface",
-                                        ## Updatable
-                                        "Version controlled",
-                                        "Semantic versioning",
-                                        "Continuously integrated",
-                                        "Deprecation"
-                                       ),
-                           Assessment = c("Yes",
-                                        "Yes",
-                                        "Yes",
-                                        "Yes",
-                                        "No",
-                                        "Yes",
-                                        "Yes",
-                                        # Reuse
-                                        "Yes",
-                                        "Yes",
-                                        "Yes",
-                                        "Yes", # "Yes",
-                                        "Yes",
-                                        "Yes",
-                                        "Yes",
-                                        "Yes",
-                                        "No",
-                                        ## Updatable
-                                        "Yes",
-                                        "Yes",
-                                        "Yes",
-                                        "Yes"
-                                        ),
-                           Description = c("Datasets are available at https://doi.org/10.7910/DVN/DKDIB0 and https://doi.org/10.7910/DVN/HJXYKQ.
-For details of where to find Development and Archive code see: https://www.ready4-dev.com/docs/getting-started/software/libraries/types/module/  https://www.ready4-dev.com/docs/getting-started/software/executables/programs/  https://www.ready4-dev.com/docs/getting-started/software/executables/subroutines/ ",
-                                           "All code libraries have documenting websites with URLs that concatenate 'https://ready4-dev.github.io/' and the library name (e.g.
-https://ready4-dev.github.io/youthvars).
-All three Markdown programs are self-documenting, with one [@hamilton_matthew_2022_6129906] including additional instructions in a README file.
-Only one sub-routine [@matthew_p_hamilton_2022_5976988] is documented with a meaningful README file.
-All datasets have meaningful metadata descriptors.",
-                                           "All libraries are authored with ready4pack [@ready4pack2022] to ensure a consistent house style.
-All libraries except [@matthew_p_hamilton_2021_5646669] use framework syntax, as does one program [@hamilton_matthew_2022_6129906].",
-                                           "All programs use literate programming.",
-                                           "No current reporting of code coverage.",
-                                           "All parts of the study workflow from raw data ingest through to data processing, analysis, reporting and dissemination of study outputs can be reproduced (if granted access to source data) or replicated (using supplied synthetic data) with one program [@hamilton_matthew_2022_6129906].",
-                                           "All libraries can return citation details when running R's 'citation' function. All code and data repositories have tools to generate citation details.",
-                                           # Reuse
-                                           "All code libraries, programs and sub-routines use GPL-3 licenses. ",
-                                           "Datasets use amended version of template provided by Harvard Dataverse [@sampleterms2022].",
-                                           "All development code is stored on repos in a GitHub organisation [@ready4gh2022] and all archived code releases are available in a Zenodo community [@ready4zen2022].
-All non-confidential data are stored in repositories within a Harvard Dataverse collection [@ready4dv2022].
-",
-                                           "Four [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155] out of five libraries include encapsulating and inheriting modules.
-See: https://www.ready4-dev.com/docs/model/finding-modules/ ",
-                                           "All code libraries include functions.
-The most complete list of functions for each library is available by clicking the 'Manual - Developer (PDF)' link on each package's documentation homepage (see item A2 above).
-The relationship between functions can be illustrated using an app: https://www.ready4-dev.com/docs/getting-started/software/libraries/dependencies/",
-                                           "All module data-structures and algorithms are distributed as code libraries [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155; @matthew_p_hamilton_2021_5646669].",
-                                           "Two synthetic datasets and their data dictionaries are publicly available in a data repository [@DVN/HJXYKQ_2021].
-One (ymh_clinical_tb.RDS) closely resembles the study dataset and was released so that the main study algorithm [@hamilton_matthew_2022_6129906] can be rerun by those without access to the confidential study dataset.
-The other (eq5d_ds_tb.Rds) is deliberately different to the source dataset in both variable naming convention and the concepts used for predictors and outcome measures.
-It was created to demonstrate the transferability of study algorithms.",                                           #
-                                           "Model catalogues (PDF files beginning with 'AAA_TTU_MDL_CTG') are available in the study results dataset [@DVN/DKDIB0_2021] and describe the predictive performance of all models under a variety of usage regimes (including when the source dataset in the R model object is replaced with fake data).
-The youthu library [@matthew_p_hamilton_2021_5646669] includes tools for searching for and applying models compatible with different types of input data.
-An example program to demonstrate this functionality is available in both RMarkdown [@hamilton_matthew_2022_6416330] and rendered PDF formats (the 'Application.pdf' file in the study results dataset [@DVN/DKDIB0_2021]).
-",
-                                           "No user interface has yet been developed.",
-                                        ## Updatable
-                                           "All code is version controlled using git [@git20XX] and GitHub [@github2007]. All source code is available in a GitHub organisation [@ready4gh2022].",
-                                           "Semantic versioning is used in all code.
-As no code library has yet been submitted to CRAN [@CRAN2022], only the development version extensions of each version number have been incremented to date.",
-                                           "All five libraries use continuous integration (CI).
-CI results for each library can be viewed at a URL that concatenates 'https://github.com/ready4-dev/', the library name and '/actions' (e.g.
-https://github.com/ready4-dev/youthvars/actions)",
-                                           "Retired code is deprecated using tools from the lifecycle R library [@lifecycle2021] (e.g.
-everything after “## DEPRECATED FNS” in https://github.com/ready4-dev/youthvars/blob/main/data-raw/fns/add.R ).
-Package vignettes and datasets are also deprecated e.g.
-https://ready4-dev.github.io/youthvars/articles/Replication_DS.html )"
-                                          ))
-
-tb2_nms_chr<-colnames(checklist_df)
-checklist_df <- data.frame(checklist_df[,1],
-                           rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; "),
-                               nrow(checklist_df)),
-                           checklist_df[,2],
-                           rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp; &nbsp; "),
-                               nrow(checklist_df)),
-                           checklist_df[,3],
-                           rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; "),
-                               nrow(checklist_df)),
-                 checklist_df[,4])
-colnames(checklist_df) <- c(ifelse(params$X@outp_formats_chr[1] == "Word","Code"," "),
-                            ifelse(params$X@outp_formats_chr[1] == "Word","YYY"," "),
-                            "Standard",#
-                             ifelse(params$X@outp_formats_chr[1] == "Word","ZZZ","   "),
-                            "Met?",
-                            ifelse(params$X@outp_formats_chr[1] == "Word","AAA","   "),
-                            tb2_nms_chr[4])
+```{r checktb, tab.cap='Transparent, reusable and updatable (TRU) assessment criteria applied to outcome valuation computational health economic model (CHEM)', tab.id = 'checktb', echo = F, results = 'asis'}
+library(kableExtra)  
+df <- data.frame(FIRST = c("REPLACE", "THESE", "PLACEHOLDERS"),
+                 SECOND = c("A","B","C"),
+                 THIRD = c("ONE","TWO","THREE"),
+                 check.names = F)
 if(params$X@outp_formats_chr[1] == "Word") {
@@
   library("ftExtra")
-  checklist_df[,
-               c(1,3,5,7
-                  )] %>%
+  df %>%
     ready4show::print_table(output_type_1L_chr = params$X@outp_formats_chr[1],
@@
   }else{
-    checklist_df %>%
-    kableExtra::kbl(format = "markdown",
-                    booktabs = T,
-                    caption = knitr::opts_current$get("tab.cap")) 
+    df %>%
+      kableExtra::kbl(booktabs = T, 
+                      escape = F,
+                      caption = knitr::opts_current$get("tab.cap")) %>%
+      kableExtra::kable_paper(full_width = F) %>%
+      kableExtra::column_spec(1, bold=T) %>%
+      kableExtra::column_spec(3, width = "35em")
     }

### 2023-10-08 setup.R

@@ -37,15 +37,19 @@ X <- renewSlot(X,
                "abstract_args_ls",
                {
                  args_ls <- X@abstract_args_ls
-                 args_ls$abstract_ls <- list(Summary = "Computers are tools that are now essential to the work of health economists. 
-                                             However, the ethical dimensions of how health economic models are implemented computationally are poorly understood. 
-                                             Explicit ethical standards for computational health economic models (CHEMs) and the technical infrastructure to facilitate implementations of that meet those standards are required. 
-                                             We propose six criteria for assessing ethical implementation of CHEMs – two each for the three domains of transparency, reusability and updatability. 
-                                             To facilitate the implementation of CHEMs that meet these criteria, we developed a novel prototype software framework in the open source programming language R. 
-                                             The framework comprises six code libraries that collectively provide a toolkit for authoring CHEMs, supplying them with data and using them to undertake generalisable and transferable analyses.  
-                                             The framework supports integrations with existing digital services for collaborative software development and data archiving. We are currently applying the software framework to develop and apply utility mapping models in youth mental health. 
-                                             We assess the first set of utility mapping CHEMs that we have developed with the framework as wholly meeting both transparency criteria (open access code and data and clarity about author contributions and beliefs), one reusability criteria (liberal terms of use) and one updatability criteria (infrastructure for model maintenance) and partially meeting the two remaining criteria for transparency (supports generalisability and transferability) and updatability (retesting and deprecation).  
-                                             The assessment criteria and the software framework we have developed can inform future work to understand and improve ethical computational implementations of health economic models.",
+                 args_ls$abstract_ls <- list(Summary = "Computers are essential tools for health economists. 
+                                                        However, the ethical dimensions of how health economic models are implemented computationally are poorly understood and inadequately fulfilled. 
+                                                        We propose six criteria for assessing ethical implementation of computational health economic models (CHEMs) – two each for the three domains of transparency, reusability and updatability. 
+                                                        Citeria for assessing CHEM transparency include open access sharing of code and data and clarity about the contributions, assumptions and judgments of model developers. 
+                                                        CHEM reusability can be assessed against the criteria of development practices that promote generalisability and transferability and release under liberal terms of use.
[…]

### 2023-10-13 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
abstract edits

@@
 In seeking to solve these problems, health economists typically use models which are simplified and selective representations of systems that are believed to influence human health.
-A health economic model should be capable of being described using words and figures (a conceptual model), equations (a mathematical model) and computer code (a computational model).
+A health economic model should be capable of being described using words and figures (a conceptual model), equations (a mathematical model) and software (a computational model).
 Health economic scientific manuscripts typically describe a model using its conceptual and mathematical representations but report results that have been generated by its computational representation (i.e., through execution of a computer program that applies the computational model to selected input data).
 The conceptual, mathematical and computational representations of a model are assumed to be isomorphic.
-However, the ease of independently assessing the validity of this assumption depends in part on how a health economic model has been implemented computationally.
+However, the ease of independently assessing the validity of this assumption depends in part on how a health economic model has been implemented as software.
 

### 2023-10-13 setup.R

@@ -37,19 +37,17 @@ X <- renewSlot(X,
                "abstract_args_ls",
                {
                  args_ls <- X@abstract_args_ls
-                 args_ls$abstract_ls <- list(Summary = "Computers are essential tools for health economists. 
-                                                        However, the ethical dimensions of how health economic models are implemented computationally are poorly understood and inadequately fulfilled. 
-                                                        We propose six criteria for assessing ethical implementation of computational health economic models (CHEMs) – two each for the three domains of transparency, reusability and updatability. 
-                                                        Citeria for assessing CHEM transparency include open access sharing of code and data and clarity about the contributions, assumptions and judgments of model developers. 
-                                                        CHEM reusability can be assessed against the criteria of development practices that promote generalisability and transferability and release under liberal terms of use.
-                                                        The updatability of CHEMS can be assessed against the criteria of use of technical infrastructure to support model maintenance and quality assuring new releases through retesting and deprecation conventions.
-                                                        To facilitate the implementation of CHEMs that meet these criteria, we developed a novel prototype software framework called ready4. 
-                                                        Software frameworks are technologies that facilitate collaborative and efficient code development.
-                                                        The ready4 framework, comprised of six code libraries in the programming language R, provides a toolkit for authoring modular and open-source CHEMs, supplying CHEMs with data and using CHEMs to undertake reproducible analyses. 
-                                                        The ready4 framework supports integrations with existing digital services for collaborative software development and data archiving. 
-                                                        We are currently applying the ready4 framework to develop and apply CHEMs in youth mental health. 
-                                                        We determined that the first set of CHEMs developed with the ready4 framework wholly met both transparency criteria and both reusability criteria. We further determined that these CHEMs wholly met the updatability criterion relating to model maintenance infrastructure  and partially met the criterion concerning retesting and deprecation. 
-                                                        The assessment criteria and the software framework we have developed can inform future work to understand and improve ethical CHEM implementations.",
+                 args_ls$abstract_ls <- list(Summary = "The ethical dimensions of implementing health economic models as software are poorly understood. 
+                                                        We propose that the core responsibilities of computational health economic model (CHEM) developers over a project lifecycle are to (i) make socially acceptable design decisions; (ii) ensure fit for purpose development; and (iii) support socially beneficial use. 
+                                                        We further propose that a transparent, reusable and updatable CHEM is suggestive of a modelling team that has largely fulfilled these responsibilities.
[…]

### 2023-10-14 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
redo of intro

--- 2023-08-16 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
@@
 
-In this paper, we describe:
+In this paper, we:
 
-(i)	criteria for assessing ethical CHEM implementations;
+(i)	propose core ethical responsibilities for CHEM developers and criteria for assessing ethical CHEM implementations;
 
-(ii) a prototype software framework for the ethical implementation of CHEMs; and
+(ii) describe a prototype software framework we have developed to support the ethical implementation of CHEMs; and
 
-(iii)	use of the software framework to develop an open-source CHEM in youth mental health, with an initial focus on outcome valuation.
+(iii)	assess an initial set of youth mental health CHEMs developed with our software framework against our proposed ethical CHEM implementation criteria.

### 2023-10-14 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
redo of intro

@@
 A health economic model should be capable of being described using words and figures (a conceptual model), equations (a mathematical model) and software (a computational model).
-Health economic scientific manuscripts typically describe a model using its conceptual and mathematical representations but report results that have been generated by its computational representation (i.e., through execution of a computer program that applies the computational model to selected input data).
+Health economic scientific manuscripts typically describe a model using its conceptual and mathematical representations but report results that have been generated by its computational representation (i.e., in a format that allows computers to perform calculations).
 The conceptual, mathematical and computational representations of a model are assumed to be isomorphic.
-However, the ease of independently assessing the validity of this assumption depends in part on how a health economic model has been implemented as software.
-
+However, the ease of independently assessing the validity of this assumption depends in part on how a health economic model has been implemented computationally.
+<!-- through execution of a computer program that applies the computational model to selected input data). -->
 <!-- the execution of a computer program that applies a computational model to compatible data inputs (e.g., parameter values) and performs a sequence of numeric calculations. -->
@@
 
-Computational health economic models (CHEMs) can be implemented using specialised commercial modelling software or authored as software development projects in an open-source programming language such as Python [@python2009] or R [@RCORE2022].
-Advantages of commercial modelling tools include simplicity and ease of use, but an open-source software development approach may facilitate computational models that are more transparent, reusable and updatable [@incerti2019r; @Pouwels2022].
-The decision about what implementation approach to adopt needs to balance both modelling team value judgments about priority model features and the resource and time constraints within which a CHEM project needs to be delivered (see Table \@ref(tab:proscons)).
+The set of digital files implementing a health economic model's structure, data and algorithms as software can be called a computational health economic model (CHEM).
+CHEMs can be developed using specialised commercial modelling software or in an open-source programming language such as Python [@python2009] or R [@RCORE2022].
+An advantage of commercial modelling software is that users often require no or limited programming skills to develop and apply CHEMs.
+However, open-source software programming languages may facilitate the development of CHEMs that are more transparent, reusable and updatable [@incerti2019r; @Pouwels2022].
+The decision about what software development approach to adopt needs to balance both modelling team value judgments about priority CHEM features and the skills, resource and time constraints within which a CHEM project needs to be delivered (see Table \@ref(tab:proscons)).
 
@@
 ```
+
+Within the health economics discipline, open-source CHEMs remain rare [@Feenstra2022; @Emerson2019].
+The main barriers to open-source CHEMs identified in a 2020 survey of health economists concern challenges relating to updating models, legal considerations, transferring model data, the platforms or languages in which models are developed, the level of public access required, lack of interest from decision-makers, model generalisability and confidentiality and security considerations [@Pouwels2022].
+<!-- A major consideration in open-source software development, is the selection of an appropriate software framework.  -->
 <!-- on considerations such as model comprehensiveness, generalisability, reproducibility and transferability -->
-For open-source software projects, a major consideration is the selection of an appropriate software framework.
+
+Some of these barriers could potentially be mitigated through the development of appropriate software frameworks.
 A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users [@myllarniemi2018development].
 A software framework provides a foundation for developing multiple software applications with shared resources (e.g., code and data files), that can be modified to suit specific needs.
+Advantages of using software frameworks include facilitating code reuse and extension, promoting good programming practice and the capability to provide enhanced functionality and performance without additional effort by developers [@edwin2014software].
 Software frameworks have widely been developed and implemented in data science, for example, PyTorch [@PyTorch2019] for machine learning using Python.
-
-Advantages of using software frameworks include facilitating code reuse and extension, promoting good programming practice and the capability to provide enhanced functionality and performance without additional effort by developers [@edwin2014software].
-However, software frameworks can be challenging and time consuming to create [@edwin2014software] and then difficult for others to learn, often requiring model developers to undergo specialist training [@myllarniemi2018development].
-There is also a risk that a software framework may become excessively complex over time [@edwin2014software].
 
@@
 <!-- When making choices about how to implement this health economic model computationally, we wished to facilitate ethical development and use. -->
-The ethical responsibilities of computational modellers seeking to inform policy decisions are often poorly understood and inadequately fulfilled [@10.3389/fpubh.2017.00068; @pliakos2021ethics; @thompson2022escape; @calder2018computational].
-Within the health economics discipline, open-source CHEMs remain rare [@Feenstra2022; @Emerson2019].
-The main barriers to open-source CHEMs identified in a 2020 survey of health economists concern challenges relating to updating models, legal considerations, transferring model data, the platforms or languages in which models are developed, the level of public access required, lack of interest from decision-makers, model generalisability and confidentiality and security considerations [@Pouwels2022].
 
-There is a potential role for software frameworks to help health economic modellers overcome some of these barriers.
 A high-level software framework for implementing open-source CHEMs in R has previously been developed with the primary aim of improving model transparency [@alarid2019need].
-Ideally, software frameworks would facilitate fulfillment of a broader set of ethical responsibilities.
-However, guidance on developing, selecting and using software frameworks for ethical CHEM implementations is scarce.
+A software framework that help CHEM developers fulfill a broader set of ethical responsibilities would require a number of conceptual, technical and behavioural challenges to be overcome.
+Firstly, the ethical responsibilities of developers of computational models designed to inform governmental decision-making are often poorly understood <!-- and inadequately fulfilled  -->[@10.3389/fpubh.2017.00068; @pliakos2021ethics; @thompson2022escape; @calder2018computational].
+Software frameworks can be challenging and time consuming to create and may become excessively complex over time [@edwin2014software].
+Furthermore, software frameworks can be difficult to learn, often requiring model developers to undergo specialist training [@myllarniemi2018development].
+<!-- a software framework is unlikely to be widely adopted unless the benefits to developers outweigh the costs associated with using it. -->
+<!-- However, guidance on developing, selecting and using software frameworks for ethical CHEM implementations is scarce. -->
 

### 2023-10-14 setup.R

@@ -13,7 +13,7 @@ X <- Ready4showSynopsis(#background_1L_chr = "Our study is entirely fictional.",
                         keywords_chr = c("open source models","health economics","mental disorders"),
                         outp_formats_chr = "PDF",
                         #sample_desc_1L_chr = "The study sample is fake data that pretends to be young people aged 12 to 25 years who attended Australian primary care services for mental health related needs between November 2019 to August 2020.",
-                        title_1L_chr = "A prototype software framework for transparent, reusable and updatable health economic models")
+                        title_1L_chr = "A prototype software framework for transparent, reusable and updatable computational health economic models")
 X <- renewSlot(X,
                "authors_r3", 
                {
@@ -37,16 +37,16 @@ X <- renewSlot(X,
                "abstract_args_ls",
                {
                  args_ls <- X@abstract_args_ls
-                 args_ls$abstract_ls <- list(Summary = "The ethical dimensions of implementing health economic models as software are poorly understood. 
-                                                        We propose that the core responsibilities of computational health economic model (CHEM) developers over a project lifecycle are to (i) make socially acceptable design decisions; (ii) ensure fit for purpose development; and (iii) support socially beneficial use. 
-                                                        We further propose that a transparent, reusable and updatable CHEM is suggestive of a modelling team that has largely fulfilled these responsibilities.
-                                                        We propose six criteria for assessing the transparency (T), reusability (R) and updatability (U) of CHEMs: (T1) Software files are published in open access repositories; (T2) It is easy to identify the underpinning judgments and individual contributions of CHEM developers; 
-                                                        (R1) Programming practices that promote generalisability and transferability have been used; (R2) Open source licenses have been used; (U1) Maintenance infrastructure is in place; and 
-                                                        (U2) New CHEM versions are systematically retested and appropriately deprecated.
+                 args_ls$abstract_ls <- list(Summary = "Most health economic analyses are undertaken with the aid of computers. However, the ethical dimensions of implementing health economic models as software are poorly understood. 
+                                                        We propose that the core responsibilities of health economic model software developers over a project lifecycle are to (i) make socially acceptable design decisions; (ii) ensure fit for purpose implementation; and (iii) support socially beneficial use. 
+                                                        We further propose that a transparent (T), reusable (R) and updatable (U) computational health economic model (CHEM) is suggestive of a developer team that has largely fulfilled these responsibilities.
+                                                        We propose six TRU criteria for assessing CHEMs: (T1) software files are open access; (T2) developer judgments and contributions are easily identified; 
[…]

### 2023-10-16 Markdown/Manuscript/Child_RMDs/MS_Conclusion.Rmd
close to submission update - except tables

--- 2022-05-30 Markdown/Manuscript/Child_RMDs/MS_Conclusion.Rmd
@@
 `r ifelse(is.na(params$X@conclusion_1L_chr),"",params$X@conclusion_1L_chr)` 
-<!-- Standards generalisable, Toolkit less os -->
+We have identified criteria that can be used to systematically assess the extent to which the computational implementation of health economic models adheres to transparency, reusability and updatability criteria.
+We have developed a prototype software framework that can support the implementation of CHEMs that largely meet these criteria.
+Our framework can be used as a prototype for developing future software frameworks to support ethical implementation of CHEMs.

### 2023-10-16 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
close to submission update - except tables

@@
 Ethical practice is a core expectation of health researchers and computational methods underpin most quantitative research, yet an understanding of what constitutes ethical computational modelling practice in health is underdeveloped [@10.3389/fpubh.2017.00068].
-The modeller responsibilities, enabling model attributes and model implementation assessment criteria that we propose can help address this gap.
+We have addressed this gap with our proposed modeller and funder responsibilities, enabling model attributes and model implementation assessment criteria.
 
-The ethical responsibilities and enabling model attributes we describe have both commonalities and distinctive features compared to a previous ethical framework for computational modelling in public health [@10.3389/fpubh.2017.00068].
-The authors of that framework propose 13 questions to evaluate ethical risk across the four criteria of independence, transparency, beneficence and justice.
-Their descriptions of the four criteria at least partially map to either our proposed modeler responsibilities (“justice” to “social acceptability”, “independence” to “adequacy for purpose” and “beneficence” to “beneficial impact”) or enabling model attributes (“transparency”).
-However, while our six assessment criteria are specific to three attributes (TRU) of the computational implementation of the model, the prior ethical framework includes questions relevant to the conceptual and mathematical models and the potential impacts of model use.
-Examples of these more general evaluation questions include (for the justice criterion) “is any lack of knowledge about important parameters attributable to uncertainty or variability?” and (for the beneficence criterion) “if a policy is based on the model evidence, is it more likely to be effective and beneficial than a decision made in the absence of the model?”.
-The less numerous and more focused assessment criteria we propose may potentially be more tractable to implement in reviews of models authored by third parties and as the basis for designing software frameworks to support ethical computational model implementation.
+<!-- The less numerous and more focused assessment criteria we propose may potentially be more tractable to implement in reviews of models authored by third parties and as the basis for designing software frameworks to support ethical computational model implementation.
+-->
 
-Currently, many if not most existing CHEMs are insufficiently transparent [@Jalali2021; @McManus2019; @Bermejo2017; @Ghabri2019], reusable [@Feenstra2022; @Emerson2019] and updatable [@Sampson2017; @10.3389/fpubh.2022.899874]].
-<!-- DELETION --> Existing incentive structures for health economists generally do not promote facilitating peers to reuse their work.
-Currently, it can take “an extraordinary amount of idealism” to commit to authoring and maintaining research software [@anzt2020environment].
+<!-- Two issues for funders - allow support for beneficial use, foster viable communities. -->
+
+Currently, many if not most existing CHEMs are insufficiently transparent [@Jalali2021; @McManus2019; @Bermejo2017; @Ghabri2019], not reusable [@Feenstra2022; @Emerson2019], nor updatable [@Sampson2017; @10.3389/fpubh.2022.899874].
+<!-- DELETION --> Addressing these issues will require changes to the tools, practices and funding underpinning health economic model development.
+
+As illustrated by Table \@ref(tab:checktb), we have developed a prototype software framework that can be used to implement youth mental health CHEMs that largely satisfy our TRU criteria.
+However, in its current form our software framework is too fragile to be anything more than a prototype for supporting the development needs other modelling teams and projects.
+We developed our prototype software framework was developed with the needs of only one group of developers in mind – ourselves.
+We currently lack the resources required to adequately implement strategies to target factors such as user enjoyment, usability, active user-community and supporting resources that influence adoption of software frameworks [@myllarniemi2018development].
+
+Our prototype has a number of features that subsequent work to develop CHEM software frameworks may find useful to incorporate.
+Firstly, developing a software framework to work within an existing and widely used open source programming language such as R or python, can keep framework scope relatively narrow.
+This makes it more tractable to develop, maintain and learn, and can integrate other modelling tools written in that language (e.g., the dependency libraries we list in Table \@ref(tab:cpkgs)).
+Secondly, implementation that combines both object oriented and functional programming paradigms can avail of the modular and syntactical simplicity benefits of the former, while limiting needless bundling of code artefacts.
+Thirdly, a sensible trade-off needs to be found between transparent code implementation (which requires clear and sufficiently detailed documentation) and Agile Software Development (for which a foundational principle is prioritising the development of working code over writing documentation [@beck2001manifesto]).
+Our software framework makes this trade off by enforcing the use of consistent code naming conventions and file organisation which in turn enables automated generation of simple documentation at every code update.
+All model data-structures and algorithms are therefore always documented (at least minimally, with machine authored content), meaning model developers have a requirement to write customised documentation less frequently.
 
 Reducing waste in research is a core responsibility of research funders [@chalmers2014increase] and funding the development of CHEMs that are not adequately understood, reused or updated is wasteful.
-Previously recommended strategies for more beneficial health economic research investments include support for harmonized ethical standards for model development [@10.3389/fpubh.2017.00068], methodological innovation to improve model transferability  [@craig2018taking], networks of modellers working on common health conditions [@Sampson2019], and  centralized infrastructure such as open source model repositories [@Pouwels2022] and a standard platform for model implementations [@Ghabri2019].
+Existing incentive structures for health economists generally do not promote facilitating peers to reuse their work and funding is rarely adequate to maintain an routinely update a model.
+Currently, it can take “an extraordinary amount of idealism” to commit to authoring and maintaining research software [@anzt2020environment].
+Previously recommended strategies for more beneficial health economic research investments include support for harmonised ethical standards for model development [@10.3389/fpubh.2017.00068], methodological innovation to improve model transferability [@craig2018taking], networks of modellers working on common health conditions [@Sampson2019], and  centralized infrastructure such as open source model repositories [@Pouwels2022] and a standard platform for model implementations [@Ghabri2019].
 Development of software frameworks to support ethical CHEM implementations could enable and enhance each of these strategies.
 
-As illustrated by Table \@ref(tab:checktb), we have developed a software framework that can help us to author a youth mental health model that largely satisfy our TRU criteria.
-However, we believe our software framework is currently too fragile to be anything more than a prototype for supporting the development needs other modelling teams and projects.
-A major reason for this distinction is that our software framework was developed with the needs of only one group of developers in mind – ourselves.
-We currently lack the resources required to adequately implement strategies to target factors such as user enjoyment, usability, active user-community and supporting resources that influence adoption of software frameworks [@myllarniemi2018development].
-
-Our prototype framework has a number of features that subsequent work to develop ethical software frameworks may find useful to incorporate.
-Firstly, developing a software framework to work within an existing and widely used open source programming language such as R or python, can keep framework scope relatively narrow (making it more tractable to develop, maintain and learn) while readily leveraging and coherently integrate other modelling tools written in that language (e.g.
-the dependency libraries we list in Table \@ref(tab:cpkgs)).
-Secondly, implementation that combines both object oriented and functional programming paradigms can avail of the modular and syntactical simplicity benefits of the former, while limiting needless bundling of code artefacts.
-Thirdly, a sensible trade-off needs to be found between transparent code implementation (which requires clear and sufficiently detailed documentation) and Agile Software Development (for which a foundational principle is prioritizing the development of working code over writing documentation [@beck2001manifesto]).
-Our software framework makes this trade off by enforcing the use of consistent code naming conventions and file organisation which in turn enables automated generation of simple documentation at every code update.
-All model data-structures and algorithms are therefore always documented (at least minimally, with machine authored content), meaning model developers have a requirement to write customized documentation less frequently.
-
 A future software framework for ethical CHEMs would ideally incorporate a base set of features useful to developers of computational models across all domains of public health, with the capability for community-led extensions that are tailored to the needs of modellers focused on specific health-conditions.

### 2023-10-16 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
close to submission update - except tables

@@
 ##	Economic topics
-Currently, we are using the ready4 software framework to develop, apply and share youth mental health CHEMs in four of the twelve domains of health economics identified by Wagstaff and Culyer [@wagstaff2012four]:
+Currently, we are using the ready4 software framework to develop, apply, and share youth mental health CHEMs in four of the twelve domains of health economics identified by Wagstaff and Culyer [@wagstaff2012four]:
 
--	health and its value (our projects: utility mapping models);
+-	health and its value (our projects: models to map psychological and functional measures to health utility);
 
@@
 
-Potential future directions are to supplement this work with CHEMs in two additional Wagstaff and Culyer domains of public health (to model the impact of selected fiscal policy and regulation options on young people's mental health) and human resources (to model the supply and behaviours of the youth mental health workforce).
+Potential future directions are to supplement this work with CHEMs in two additional Wagstaff and Culyer domains of: (i) public health (to model the impact of selected fiscal policy and regulation options on young people's mental health); and (ii) human resources (to model the supply and behaviours of the youth mental health workforce).
 Our ultimate aim is to flexibly combining all our CHEMs in analyses that help answer questions in two additional Wagstaff and Culyer domains:
@@
 
-Although principally interested in using our CHEMs to answer policy questions relating to the mental health of young people in Australia, we want to facilitate CHEM transferability to other jurisdictions.
-Our CHEMs are therefore being derived from and applied to real data (which can be assumption, empirical or simulated, so long as it is appropriate for use in analysis intended to inform decision-making) from Australia.
-Additionally, we plan for all our CHEMs to be distributed with toy (fake) data to help demonstrate the potential use of these CHEMS in other decision contexts.
+Although we are principally interested in using CHEMs to answer policy questions relating to the mental health of young people in Australia, we want to facilitate CHEM transferability to other jurisdictions.
+Our CHEMs are being derived from and applied to real data (which can be assumption, empirical or simulated, so long as it is appropriate for use in analysis intended to inform decision-making) from Australia.
+To help demonstrate the potential use of CHEMs in other decision contexts, we also create toy datasets.
+Data created for illustration purposes is prominently labelled as not for use in decision-analysis.
 
 ## Case study: health and its value
-We have previously described [@Hamilton2021.07.07.21260129] a study to develop utility mapping models for use in samples of young people presenting to primary mental health services.
+We have previously describeda study [@Hamilton2021.07.07.21260129] to develop utility mapping models for use in samples of young people presenting to primary mental health services.
 The ready4 software framework was used in that study to develop CHEM modules, supply those modules with data and implement modelling analyses, creating the following artefacts:
@@
 For each criterion, we provided a global assessment of whether it was met using the responses “yes”, “no” or “partial”.
-We believe the outputs from our utility mapping study may be assessable as having satisfactorily met five of the six criteria (T1, T2, R1, R2 and U1) and to have partially met one criterion (U2).
-The main shortcomings that we identified when applying the assessment criteria was that we have yet to adequately implement unit testing of the R libraries we authored as part of this study.
+We believe our utility mapping study CHEMs have satisfactorily met five of the six criteria (T1, T2, R1, R2 and U1) and have partially met one criterion (U2).
+The main shortcomings that we identified when applying the assessment criteria was that we have yet to adequately implement unit testing of the R libraries authored as part of this study.
 

### 2023-10-16 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
close to submission update - except tables

@@
 
-We considered prior literature on modelling practice and our own professional experience to identify: (i) some core ethical responsibilities of CHEM developers; (ii) attributes of CHEMs that can suggest fulfillment of these responsibilities; and (iii) criteria against which these attributes can be assessed.
+We considered prior literature on modelling practice and our own professional experience to identify: (i) some core ethical responsibilities of CHEM developers and funders; (ii) attributes of CHEMs that can suggest fulfillment of these responsibilities; and (iii) criteria against which these attributes can be assessed.
 
-## Ethical responsibilities of CHEM developers 
-For simplicity, we sought to identify one overarching ethical responsibility for modellers at each distinct phase of a CHEM project.
-As CHEMs are implemented as software, software development lifecycle (SDLC) models may provide an appropriate basis for identifying the main phases of a CHEM project.
-There are multiple SDLC models, each taking a different approach to the number, naming, definition, sequencing and iteration of project phases [@ruparelia2010software].
-However, components of most SDLC models can broadly be mapped to the concepts of *planning* (in which software requirements and design specification are agreed), *development* (in which software is authored and tested) and *deployment* (in which software is made available as production ready tools for end-users).
-We contend that ethical responsibilities of computational modellers identified in prior literature [@10.3389/fpubh.2017.00068; @pliakos2021ethics; @thompson2022escape; @calder2018computational] can be summarised under the following three overarching goals (one for each phase):
+## Ethical responsibilities of CHEM developers and funders
+<!-- The ethical responsibilities and enabling model attributes we describe have both commonalities and distinctive features compared to a previous  -->
+Boden and McKendrick [@10.3389/fpubh.2017.00068] proposed a framework for ethical computational modelling in public health based on the four ethical criteria of justice (concerning the social obligations of modellers to consider and communicate ethical issues), independence (concerning how modeller subjectivity shapes model design), transparency (concerning the need for policymakers to reliably evaluate model strengths and weaknesses) and beneficence / non-maleficence (concerning model quality and utility).
+However, the framework's authors mostly discuss these criteria in the context of a modelling project as a whole, including a model's conceptual and mathematical representations.
+The authors propose 13 questions to evaluate ethical risk across the four criteria, but of these only "is the model code open source or available on request" (for transparency) and "has the model been verified, i.e., does it do what the modeller wants it to do?" (for beneficence / non-maleficence) are specific to model's representation as software.
 
-- **make socially acceptable value judgments** (when planning CHEM projects);
+To reconceptualise these four criteria as ethical responsibilities that are specific to CHEM developers and funders, we first considered the distinct phases in a software development project.
+Software development lifecycle (SDLC) models take different approaches to the inclusion, naming, definition, sequencing and iteration of project phases [@ruparelia2010software].
+However, SDLC models typically have components that can principally map to the concepts of *planning* (e.g.
+identification of system / user requirements and design specifications), *implementation* (e.g.
+development and testing) and *release* (e.g.deployment, system integration and maintenance).
+For simplicity, we propose one overarching ethical responsibility for CHEM developers and funders for each of these phases.
+These responsibilities are to:
 
-- **ensure model fitness for purpose** (when developing CHEMs); and
+(i) **make socially acceptable system requirements and design decisions** (during CHEM planning);
 
-- **promote socially beneficial use of models** (once CHEMs have been deployed).
+(ii) **ensure fitness for purpose** (of CHEM implementation); and
 
-There is significant scope for health economists to improve fulfilment of each of these responsibilities.
+(iii) **support socially beneficial use** (on CHEM release).
+
+Each responsibility combines different aspects of Boden and McKendrick's ethical criteria: responsibility (i) incorporates justice and independence; responsibility (ii) incorporates independence and transparency; and responsibility (iii) incorporates beneficence / non-maleficence and justice.
+Model developers and funders share these responsibilities as each one has implications for both professional practice and project resourcing.
+
+<!-- . The authors of that framework propose 13 questions to evaluate ethical risk across the four criteria of  -->
+<!-- .
+However, while our six assessment criteria are specific to three attributes (TRU) of the computational implementation of the model, the prior ethical framework includes questions relevant to the conceptual and mathematical models and the potential impacts of model use.
+Examples of these more general evaluation questions include (for the justice criterion) “is any lack of knowledge about important parameters attributable to uncertainty or variability?” and (for the beneficence criterion) “if a policy is based on the model evidence, is it more likely to be effective and beneficial than a decision made in the absence of the model?”.
+-->
+
+<!-- Multiple ethical considerations of computational modeling have previously been identified [@10.3389/fpubh.2017.00068; @pliakos2021ethics; @thompson2022escape; @calder2018computational],  -->
 
 Misalignment between the values of computational model developers and those of the population groups affected by decisions based on their models presents significant ethical risks [@thompson2022escape; @duckett2022journey].
-The value judgments of CHEM developers influence the assumptions, selection of model features and standards for evidence that shape the model development process [@HARVARD2020112975].
+The value judgments of health economists influence the assumptions, selection of model features and standards for evidence that shape health economic model projects [@HARVARD2020112975].
 These value judgments are rarely made explicit, omissions that may lead to socially unacceptable policy recommendations [@duckett2022journey].
-Ideally, it should be straightforward for CHEMs to be modified to reflect alternative value judgments.
-However, such adaptability depends in part on the approach taken to computational model implementation (see Table \@ref(tab:proscons)).
+modeller value judgments also determine the computational implementation of health economic models.
+For example, as illustrated in Table \@ref(tab:proscons), project resource constraints may require trade offs between desired CHEM **system requirements and design** features.
+These trade offs in turn determine how straightforward it is for CHEMs to be amended by third parties to reflect alternative value judgments in model conceptualisation and mathematical formalisation (Table \@ref(tab:timelygls)).
 
@@
 
-Computational modellers have duties both to take sufficient care that a computational model is adequate for the explicit purpose for which it was developed and to provide potential third-party users with the means of assessing its adequacy for their proposed purposes [@Erdemir2020; @Feenstra2022; @thompson2019escape; @10.3389/fpubh.2017.00068].
+Computational modellers have duties both to ensure computational model **fitness for purpose** and to provide potential third-party users with the means of assessing its adequacy for their proposed purposes [@Erdemir2020; @Feenstra2022; @thompson2019escape; @10.3389/fpubh.2017.00068].
 However, it is common for health economic models to have serious methodological flaws [@carletto_zanuzzi_sammarco_russo_2020; @WONDER2015467]; insufficient validation [@Ghabri2019; @kolovos2017model; @haji2013model], poor reproducibility [@Jalali2021; @McManus2019; @Bermejo2017]; and undeclared errors [@Radeva2020].
@@
 
-A health economic model will have limited public benefit if it not much used, if it is mis-used or when its acceptability and adequacy rapidly decay.
+A CHEM will have limited **social benefit** if it is rarely used, if mis-used or when its acceptability and adequacy rapidly decay.
 Reuse of CHEMs as components of other models can potentially make model development more efficient [@Arnold2010; @garcia2021cost].
@@
 ## CHEM attributes associated with ethical modelling practice
-Health economist responsibilities during the planning, implementation and use of CHEMs are easier to state than to measure.
+The responsibilities of model developers and funders over a CHEM lifecycle are easier to state than to measure.
 However, aspects of ethical modelling practice may be inferred from measurable attributes of CHEMs.
@@
 Notably, the same guidelines, published over ten years ago, did not recommend sharing model code and data.
-However, more recent healthcare modelling guidance does recommend publicly dissemination of such artefacts [@Erdemir2020].
+However, more recent healthcare modelling guidance does recommend public dissemination of such artefacts [@Erdemir2020].
 Online repository services such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each code and data collection.
@@
 Models should be **updatable** so that they remain valid for longer, evolving as new evidence emerges and the systems being modelled change [@Jenkins2021; @garcia2021cost].
-Ensuring that a model is regularly reviewed to identify and implement required improvements is a recommended defense against model validity decay [@calder2018computational].
+Ensuring that a model is regularly reviewed to identify and implement required improvements is a recommended defence against model validity decay [@calder2018computational].
 Sustainable maintenance of open source research software requires both a core development team and an active user community [@info:doi/10.2196/20028].
@@
 
--	**T1**: All model code, non-confidential data and testing procedures and outcomes are available in open access repositories.
+-	**T1**: Software files (executable code, testing procedures and outcomes and non-confidential data) are available in open access repositories.
 
--	**T2**: It is easy to see who developed and tested each part of the CHEM and to identify the modelling team’s assumptions, judgments and theories about CHEM development and use.
+-	**T2**: It is easy to see who funded, developed and tested each part of the CHEM and to identify the modelling team’s assumptions, judgments and theories about CHEM development and use.
 
@@
 
--	**R1**: Model code and data are implemented to facilitate both generalisability and transferability.
+-	**R1**: Programming practices facilitate both generalisability and transferability.
 
--	**R2**: Terms of use allow anyone to reuse model code and non-confidential data, in whole or in part, without charge, and for purposes that include the creation of derivative works.
+-	**R2**: Terms of use place only ethical restrictions on reuse and allow anyone to ethically reuse model code and non-confidential data, in whole or in part, without charge, and for purposes that include the creation of derivative works.
 
@@
 
--	**U1**: Technical infrastructure is in place to support version control and collaboration with model users in the maintenance of a model.
+-	**U1**: Maintenance infrastructure is in place to support version control and collaboration with model users.
 
--	**U2**: Each new release of a model is retested, with changes implemented to minimize disruptions for existing model users.
+-	**U2**: Each new release of a model is systematically retested, with changes implemented to minimise disruptions for existing model users.

### 2023-10-16 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
close to submission update - except tables

@@
 ## R libraries 
-A library in the R language will typically depend on multiple other R libraries, all of which potentially having different authors.
-As the number of third-party dependencies of an R library grows so does the fragility of that library (e.g.
-the library may cease to work as intended due to changes in one of its dependency libraries).
+A library in the R language will typically depend on multiple other R libraries, all of which potentially have different authors.
+As the number of third-party dependencies of an R library grows so does the fragility of that library (e.g., the library may cease to work as intended due to changes in one of its dependency libraries).
 To reduce the fragility of our framework we implemented it as multiple R libraries rather than one R library.
@@
 One of these inherited properties is a novel syntax of 15 core commands that enable CHEM module algorithms to be consistently named.
-The foundation library also contains tools for retrieving web-based information on CHEM modules, datasets and analysis programs authored with the framework and for partially automating updates to a project documentation website.
+The foundation library also contains tools for retrieving web-based information on CHEM modules, datasets and analysis programs authored with the framework and tools for partially automating updates to a project documentation website.
 
@@
 
-A library for **managing CHEM data** contains tools for supplying CHEM modules with input data ingested from local (i.e.
-a user's computer) or remote (online repositories) locations, labelling CHEM module datasets and exporting CHEM module data to online repositories.
+A library for **managing CHEM data** contains tools for supplying CHEM modules with input data ingested from local (i.e., a user's computer) or remote (online repositories) locations, labelling CHEM module datasets and exporting CHEM module data to online repositories.
 A library for **authoring reproducible analyses** contains tools to help write programs that apply CHEM modules to compatible datasets for the purpose of undertaking health economic analyses.
-These analysis programs can be either self-documenting (code is integrated with plain English explanations of what it does) or trigger the creation of separate documents (e.g.
-a scientific manuscript).
+These analysis programs can be either self-documenting (code is integrated with plain English explanations of what it does) or trigger the creation of separate documents (e.g., a scientific manuscript).
 
@@
 
-We created a GitHub organisation (a collection of code repositories) where code (libraries, programs and sub-routines) that we author for and with the framework is stored and version controlled.
+We created a GitHub organisation (a collection of code repositories) where source code that we author is stored and version controlled.
 We configured individual repositories in our GitHub organisation to use GitHub actions to implement continuous integration.

### 2023-10-16 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
close to submission update - except tables

@@
 A health economic model should be capable of being described using words and figures (a conceptual model), equations (a mathematical model) and software (a computational model).
-Health economic scientific manuscripts typically describe a model using its conceptual and mathematical representations but report results that have been generated by its computational representation (i.e., in a format that allows computers to perform calculations).
+Health economic scientific manuscripts typically describe a model using its conceptual and mathematical representations but report results that have been generated by its computational representation (i.e., the format that allows computers to perform calculations).
 The conceptual, mathematical and computational representations of a model are assumed to be isomorphic.
@@
 The set of digital files implementing a health economic model's structure, data and algorithms as software can be called a computational health economic model (CHEM).
-CHEMs can be developed using specialised commercial modelling software or in an open-source programming language such as Python [@python2009] or R [@RCORE2022].
+CHEMs can be developed using commercial modelling software or in an open-source programming language such as Python [@python2009] or R [@RCORE2022].
 An advantage of commercial modelling software is that users often require no or limited programming skills to develop and apply CHEMs.
 However, open-source software programming languages may facilitate the development of CHEMs that are more transparent, reusable and updatable [@incerti2019r; @Pouwels2022].
-The decision about what software development approach to adopt needs to balance both modelling team value judgments about priority CHEM features and the skills, resource and time constraints within which a CHEM project needs to be delivered (see Table \@ref(tab:proscons)).
+The decision about what type of software development platform to use needs to balance ethical and pragmatic considerations  (see Table \@ref(tab:proscons)).
+
+<!-- modelling team value judgments about priority CHEM features and the skills, resource and time constraints within which a CHEM project needs to be delivered -->
 
@@
 
-Within the health economics discipline, open-source CHEMs remain rare [@Feenstra2022; @Emerson2019].
-The main barriers to open-source CHEMs identified in a 2020 survey of health economists concern challenges relating to updating models, legal considerations, transferring model data, the platforms or languages in which models are developed, the level of public access required, lack of interest from decision-makers, model generalisability and confidentiality and security considerations [@Pouwels2022].
+Open-source CHEMs remain rare [@Feenstra2022; @Emerson2019].
+Additional resources, skills and tools may be required to overcome a number of barriers to greater health economist adoption of open-source development.
+CHEM software development platforms were identified in a 2020 survey of health economists as a barrier to open-source model implementations  [@Pouwels2022].
+Other reported barriers relate to difficulties in generalising models, updating models and transferring model data, concerns about the level of public access required and lack of interest from decision-makers, and legal, confidentiality and security considerations [@Pouwels2022].
+
 <!-- A major consideration in open-source software development, is the selection of an appropriate software framework.  -->
 <!-- on considerations such as model comprehensiveness, generalisability, reproducibility and transferability -->
+<!-- Although there appears to be in principle support from many health economists for greater use of open source health economic models (OSHEMs)  [@Pouwels2022], actual implementations are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022].
+Barriers to adoption of OSHEMs include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations [@Pouwels2022; @Wu2019].
+Adherence to good practice guidance is an essential requirement for healthcare modelling [@Erdemir2020],  -->
 
-Some of these barriers could potentially be mitigated through the development of appropriate software frameworks.
+Better software frameworks could potentially improve open-source CHEM development.
 A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users [@myllarniemi2018development].
@@
 A high-level software framework for implementing open-source CHEMs in R has previously been developed with the primary aim of improving model transparency [@alarid2019need].
-A software framework that help CHEM developers fulfill a broader set of ethical responsibilities would require a number of conceptual, technical and behavioural challenges to be overcome.
-Firstly, the ethical responsibilities of developers of computational models designed to inform governmental decision-making are often poorly understood <!-- and inadequately fulfilled  -->[@10.3389/fpubh.2017.00068; @pliakos2021ethics; @thompson2022escape; @calder2018computational].
-Software frameworks can be challenging and time consuming to create and may become excessively complex over time [@edwin2014software].
-Furthermore, software frameworks can be difficult to learn, often requiring model developers to undergo specialist training [@myllarniemi2018development].
+However, to gain widespread adoption, a software framework for CHEM developers may need to provide tools to help meet a broader range of ethical practice requirements.
+There are multiple challenges to overcome.
+Firstly, the ethical responsibilities of public health computational modellers remain poorly understood <!-- and inadequately fulfilled  [@pliakos2021ethics; @thompson2022escape;]-->[@10.3389/fpubh.2017.00068] and the computational modelling landscape is changing fast [@calder2018computational.
+Secondly, software frameworks can be challenging and time consuming to create and may become excessively complex over time [@edwin2014software].
+Thirdly, software frameworks can be difficult to learn, often requiring model developers to undergo specialist training [@myllarniemi2018development].
 <!-- a software framework is unlikely to be widely adopted unless the benefits to developers outweigh the costs associated with using it. -->

### 2023-10-16 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
close to submission update - except tables

@@
 
-# Assessing ethical CHEM implementations
+# Ethical responsibilities and assessment criteria
 ```{r child="../Child_RMDs/MS_Imp_Guidelines.Rmd", echo=FALSE}
@@
 
-# Software framework
+# Prototype software framework
 ```{r child="../Child_RMDs/MS_Imp_Toolkit.Rmd", echo=FALSE}
@@
 
-# Application
+# Application in youth mental health
 ```{r child="../Child_RMDs/MS_Imp_Example.Rmd", echo=FALSE}

### 2023-10-16 setup.R

@@ -38,8 +38,8 @@ X <- renewSlot(X,
                {
                  args_ls <- X@abstract_args_ls
                  args_ls$abstract_ls <- list(Summary = "Most health economic analyses are undertaken with the aid of computers. However, the ethical dimensions of implementing health economic models as software are poorly understood. 
-                                                        We propose that the core responsibilities of health economic model software developers over a project lifecycle are to (i) make socially acceptable design decisions; (ii) ensure fit for purpose implementation; and (iii) support socially beneficial use. 
-                                                        We further propose that a transparent (T), reusable (R) and updatable (U) computational health economic model (CHEM) is suggestive of a developer team that has largely fulfilled these responsibilities.
+                                                        We propose that the core ethical responsibilities of model developers and funders over a health economic software development lifecycle are to (i) make socially acceptable system requirements and design decisions; (ii) ensure fit for purpose implementation; and (iii) support socially beneficial use. 
+                                                        We further propose that a transparent (T), reusable (R) and updatable (U) computational health economic model (CHEM) is suggestive of a project team that has largely fulfilled these responsibilities.
                                                         We propose six TRU criteria for assessing CHEMs: (T1) software files are open access; (T2) developer judgments and contributions are easily identified; 
                                                         (R1) programming practices promote generalisability and transferability; (R2) terms of use restrict only unethical applications; (U1) maintenance infrastructure is in place; and 
                                                         (U2) new releases are systematically retested and appropriately deprecated.

### 2023-10-16 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
missing tables

@@
 <!-- Talk about DARTH (https://doi.org/10.1007/s40273-019-00837-x )/ BCEA -->
-Ethical practice is a core expectation of health researchers and computational methods underpin most quantitative research, yet an understanding of what constitutes ethical computational modelling practice in health is underdeveloped [@10.3389/fpubh.2017.00068].
-We have addressed this gap with our proposed modeller and funder responsibilities, enabling model attributes and model implementation assessment criteria.
+Ethical practice is a core expectation of health researchers and computational methods underpin most quantitative research, yet an understanding of what constitutes ethical public health modelling practice is underdeveloped [@10.3389/fpubh.2017.00068].
+We have addressed this gap with our proposed project team responsibilities, enabling model attributes and model implementation assessment criteria.
 
@@
 As illustrated by Table \@ref(tab:checktb), we have developed a prototype software framework that can be used to implement youth mental health CHEMs that largely satisfy our TRU criteria.
-However, in its current form our software framework is too fragile to be anything more than a prototype for supporting the development needs other modelling teams and projects.
-We developed our prototype software framework was developed with the needs of only one group of developers in mind – ourselves.
-We currently lack the resources required to adequately implement strategies to target factors such as user enjoyment, usability, active user-community and supporting resources that influence adoption of software frameworks [@myllarniemi2018development].
+However, in its current form our software framework is too fragile to be recommended as anything more than a prototype for supporting the development needs of other modelling teams and projects.
+We developed our prototype software framework primarily to address the user requirements of one group – ourselves.
+Factors such as user enjoyment, usability, active user-community and supporting resources influence adoption of software frameworks [@myllarniemi2018development].
+We currently lack the resources required to provide ongoing address these issues.
 
-Our prototype has a number of features that subsequent work to develop CHEM software frameworks may find useful to incorporate.
+However, our prototype has a number of features that future work on CHEM software frameworks may find useful to incorporate.
 Firstly, developing a software framework to work within an existing and widely used open source programming language such as R or python, can keep framework scope relatively narrow.
 This makes it more tractable to develop, maintain and learn, and can integrate other modelling tools written in that language (e.g., the dependency libraries we list in Table \@ref(tab:cpkgs)).
-Secondly, implementation that combines both object oriented and functional programming paradigms can avail of the modular and syntactical simplicity benefits of the former, while limiting needless bundling of code artefacts.
+Secondly, implementation that combines both object-oriented and functional programming paradigms can avail of the modular and syntactical simplicity benefits of the former, while limiting needless bundling of code artefacts.
 Thirdly, a sensible trade-off needs to be found between transparent code implementation (which requires clear and sufficiently detailed documentation) and Agile Software Development (for which a foundational principle is prioritising the development of working code over writing documentation [@beck2001manifesto]).
-Our software framework makes this trade off by enforcing the use of consistent code naming conventions and file organisation which in turn enables automated generation of simple documentation at every code update.
+Our software framework makes this trade off by enforcing the use of consistent naming conventions and file organisation which in turn enables automated generation of simple documentation at every code update.
 All model data-structures and algorithms are therefore always documented (at least minimally, with machine authored content), meaning model developers have a requirement to write customised documentation less frequently.
+Many of the features of our prototype software framework have the potential to be significantly enhanced through integration with evolving code-authoring and documentation authoring capabilities of large language models.
 
+Our software framework provides the outline of a technical solution to some of the challenges of open source CHEM development.
+However, better tools alone are insufficient and policy and institutional changes are also required.
 Reducing waste in research is a core responsibility of research funders [@chalmers2014increase] and funding the development of CHEMs that are not adequately understood, reused or updated is wasteful.
@@
 A future software framework for ethical CHEMs would ideally incorporate a base set of features useful to developers of computational models across all domains of public health, with the capability for community-led extensions that are tailored to the needs of modellers focused on specific health-conditions.
+Such approaches will likely be important to ensure that the potential user-base is sufficient to make CHEM software frameworks sustainable.

### 2023-10-16 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
missing tables

@@
 <!-- Add intro text -->
-We plan on using the ready4 software framework to implement multiple transparent, reusable and updatable CHEMs in youth mental health (see Figure \@ref(fig:fig1)).
-Some initial outputs from this work are publicly available.
+We are using the ready4 software framework to implement multiple transparent, reusable and updatable CHEMs in youth mental health (see Figure \@ref(fig:fig1)).
+Some initial outputs from this work are publicly available as development version releases.
 
@@
 ## Case study: health and its value
-We have previously describeda study [@Hamilton2021.07.07.21260129] to develop utility mapping models for use in samples of young people presenting to primary mental health services.
+We have previously described a study [@Hamilton2021.07.07.21260129] to develop utility mapping models for use in samples of young people presenting to primary mental health services.
 The ready4 software framework was used in that study to develop CHEM modules, supply those modules with data and implement modelling analyses, creating the following artefacts:

### 2023-10-16 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
missing tables

@@
 
-We considered prior literature on modelling practice and our own professional experience to identify: (i) some core ethical responsibilities of CHEM developers and funders; (ii) attributes of CHEMs that can suggest fulfillment of these responsibilities; and (iii) criteria against which these attributes can be assessed.
+We considered prior literature on modelling practice and our own experience with developing and using CHEMs to identify: (i) some core ethical responsibilities of CHEM project teams; (ii) attributes of CHEMs that can suggest fulfillment of these responsibilities; and (iii) criteria against which these attributes can be assessed.
 
-## Ethical responsibilities of CHEM developers and funders
+## Ethical responsibilities of CHEM project teams
 <!-- The ethical responsibilities and enabling model attributes we describe have both commonalities and distinctive features compared to a previous  -->
-Boden and McKendrick [@10.3389/fpubh.2017.00068] proposed a framework for ethical computational modelling in public health based on the four ethical criteria of justice (concerning the social obligations of modellers to consider and communicate ethical issues), independence (concerning how modeller subjectivity shapes model design), transparency (concerning the need for policymakers to reliably evaluate model strengths and weaknesses) and beneficence / non-maleficence (concerning model quality and utility).
-However, the framework's authors mostly discuss these criteria in the context of a modelling project as a whole, including a model's conceptual and mathematical representations.
-The authors propose 13 questions to evaluate ethical risk across the four criteria, but of these only "is the model code open source or available on request" (for transparency) and "has the model been verified, i.e., does it do what the modeller wants it to do?" (for beneficence / non-maleficence) are specific to model's representation as software.
+Boden and McKendrick [@10.3389/fpubh.2017.00068] propose a framework for ethical public health modelling based on the criteria of independence (concerning how modeller subjectivity shapes model design), beneficence / non-maleficence (concerning model quality and utility), transparency (concerning the need for policymakers to reliably evaluate model strengths and weaknesses) and justice (concerning the social obligations of modellers to consider and communicate ethical issues about model use).
+However, these criteria are not specific to the computational model, but are designed to apply to a modelling project as a whole, including a model's conceptual and mathematical representations.
+The authors propose 13 questions to evaluate ethical risk across the four criteria, but of these, only "is the model code open source or available on request" (for transparency) and "has the model been verified, i.e., does it do what the modeller wants it to do?" (for beneficence / non-maleficence) are specific to model's representation as software.
 
-To reconceptualise these four criteria as ethical responsibilities that are specific to CHEM developers and funders, we first considered the distinct phases in a software development project.
+To help identify ethical responsibilities that are specific to CHEM project teams, we first considered the distinct phases in a software development project.
 Software development lifecycle (SDLC) models take different approaches to the inclusion, naming, definition, sequencing and iteration of project phases [@ruparelia2010software].
-However, SDLC models typically have components that can principally map to the concepts of *planning* (e.g.
-identification of system / user requirements and design specifications), *implementation* (e.g.
-development and testing) and *release* (e.g.deployment, system integration and maintenance).
+However, SDLC models typically have components that can principally map to the concepts of *planning* (e.g., identification of system / user requirements and design specifications), *implementation* (e.g., development and testing) and *release* (e.g., deployment, system integration, maintenance and support).
 For simplicity, we propose one overarching ethical responsibility for CHEM developers and funders for each of these phases.
@@
 
-(i) **make socially acceptable system requirements and design decisions** (during CHEM planning);
+(i) **establish socially acceptable system requirements and design specifications** (during CHEM planning);
 
-(ii) **ensure fitness for purpose** (of CHEM implementation); and
+(ii) **ensure fit for purpose implementation** (during CHEM implementation); and
 
@@
 
-Each responsibility combines different aspects of Boden and McKendrick's ethical criteria: responsibility (i) incorporates justice and independence; responsibility (ii) incorporates independence and transparency; and responsibility (iii) incorporates beneficence / non-maleficence and justice.
-Model developers and funders share these responsibilities as each one has implications for both professional practice and project resourcing.
+Each responsibility relates to aspects of Boden and McKendrick's ethical criteria.
+Transparency underpins all three responsibilities (Table \@ref(tab:timelygls).
+Additionally, the planning responsibility incorporates justice and independence, the implementation responsibility incorporates independence and the release responsibility incorporates beneficence / non-maleficence and justice.
+All three ethical responsibilities have implications for both professional practice and project resourcing and should therefore apply to model developers and funders jointly.
 
@@
 Misalignment between the values of computational model developers and those of the population groups affected by decisions based on their models presents significant ethical risks [@thompson2022escape; @duckett2022journey].
-The value judgments of health economists influence the assumptions, selection of model features and standards for evidence that shape health economic model projects [@HARVARD2020112975].
-These value judgments are rarely made explicit, omissions that may lead to socially unacceptable policy recommendations [@duckett2022journey].
-modeller value judgments also determine the computational implementation of health economic models.
-For example, as illustrated in Table \@ref(tab:proscons), project resource constraints may require trade offs between desired CHEM **system requirements and design** features.
-These trade offs in turn determine how straightforward it is for CHEMs to be amended by third parties to reflect alternative value judgments in model conceptualisation and mathematical formalisation (Table \@ref(tab:timelygls)).
+The value judgments of health economic modellers are rarely adequately specified, omissions that may lead to socially unacceptable policy recommendations [@duckett2022journey].
+These value judgments influence the assumptions, selection of model features and standards for evidence that shape health economic model projects [@HARVARD2020112975].
+For example, as illustrated in Table \@ref(tab:proscons), project resource constraints may require trade-offs between desired CHEM **system requirements and design** features.
+These trade-offs in turn determine how straightforward it is for CHEMs to be amended by third parties to reflect alternative value judgments in model conceptualisation and mathematical formalisation (Table \@ref(tab:timelygls)).
 
@@
 
-Computational modellers have duties both to ensure computational model **fitness for purpose** and to provide potential third-party users with the means of assessing its adequacy for their proposed purposes [@Erdemir2020; @Feenstra2022; @thompson2019escape; @10.3389/fpubh.2017.00068].
+Modellers have duties both to ensure a computational model is **fit for purpose** and to provide potential third-party users with the means of assessing its adequacy for their proposed uses [@Erdemir2020; @Feenstra2022; @thompson2019escape; @10.3389/fpubh.2017.00068].
 However, it is common for health economic models to have serious methodological flaws [@carletto_zanuzzi_sammarco_russo_2020; @WONDER2015467]; insufficient validation [@Ghabri2019; @kolovos2017model; @haji2013model], poor reproducibility [@Jalali2021; @McManus2019; @Bermejo2017]; and undeclared errors [@Radeva2020].
@@
 ## CHEM attributes associated with ethical modelling practice
-The responsibilities of model developers and funders over a CHEM lifecycle are easier to state than to measure.
+The responsibilities of model project teams over a CHEM lifecycle are easier to state than to measure.
 However, aspects of ethical modelling practice may be inferred from measurable attributes of CHEMs.
@@
 Taking steps to make computational models **transparent** is an important part of ethical public health modelling practice [@10.3389/fpubh.2017.00068].
-Guidance on transparency in health economic modelling recommended that model code and data should be clearly documented [@Eddy2012].
-Notably, the same guidelines, published over ten years ago, did not recommend sharing model code and data.
+Guidance on transparency in health economic modelling recommend that model code and data should be clearly documented [@Eddy2012].
+Notably, the same guidelines, published over ten years ago, do not recommend sharing model code and data.
 However, more recent healthcare modelling guidance does recommend public dissemination of such artefacts [@Erdemir2020].
@@
 It is also important that verification checks are rerun with each model update, a task that can be automated using the software development practice of continuous integration [@CI2017].
-The risk of model revisions having unintended consequences for third party users can be mitigated through the use of deprecation conventions [@zhou2016api] that take an informative and staged approach to retiring outdated model code and data.
+The risk of software revisions having unintended consequences for third party users can be mitigated through the use of deprecation conventions [@zhou2016api] that take an informative and staged approach to retiring outdated CHEMs.
 <!-- Currently, the core development team for a CHEM will be typically be funded to produce a project end-point deliverable whose specifications are well defined early in the project.
@@
 
--	**R2**: Terms of use place only ethical restrictions on reuse and allow anyone to ethically reuse model code and non-confidential data, in whole or in part, without charge, and for purposes that include the creation of derivative works.
+-	**R2**: Terms of use place restrict only unethical usage and allow anyone to ethically reuse model code and non-confidential data, in whole or in part, without charge, and for purposes that include the creation of derivative works.
 

### 2023-10-16 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
missing tables

@@
 Authoring with each of these paradigms is facilitated by a dedicated CHEM module authoring library.
-One module authoring library contains tools for writing functions in a consistent house style and then using the standardised naming conventions of that house style to automatically generate basic documentation for each function.
+One module authoring library contains tools for writing functions in a consistent house style and automatically generating basic documentation for each function.
 A second module authoring library contains tools to help streamline and standardise the authoring and documenting of novel CHEM modules.
@@
 We created a GitHub organisation (a collection of code repositories) where source code that we author is stored and version controlled.
-We configured individual repositories in our GitHub organisation to use GitHub actions to implement continuous integration.
+We configured individual repositories in our GitHub organisation to implement continuous integration.
 By default, code libraries authored with our framework will use continuous integration to assess compliance with policies specified by the Comprehensive R Archive Network (CRAN) [@CRAN2022].

### 2023-10-16 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
missing tables

@@
 
-The set of digital files implementing a health economic model's structure, data and algorithms as software can be called a computational health economic model (CHEM).
-CHEMs can be developed using commercial modelling software or in an open-source programming language such as Python [@python2009] or R [@RCORE2022].
+The set of software files implementing a health economic model's structure, data and algorithms can be called a computational health economic model (CHEM).
+CHEMs can be developed using commercial modelling software or open-source programming languages such as Python [@python2009] or R [@RCORE2022].
 An advantage of commercial modelling software is that users often require no or limited programming skills to develop and apply CHEMs.
 However, open-source software programming languages may facilitate the development of CHEMs that are more transparent, reusable and updatable [@incerti2019r; @Pouwels2022].
-The decision about what type of software development platform to use needs to balance ethical and pragmatic considerations  (see Table \@ref(tab:proscons)).
+The decision about what type of software development platform to use must balance ethical considerations and resource constraints (see Table \@ref(tab:proscons)).
 
@@
 Open-source CHEMs remain rare [@Feenstra2022; @Emerson2019].
-Additional resources, skills and tools may be required to overcome a number of barriers to greater health economist adoption of open-source development.
-CHEM software development platforms were identified in a 2020 survey of health economists as a barrier to open-source model implementations  [@Pouwels2022].
-Other reported barriers relate to difficulties in generalising models, updating models and transferring model data, concerns about the level of public access required and lack of interest from decision-makers, and legal, confidentiality and security considerations [@Pouwels2022].
-
+The software used to develop CHEMs was identified as a barrier to open-source model implementations by participants in a 2020 survey of health economists [@Pouwels2022].
+Other reported barriers relate to difficulties in generalising models, updating models and transferring model data, concerns about the level of public access and lack of interest from decision-makers, and legal, confidentiality and security considerations [@Pouwels2022].
+<!-- Additional resources, skills and tools may be required to overcome a number of barriers to greater health economist adoption of open-source development. -->
 <!-- A major consideration in open-source software development, is the selection of an appropriate software framework.  -->
@@
 
-Better software frameworks could potentially improve open-source CHEM development.
+Better software frameworks could potentially help address some of the barriers to open-source CHEM development.
 A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users [@myllarniemi2018development].
@@
 A high-level software framework for implementing open-source CHEMs in R has previously been developed with the primary aim of improving model transparency [@alarid2019need].
-However, to gain widespread adoption, a software framework for CHEM developers may need to provide tools to help meet a broader range of ethical practice requirements.
+However, to gain widespread adoption, a software framework for CHEMs may need to provide tools to help model developers meet a broader range of ethical practice requirements.
 There are multiple challenges to overcome.
-Firstly, the ethical responsibilities of public health computational modellers remain poorly understood <!-- and inadequately fulfilled  [@pliakos2021ethics; @thompson2022escape;]-->[@10.3389/fpubh.2017.00068] and the computational modelling landscape is changing fast [@calder2018computational.
+Firstly, the ethical responsibilities of public health computational modellers remain poorly understood <!-- and inadequately fulfilled  [@pliakos2021ethics; @thompson2022escape;]-->[@10.3389/fpubh.2017.00068] and the computational modelling landscape is changing fast [@calder2018computational].
 Secondly, software frameworks can be challenging and time consuming to create and may become excessively complex over time [@edwin2014software].
 Thirdly, software frameworks can be difficult to learn, often requiring model developers to undergo specialist training [@myllarniemi2018development].
+
 <!-- a software framework is unlikely to be widely adopted unless the benefits to developers outweigh the costs associated with using it. -->
 <!-- However, guidance on developing, selecting and using software frameworks for ethical CHEM implementations is scarce. -->
-
 <!--  -->
-
 <!-- Transparency has been proposed as one of the core ethical responsibilities of public health computational modellers [@10.3389/fpubh.2017.00068].  -->
-
 <!-- Although computational models are widely used to inform health policy and system design [@dakin2015influence; @Erdemir2020; @LO2022100570; @Christene006827], -->

### 2023-10-16 setup.R

@@ -38,9 +38,9 @@ X <- renewSlot(X,
                {
                  args_ls <- X@abstract_args_ls
                  args_ls$abstract_ls <- list(Summary = "Most health economic analyses are undertaken with the aid of computers. However, the ethical dimensions of implementing health economic models as software are poorly understood. 
-                                                        We propose that the core ethical responsibilities of model developers and funders over a health economic software development lifecycle are to (i) make socially acceptable system requirements and design decisions; (ii) ensure fit for purpose implementation; and (iii) support socially beneficial use. 
-                                                        We further propose that a transparent (T), reusable (R) and updatable (U) computational health economic model (CHEM) is suggestive of a project team that has largely fulfilled these responsibilities.
-                                                        We propose six TRU criteria for assessing CHEMs: (T1) software files are open access; (T2) developer judgments and contributions are easily identified; 
+                                                        We propose that developers and funders of computational health economic models (CHEMs) share ethical responsibilities to (i) establish socially acceptable system requirements and design specifications; (ii) ensure fit for purpose implementation; and (iii) support socially beneficial use. 
+                                                        We further propose that a transparent (T), reusable (R) and updatable (U) CHEM is suggestive of a project team that has largely fulfilled these responsibilities.
+                                                        We propose six TRU criteria for assessing CHEMs: (T1) software files are open access; (T2) project team judgments and contributions are easily identified; 
                                                         (R1) programming practices promote generalisability and transferability; (R2) terms of use restrict only unethical applications; (U1) maintenance infrastructure is in place; and 
                                                         (U2) new releases are systematically retested and appropriately deprecated.
                                                         To facilitate CHEMs that meet TRU criteria, we have developed a prototype software framework in the programming language R.

### 2023-10-21 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
one table to go

@@
 Ethical practice is a core expectation of health researchers and computational methods underpin most quantitative research, yet an understanding of what constitutes ethical public health modelling practice is underdeveloped [@10.3389/fpubh.2017.00068].
-We have addressed this gap with our proposed project team responsibilities, enabling model attributes and model implementation assessment criteria.
+We have addressed this gap with our proposed responsibilities for model developers and funders, enabling CHEM attributes and CHEM implementation assessment criteria.
 
@@
 Factors such as user enjoyment, usability, active user-community and supporting resources influence adoption of software frameworks [@myllarniemi2018development].
-We currently lack the resources required to provide ongoing address these issues.
+We currently lack the resources required to  address these issues for our software framework.
 
 However, our prototype has a number of features that future work on CHEM software frameworks may find useful to incorporate.
-Firstly, developing a software framework to work within an existing and widely used open source programming language such as R or python, can keep framework scope relatively narrow.
+Firstly, developing a software framework to work within an existing and widely used open source programming language such as R or Python, can keep framework scope relatively narrow.
 This makes it more tractable to develop, maintain and learn, and can integrate other modelling tools written in that language (e.g., the dependency libraries we list in Table \@ref(tab:cpkgs)).
@@
 Thirdly, a sensible trade-off needs to be found between transparent code implementation (which requires clear and sufficiently detailed documentation) and Agile Software Development (for which a foundational principle is prioritising the development of working code over writing documentation [@beck2001manifesto]).
-Our software framework makes this trade off by enforcing the use of consistent naming conventions and file organisation which in turn enables automated generation of simple documentation at every code update.
+Our software framework makes this trade off by enforcing the use of consistent code style conventions and file organisation which in turn enables automated generation of simple documentation at every CHEM module update.
 All model data-structures and algorithms are therefore always documented (at least minimally, with machine authored content), meaning model developers have a requirement to write customised documentation less frequently.
-Many of the features of our prototype software framework have the potential to be significantly enhanced through integration with evolving code-authoring and documentation authoring capabilities of large language models.
+Many of the features of our prototype software framework have the potential to be significantly enhanced through integration with evolving code and documentation authoring capabilities of large language models.
 
@@
 Reducing waste in research is a core responsibility of research funders [@chalmers2014increase] and funding the development of CHEMs that are not adequately understood, reused or updated is wasteful.
-Existing incentive structures for health economists generally do not promote facilitating peers to reuse their work and funding is rarely adequate to maintain an routinely update a model.
+Existing incentive structures for health economists generally do not promote facilitating peers to reuse their work and funding is rarely adequate to maintain and routinely update a model.
 Currently, it can take “an extraordinary amount of idealism” to commit to authoring and maintaining research software [@anzt2020environment].
@@
 
-A future software framework for ethical CHEMs would ideally incorporate a base set of features useful to developers of computational models across all domains of public health, with the capability for community-led extensions that are tailored to the needs of modellers focused on specific health-conditions.
-Such approaches will likely be important to ensure that the potential user-base is sufficient to make CHEM software frameworks sustainable.
+A future software framework for ethical CHEMs would ideally incorporate a base set of features useful to developers of computational models across all domains of public health and health economics, with the capability for community-led extensions that are tailored to the needs of modellers focused on specific health-conditions.
+Such approaches will likely be important to ensure a sufficient potential user-base to make CHEM software frameworks sustainable.

### 2023-10-21 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
one table to go

@@
 Although we are principally interested in using CHEMs to answer policy questions relating to the mental health of young people in Australia, we want to facilitate CHEM transferability to other jurisdictions.
-Our CHEMs are being derived from and applied to real data (which can be assumption, empirical or simulated, so long as it is appropriate for use in analysis intended to inform decision-making) from Australia.
+Our CHEMs are being derived from and applied to real data (which can be empirical, simulated or assumption, so long as it is appropriate for use in analysis intended to inform decision-making) from Australia.
 To help demonstrate the potential use of CHEMs in other decision contexts, we also create toy datasets.
@@
 
- - collections of real data (study input and results [@DVN/DKDIB0_2021]) and fake data (synthetic populations for testing model modules [@DVN/HJXYKQ_2021]);
+ - collections of real data (study input and results [@DVN/DKDIB0_2021]) and toy data (synthetic populations for testing model modules [@DVN/HJXYKQ_2021]);
 

### 2023-10-21 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
one table to go

@@
 
-We considered prior literature on modelling practice and our own experience with developing and using CHEMs to identify: (i) some core ethical responsibilities of CHEM project teams; (ii) attributes of CHEMs that can suggest fulfillment of these responsibilities; and (iii) criteria against which these attributes can be assessed.
+We considered literature on modelling practice and reflected on our prior experience with developing and using CHEMs to identify: (i) some core ethical responsibilities of CHEM project teams; (ii) attributes of CHEMs that can suggest fulfillment of these responsibilities; and (iii) criteria against which these attributes can be assessed.
 
@@
 
-To help identify ethical responsibilities that are specific to CHEM project teams, we first considered the distinct phases in a software development project.
+To identify ethical issues that are specific to CHEMs, we first considered the distinct phases in a software development project.
 Software development lifecycle (SDLC) models take different approaches to the inclusion, naming, definition, sequencing and iteration of project phases [@ruparelia2010software].
 However, SDLC models typically have components that can principally map to the concepts of *planning* (e.g., identification of system / user requirements and design specifications), *implementation* (e.g., development and testing) and *release* (e.g., deployment, system integration, maintenance and support).
-For simplicity, we propose one overarching ethical responsibility for CHEM developers and funders for each of these phases.
+For simplicity, we propose one overarching ethical responsibility for CHEM project teams for each phase.
 These responsibilities are to:
 
-(i) **establish socially acceptable system requirements and design specifications** (during CHEM planning);
+(i) **establish socially acceptable user requirements and design specifications** (during CHEM planning);
 
-(ii) **ensure fit for purpose implementation** (during CHEM implementation); and
+(ii) **ensure fitness for purpose** (of CHEM implementation); and
 
@@
 
-Each responsibility relates to aspects of Boden and McKendrick's ethical criteria.
-Transparency underpins all three responsibilities (Table \@ref(tab:timelygls).
-Additionally, the planning responsibility incorporates justice and independence, the implementation responsibility incorporates independence and the release responsibility incorporates beneficence / non-maleficence and justice.
-All three ethical responsibilities have implications for both professional practice and project resourcing and should therefore apply to model developers and funders jointly.
+Transparency underpins all three responsibilities (Table \@ref(tab:timelygls)).
+Boden and McKendrick’s other ethical criteria can be selectively mapped to each phase's responsibility: justice and independence to the planning responsibility; independence to the implementation responsibility; and beneficence / non-maleficence and justice to the release responsibility.
+All three ethical responsibilities have implications for both professional practice and project resourcing.
+As it is unreasonable to place expectations of modellers that they are not resourced to fulfil, these responsibilities should apply jointly to health economic model developers and funders.
 
@@
 These value judgments influence the assumptions, selection of model features and standards for evidence that shape health economic model projects [@HARVARD2020112975].
-For example, as illustrated in Table \@ref(tab:proscons), project resource constraints may require trade-offs between desired CHEM **system requirements and design** features.
-These trade-offs in turn determine how straightforward it is for CHEMs to be amended by third parties to reflect alternative value judgments in model conceptualisation and mathematical formalisation (Table \@ref(tab:timelygls)).
+For example, as illustrated in Table \@ref(tab:proscons), project resource constraints may require model developers to make trade-offs when agreeing CHEM **user requirements and design specifications**.
+These trade-offs in turn determine how straightforward it is for a CHEM to be subsequently amended to reflect alternative value judgments relating to model conceptualisation and mathematical formalisation (Table \@ref(tab:timelygls)).
 
@@
 A CHEM that is **reusable** also signals ethical modelling practice.
-Making a CHEM’s code, data and documentation publicly available is increasingly considered good practice, yet is not sufficient to promote model re-use.
-Key concepts in health economic model reuse include generalisability (application without adaptation) and transferability (selective reuse and/or modification of model components) [@RN39].
+Although making a CHEM’s code, data and documentation publicly available is increasingly considered good practice, it is insufficient to enable model re-use.
+Key concerns for health economists when considering model reuse are generalisability (application without adaptation) and transferability (selective reuse and/or modification of model components) [@RN39].
 Writing model algorithms as collections of functions (short, self-contained and reusable software routines that each perform a discrete task) is good scientific computing practice [@Wilson_2017] and promotes selective reuse.
@@
 Some guidance strongly recommends the use of permissive licensing [@Wilson_2017] that provides users with great flexibility as to the purposes (including commercial) for which content can be re-used.
-An alternative approach is to use copyleft licenses [@copyleft2022] that can require content users to distribute any derivative works they create under similar open-source arrangements.
+Alternatively, copyleft licenses [@copyleft2022] can be used to require that derivative works created by content users remain open-source.
 <!-- Compared to using commercial modelling software, authoring CHEMs in an open-source language like R [@RCORE2022] makes it easier to -->
@@
 
--	**R2**: Terms of use place restrict only unethical usage and allow anyone to ethically reuse model code and non-confidential data, in whole or in part, without charge, and for purposes that include the creation of derivative works.
+-	**R2**: Licenses restrict only unethical use and allow anyone to ethically reuse model code and non-confidential data, in whole or in part, without charge, and for purposes that include the creation of derivative works.
 

### 2023-10-21 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
one table to go

@@
 A library for **authoring reproducible analyses** contains tools to help write programs that apply CHEM modules to compatible datasets for the purpose of undertaking health economic analyses.
-These analysis programs can be either self-documenting (code is integrated with plain English explanations of what it does) or trigger the creation of separate documents (e.g., a scientific manuscript).
+These analysis programs can be either self-documenting (code is integrated with plain English explanations of what it does) or trigger the creation of explanatory documents (e.g., a scientific manuscript).
 
@@
 ##	Documentation website
-We developed a framework documentation website (www.ready4-dev.com) that provides guidance to model developers on how to use and contribute improvements to the ready4 software framework and models developed with it.
+We developed a framework documentation website (https://www.ready4-dev.com) that provides guidance to model developers on how to use and contribute improvements to the ready4 software framework and CHEM modules developed with it.
 The documentation website is versioned, which means documentation relating to prior versions of framework software can be archived, retrieved and viewed.

### 2023-10-21 Markdown/Manuscript/Child_RMDs/MS_Tables_3.Rmd
one table to go

@@
                                        "ready4show"),
-                           # Version = Package %>%
-                           #   purrr::map_chr(~utils::packageDescription(.x) %>%
-                           #                    purrr::pluck("Version")),
-                           Focus = c("Foundation",
-                                     "Module algorithms",
-                                     "Module structures",
-                                     "Module libraries",
-                                     "Datasets",
-                                     "Analyses"),
-                           A = c("3","2-3","2","1-2,5,7","1-2,7","4,6"), 
-                           R = c("4","5","4-5","1,3,6","3,7",""),
-                           U = c("","","","1-3","1",""),
-                           # E = c("", "1","1-2","1","3",""),
-                           # L = c("","","","1,3","2-3",""),
-                           # Y = c("","","","","","1-2"),
-                           `Depends on` = Package %>%
+                     Purpose = c("Provide a template and novel syntax for modular CHEM implementations and tools for finding interoperable CHEM modules, datasets and reproducible analysis programs.",
+                                 "Streamline and standardise the authoring and documenting of functions that support transferable and generalisable model algorithms.",
+                                 "Streamline and standardise the authoring and documenting of new interoperable CHEM modules.",
+                                 "Help bundle and disseminate newly created CHEM modules as R libraries that are documented, licensed and quality assured.",
+                                 "Help manage the labelling and transfer of data between CHEM modules and local and remote data repositories.",
+                                 "Facilitate the use of CHEM modules in programs to implement integrated and reproducible data ingest, analysis and reporting pipelines."),
+                           # A = c("3","2-3","2","1-2,5,7","1-2,7","4,6"), 
+                           # R = c("4","5","4-5","1,3,6","3,7",""),
+                           # U = c("","","","1-3","1",""),
+                           `R library dependencies` = Package %>%
                              purrr::map(~ {
@@
   as.data.frame() 
-if(params$X@outp_formats_chr[1] != "Word"){
-      df$Ref <- c(rep("",6)
-       # "@ready42022","@ready4fun2022","@ready4class2022","@ready4pack2022","@ready4use2022","@ready4show2022"
-                  )
-}else{
-  df$Ref <- ""
-}
+# if(params$X@outp_formats_chr[1] != "Word"){
+#       df$Ref <- c(rep("",6)
+#        # "@ready42022","@ready4fun2022","@ready4class2022","@ready4pack2022","@ready4use2022","@ready4show2022"
+#                   )
+# }else{
+#   df$Ref <- ""
+# }
 
 df <- df %>%
-  dplyr::mutate(Standard = purrr::pmap_chr(df,
-                                           ~paste0("A",
-                                                  ..3,
-                                                  paste0(rep("&nbsp;",
-                                                      2+max(nchar(df[,3]))-nchar(..3)),
-                                                      collapse = ""#
-                                                      ),
-                                                  ifelse(..4=="","","R"),
-                                                  ..4,
-                                                  paste0(rep("&nbsp;",
-                                                      2+max(nchar(df[,4]))-nchar(..4)),
-                                                      collapse = ""#
-                                                      ),
-                                                  ifelse(..5=="","","U"),
-                                                  ..5,
-                                                  paste0(rep("&nbsp;",
-                                                      1+max(nchar(df[,5]))-nchar(..5)),
-                                                      collapse = ""#
-                                                      )#,
-                                                  # ifelse(..6=="","","E"),
-                                                  # ..6,
+  # dplyr::mutate(Standard = purrr::pmap_chr(df,
+  #                                          ~paste0("A",
+  #                                                 ..3,
   #                                                 paste0(rep("&nbsp;",
-                                                  #     1+max(nchar(df[,6]))-nchar(..6)),
+  #                                                     2+max(nchar(df[,3]))-nchar(..3)),
   #                                                     collapse = ""#
   #                                                     ),
-                                                  # ifelse(..7=="","","L"),
-                                                  # ..7,
-                                                  # # paste0(rep("&nbsp;",
-                                                  # #     1+max(nchar(df[,7]))-nchar(..7)),
-                                                  # #     collapse = ""#
-                                                  # #     ),
-                                                  # ifelse(..8=="","","&nbsp; &nbsp; &nbsp; &nbsp; Y"),
-                                                  # ..8,
+  #                                                 ifelse(..4=="","","R"),
+  #                                                 ..4,
   #                                                 paste0(rep("&nbsp;",
-                                                  #     1+max(nchar(df[,8]))-nchar(..8)),
+  #                                                     2+max(nchar(df[,4]))-nchar(..4)),
   #                                                     collapse = ""#
-                                                  #     )
-                                                  ))) %>%
+  #                                                     ),
+  #                                                 ifelse(..5=="","","U"),
+  #                                                 ..5,
+  #                                                 paste0(rep("&nbsp;",
+  #                                                     1+max(nchar(df[,5]))-nchar(..5)),
+  #                                                     collapse = ""#
+  #                                                     )#,
+  #                                                 ))) %>%
 
   dplyr::select(Package,
-                Ref,
-                Focus,
-                Standard,
-                `Depends on`)
+                #Ref,
+                Purpose,
+                #Standard,
+                `R library dependencies`)
 
 names_chr <- names(df)
-df <- data.frame(df[,1],
-                 rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp;"),
-                     nrow(df)),
-                 df[,2:3],
-                 rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp;")
-                     ,nrow(df)),
-                 df[,4],
-                 #rep("&nbsp; &nbsp; &nbsp;",nrow(df)),
-                 df[,5])
-colnames(df) <- c("Package",
-                  ifelse(params$X@outp_formats_chr[1] == "Word","XXX"," "),
-                  "Ref", "Focus", 
-                  ifelse(params$X@outp_formats_chr[1] == "Word","YYY"," "),
-                  "Standard     ",# " ",
-                  "Depends on these R libraries")
+# df <- data.frame(df[,1],
+#                  rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp;"),
+#                      nrow(df)),
+#                  df[,2#:3
+#                     ],
+#                  rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp;")
+#                      ,nrow(df)),
+#                  #df[,4],
+#                  #rep("&nbsp; &nbsp; &nbsp;",nrow(df)),
+#                  df[,3#5
+#                     ])
+# colnames(df) <- c("Package",
+#                   ifelse(params$X@outp_formats_chr[1] == "Word","XXX"," "),
+#                   #"Ref", 
+#                   "Purpose", 
+#                   ifelse(params$X@outp_formats_chr[1] == "Word","YYY"," "),
+#                   #"Standard     ",# " ",
+#                   "R library dependencies")
 #df$Package <- "![](../Data/images/ready4.png){ width=10% }"#"\\includegraphics[valign=T,scale=2.5,raise=2mm]{../Data/images/ready4.png}"
-df$`Standard     `  <- df$`Standard     ` %>% stringr::str_replace_all("&nbsp;"," ")
+#df$`Standard     `  <- df$`Standard     ` %>% stringr::str_replace_all("&nbsp;"," ")
 if(params$X@outp_formats_chr[1] == "Word") {
@@
   }else{
-    df$Ref<-NULL
+    #df$Ref<-NULL
     #df$Package <- ""
@@
     # df$Package <- "\\includegraphics[valign=M,scale=0.08,raise=3mm]{../Data/images/ready4.png}"
-    df[,c(1,3,5:6)]   %>%
+    #df[,c(1,3,5:6)]   %>%
+    df %>%
     # kableExtra::kbl(format = "markdown",
@@
       kableExtra::kable_paper(full_width = F) %>%
-      kableExtra::column_spec(3,latex_valign = "m") %>%
+      kableExtra::column_spec(2, width = "20em", latex_valign = "m") %>%
       # kableExtra::column_spec(1, 
@@
       #                                                           150, 150)) %>%
-      kableExtra::column_spec(4, width = "24em",latex_valign = "m")
+      kableExtra::column_spec(3, width = "20em",
+                              latex_valign = "m")
     }

### 2023-10-21 Markdown/Manuscript/Child_RMDs/MS_Tables_4.Rmd
one table to go

@@
 
-```{r checktb, tab.cap='Transparent, reusable and updatable (TRU) assessment criteria applied to outcome valuation computational health economic model (CHEM)', tab.id = 'checktb', echo = F, results = 'asis'}
+```{r checktb, tab.cap='Assessment of a CHEM implementation in youth mental health using Transparent, Reusable and Updatable (TRU) criteria', tab.id = 'checktb', echo = F, results = 'asis'}
 library(kableExtra)  
-df <- data.frame(FIRST = c("REPLACE", "THESE", "PLACEHOLDERS"),
-                 SECOND = c("A","B","C"),
-                 THIRD = c("ONE","TWO","THREE"),
+df <- data.frame(Criterion = c("T1 Software files are open access", 
+                               "T2 Judgments and contributions are easily identified", 
+                               "R1 Programming practices promote generalisability and transferability",
+                               "R2 Licenses restrict only unethical reuse",
+                               "U1 Maintenance infrastructure is in place",
+                               "U2 New releases are systematically retested and deprecated"),
+                 `Met?` = c(rep("Yes",5),"Partial"),
+                 Detail = c("All source code and testing procedures are available in public GitHub repositories, with each code release persistently available in a Zenodo repository.
+Study dataset contains confidential patient records and was not published.
+Instead, a synthetic representation of the study dataset is persistently available in a repository in the Harvard Dataverse.
+Data files to support out of sample application of models are published at the same location.",
+                            "All module libraries, programs, and datasets are distributed with citation information.
+GitHub repositories detail author code contributions over project development history are publicly visible.
+Model catalogues persistently available on the Harvard Dataverse describe the predictive performance of models under multiple usage regimes.
+Each code library is documented with worked examples of how to apply modules.
+Analysis and reporting programs are self-documenting.
+Sub-routines for generating reports are documented with README files.",
+                            "Model code is written using both functional and object-oriented paradigms.
+Code library websites include hypothetical examples of generalisability (applying study algorithm to estimate mapping models from new data with the same predictor and outcome variables) and transferability (adapting study algorithm to develop mapping models from datasets with different predictor variables and outcomes measured with a different utility instrument)." ,
+                            "All code is distributed using GPL-3 licenses.
+Datasets use amended version of template provided by Harvard Dataverse, allowing reuse of data subject to some ethical restrictions (e.g., use in efforts to reidentify study participants is prohibited).",
+                            "All code is version controlled using git and GitHub, with semantic versioning.
+Each code library has a specified maintainer and guidance for potential code contributors is available on the project website.",
+                            "Continuous integration used for all code libraries, primarily for acceptance testing.
+Only limited use is made of unit testing.
+Retired library code is deprecated using tools from the lifecycle R library.
+Library documentation articles and datasets are also deprecated."),
                  check.names = F)
@@
       kableExtra::kable_paper(full_width = F) %>%
-      kableExtra::column_spec(1, bold=T) %>%
+      kableExtra::column_spec(1, width = "10em", bold=T) %>%
       kableExtra::column_spec(3, width = "35em")

### 2023-10-21 setup.R

@@ -8,7 +8,7 @@ X <- Ready4showSynopsis(#background_1L_chr = "Our study is entirely fictional.",
                         #conclusion_1L_chr = "We have identified criteria that can be used to systematically assess extent to which the computational implementation of health economic models adheres to the ethical goals of transparency, reusability and updatability. We have developed an open-source software framework that can support the ethical computational implementation of economic models in youth mental health. Our framework can be used as a prototype for developing future software frameworks to support ethical implementation of CHEMs.",
                         digits_int = 3L,
                         ethics_1L_chr = "Software framework development did not involve human subject research and was not ethically reviewed. The utility mapping worked example is a previously reported study that was reviewed and granted approval by the University of Melbourne’s Human Research Ethics Committee, and the local Human Ethics and Advisory Group (1645367.1).",
-                        funding_1L_chr = "Software framework development was funded by Orygen, VicHealth, Victoria University and an Australian Government Research Training Program (RTP) Scholarship . The utility mapping study used as a worked example was funded by the National Health and Medical Research Council (NHMRC, APP1076940), Orygen and headspace.",
+                        funding_1L_chr = "Software framework development was funded by Orygen, VicHealth, Victoria University and an Australian Government Research Training Program (RTP) Scholarship. The utility mapping study used as a worked example was funded by the National Health and Medical Research Council (NHMRC, APP1076940), Orygen and headspace.",
                         #interval_chr = "three months",
                         keywords_chr = c("open source models","health economics","mental disorders"),
                         outp_formats_chr = "PDF",
@@ -37,17 +37,17 @@ X <- renewSlot(X,
                "abstract_args_ls",
                {
                  args_ls <- X@abstract_args_ls
-                 args_ls$abstract_ls <- list(Summary = "Most health economic analyses are undertaken with the aid of computers. However, the ethical dimensions of implementing health economic models as software are poorly understood. 
-                                                        We propose that developers and funders of computational health economic models (CHEMs) share ethical responsibilities to (i) establish socially acceptable system requirements and design specifications; (ii) ensure fit for purpose implementation; and (iii) support socially beneficial use. 
+                 args_ls$abstract_ls <- list(Summary = "Most health economic analyses are undertaken with the aid of computers. However, the ethical dimensions of implementing health economic models as software (or computational health economic models (CHEMs)) are poorly understood. 
[…]

### 2023-10-21 Markdown/Manuscript/Child_RMDs/MS_Tables_2.Rmd
table 2 still a pain

--- 2023-08-01 Markdown/Manuscript/Child_RMDs/MS_Tables_2.Rmd
@@
 ---
-```{r timelygls, tab.cap='Framework standards', tab.id = 'timelygls', echo = F, results = 'asis'}
+```{r timelygls, tab.cap='Transparent, reusable and updatable (TRU) computational health economic models (CHEMs) are suggestive of ethical modelling practice', tab.id = 'timelygls', echo = F, results = 'asis', warning=FALSE}
 library(kableExtra)  
-df <- data.frame(`Objective` = rep("",20),
-  # `Models are` = c(rep("Transparent",6),
-  #                                 rep("Iterative",4),
-  #                                 rep("Modular",2),
-  #                                 rep("Epitomising",3),
-  #                                 rep("Licensed",3),
-  #                                 rep("Yielding",2)),
-  #                Goal = c(rep("people can easily see how a model has been implemented and tested",6),
-  #                         rep("a model is routinely updated to maintain and improve validity",4),
-  #                         rep("models and their components can be combined to extend their scope",2),
-  #                         rep("model code is sufficiently general to be be re-used in multiple decision contexts",3),
-  #                         rep("a model, its components and derivatives are persistently re-usable by other modeller",3),
-  #                         rep("a model can be simply, flexibly and reliably used as a decision aid",2)),
-                 Standard = c(paste0("A",#"T", 
-                                      1:7
-                                      ),
-                               paste0("R",1:9),# paste0("M",1:2),
-                               # paste0("E",1:3),
-                               # paste0("L",1:3),
-                               # paste0("Y",1:2),
-                               paste0("U",#"I",
-                                      1:4)
-                               ),
-                 Meaning = c(
-                   "Open online repositories are used to permanently archive, uniquely identify and transparently record authorship and development history of model code and data.",#T1
-                   # T2 MISSING - Merged With T1
-                   "Model code and data are documented.",#<T2, Was T3
-                   "Model code uses consistent and abstracted syntax.",# T3, Was T4 -->
-                   "Literate programming is used to implement model analyses.",#T4,Was T5
-                   "Model code coverage is reported.", #T5, New, replaces version now moved to T4 
-                   "All parts of a study analysis and reporting workflow can be reproduced and/or replicated.", #T6, was T7, Replaces Deleted T6 
-                   "Model code and data are distributed with tools to support appropriate citation.",#*L3: New, new location
-                   "Model code is made available for re-use under copyleft or permissive licenses.",#L1: **
-                   "Non-confidential model data is licensed for liberal re-use (potentially subject to ethical use terms).",#L2
-                   "Model code and data are stored and managed separately.",#*M1: Modified (lost ref to licensed and cited) 
-                   "Model code uses encapsulation and inheritence for data structures.",#*M2: Replacement - Old version now merged with E1 # And with E2: "Modules are inheriting data-structures.",#E2
-                   "Model code uses functions to implement algorithms.",#E1: Modified (lost ref to OOP and merged with M2) -->
-                   "Model code is distributed as code libraries.",
-                   "Test data is available to demonstrate the transferability of model code.",#E3: **
-                   # OLD CITATION
-                   "Statistical models are distributed with tools for making out of sample predictions.",#*Y1: New, Replaces Old Y1 (now Y2)
-                   "User-interfaces allow non-technical users to configure and use models.",#Y2: Was Y1     
-                   "Model code and data are version controlled.",#*I1, Was I2 
-                   "The signficiance and status of code and data updates are indicated with semantic versioning and release types.",#I2, Was I1 
-                   "Continuous integration is used to verify model code updates.",#I3 
-                   "Deprecation conventions are used to retire model code and data."#**I4 
-                 ),
+df <- data.frame(`CHEM attribute` = c("Transparent", "Reusable", "Updatable"),
+                 `Social acceptability` = c("Modeller judgments, model features and verification checks can be reviewed by third parties.",
+                                                                        "Models can be modified to reflect alternative value judgments.",
+                                                                        "Models can be modified to reflect alternative value judgments."),
+                 `Fitness for purpose` = c("Modeller judgments, model features and verification checks can be reviewed by third parties.","Third party use increases likelihood of errors being identified.","Models that are maintained can be validly used for longer."),
+                 `Beneficial use` = c("Decision makers more likely to understand strengths and weakness of model before applying it.","Can be used to inform more decision problems, in more contexts and can help reduce duplicative mode development effort.","Models that are maintained can be validly used for longer."),
                  check.names = F)
@@
   }else{
-    df %>%
-      kableExtra::kbl(booktabs = T, 
-                      escape = F,
-                      caption = knitr::opts_current$get("tab.cap")) %>%
-      kableExtra::kable_paper(full_width = F) %>%
-      kableExtra::column_spec(1, bold=T) %>%
-      # kableExtra::collapse_rows(columns = 1) %>%
-      kableExtra::column_spec(3, width = "35em") %>%
-      kableExtra::pack_rows("Accountable - it is easy to see who developed, tested and applied a model and how they did it.",1,7) %>%
-      kableExtra::pack_rows("Updatable - a model and its components are maintained and continuously improved.",17,20) %>%
-      # kableExtra::pack_rows("Modular - models and their components can be combined to extend their scope",11,12) %>%
-      # kableExtra::pack_rows("Epitomising - model code can be re-used in other decision contexts",13,15) %>%
-      kableExtra::pack_rows("Reusable - a model and its components can be used in other models and by other modellers.",8,16) #%>%
+    # library(huxtable)
+    # library(dplyr)
+    #flextable::set_flextable_defaults() #fonts_ignore=TRUE
+    flextable::flextable(df) %>%
+      flextable::add_header_row(values = c(" ","Project team responsibility"),colwidths = c(1,3)) %>%
+      flextable::border_inner(border = officer::fp_border(style = "none")) %>%
+      flextable::border_outer() %>%
+      flextable::padding(padding.top = 5, part = "all") %>%
+      flextable::padding(padding.bottom = 5, part = "all") %>%
+            flextable::padding(padding.left = 5, part = "all") %>%
+      flextable::padding(padding.right = 5, part = "all") %>%
+      flextable::align(align = "center", part = "header") %>%
+      flextable::merge_h() %>%
+      flextable::merge_v() %>%
+      flextable::bold(j=1, part = "header") %>%
+      flextable::width(width = 1.5)
+    # %>%
+    #   
+      #flextable::merge_at(i=2,j=1:2)
+    # huxtable::as_hux(df) %>% 
+    #   #insert_row("MPG-DISP", "", "", "HP-WT", fill = "") %>% 
+    #   #huxtable::merge_cells(2:3,1) %>% 
+    #  # huxtable::set_header_rows(1, TRUE) %>% 
+    #   huxtable::set_col_width(c(.1,.1,.1,.7)) %>%
+    #   huxtable::set_wrap(1, value=T)
+      #huxtable::style_headers(bold = TRUE)
+    # df %>%
+    #   kableExtra::kbl(booktabs = T, 
+    #                   escape = F,
+    #                   caption = knitr::opts_current$get("tab.cap")) %>%
+    #   kableExtra::kable_paper(full_width = F) %>%
+    #   kableExtra::column_spec(1, bold=T) %>%
+    #   kableExtra::add_header_above(c(" ", "Project team responsibility" = 3), bold = T, italic = T) %>%
+    #   kableExtra::column_spec(2, width = "13em") %>%
+    #   kableExtra::column_spec(3, width = "13em") %>%
+    #   kableExtra::column_spec(4, width = "13em") %>%
+    #   kableExtra::collapse_rows(columns = 2, latex_hline = "none")
+      # kableExtra::column_spec(3, width = "35em") %>%
+      # kableExtra::pack_rows("Accountable - it is easy to see who developed, tested and applied a model and how they did it.",1,7) %>%
+      # kableExtra::pack_rows("Updatable - a model and its components are maintained and continuously improved.",17,20) %>%
+      # # kableExtra::pack_rows("Modular - models and their components can be combined to extend their scope",11,12) %>%
+      # # kableExtra::pack_rows("Epitomising - model code can be re-used in other decision contexts",13,15) %>%
+      # kableExtra::pack_rows("Reusable - a model and its components can be used in other models and by other modellers.",8,16) #%>%
       # kableExtra::pack_rows("Yielding - a model can be simply, flexibly and reliably used as a decision aid",19,20)
-
     }

### 2023-10-21 Markdown/Manuscript/Parent_PDF/Main_Bookdown_PDF.Rmd
table 2 still a pain

@@
     toc: no
+    kep_tex: yes
 params:

### 2023-10-21 Markdown/Manuscript/Parent_PDF/Parent_PDF.Rmd
table 2 still a pain

@@
       in_header: preamble.tex
+    keep_tex: true
     pandoc_args: 

### 2023-10-22 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
problems with table and figure placement

@@
 However, our prototype has a number of features that future work on CHEM software frameworks may find useful to incorporate.
-Firstly, developing a software framework to work within an existing and widely used open source programming language such as R or Python, can keep framework scope relatively narrow.
-This makes it more tractable to develop, maintain and learn, and can integrate other modelling tools written in that language (e.g., the dependency libraries we list in Table \@ref(tab:cpkgs)).
+Firstly, developing a software framework to work within an existing and widely used open source programming language such as R, can keep framework scope relatively narrow.
+This makes it more tractable to develop, maintain and learn, and facilitates integration with other modelling tools written in that language (e.g., the dependency libraries we list in Table \@ref(tab:cpkgs)).
 Secondly, implementation that combines both object-oriented and functional programming paradigms can avail of the modular and syntactical simplicity benefits of the former, while limiting needless bundling of code artefacts.

### 2023-10-22 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
problems with table and figure placement

@@
 
- - programs for replicating all steps from data ingest to manuscript reporting [@hamilton_matthew_2022_6129906], applying utility mapping models to new data [@hamilton_matthew_2022_6416330] and generating a synthetic representation of the study dataset [@hamilton_matthew_p_2022_6321821]; and
+ - programs for replicating all steps from data ingest to manuscript production [@hamilton_matthew_2022_6129906], applying utility mapping models to new data [@hamilton_matthew_2022_6416330] and generating a synthetic representation of the study dataset [@hamilton_matthew_p_2022_6321821]; and
 

### 2023-10-22 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
problems with table and figure placement

@@
 Although making a CHEM’s code, data and documentation publicly available is increasingly considered good practice, it is insufficient to enable model re-use.
-Key concerns for health economists when considering model reuse are generalisability (application without adaptation) and transferability (selective reuse and/or modification of model components) [@RN39].
+Key concerns for health economists when considering whether to reuse a model are generalisability (application without adaptation) and transferability (selective reuse and/or modification of model components) [@RN39].
 Writing model algorithms as collections of functions (short, self-contained and reusable software routines that each perform a discrete task) is good scientific computing practice [@Wilson_2017] and promotes selective reuse.
 Computational implementations that store model code and data in distinct files and locations (as opposed to embedding data such as parameter values into source code) are easier to selectively modify.
-Modular implementations construct models from multiple independently reusable and replaceable sub-models (modules) [@pan2021modular].
+Modular implementations enable models to be constructed from multiple independently reusable and replaceable sub-models (modules) [@pan2021modular].
 The programming concept inheritance [@8717448], deployed in object-oriented programming approaches, can facilitate the duplication and selective modification of models.
@@
 ##	Assessment criteria
-For each CHEM attribute that suggests ethical CHEM modelling practice, we identified assessment criteria that have the potential to be met with the assistance of software frameworks.
+For each CHEM attribute that suggests ethical CHEM modelling practice, we identified assessment criteria. <!-- that have the potential to be met with the assistance of software frameworks -->
 
@@
 
--	**U2**: Each new release of a model is systematically retested, with changes implemented to minimise disruptions for existing model users.
+-	**U2**: Each new release of a CHEM is systematically retested, with changes implemented to minimise disruptions for existing model users.

### 2023-10-22 Markdown/Manuscript/Child_RMDs/MS_Tables_2.Rmd
problems with table and figure placement

@@
 library(kableExtra)  
-df <- data.frame(`CHEM attribute` = c("Transparent", "Reusable", "Updatable"),
+df <- data.frame(` ` = c("Transparent", "Reusable", "Updatable"),
                  `Social acceptability` = c("Modeller judgments, model features and verification checks can be reviewed by third parties.",
@@
                  `Fitness for purpose` = c("Modeller judgments, model features and verification checks can be reviewed by third parties.","Third party use increases likelihood of errors being identified.","Models that are maintained can be validly used for longer."),
-                 `Beneficial use` = c("Decision makers more likely to understand strengths and weakness of model before applying it.","Can be used to inform more decision problems, in more contexts and can help reduce duplicative mode development effort.","Models that are maintained can be validly used for longer."),
+                 `Beneficial use` = c("Decision-makers can understand the strengths and weakness of models before applying them.","Can inform more decision problems, in more contexts with less duplicative effort.","Models can be validly used for longer."),
                  check.names = F)
@@
     #flextable::set_flextable_defaults() #fonts_ignore=TRUE
-    flextable::flextable(df) %>%
-      flextable::add_header_row(values = c(" ","Project team responsibility"),colwidths = c(1,3)) %>%
-      flextable::border_inner(border = officer::fp_border(style = "none")) %>%
-      flextable::border_outer() %>%
-      flextable::padding(padding.top = 5, part = "all") %>%
-      flextable::padding(padding.bottom = 5, part = "all") %>%
-            flextable::padding(padding.left = 5, part = "all") %>%
-      flextable::padding(padding.right = 5, part = "all") %>%
-      flextable::align(align = "center", part = "header") %>%
-      flextable::merge_h() %>%
-      flextable::merge_v() %>%
-      flextable::bold(j=1, part = "header") %>%
-      flextable::width(width = 1.5)
+    # flextable::flextable(df) %>%
+    #   flextable::border_inner(border = officer::fp_border(style = "none")) %>%
+    #   flextable::border_outer() %>%
+    #   flextable::align(align = "center", part = "header") %>%
+    #   flextable::merge_h() %>%
+    #   flextable::merge_v() %>%
+    #   flextable::valign(j=2, valign = "top") %>%
+    #   flextable::align(j=2:4, align = "center") %>%
+    #   flextable::bold(j=1, part = "all") %>%
+    #   flextable::bold(part = "header") %>%
+    #   flextable::width(j = 1, width = 1.2) %>%
+    #   flextable::width(j = 2:4, width = 1.6)
     # %>%
@@
       #huxtable::style_headers(bold = TRUE)
-    # df %>%
-    #   kableExtra::kbl(booktabs = T, 
-    #                   escape = F,
-    #                   caption = knitr::opts_current$get("tab.cap")) %>%
-    #   kableExtra::kable_paper(full_width = F) %>%
-    #   kableExtra::column_spec(1, bold=T) %>%
-    #   kableExtra::add_header_above(c(" ", "Project team responsibility" = 3), bold = T, italic = T) %>%
-    #   kableExtra::column_spec(2, width = "13em") %>%
-    #   kableExtra::column_spec(3, width = "13em") %>%
-    #   kableExtra::column_spec(4, width = "13em") %>%
-    #   kableExtra::collapse_rows(columns = 2, latex_hline = "none")
+    df %>%
+      kableExtra::kbl(booktabs = T,
+                      escape = F,
+                      caption = knitr::opts_current$get("tab.cap")) %>%
+      kableExtra::kable_paper(full_width = F) %>%
+      kableExtra::column_spec(1, bold=T) %>%
+      kableExtra::add_header_above(c(" ", "Project team responsibility" = 3), bold = T, italic = T) %>%
+      kableExtra::column_spec(2, width = "13em") %>%
+      kableExtra::column_spec(3, width = "13em") %>%
+      kableExtra::column_spec(4, width = "13em") %>%
+      kableExtra::collapse_rows(columns = 2, latex_hline = "none")
       # kableExtra::column_spec(3, width = "35em") %>%

### 2023-10-22 Markdown/Manuscript/Child_RMDs/MS_Tables_3.Rmd
problems with table and figure placement

@@
   library("ftExtra")
-  df[,c(1,3:4,6:7)] %>%
+  df %>% #[,c(1,3:4,6:7)] %>%
     ready4show::print_table(output_type_1L_chr = params$X@outp_formats_chr[1],
@@
     #df$Package <- ""
-    df$Package  <- df$Package %>% 
-                      purrr::map_chr(~paste0("\\includegraphics[valign=M,width=1.9cm,raise=4mm]{../Data/images/",.x,"_logo.png}"))#scale=0.4,raise=3mm]
+    # df$Package  <- df$Package %>% 
+    #                   purrr::map_chr(~paste0("\\includegraphics[valign=M,width=1.9cm,raise=4mm]{../Data/images/",.x,"_logo.png}"))#scale=0.4,raise=3mm]
     # df$Package <- "\\includegraphics[valign=M,scale=0.08,raise=3mm]{../Data/images/ready4.png}"

### 2023-10-22 Markdown/Manuscript/Child_RMDs/MS_Tables_4.Rmd
problems with table and figure placement

@@
 df <- data.frame(Criterion = c("T1 Software files are open access", 
-                               "T2 Judgments and contributions are easily identified", 
+                               "T2 Project team contributions and judgments are easily identified", 
                                "R1 Programming practices promote generalisability and transferability",
@@
                  Detail = c("All source code and testing procedures are available in public GitHub repositories, with each code release persistently available in a Zenodo repository.
-Study dataset contains confidential patient records and was not published.
+As the study dataset contains confidential patient records, it was not published.
 Instead, a synthetic representation of the study dataset is persistently available in a repository in the Harvard Dataverse.
@@
                             "All module libraries, programs, and datasets are distributed with citation information.
-GitHub repositories detail author code contributions over project development history are publicly visible.
+Public GitHub repositories detail author code contributions over project development history.
 Model catalogues persistently available on the Harvard Dataverse describe the predictive performance of models under multiple usage regimes.
-Each code library is documented with worked examples of how to apply modules.
+Each code library is documented with worked examples of how to apply CHEM modules.
 Analysis and reporting programs are self-documenting.
 Sub-routines for generating reports are documented with README files.",
-                            "Model code is written using both functional and object-oriented paradigms.
-Code library websites include hypothetical examples of generalisability (applying study algorithm to estimate mapping models from new data with the same predictor and outcome variables) and transferability (adapting study algorithm to develop mapping models from datasets with different predictor variables and outcomes measured with a different utility instrument)." ,
+                            "CHEMs are written using both functional and object-oriented paradigms.
+Code library documentation websites include hypothetical examples of generalisability (applying study algorithm to estimate mapping models from new data with the same predictor and outcome variables) and transferability (adapting study algorithm to develop mapping models from datasets with different predictor variables and outcomes measured with a different utility instrument)." ,
                             "All code is distributed using GPL-3 licenses.
-Datasets use amended version of template provided by Harvard Dataverse, allowing reuse of data subject to some ethical restrictions (e.g., use in efforts to reidentify study participants is prohibited).",
+Datasets use an amended version of template terms provided by Harvard Dataverse, allowing reuse of data subject to some ethical restrictions (e.g., use in efforts to reidentify study participants is prohibited).",
                             "All code is version controlled using git and GitHub, with semantic versioning.
 Each code library has a specified maintainer and guidance for potential code contributors is available on the project website.",
-                            "Continuous integration used for all code libraries, primarily for acceptance testing.
+                            "Continuous integration is used for all code libraries, primarily for acceptance testing.
 Only limited use is made of unit testing.

### 2023-10-22 Markdown/Manuscript/Parent_PDF/Main_Bookdown_PDF.Rmd
problems with table and figure placement

--- 2022-04-19 Markdown/Manuscript/Parent_PDF/Main_Bookdown_PDF.Rmd
@@
   bookdown::pdf_document2: 
+    toc: no
+    keep_tex: true
     includes:
@@
       - '--lua-filter=../Filters/author-info-blocks.lua'
-    toc: no
 params:

### 2023-10-22 Markdown/Manuscript/Parent_PDF/Springer.Rmd
problems with table and figure placement

---
# Supported options: 
#   sn-nature:       Style for submissions to Nature Portfolio journals
#   sn-basic:        Basic Springer Nature Reference Style/Chemistry Reference Style
#   sn-mathphys:     Math and Physical Sciences Reference Style
#   sn-aps:          American Physical Society (APS) Reference Style
#   sn-vancouver:    Vancouver Reference Style
#   sn-apa:          APA Reference Style 
#   sn-chicago:      Chicago-based Humanities Reference Style
#   default:         Default

classoptions: 
  - sn-vancouver      
  - Numbered      # Optional: Use numbered references instead of namedate references (only for sn-nature, sn-basic, sn-vancouver, sn-chicago, sn-mathphys or sn-nature)
  # - referee       # Optional: Use double line spacing 
  # - lineno        # Optional: Add line numbers
  # - iicol         # Optional: Double column layour

title: A prototype software framework for transparent, reusable and updatable computational health economic models
titlerunning: Transparent, reusable and updatable computational models

authors: 
  - prefix: Dr.
    firstname: Leading
    particle: van 
    lastname: Author
    suffix: III
    naturename: Poet Laureate
    degrees: MSc, PhD
    email: abc@def
    affiliation: [1,2]
    corresponding: TRUE
    equalcont: These authors contributed equally to this work.

  - firstname: Second
    lastname: Author
    affiliation: 2
    equalcont: These authors contributed equally to this work.

affiliations:
  - number: 1
    corresponding: TRUE
    info:
      orgdiv: Department
      orgname: Organization
    address:
        street: Street
        city: City
        postcode: 100190
        state: State
        country: Country
  - number: 2
    corresponding: TRUE
    info:
      orgname: Other Organisation

keywords:
  - key
  - dictionary
  - word

pacs: 
  jel:
    - "D8"
    - "H51"
  msc:
    - "35A01"
    - "65L10"

# Sample for unstructured abstract

params:
  X: NULL

abstract: "`r paste0(readLines('../Header/abstract.txt'),collapse=' ')`"

bibliography: bibliography.bib

header-includes: |
  %% Per the spinger doc, new theorem styles can be included using built in style, 
  %% but it seems the don't work so commented below
  %\theoremstyle{thmstyleone}%
  \newtheorem{theorem}{Theorem}%  meant for continuous numbers
  %%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
  %% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
  \newtheorem{proposition}[theorem]{Proposition}%
  %%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.

  %% \theoremstyle{thmstyletwo}%
  \theoremstyle{remark}
  \newtheorem{example}{Example}%
  \newtheorem{remark}{Remark}%

  %% \theoremstyle{thmstylethree}%
  \theoremstyle{definition}
  \newtheorem{definition}{Definition}%

  \usepackage{float}
  \let\origfigure\figure
  \let\endorigfigure\endfigure
  \renewenvironment{figure}[1][2] {
      \expandafter\origfigure\expandafter[H]
  } {
      \endorigfigure
  }
  \usepackage{lscape}
  \usepackage{pdflscape}
  \newcommand{\blandscape}{\begin{landscape}}
  \newcommand{\elandscape}{\end{landscape}}
  \usepackage[none]{hyphenat}
  \usepackage[export]{adjustbox}
  \usepackage{multirow}
  \usepackage{longtable}
  \usepackage{array}
  \usepackage{wrapfig}
  \usepackage{colortbl}
  \usepackage{booktabs} 
  \usepackage{colortbl}
  \usepackage{pdflscape}
  \usepackage{tabu}
  \usepackage{threeparttable}
  \usepackage[normalem]{ulem}
  \usepackage{threeparttablex}
  \usepackage{makecell}

# output: rticles::springer_article
output: 
  bookdown::pdf_book: 
    base_format: rticles::springer_article
    # includes:
    #   in_header: preamble.tex
    keep_tex: true
    pandoc_args: 
      - '--lua-filter=../Filters/scholarly-metadata.lua'
      - '--lua-filter=../Filters/author-info-blocks.lua'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      out.extra = "")
#library(flextable)# This forces knitr to label all figures.
```

```{r child="../Child_RMDs/All_Content.Rmd", echo=FALSE, warning=FALSE}
```

### 2023-10-22 Reports/Manuscript/Manuscript.tex
problems with table and figure placement

@@
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else
+  % xetex/luatex font selection
 \fi
@@
 \usepackage{lscape}
+\usepackage{pdflscape}
 \newcommand{\blandscape}{\begin{landscape}}
@@
 \usepackage{multirow}
+\usepackage{multirow}
+\usepackage{multicol}
+\usepackage{colortbl}
+\usepackage{hhline}
+\newlength\Oldarrayrulewidth
+\newlength\Oldtabcolsep
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{hyperref}
+\usepackage{float}
+\usepackage{wrapfig}
 \ifLuaTeX
@@
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
-  pdftitle={A framework for implementing an open source and modular economic model of youth mental health that is accountable, reusable and updatable},
-  pdfauthor={Matthew P Hamilton1,2,; Caroline X Gao1,3,2; Glen Wiesner4; Kate M Filia1,3; Jana M Menssink1,3; Petra Plencnerova5; David Baker1,3; Patrick D McGorry1,3; Alexandra Parker6; Jonathan Karnon7; Sue M Cotton1,3; Cathrine Mihalopoulos2},
-  pdfkeywords={open source models, health economics, mental disorders},
+  pdftitle={A prototype software framework for transparent, reusable and updatable computational health economic models},
+  pdfauthor={Matthew P Hamilton1,2,; Caroline X Gao2,3,1; Glen Wiesner4; Kate M Filia2,3; Jana M Menssink2,3; Petra Plencnerova5; David Baker2,3; Patrick D McGorry2,3; Alexandra Parker6,3; Jonathan Karnon7; Sue M Cotton2,3; Cathrine Mihalopoulos1},
+  pdfkeywords={computational models, ethics of modelling, health economics, mental disorders, open-source models, software frameworks},
   hidelinks,
@@
 
-\title{A framework for implementing an open source and modular economic model of youth mental health that is accountable, reusable and updatable}
-\author{Matthew P Hamilton\textsuperscript{1,2,*} \and Caroline X Gao\textsuperscript{1,3,2} \and Glen Wiesner\textsuperscript{4} \and Kate M Filia\textsuperscript{1,3} \and Jana M Menssink\textsuperscript{1,3} \and Petra Plencnerova\textsuperscript{5} \and David Baker\textsuperscript{1,3} \and Patrick D McGorry\textsuperscript{1,3} \and Alexandra Parker\textsuperscript{6} \and Jonathan Karnon\textsuperscript{7} \and Sue M Cotton\textsuperscript{1,3} \and Cathrine Mihalopoulos\textsuperscript{2}}
+\title{A prototype software framework for transparent, reusable and updatable computational health economic models}
+\author{Matthew P Hamilton\textsuperscript{1,2,*} \and Caroline X Gao\textsuperscript{2,3,1} \and Glen Wiesner\textsuperscript{4} \and Kate M Filia\textsuperscript{2,3} \and Jana M Menssink\textsuperscript{2,3} \and Petra Plencnerova\textsuperscript{5} \and David Baker\textsuperscript{2,3} \and Patrick D McGorry\textsuperscript{2,3} \and Alexandra Parker\textsuperscript{6,3} \and Jonathan Karnon\textsuperscript{7} \and Sue M Cotton\textsuperscript{2,3} \and Cathrine Mihalopoulos\textsuperscript{1}}
 \date{}
@@
 \begin{abstract}
-\textbf{Summary: } Compared to other disciplines, health economics rarely uses modular approaches to model development that facilitate re-use of model components.
-Although interest in open source health economic models (OSHEMs) is growing, uptake remains limited.
-We propose a framework for a modular OSHEM in youth mental health.
-The framework includes of set of X1 good practice standards for implementing a model that is accountable (X2 standards), reusable (X3 standards) and upatable (X4 standards).
-We provide a rationale for each standard.
-The framework also includes software toolkit of six R packages for authoring model modules (data structures and algorithms), supplying those modules with data and using the modules to implement reproducible modelling analyses.
-We describe an early application of the framework to developing utility mapping models that meet X5 standards.
-We discuss the potential benefits and challenges of extending this initial work to develop a more extensive model for undertaking economic analyses in youth mental health.
-\newline \newline \textbf{Code: } Visit \url{https://www.ready4-dev.com} for more information about how to find, install and apply the framework and model.
+\textbf{Summary: } Most health economic analyses are undertaken with the aid of computers.
+However, the ethical dimensions of implementing health economic models as software (or computational health economic models (CHEMs)) are poorly understood.
+We propose that developers and funders of CHEMs share ethical responsibilities to (i) establish socially acceptable user requirements and design specifications; (ii) ensure fitness for purpose; and (iii) support socially beneficial use.
+We further propose that a transparent (T), reusable (R) and updatable (U) CHEM is suggestive of a project team that has largely fulfilled these responsibilities.
+We propose six criteria for assessing CHEMs: (T1) software files are open access; (T2) project team contributions and judgments are easily identified; (R1) programming practices promote generalisability and transferability; (R2) licenses restrict only unethical reuse; (U1) maintenance infrastructure is in place; and (U2) new releases are systematically retested and appropriately deprecated.
+To facilitate CHEMs that meet TRU criteria, we have developed a prototype software framework in the open-source programming language R.
+The framework comprises six code libraries for authoring CHEMs, supplying CHEMs with data and undertaking analyses with CHEMs.
+The prototype software framework integrates with services for software development and research data archiving.
+We determine that an initial set of youth mental health CHEMs we developed with the prototype software framework wholly meet criteria T1-2, R1-2 and U1 and partially meet criterion U2.
+Our assessment criteria and prototype software framework can help inform and improve ethical implementation of CHEMs.
+Resource barriers to ethical CHEM practice should be addressed by research funders.
+\newline \newline \textbf{Code: } Visit \url{https://www.ready4-dev.com} for more information about how to find, install and apply the prototype software framework and CHEMs developed with it.
 \newline \newline
@@
 
-\textsuperscript{1} Orygen, Parkville, Australia\\
-\textsuperscript{2} School of Public Health and Preventive Medicine, Monash University, Clayton, Australia\\
+\textsuperscript{1} School of Public Health and Preventive Medicine, Monash University, Clayton, Australia\\
+\textsuperscript{2} Orygen, Parkville, Australia\\
 \textsuperscript{3} Centre for Youth Mental Health; The University of Melbourne, Parkville, Australia\\
@@
 \textsuperscript{5} headspace National Youth Mental Health Foundation, Melbourne, Australia\\
-\textsuperscript{6} Victoria University, Footscray, Australia\\
+\textsuperscript{6} Institute for Health and Sport, Victoria University, Footscray, Australia\\
 \textsuperscript{7} Flinders University, Adelaide, Australia
 
-\textsuperscript{*} Correspondence: \href{mailto:matthew.hamilton@orygen.org.au}{Matthew P Hamilton \textless{}\href{mailto:matthew.hamilton@orygen.org.au}{\nolinkurl{matthew.hamilton@orygen.org.au}}\textgreater{}}
+\textsuperscript{*} Correspondence: \href{mailto:matthew.hamilton1@monash.edu}{Matthew P Hamilton \textless{}\href{mailto:matthew.hamilton1@monash.edu}{\nolinkurl{matthew.hamilton1@monash.edu}}\textgreater{}}
 
@@
 
-Computational models, particularly those addressing economic topics, have become essential tools for health policy development {[}1,2{]}.
-Although influential and widely used, health economic models typically have a number of limitations that at best restrict their usefulness and which in some cases may facilitate harmful misuse.
-
-There is a strong case for making health economists more accountable for the appropriate use and social acceptability of their models.
-Users of models should be able to assess their adequacy for a particular purpose {[}3{]}.
-This goal is difficult to achieve in the current context of the poor reproducibility {[}4--6{]} and frequently insufficient validation {[}7{]} of health economic models.
-Value judgments strongly shape health economic analyses, yet are rarely made explicit, omissions that may lead to socially unacceptable policy recommendations {[}8{]}.
-A modelling team's value judgments about what questions to address, the most important features of a system to represent and the weighting of different types of evidence may be poorly aligned with those of the people impacted by decisions informed by model analyses {[}9{]}.
-As health economic models adopt more sophisticated techniques, the need for accountability grows.
-More complex models may be more prone to propagation errors {[}10{]} and models designed to address multiple questions should be expected to meet more onerous verification and validation obligations {[}11,12{]}.
-The nature and extent of individual model authorship contributions may be less clear in models implemented over longer time-frames with a large and changing group of collaborators {[}\textbf{thompson2022?}{]}.
-
-Collaborative approaches that encourage re-use of models by other modellers can help make modelling pojects more tractable {[}13{]}.
-However, as many health economic models are owned by pharmaceutical companies and consultancies, commercial considerations can limit the reuse of models and their constituent code and data {[}12{]}.
-Not all data included in health economic models can be ethically made publicly available due to privacy and confidentiality requirements.
-Transferring a health economic model developed for one jurisdiction for application in another will involve retaining some features and updating others {[}14{]}.
-Use of concepts with standardised meanings across jurisdictions {[}15{]}, supplying context specific data as replaceable data-packs and distributing source code under licenses that allow derivative works are all steps that can enhance model transferability.
-
-Health economic models should be updated and refined as new evidence emerges and decision contexts change {[}16{]}, but this occurs infrequently {[}17{]}.
-Decision makers are frequently left to rely on economic analyses that become less valid and relevant each year.
-A model can grow stale when changes in the real world, whether sudden (e.g.~new pandemics) or gradual (e.g.~demographic), is not represented by corresponding updates to relevant model features.
-Even when the system being modelled remains relatively stable, new research findings may potentially invalidate aspects of a model's original conceptualisation and implementation.
-Funding for health economic modelling projects rarely extend to provision of medium term support for model updates and improvements.
-The career trajectories of health economists can also mitigate against adequate maintenance of a model, it being relatively common for model authors to have moved on from the team that owns the model and / or from working on the health condition for which the model was developed.
-
-A potential strategy for improving model accountability, reusability and updatability is to make models both modular and open-source.
-
-A modular approach to model building involves models being constructed by combining multiple replaceable sub-models (modules) {[}18{]}.
-When used as model sub-components, modules communicate with other modules but they can be also run independently {[}19{]}.
-Advantages of modular models include feasibility (large projects are broken into smaller tasks, with each component independently developed and tested) and flexibility (making it easier to selectively replace or update specific parts of a model and to scale up or down the level of granularity) {[}18{]}.
-Modular approaches are currently being used to facilitate the development of complex computational models in disciplines such as biology {[}18{]}, neuroscience {[}20{]} and ecology {[}19{]}.
-Although the related and enabling concept of reusable reference models has been recommended in health economics {[}21{]}, peer reviewed studies describing modular health economic models remain relatively rare, though examples exist in tuberculosis {[}22{]} and cardiology {[}23{]}.
-
-The benefits of modular models can be enhanced if multiple modelling teams have the capacity to contribute and use model modules.
-To facilitate this, modular models may be implemented as open source projects that grant liberal permissions to access and re-use model source code and data {[}18--20{]}.
-Although there appears to be in principle support from many health economists for greater use of open source health economic models (OSHEMs) {[}24{]}, actual implementations are rare {[}12,25,26{]}.
-Barriers to adoption of OSHEMs include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations {[}24,27{]}.
-Adherence to good practice guidance is an essential requirement for healthcare modelling {[}2{]}, but guidelines for implementing OSHEMs remain scarce, piecemeal and need improving {[}28{]}.
-
-We plan to develop a modular OSHEM of youth mental health.
-Open source approaches have been recommended to help develop the mental health modelling field {[}29{]} but only one mental health related model (in Alcohol Use Disorder {[}30{]}) is currently indexed {[}RECHECK{]} in the Open Source Models Clearinghouse {[}25,31{]}.
-Other than our own work, we are aware of just one open source mental health reference model - in Major Depressive Disorder - that is currently in development {[}32{]}.
-
-In this paper, we introduce a framework for developing a modular youth mental health OSHEM. Specifically we describe the framework's:
-
-\begin{itemize}
-\item
-  good practice standards for implementing a modular OSHEM;
-\item
-  software toolkit for developing a modular OSHEM consistent with those good practice standards; and
-\item
-  application to implementing model modules to support the development and use of utility mapping models.
-\end{itemize}
-
-\hypertarget{guidelines-for-oshems}{%
-\section{Guidelines for OSHEMs}\label{guidelines-for-oshems}}
-
-Guidelines on health economic model transparency were published ten years ago {[}11{]} and made recommendations on documenting models; however, notably missing were recommendations on the sharing of model code and data.
-More recent and more general modelling guidance {[}2{]} recommends the sharing of code and data through digital repository services and the use of version control systems.
-Based on these and other existing sources of guidance and our own experience, we propose 20 guidelines for implementing OSHEMs that are \textbf{TIMELY} (Transparent, Iterative, Modular, Epitomising, Licensed and Yielding - see Table @ref(tab:timelygls)).
+Health economics is a discipline concerned with problems that arise due to scarce resources, such as how to value health and healthcare, allocate healthcare budgets and configure health services {[}1{]}.
+In seeking to solve these problems, health economists typically use models which are simplified and selective representations of systems that are believed to influence human health.
+A health economic model should be capable of being described using words and figures (a conceptual model), equations (a mathematical model) and software (a computational model).
+Health economic scientific manuscripts typically describe a model using its conceptual and mathematical representations but report results that have been generated by its computational representation (i.e., the format that allows computers to perform calculations).
+The conceptual, mathematical and computational representations of a model are assumed to be isomorphic.
+However, the ease of independently assessing the validity of this assumption depends in part on how a health economic model has been implemented computationally.
+
+The set of software files implementing a health economic model's structure, data and algorithms can be called a computational health economic model (CHEM).
+CHEMs can be developed using commercial modelling software or open-source programming languages such as Python {[}2{]} or R {[}3{]}.
+An advantage of commercial modelling software is that users often require limited or no programming skills to develop and apply CHEMs.
+However, open-source software programming languages may facilitate the development of CHEMs that are more transparent, reusable and updatable {[}4,5{]}.
+The decision about what type of software development platform to use must balance ethical considerations and resource constraints (see Table \ref{tab:proscons}).
 
@@
 
-\caption{(\#tab:timelygls)TIMELY Guidelines for OSHEMs}
+\caption{\label{tab:proscons}Implications of choosing commercial modelling software or an open-source programming language for the computational implementation of health economic models}
 \centering
-\begin{tabular}[t]{>{}ll>{\raggedright\arraybackslash}p{35em}}
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{7em}>{\raggedright\arraybackslash}p{20em}>{\raggedright\arraybackslash}p{20em}}
 \toprule
-Characteristic & Guideline & Meaning\\
+Implications & Commercial modelling software & Open-source programming language\\
 \midrule
+ & (+) Will include tools to efficienty accomplish many common modelling tasks. & (-) Initial development is likely to be time and resource intensive.\\
+
+ & (+) Requires limited or no programming skills. & (+) Over medium term, efficiency savings are possible if:\\
+
+ & (-) Requires model developers and users to purchase software licenses & (i)  artefacts (code and data) from pre-existing models are leveraged; and / or\\
+
+\multirow{-4}{7em}{\raggedright\arraybackslash \textbf{Resources}} &  & (ii)    maintaining and transferring (e.g. to new decision problems / contexts) model.\\
+\cmidrule{1-3}
 \addlinespace[0.3em]
-\multicolumn{3}{l}{\textbf{Transparent - people can easily see how a model has been implemented and tested}}\\
-\hspace{1em}\textbf{} & T1 & Uniquely identified copies of model code and data are permanently archived in open online repositories\\
-\hspace{1em}\textbf{} & T2 & Model code and data are documented\\
-\hspace{1em}\textbf{} & T3 & Model code uses a simple and consistent syntax\\
-\hspace{1em}\textbf{} & T4 & Model analyses and reporting are implemented using literate programming\\
-\hspace{1em}\textbf{} & T5 & Code coverage is reported\\
-\hspace{1em}\textbf{} & T6 & All parts of a study analysis and reporting workflow can be reproduced and/or replicated\\
+\multicolumn{3}{c}{\textbf{Transparency}}\\
+\hspace{1em} & (+) Popular tools (e.g. Excel) are readily understood by many. & (+) Easy to publicly share testable source code while selectively restricting access to confidential data.\\
+
+\hspace{1em} & (-) Non seemless integration with scientific manuscript authoring pipelines raises risk of (undetected) transcription errors when reporting results.
+& (+) Easy to make clear who has developed and tested each part.\\
+
+\hspace{1em} &  & (-) Novel code increases likelihood of (undetected) software errors.\\
+
 \addlinespace[0.3em]
-\multicolumn{3}{l}{\textbf{Iterative - a model is routinely updated to maintain and improve validity}}\\
-\hspace{1em}\textbf{} & I1 & Model code and data are version controlled\\
-\hspace{1em}\textbf{} & I2 & Model code and data use semantic versioning\\
-\hspace{1em}\textbf{} & I3 & Continuous integration is used to verify model code updates\\
-\hspace{1em}\textbf{} & I4 & Deprecation conventions are used to retire model code and data\\
+\multicolumn{3}{c}{\textbf{Reusability}}\\
+\hspace{1em} & (+) Files will open and execute correctly for years after project is completed.
+& (-) Potentially fragile – if not maintained / not bundled with all required and correctly versioned dependencies\\
+
+\hspace{1em} &  & (+) Facilitates modular implementations that make complex model representations more tractable.\\
+
+\hspace{1em} &  & (+) Facilitates customised integration with existing data / decision systems.\\
+
 \addlinespace[0.3em]
-\multicolumn{3}{l}{\textbf{Modular - models and their components can be combined to extend their scope}}\\
-\hspace{1em}\textbf{} & M1 & Model code and data are stored and managed separately\\
-\hspace{1em}\textbf{} & M2 & Model code defines encapsulating data structures\\
-\addlinespace[0.3em]
-\multicolumn{3}{l}{\textbf{Epitomising - model code can be re-used in other decision contexts}}\\
-\hspace{1em}\textbf{} & E1 & Model code is distributed as libraries of classes and functions\\
-\hspace{1em}\textbf{} & E2 & Model code defines inheriting data-structures\\
-\hspace{1em}\textbf{} & E3 & Test data is available to demonstrate generalised applications of model code\\
-\addlinespace[0.3em]
-\multicolumn{3}{l}{\textbf{Licensed - a model and its components are persistently re-usable by other modellers}}\\
-\hspace{1em}\textbf{} & L1 & Model code is made available for re-use under copyleft or permissive licenses\\
-\hspace{1em}\textbf{} & L2 & Non-confidential model data is licensed for liberal re-use (subject to additional terms for de-identified human data)\\
-\hspace{1em}\textbf{} & L3 & Model code and data are distributed with tools to support appropriate citation\\
-\addlinespace[0.3em]
-\multicolumn{3}{l}{\textbf{Yielding - a model can be simply, flexibly and reliably used as a decision aid}}\\
-\hspace{1em}\textbf{} & Y1 & Models are distributed with validated tools to support their safe and appropriate re-use\\
-\hspace{1em}\textbf{} & Y2 & Simple user-interfaces allow non-technical users to configure and run models\\
+\multicolumn{3}{c}{\textbf{Updatability}}\\
+\hspace{1em}\multirow{-7}{7em}{\raggedright\arraybackslash \textbf{Ethical}} & (-) Selective modification with appropriate attribution can be difficult.
+& (-) Facilitates collaborative development and maintenance.\\
 \bottomrule
@@
 
-\hypertarget{transparent-models}{%
-\subsection{Transparent models}\label{transparent-models}}
-
-A range of tools and practices are available to help make models more transparent.
-The most efficient way to widely disseminate code and data may be to use existing open science infrastructure {[}2{]} to make permanently accessible and uniquely identfied digital artefacts.
-Model code and data also need to be clearly documented, potentially with different versions for technical and non-technical users {[}11{]}.
-Consistent use of meaningful naming conventions when authoring code is recommended {[}33,34{]}.
-Code can be made easier to follow by using the practices of abstraction {[}35{]}, where only simple, high level commands are routinely exposed to reviewers, and polymorphism {[}36{]}, where the same command (e.g.~``simulate'') can be reused to implement different algorithms of the same type.
-Programs to implement model analyses can be made comprehensible to even non-technical users through the use of literate programming techniques to render documents that integrate computer code with plain English descriptions.
-
-An essential component of quality assuring health economic models is verification - ensuring that calculations are correct and consistent with model specifications {[}37{]}.
-One useful concept for informing model users about the extensiveness of verification checks is code coverage {[}38{]} - the proportion of model code that has been explicitly tested.
-Finally, transcription errors - mistakes introduced when transferring data between sources, models and reports - are very common in health economic models {[}39{]}.
-The risk of these errors might be lower if there was full transparency across all steps in a study workflow.
-Scientific computing tools now make it relatively straightforward to author programs that reproducibly execute all steps in data ingest, processing and reporting {[}33{]}.
-
-\hypertarget{iterative-models}{%
-\subsection{Iterative models}\label{iterative-models}}
-
-To avoid OSHEMs going stale - losing validity and usefulness with time - they should be routinely updated.
-Each update of code and data should be uniquely identifiable and retrievable, a goal that can be facilitated by use of version control tools {[}2{]}.Labeling each change using semantic versioning {[}40{]} conventions can signal the potential importance of an update to users of model code and data.
-Continuous integration {[}41{]} tools can help verify that each code update passes multiple quality tests.
-Finally, using deprecation conventions that take an informative and staged approach to retiring old code and data reduces the risk that model revisions have unintended consequences on third party users.\\
-
-\hypertarget{modular-models}{%
-\subsection{Modular models}\label{modular-models}}
-
-An important consideration when combining model components (or modules) is to ensure that interactions between two modules do not compromise the validity of either.
-Using the coding practice of encapsulation {[}35{]} can help ensure that model modules can be safely combined {[}42{]}.
-
-\hypertarget{epitomising-models}{%
-\subsection{Epitomising models}\label{epitomising-models}}
-
-A key challenge to generalising health economic models is that they are typically developed to inform a decision problem with a highly specific jurisdictional context.
-However, a number of choices about how these models are implemented can significantly increase the re-usability of model code in other contexts.
-
-Writing code as collections of functions (short, self-contained and reusable algorithms that each perform a discrete task) is recommended as good practice for scientific computing {[}33{]}.
-When bundled for distribution as libraries, functions have the potential to be widely re-used, often in contexts very different than those they were originally developed for.
-A special type of function, called a method, can only be applied to a pre-defined class of data structure.
-Due to the coding concept of inheritance {[}35{]}, the more restricted nature of methods can be used to enhance the re-usability of model code in different decision contexts {[}42{]}.
-For example, when generalising a model developed for the Australian context to a UK context, one could create a class that initially inherits all of the methods defined for the Australian model and then write new or replacement methods as needed for the UK model.Whatever type of functions are written for a modelling project, it is good practice to make available test or toy data to demonstrate their use {[}33{]}.
-
-\hypertarget{licensed-models}{%
-\subsection{Licensed models}\label{licensed-models}}
-
-To make model code and data widely re-usable by others, it is important to provide users with appropriate and explicit permissions.
-In the context of open source models, there are two broad categories of licensing options.
-Some guidance strongly recommends the use of permissive licensing {[}33{]} that provides users with great flexibility as to the purposes (including commercial) for which the content could be re-used.
-An alternative approach is to use copyleft licenses {[}43{]} that can require content users to distribute any derivative works they create under similar open source arrangements.The most suitable approach may differ for code and data.
-
-For code, it may be appropriate to adopt the prevailing open source licensing practice within the programming language being used.
-For data, it may not be sufficient to simply choose between a permissive license like the Public Domain Dedication (CC0) {[}44{]} or a copyleft option such as the Attribution-Share Alike (CC-BY-SA) {[}45{]}.
-Responsible custodianship of some de-identified mental health data may involve using or adapting template terms of use {[}46{]} which have a number of ethical clauses (for example, prohibiting efforts to re-identify research participants).
-Licenses may or may not specify that model re-users must give appropriate acknowledgement to model authors.
-Citation tools can be distributed with each individual code or data item to inform re-users of the desired attribution.
-
-\hypertarget{yielding-models}{%
-\subsection{Yielding models}\label{yielding-models}}
-
-OSHEMs can be time and skills intensive for modellers to develop - but they should be easy for others to use.
-Statistical models are a common output of health economic evaluations, but they are often not reported in a format that enables others to confidently and reliably re-use them {[}47{]}.
-Open source approaches can help address this by disseminating code artefacts that enable easy and appropriate use of a statistical model to make predictions with new data.
-However, great care must be exercised when doing so if models are derived from data on human subjects as some software artefacts by default contain a copy of the source dataset.
-Such dataset copies must therefore be replaced (for example, with synthetic data) and the amended artefact's predictive performance then retested before any public release.
-Another way to make OSHEMs easier to use is to develop simple user-interfaces for non-technical users.
-
-\hypertarget{modelling-toolkit}{%
-\section{Modelling Toolkit}\label{modelling-toolkit}}
-
-We have developed a toolkit to help streamline the process of developing OSHEMs that meet the TIMELY standards. The toolkit is comprised of online repositories and software.
-
-\hypertarget{repositories}{%
-\subsection{\texorpdfstring{Repositories }{Repositories }}\label{repositories}}
-
-We created a GitHub organisation where all framework software source code is stored, documented, version controlled and continuously integrated {[}48{]}.
-To store citable archived copies of release copies of our software, we created a Zenodo community {[}49{]}.
-Finally, to manage datasets for use in models developed with the framework, we created a dedicated collection within the Harvard Dataverse {[}50{]}.
-
-\hypertarget{software}{%
-\subsection{\texorpdfstring{Software }{Software }}\label{software}}
-
-A coding framework for OSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions {[}34{]}.
-
-As a foundation for implementing the framework, we authored a development version R package that defines a novel syntax and a template class for model modules {[}51{]}.
-To enable the syntax and module template be applied to modelling projects, we then created five additional development version R packages that provide tools for authoring:
+Open-source CHEMs remain rare {[}6,7{]}.
+The software used to develop CHEMs was identified as a barrier to open-source model implementations by participants in a 2020 survey of health economists {[}5{]}.
+Other reported barriers relate to difficulties in generalising models, updating models and transferring model data, concerns about the level of public access and lack of interest from decision-makers, and legal, confidentiality and security considerations {[}5{]}.
+
+Better software frameworks could potentially help address some of the barriers to open-source CHEM development.
+A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users {[}8{]}.
+A software framework provides a foundation for developing multiple software applications with shared resources (e.g., code and data files), that can be modified to suit specific needs.
+Advantages of using software frameworks include facilitating code reuse and extension, promoting good programming practice and the capability to provide enhanced functionality and performance without additional effort by developers {[}9{]}.
+Software frameworks have widely been developed and implemented in data science, for example, PyTorch {[}10{]} for machine learning using Python.
+
+A high-level software framework for implementing open-source CHEMs in R has previously been developed with the primary aim of improving model transparency {[}11{]}.
+However, to gain widespread adoption, a software framework for CHEMs may need to provide tools to help model developers meet a broader range of ethical practice requirements.
+There are multiple challenges to overcome.
+Firstly, the ethical responsibilities of public health computational modellers remain poorly understood {[}12{]} and the computational modelling landscape is changing fast {[}13{]}.
+Secondly, software frameworks can be challenging and time consuming to create and may become excessively complex over time {[}9{]}.
+Thirdly, software frameworks can be difficult to learn, often requiring model developers to undergo specialist training {[}8{]}.
+
+In this paper, we:
+
+\begin{enumerate}
+\def\labelenumi{(\roman{enumi})}
+\item
+  propose a set of ethical responsibilities for CHEM project teams and criteria for assessing ethical CHEM implementations;
+\item
+  describe a prototype software framework we have developed to support the ethical implementation of CHEMs; and
+\item
+  assess an initial set of youth mental health CHEMs developed with our software framework against our proposed ethical CHEM implementation criteria.
+\end{enumerate}
+
+\hypertarget{ethical-issues}{%
+\section{Ethical issues}\label{ethical-issues}}
+
+We considered literature on modelling practice and reflected on our prior experience with developing and using CHEMs to identify: (i) some core ethical responsibilities of CHEM project teams; (ii) attributes of CHEMs that can suggest fulfillment of these responsibilities; and (iii) criteria against which these attributes can be assessed.
+
+\hypertarget{ethical-responsibilities-of-chem-project-teams}{%
+\subsection{Ethical responsibilities of CHEM project teams}\label{ethical-responsibilities-of-chem-project-teams}}
+
+Boden and McKendrick {[}12{]} propose a framework for ethical public health modelling based on the criteria of independence (concerning how modeller subjectivity shapes model design), beneficence / non-maleficence (concerning model quality and utility), transparency (concerning the need for policymakers to reliably evaluate model strengths and weaknesses) and justice (concerning the social obligations of modellers to consider and communicate ethical issues about model use).
+However, these criteria are not specific to the computational model, but are designed to apply to a modelling project as a whole, including a model's conceptual and mathematical representations.
+The authors propose 13 questions to evaluate ethical risk across the four criteria, but of these, only ``is the model code open source or available on request'' (for transparency) and ``has the model been verified, i.e., does it do what the modeller wants it to do?'' (for beneficence / non-maleficence) are specific to model's representation as software.
+
+To identify ethical issues that are specific to CHEMs, we first considered the distinct phases in a software development project.
+Software development lifecycle (SDLC) models take different approaches to the inclusion, naming, definition, sequencing and iteration of project phases {[}14{]}.
+However, SDLC models typically have components that can principally map to the concepts of \emph{planning} (e.g., identification of system / user requirements and design specifications), \emph{implementation} (e.g., development and testing) and \emph{release} (e.g., deployment, system integration, maintenance and support).
+For simplicity, we propose one overarching ethical responsibility for CHEM project teams for each phase.
+These responsibilities are to:
+
+\begin{enumerate}
+\def\labelenumi{(\roman{enumi})}
+\item
+  \textbf{establish socially acceptable user requirements and design specifications} (during CHEM planning);
+\item
+  \textbf{ensure fitness for purpose} (of CHEM implementation); and
+\item
+  \textbf{support socially beneficial use} (on CHEM release).
+\end{enumerate}
+
+Transparency underpins all three responsibilities (Table \ref{tab:timelygls}).
+Boden and McKendrick's other ethical criteria can be selectively mapped to each phase's responsibility: justice and independence to the planning responsibility; independence to the implementation responsibility; and beneficence / non-maleficence and justice to the release responsibility.
+All three ethical responsibilities have implications for both professional practice and project resourcing.
+As it is unreasonable to place expectations of modellers that they are not resourced to fulfil, these responsibilities should apply jointly to health economic model developers and funders.
+
+Misalignment between the values of computational model developers and those of the population groups affected by decisions based on their models presents significant ethical risks {[}15,16{]}.
+The value judgments of health economic modellers are rarely adequately specified, omissions that may lead to socially unacceptable policy recommendations {[}16{]}.
+These value judgments influence the assumptions, selection of model features and standards for evidence that shape health economic model projects {[}17{]}.
+For example, as illustrated in Table \ref{tab:proscons}, project resource constraints may require model developers to make trade-offs when agreeing CHEM \textbf{user requirements and design specifications}.
+These trade-offs in turn determine how straightforward it is for a CHEM to be subsequently amended to reflect alternative value judgments relating to model conceptualisation and mathematical formalisation (Table \ref{tab:timelygls}).
+
+Modellers have duties both to ensure a computational model is \textbf{fit for purpose} and to provide potential third-party users with the means of assessing its adequacy for their proposed uses {[}6,12,18,19{]}.
+However, it is common for health economic models to have serious methodological flaws {[}20,21{]}; insufficient validation {[}22--24{]}, poor reproducibility {[}25--27{]}; and undeclared errors {[}28{]}.
+Appropriate computational implementation choices can help address many of these shortcomings, for example by automating quality assurance checks and facilitating manual reviews by third parties.
+
+A CHEM will have limited \textbf{social benefit} if it is rarely used, if mis-used or when its acceptability and adequacy rapidly decay.
+Reuse of CHEMs as components of other models can potentially make model development more efficient {[}29,30{]}.
+However, health economic models face challenges related to transferability across jurisdictions {[}30{]} that create barriers to reuse.
+Without ongoing maintenance, a CHEM risks becoming less reliable with time {[}30{]} and is at risk of being deployed for purposes for which it is poorly suited {[}13{]}.
+Currently, health economic models are rarely implemented computationally in a manner that facilitates routine updates {[}31{]}, thus limiting the temporal window within which a CHEM can be validly applied.
+
+\hypertarget{chem-attributes-associated-with-ethical-modelling-practice}{%
+\subsection{CHEM attributes associated with ethical modelling practice}\label{chem-attributes-associated-with-ethical-modelling-practice}}
+
+The responsibilities of model project teams over a CHEM lifecycle are easier to state than to measure.
+However, aspects of ethical modelling practice may be inferred from measurable attributes of CHEMs.
+As described in Table \ref{tab:timelygls}, we believe that the creators of transparent, reusable and updatable (TRU) CHEMs are likely to have fulfilled a number of their ethical obligations.
+We therefore selected these model attributes to use as the basis for deriving ethical assessment criteria.
+
+\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
+
+\global\setlength{\Oldtabcolsep}{\tabcolsep}
+
+\setlength{\tabcolsep}{0pt}
+
+\renewcommand*{\arraystretch}{1.5}
+
+\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
+
+\begin{longtable}[c]{|p{1.20in}|p{1.60in}|p{1.60in}|p{1.60in}}
+
+\caption{Transparent,\ reusable\ and\ updatable\ (TRU)\ computational\ health\ economic\ models\ (CHEMs)\ are\ suggestive\ of\ ethical\ modelling\ practice}\label{tab:timelygls}\\
+
+\ascline{1pt}{666666}{1-4}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{\ }}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1pt}>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{Social\ acceptability}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1pt}>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{Fitness\ for\ purpose}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1pt}>{\centering}m{\dimexpr 1.6in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{Beneficial\ use}}}} \\
+
+\ascline{1pt}{666666}{1-4}\endfirsthead \caption[]{Transparent,\ reusable\ and\ updatable\ (TRU)\ computational\ health\ economic\ models\ (CHEMs)\ are\ suggestive\ of\ ethical\ modelling\ practice}\label{tab:timelygls}\\
+
+\ascline{1pt}{666666}{1-4}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{\ }}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1pt}>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{Social\ acceptability}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1pt}>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{Fitness\ for\ purpose}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1pt}>{\centering}m{\dimexpr 1.6in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{Beneficial\ use}}}} \\
+
+\ascline{1pt}{666666}{1-4}\endhead
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{Transparent}}}} & \multicolumn{2}{!{\color[HTML]{000000}\vrule width 1pt}>{\centering}p{\dimexpr 3.2in+2\tabcolsep+1pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Modeller\ judgments,\ model\ features\ and\ verification\ checks\ can\ be\ reviewed\ by\ third\ parties.}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1pt}>{\centering}m{\dimexpr 1.6in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Decision-makers\ can\ understand\ the\ strengths\ and\ weakness\ of\ models\ before\ applying\ them.}}} \\
+
+\ascline{1pt}{000000}{1-4}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{Reusable}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1pt}>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Third\ party\ use\ increases\ likelihood\ of\ errors\ being\ identified.}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1pt}>{\centering}m{\dimexpr 1.6in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Can\ inform\ more\ decision\ problems,\ in\ more\ contexts\ with\ less\ duplicative\ effort.}}} \\
+
+\ascline{1pt}{000000}{1-1}\ascline{1pt}{000000}{3-4}
+
+\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{Updatable}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep}}{\multirow[t]{-2}{*}{\parbox{1.6in}{\centering \textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Models\ can\ be\ modified\ to\ reflect\ alternative\ value\ judgments.}}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1pt}>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Models\ that\ are\ maintained\ can\ be\ validly\ used\ for\ longer.}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1pt}>{\centering}m{\dimexpr 1.6in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Models\ can\ be\ validly\ used\ for\ longer.}}} \\
+
+\ascline{1pt}{666666}{1-4}
+
+\end{longtable}
+
+\arrayrulecolor[HTML]{000000}
+
+\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
+
+\global\setlength{\tabcolsep}{\Oldtabcolsep}
+
+\renewcommand*{\arraystretch}{1}
+
+Taking steps to make computational models \textbf{transparent} is an important part of ethical public health modelling practice {[}12{]}.
+Guidance on transparency in health economic modelling recommend that model code and data should be clearly documented {[}32{]}.
+Notably, the same guidelines, published over ten years ago, do not recommend sharing model code and data.
+However, more recent healthcare modelling guidance does recommend public dissemination of such artefacts {[}18{]}.
+Online repository services such as Zenodo {[}33{]} and Dataverse {[}34{]} provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each code and data collection.
+Ensuring that calculations are correct and consistent with model specifications is an essential part of CHEM quality assurance {[}35{]}.
+The extensiveness of such verification checks can be reported using the concept of code coverage {[}36{]} - the proportion of model code that has been explicitly tested.
+Tests should ideally combine both unit tests (to verify that small, isolated sections of code produce the correct output when run independently) and acceptance tests (to verify that the correct output is produced when multiple code components are run together to perform tasks that meet core user-requirements {[}37{]}).
+The nature and extent of individual model authorship contributions can become unclear when models are implemented over longer time-frames with a large and changing group of collaborators {[}15{]}.
+This issue can be addressed by use of online repository services such as GitHub {[}38{]}, that provide citation tools and can transparently record all individual code contributions to a modelling project over its lifecycle.
+
+A CHEM that is \textbf{reusable} also signals ethical modelling practice.
+Although making a CHEM's code, data and documentation publicly available is increasingly considered good practice, it is insufficient to enable model re-use.
+Key concerns for health economists when considering whether to reuse a model are generalisability (application without adaptation) and transferability (selective reuse and/or modification of model components) {[}39{]}.
+Writing model algorithms as collections of functions (short, self-contained and reusable software routines that each perform a discrete task) is good scientific computing practice {[}40{]} and promotes selective reuse.
+Computational implementations that store model code and data in distinct files and locations (as opposed to embedding data such as parameter values into source code) are easier to selectively modify.
+Modular implementations enable models to be constructed from multiple independently reusable and replaceable sub-models (modules) {[}41{]}.
+The programming concept inheritance {[}42{]}, deployed in object-oriented programming approaches, can facilitate the duplication and selective modification of models.
+Granting permissions to others to use, test and adapt models and their components, can be facilitated by two broad categories of open source licenses.
+Some guidance strongly recommends the use of permissive licensing {[}40{]} that provides users with great flexibility as to the purposes (including commercial) for which content can be re-used.
+Alternatively, copyleft licenses {[}43{]} can be used to require that derivative works created by content users remain open-source.
+
+Models should be \textbf{updatable} so that they remain valid for longer, evolving as new evidence emerges and the systems being modelled change {[}30,44{]}.
+Ensuring that a model is regularly reviewed to identify and implement required improvements is a recommended defence against model validity decay {[}13{]}.
+Sustainable maintenance of open source research software requires both a core development team and an active user community {[}45{]}.
+Online communities can be an efficient means of engaging model users in testing each version of a model, identifying issues and suggesting improvements.
+Services such as GitHub {[}38{]} provide collaborative code development tools {[}46{]} that help elicit, integrate and reconcile contributions from multiple contributors and to ensure each update is uniquely identifiable and retrievable.
+It is also important that verification checks are rerun with each model update, a task that can be automated using the software development practice of continuous integration {[}47{]}.
+The risk of software revisions having unintended consequences for third party users can be mitigated through the use of deprecation conventions {[}48{]} that take an informative and staged approach to retiring outdated CHEMs.
+
+\hypertarget{assessment-criteria}{%
+\subsection{Assessment criteria}\label{assessment-criteria}}
+
+For each CHEM attribute that suggests ethical CHEM modelling practice, we identified assessment criteria.
+
+How \textbf{transparent} a CHEM is can be assessed against the criteria:
 
@@
 \item
-  documented model modules {[}52{]};
-\item
-  documented functions (including methods), written in a consistent house style {[}53{]};
-\item
-  citable, quality assured R packages {[}54{]};
-\item
-  model datasets {[}55{]};
-\item
-  model analyses and reports {[}56{]}.
+  \textbf{T1}: Software files (executable code, testing procedures and outcomes and non-confidential data) are available in open access repositories.
+\item
+  \textbf{T2}: It is easy to see who funded, developed and tested each part of the CHEM and to identify the modelling team's assumptions, judgments and theories about CHEM development and use.
 \end{itemize}
 
-The six R packages, their primary focus, the TIMELY standards they support and the third-party packages they depend on are summarised in Table @ref(tab:cpkgs).
-When used in conjunction with framework repositories, the six packages extend existing R packages provide strong support for implementing 16 of the TIMELY standards.
-However, the software only weakly supports implementing the standards relating to disseminating statistical models (Y1) and user-interface development (Y2) and does not yet provide any workflow tools to help implement the standards for code coverage (T5) and deprecation conventions (I4).
-Standards not supported or weakly supported by our software can be met with existing developer tools in R and we plan to progressively integrate these third-party tools with our own in future releases of our software.
-Another future priority is to submit production versions of each R package for review by and archiving on the Comprehensive R Archive Network (CRAN) {[}57{]}.
+How \textbf{reusable} a CHEM is can be assessed against the criteria:
+
+\begin{itemize}
+\item
+  \textbf{R1}: Programming practices facilitate both generalisability and transferability.
+\item
+  \textbf{R2}: Licenses restrict only unethical use and allow anyone to ethically reuse model code and non-confidential data, in whole or in part, without charge, and for purposes that include the creation of derivative works.
+\end{itemize}
+
+How \textbf{updatable} a CHEM is can be assessed against the criteria:
+
+\begin{itemize}
+\item
+  \textbf{U1}: Maintenance infrastructure is in place to support version control and collaboration with model users.
+\item
+  \textbf{U2}: Each new release of a CHEM is systematically retested, with changes implemented to minimise disruptions for existing model users.
+\end{itemize}
+
+\hypertarget{prototype-software-framework}{%
+\section{Prototype software framework}\label{prototype-software-framework}}
+
+To support the development of CHEMs that meet TRU assessment criteria, we have created a prototype software framework called ready4.
+The software framework aims to provide a toolkit for: (i) enabling modular implementation of CHEMs; (ii) authoring and documenting CHEM modules; (iii) managing the labelling and transfer of CHEM input and output data; and (iv) authoring reproducible analyses that apply CHEMs to compatible data.
+
+To achieve these goals, we have implemented the software framework as R {[}3{]} code libraries that integrate with a number of online services and which are supported by a documentation website.
+
+\hypertarget{r-libraries}{%
+\subsection{R libraries}\label{r-libraries}}
+
+A library in the R language will typically depend on multiple other R libraries, all of which potentially have different authors.
+As the number of third-party dependencies of an R library grows so does the fragility of that library (e.g., the library may cease to work as intended due to changes in one of its dependency libraries).
+To reduce the fragility of our framework we implemented it as multiple R libraries rather than one R library.
+In total we authored six novel R libraries to implement the ready4 framework, all of which have distinct purposes and dependencies (Table \ref{tab:cpkgs}).
+
+One framework library provides a \textbf{foundation for modular CHEM implementations}.
+In modular model implementations, modules need to be able to share inputs and outputs with each other and to be run as independent models {[}49{]}.
+To achieve this, the foundation framework library defines a template CHEM module (using R's S4 class system), which can be used to create other CHEM modules with a common set of inherited properties.
+One of these inherited properties is a novel syntax of 15 core commands that enable CHEM module algorithms to be consistently named.
+The foundation library also contains tools for retrieving web-based information on CHEM modules, datasets and analysis programs authored with the framework and tools for partially automating updates to a project documentation website.
+
+Three framework libraries are designed to help streamline and standardise workflows for \textbf{authoring CHEM modules} from the template module.
+The R language supports functional and object-oriented programming paradigms {[}50{]}.
+Authoring with each of these paradigms is facilitated by a dedicated CHEM module authoring library.
+One module authoring library contains tools for writing functions in a consistent house style and automatically generating basic documentation for each function.
+A second module authoring library contains tools to help streamline and standardise the authoring and documenting of novel CHEM modules.
+A third module authoring library provides tools for disseminating themed bundles of CHEM modules as R libraries that are:
+
+\begin{itemize}
+\item
+  documented (with a website and PDF manuals);
+\item
+  licensed (using the copyleft GNU GPL-3 {[}66{]} by default);
+\item
+  easily citable (citation information can be retrieved within an R session or from hosting repositories); and
+\item
+  quality assured (each update triggers continuous integration workflows, including any acceptance and unit tests created by module library authors).
+\end{itemize}
+
+A library for \textbf{managing CHEM data} contains tools for supplying CHEM modules with input data ingested from local (i.e., a user's computer) or remote (online repositories) locations, labelling CHEM module datasets and exporting CHEM module data to online repositories.
+A library for \textbf{authoring reproducible analyses} contains tools to help write programs that apply CHEM modules to compatible datasets for the purpose of undertaking health economic analyses.
+These analysis programs can be either self-documenting (code is integrated with plain English explanations of what it does) or trigger the creation of explanatory documents (e.g., a scientific manuscript).
 
@@
 
-\caption{(\#tab:cpkgs)Framework software to enable the readyforwhatsnext model to meet TIMELY guidelines}
+\caption{\label{tab:cpkgs}Software framework R libraries}
 \centering
-\begin{tabular}[t]{ll>{}l>{\raggedright\arraybackslash}m{24em}}
+\begin{tabular}[t]{l>{\raggedright\arraybackslash}m{20em}>{\raggedright\arraybackslash}m{20em}}
 \toprule
-Package & Focus & Guideline      & Depends on these R packages\\
+Package & Purpose & R library dependencies\\
 \midrule
-\includegraphics[valign=M,width=1.9cm,raise=4mm]{../Data/images/ready4_logo.png} & Syntax & T3           M3 & assertthat bib2df dataverse dplyr fs Hmisc kableExtra knitr lifecycle magrittr methods natmanager piggyback purrr readr readxl rlang rmarkdown rvest stats stringi stringr testit testthat tibble tidyRSS tools utils zen4R\\
-\includegraphics[valign=M,width=1.9cm,raise=4mm]{../Data/images/ready4fun_logo.png} & Functions & T2-3             E1 & desc devtools dplyr generics gert Hmisc knitr lifecycle lubridate magrittr methods piggyback pkgdown purrr readxl ready4 ready4show ready4use rlang sinew stats stringi stringr testit testthat tibble tidyr tools usethis utils xfun\\
-\includegraphics[valign=M,width=1.9cm,raise=4mm]{../Data/images/ready4class_logo.png} & Modules & T2-3         M2   E1-2 & devtools dplyr fs gtools Hmisc knitr lifecycle magrittr methods purrr ready4 ready4fun ready4show rlang stats stringi stringr testit testthat tibble tidyr usethis utils\\
-\includegraphics[valign=M,width=1.9cm,raise=4mm]{../Data/images/ready4pack_logo.png} & Libraries & T1      I1-3  M1-2 E1   L1,3 & dataverse dplyr knitr lifecycle magrittr methods purrr ready4 ready4class ready4fun rlang stringr testthat tibble tidyr utils\\
-\includegraphics[valign=M,width=1.9cm,raise=4mm]{../Data/images/ready4use_logo.png} & Data & T1-2         M1   E3   L2-3 & data.table dataverse dplyr fs Hmisc knitr lifecycle magrittr methods piggyback purrr readxl ready4 ready4show rlang stats stringi stringr testit testthat tibble tidyr utils\\
+ready4 & Provide a template and novel syntax for modular CHEM implementations and tools for finding interoperable CHEM modules, datasets and reproducible analysis programs.
+& assertthat bib2df dataverse dplyr fs Hmisc kableExtra knitr lifecycle magrittr methods natmanager piggyback purrr readr readxl rlang rmarkdown rvest stats stringi stringr testit testthat tibble tidyRSS tools utils zen4R\\
+ready4fun & Streamline and standardise the authoring and documenting of functions that support transferable and generalisable model algorithms.
+& desc devtools dplyr gert Hmisc knitr lifecycle lubridate magrittr methods piggyback pkgdown purrr readxl ready4 ready4show ready4use rlang sinew stats stringi stringr testit testthat tibble tidyr tools usethis utils xfun\\
+ready4class & Streamline and standardise the authoring and documenting of new interoperable CHEM modules.
+& devtools dplyr fs gtools Hmisc knitr lifecycle magrittr methods purrr ready4 ready4fun ready4show rlang stats stringi stringr testit testthat tibble tidyr usethis utils\\
+ready4pack & Help bundle and disseminate newly created CHEM modules as R libraries that are documented, licensed and quality assured.
+& dataverse dplyr knitr lifecycle magrittr methods purrr ready4 ready4class ready4fun rlang stringr testthat tibble tidyr utils\\
+ready4use & Help manage the labelling and transfer of data between CHEM modules and local and remote data repositories.
+& data.table dataverse dplyr fs Hmisc knitr lifecycle magrittr methods piggyback purrr readxl ready4 ready4show rlang stats stringi stringr testit testthat tibble tidyr utils\\
 \addlinespace
-\includegraphics[valign=M,width=1.9cm,raise=4mm]{../Data/images/ready4show_logo.png} & Reporting & T2,4,6                           Y1-2 & dataverse DescTools dplyr flextable grDevices here Hmisc kableExtra knitr knitrBootstrap lifecycle magrittr methods officer purrr ready4 rlang rmarkdown stringi stringr testthat tibble tidyr utils xtable\\
+ready4show & Facilitate the use of CHEM modules in programs to implement integrated and reproducible data ingest, analysis and reporting pipelines.
+& dataverse DescTools dplyr flextable grDevices here Hmisc kableExtra knitr knitrBootstrap lifecycle magrittr methods officer purrr ready4 rlang rmarkdown stringi stringr testthat tibble tidyr utils xtable\\
 \bottomrule
@@
 
+\hypertarget{online-services}{%
+\subsection{Online services}\label{online-services}}
+
+Framework libraries are designed to be used in conjunction with a number of third-party online services that we established and configured accounts with.
+
+We created a GitHub organisation (a collection of code repositories) where source code that we author is stored and version controlled.
+We configured individual repositories in our GitHub organisation to implement continuous integration.
+By default, code libraries authored with our framework will use continuous integration to assess compliance with policies specified by the Comprehensive R Archive Network (CRAN) {[}51{]}.
+To track our code coverage, we linked our GitHub organisation to an account we established at codecov {[}52{]}.
+To facilitate the creation and hosting of documentation websites, we enabled GitHub Pages in each repository used for code library development.
+
+We also created a Zenodo community - a collection of permanent, uniquely identified repositories.
+We then linked our Zenodo community and GitHub organisation so that every time we specify a version of code in one of our GitHub repositories as a ``release'', a copy of that code is automatically created on Zenodo with a DOI.
+Finally, to manage model datasets, we created a dedicated collection within the Harvard Dataverse installation.
+
+\hypertarget{documentation-website}{%
+\subsection{Documentation website}\label{documentation-website}}
+
+We developed a framework documentation website (\url{https://www.ready4-dev.com}) that provides guidance to model developers on how to use and contribute improvements to the ready4 software framework and CHEM modules developed with it.
+The documentation website is versioned, which means documentation relating to prior versions of framework software can be archived, retrieved and viewed.
+
+The documentation website was developed using the Hugo framework {[}53{]}, Docsy theme {[}54{]} and Algolia DocSearch {[}55{]} and is hosted using the Netlify {[}56{]} service.
+We used functions from our foundation framework library to partially automate website updates relating to available CHEM modules, datasets and analysis programs.
+We linked our Netlify account to our GitHub organisation so that the project website would automatically update whenever its source code (publicly available in a GitHub repository) was edited.
+
+\hypertarget{application-in-youth-mental-health}{%
+\section{Application in youth mental health}\label{application-in-youth-mental-health}}
+
+We are using the ready4 software framework to implement multiple transparent, reusable and updatable CHEMs in youth mental health (see Figure \ref{fig:fig1}).
+Some initial outputs from this work are publicly available as development version releases.
+
+\begin{figure}
+\includegraphics[width=400px]{../Data/images/Figure1} \caption{High level summary of planned implementation of youth mental health economic model}\label{fig:fig1}
+\end{figure}
+
+\hypertarget{economic-topics}{%
+\subsection{Economic topics}\label{economic-topics}}
+
+Currently, we are using the ready4 software framework to develop, apply, and share youth mental health CHEMs in four of the twelve domains of health economics identified by Wagstaff and Culyer {[}1{]}:
+
+\begin{itemize}
+\item
+  health and its value (our projects: models to map psychological and functional measures to health utility);
+\item
+  determinants of health and ill-health (our projects: models for creating synthetic household populations with key risk and protective factors for mental disorders);
+\item
+  demand for health and health care (our projects: spatial epidemiology and help-seeking choice models); and
+\item
+  supply of health services (our projects: a model of primary mental health care services for young people).
+\end{itemize}
+
+Potential future directions are to supplement this work with CHEMs in two additional Wagstaff and Culyer domains of: (i) public health (to model the impact of selected fiscal policy and regulation options on young people's mental health); and (ii) human resources (to model the supply and behaviours of the youth mental health workforce).
+Our ultimate aim is to flexibly combining all our CHEMs in analyses that help answer questions in two additional Wagstaff and Culyer domains:
+
+\begin{itemize}
+\item
+  efficiency and equity (our goal: assess the distributional impacts and identify the optimal targeting of youth mental health interventions); and
+\item
+  economic evaluation (our goal: assess the cost-utility of competing policy options for improving the mental health of young people).
+\end{itemize}
+
+Although we are principally interested in using CHEMs to answer policy questions relating to the mental health of young people in Australia, we want to facilitate CHEM transferability to other jurisdictions.
+Our CHEMs are being derived from and applied to real data (which can be empirical, simulated or assumption, so long as it is appropriate for use in analysis intended to inform decision-making) from Australia.
+To help demonstrate the potential use of CHEMs in other decision contexts, we also create toy datasets.
+Data created for illustration purposes is prominently labelled as not for use in decision-analysis.
+
+\hypertarget{case-study-health-and-its-value}{%
+\subsection{Case study: health and its value}\label{case-study-health-and-its-value}}
+
+We have previously described a study {[}57{]} to develop utility mapping models for use in samples of young people presenting to primary mental health services.
+The ready4 software framework was used in that study to develop CHEM modules, supply those modules with data and implement modelling analyses, creating the following artefacts:
+
+\begin{itemize}
+\item
+  development version module libraries for describing and validating youth mental health human record datasets {[}58{]}, scoring health utility {[}59{]}, specifying utility mapping models {[}60{]} and implementing reproducible utility mapping studies {[}61{]};
+\item
+  a development version library of functions for finding and using utility mapping models developed with these tools {[}62{]};
+\item
+  collections of real data (study input and results {[}63{]}) and toy data (synthetic populations for testing model modules {[}64{]});
+\item
+  programs for replicating all steps from data ingest to manuscript production {[}65{]}, applying utility mapping models to new data {[}66{]} and generating a synthetic representation of the study dataset {[}67{]}; and
+\item
+  subroutines for creating a catalogue of utility mapping models {[}68{]} and generating a draft scientific manuscript {[}69{]} for studies implemented with these modules.
+\end{itemize}
+
+We created a checklist (Table \ref{tab:checktb}) that we used to subjectively assess these study outputs against TRU criteria.
+For each criterion, we provided a global assessment of whether it was met using the responses ``yes'', ``no'' or ``partial''.
+We believe our utility mapping study CHEMs have satisfactorily met five of the six criteria (T1, T2, R1, R2 and U1) and have partially met one criterion (U2).
+The main shortcomings that we identified when applying the assessment criteria was that we have yet to adequately implement unit testing of the R libraries authored as part of this study.
+
 \blandscape
 
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0040}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0094}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0335}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0375}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0067}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0094}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.8995}}@{}}
-\caption{(\#tab:checktb)TIMELY Checklist applied to utility mapping study}\tabularnewline
-\toprule()
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Standard
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Met?
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Description
-\end{minipage} \\
-\midrule()
-\endfirsthead
-\toprule()
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Standard
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Met?
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Description
-\end{minipage} \\
-\midrule()
-\endhead
-T1 & ~ & Publicly archived & ~ ~ ~ ~ & Yes & ~ & 5 libraries (youthvars, scorz, specific, TTU and youthu) {[}58--62{]}, 3 programs {[}63--65{]}, 2 sub-routines {[}66,67{]} and 2 datasets {[}68,69{]} are permanently archived with unique identifiers.
-\\
-T2 & ~ & Documented & ~ ~ ~ ~ & Yes & ~ & All code libraries have documenting websites with URLs that concatenate `\url{https://ready4-dev.github.io/}' and the package name (e.g.~\url{https://ready4-dev.github.io/youthvars}).
-All three Markdown programs are self-documenting, with one {[}63{]} including additional instructions in a README file.
-Only one sub-routine {[}67{]} is documented with a meaningful README file.
-All datasets have meaningful metadata descriptors.
-\\
-T3 & ~ & Consistent syntax & ~ ~ ~ ~ & Yes & ~ & All libraries, programs and sub-routines use the same house style, which allows most library documentation to be written by algorithms from the ready4fun package {[}53{]}.
-All libraries except {[}62{]} use framework syntax, as does one program {[}63{]}.
-\\
-T4 & ~ & Literately programmed & ~ ~ ~ ~ & Yes & ~ & All programs use literate programming. \\
-T5 & ~ & Code coverage & ~ ~ ~ ~ & No & ~ & No current reporting of code coverage. \\
-T6 & ~ & Reproducible & ~ ~ ~ ~ & Yes & ~ & All parts of the study workflow from raw data ingest through to data processing, analysis, reporting and dissemination of study outputs can be reproduced (if granted access to source data) or replicated (using supplied synthetic data) with one program {[}63{]}.
-\\
-I1 & ~ & Version controlled & ~ ~ ~ ~ & Yes & ~ & All code is version controlled using Git and GitHub. All source code is available in a GitHub organisation {[}48{]}. \\
-I2 & ~ & Semanticly versioned & ~ ~ ~ ~ & Yes & ~ & Semantic version is used in all code.
-As no code library has yet been submitted to CRAN, only the development version extensions of each version number have been incremented to date.
-\\
-I3 & ~ & Continuously integrated & ~ ~ ~ ~ & Yes & ~ & All six libraries use continuous integration (CI).
-CI results for each library can be viewed at a URL that concatenates `\url{https://github.com/ready4-dev/}', the package name and `/actions' (e.g.~\url{https://github.com/ready4-dev/youthvars/actions}) \\
-I4 & ~ & Deprecation & ~ ~ ~ ~ & Yes & ~ & Retired code is deprecated using lifecycle package tools (e.g.~everything after ``\#\# DEPRECATED FNS'' in \url{https://github.com/ready4-dev/youthvars/blob/main/data-raw/fns/add.R} ).
-Package vignettes and datasets are also deprecated e.g.~\url{https://ready4-dev.github.io/youthvars/articles/Replication_DS.html} ) \\
-M1 & ~ & Separate code and data & ~ ~ ~ ~ & Yes & ~ & All development code is stored on repos in a GitHub organisation {[}48{]} and all archived releases are available in a Zenodo community {[}49{]}.
-All non-confidential data is stored in repositories within a Harvard Dataverse collection {[}50{]}.
-\\
-M2 & ~ & Encapsulated & ~ ~ ~ ~ & Yes & ~ & Four {[}58--61{]} out of five libraries include encapsulated modules.
-Examples are the items beginning with Scorz, Specific and Youthvars that are listed in this table: \url{https://ready4-dev.github.io/ready4/articles/V_01.html\#current-ready4-framework-modules} as well as the S4 classess from the TTU package listed here: \url{https://ready4-dev.github.io/TTU/reference/index.html} \\
-E1 & ~ & Libraries & ~ ~ ~ ~ & Yes & ~ & All code libraries include functions.
-The most complete list of functions for each library is available by clicking the `Manual - Developer (PDF)' link on each package's documentation homepage (see item T2 above).
-\\
-E2 & ~ & Inheriting & ~ ~ ~ ~ & Yes & ~ & All modules (see item M2) inherit from the Ready4Module class and can be inherited from. \\
-E3 & ~ & Test data & ~ ~ ~ ~ & Yes & ~ & Two synthetic datasets and their data dictionaries are publicly available in a data repository {[}69{]}.
-One (ymh\_clinical\_tb.RDS) closely resembles the study dataset and was released so that the main study algorithm {[}63{]} can be rerun by those without access to the confidential study dataset.
-The other (eq5d\_ds\_dict.RDS) is deliberately different to the source dataset in both variable naming convention and the concepts used for predictors and outcome measures.
-It was created to demonstrate generalised applications of study algorithms.
-\\
-L1 & ~ & Copyleft code & ~ ~ ~ ~ & Yes & ~ & All code libraries, programs and sub-routines use GPL-3 licenses. \\
-L2 & ~ & Liberal, safe data terms & ~ ~ ~ ~ & Yes & ~ & Datasets use amended version of template provided by Harvard Dataverse {[}46{]}. \\
-L3 & ~ & Citation tools & ~ ~ ~ ~ & Yes & ~ & All libraries have a CITATION file in the inst directory.
-All code repositories have a CITATION.cff file.
-All datasets have citation generating metadata.
-\\
-Y1 & ~ & Prediction tools & ~ ~ ~ ~ & Yes & ~ & Model catalogues (PDF files beginning with `AAA\_TTU\_MDL\_CTG') are available in the study results dataset {[}68{]} and describe the predictive performance of all models under a variety of usage regimes (including when the source dataset in the R model object is replaced with fake data).
-The youthu library {[}62{]} includes tools for searching for and applying models compatible with different types of input data.
-An example program to demonstrate this functionality is available in both RMarkdown {[}64{]} and rendered PDF formats (the `Application.pdf' file in the study results dataset {[}68{]}).
-\\
-Y2 & ~ & User interface & ~ ~ ~ ~ & No & ~ & No Shiny app user interface has yet been developed. \\
-\bottomrule()
-\end{longtable}
+\begin{table}
+
+\caption{\label{tab:checktb}Assessment of a CHEM implementation in youth mental health using Transparent, Reusable and Updatable (TRU) criteria}
+\centering
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{10em}l>{\raggedright\arraybackslash}p{35em}}
+\toprule
+Criterion & Met? & Detail\\
+\midrule
+\textbf{T1 Software files are open access} & Yes & All source code and testing procedures are available in public GitHub repositories, with each code release persistently available in a Zenodo repository.
+As the study dataset contains confidential patient records, it was not published.
+Instead, a synthetic representation of the study dataset is persistently available in a repository in the Harvard Dataverse.
+Data files to support out of sample application of models are published at the same location.\\
+\textbf{T2 Project team contributions and judgments are easily identified} & Yes & All module libraries, programs, and datasets are distributed with citation information.
+Public GitHub repositories detail author code contributions over project development history.
+Model catalogues persistently available on the Harvard Dataverse describe the predictive performance of models under multiple usage regimes.
+Each code library is documented with worked examples of how to apply CHEM modules.
+Analysis and reporting programs are self-documenting.
+Sub-routines for generating reports are documented with README files.\\
+\textbf{R1 Programming practices promote generalisability and transferability} & Yes & CHEMs are written using both functional and object-oriented paradigms.
+Code library documentation websites include hypothetical examples of generalisability (applying study algorithm to estimate mapping models from new data with the same predictor and outcome variables) and transferability (adapting study algorithm to develop mapping models from datasets with different predictor variables and outcomes measured with a different utility instrument).\\
+\textbf{R2 Licenses restrict only unethical reuse} & Yes & All code is distributed using GPL-3 licenses.
+Datasets use an amended version of template terms provided by Harvard Dataverse, allowing reuse of data subject to some ethical restrictions (e.g., use in efforts to reidentify study participants is prohibited).\\
+\textbf{U1 Maintenance infrastructure is in place} & Yes & All code is version controlled using git and GitHub, with semantic versioning.
+Each code library has a specified maintainer and guidance for potential code contributors is available on the project website.\\
+\addlinespace
+\textbf{U2 New releases are systematically retested and deprecated} & Partial & Continuous integration is used for all code libraries, primarily for acceptance testing.
+Only limited use is made of unit testing.
+Retired library code is deprecated using tools from the lifecycle R library.
+Library documentation articles and datasets are also deprecated.\\
+\bottomrule
+\end{tabular}
+\end{table}
 
 \elandscape
-
-\hypertarget{application}{%
-\section{Application}\label{application}}
-
-\hypertarget{readyforwhatsnext}{%
-\subsection{readyforwhatsnext}\label{readyforwhatsnext}}
-
-Our approach to model development is to undertake a number of discrete modelling projects of the people, places, platforms and programs that shape the mental health and wellbeing of young people and to progressively link them together by means of a common framework.
-To model people we are developing synthetic representations of populations of interest {[}69{]} that describe relevant individual characteristics and their relationships, algorithms that map psychological measures to health utility {[}70{]} and choice models for predicting the helpseeking behaviour of young people {[}71{]}.
-Our in-development model of places {[}72{]} has the aim of synthesising geometry and spatial attribute data to characterise the geographic distribution of relevant demographic, environmental, epidemiological and service infrastructure features.
-We are in the early stages of a multi-annual project to develop a service platform model that will represent the processes and operations of a complex primary youth mental health service.
-We also plan to extend and update our prior work reviewing economic evidence relating to youth mental health programs {[}73{]} so that it can be integrated with this model.
-
-Our initial work on \textbf{readyforwhatsnext} is focused on Victoria, Australia but the framework we are using to develop it is designed to facilitate extension by ourselves and others to different jurisdictional decision contexts.
-Progress is reported on a project website {[}74{]}.
-
-\hypertarget{utility-mapping}{%
-\subsection{Utility mapping}\label{utility-mapping}}
-
-We used framework toolkits to develop model code and datasets for implementing a utility mapping study that has previously been described {[}70{]}.
-Table @ref(tab:checktb) assesses that study against each TIMELY standard, 18 of which the study was able to meet.
-The two current standards where the study falls short are in reporting code coverage and including a user-interface.
-Both these items are current development priorities for our team.
 
@@
 
-Mental disorders impose high health, social and economic burdens worldwide {[}75,76{]}.
-Much of this burden is potentially avertable {[}77{]}, but poorly financed and organised mental health systems are ill-equipped for this challenge{[}78,79{]}.
-The large and widespread additional mental health burdens recently observed during the COVID-19 pandemic{[}80{]} and predicted as a potential future consequence of climate change {[}81{]}, highlight the need to improve the resilience and adaptability of these systems.
-To help stem growing demand for mental health services, policymakers have also been encouraged to place greater emphasis on tackling the social determinants of mental disorders {[}82{]}.
-
-Major mental health reform programs, can involve the identification, prioritisation, sequencing, targeting and monitoring of multiple interdependent initiatives.
-
-The significant deficits in our understanding of the systems in which mental disorders emerge and are treated {[}83{]} suggest that there is ample scope for mental health systems models to progressively improve their validity over time.
-Prospective work could address the weak theoretical underpinnings for understanding complex mental health systems {[}84{]}.
-For example, it remains unclear why increased investments in mental health care have yet to discernibly reduce the prevalence and burden of mental disorders{[}85{]}.
-The literature, and evidence base, regarding how the requirements, characteristics and performance of mental health services are shaped by spatiotemporal context needs to be further developed {[}86{]}.
-There is also a need for better evidence to identify the social determinants of mental disorders most amenable to preventative interventions, and for which population sub-groups such interventions would be most effective {[}87{]}.
-
-The development, validation and updating of more complex mental health economic models implemented over longer time frames may be too onerous a burden for a single modelling team.
-
-Developing networks of modellers working on common health conditions has been recommended as a strategy for improving model validity {[}28{]} and some of us are part of a nascent initiate of this type in mental health {[}88{]}.
-Similarly, developing partnerships between modellers and decision-makers across the life-cycle of a modelling project can help ensure models are appropriately conceptualised, implemented and have practical utility as decision aids {[}89,90{]}.
+Ethical practice is a core expectation of health researchers and computational methods underpin most quantitative research, yet an understanding of what constitutes ethical public health modelling practice is underdeveloped {[}12{]}.
+We have addressed this gap with our proposed responsibilities for model developers and funders, enabling CHEM attributes and CHEM implementation assessment criteria.
+
+Currently, many if not most existing CHEMs are insufficiently transparent {[}22,25--27{]}, not reusable {[}6,7{]}, nor updatable {[}31,70{]}.
+Addressing these issues will require changes to the tools, practices and funding underpinning health economic model development.
+
+As illustrated by Table \ref{tab:checktb}, we have developed a prototype software framework that can be used to implement youth mental health CHEMs that largely satisfy our TRU criteria.
+However, in its current form our software framework is too fragile to be recommended as anything more than a prototype for supporting the development needs of other modelling teams and projects.
+We developed our prototype software framework primarily to address the user requirements of one group -- ourselves.
+Factors such as user enjoyment, usability, active user-community and supporting resources influence adoption of software frameworks {[}8{]}.
+We currently lack the resources required to address these issues for our software framework.
+
+However, our prototype has a number of features that future work on CHEM software frameworks may find useful to incorporate.
+Firstly, developing a software framework to work within an existing and widely used open source programming language such as R, can keep framework scope relatively narrow.
+This makes it more tractable to develop, maintain and learn, and facilitates integration with other modelling tools written in that language (e.g., the dependency libraries we list in Table \ref{tab:cpkgs}).
+Secondly, implementation that combines both object-oriented and functional programming paradigms can avail of the modular and syntactical simplicity benefits of the former, while limiting needless bundling of code artefacts.
+Thirdly, a sensible trade-off needs to be found between transparent code implementation (which requires clear and sufficiently detailed documentation) and Agile Software Development (for which a foundational principle is prioritising the development of working code over writing documentation {[}71{]}).
+Our software framework makes this trade off by enforcing the use of consistent code style conventions and file organisation which in turn enables automated generation of simple documentation at every CHEM module update.
+All model data-structures and algorithms are therefore always documented (at least minimally, with machine authored content), meaning model developers have a requirement to write customised documentation less frequently.
+Many of the features of our prototype software framework have the potential to be significantly enhanced through integration with evolving code and documentation authoring capabilities of large language models.
+
+Our software framework provides the outline of a technical solution to some of the challenges of open source CHEM development.
+However, better tools alone are insufficient and policy and institutional changes are also required.
+Reducing waste in research is a core responsibility of research funders {[}72{]} and funding the development of CHEMs that are not adequately understood, reused or updated is wasteful.
+Existing incentive structures for health economists generally do not promote facilitating peers to reuse their work and funding is rarely adequate to maintain and routinely update a model.
+Currently, it can take ``an extraordinary amount of idealism'' to commit to authoring and maintaining research software {[}73{]}.
+Previously recommended strategies for more beneficial health economic research investments include support for harmonised ethical standards for model development {[}12{]}, methodological innovation to improve model transferability {[}74{]}, networks of modellers working on common health conditions {[}75{]}, and centralized infrastructure such as open source model repositories {[}5{]} and a standard platform for model implementations {[}22{]}.
+Development of software frameworks to support ethical CHEM implementations could enable and enhance each of these strategies.
+
+A future software framework for ethical CHEMs would ideally incorporate a base set of features useful to developers of computational models across all domains of public health and health economics, with the capability for community-led extensions that are tailored to the needs of modellers focused on specific health-conditions.
+Such approaches will likely be important to ensure a sufficient potential user-base to make CHEM software frameworks sustainable.
 
@@
 
-We have identified a number of standards that we believe are appropriate to implementing quality OSHEMs in youth mental health.
-Most of these standards are probably relevant to OSHEMs in other health conditions, though some such as the copyleft licensing may be less relevant to modellers using different tools.
-Our framework toolkits can help support standardised approaches to dynamic systems model development that are important for collaborative and interdependent projects.\\
+We have identified criteria that can be used to systematically assess the extent to which the computational implementation of health economic models adheres to transparency, reusability and updatability criteria.
+We have developed a prototype software framework that can support the implementation of CHEMs that largely meet these criteria.
+Our framework can be used as a prototype for developing future software frameworks to support ethical implementation of CHEMs.
+Barriers to ethical CHEM practice arising from resource constraints should be addressed by research funders.
 
 \hypertarget{acknowledgement}{%
-\subsection{Acknowledgement}\label{acknowledgement}}
+\subsection*{Acknowledgement}\label{acknowledgement}}
+\addcontentsline{toc}{subsection}{Acknowledgement}
 
@@
 
+The most up to date and comprehensive source of documentation on our framework and model is available at \url{https://www.ready4-dev.com} .
 Development versions of all code repositories referenced in this article are available in \url{https://github.com/ready4-dev/} .
 Archived code releases are available in \url{https://zenodo.org/communities/ready4} .
-
 All data repositories referenced in this article are available in \url{https://dataverse.harvard.edu/dataverse/ready4} .
@@
 
-Framework development did not involve human subject research and was not ethically reviewed.
-The worked example of framework application is a previously reported study that was reviewed and granted approval by the University of Melbourne's Human Research Ethics Committee, and the local Human Ethics and Advisory Group (1645367.1).
+Software framework development did not involve human subject research and was not ethically reviewed.
+The utility mapping worked example is a previously reported study that was reviewed and granted approval by the University of Melbourne's Human Research Ethics Committee, and the local Human Ethics and Advisory Group (1645367.1).
 
@@
 
-Framework development was funded by Orygen, VicHealth and Victoria University.
-The previously reported study used as a worked example was funded by the National Health and Medical Research Council (NHMRC, APP1076940), Orygen and headspace.
+Software framework development was funded by Orygen, VicHealth, Victoria University and an Australian Government Research Training Program (RTP) Scholarship.
+The utility mapping study used as a worked example was funded by the National Health and Medical Research Council (NHMRC, APP1076940), Orygen and headspace.
 
@@
 \begin{CSLReferences}{0}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-dakin2015influence}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-wagstaff2012four}{}}%
 \CSLLeftMargin{1. }%
-\CSLRightInline{Dakin H, Devlin N, Feng Y, Rice N, O'Neill P, Parkin D.
-The influence of cost-effectiveness and other factors on nice decisions.
-Health economics.
-Wiley Online Library; 2015;24: 1256--1271.
+\CSLRightInline{Wagstaff A, Culyer AJ. Four decades of health economics through a bibliometric lens. Journal of health economics. Elsevier; 2012;31: 406--439. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-python2009}{}}%
+\CSLLeftMargin{2. }%
+\CSLRightInline{Van Rossum G, Drake FL. Python 3 reference manual. Scotts Valley, CA: CreateSpace; 2009. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-RCORE2022}{}}%
+\CSLLeftMargin{3. }%
+\CSLRightInline{R Core Team.
+R: A language and environment for statistical computing {[}Internet{]}.
+Vienna, Austria: R Foundation for Statistical Computing; 2022.
+Available: \url{https://www.R-project.org/}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-incerti2019r}{}}%
+\CSLLeftMargin{4. }%
+\CSLRightInline{Incerti D, Thom H, Baio G, Jansen JP. R you still using excel? The advantages of modern software tools for health technology assessment. Value in Health. Elsevier; 2019;22: 575--579. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-Pouwels2022}{}}%
+\CSLLeftMargin{5. }%
+\CSLRightInline{Pouwels X, Sampson CJ, Arnold RJG.
+Opportunities and barriers to the development and use of open source health economic models: A survey.
+Value Health.
+2022;25: 473--479.
+doi:\href{https://doi.org/10.1016/j.jval.2021.10.001}{10.1016/j.jval.2021.10.001}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Feenstra2022}{}}%
+\CSLLeftMargin{6. }%
+\CSLRightInline{Feenstra T, Corro-Ramos I, Hamerlijnck D, Voorn G van, Ghabri S.
+Four aspects affecting health economic decision models and their validation.
+PharmacoEconomics.
+2022;40: 241--248.
+doi:\href{https://doi.org/10.1007/s40273-021-01110-w}{10.1007/s40273-021-01110-w}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Emerson2019}{}}%
+\CSLLeftMargin{7. }%
+\CSLRightInline{Emerson J, Bacon R, Kent A, Neumann PJ, Cohen JT.
+Publication of decision model source code: Attitudes of health economics authors.
+PharmacoEconomics.
+2019;37: 1409--1410.
+doi:\href{https://doi.org/10.1007/s40273-019-00796-3}{10.1007/s40273-019-00796-3}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-myllarniemi2018development}{}}%
+\CSLLeftMargin{8. }%
+\CSLRightInline{Myllärniemi V, Kujala S, Raatikainen M, Sevońn P.
+Development as a journey: Factors supporting the adoption and use of software frameworks.
+Journal of software engineering research and development.
+SpringerOpen; 2018;6: 1--22.
 }
 
+\leavevmode\vadjust pre{\hypertarget{ref-edwin2014software}{}}%
+\CSLLeftMargin{9. }%
+\CSLRightInline{Edwin NM. Software frameworks, architectural and design patterns. Journal of Software Engineering and Applications. Scientific Research Publishing; 2014;2014. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-PyTorch2019}{}}%
+\CSLLeftMargin{10. }%
+\CSLRightInline{Paszke A, Gross S, Massa F, Lerer A, Bradbury J, Chanan G, et al.
+PyTorch: An imperative style, high-performance deep learning library.
+Proceedings of the 33rd international conference on neural information processing systems.
+Red Hook, NY, USA: Curran Associates Inc.; 2019.
+}
+
+\leavevmode\vadjust pre{\hypertarget{ref-alarid2019need}{}}%
+\CSLLeftMargin{11. }%
+\CSLRightInline{Alarid-Escudero F, Krijkamp EM, Pechlivanoglou P, Jalal H, Kao S-YZ, Yang A, et al.
+A need for change!
+A coding framework for improving transparency in decision modeling.
+Pharmacoeconomics.
+Springer; 2019;37: 1329--1339.
+}
+
+\leavevmode\vadjust pre{\hypertarget{ref-10.3389ux2ffpubh.2017.00068}{}}%
+\CSLLeftMargin{12. }%
+\CSLRightInline{Boden LA, McKendrick IJ.
+Model-based policymaking: A framework to promote ethical {``good practice''} in mathematical modeling for public health policymaking.
+Frontiers in Public Health.
+2017;5.
+doi:\href{https://doi.org/10.3389/fpubh.2017.00068}{10.3389/fpubh.2017.00068}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-calder2018computational}{}}%
+\CSLLeftMargin{13. }%
+\CSLRightInline{Calder M, Craig C, Culley D, De Cani R, Donnelly CA, Douglas R, et al.
+Computational modelling for decision-making: Where, why, what, who and how.
+Royal Society open science.
+The Royal Society Publishing; 2018;5: 172096.
+}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ruparelia2010software}{}}%
+\CSLLeftMargin{14. }%
+\CSLRightInline{Ruparelia NB. Software development lifecycle models. ACM SIGSOFT Software Engineering Notes. ACM New York, NY, USA; 2010;35: 8--13. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-thompson2022escape}{}}%
+\CSLLeftMargin{15. }%
+\CSLRightInline{Thompson E. Escape from model land: How mathematical models can lead us astray and what we can do about it. New Yourk: Basic Books; 2022. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-duckett2022journey}{}}%
+\CSLLeftMargin{16. }%
+\CSLRightInline{Duckett S. A journey towards a theology of health economics and healthcare funding. Theology. SAGE Publications Sage UK: London, England; 2022;125: 326--334. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-HARVARD2020112975}{}}%
+\CSLLeftMargin{17. }%
+\CSLRightInline{Harvard S, Werker GR, Silva DS.
+Social, ethical, and other value judgments in health economics modelling.
+Social Science \& Medicine.
+2020;253: 112975.
+doi:\url{https://doi.org/10.1016/j.socscimed.2020.112975}}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Erdemir2020}{}}%
-\CSLLeftMargin{2. }%
+\CSLLeftMargin{18. }%
 \CSLRightInline{Erdemir A, Mulugeta L, Ku JP, Drach A, Horner M, Morrison TM, et al.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-thompson2019escape}{}}%
-\CSLLeftMargin{3. }%
+\CSLLeftMargin{19. }%
 \CSLRightInline{Thompson EL, Smith LA. Escape from model-land. Economics. De Gruyter Open Access; 2019;13. }
 
+\leavevmode\vadjust pre{\hypertarget{ref-carletto_zanuzzi_sammarco_russo_2020}{}}%
+\CSLLeftMargin{20. }%
+\CSLRightInline{Carletto A, Zanuzzi M, Sammarco A, Russo P.
+Quality of health economic evaluations submitted to the italian medicines agency: Current state and future actions.
+International Journal of Technology Assessment in Health Care.
+Cambridge University Press; 2020;36: 560--568.
+doi:\href{https://doi.org/10.1017/S0266462320000641}{10.1017/S0266462320000641}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-WONDER2015467}{}}%
+\CSLLeftMargin{21. }%
+\CSLRightInline{Wonder M, Dunlop S.
+Assessment of the quality of the clinical evidence in submissions to the australian pharmaceutical benefits advisory committee: Fit for purpose?
+Value in Health.
+2015;18: 467--476.
+doi:\url{https://doi.org/10.1016/j.jval.2015.02.011}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Ghabri2019}{}}%
+\CSLLeftMargin{22. }%
+\CSLRightInline{Ghabri S, Stevenson M, Möller J, Caro JJ.
+Trusting the results of model-based economic analyses: Is there a pragmatic validation solution?
+Pharmacoeconomics.
+2019;37: 1--6.
+doi:\href{https://doi.org/10.1007/s40273-018-0711-9}{10.1007/s40273-018-0711-9}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kolovos2017model}{}}%
+\CSLLeftMargin{23. }%
+\CSLRightInline{Kolovos S, Bosmans JE, Riper H, Chevreul K, Coupé VM, Tulder MW van.
+Model-based economic evaluation of treatments for depression: A systematic literature review.
+PharmacoEconomics-open.
+Springer; 2017;1: 149--165.
+}
+
+\leavevmode\vadjust pre{\hypertarget{ref-haji2013model}{}}%
+\CSLLeftMargin{24. }%
+\CSLRightInline{Haji Ali Afzali H, Gray J, Karnon J.
+Model performance evaluation (validation and calibration) in model-based studies of therapeutic interventions for cardiovascular diseases: A review and suggested reporting framework.
+Applied health economics and health policy.
+Springer; 2013;11: 85--93.
+}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Jalali2021}{}}%
-\CSLLeftMargin{4. }%
+\CSLLeftMargin{25. }%
 \CSLRightInline{Jalali MS, DiGennaro C, Guitar A, Lew K, Rahmandad H.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-McManus2019}{}}%
-\CSLLeftMargin{5. }%
+\CSLLeftMargin{26. }%
 \CSLRightInline{McManus E, Turner D, Sach T.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Bermejo2017}{}}%
-\CSLLeftMargin{6. }%
+\CSLLeftMargin{27. }%
 \CSLRightInline{Bermejo I, Tappenden P, Youn J-H.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Ghabri2019}{}}%
-\CSLLeftMargin{7. }%
-\CSLRightInline{Ghabri S, Stevenson M, Möller J, Caro JJ.
-Trusting the results of model-based economic analyses: Is there a pragmatic validation solution?
-Pharmacoeconomics.
-2019;37: 1--6.
-doi:\href{https://doi.org/10.1007/s40273-018-0711-9}{10.1007/s40273-018-0711-9}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-duckett2022journey}{}}%
-\CSLLeftMargin{8. }%
-\CSLRightInline{Duckett S. A journey towards a theology of health economics and healthcare funding. Theology. SAGE Publications Sage UK: London, England; 2022;125: 326--334. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-thompson2022escape}{}}%
-\CSLLeftMargin{9. }%
-\CSLRightInline{Thompson E. Escape from model land: How mathematical models can lead us astray and what we can do about it. New Yourk: Basic Books; 2022. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-Saltelli2019}{}}%
-\CSLLeftMargin{10. }%
-\CSLRightInline{Saltelli A.
-A short comment on statistical versus mathematical modelling.
-Nature Communications.
-2019;10: 3870.
-doi:\href{https://doi.org/10.1038/s41467-019-11865-8}{10.1038/s41467-019-11865-8}}
+\leavevmode\vadjust pre{\hypertarget{ref-Radeva2020}{}}%
+\CSLLeftMargin{28. }%
+\CSLRightInline{Radeva D, Hopkin G, Mossialos E, Borrill J, Osipenko L, Naci H.
+Assessment of technical errors and validation processes in economic models submitted by the company for NICE technology appraisals.
+International Journal of Technology Assessment in Health Care.
+2020;36: 311--316.
+doi:\href{https://doi.org/10.1017/S0266462320000422}{10.1017/S0266462320000422}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Arnold2010}{}}%
+\CSLLeftMargin{29. }%
+\CSLRightInline{Arnold RJG, Ekins S.
+Time for cooperation in health economics among the modelling community.
+PharmacoEconomics.
+2010;28: 609--613.
+doi:\href{https://doi.org/10.2165/11537580-000000000-00000}{10.2165/11537580-000000000-00000}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-garcia2021cost}{}}%
+\CSLLeftMargin{30. }%
+\CSLRightInline{Garcia-Mochon L, Rovira Forns J, Espin J.
+Cost transferability problems in economic evaluation as a framework for an european health care and social costs database.
+Cost Effectiveness and Resource Allocation.
+Springer; 2021;19: 1--12.
+}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Sampson2017}{}}%
+\CSLLeftMargin{31. }%
+\CSLRightInline{Sampson CJ, Wrightson T.
+Model registration: A call to action.
+PharmacoEconomics - Open.
+2017;1: 73--77.
+doi:\href{https://doi.org/10.1007/s41669-017-0019-2}{10.1007/s41669-017-0019-2}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Eddy2012}{}}%
-\CSLLeftMargin{11. }%
+\CSLLeftMargin{32. }%
 \CSLRightInline{Eddy DM, Hollingworth W, Caro JJ, Tsevat J, McDonald KM, Wong JB.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Feenstra2022}{}}%
-\CSLLeftMargin{12. }%
-\CSLRightInline{Feenstra T, Corro-Ramos I, Hamerlijnck D, Voorn G van, Ghabri S.
-Four aspects affecting health economic decision models and their validation.
+\leavevmode\vadjust pre{\hypertarget{ref-Zenodo2013}{}}%
+\CSLLeftMargin{33. }%
+\CSLRightInline{European Organization For Nuclear Research, OpenAIRE. Zenodo {[}Internet{]}. CERN; 2013. doi:\href{https://doi.org/10.25495/7GXK-RD71}{10.25495/7GXK-RD71}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Dataverse2007}{}}%
+\CSLLeftMargin{34. }%
+\CSLRightInline{Quantitative Social Science I for. Dataverse {[}Internet{]}. Harvard University; 2007. Available: \url{https://dataverse.org}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-techver2019}{}}%
+\CSLLeftMargin{35. }%
+\CSLRightInline{Büyükkaramikli NC, Rutten-van Mölken MPMH, Severens JL, Al M.
+TECH-VER: A verification checklist to reduce errors in models and improve their credibility.
 PharmacoEconomics.
-2022;40: 241--248.
-doi:\href{https://doi.org/10.1007/s40273-021-01110-w}{10.1007/s40273-021-01110-w}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Arnold2010}{}}%
-\CSLLeftMargin{13. }%
-\CSLRightInline{Arnold RJG, Ekins S.
-Time for cooperation in health economics among the modelling community.
-PharmacoEconomics.
-2010;28: 609--613.
-doi:\href{https://doi.org/10.2165/11537580-000000000-00000}{10.2165/11537580-000000000-00000}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-barbieri2010international}{}}%
-\CSLLeftMargin{14. }%
-\CSLRightInline{Barbieri M, Drummond M, Rutten F, Cook J, Glick HA, Lis J, et al.
-What do international pharmacoeconomic guidelines say about economic data transferability?
-Value in Health.
-Elsevier; 2010;13: 1028--1037.
-}
-
-\leavevmode\vadjust pre{\hypertarget{ref-garcia2021cost}{}}%
-\CSLLeftMargin{15. }%
-\CSLRightInline{Garcı́a-Mochón L, Rovira Forns J, Espin J.
-Cost transferability problems in economic evaluation as a framework for an european health care and social costs database.
-Cost Effectiveness and Resource Allocation.
-Springer; 2021;19: 1--12.
-}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Jenkins2021}{}}%
-\CSLLeftMargin{16. }%
-\CSLRightInline{Jenkins DA, Martin GP, Sperrin M, Riley RD, Debray TPA, Collins GS, et al.
-Continual updating and monitoring of clinical prediction models: Time for dynamic prediction systems?
-Diagnostic and Prognostic Research.
-2021;5: 1.
-doi:\href{https://doi.org/10.1186/s41512-020-00090-3}{10.1186/s41512-020-00090-3}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Sampson2017}{}}%
-\CSLLeftMargin{17. }%
-\CSLRightInline{Sampson CJ, Wrightson T.
-Model registration: A call to action.
-PharmacoEconomics - Open.
-2017;1: 73--77.
-doi:\href{https://doi.org/10.1007/s41669-017-0019-2}{10.1007/s41669-017-0019-2}}
+2019;37: 1391--1408.
+doi:\href{https://doi.org/10.1007/s40273-019-00844-y}{10.1007/s40273-019-00844-y}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ERICWONG2010188}{}}%
+\CSLLeftMargin{36. }%
+\CSLRightInline{Eric Wong W, Debroy V, Choi B.
+A family of code coverage-based heuristics for effective fault localization.
+Journal of Systems and Software.
+2010;83: 188--208.
+doi:\url{https://doi.org/10.1016/j.jss.2009.09.037}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-martin2003agile}{}}%
+\CSLLeftMargin{37. }%
+\CSLRightInline{Martin RC. Agile software development: Principles, patterns, and practices. Prentice Hall PTR; 2003. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-github2007}{}}%
+\CSLLeftMargin{38. }%
+\CSLRightInline{github. GitHub {[}Internet{]}. 2007. Available: \url{https://github.com/}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-RN39}{}}%
+\CSLLeftMargin{39. }%
+\CSLRightInline{Augustovski F, Iglesias C, Manca A, Drummond M, Rubinstein A, Marti SG.
+Barriers to generalizability of health economic evaluations in latin america and the caribbean region.
+Pharmacoeconomics.
+2009;27: 919--29.
+doi:\href{https://doi.org/10.2165/11313670-000000000-00000}{10.2165/11313670-000000000-00000}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wilson_2017}{}}%
+\CSLLeftMargin{40. }%
+\CSLRightInline{Wilson JAC Greg AND Bryan.
+Good enough practices in scientific computing.
+PLOS Computational Biology.
+Public Library of Science; 2017;13: 1--20.
+doi:\href{https://doi.org/10.1371/journal.pcbi.1005510}{10.1371/journal.pcbi.1005510}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-pan2021modular}{}}%
-\CSLLeftMargin{18. }%
+\CSLLeftMargin{41. }%
 \CSLRightInline{Pan M, Gawthrop PJ, Cursons J, Crampin EJ.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-barros2023empowering}{}}%
-\CSLLeftMargin{19. }%
-\CSLRightInline{Barros C, Luo Y, Chubaty AM, Eddy IM, Micheletti T, Boisvenue C, et al.
-Empowering ecological modellers with a PERFICT workflow: Seamlessly linking data, parameterisation, prediction, validation and visualisation.
-Methods in Ecology and Evolution.
-Wiley Online Library; 2023; }
-
-\leavevmode\vadjust pre{\hypertarget{ref-frazier2022robust}{}}%
-\CSLLeftMargin{20. }%
-\CSLRightInline{Frazier-Logue N, Wang J, Wang Z, Sodums D, Khosla A, Samson AD, et al.
-A robust modular automated neuroimaging pipeline for model inputs to TheVirtualBrain.
-Frontiers in Neuroinformatics.
-Frontiers Media SA; 2022;16: 883223.
-}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Afzali2013}{}}%
-\CSLLeftMargin{21. }%
-\CSLRightInline{Afzali HH, Karnon J, Merlin T.
-Improving the accuracy and comparability of model-based economic evaluations of health technologies for reimbursement decisions: A methodological framework for the development of reference models.
-Med Decis Making.
-2013;33: 325--32.
-doi:\href{https://doi.org/10.1177/0272989x12458160}{10.1177/0272989x12458160}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Trauer2017}{}}%
-\CSLLeftMargin{22. }%
-\CSLRightInline{Trauer JM, Ragonnet R, Doan TN, McBryde ES.
-Modular programming for tuberculosis control, the {``AuTuMN''} platform.
-BMC Infectious Diseases.
-2017;17: 546.
-doi:\href{https://doi.org/10.1186/s12879-017-2648-6}{10.1186/s12879-017-2648-6}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Urach2013}{}}%
-\CSLLeftMargin{23. }%
-\CSLRightInline{Urach C, Zauner G, Endel G, Wilbacher I, Breitenecker F.
-A modular simulation model for assessing interventions for abdominal aortic aneurysms.
-2013 winter simulations conference (WSC).
-2013.
-pp.
-66--76.
-doi:\href{https://doi.org/10.1109/WSC.2013.6721408}{10.1109/WSC.2013.6721408}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Pouwels2022}{}}%
-\CSLLeftMargin{24. }%
-\CSLRightInline{Pouwels X, Sampson CJ, Arnold RJG.
-Opportunities and barriers to the development and use of open source health economic models: A survey.
-Value Health.
-2022;25: 473--479.
-doi:\href{https://doi.org/10.1016/j.jval.2021.10.001}{10.1016/j.jval.2021.10.001}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Emerson2019}{}}%
-\CSLLeftMargin{25. }%
-\CSLRightInline{Emerson J, Bacon R, Kent A, Neumann PJ, Cohen JT.
-Publication of decision model source code: Attitudes of health economics authors.
-PharmacoEconomics.
-2019;37: 1409--1410.
-doi:\href{https://doi.org/10.1007/s40273-019-00796-3}{10.1007/s40273-019-00796-3}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Michalczyk2018}{}}%
-\CSLLeftMargin{26. }%
-\CSLRightInline{Michalczyk J, Clay E, Pochopien M, Aballea S.
-PRM123 - AN OVERVIEW OF OPEN-SOURCE MODELS IN HEALTH ECONOMICS.
-Value in Health.
-2018;21: S377.
-doi:\href{https://doi.org/10.1016/j.jval.2018.09.2243}{10.1016/j.jval.2018.09.2243}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wu2019}{}}%
-\CSLLeftMargin{27. }%
-\CSLRightInline{Wu EQ, Zhou Z-Y, Xie J, Metallo C, Thokala P.
-Transparency in health economic modeling: Options, issues and potential solutions.
-PharmacoEconomics.
-2019;37: 1349--1354.
-doi:\href{https://doi.org/10.1007/s40273-019-00842-0}{10.1007/s40273-019-00842-0}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Sampson2019}{}}%
-\CSLLeftMargin{28. }%
-\CSLRightInline{Sampson CJ, Arnold R, Bryan S, Clarke P, Ekins S, Hatswell A, et al.
-Transparency in decision modelling: What, why, who and how?
-PharmacoEconomics.
-2019;37: 1355--1369.
-doi:\href{https://doi.org/10.1007/s40273-019-00819-z}{10.1007/s40273-019-00819-z}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RN73}{}}%
-\CSLLeftMargin{29. }%
-\CSLRightInline{Long KM, Meadows GN.
-Simulation modelling in mental health: A systematic review.
-Journal of Simulation.
-2017; doi:\href{https://doi.org/10.1057/s41273-017-0062-0}{10.1057/s41273-017-0062-0}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Basu2018}{}}%
-\CSLLeftMargin{30. }%
-\CSLRightInline{Clearinghouse C. Basu, kim: Alcohol use disorder {[}Internet{]}. OSF; 2018. Available: \href{https://osf.io/jvayu}{osf.io/jvayu}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-OSMC_20xx}{}}%
-\CSLLeftMargin{31. }%
-\CSLRightInline{Evaluation of Value C for the, Health R in.
-Open-source model clearinghouse {[}Internet{]}.
-Tufts Medical Center; Available: \url{http://ghcearegistry.org/orchard/open-source-model-clearinghouse}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-IVIMDD2022}{}}%
-\CSLLeftMargin{32. }%
-\CSLRightInline{Innovation T, Initiative V. IVI-MDD value model {[}Internet{]}. 2022. Available: \url{https://www.thevalueinitiative.org/ivi-mdd-value-model/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wilson_2017}{}}%
-\CSLLeftMargin{33. }%
-\CSLRightInline{Wilson JAC Greg AND Bryan.
-Good enough practices in scientific computing.
-PLOS Computational Biology.
-Public Library of Science; 2017;13: 1--20.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1005510}{10.1371/journal.pcbi.1005510}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Alarid2019}{}}%
-\CSLLeftMargin{34. }%
-\CSLRightInline{Alarid-Escudero F, Krijkamp EM, Pechlivanoglou P, Jalal H, Kao S-YZ, Yang A, et al.
-A need for change!
-A coding framework for improving transparency in decision modeling.
-PharmacoEconomics.
-2019;37: 1329--1339.
-doi:\href{https://doi.org/10.1007/s40273-019-00837-x}{10.1007/s40273-019-00837-x}}
-
 \leavevmode\vadjust pre{\hypertarget{ref-8717448}{}}%
-\CSLLeftMargin{35. }%
+\CSLLeftMargin{42. }%
 \CSLRightInline{Hourani H, Wasmi H, Alrawashdeh T.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-7181447}{}}%
-\CSLLeftMargin{36. }%
-\CSLRightInline{Milojkovic N, Caracciolo A, Lungu MF, Nierstrasz O, Röthlisberger D, Robbes R.
-Polymorphism in the spotlight: Studying its prevalence in java and smalltalk.
-2015 IEEE 23rd international conference on program comprehension.
-2015.
-pp.
-186--195.
-doi:\href{https://doi.org/10.1109/ICPC.2015.29}{10.1109/ICPC.2015.29}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-techver2019}{}}%
-\CSLLeftMargin{37. }%
-\CSLRightInline{Büyükkaramikli NC, Rutten-van Mölken MPMH, Severens JL, Al M.
-TECH-VER: A verification checklist to reduce errors in models and improve their credibility.
-PharmacoEconomics.
-2019;37: 1391--1408.
-doi:\href{https://doi.org/10.1007/s40273-019-00844-y}{10.1007/s40273-019-00844-y}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ERICWONG2010188}{}}%
-\CSLLeftMargin{38. }%
-\CSLRightInline{Eric Wong W, Debroy V, Choi B.
-A family of code coverage-based heuristics for effective fault localization.
-Journal of Systems and Software.
-2010;83: 188--208.
-doi:\url{https://doi.org/10.1016/j.jss.2009.09.037}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Radeva2020}{}}%
-\CSLLeftMargin{39. }%
-\CSLRightInline{Radeva D, Hopkin G, Mossialos E, Borrill J, Osipenko L, Naci H.
-Assessment of technical errors and validation processes in economic models submitted by the company for NICE technology appraisals.
-International Journal of Technology Assessment in Health Care.
-2020;36: 311--316.
-doi:\href{https://doi.org/10.1017/S0266462320000422}{10.1017/S0266462320000422}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-semver20xx}{}}%
-\CSLLeftMargin{40. }%
-\CSLRightInline{Preston-Werner T. Semantic versioning 2.0.0 {[}Internet{]}. 2022. Available: \url{https://semver.org}}
+\leavevmode\vadjust pre{\hypertarget{ref-copyleft2022}{}}%
+\CSLLeftMargin{43. }%
+\CSLRightInline{Foundation TFS. What is copyleft? {[}Internet{]}. Available: \url{https://www.gnu.org/copyleft/}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Jenkins2021}{}}%
+\CSLLeftMargin{44. }%
+\CSLRightInline{Jenkins DA, Martin GP, Sperrin M, Riley RD, Debray TPA, Collins GS, et al.
+Continual updating and monitoring of clinical prediction models: Time for dynamic prediction systems?
+Diagnostic and Prognostic Research.
+2021;5: 1.
+doi:\href{https://doi.org/10.1186/s41512-020-00090-3}{10.1186/s41512-020-00090-3}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-info:doiux2f10.2196ux2f20028}{}}%
+\CSLLeftMargin{45. }%
+\CSLRightInline{Ye Y, Barapatre S, Davis MK, Elliston KO, Davatzikos C, Fedorov A, et al.
+Open-source software sustainability models: Initial white paper from the informatics technology for cancer research sustainability and industry partnership working group.
+J Med Internet Res.
+2021;23: e20028.
+doi:\href{https://doi.org/10.2196/20028}{10.2196/20028}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-MERGEL2015464}{}}%
+\CSLLeftMargin{46. }%
+\CSLRightInline{Mergel I.
+Open collaboration in the public sector: The case of social coding on GitHub.
+Government Information Quarterly.
+2015;32: 464--472.
+doi:\url{https://doi.org/10.1016/j.giq.2015.09.004}}
 
 \leavevmode\vadjust pre{\hypertarget{ref-CI2017}{}}%
-\CSLLeftMargin{41. }%
+\CSLLeftMargin{47. }%
 \CSLRightInline{Shahin M, Ali Babar M, Zhu L.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-ready4oop2022}{}}%
-\CSLLeftMargin{42. }%
-\CSLRightInline{Hamilton M.
-Apply an object-oriented paradigm to computational models of mental health systems {[}Internet{]}.
-2022.
-Available: \url{https://ready4-dev.github.io/ready4/articles/V_03.html}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-copyleft2022}{}}%
-\CSLLeftMargin{43. }%
-\CSLRightInline{Foundation TFS. What is copyleft? {[}Internet{]}. Available: \url{https://www.gnu.org/copyleft/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cc02022}{}}%
-\CSLLeftMargin{44. }%
-\CSLRightInline{Commons C. CC0 1.0 universal {[}Internet{]}. 2022. Available: \url{https://creativecommons.org/publicdomain/zero/1.0/legalcode}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bysa2022}{}}%
-\CSLLeftMargin{45. }%
-\CSLRightInline{Commons C. Attribution-ShareAlike 4.0 international {[}Internet{]}. 2022. Available: \url{https://creativecommons.org/licenses/by-sa/4.0/legalcode}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sampleterms2022}{}}%
-\CSLLeftMargin{46. }%
-\CSLRightInline{Quantitative Social Science I for. Sample data usage agreement {[}Internet{]}. 2022. Available: \url{https://support.dataverse.harvard.edu/sample-data-usage-agreement}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kearns2013}{}}%
-\CSLLeftMargin{47. }%
-\CSLRightInline{Kearns B, Ara R, Wailoo A, Manca A, Alava MH, Abrams K, et al.
-Good practice guidelines for the use of statistical regression models in economic evaluations.
-PharmacoEconomics.
-2013;31: 643--652.
-doi:\href{https://doi.org/10.1007/s40273-013-0069-y}{10.1007/s40273-013-0069-y}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ready4gh2022}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-zhou2016api}{}}%
 \CSLLeftMargin{48. }%
-\CSLRightInline{Orygen.
-ready4: A suite of authoring, modelling and prediction tools for exploring topics in young people's mental health {[}Internet{]}.
-2022.
-Available: \url{https://github.com/ready4-dev/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ready4zen2022}{}}%
+\CSLRightInline{Zhou J, Walker RJ.
+API deprecation: A retrospective analysis and detection method for code examples on the web.
+Proceedings of the 2016 24th ACM SIGSOFT international symposium on foundations of software engineering.
+2016.
+pp.
+266--277.
+}
+
+\leavevmode\vadjust pre{\hypertarget{ref-barros2023empowering}{}}%
 \CSLLeftMargin{49. }%
-\CSLRightInline{Orygen. ready4: Open and modular mental health systems models {[}Internet{]}. 2022. Available: \url{https://zenodo.org/communities/ready4}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ready4dv2022}{}}%
+\CSLRightInline{Barros C, Luo Y, Chubaty AM, Eddy IM, Micheletti T, Boisvenue C, et al.
+Empowering ecological modellers with a PERFICT workflow: Seamlessly linking data, parameterisation, prediction, validation and visualisation.
+Methods in Ecology and Evolution.
+Wiley Online Library; 2023; }
+
+\leavevmode\vadjust pre{\hypertarget{ref-10.1214ux2f13-STS452}{}}%
 \CSLLeftMargin{50. }%
-\CSLRightInline{Orygen. ready4: Open and modular mental health systems models {[}Internet{]}. 2022. Available: \url{https://dataverse.harvard.edu/dataverse/ready4)}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ready42022}{}}%
+\CSLRightInline{Chambers JM.
+{Object-Oriented Programming, Functional Programming and R}.
+Statistical Science.
+Institute of Mathematical Statistics; 2014;29: 167--180.
+doi:\href{https://doi.org/10.1214/13-STS452}{10.1214/13-STS452}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-CRAN2022}{}}%
 \CSLLeftMargin{51. }%
-\CSLRightInline{Hamilton MP.
-ready4: Implement open science computational models of mental health systems {[}Internet{]}.
-2021.
-doi:\href{https://doi.org/10.5281/zenodo.5606250}{10.5281/zenodo.5606250}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ready4class2022}{}}%
+\CSLRightInline{Statistical Computing RF for. The comprehensive r archive network {[}Internet{]}. 2022. Available: \url{https://cran.r-project.org}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-codecov_2022}{}}%
 \CSLLeftMargin{52. }%
-\CSLRightInline{Hamilton M, Wiesner G. ready4class: Author Ready4 framework modules {[}Internet{]}. 2022. doi:\href{https://doi.org/10.5281/zenodo.5640313}{10.5281/zenodo.5640313}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ready4fun2022}{}}%
+\CSLRightInline{Codecov {[}Internet{]}. Available: \url{https://about.codecov.io/}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hugo_2023}{}}%
 \CSLLeftMargin{53. }%
-\CSLRightInline{Hamilton M, Wiesner G.
-ready4fun: Author and document functions that extend the Ready4 framework {[}Internet{]}.
-2022.
-doi:\href{https://doi.org/10.5281/zenodo.5611779}{10.5281/zenodo.5611779}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ready4pack2022}{}}%
+\CSLRightInline{Hugo: The world's fastest framework for building websites {[}Internet{]}. Available: \url{https://gohugo.io}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-docsy_2023}{}}%
 \CSLLeftMargin{54. }%
-\CSLRightInline{Hamilton M. ready4pack: Author r packages that extend the Ready4 framework {[}Internet{]}. 2022. doi:\href{https://doi.org/10.5281/zenodo.5644322}{10.5281/zenodo.5644322}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ready4use2022}{}}%
+\CSLRightInline{Docsy {[}Internet{]}. Available: \url{https://www.docsy.dev}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-algoliadocsearch_2023}{}}%
 \CSLLeftMargin{55. }%
-\CSLRightInline{Hamilton M, Wiesner G. ready4use: Author, label and share Ready4 framework datasets {[}Internet{]}. 2022. doi:\href{https://doi.org/10.5281/zenodo.5644336}{10.5281/zenodo.5644336}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ready4show2022}{}}%
+\CSLRightInline{Docsearch {[}Internet{]}. Available: \url{https://docsearch.algolia.com}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-netlify_2023}{}}%
 \CSLLeftMargin{56. }%
-\CSLRightInline{Hamilton M, Wiesner G.
-ready4show: Author literate programs to share insights from applying the Ready4 framework {[}Internet{]}.
-2022.
-doi:\href{https://doi.org/10.5281/zenodo.5644568}{10.5281/zenodo.5644568}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-CRAN2022}{}}%
+\CSLRightInline{Netlify {[}Internet{]}. Available: \url{https://www.netlify.com}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Hamilton2021.07.07.21260129}{}}%
 \CSLLeftMargin{57. }%
-\CSLRightInline{Statistical Computing RF for. The comprehensive r archive network {[}Internet{]}. 2022. Available: \url{https://cran.r-project.org}}
+\CSLRightInline{Hamilton MP, Gao CX, Filia KM, Menssink JM, Sharmin S, Telford N, et al.
+Mapping psychological distress, depression and anxiety measures to AQoL-6D utility using data from a sample of young people presenting to primary mental health services.
+medRxiv.
+Cold Spring Harbor Laboratory Press; 2022; doi:\href{https://doi.org/10.1101/2021.07.07.21260129}{10.1101/2021.07.07.21260129}}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-DVNux2fDKDIB0_2021}{}}%
+\CSLLeftMargin{63. }%
+\CSLRightInline{Hamilton MP, Gao CX, Filia KM, Menssink JM, Sharmin S, Telford N, et al.
+{Transfer to AQoL-6D Utility Mapping Algorithms} {[}Internet{]}.
+Harvard Dataverse; 2021.
+doi:\href{https://doi.org/10.7910/DVN/DKDIB0}{10.7910/DVN/DKDIB0}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-DVNux2fHJXYKQ_2021}{}}%
+\CSLLeftMargin{64. }%
+\CSLRightInline{Hamilton MP.
+{Synthetic (fake) youth mental health datasets and data dictionaries} {[}Internet{]}.
+Harvard Dataverse; 2021.
+doi:\href{https://doi.org/10.7910/DVN/HJXYKQ}{10.7910/DVN/HJXYKQ}}
+
 \leavevmode\vadjust pre{\hypertarget{ref-hamilton_matthew_2022_6129906}{}}%
-\CSLLeftMargin{63. }%
+\CSLLeftMargin{65. }%
 \CSLRightInline{Hamilton M, Gao C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hamilton_matthew_2022_6416330}{}}%
-\CSLLeftMargin{64. }%
+\CSLLeftMargin{66. }%
 \CSLRightInline{Hamilton M, Gao C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hamilton_matthew_p_2022_6321821}{}}%
-\CSLLeftMargin{65. }%
+\CSLLeftMargin{67. }%
 \CSLRightInline{Hamilton MP.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hamilton_matthew_2022_6116385}{}}%
-\CSLLeftMargin{66. }%
+\CSLLeftMargin{68. }%
 \CSLRightInline{Hamilton M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-matthew_p_hamilton_2022_5976988}{}}%
-\CSLLeftMargin{67. }%
+\CSLLeftMargin{69. }%
 \CSLRightInline{Hamilton MP.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-DVNux2fDKDIB0_2021}{}}%
-\CSLLeftMargin{68. }%
-\CSLRightInline{Hamilton MP, Gao CX, Filia KM, Menssink JM, Sharmin S, Telford N, et al.
-{Transfer to AQoL-6D Utility Mapping Algorithms} {[}Internet{]}.
-Harvard Dataverse; 2021.
-doi:\href{https://doi.org/10.7910/DVN/DKDIB0}{10.7910/DVN/DKDIB0}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-DVNux2fHJXYKQ_2021}{}}%
-\CSLLeftMargin{69. }%
-\CSLRightInline{Hamilton MP.
-{Synthetic (fake) youth mental health datasets and data dictionaries} {[}Internet{]}.
-Harvard Dataverse; 2021.
-doi:\href{https://doi.org/10.7910/DVN/HJXYKQ}{10.7910/DVN/HJXYKQ}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hamilton2021.07.07.21260129}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-10.3389ux2ffpubh.2022.899874}{}}%
 \CSLLeftMargin{70. }%
-\CSLRightInline{Hamilton MP, Gao CX, Filia KM, Menssink JM, Sharmin S, Telford N, et al.
-Predicting quality adjusted life years in young people attending primary mental health services.
-medRxiv.
-Cold Spring Harbor Laboratory Press; 2021; doi:\href{https://doi.org/10.1101/2021.07.07.21260129}{10.1101/2021.07.07.21260129}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hamilton_matthew_2022_6627995}{}}%
+\CSLRightInline{Kokol P, Blažun Vošner H, Kokol M, Završnik J.
+Role of agile in digital public health transformation.
+Frontiers in Public Health.
+2022;10.
+doi:\href{https://doi.org/10.3389/fpubh.2022.899874}{10.3389/fpubh.2022.899874}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-beck2001manifesto}{}}%
 \CSLLeftMargin{71. }%
-\CSLRightInline{Hamilton M.
-{dce\_sa\_design: An R Markdown program to create the experimental design for a Discrete Choice Experiment (DCE) exploring online help seeking in socially anxious young people} {[}Internet{]}.
-Zenodo; 2022.
-doi:\href{https://doi.org/10.5281/zenodo.6627995}{10.5281/zenodo.6627995}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-DVNux2fV3OKZV_2022}{}}%
+\CSLRightInline{Beck K, Beedle M, Van Bennekum A, Cockburn A, Cunningham W, Fowler M, et al. Manifesto for agile software development. Snowbird, UT; 2001; }
+
+\leavevmode\vadjust pre{\hypertarget{ref-chalmers2014increase}{}}%
 \CSLLeftMargin{72. }%
-\CSLRightInline{Hamilton M.
-{Springtides reports for Local Government Areas in the North West of Melbourne} {[}Internet{]}.
-Harvard Dataverse; 2022.
-doi:\href{https://doi.org/10.7910/DVN/V3OKZV}{10.7910/DVN/V3OKZV}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RN33}{}}%
+\CSLRightInline{Chalmers I, Bracken MB, Djulbegovic B, Garattini S, Grant J, Gülmezoglu AM, et al.
+How to increase value and reduce waste when research priorities are set.
+The Lancet.
+Elsevier; 2014;383: 156--165.
+}
+
+\leavevmode\vadjust pre{\hypertarget{ref-anzt2020environment}{}}%
 \CSLLeftMargin{73. }%
-\CSLRightInline{Hamilton MP, Hetrick SE, Mihalopoulos C, Baker D, Browne V, Chanen AM, et al.
-Identifying attributes of care that may improve cost-effectiveness in the youth mental health service system.
-Med J Aust.
-2017;207: S27--S37.
-doi:\href{https://doi.org/10.5694/mja17.00972}{10.5694/mja17.00972}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rfwn2022}{}}%
+\CSLRightInline{Anzt H, Bach F, Druskat S, Löffler F, Loewe A, Renard BY, et al.
+An environment for sustainable research software in germany and beyond: Current state, open challenges, and call for action.
+F1000Research.
+Faculty of 1000 Ltd; 2020;9.
+}
+
+\leavevmode\vadjust pre{\hypertarget{ref-craig2018taking}{}}%
 \CSLLeftMargin{74. }%
-\CSLRightInline{Orygen. ready4-dev - documenting the development of an open souce youth mental health systems model {[}Internet{]}. Available: \url{https://ready4-dev.com/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RN8}{}}%
+\CSLRightInline{Craig P, Di Ruggiero E, Frolich KL, Mykhalovskiy E, White M, Campbell R, et al.
+Taking account of context in population health intervention research: Guidance for producers, users and funders of research.
+National Institute for Health Research; 2018; }
+
+\leavevmode\vadjust pre{\hypertarget{ref-Sampson2019}{}}%
 \CSLLeftMargin{75. }%
-\CSLRightInline{Bloom DE, Cafiero ET, Jané-Llopis E, Abrahams-Gessel S, Bloom LR, Fathima S, et al.
-The global economic burden of noncommunicable diseases.
-91-93 route de la Capite,CH-1223 Cologny/Geneva,Switzerland: World Economic Forum.; 2011.
-}
-
-\leavevmode\vadjust pre{\hypertarget{ref-GBD2019}{}}%
-\CSLLeftMargin{76. }%
-\CSLRightInline{Global, regional, and national burden of 12 mental disorders in 204 countries and territories, 1990\&\#x2013;2019: A systematic analysis for the global burden of disease study 2019.
-The Lancet Psychiatry.
-2022;9: 137--150.
-doi:\href{https://doi.org/10.1016/S2215-0366(21)00395-3}{10.1016/S2215-0366(21)00395-3}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RN25}{}}%
-\CSLLeftMargin{77. }%
-\CSLRightInline{Chisholm D, Sweeny K, Sheehan P, Rasmussen B, Smit F, Cuijpers P, et al.
-Scaling-up treatment of depression and anxiety: A global return on investment analysis.
-The Lancet Psychiatry.
-2016; doi:\href{https://doi.org/10.1016/s2215-0366(16)30024-4}{10.1016/s2215-0366(16)30024-4}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RN22}{}}%
-\CSLLeftMargin{78. }%
-\CSLRightInline{Saxena S, Thornicroft G, Knapp M, Whiteford H.
-Resources for mental health: Scarcity, inequity, and inefficiency.
-The Lancet.
-370: 878--889.
-doi:\href{https://doi.org/10.1016/S0140-6736(07)61239-2}{10.1016/S0140-6736(07)61239-2}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RN23}{}}%
-\CSLLeftMargin{79. }%
-\CSLRightInline{Whiteford H, Ferrari A, Degenhardt L.
-Global burden of disease studies: Implications for mental and substance use disorders.
-Health Affairs.
-2016;35: 1114--1120.
-doi:\href{https://doi.org/10.1377/hlthaff.2016.0082}{10.1377/hlthaff.2016.0082}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-20211700}{}}%
-\CSLLeftMargin{80. }%
-\CSLRightInline{Santomauro DF, Mantilla Herrera AM, Shadid J, Zheng P, Ashbaugh C, Pigott DM, et al.
-Global prevalence and burden of depressive and anxiety disorders in 204 countries and territories in 2020 due to the COVID-19 pandemic.
-The Lancet.
-2021;398: 1700--1712.
-doi:\url{https://doi.org/10.1016/S0140-6736(21)02143-7}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-page_howard_2010}{}}%
-\CSLLeftMargin{81. }%
-\CSLRightInline{Page LA, Howard LM.
-The impact of climate change on mental health (but will mental health be discussed at copenhagen?).
-Psychological Medicine.
-Cambridge University Press; 2010;40: 177--180.
-doi:\href{https://doi.org/10.1017/S0033291709992169}{10.1017/S0033291709992169}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RN11}{}}%
-\CSLLeftMargin{82. }%
-\CSLRightInline{Organization WH, Foundation CG. Social determinants of mental health. Geneva: World Health Organization; 2014. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-Fried2020}{}}%
-\CSLLeftMargin{83. }%
-\CSLRightInline{Fried EI, Robinaugh DJ.
-Systems all the way down: Embracing complexity in mental health research.
-BMC Medicine.
-2020;18: 205.
-doi:\href{https://doi.org/10.1186/s12916-020-01668-w}{10.1186/s12916-020-01668-w}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RN2111}{}}%
-\CSLLeftMargin{84. }%
-\CSLRightInline{Langellier BA, Yang Y, Purtle J, Nelson KL, Stankov I, Diez Roux AV.
-Complex systems approaches to understand drivers of mental health and inform mental health policy: A systematic review.
-Administration And Policy In Mental Health.
-2018; doi:\href{https://doi.org/10.1007/s10488-018-0887-5}{10.1007/s10488-018-0887-5}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RN26}{}}%
-\CSLLeftMargin{85. }%
-\CSLRightInline{Jorm AF, Patten SB, Brugha TS, Mojtabai R.
-Has increased provision of treatment reduced the prevalence of common mental disorders?
-Review of the evidence from four countries.
-World psychiatry : official journal of the World Psychiatric Association (WPA).
-2017;16: 90--99.
-doi:\href{https://doi.org/10.1002/wps.20388}{10.1002/wps.20388}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RN42}{}}%
-\CSLLeftMargin{86. }%
-\CSLRightInline{Furst MA, Gandré C, Romero López-Alberca C, Salvador-Carulla L.
-Healthcare ecosystems research in mental health: A scoping review of methods to describe the context of local care delivery.
-BMC Health Services Research.
-2019;19: 173.
-doi:\href{https://doi.org/10.1186/s12913-019-4005-5}{10.1186/s12913-019-4005-5}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RN43}{}}%
-\CSLLeftMargin{87. }%
-\CSLRightInline{Alegría M, NeMoyer A, Falgàs Bagué I, Wang Y, Alvarez K.
-Social determinants of mental health: Where we are and where we need to go.
-Current Psychiatry Reports.
-2018;20: 95--95.
-doi:\href{https://doi.org/10.1007/s11920-018-0969-9}{10.1007/s11920-018-0969-9}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-nmhsmn2022}{}}%
-\CSLLeftMargin{88. }%
-\CSLRightInline{Mental Health Research QC for.
-National mental health systems modelling network {[}Internet{]}.
-2022.
-Available: \url{https://qcmhr.org/research/research-streams/mental-health-services-research/national-mental-health-systems-modelling-network/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Zabell2021}{}}%
-\CSLLeftMargin{89. }%
-\CSLRightInline{Zabell T, Long KM, Scott D, Hope J, McLoughlin I, Enticott J.
-Engaging healthcare staff and stakeholders in healthcare simulation modeling to better translate research into health impact: A systematic review.
-Frontiers in Health Services.
-2021;1.
-doi:\href{https://doi.org/10.3389/frhs.2021.644831}{10.3389/frhs.2021.644831}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-SQUIRES2016588}{}}%
-\CSLLeftMargin{90. }%
-\CSLRightInline{Squires H, Chilcott J, Akehurst R, Burr J, Kelly MP.
-A framework for developing the structure of public health economic models.
-Value in Health.
-2016;19: 588--601.
-doi:\url{https://doi.org/10.1016/j.jval.2016.02.011}}
+\CSLRightInline{Sampson CJ, Arnold R, Bryan S, Clarke P, Ekins S, Hatswell A, et al.
+Transparency in decision modelling: What, why, who and how?
+PharmacoEconomics.
+2019;37: 1355--1369.
+doi:\href{https://doi.org/10.1007/s40273-019-00819-z}{10.1007/s40273-019-00819-z}}
 

### 2023-10-22 Reports/Manuscript/Submission.tex
problems with table and figure placement

--- 2023-10-22 Reports/Manuscript/Manuscript.tex
@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
+%Version 2.1 April 2023
+% See section 11 of the User Manual for version history
 %
-\documentclass[
-]{article}
-\usepackage{amsmath,amssymb}
-\usepackage{iftex}
-\ifPDFTeX
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math} % this also loads fontspec
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-\usepackage{lmodern}
-\ifPDFTeX\else
-  % xetex/luatex font selection
-\fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
-\usepackage{xcolor}
-\usepackage[margin=1in]{geometry}
-\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
-\usepackage{graphicx}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{5}
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
-  \fi
-  % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                                 %%
+%% Please do not use \input{...} to include other tex files.       %%
+%% Submit your LaTeX manuscript as one .tex document.              %%
+%%                                                                 %%
+%% All additional figures and files should be attached             %%
+%% separately and not embedded in the \TeX\ document itself.       %%
+%%                                                                 %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\documentclass[sn-vancouver,Numbered,pdflatex]{sn-jnl}
+
+%%%% Standard Packages
+%%<additional latex packages if required can be included here>
+
+\usepackage{graphicx}%
+\usepackage{multirow}%
+\usepackage{amsmath,amssymb,amsfonts}%
+\usepackage{amsthm}%
+\usepackage{mathrsfs}%
+\usepackage[title]{appendix}%
+\usepackage{xcolor}%
+\usepackage{textcomp}%
+\usepackage{manyfoot}%
+\usepackage{booktabs}%
+\usepackage{algorithm}%
+\usepackage{algorithmicx}%
+\usepackage{algpseudocode}%
+\usepackage{listings}%
+%%%%
+
+%%%%%=============================================================================%%%%
+%%%%  Remarks: This template is provided to aid authors with the preparation
+%%%%  of original research articles intended for submission to journals published
+%%%%  by Springer Nature. The guidance has been prepared in partnership with
+%%%%  production teams to conform to Springer Nature technical requirements.
+%%%%  Editorial and presentation requirements differ among journal portfolios and
+%%%%  research disciplines. You may find sections in this template are irrelevant
+%%%%  to your work and are empowered to omit any such section if allowed by the
+%%%%  journal you intend to submit to. The submission guidelines and policies
+%%%%  of the journal take precedence. A detailed User Manual is available in the
+%%%%  template package for technical guidance.
+%%%%%=============================================================================%%%%
+
+%% Per the spinger doc, new theorem styles can be included using built in style, 
+%% but it seems the don't work so commented below
+%\theoremstyle{thmstyleone}%
+\newtheorem{theorem}{Theorem}%  meant for continuous numbers
+%%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
+%% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
+\newtheorem{proposition}[theorem]{Proposition}%
+%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.
+
+%% \theoremstyle{thmstyletwo}%
+\theoremstyle{remark}
+\newtheorem{example}{Example}%
+\newtheorem{remark}{Remark}%
+
+%% \theoremstyle{thmstylethree}%
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}%
+
 \usepackage{float}
@@
 \usepackage{multirow}
-\usepackage{multirow}
-\usepackage{multicol}
-\usepackage{colortbl}
-\usepackage{hhline}
-\newlength\Oldarrayrulewidth
-\newlength\Oldtabcolsep
 \usepackage{longtable}
 \usepackage{array}
-\usepackage{hyperref}
-\usepackage{float}
 \usepackage{wrapfig}
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same}
-\hypersetup{
-  pdftitle={A prototype software framework for transparent, reusable and updatable computational health economic models},
-  pdfauthor={Matthew P Hamilton1,2,; Caroline X Gao2,3,1; Glen Wiesner4; Kate M Filia2,3; Jana M Menssink2,3; Petra Plencnerova5; David Baker2,3; Patrick D McGorry2,3; Alexandra Parker6,3; Jonathan Karnon7; Sue M Cotton2,3; Cathrine Mihalopoulos1},
-  pdfkeywords={computational models, ethics of modelling, health economics, mental disorders, open-source models, software frameworks},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
+\usepackage{colortbl}
+\usepackage{booktabs} 
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage[normalem]{ulem}
+\usepackage{threeparttablex}
+\usepackage{makecell}
 
-\title{A prototype software framework for transparent, reusable and updatable computational health economic models}
-\author{Matthew P Hamilton\textsuperscript{1,2,*} \and Caroline X Gao\textsuperscript{2,3,1} \and Glen Wiesner\textsuperscript{4} \and Kate M Filia\textsuperscript{2,3} \and Jana M Menssink\textsuperscript{2,3} \and Petra Plencnerova\textsuperscript{5} \and David Baker\textsuperscript{2,3} \and Patrick D McGorry\textsuperscript{2,3} \and Alexandra Parker\textsuperscript{6,3} \and Jonathan Karnon\textsuperscript{7} \and Sue M Cotton\textsuperscript{2,3} \and Cathrine Mihalopoulos\textsuperscript{1}}
-\date{}
+\raggedbottom
+
+% tightlist command for lists without linebreak
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
+% From pandoc table feature
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
 
 \begin{document}
-\maketitle
-\begin{abstract}
-\textbf{Summary: } Most health economic analyses are undertaken with the aid of computers.
+
+\title[Transparent, reusable and updatable computational models]{A prototype software framework for transparent, reusable and updatable computational health economic models}
+
+%%=============================================================%%
+%% Prefix	-> \pfx{Dr}
+%% GivenName	-> \fnm{Joergen W.}
+%% Particle	-> \spfx{van der} -> surname prefix
+%% FamilyName	-> \sur{Ploeg}
+%% Suffix	-> \sfx{IV}
+%% NatureName	-> \tanm{Poet Laureate} -> Title after name
+%% Degrees	-> \dgr{MSc, PhD}
+%% \author*[1,2]{\pfx{Dr} \fnm{Joergen W.} \spfx{van der} \sur{Ploeg} \sfx{IV} \tanm{Poet Laureate}
+%%                 \dgr{MSc, PhD}}\email{iauthor@gmail.com}
+%%=============================================================%%
+
+\author*[1,2]{\pfx{Dr.} \fnm{Leading} \spfx{van} \sur{Author} \sfx{III} \tanm{Poet Laureate} \dgr{MSc, PhD}}\email{\href{mailto:abc@def}{\nolinkurl{abc@def}}}
+
+\author[2]{\fnm{Second} \sur{Author} }
+
+  \affil*[1]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\city{City}, \country{Country}, \postcode{100190}, \state{State}, \street{Street}}}
+  \affil*[2]{\orgname{Other Organisation}}
+
+\abstract{\textbf{Summary: } Most health economic analyses are undertaken with the aid of computers.
 However, the ethical dimensions of implementing health economic models as software (or computational health economic models (CHEMs)) are poorly understood.
@@
 \newline \newline \textbf{Code: } Visit \url{https://www.ready4-dev.com} for more information about how to find, install and apply the prototype software framework and CHEMs developed with it.
-\newline \newline
-\end{abstract}
+\newline \newline}
 
-\textsuperscript{1} School of Public Health and Preventive Medicine, Monash University, Clayton, Australia\\
-\textsuperscript{2} Orygen, Parkville, Australia\\
-\textsuperscript{3} Centre for Youth Mental Health; The University of Melbourne, Parkville, Australia\\
-\textsuperscript{4} Heart Foundation, Melbourne, Australia\\
-\textsuperscript{5} headspace National Youth Mental Health Foundation, Melbourne, Australia\\
-\textsuperscript{6} Institute for Health and Sport, Victoria University, Footscray, Australia\\
-\textsuperscript{7} Flinders University, Adelaide, Australia
+\keywords{key, dictionary, word}
 
-\textsuperscript{*} Correspondence: \href{mailto:matthew.hamilton1@monash.edu}{Matthew P Hamilton \textless{}\href{mailto:matthew.hamilton1@monash.edu}{\nolinkurl{matthew.hamilton1@monash.edu}}\textgreater{}}
+\pacs[JEL Classification]{D8, H51}
+\pacs[MSC Classification]{35A01, 65L10}
+
+\maketitle
 
@@
 
-Health economics is a discipline concerned with problems that arise due to scarce resources, such as how to value health and healthcare, allocate healthcare budgets and configure health services {[}1{]}.
+Health economics is a discipline concerned with problems that arise due to scarce resources, such as how to value health and healthcare, allocate healthcare budgets and configure health services \citep{wagstaff2012four}.
 In seeking to solve these problems, health economists typically use models which are simplified and selective representations of systems that are believed to influence human health.
@@
 The set of software files implementing a health economic model's structure, data and algorithms can be called a computational health economic model (CHEM).
-CHEMs can be developed using commercial modelling software or open-source programming languages such as Python {[}2{]} or R {[}3{]}.
+CHEMs can be developed using commercial modelling software or open-source programming languages such as Python \citep{python2009} or R \citep{RCORE2022}.
 An advantage of commercial modelling software is that users often require limited or no programming skills to develop and apply CHEMs.
-However, open-source software programming languages may facilitate the development of CHEMs that are more transparent, reusable and updatable {[}4,5{]}.
+However, open-source software programming languages may facilitate the development of CHEMs that are more transparent, reusable and updatable \citep{incerti2019r, Pouwels2022}.
 The decision about what type of software development platform to use must balance ethical considerations and resource constraints (see Table \ref{tab:proscons}).
 
-\begin{table}
-
-\caption{\label{tab:proscons}Implications of choosing commercial modelling software or an open-source programming language for the computational implementation of health economic models}
-\centering
-\begin{tabular}[t]{>{\raggedright\arraybackslash}p{7em}>{\raggedright\arraybackslash}p{20em}>{\raggedright\arraybackslash}p{20em}}
-\toprule
-Implications & Commercial modelling software & Open-source programming language\\
-\midrule
- & (+) Will include tools to efficienty accomplish many common modelling tasks. & (-) Initial development is likely to be time and resource intensive.\\
-
- & (+) Requires limited or no programming skills. & (+) Over medium term, efficiency savings are possible if:\\
-
- & (-) Requires model developers and users to purchase software licenses & (i)  artefacts (code and data) from pre-existing models are leveraged; and / or\\
-
-\multirow{-4}{7em}{\raggedright\arraybackslash \textbf{Resources}} &  & (ii)    maintaining and transferring (e.g. to new decision problems / contexts) model.\\
-\cmidrule{1-3}
-\addlinespace[0.3em]
-\multicolumn{3}{c}{\textbf{Transparency}}\\
-\hspace{1em} & (+) Popular tools (e.g. Excel) are readily understood by many. & (+) Easy to publicly share testable source code while selectively restricting access to confidential data.\\
-
-\hspace{1em} & (-) Non seemless integration with scientific manuscript authoring pipelines raises risk of (undetected) transcription errors when reporting results.
-& (+) Easy to make clear who has developed and tested each part.\\
-
-\hspace{1em} &  & (-) Novel code increases likelihood of (undetected) software errors.\\
-
-\addlinespace[0.3em]
-\multicolumn{3}{c}{\textbf{Reusability}}\\
-\hspace{1em} & (+) Files will open and execute correctly for years after project is completed.
-& (-) Potentially fragile – if not maintained / not bundled with all required and correctly versioned dependencies\\
-
-\hspace{1em} &  & (+) Facilitates modular implementations that make complex model representations more tractable.\\
-
-\hspace{1em} &  & (+) Facilitates customised integration with existing data / decision systems.\\
-
-\addlinespace[0.3em]
-\multicolumn{3}{c}{\textbf{Updatability}}\\
-\hspace{1em}\multirow{-7}{7em}{\raggedright\arraybackslash \textbf{Ethical}} & (-) Selective modification with appropriate attribution can be difficult.
-& (-) Facilitates collaborative development and maintenance.\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-Open-source CHEMs remain rare {[}6,7{]}.
-The software used to develop CHEMs was identified as a barrier to open-source model implementations by participants in a 2020 survey of health economists {[}5{]}.
-Other reported barriers relate to difficulties in generalising models, updating models and transferring model data, concerns about the level of public access and lack of interest from decision-makers, and legal, confidentiality and security considerations {[}5{]}.
+Open-source CHEMs remain rare \citep{Feenstra2022, Emerson2019}.
+The software used to develop CHEMs was identified as a barrier to open-source model implementations by participants in a 2020 survey of health economists \citep{Pouwels2022}.
+Other reported barriers relate to difficulties in generalising models, updating models and transferring model data, concerns about the level of public access and lack of interest from decision-makers, and legal, confidentiality and security considerations \citep{Pouwels2022}.
 
 Better software frameworks could potentially help address some of the barriers to open-source CHEM development.
-A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users {[}8{]}.
+A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users \citep{myllarniemi2018development}.
 A software framework provides a foundation for developing multiple software applications with shared resources (e.g., code and data files), that can be modified to suit specific needs.
-Advantages of using software frameworks include facilitating code reuse and extension, promoting good programming practice and the capability to provide enhanced functionality and performance without additional effort by developers {[}9{]}.
-Software frameworks have widely been developed and implemented in data science, for example, PyTorch {[}10{]} for machine learning using Python.
+Advantages of using software frameworks include facilitating code reuse and extension, promoting good programming practice and the capability to provide enhanced functionality and performance without additional effort by developers \citep{edwin2014software}.
+Software frameworks have widely been developed and implemented in data science, for example, PyTorch \citep{PyTorch2019} for machine learning using Python.
 
-A high-level software framework for implementing open-source CHEMs in R has previously been developed with the primary aim of improving model transparency {[}11{]}.
+A high-level software framework for implementing open-source CHEMs in R has previously been developed with the primary aim of improving model transparency \citep{alarid2019need}.
 However, to gain widespread adoption, a software framework for CHEMs may need to provide tools to help model developers meet a broader range of ethical practice requirements.
 There are multiple challenges to overcome.
-Firstly, the ethical responsibilities of public health computational modellers remain poorly understood {[}12{]} and the computational modelling landscape is changing fast {[}13{]}.
-Secondly, software frameworks can be challenging and time consuming to create and may become excessively complex over time {[}9{]}.
-Thirdly, software frameworks can be difficult to learn, often requiring model developers to undergo specialist training {[}8{]}.
+Firstly, the ethical responsibilities of public health computational modellers remain poorly understood \citep{10.3389/fpubh.2017.00068} and the computational modelling landscape is changing fast \citep{calder2018computational}.
+Secondly, software frameworks can be challenging and time consuming to create and may become excessively complex over time \citep{edwin2014software}.
+Thirdly, software frameworks can be difficult to learn, often requiring model developers to undergo specialist training \citep{myllarniemi2018development}.
 
@@
 
-Boden and McKendrick {[}12{]} propose a framework for ethical public health modelling based on the criteria of independence (concerning how modeller subjectivity shapes model design), beneficence / non-maleficence (concerning model quality and utility), transparency (concerning the need for policymakers to reliably evaluate model strengths and weaknesses) and justice (concerning the social obligations of modellers to consider and communicate ethical issues about model use).
+Boden and McKendrick \citep{10.3389/fpubh.2017.00068} propose a framework for ethical public health modelling based on the criteria of independence (concerning how modeller subjectivity shapes model design), beneficence / non-maleficence (concerning model quality and utility), transparency (concerning the need for policymakers to reliably evaluate model strengths and weaknesses) and justice (concerning the social obligations of modellers to consider and communicate ethical issues about model use).
 However, these criteria are not specific to the computational model, but are designed to apply to a modelling project as a whole, including a model's conceptual and mathematical representations.
@@
 To identify ethical issues that are specific to CHEMs, we first considered the distinct phases in a software development project.
-Software development lifecycle (SDLC) models take different approaches to the inclusion, naming, definition, sequencing and iteration of project phases {[}14{]}.
+Software development lifecycle (SDLC) models take different approaches to the inclusion, naming, definition, sequencing and iteration of project phases \citep{ruparelia2010software}.
 However, SDLC models typically have components that can principally map to the concepts of \emph{planning} (e.g., identification of system / user requirements and design specifications), \emph{implementation} (e.g., development and testing) and \emph{release} (e.g., deployment, system integration, maintenance and support).
@@
 
-Misalignment between the values of computational model developers and those of the population groups affected by decisions based on their models presents significant ethical risks {[}15,16{]}.
-The value judgments of health economic modellers are rarely adequately specified, omissions that may lead to socially unacceptable policy recommendations {[}16{]}.
-These value judgments influence the assumptions, selection of model features and standards for evidence that shape health economic model projects {[}17{]}.
+Misalignment between the values of computational model developers and those of the population groups affected by decisions based on their models presents significant ethical risks \citep{thompson2022escape, duckett2022journey}.
+The value judgments of health economic modellers are rarely adequately specified, omissions that may lead to socially unacceptable policy recommendations \citep{duckett2022journey}.
+These value judgments influence the assumptions, selection of model features and standards for evidence that shape health economic model projects \citep{HARVARD2020112975}.
 For example, as illustrated in Table \ref{tab:proscons}, project resource constraints may require model developers to make trade-offs when agreeing CHEM \textbf{user requirements and design specifications}.
@@
 
-Modellers have duties both to ensure a computational model is \textbf{fit for purpose} and to provide potential third-party users with the means of assessing its adequacy for their proposed uses {[}6,12,18,19{]}.
-However, it is common for health economic models to have serious methodological flaws {[}20,21{]}; insufficient validation {[}22--24{]}, poor reproducibility {[}25--27{]}; and undeclared errors {[}28{]}.
+Modellers have duties both to ensure a computational model is \textbf{fit for purpose} and to provide potential third-party users with the means of assessing its adequacy for their proposed uses \citep{Erdemir2020, Feenstra2022, thompson2019escape, 10.3389/fpubh.2017.00068}.
+However, it is common for health economic models to have serious methodological flaws \citep{carletto_zanuzzi_sammarco_russo_2020, WONDER2015467}; insufficient validation \citep{Ghabri2019, kolovos2017model, haji2013model}, poor reproducibility \citep{Jalali2021, McManus2019, Bermejo2017}; and undeclared errors \citep{Radeva2020}.
 Appropriate computational implementation choices can help address many of these shortcomings, for example by automating quality assurance checks and facilitating manual reviews by third parties.
@@
 A CHEM will have limited \textbf{social benefit} if it is rarely used, if mis-used or when its acceptability and adequacy rapidly decay.
-Reuse of CHEMs as components of other models can potentially make model development more efficient {[}29,30{]}.
-However, health economic models face challenges related to transferability across jurisdictions {[}30{]} that create barriers to reuse.
-Without ongoing maintenance, a CHEM risks becoming less reliable with time {[}30{]} and is at risk of being deployed for purposes for which it is poorly suited {[}13{]}.
-Currently, health economic models are rarely implemented computationally in a manner that facilitates routine updates {[}31{]}, thus limiting the temporal window within which a CHEM can be validly applied.
+Reuse of CHEMs as components of other models can potentially make model development more efficient \citep{Arnold2010, garcia2021cost}.
+However, health economic models face challenges related to transferability across jurisdictions \citep{garcia2021cost} that create barriers to reuse.
+Without ongoing maintenance, a CHEM risks becoming less reliable with time \citep{garcia2021cost} and is at risk of being deployed for purposes for which it is poorly suited \citep{calder2018computational}.
+Currently, health economic models are rarely implemented computationally in a manner that facilitates routine updates \citep{Sampson2017}, thus limiting the temporal window within which a CHEM can be validly applied.
 
@@
 
-\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
-
-\global\setlength{\Oldtabcolsep}{\tabcolsep}
-
-\setlength{\tabcolsep}{0pt}
-
-\renewcommand*{\arraystretch}{1.5}
-
-\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\begin{longtable}[c]{|p{1.20in}|p{1.60in}|p{1.60in}|p{1.60in}}
-
-\caption{Transparent,\ reusable\ and\ updatable\ (TRU)\ computational\ health\ economic\ models\ (CHEMs)\ are\ suggestive\ of\ ethical\ modelling\ practice}\label{tab:timelygls}\\
-
-\ascline{1pt}{666666}{1-4}
-
-\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{\ }}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1pt}>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{Social\ acceptability}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1pt}>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{Fitness\ for\ purpose}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1pt}>{\centering}m{\dimexpr 1.6in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{Beneficial\ use}}}} \\
-
-\ascline{1pt}{666666}{1-4}\endfirsthead \caption[]{Transparent,\ reusable\ and\ updatable\ (TRU)\ computational\ health\ economic\ models\ (CHEMs)\ are\ suggestive\ of\ ethical\ modelling\ practice}\label{tab:timelygls}\\
-
-\ascline{1pt}{666666}{1-4}
-
-\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{\ }}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1pt}>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{Social\ acceptability}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1pt}>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{Fitness\ for\ purpose}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1pt}>{\centering}m{\dimexpr 1.6in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{Beneficial\ use}}}} \\
-
-\ascline{1pt}{666666}{1-4}\endhead
-
-\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{Transparent}}}} & \multicolumn{2}{!{\color[HTML]{000000}\vrule width 1pt}>{\centering}p{\dimexpr 3.2in+2\tabcolsep+1pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Modeller\ judgments,\ model\ features\ and\ verification\ checks\ can\ be\ reviewed\ by\ third\ parties.}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1pt}>{\centering}m{\dimexpr 1.6in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Decision-makers\ can\ understand\ the\ strengths\ and\ weakness\ of\ models\ before\ applying\ them.}}} \\
-
-\ascline{1pt}{000000}{1-4}
-
-\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{Reusable}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1pt}>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Third\ party\ use\ increases\ likelihood\ of\ errors\ being\ identified.}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1pt}>{\centering}m{\dimexpr 1.6in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Can\ inform\ more\ decision\ problems,\ in\ more\ contexts\ with\ less\ duplicative\ effort.}}} \\
-
-\ascline{1pt}{000000}{1-1}\ascline{1pt}{000000}{3-4}
-
-\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{Updatable}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep}}{\multirow[t]{-2}{*}{\parbox{1.6in}{\centering \textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Models\ can\ be\ modified\ to\ reflect\ alternative\ value\ judgments.}}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1pt}>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Models\ that\ are\ maintained\ can\ be\ validly\ used\ for\ longer.}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1pt}>{\centering}m{\dimexpr 1.6in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Models\ can\ be\ validly\ used\ for\ longer.}}} \\
-
-\ascline{1pt}{666666}{1-4}
-
-\end{longtable}
-
-\arrayrulecolor[HTML]{000000}
-
-\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
-
-\global\setlength{\tabcolsep}{\Oldtabcolsep}
-
-\renewcommand*{\arraystretch}{1}
-
-Taking steps to make computational models \textbf{transparent} is an important part of ethical public health modelling practice {[}12{]}.
-Guidance on transparency in health economic modelling recommend that model code and data should be clearly documented {[}32{]}.
+Taking steps to make computational models \textbf{transparent} is an important part of ethical public health modelling practice \citep{10.3389/fpubh.2017.00068}.
+Guidance on transparency in health economic modelling recommend that model code and data should be clearly documented \citep{Eddy2012}.
 Notably, the same guidelines, published over ten years ago, do not recommend sharing model code and data.
-However, more recent healthcare modelling guidance does recommend public dissemination of such artefacts {[}18{]}.
-Online repository services such as Zenodo {[}33{]} and Dataverse {[}34{]} provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each code and data collection.
-Ensuring that calculations are correct and consistent with model specifications is an essential part of CHEM quality assurance {[}35{]}.
-The extensiveness of such verification checks can be reported using the concept of code coverage {[}36{]} - the proportion of model code that has been explicitly tested.
-Tests should ideally combine both unit tests (to verify that small, isolated sections of code produce the correct output when run independently) and acceptance tests (to verify that the correct output is produced when multiple code components are run together to perform tasks that meet core user-requirements {[}37{]}).
-The nature and extent of individual model authorship contributions can become unclear when models are implemented over longer time-frames with a large and changing group of collaborators {[}15{]}.
-This issue can be addressed by use of online repository services such as GitHub {[}38{]}, that provide citation tools and can transparently record all individual code contributions to a modelling project over its lifecycle.
+However, more recent healthcare modelling guidance does recommend public dissemination of such artefacts \citep{Erdemir2020}.
+Online repository services such as Zenodo \citep{Zenodo2013} and Dataverse \citep{Dataverse2007} provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each code and data collection.
+Ensuring that calculations are correct and consistent with model specifications is an essential part of CHEM quality assurance \citep{techver2019}.
+The extensiveness of such verification checks can be reported using the concept of code coverage \citep{ERICWONG2010188} - the proportion of model code that has been explicitly tested.
+Tests should ideally combine both unit tests (to verify that small, isolated sections of code produce the correct output when run independently) and acceptance tests (to verify that the correct output is produced when multiple code components are run together to perform tasks that meet core user-requirements \citep{martin2003agile}).
+The nature and extent of individual model authorship contributions can become unclear when models are implemented over longer time-frames with a large and changing group of collaborators \citep{thompson2022escape}.
+This issue can be addressed by use of online repository services such as GitHub \citep{github2007}, that provide citation tools and can transparently record all individual code contributions to a modelling project over its lifecycle.
 
@@
 Although making a CHEM's code, data and documentation publicly available is increasingly considered good practice, it is insufficient to enable model re-use.
-Key concerns for health economists when considering whether to reuse a model are generalisability (application without adaptation) and transferability (selective reuse and/or modification of model components) {[}39{]}.
-Writing model algorithms as collections of functions (short, self-contained and reusable software routines that each perform a discrete task) is good scientific computing practice {[}40{]} and promotes selective reuse.
+Key concerns for health economists when considering whether to reuse a model are generalisability (application without adaptation) and transferability (selective reuse and/or modification of model components) \citep{RN39}.
+Writing model algorithms as collections of functions (short, self-contained and reusable software routines that each perform a discrete task) is good scientific computing practice \citep{Wilson_2017} and promotes selective reuse.
 Computational implementations that store model code and data in distinct files and locations (as opposed to embedding data such as parameter values into source code) are easier to selectively modify.
-Modular implementations enable models to be constructed from multiple independently reusable and replaceable sub-models (modules) {[}41{]}.
-The programming concept inheritance {[}42{]}, deployed in object-oriented programming approaches, can facilitate the duplication and selective modification of models.
+Modular implementations enable models to be constructed from multiple independently reusable and replaceable sub-models (modules) \citep{pan2021modular}.
+The programming concept inheritance \citep{8717448}, deployed in object-oriented programming approaches, can facilitate the duplication and selective modification of models.
 Granting permissions to others to use, test and adapt models and their components, can be facilitated by two broad categories of open source licenses.
-Some guidance strongly recommends the use of permissive licensing {[}40{]} that provides users with great flexibility as to the purposes (including commercial) for which content can be re-used.
-Alternatively, copyleft licenses {[}43{]} can be used to require that derivative works created by content users remain open-source.
+Some guidance strongly recommends the use of permissive licensing \citep{Wilson_2017} that provides users with great flexibility as to the purposes (including commercial) for which content can be re-used.
+Alternatively, copyleft licenses \citep{copyleft2022} can be used to require that derivative works created by content users remain open-source.
 
-Models should be \textbf{updatable} so that they remain valid for longer, evolving as new evidence emerges and the systems being modelled change {[}30,44{]}.
-Ensuring that a model is regularly reviewed to identify and implement required improvements is a recommended defence against model validity decay {[}13{]}.
-Sustainable maintenance of open source research software requires both a core development team and an active user community {[}45{]}.
+Models should be \textbf{updatable} so that they remain valid for longer, evolving as new evidence emerges and the systems being modelled change \citep{Jenkins2021, garcia2021cost}.
+Ensuring that a model is regularly reviewed to identify and implement required improvements is a recommended defence against model validity decay \citep{calder2018computational}.
+Sustainable maintenance of open source research software requires both a core development team and an active user community \citep{info:doi/10.2196/20028}.
 Online communities can be an efficient means of engaging model users in testing each version of a model, identifying issues and suggesting improvements.
-Services such as GitHub {[}38{]} provide collaborative code development tools {[}46{]} that help elicit, integrate and reconcile contributions from multiple contributors and to ensure each update is uniquely identifiable and retrievable.
-It is also important that verification checks are rerun with each model update, a task that can be automated using the software development practice of continuous integration {[}47{]}.
-The risk of software revisions having unintended consequences for third party users can be mitigated through the use of deprecation conventions {[}48{]} that take an informative and staged approach to retiring outdated CHEMs.
+Services such as GitHub \citep{github2007} provide collaborative code development tools \citep{MERGEL2015464} that help elicit, integrate and reconcile contributions from multiple contributors and to ensure each update is uniquely identifiable and retrievable.
+It is also important that verification checks are rerun with each model update, a task that can be automated using the software development practice of continuous integration \citep{CI2017}.
+The risk of software revisions having unintended consequences for third party users can be mitigated through the use of deprecation conventions \citep{zhou2016api} that take an informative and staged approach to retiring outdated CHEMs.
 
@@
 
-To achieve these goals, we have implemented the software framework as R {[}3{]} code libraries that integrate with a number of online services and which are supported by a documentation website.
+To achieve these goals, we have implemented the software framework as R \citep{RCORE2022} code libraries that integrate with a number of online services and which are supported by a documentation website.
 
@@
 One framework library provides a \textbf{foundation for modular CHEM implementations}.
-In modular model implementations, modules need to be able to share inputs and outputs with each other and to be run as independent models {[}49{]}.
+In modular model implementations, modules need to be able to share inputs and outputs with each other and to be run as independent models \citep{barros2023empowering}.
 To achieve this, the foundation framework library defines a template CHEM module (using R's S4 class system), which can be used to create other CHEM modules with a common set of inherited properties.
@@
 Three framework libraries are designed to help streamline and standardise workflows for \textbf{authoring CHEM modules} from the template module.
-The R language supports functional and object-oriented programming paradigms {[}50{]}.
+The R language supports functional and object-oriented programming paradigms \citep{10.1214/13-STS452}.
 Authoring with each of these paradigms is facilitated by a dedicated CHEM module authoring library.
@@
 
-\begin{table}
-
-\caption{\label{tab:cpkgs}Software framework R libraries}
-\centering
-\begin{tabular}[t]{l>{\raggedright\arraybackslash}m{20em}>{\raggedright\arraybackslash}m{20em}}
-\toprule
-Package & Purpose & R library dependencies\\
-\midrule
-ready4 & Provide a template and novel syntax for modular CHEM implementations and tools for finding interoperable CHEM modules, datasets and reproducible analysis programs.
-& assertthat bib2df dataverse dplyr fs Hmisc kableExtra knitr lifecycle magrittr methods natmanager piggyback purrr readr readxl rlang rmarkdown rvest stats stringi stringr testit testthat tibble tidyRSS tools utils zen4R\\
-ready4fun & Streamline and standardise the authoring and documenting of functions that support transferable and generalisable model algorithms.
-& desc devtools dplyr gert Hmisc knitr lifecycle lubridate magrittr methods piggyback pkgdown purrr readxl ready4 ready4show ready4use rlang sinew stats stringi stringr testit testthat tibble tidyr tools usethis utils xfun\\
-ready4class & Streamline and standardise the authoring and documenting of new interoperable CHEM modules.
-& devtools dplyr fs gtools Hmisc knitr lifecycle magrittr methods purrr ready4 ready4fun ready4show rlang stats stringi stringr testit testthat tibble tidyr usethis utils\\
-ready4pack & Help bundle and disseminate newly created CHEM modules as R libraries that are documented, licensed and quality assured.
-& dataverse dplyr knitr lifecycle magrittr methods purrr ready4 ready4class ready4fun rlang stringr testthat tibble tidyr utils\\
-ready4use & Help manage the labelling and transfer of data between CHEM modules and local and remote data repositories.
-& data.table dataverse dplyr fs Hmisc knitr lifecycle magrittr methods piggyback purrr readxl ready4 ready4show rlang stats stringi stringr testit testthat tibble tidyr utils\\
-\addlinespace
-ready4show & Facilitate the use of CHEM modules in programs to implement integrated and reproducible data ingest, analysis and reporting pipelines.
-& dataverse DescTools dplyr flextable grDevices here Hmisc kableExtra knitr knitrBootstrap lifecycle magrittr methods officer purrr ready4 rlang rmarkdown stringi stringr testthat tibble tidyr utils xtable\\
-\bottomrule
-\end{tabular}
-\end{table}
-
 \hypertarget{online-services}{%
@@
 We configured individual repositories in our GitHub organisation to implement continuous integration.
-By default, code libraries authored with our framework will use continuous integration to assess compliance with policies specified by the Comprehensive R Archive Network (CRAN) {[}51{]}.
-To track our code coverage, we linked our GitHub organisation to an account we established at codecov {[}52{]}.
+By default, code libraries authored with our framework will use continuous integration to assess compliance with policies specified by the Comprehensive R Archive Network (CRAN) \citep{CRAN2022}.
+To track our code coverage, we linked our GitHub organisation to an account we established at codecov \citep{codecov_2022}.
 To facilitate the creation and hosting of documentation websites, we enabled GitHub Pages in each repository used for code library development.
@@
 
-The documentation website was developed using the Hugo framework {[}53{]}, Docsy theme {[}54{]} and Algolia DocSearch {[}55{]} and is hosted using the Netlify {[}56{]} service.
+The documentation website was developed using the Hugo framework \citep{hugo_2023}, Docsy theme \citep{docsy_2023} and Algolia DocSearch \citep{algoliadocsearch_2023} and is hosted using the Netlify \citep{netlify_2023} service.
 We used functions from our foundation framework library to partially automate website updates relating to available CHEM modules, datasets and analysis programs.
@@
 
-\begin{figure}
-\includegraphics[width=400px]{../Data/images/Figure1} \caption{High level summary of planned implementation of youth mental health economic model}\label{fig:fig1}
-\end{figure}
-
 \hypertarget{economic-topics}{%
@@
 
-Currently, we are using the ready4 software framework to develop, apply, and share youth mental health CHEMs in four of the twelve domains of health economics identified by Wagstaff and Culyer {[}1{]}:
+Currently, we are using the ready4 software framework to develop, apply, and share youth mental health CHEMs in four of the twelve domains of health economics identified by Wagstaff and Culyer \citep{wagstaff2012four}:
 
@@
 
-We have previously described a study {[}57{]} to develop utility mapping models for use in samples of young people presenting to primary mental health services.
+We have previously described a study \citep{Hamilton2021.07.07.21260129} to develop utility mapping models for use in samples of young people presenting to primary mental health services.
 The ready4 software framework was used in that study to develop CHEM modules, supply those modules with data and implement modelling analyses, creating the following artefacts:
@@
 \item
-  development version module libraries for describing and validating youth mental health human record datasets {[}58{]}, scoring health utility {[}59{]}, specifying utility mapping models {[}60{]} and implementing reproducible utility mapping studies {[}61{]};
+  development version module libraries for describing and validating youth mental health human record datasets \citep{hamilton_matthew_2022_6084467}, scoring health utility \citep{hamilton_matthew_2022_6084824}, specifying utility mapping models \citep{hamilton_matthew_2022_6116701} and implementing reproducible utility mapping studies \citep{gao_caroline_2022_6130155};
 \item
-  a development version library of functions for finding and using utility mapping models developed with these tools {[}62{]};
+  a development version library of functions for finding and using utility mapping models developed with these tools \citep{matthew_p_hamilton_2021_5646669};
 \item
-  collections of real data (study input and results {[}63{]}) and toy data (synthetic populations for testing model modules {[}64{]});
+  collections of real data (study input and results \citep{DVN/DKDIB0_2021}) and toy data (synthetic populations for testing model modules \citep{DVN/HJXYKQ_2021});
 \item
-  programs for replicating all steps from data ingest to manuscript production {[}65{]}, applying utility mapping models to new data {[}66{]} and generating a synthetic representation of the study dataset {[}67{]}; and
+  programs for replicating all steps from data ingest to manuscript production \citep{hamilton_matthew_2022_6129906}, applying utility mapping models to new data \citep{hamilton_matthew_2022_6416330} and generating a synthetic representation of the study dataset \citep{hamilton_matthew_p_2022_6321821}; and
 \item
-  subroutines for creating a catalogue of utility mapping models {[}68{]} and generating a draft scientific manuscript {[}69{]} for studies implemented with these modules.
+  subroutines for creating a catalogue of utility mapping models \citep{hamilton_matthew_2022_6116385} and generating a draft scientific manuscript \citep{matthew_p_hamilton_2022_5976988} for studies implemented with these modules.
 \end{itemize}
@@
 
-\blandscape
+\begin{landscape}
 
-\begin{table}
-
-\caption{\label{tab:checktb}Assessment of a CHEM implementation in youth mental health using Transparent, Reusable and Updatable (TRU) criteria}
-\centering
-\begin{tabular}[t]{>{\raggedright\arraybackslash}p{10em}l>{\raggedright\arraybackslash}p{35em}}
-\toprule
-Criterion & Met? & Detail\\
-\midrule
-\textbf{T1 Software files are open access} & Yes & All source code and testing procedures are available in public GitHub repositories, with each code release persistently available in a Zenodo repository.
-As the study dataset contains confidential patient records, it was not published.
-Instead, a synthetic representation of the study dataset is persistently available in a repository in the Harvard Dataverse.
-Data files to support out of sample application of models are published at the same location.\\
-\textbf{T2 Project team contributions and judgments are easily identified} & Yes & All module libraries, programs, and datasets are distributed with citation information.
-Public GitHub repositories detail author code contributions over project development history.
-Model catalogues persistently available on the Harvard Dataverse describe the predictive performance of models under multiple usage regimes.
-Each code library is documented with worked examples of how to apply CHEM modules.
-Analysis and reporting programs are self-documenting.
-Sub-routines for generating reports are documented with README files.\\
-\textbf{R1 Programming practices promote generalisability and transferability} & Yes & CHEMs are written using both functional and object-oriented paradigms.
-Code library documentation websites include hypothetical examples of generalisability (applying study algorithm to estimate mapping models from new data with the same predictor and outcome variables) and transferability (adapting study algorithm to develop mapping models from datasets with different predictor variables and outcomes measured with a different utility instrument).\\
-\textbf{R2 Licenses restrict only unethical reuse} & Yes & All code is distributed using GPL-3 licenses.
-Datasets use an amended version of template terms provided by Harvard Dataverse, allowing reuse of data subject to some ethical restrictions (e.g., use in efforts to reidentify study participants is prohibited).\\
-\textbf{U1 Maintenance infrastructure is in place} & Yes & All code is version controlled using git and GitHub, with semantic versioning.
-Each code library has a specified maintainer and guidance for potential code contributors is available on the project website.\\
-\addlinespace
-\textbf{U2 New releases are systematically retested and deprecated} & Partial & Continuous integration is used for all code libraries, primarily for acceptance testing.
-Only limited use is made of unit testing.
-Retired library code is deprecated using tools from the lifecycle R library.
-Library documentation articles and datasets are also deprecated.\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\elandscape
+\end{landscape}
 
@@
 
-Ethical practice is a core expectation of health researchers and computational methods underpin most quantitative research, yet an understanding of what constitutes ethical public health modelling practice is underdeveloped {[}12{]}.
+Ethical practice is a core expectation of health researchers and computational methods underpin most quantitative research, yet an understanding of what constitutes ethical public health modelling practice is underdeveloped \citep{10.3389/fpubh.2017.00068}.
 We have addressed this gap with our proposed responsibilities for model developers and funders, enabling CHEM attributes and CHEM implementation assessment criteria.
 
-Currently, many if not most existing CHEMs are insufficiently transparent {[}22,25--27{]}, not reusable {[}6,7{]}, nor updatable {[}31,70{]}.
+Currently, many if not most existing CHEMs are insufficiently transparent \citep{Jalali2021, McManus2019, Bermejo2017, Ghabri2019}, not reusable \citep{Feenstra2022, Emerson2019}, nor updatable \citep{Sampson2017, 10.3389/fpubh.2022.899874}.
 Addressing these issues will require changes to the tools, practices and funding underpinning health economic model development.
@@
 We developed our prototype software framework primarily to address the user requirements of one group -- ourselves.
-Factors such as user enjoyment, usability, active user-community and supporting resources influence adoption of software frameworks {[}8{]}.
+Factors such as user enjoyment, usability, active user-community and supporting resources influence adoption of software frameworks \citep{myllarniemi2018development}.
 We currently lack the resources required to address these issues for our software framework.
@@
 Secondly, implementation that combines both object-oriented and functional programming paradigms can avail of the modular and syntactical simplicity benefits of the former, while limiting needless bundling of code artefacts.
-Thirdly, a sensible trade-off needs to be found between transparent code implementation (which requires clear and sufficiently detailed documentation) and Agile Software Development (for which a foundational principle is prioritising the development of working code over writing documentation {[}71{]}).
+Thirdly, a sensible trade-off needs to be found between transparent code implementation (which requires clear and sufficiently detailed documentation) and Agile Software Development (for which a foundational principle is prioritising the development of working code over writing documentation \citep{beck2001manifesto}).
 Our software framework makes this trade off by enforcing the use of consistent code style conventions and file organisation which in turn enables automated generation of simple documentation at every CHEM module update.
@@
 However, better tools alone are insufficient and policy and institutional changes are also required.
-Reducing waste in research is a core responsibility of research funders {[}72{]} and funding the development of CHEMs that are not adequately understood, reused or updated is wasteful.
+Reducing waste in research is a core responsibility of research funders \citep{chalmers2014increase} and funding the development of CHEMs that are not adequately understood, reused or updated is wasteful.
 Existing incentive structures for health economists generally do not promote facilitating peers to reuse their work and funding is rarely adequate to maintain and routinely update a model.
-Currently, it can take ``an extraordinary amount of idealism'' to commit to authoring and maintaining research software {[}73{]}.
-Previously recommended strategies for more beneficial health economic research investments include support for harmonised ethical standards for model development {[}12{]}, methodological innovation to improve model transferability {[}74{]}, networks of modellers working on common health conditions {[}75{]}, and centralized infrastructure such as open source model repositories {[}5{]} and a standard platform for model implementations {[}22{]}.
+Currently, it can take ``an extraordinary amount of idealism'' to commit to authoring and maintaining research software \citep{anzt2020environment}.
+Previously recommended strategies for more beneficial health economic research investments include support for harmonised ethical standards for model development \citep{10.3389/fpubh.2017.00068}, methodological innovation to improve model transferability \citep{craig2018taking}, networks of modellers working on common health conditions \citep{Sampson2019}, and centralized infrastructure such as open source model repositories \citep{Pouwels2022} and a standard platform for model implementations \citep{Ghabri2019}.
 Development of software frameworks to support ethical CHEM implementations could enable and enhance each of these strategies.
@@
 
-\hypertarget{refs}{}
-\begin{CSLReferences}{0}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-wagstaff2012four}{}}%
-\CSLLeftMargin{1. }%
-\CSLRightInline{Wagstaff A, Culyer AJ. Four decades of health economics through a bibliometric lens. Journal of health economics. Elsevier; 2012;31: 406--439. }
+\newpage
 
-\leavevmode\vadjust pre{\hypertarget{ref-python2009}{}}%
-\CSLLeftMargin{2. }%
-\CSLRightInline{Van Rossum G, Drake FL. Python 3 reference manual. Scotts Valley, CA: CreateSpace; 2009. }
+\hypertarget{tables-and-figures}{%
+\subsection*{Tables and figures}\label{tables-and-figures}}
+\addcontentsline{toc}{subsection}{Tables and figures}
 
-\leavevmode\vadjust pre{\hypertarget{ref-RCORE2022}{}}%
-\CSLLeftMargin{3. }%
-\CSLRightInline{R Core Team.
-R: A language and environment for statistical computing {[}Internet{]}.
-Vienna, Austria: R Foundation for Statistical Computing; 2022.
-Available: \url{https://www.R-project.org/}}
+\begin{table}
 
-\leavevmode\vadjust pre{\hypertarget{ref-incerti2019r}{}}%
-\CSLLeftMargin{4. }%
-\CSLRightInline{Incerti D, Thom H, Baio G, Jansen JP. R you still using excel? The advantages of modern software tools for health technology assessment. Value in Health. Elsevier; 2019;22: 575--579. }
+\caption{\label{tab:proscons}Implications of choosing commercial modelling software or an open-source programming language for the computational implementation of health economic models}
+\centering
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{7em}>{\raggedright\arraybackslash}p{20em}>{\raggedright\arraybackslash}p{20em}}
+\toprule
+Implications & Commercial modelling software & Open-source programming language\\
+\midrule
+ & (+) Will include tools to efficienty accomplish many common modelling tasks. & (-) Initial development is likely to be time and resource intensive.\\
 
-\leavevmode\vadjust pre{\hypertarget{ref-Pouwels2022}{}}%
-\CSLLeftMargin{5. }%
-\CSLRightInline{Pouwels X, Sampson CJ, Arnold RJG.
-Opportunities and barriers to the development and use of open source health economic models: A survey.
-Value Health.
-2022;25: 473--479.
-doi:\href{https://doi.org/10.1016/j.jval.2021.10.001}{10.1016/j.jval.2021.10.001}}
+ & (+) Requires limited or no programming skills. & (+) Over medium term, efficiency savings are possible if:\\
 
-\leavevmode\vadjust pre{\hypertarget{ref-Feenstra2022}{}}%
-\CSLLeftMargin{6. }%
-\CSLRightInline{Feenstra T, Corro-Ramos I, Hamerlijnck D, Voorn G van, Ghabri S.
-Four aspects affecting health economic decision models and their validation.
-PharmacoEconomics.
-2022;40: 241--248.
-doi:\href{https://doi.org/10.1007/s40273-021-01110-w}{10.1007/s40273-021-01110-w}}
+ & (-) Requires model developers and users to purchase software licenses & (i)  artefacts (code and data) from pre-existing models are leveraged; and / or\\
 
-\leavevmode\vadjust pre{\hypertarget{ref-Emerson2019}{}}%
-\CSLLeftMargin{7. }%
-\CSLRightInline{Emerson J, Bacon R, Kent A, Neumann PJ, Cohen JT.
-Publication of decision model source code: Attitudes of health economics authors.
-PharmacoEconomics.
-2019;37: 1409--1410.
-doi:\href{https://doi.org/10.1007/s40273-019-00796-3}{10.1007/s40273-019-00796-3}}
+\multirow{-4}{7em}{\raggedright\arraybackslash \textbf{Resources}} &  & (ii)    maintaining and transferring (e.g. to new decision problems / contexts) model.\\
+\cmidrule{1-3}
+\addlinespace[0.3em]
+\multicolumn{3}{c}{\textbf{Transparency}}\\
+\hspace{1em} & (+) Popular tools (e.g. Excel) are readily understood by many. & (+) Easy to publicly share testable source code while selectively restricting access to confidential data.\\
 
-\leavevmode\vadjust pre{\hypertarget{ref-myllarniemi2018development}{}}%
-\CSLLeftMargin{8. }%
-\CSLRightInline{Myllärniemi V, Kujala S, Raatikainen M, Sevońn P.
-Development as a journey: Factors supporting the adoption and use of software frameworks.
-Journal of software engineering research and development.
-SpringerOpen; 2018;6: 1--22.
-}
+\hspace{1em} & (-) Non seemless integration with scientific manuscript authoring pipelines raises risk of (undetected) transcription errors when reporting results.
+& (+) Easy to make clear who has developed and tested each part.\\
 
-\leavevmode\vadjust pre{\hypertarget{ref-edwin2014software}{}}%
-\CSLLeftMargin{9. }%
-\CSLRightInline{Edwin NM. Software frameworks, architectural and design patterns. Journal of Software Engineering and Applications. Scientific Research Publishing; 2014;2014. }
+\hspace{1em} &  & (-) Novel code increases likelihood of (undetected) software errors.\\
 
-\leavevmode\vadjust pre{\hypertarget{ref-PyTorch2019}{}}%
-\CSLLeftMargin{10. }%
-\CSLRightInline{Paszke A, Gross S, Massa F, Lerer A, Bradbury J, Chanan G, et al.
-PyTorch: An imperative style, high-performance deep learning library.
-Proceedings of the 33rd international conference on neural information processing systems.
-Red Hook, NY, USA: Curran Associates Inc.; 2019.
-}
+\addlinespace[0.3em]
+\multicolumn{3}{c}{\textbf{Reusability}}\\
+\hspace{1em} & (+) Files will open and execute correctly for years after project is completed.
+& (-) Potentially fragile – if not maintained / not bundled with all required and correctly versioned dependencies\\
 
-\leavevmode\vadjust pre{\hypertarget{ref-alarid2019need}{}}%
-\CSLLeftMargin{11. }%
-\CSLRightInline{Alarid-Escudero F, Krijkamp EM, Pechlivanoglou P, Jalal H, Kao S-YZ, Yang A, et al.
-A need for change!
-A coding framework for improving transparency in decision modeling.
-Pharmacoeconomics.
-Springer; 2019;37: 1329--1339.
-}
+\hspace{1em} &  & (+) Facilitates modular implementations that make complex model representations more tractable.\\
 
-\leavevmode\vadjust pre{\hypertarget{ref-10.3389ux2ffpubh.2017.00068}{}}%
-\CSLLeftMargin{12. }%
-\CSLRightInline{Boden LA, McKendrick IJ.
-Model-based policymaking: A framework to promote ethical {``good practice''} in mathematical modeling for public health policymaking.
-Frontiers in Public Health.
-2017;5.
-doi:\href{https://doi.org/10.3389/fpubh.2017.00068}{10.3389/fpubh.2017.00068}}
+\hspace{1em} &  & (+) Facilitates customised integration with existing data / decision systems.\\
 
-\leavevmode\vadjust pre{\hypertarget{ref-calder2018computational}{}}%
-\CSLLeftMargin{13. }%
-\CSLRightInline{Calder M, Craig C, Culley D, De Cani R, Donnelly CA, Douglas R, et al.
-Computational modelling for decision-making: Where, why, what, who and how.
-Royal Society open science.
-The Royal Society Publishing; 2018;5: 172096.
-}
+\addlinespace[0.3em]
+\multicolumn{3}{c}{\textbf{Updatability}}\\
+\hspace{1em}\multirow{-7}{7em}{\raggedright\arraybackslash \textbf{Ethical}} & (-) Selective modification with appropriate attribution can be difficult.
+& (-) Facilitates collaborative development and maintenance.\\
+\bottomrule
+\end{tabular}
+\end{table}
+\newpage
 
-\leavevmode\vadjust pre{\hypertarget{ref-ruparelia2010software}{}}%
-\CSLLeftMargin{14. }%
-\CSLRightInline{Ruparelia NB. Software development lifecycle models. ACM SIGSOFT Software Engineering Notes. ACM New York, NY, USA; 2010;35: 8--13. }
+\begin{table}
 
-\leavevmode\vadjust pre{\hypertarget{ref-thompson2022escape}{}}%
-\CSLLeftMargin{15. }%
-\CSLRightInline{Thompson E. Escape from model land: How mathematical models can lead us astray and what we can do about it. New Yourk: Basic Books; 2022. }
+\caption{\label{tab:timelygls}Transparent, reusable and updatable (TRU) computational health economic models (CHEMs) are suggestive of ethical modelling practice}
+\centering
+\begin{tabular}[t]{>{}l>{\raggedright\arraybackslash}p{13em}>{\raggedright\arraybackslash}p{13em}>{\raggedright\arraybackslash}p{13em}}
+\toprule
+\multicolumn{1}{c}{\em{\textbf{ }}} & \multicolumn{3}{c}{\em{\textbf{Project team responsibility}}} \\
+\cmidrule(l{3pt}r{3pt}){2-4}
+  & Social acceptability & Fitness for purpose & Beneficial use\\
+\midrule
+\textbf{Transparent} & Modeller judgments, model features and verification checks can be reviewed by third parties.
+& Modeller judgments, model features and verification checks can be reviewed by third parties.
+& Decision-makers can understand the strengths and weakness of models before applying them.\\
 
-\leavevmode\vadjust pre{\hypertarget{ref-duckett2022journey}{}}%
-\CSLLeftMargin{16. }%
-\CSLRightInline{Duckett S. A journey towards a theology of health economics and healthcare funding. Theology. SAGE Publications Sage UK: London, England; 2022;125: 326--334. }
+\textbf{Reusable} &  & Third party use increases likelihood of errors being identified. & Can inform more decision problems, in more contexts with less duplicative effort.\\
 
-\leavevmode\vadjust pre{\hypertarget{ref-HARVARD2020112975}{}}%
-\CSLLeftMargin{17. }%
-\CSLRightInline{Harvard S, Werker GR, Silva DS.
-Social, ethical, and other value judgments in health economics modelling.
-Social Science \& Medicine.
-2020;253: 112975.
-doi:\url{https://doi.org/10.1016/j.socscimed.2020.112975}}
+\textbf{Updatable} & \multirow{-2}{13em}{\raggedright\arraybackslash Models can be modified to reflect alternative value judgments.} & Models that are maintained can be validly used for longer.
+& Models can be validly used for longer.\\
+\bottomrule
+\end{tabular}
+\end{table}
+\newpage
 
-\leavevmode\vadjust pre{\hypertarget{ref-Erdemir2020}{}}%
-\CSLLeftMargin{18. }%
-\CSLRightInline{Erdemir A, Mulugeta L, Ku JP, Drach A, Horner M, Morrison TM, et al.
-Credible practice of modeling and simulation in healthcare: Ten rules from a multidisciplinary perspective.
-Journal of translational medicine.
-2020;18: 369.
-doi:\href{https://doi.org/10.1186/s12967-020-02540-4}{10.1186/s12967-020-02540-4}}
+\begin{table}
 
-\leavevmode\vadjust pre{\hypertarget{ref-thompson2019escape}{}}%
-\CSLLeftMargin{19. }%
-\CSLRightInline{Thompson EL, Smith LA. Escape from model-land. Economics. De Gruyter Open Access; 2019;13. }
+\caption{\label{tab:cpkgs}Software framework R libraries}
+\centering
+\begin{tabular}[t]{l>{\raggedright\arraybackslash}m{20em}>{\raggedright\arraybackslash}m{20em}}
+\toprule
+Package & Purpose & R library dependencies\\
+\midrule
+ready4 & Provide a template and novel syntax for modular CHEM implementations and tools for finding interoperable CHEM modules, datasets and reproducible analysis programs.
+& assertthat bib2df dataverse dplyr fs Hmisc kableExtra knitr lifecycle magrittr methods natmanager piggyback purrr readr readxl rlang rmarkdown rvest stats stringi stringr testit testthat tibble tidyRSS tools utils zen4R\\
+ready4fun & Streamline and standardise the authoring and documenting of functions that support transferable and generalisable model algorithms.
+& desc devtools dplyr gert Hmisc knitr lifecycle lubridate magrittr methods piggyback pkgdown purrr readxl ready4 ready4show ready4use rlang sinew stats stringi stringr testit testthat tibble tidyr tools usethis utils xfun\\
+ready4class & Streamline and standardise the authoring and documenting of new interoperable CHEM modules.
+& devtools dplyr fs gtools Hmisc knitr lifecycle magrittr methods purrr ready4 ready4fun ready4show rlang stats stringi stringr testit testthat tibble tidyr usethis utils\\
+ready4pack & Help bundle and disseminate newly created CHEM modules as R libraries that are documented, licensed and quality assured.
+& dataverse dplyr knitr lifecycle magrittr methods purrr ready4 ready4class ready4fun rlang stringr testthat tibble tidyr utils\\
+ready4use & Help manage the labelling and transfer of data between CHEM modules and local and remote data repositories.
+& data.table dataverse dplyr fs Hmisc knitr lifecycle magrittr methods piggyback purrr readxl ready4 ready4show rlang stats stringi stringr testit testthat tibble tidyr utils\\
+\addlinespace
+ready4show & Facilitate the use of CHEM modules in programs to implement integrated and reproducible data ingest, analysis and reporting pipelines.
+& dataverse DescTools dplyr flextable grDevices here Hmisc kableExtra knitr knitrBootstrap lifecycle magrittr methods officer purrr ready4 rlang rmarkdown stringi stringr testthat tibble tidyr utils xtable\\
+\bottomrule
+\end{tabular}
+\end{table}
+\newpage
 
-\leavevmode\vadjust pre{\hypertarget{ref-carletto_zanuzzi_sammarco_russo_2020}{}}%
-\CSLLeftMargin{20. }%
-\CSLRightInline{Carletto A, Zanuzzi M, Sammarco A, Russo P.
-Quality of health economic evaluations submitted to the italian medicines agency: Current state and future actions.
-International Journal of Technology Assessment in Health Care.
-Cambridge University Press; 2020;36: 560--568.
-doi:\href{https://doi.org/10.1017/S0266462320000641}{10.1017/S0266462320000641}}
+\begin{table}
 
-\leavevmode\vadjust pre{\hypertarget{ref-WONDER2015467}{}}%
-\CSLLeftMargin{21. }%
-\CSLRightInline{Wonder M, Dunlop S.
-Assessment of the quality of the clinical evidence in submissions to the australian pharmaceutical benefits advisory committee: Fit for purpose?
-Value in Health.
-2015;18: 467--476.
-doi:\url{https://doi.org/10.1016/j.jval.2015.02.011}}
+\caption{\label{tab:checktb}Assessment of a CHEM implementation in youth mental health using Transparent, Reusable and Updatable (TRU) criteria}
+\centering
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{10em}l>{\raggedright\arraybackslash}p{35em}}
+\toprule
+Criterion & Met? & Detail\\
+\midrule
+\textbf{T1 Software files are open access} & Yes & All source code and testing procedures are available in public GitHub repositories, with each code release persistently available in a Zenodo repository.
+As the study dataset contains confidential patient records, it was not published.
+Instead, a synthetic representation of the study dataset is persistently available in a repository in the Harvard Dataverse.
+Data files to support out of sample application of models are published at the same location.\\
+\textbf{T2 Project team contributions and judgments are easily identified} & Yes & All module libraries, programs, and datasets are distributed with citation information.
+Public GitHub repositories detail author code contributions over project development history.
+Model catalogues persistently available on the Harvard Dataverse describe the predictive performance of models under multiple usage regimes.
+Each code library is documented with worked examples of how to apply CHEM modules.
+Analysis and reporting programs are self-documenting.
+Sub-routines for generating reports are documented with README files.\\
+\textbf{R1 Programming practices promote generalisability and transferability} & Yes & CHEMs are written using both functional and object-oriented paradigms.
+Code library documentation websites include hypothetical examples of generalisability (applying study algorithm to estimate mapping models from new data with the same predictor and outcome variables) and transferability (adapting study algorithm to develop mapping models from datasets with different predictor variables and outcomes measured with a different utility instrument).\\
+\textbf{R2 Licenses restrict only unethical reuse} & Yes & All code is distributed using GPL-3 licenses.
+Datasets use an amended version of template terms provided by Harvard Dataverse, allowing reuse of data subject to some ethical restrictions (e.g., use in efforts to reidentify study participants is prohibited).\\
+\textbf{U1 Maintenance infrastructure is in place} & Yes & All code is version controlled using git and GitHub, with semantic versioning.
+Each code library has a specified maintainer and guidance for potential code contributors is available on the project website.\\
+\addlinespace
+\textbf{U2 New releases are systematically retested and deprecated} & Partial & Continuous integration is used for all code libraries, primarily for acceptance testing.
+Only limited use is made of unit testing.
+Retired library code is deprecated using tools from the lifecycle R library.
+Library documentation articles and datasets are also deprecated.\\
+\bottomrule
+\end{tabular}
+\end{table}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Ghabri2019}{}}%
-\CSLLeftMargin{22. }%
-\CSLRightInline{Ghabri S, Stevenson M, Möller J, Caro JJ.
-Trusting the results of model-based economic analyses: Is there a pragmatic validation solution?
-Pharmacoeconomics.
-2019;37: 1--6.
-doi:\href{https://doi.org/10.1007/s40273-018-0711-9}{10.1007/s40273-018-0711-9}}
+\newpage
 
-\leavevmode\vadjust pre{\hypertarget{ref-kolovos2017model}{}}%
-\CSLLeftMargin{23. }%
-\CSLRightInline{Kolovos S, Bosmans JE, Riper H, Chevreul K, Coupé VM, Tulder MW van.
-Model-based economic evaluation of treatments for depression: A systematic literature review.
-PharmacoEconomics-open.
-Springer; 2017;1: 149--165.
-}
+\bgroup 
+    \origfigure[H]
 
-\leavevmode\vadjust pre{\hypertarget{ref-haji2013model}{}}%
-\CSLLeftMargin{24. }%
-\CSLRightInline{Haji Ali Afzali H, Gray J, Karnon J.
-Model performance evaluation (validation and calibration) in model-based studies of therapeutic interventions for cardiovascular diseases: A review and suggested reporting framework.
-Applied health economics and health policy.
-Springer; 2013;11: 85--93.
-}
+\includegraphics[width=400px,]{../Data/images/Figure1} \caption{High level summary of planned implementation of youth mental health economic model}\label{fig:fig1}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Jalali2021}{}}%
-\CSLLeftMargin{25. }%
-\CSLRightInline{Jalali MS, DiGennaro C, Guitar A, Lew K, Rahmandad H.
-Evolution and reproducibility of simulation modeling in epidemiology and health policy over half a century.
-Epidemiologic Reviews.
-2021;43: 166--175.
-doi:\href{https://doi.org/10.1093/epirev/mxab006}{10.1093/epirev/mxab006}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-McManus2019}{}}%
-\CSLLeftMargin{26. }%
-\CSLRightInline{McManus E, Turner D, Sach T.
-Can you repeat that?
-Exploring the definition of a successful model replication in health economics.
-Pharmacoeconomics.
-2019;37: 1371--1381.
-doi:\href{https://doi.org/10.1007/s40273-019-00836-y}{10.1007/s40273-019-00836-y}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bermejo2017}{}}%
-\CSLLeftMargin{27. }%
-\CSLRightInline{Bermejo I, Tappenden P, Youn J-H.
-Replicating health economic models: Firm foundations or a house of cards?
-PharmacoEconomics.
-2017;35: 1113--1121.
-doi:\href{https://doi.org/10.1007/s40273-017-0553-x}{10.1007/s40273-017-0553-x}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Radeva2020}{}}%
-\CSLLeftMargin{28. }%
-\CSLRightInline{Radeva D, Hopkin G, Mossialos E, Borrill J, Osipenko L, Naci H.
-Assessment of technical errors and validation processes in economic models submitted by the company for NICE technology appraisals.
-International Journal of Technology Assessment in Health Care.
-2020;36: 311--316.
-doi:\href{https://doi.org/10.1017/S0266462320000422}{10.1017/S0266462320000422}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Arnold2010}{}}%
-\CSLLeftMargin{29. }%
-\CSLRightInline{Arnold RJG, Ekins S.
-Time for cooperation in health economics among the modelling community.
-PharmacoEconomics.
-2010;28: 609--613.
-doi:\href{https://doi.org/10.2165/11537580-000000000-00000}{10.2165/11537580-000000000-00000}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-garcia2021cost}{}}%
-\CSLLeftMargin{30. }%
-\CSLRightInline{Garcia-Mochon L, Rovira Forns J, Espin J.
-Cost transferability problems in economic evaluation as a framework for an european health care and social costs database.
-Cost Effectiveness and Resource Allocation.
-Springer; 2021;19: 1--12.
-}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Sampson2017}{}}%
-\CSLLeftMargin{31. }%
-\CSLRightInline{Sampson CJ, Wrightson T.
-Model registration: A call to action.
-PharmacoEconomics - Open.
-2017;1: 73--77.
-doi:\href{https://doi.org/10.1007/s41669-017-0019-2}{10.1007/s41669-017-0019-2}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Eddy2012}{}}%
-\CSLLeftMargin{32. }%
-\CSLRightInline{Eddy DM, Hollingworth W, Caro JJ, Tsevat J, McDonald KM, Wong JB.
-Model transparency and validation: A report of the ISPOR-SMDM modeling good research practices task force-7.
-Med Decis Making.
-2012;32: 733--43.
-doi:\href{https://doi.org/10.1177/0272989x12454579}{10.1177/0272989x12454579}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Zenodo2013}{}}%
-\CSLLeftMargin{33. }%
-\CSLRightInline{European Organization For Nuclear Research, OpenAIRE. Zenodo {[}Internet{]}. CERN; 2013. doi:\href{https://doi.org/10.25495/7GXK-RD71}{10.25495/7GXK-RD71}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Dataverse2007}{}}%
-\CSLLeftMargin{34. }%
-\CSLRightInline{Quantitative Social Science I for. Dataverse {[}Internet{]}. Harvard University; 2007. Available: \url{https://dataverse.org}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-techver2019}{}}%
-\CSLLeftMargin{35. }%
-\CSLRightInline{Büyükkaramikli NC, Rutten-van Mölken MPMH, Severens JL, Al M.
-TECH-VER: A verification checklist to reduce errors in models and improve their credibility.
-PharmacoEconomics.
-2019;37: 1391--1408.
-doi:\href{https://doi.org/10.1007/s40273-019-00844-y}{10.1007/s40273-019-00844-y}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ERICWONG2010188}{}}%
-\CSLLeftMargin{36. }%
-\CSLRightInline{Eric Wong W, Debroy V, Choi B.
-A family of code coverage-based heuristics for effective fault localization.
-Journal of Systems and Software.
-2010;83: 188--208.
-doi:\url{https://doi.org/10.1016/j.jss.2009.09.037}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-martin2003agile}{}}%
-\CSLLeftMargin{37. }%
-\CSLRightInline{Martin RC. Agile software development: Principles, patterns, and practices. Prentice Hall PTR; 2003. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-github2007}{}}%
-\CSLLeftMargin{38. }%
-\CSLRightInline{github. GitHub {[}Internet{]}. 2007. Available: \url{https://github.com/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RN39}{}}%
-\CSLLeftMargin{39. }%
-\CSLRightInline{Augustovski F, Iglesias C, Manca A, Drummond M, Rubinstein A, Marti SG.
-Barriers to generalizability of health economic evaluations in latin america and the caribbean region.
-Pharmacoeconomics.
-2009;27: 919--29.
-doi:\href{https://doi.org/10.2165/11313670-000000000-00000}{10.2165/11313670-000000000-00000}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wilson_2017}{}}%
-\CSLLeftMargin{40. }%
-\CSLRightInline{Wilson JAC Greg AND Bryan.
-Good enough practices in scientific computing.
-PLOS Computational Biology.
-Public Library of Science; 2017;13: 1--20.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1005510}{10.1371/journal.pcbi.1005510}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-pan2021modular}{}}%
-\CSLLeftMargin{41. }%
-\CSLRightInline{Pan M, Gawthrop PJ, Cursons J, Crampin EJ.
-Modular assembly of dynamic models in systems biology.
-PLoS computational biology.
-Public Library of Science San Francisco, CA USA; 2021;17: e1009513.
-}
-
-\leavevmode\vadjust pre{\hypertarget{ref-8717448}{}}%
-\CSLLeftMargin{42. }%
-\CSLRightInline{Hourani H, Wasmi H, Alrawashdeh T.
-A code complexity model of object oriented programming (OOP).
-2019 IEEE jordan international joint conference on electrical engineering and information technology (JEEIT).
-2019.
-pp.
-560--564.
-doi:\href{https://doi.org/10.1109/JEEIT.2019.8717448}{10.1109/JEEIT.2019.8717448}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-copyleft2022}{}}%
-\CSLLeftMargin{43. }%
-\CSLRightInline{Foundation TFS. What is copyleft? {[}Internet{]}. Available: \url{https://www.gnu.org/copyleft/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Jenkins2021}{}}%
-\CSLLeftMargin{44. }%
-\CSLRightInline{Jenkins DA, Martin GP, Sperrin M, Riley RD, Debray TPA, Collins GS, et al.
-Continual updating and monitoring of clinical prediction models: Time for dynamic prediction systems?
-Diagnostic and Prognostic Research.
-2021;5: 1.
-doi:\href{https://doi.org/10.1186/s41512-020-00090-3}{10.1186/s41512-020-00090-3}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-info:doiux2f10.2196ux2f20028}{}}%
-\CSLLeftMargin{45. }%
-\CSLRightInline{Ye Y, Barapatre S, Davis MK, Elliston KO, Davatzikos C, Fedorov A, et al.
-Open-source software sustainability models: Initial white paper from the informatics technology for cancer research sustainability and industry partnership working group.
-J Med Internet Res.
-2021;23: e20028.
-doi:\href{https://doi.org/10.2196/20028}{10.2196/20028}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-MERGEL2015464}{}}%
-\CSLLeftMargin{46. }%
-\CSLRightInline{Mergel I.
-Open collaboration in the public sector: The case of social coding on GitHub.
-Government Information Quarterly.
-2015;32: 464--472.
-doi:\url{https://doi.org/10.1016/j.giq.2015.09.004}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-CI2017}{}}%
-\CSLLeftMargin{47. }%
-\CSLRightInline{Shahin M, Ali Babar M, Zhu L.
-Continuous integration, delivery and deployment: A systematic review on approaches, tools, challenges and practices.
-IEEE Access.
-2017;5: 3909--3943.
-doi:\href{https://doi.org/10.1109/ACCESS.2017.2685629}{10.1109/ACCESS.2017.2685629}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-zhou2016api}{}}%
-\CSLLeftMargin{48. }%
-\CSLRightInline{Zhou J, Walker RJ.
-API deprecation: A retrospective analysis and detection method for code examples on the web.
-Proceedings of the 2016 24th ACM SIGSOFT international symposium on foundations of software engineering.
-2016.
-pp.
-266--277.
-}
-
-\leavevmode\vadjust pre{\hypertarget{ref-barros2023empowering}{}}%
-\CSLLeftMargin{49. }%
-\CSLRightInline{Barros C, Luo Y, Chubaty AM, Eddy IM, Micheletti T, Boisvenue C, et al.
-Empowering ecological modellers with a PERFICT workflow: Seamlessly linking data, parameterisation, prediction, validation and visualisation.
-Methods in Ecology and Evolution.
-Wiley Online Library; 2023; }
-
-\leavevmode\vadjust pre{\hypertarget{ref-10.1214ux2f13-STS452}{}}%
-\CSLLeftMargin{50. }%
-\CSLRightInline{Chambers JM.
-{Object-Oriented Programming, Functional Programming and R}.
-Statistical Science.
-Institute of Mathematical Statistics; 2014;29: 167--180.
-doi:\href{https://doi.org/10.1214/13-STS452}{10.1214/13-STS452}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-CRAN2022}{}}%
-\CSLLeftMargin{51. }%
-\CSLRightInline{Statistical Computing RF for. The comprehensive r archive network {[}Internet{]}. 2022. Available: \url{https://cran.r-project.org}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-codecov_2022}{}}%
-\CSLLeftMargin{52. }%
-\CSLRightInline{Codecov {[}Internet{]}. Available: \url{https://about.codecov.io/}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hugo_2023}{}}%
-\CSLLeftMargin{53. }%
-\CSLRightInline{Hugo: The world's fastest framework for building websites {[}Internet{]}. Available: \url{https://gohugo.io}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-docsy_2023}{}}%
-\CSLLeftMargin{54. }%
-\CSLRightInline{Docsy {[}Internet{]}. Available: \url{https://www.docsy.dev}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-algoliadocsearch_2023}{}}%
-\CSLLeftMargin{55. }%
-\CSLRightInline{Docsearch {[}Internet{]}. Available: \url{https://docsearch.algolia.com}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-netlify_2023}{}}%
-\CSLLeftMargin{56. }%
-\CSLRightInline{Netlify {[}Internet{]}. Available: \url{https://www.netlify.com}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hamilton2021.07.07.21260129}{}}%
-\CSLLeftMargin{57. }%
-\CSLRightInline{Hamilton MP, Gao CX, Filia KM, Menssink JM, Sharmin S, Telford N, et al.
-Mapping psychological distress, depression and anxiety measures to AQoL-6D utility using data from a sample of young people presenting to primary mental health services.
-medRxiv.
-Cold Spring Harbor Laboratory Press; 2022; doi:\href{https://doi.org/10.1101/2021.07.07.21260129}{10.1101/2021.07.07.21260129}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hamilton_matthew_2022_6084467}{}}%
-\CSLLeftMargin{58. }%
-\CSLRightInline{Hamilton M, Gao C.
-{youthvars: Describe and Validate Youth Mental Health Datasets} {[}Internet{]}.
-Zenodo; 2022.
-doi:\href{https://doi.org/10.5281/zenodo.6084467}{10.5281/zenodo.6084467}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hamilton_matthew_2022_6084824}{}}%
-\CSLLeftMargin{59. }%
-\CSLRightInline{Hamilton M, Gao C. Scorz: Score questionnaire item responses {[}Internet{]}. Zenodo; 2022. doi:\href{https://doi.org/10.5281/zenodo.6084824}{10.5281/zenodo.6084824}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hamilton_matthew_2022_6116701}{}}%
-\CSLLeftMargin{60. }%
-\CSLRightInline{Hamilton M, Gao C.
-{specific: Specify Candidate Models for Representing Mental Health Systems} {[}Internet{]}.
-Zenodo; 2022.
-doi:\href{https://doi.org/10.5281/zenodo.6116701}{10.5281/zenodo.6116701}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gao_caroline_2022_6130155}{}}%
-\CSLLeftMargin{61. }%
-\CSLRightInline{Gao C, Hamilton M. {TTU: Implement Transfer to Utility Mapping Algorithms} {[}Internet{]}. Zenodo; 2022. doi:\href{https://doi.org/10.5281/zenodo.6130155}{10.5281/zenodo.6130155}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-matthew_p_hamilton_2021_5646669}{}}%
-\CSLLeftMargin{62. }%
-\CSLRightInline{Hamilton MP, Gao CX.
-Youthu: Transform youth outcomes to health utility predictions {[}Internet{]}.
-Zenodo; 2022.
-doi:\href{https://doi.org/10.5281/zenodo.6210978}{10.5281/zenodo.6210978}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-DVNux2fDKDIB0_2021}{}}%
-\CSLLeftMargin{63. }%
-\CSLRightInline{Hamilton MP, Gao CX, Filia KM, Menssink JM, Sharmin S, Telford N, et al.
-{Transfer to AQoL-6D Utility Mapping Algorithms} {[}Internet{]}.
-Harvard Dataverse; 2021.
-doi:\href{https://doi.org/10.7910/DVN/DKDIB0}{10.7910/DVN/DKDIB0}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-DVNux2fHJXYKQ_2021}{}}%
-\CSLLeftMargin{64. }%
-\CSLRightInline{Hamilton MP.
-{Synthetic (fake) youth mental health datasets and data dictionaries} {[}Internet{]}.
-Harvard Dataverse; 2021.
-doi:\href{https://doi.org/10.7910/DVN/HJXYKQ}{10.7910/DVN/HJXYKQ}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hamilton_matthew_2022_6129906}{}}%
-\CSLLeftMargin{65. }%
-\CSLRightInline{Hamilton M, Gao C.
-{Complete study program to reproduce all steps from data ingest through to results dissemination for a study to map mental health measures to AQoL-6D health utility} {[}Internet{]}.
-Zenodo; 2022.
-doi:\href{https://doi.org/10.5281/zenodo.6212704}{10.5281/zenodo.6212704}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hamilton_matthew_2022_6416330}{}}%
-\CSLLeftMargin{66. }%
-\CSLRightInline{Hamilton M, Gao C.
-{aqol6dmap\_use: Apply AQoL-6D Utility Mapping Models To New Data} {[}Internet{]}.
-Zenodo; 2022.
-doi:\href{https://doi.org/10.5281/zenodo.6416330}{10.5281/zenodo.6416330}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hamilton_matthew_p_2022_6321821}{}}%
-\CSLLeftMargin{67. }%
-\CSLRightInline{Hamilton MP.
-{aqol6dmap\_fakes: Generate fake input data for an AQoL-6D mapping study} {[}Internet{]}.
-Zenodo; 2022.
-doi:\href{https://doi.org/10.5281/zenodo.6321821}{10.5281/zenodo.6321821}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hamilton_matthew_2022_6116385}{}}%
-\CSLLeftMargin{68. }%
-\CSLRightInline{Hamilton M.
-{ttu\_mdl\_ctlg: Generate a template utility mapping (transfer to utility) model catalogue} {[}Internet{]}.
-Zenodo; 2022.
-doi:\href{https://doi.org/10.5281/zenodo.6116385}{10.5281/zenodo.6116385}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-matthew_p_hamilton_2022_5976988}{}}%
-\CSLLeftMargin{69. }%
-\CSLRightInline{Hamilton MP.
-{ready4-dev/ttu\_lng\_ss: Create a Draft Scientific Manuscript For A Utility Mapping Study} {[}Internet{]}.
-Zenodo; 2022.
-doi:\href{https://doi.org/10.5281/zenodo.5976988}{10.5281/zenodo.5976988}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-10.3389ux2ffpubh.2022.899874}{}}%
-\CSLLeftMargin{70. }%
-\CSLRightInline{Kokol P, Blažun Vošner H, Kokol M, Završnik J.
-Role of agile in digital public health transformation.
-Frontiers in Public Health.
-2022;10.
-doi:\href{https://doi.org/10.3389/fpubh.2022.899874}{10.3389/fpubh.2022.899874}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-beck2001manifesto}{}}%
-\CSLLeftMargin{71. }%
-\CSLRightInline{Beck K, Beedle M, Van Bennekum A, Cockburn A, Cunningham W, Fowler M, et al. Manifesto for agile software development. Snowbird, UT; 2001; }
-
-\leavevmode\vadjust pre{\hypertarget{ref-chalmers2014increase}{}}%
-\CSLLeftMargin{72. }%
-\CSLRightInline{Chalmers I, Bracken MB, Djulbegovic B, Garattini S, Grant J, Gülmezoglu AM, et al.
-How to increase value and reduce waste when research priorities are set.
-The Lancet.
-Elsevier; 2014;383: 156--165.
-}
-
-\leavevmode\vadjust pre{\hypertarget{ref-anzt2020environment}{}}%
-\CSLLeftMargin{73. }%
-\CSLRightInline{Anzt H, Bach F, Druskat S, Löffler F, Loewe A, Renard BY, et al.
-An environment for sustainable research software in germany and beyond: Current state, open challenges, and call for action.
-F1000Research.
-Faculty of 1000 Ltd; 2020;9.
-}
-
-\leavevmode\vadjust pre{\hypertarget{ref-craig2018taking}{}}%
-\CSLLeftMargin{74. }%
-\CSLRightInline{Craig P, Di Ruggiero E, Frolich KL, Mykhalovskiy E, White M, Campbell R, et al.
-Taking account of context in population health intervention research: Guidance for producers, users and funders of research.
-National Institute for Health Research; 2018; }
-
-\leavevmode\vadjust pre{\hypertarget{ref-Sampson2019}{}}%
-\CSLLeftMargin{75. }%
-\CSLRightInline{Sampson CJ, Arnold R, Bryan S, Clarke P, Ekins S, Hatswell A, et al.
-Transparency in decision modelling: What, why, who and how?
-PharmacoEconomics.
-2019;37: 1355--1369.
-doi:\href{https://doi.org/10.1007/s40273-019-00819-z}{10.1007/s40273-019-00819-z}}
-
-\end{CSLReferences}
+    \endfigure
+\egroup 
+\newpage
 
@@
 
+\bibliography{bibliography.bib}
+
 \end{document}

### 2023-10-22 Reports/Manuscript/Tex_Export/Manuscript.tex
problems with table and figure placement

--- 2023-10-22 Reports/Manuscript/Manuscript.tex
@@
 \midrule
-ready4 & Provide a template and novel syntax for modular CHEM implementations and tools for finding interoperable CHEM modules, datasets and reproducible analysis programs.
+\includegraphics[valign=M,width=1.9cm,raise=4mm]{ready4_logo.png} & Provide a template and novel syntax for modular CHEM implementations and tools for finding interoperable CHEM modules, datasets and reproducible analysis programs.
 & assertthat bib2df dataverse dplyr fs Hmisc kableExtra knitr lifecycle magrittr methods natmanager piggyback purrr readr readxl rlang rmarkdown rvest stats stringi stringr testit testthat tibble tidyRSS tools utils zen4R\\
-ready4fun & Streamline and standardise the authoring and documenting of functions that support transferable and generalisable model algorithms.
+\includegraphics[valign=M,width=1.9cm,raise=4mm]{ready4fun_logo.png} & Streamline and standardise the authoring and documenting of functions that support transferable and generalisable model algorithms.
 & desc devtools dplyr gert Hmisc knitr lifecycle lubridate magrittr methods piggyback pkgdown purrr readxl ready4 ready4show ready4use rlang sinew stats stringi stringr testit testthat tibble tidyr tools usethis utils xfun\\
-ready4class & Streamline and standardise the authoring and documenting of new interoperable CHEM modules.
+\includegraphics[valign=M,width=1.9cm,raise=4mm]{ready4class_logo.png} & Streamline and standardise the authoring and documenting of new interoperable CHEM modules.
 & devtools dplyr fs gtools Hmisc knitr lifecycle magrittr methods purrr ready4 ready4fun ready4show rlang stats stringi stringr testit testthat tibble tidyr usethis utils\\
-ready4pack & Help bundle and disseminate newly created CHEM modules as R libraries that are documented, licensed and quality assured.
+\includegraphics[valign=M,width=1.9cm,raise=4mm]{ready4pack_logo.png} & Help bundle and disseminate newly created CHEM modules as R libraries that are documented, licensed and quality assured.
 & dataverse dplyr knitr lifecycle magrittr methods purrr ready4 ready4class ready4fun rlang stringr testthat tibble tidyr utils\\
-ready4use & Help manage the labelling and transfer of data between CHEM modules and local and remote data repositories.
+\includegraphics[valign=M,width=1.9cm,raise=4mm]{ready4use_logo.png} & Help manage the labelling and transfer of data between CHEM modules and local and remote data repositories.
 & data.table dataverse dplyr fs Hmisc knitr lifecycle magrittr methods piggyback purrr readxl ready4 ready4show rlang stats stringi stringr testit testthat tibble tidyr utils\\
 \addlinespace
-ready4show & Facilitate the use of CHEM modules in programs to implement integrated and reproducible data ingest, analysis and reporting pipelines.
+\includegraphics[valign=M,width=1.9cm,raise=4mm]{ready4show_logo.png} & Facilitate the use of CHEM modules in programs to implement integrated and reproducible data ingest, analysis and reporting pipelines.
 & dataverse DescTools dplyr flextable grDevices here Hmisc kableExtra knitr knitrBootstrap lifecycle magrittr methods officer purrr ready4 rlang rmarkdown stringi stringr testthat tibble tidyr utils xtable\\
@@
 \begin{figure}
-\includegraphics[width=400px]{../Data/images/Figure1} \caption{High level summary of planned implementation of youth mental health economic model}\label{fig:fig1}
+\includegraphics[width=400px]{Figure1} \caption{High level summary of planned implementation of youth mental health economic model}\label{fig:fig1}
 \end{figure}

### 2023-10-22 setup.R

@@ -10,7 +10,7 @@ X <- Ready4showSynopsis(#background_1L_chr = "Our study is entirely fictional.",
                         ethics_1L_chr = "Software framework development did not involve human subject research and was not ethically reviewed. The utility mapping worked example is a previously reported study that was reviewed and granted approval by the University of Melbourne’s Human Research Ethics Committee, and the local Human Ethics and Advisory Group (1645367.1).",
                         funding_1L_chr = "Software framework development was funded by Orygen, VicHealth, Victoria University and an Australian Government Research Training Program (RTP) Scholarship. The utility mapping study used as a worked example was funded by the National Health and Medical Research Council (NHMRC, APP1076940), Orygen and headspace.",
                         #interval_chr = "three months",
-                        keywords_chr = c("open source models","health economics","mental disorders"),
+                        keywords_chr = c("computational models", "ethics of modelling", "health economics", "mental disorders", "open-source models", "software frameworks"),
                         outp_formats_chr = "PDF",
                         #sample_desc_1L_chr = "The study sample is fake data that pretends to be young people aged 12 to 25 years who attended Australian primary care services for mental health related needs between November 2019 to August 2020.",
                         title_1L_chr = "A prototype software framework for transparent, reusable and updatable computational health economic models")
@@ -40,7 +40,7 @@ X <- renewSlot(X,
                  args_ls$abstract_ls <- list(Summary = "Most health economic analyses are undertaken with the aid of computers. However, the ethical dimensions of implementing health economic models as software (or computational health economic models (CHEMs)) are poorly understood. 
                                                         We propose that developers and funders of CHEMs share ethical responsibilities to (i) establish socially acceptable user requirements and design specifications; (ii) ensure fitness for purpose; and (iii) support socially beneficial use. 
                                                         We further propose that a transparent (T), reusable (R) and updatable (U) CHEM is suggestive of a project team that has largely fulfilled these responsibilities.
-                                                        We propose six criteria for assessing CHEMs: (T1) software files are open access; (T2) project team judgments and contributions are easily identified; 
+                                                        We propose six criteria for assessing CHEMs: (T1) software files are open access; (T2) project team contributions and judgments are easily identified; 
[…]

### 2023-10-23 Markdown/Manuscript/Child_RMDs/Clippings.Rmd
built submission files

@@
 We also plan to extend and update our prior work reviewing economic evidence relating to youth mental health programs [@RN33] so that it can be integrated with this model.
-Our initial work on **readyforwhatsnext** is focused on Victoria, Australia but the framework we are using to develop it is designed to facilitate extension by ourselves and others to different jurisdictional decision contexts.
+Our initial work on *readyforwhatsnext* is focused on Victoria, Australia but the framework we are using to develop it is designed to facilitate extension by ourselves and others to different jurisdictional decision contexts.
 Progress is reported on a project website [@rfwn2022].

### 2023-10-23 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
built submission files

@@
 
-(i) **establish socially acceptable user requirements and design specifications** (during CHEM planning);
+(i) *establish socially acceptable user requirements and design specifications* (during CHEM planning);
 
-(ii) **ensure fitness for purpose** (of CHEM implementation); and
+(ii) *ensure fitness for purpose* (of CHEM implementation); and
 
-(iii) **support socially beneficial use** (on CHEM release).
+(iii) *support socially beneficial use* (on CHEM release).
 
@@
 These value judgments influence the assumptions, selection of model features and standards for evidence that shape health economic model projects [@HARVARD2020112975].
-For example, as illustrated in Table \@ref(tab:proscons), project resource constraints may require model developers to make trade-offs when agreeing CHEM **user requirements and design specifications**.
+For example, as illustrated in Table \@ref(tab:proscons), project resource constraints may require model developers to make trade-offs when agreeing CHEM *user requirements and design specifications*.
 These trade-offs in turn determine how straightforward it is for a CHEM to be subsequently amended to reflect alternative value judgments relating to model conceptualisation and mathematical formalisation (Table \@ref(tab:timelygls)).
@@
 
-Modellers have duties both to ensure a computational model is **fit for purpose** and to provide potential third-party users with the means of assessing its adequacy for their proposed uses [@Erdemir2020; @Feenstra2022; @thompson2019escape; @10.3389/fpubh.2017.00068].
+Modellers have duties both to ensure a computational model is *fit for purpose* and to provide potential third-party users with the means of assessing its adequacy for their proposed uses [@Erdemir2020; @Feenstra2022; @thompson2019escape; @10.3389/fpubh.2017.00068].
 However, it is common for health economic models to have serious methodological flaws [@carletto_zanuzzi_sammarco_russo_2020; @WONDER2015467]; insufficient validation [@Ghabri2019; @kolovos2017model; @haji2013model], poor reproducibility [@Jalali2021; @McManus2019; @Bermejo2017]; and undeclared errors [@Radeva2020].
@@
 
-A CHEM will have limited **social benefit** if it is rarely used, if mis-used or when its acceptability and adequacy rapidly decay.
+A CHEM will have limited *social benefit* if it is rarely used, if mis-used or when its acceptability and adequacy rapidly decay.
 Reuse of CHEMs as components of other models can potentially make model development more efficient [@Arnold2010; @garcia2021cost].
@@
 
-Taking steps to make computational models **transparent** is an important part of ethical public health modelling practice [@10.3389/fpubh.2017.00068].
+Taking steps to make computational models *transparent* is an important part of ethical public health modelling practice [@10.3389/fpubh.2017.00068].
 Guidance on transparency in health economic modelling recommend that model code and data should be clearly documented [@Eddy2012].
@@
 
-A CHEM that is **reusable** also signals ethical modelling practice.
+A CHEM that is *reusable* also signals ethical modelling practice.
 Although making a CHEM’s code, data and documentation publicly available is increasingly considered good practice, it is insufficient to enable model re-use.
@@
 
-Models should be **updatable** so that they remain valid for longer, evolving as new evidence emerges and the systems being modelled change [@Jenkins2021; @garcia2021cost].
+Models should be *updatable* so that they remain valid for longer, evolving as new evidence emerges and the systems being modelled change [@Jenkins2021; @garcia2021cost].
 Ensuring that a model is regularly reviewed to identify and implement required improvements is a recommended defence against model validity decay [@calder2018computational].
@@
 
-How **transparent** a CHEM is can be assessed against the criteria:
+How *transparent* a CHEM is can be assessed against the criteria:
 
--	**T1**: Software files (executable code, testing procedures and outcomes and non-confidential data) are available in open access repositories.
+-	*T1*: Software files (executable code, testing procedures and outcomes and non-confidential data) are available in open access repositories.
 
--	**T2**: It is easy to see who funded, developed and tested each part of the CHEM and to identify the modelling team’s assumptions, judgments and theories about CHEM development and use.
+-	*T2*: It is easy to see who funded, developed and tested each part of the CHEM and to identify the modelling team’s assumptions, judgments and theories about CHEM development and use.
 
-How **reusable** a CHEM is can be assessed against the criteria:
+How *reusable* a CHEM is can be assessed against the criteria:
 
--	**R1**: Programming practices facilitate both generalisability and transferability.
+-	*R1*: Programming practices facilitate both generalisability and transferability.
 
--	**R2**: Licenses restrict only unethical use and allow anyone to ethically reuse model code and non-confidential data, in whole or in part, without charge, and for purposes that include the creation of derivative works.
+-	*R2*: Licenses restrict only unethical use and allow anyone to ethically reuse model code and non-confidential data, in whole or in part, without charge, and for purposes that include the creation of derivative works.
 
-How **updatable** a CHEM is can be assessed against the criteria:
+How *updatable* a CHEM is can be assessed against the criteria:
 
--	**U1**: Maintenance infrastructure is in place to support version control and collaboration with model users.
+-	*U1*: Maintenance infrastructure is in place to support version control and collaboration with model users.
 
--	**U2**: Each new release of a CHEM is systematically retested, with changes implemented to minimise disruptions for existing model users.
+-	*U2*: Each new release of a CHEM is systematically retested, with changes implemented to minimise disruptions for existing model users.

### 2023-10-23 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
built submission files

@@
 
-One framework library provides a **foundation for modular CHEM implementations**.
+One framework library provides a *foundation for modular CHEM implementations*.
 In modular model implementations, modules need to be able to share inputs and outputs with each other and to be run as independent models [@barros2023empowering].
@@
 
-Three framework libraries are designed to help streamline and standardise workflows for **authoring CHEM modules** from the template module.
+Three framework libraries are designed to help streamline and standardise workflows for *authoring CHEM modules* from the template module.
 The R language supports functional and object-oriented programming paradigms [@10.1214/13-STS452].
@@
 
-A library for **managing CHEM data** contains tools for supplying CHEM modules with input data ingested from local (i.e., a user's computer) or remote (online repositories) locations, labelling CHEM module datasets and exporting CHEM module data to online repositories.
-A library for **authoring reproducible analyses** contains tools to help write programs that apply CHEM modules to compatible datasets for the purpose of undertaking health economic analyses.
+A library for *managing CHEM data* contains tools for supplying CHEM modules with input data ingested from local (i.e., a user's computer) or remote (online repositories) locations, labelling CHEM module datasets and exporting CHEM module data to online repositories.
+A library for *authoring reproducible analyses* contains tools to help write programs that apply CHEM modules to compatible datasets for the purpose of undertaking health economic analyses.
 These analysis programs can be either self-documenting (code is integrated with plain English explanations of what it does) or trigger the creation of explanatory documents (e.g., a scientific manuscript).

### 2023-10-23 Markdown/Manuscript/Parent_PDF/Springer.Rmd
built submission files

@@
 title: A prototype software framework for transparent, reusable and updatable computational health economic models
-titlerunning: Transparent, reusable and updatable computational models
+titlerunning: Framework for ethical computational models
 
+# authors:
+#   - name: Matthew P Hamilton
+#     email: matthew.hamilton@orygen.org.au
+#     address: Orygen, Parkville, Australia
+#     correspondence: true
+#     equal_contributor: "yes"
+#   - name: Caroline X Gao
+#     address: Orygen, Parkville, Australia, Centre for Youth Mental Health, University of Melbourne, Parkville, Australia and School of Public Health and Preventive Medicine, Monash University, Clayton, Australia
+#     equal_contributor: "yes"
+#   - name: Kate M Filia
+#     address: Orygen, Parkville, Australia and Centre for Youth Mental Health, University of Melbourne, Parkville, Australia
+#   - name: Jana M Menssink
+#     address: Orygen, Parkville, Australia and Centre for Youth Mental Health, University of Melbourne, Parkville, Australia
+#   - name: Sonia  Sharmin
+#     address: Orygen, Parkville, Australia and Centre for Youth Mental Health, University of Melbourne, Parkville, Australia
+#   - name: Nic Telford
+#     address: headspace National Youth Mental Health Foundation, Melbourne, Australia
+#   - name: Helen Herrman
+#     address: Orygen, Parkville, Australia and Centre for Youth Mental Health, University of Melbourne, Parkville, Australia
+#   - name: Ian B Hickie
+#     address: Brain and Mind Centre, Youth Mental Health & Technology, Faculty of Medicine & Health, The University of Sydney,  Australia
+#   - name: Cathrine  Mihalopoulos
+#     address: Deakin Health Economics, Institute for Health Transformation, Deakin University, Geelong,  Australia
+#   - name: Debra J Rickwood
+#     address: Faculty of Health, University of Canberra, Australia and headspace National Youth Mental Health Foundation, Melbourne, Australia
+#   - name: Patrick D McGorry
+#     address: Orygen, Parkville, Australia and Centre for Youth Mental Health, University of Melbourne, Parkville, Australia
+#   - name: Sue M Cotton
+#     address: Orygen, Parkville, Australia and Centre for Youth Mental Health, University of Melbourne, Parkville, Australia
 authors: 
-  - prefix: Dr.
-    firstname: Leading
-    particle: van 
-    lastname: Author
-    suffix: III
-    naturename: Poet Laureate
-    degrees: MSc, PhD
-    email: abc@def
+  - firstname: Matthew
+    particle: P 
+    lastname: Hamilton
+    email: matthew.hamilton1@monash.edu
     affiliation: [1,2]
     corresponding: TRUE
-    equalcont: These authors contributed equally to this work.
+  # - prefix: Mr.
+    #suffix: III
+    #naturename: Poet Laureate
+    # degrees: MSc #, PhD
+    #equalcont: These authors contributed equally to this work.
 
-  - firstname: Second
-    lastname: Author
-    affiliation: 2
-    equalcont: These authors contributed equally to this work.
+  - firstname: Caroline
+    lastname: Gao
+    #     email: caroline.gao@orygen.org.au
+    affiliation: [2,3,1]
+
+  - firstname: Glen
+    lastname: Wiesner
+    #     email: glen.wiesner@heartfoundation.org.au
+    affiliation: [4]
+
+  - firstname: Kate  
+    particle: M
+    lastname: Filia
+    #     email: kate.filia@orygen.org.au
+    affiliation: [2,3]
+
+  - firstname: Jana
+    particle: M
+    lastname: Menssink
+    #     email: jana.menssink@orygen.org.au
+    affiliation: [2,3]
+
+  - firstname: Petra
+    lastname: Plencnerova
+    #     email: pplencnerova@headspace.org.au
+    affiliation: [5]
+
+  - firstname: David  
+    lastname: Baker
+    #     email: david.baker@orygen.org.au
+    affiliation: [2,3]
+
+  - firstname: Patrick 
+    particle: D 
+    lastname: McGorry
+    #     email: pat.mcgorry@orygen.org.au
+    affiliation: [2,3]
+
+  - firstname: Alexandra  
+    lastname: Parker
+    #     email: alex.parker@vu.edu.au
+    affiliation: [6,3]
+
+  - firstname: Jonathan  
+    lastname: Karnon
+    #     email: jonathan.karnon@flinders.edu.au
+    affiliation: [7]
+
+  - firstname: Sue
+    particle: M
+    lastname: Cotton
+    #     email: sue.cotton@orygen.org.au
+    affiliation: [2,3]
+
+  - firstname: Cathrine
+    lastname: Mihalopoulos
+    #     email: cathy.mihalopoulos@deakin.edu.au
+    affiliation: [1]
 
@@
     info:
-      orgdiv: Department
-      orgname: Organization
+      orgdiv: School of Public Health and Preventive Medicine
+      orgname: Monash University
     address:
-        street: Street
-        city: City
-        postcode: 100190
-        state: State
-        country: Country
+        #street: "553 St Kilda Road"
+        city: Melbourne
+        #postcode: 3004
+        #state: Victoria
+        country: Australia
   - number: 2
-    corresponding: TRUE
+    corresponding: FALSE
     info:
-      orgname: Other Organisation
-
+      orgname: Orygen
+    address:
+     #   street: "35 Poplar Road"
+        city: Parkville
+        # postcode: 3052
+        #state: Victoria
+        country: Australia
+  - number: 3
+    corresponding: FALSE
+    info:
+      orgdiv: Centre for Youth Mental Health
+      orgname: The University of Melbourne
+    address:
+     #   street: "35 Poplar Road"
+        city: Parkville
+        # postcode: 3052
+    #   state: Victoria
+        country: Australia
+  - number: 4
+    corresponding: FALSE
+    info:
+#      orgdiv: XXXXXXXXXXX
+      orgname: Heart Foundation      
+    address:
+     #   street: "2/850 Collins St"
+        city: Docklands
+        # postcode: 3008
+     #   state: Victoria
+        country: Australia
+  - number: 5
+    corresponding: FALSE
+    info:
+#      orgdiv: XXXXXXXXXXX
+      orgname: headspace National Youth Mental Health Foundation   
+    address:
+    #  #   street: "485 La Trobe St"
+        city: Melbourne
+    #     postcode: 3000
+    #  #   state: Victoria
+        country: Australia     
+  - number: 6
+    corresponding: FALSE
+    info:
+      orgdiv: Institute for Health and Sport
+      orgname: Victoria University 
+    address:
+    #  #   street: "70/104 Ballarat Rd"
+        city: Footscray
+    #     postcode: 3011
+    #  #   state: Victoria
+        country: Australia 
+      # 
+  - number: 7
+    corresponding: FALSE
+    info:
+#      orgdiv: XXXXXXXXXXX
+      orgname: Flinders University   
+    address:
+    #     # street: "182 Victoria Square"     
+        city: Adelaide
+    #     postcode: 5000
+    #  #   state: South Australia
+        country: Australia 
 keywords:  
-  - key
-  - dictionary
-  - word
+  - computational models
+  - ethics of modelling
+  - health economics
+  - mental disorders
+  - open-source models
+  - software frameworks
 
@@
   jel:
-    - "D8"
-    - "H51"
+    - "C63"
+    - "C88"
+    - "I10"
   msc:
-    - "35A01"
-    - "65L10"
+    - "91-08"
 

### 2023-10-23 Reports/Manuscript/Submission_files/Submission.tex
built submission files

--- 2023-10-22 Reports/Manuscript/Submission.tex
@@
 
-\title[Transparent, reusable and updatable computational models]{A prototype software framework for transparent, reusable and updatable computational health economic models}
+\title[Framework for ethical computational models]{A prototype software framework for transparent, reusable and updatable computational health economic models}
 
@@
 
-\author*[1,2]{\pfx{Dr.} \fnm{Leading} \spfx{van} \sur{Author} \sfx{III} \tanm{Poet Laureate} \dgr{MSc, PhD}}\email{\href{mailto:abc@def}{\nolinkurl{abc@def}}}
+\author*[1,2]{\fnm{Matthew} \spfx{P} \sur{Hamilton} }\email{\href{mailto:matthew.hamilton1@monash.edu}{\nolinkurl{matthew.hamilton1@monash.edu}}}
 
-\author[2]{\fnm{Second} \sur{Author} }
+\author[2,3,1]{\fnm{Caroline} \sur{Gao} }
 
-  \affil*[1]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\city{City}, \country{Country}, \postcode{100190}, \state{State}, \street{Street}}}
-  \affil*[2]{\orgname{Other Organisation}}
+\author[4]{\fnm{Glen} \sur{Wiesner} }
+
+\author[2,3]{\fnm{Kate} \spfx{M} \sur{Filia} }
+
+\author[2,3]{\fnm{Jana} \spfx{M} \sur{Menssink} }
+
+\author[5]{\fnm{Petra} \sur{Plencnerova} }
+
+\author[2,3]{\fnm{David} \sur{Baker} }
+
+\author[2,3]{\fnm{Patrick} \spfx{D} \sur{McGorry} }
+
+\author[6,3]{\fnm{Alexandra} \sur{Parker} }
+
+\author[7]{\fnm{Jonathan} \sur{Karnon} }
+
+\author[2,3]{\fnm{Sue} \spfx{M} \sur{Cotton} }
+
+\author[1]{\fnm{Cathrine} \sur{Mihalopoulos} }
+
+  \affil*[1]{\orgdiv{School of Public Health and Preventive Medicine}, \orgname{Monash University}, \orgaddress{\city{Melbourne}, \country{Australia}}}
+  \affil[2]{\orgname{Orygen}, \orgaddress{\city{Parkville}, \country{Australia}}}
+  \affil[3]{\orgdiv{Centre for Youth Mental Health}, \orgname{The University of Melbourne}, \orgaddress{\city{Parkville}, \country{Australia}}}
+  \affil[4]{\orgname{Heart Foundation}, \orgaddress{\city{Docklands}, \country{Australia}}}
+  \affil[5]{\orgname{headspace National Youth Mental Health Foundation}, \orgaddress{\city{Melbourne}, \country{Australia}}}
+  \affil[6]{\orgdiv{Institute for Health and Sport}, \orgname{Victoria University}, \orgaddress{\city{Footscray}, \country{Australia}}}
+  \affil[7]{\orgname{Flinders University}, \orgaddress{\city{Adelaide}, \country{Australia}}}
 
@@
 
-\keywords{key, dictionary, word}
+\keywords{computational models, ethics of modelling, health economics, mental disorders, open-source models, software frameworks}
 
-\pacs[JEL Classification]{D8, H51}
-\pacs[MSC Classification]{35A01, 65L10}
+\pacs[JEL Classification]{C63, C88, I10}
+\pacs[MSC Classification]{91-08}
 
@@
 The decision about what type of software development platform to use must balance ethical considerations and resource constraints (see Table \ref{tab:proscons}).
+
+\begin{table}
+
+\caption{\label{tab:proscons}Implications of choosing commercial modelling software or an open-source programming language for the computational implementation of health economic models}
+\centering
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{7em}>{\raggedright\arraybackslash}p{20em}>{\raggedright\arraybackslash}p{20em}}
+\toprule
+Implications & Commercial modelling software & Open-source programming language\\
+\midrule
+ & (+) Will include tools to efficienty accomplish many common modelling tasks. & (-) Initial development is likely to be time and resource intensive.\\
+
+ & (+) Requires limited or no programming skills. & (+) Over medium term, efficiency savings are possible if:\\
+
+ & (-) Requires model developers and users to purchase software licenses & (i)  artefacts (code and data) from pre-existing models are leveraged; and / or\\
+
+\multirow{-4}{7em}{\raggedright\arraybackslash \textbf{Resources}} &  & (ii)    maintaining and transferring (e.g. to new decision problems / contexts) model.\\
+\cmidrule{1-3}
+\addlinespace[0.3em]
+\multicolumn{3}{c}{\textbf{Transparency}}\\
+\hspace{1em} & (+) Popular tools (e.g. Excel) are readily understood by many. & (+) Easy to publicly share testable source code while selectively restricting access to confidential data.\\
+
+\hspace{1em} & (-) Non seemless integration with scientific manuscript authoring pipelines raises risk of (undetected) transcription errors when reporting results.
+& (+) Easy to make clear who has developed and tested each part.\\
+
+\hspace{1em} &  & (-) Novel code increases likelihood of (undetected) software errors.\\
+
+\addlinespace[0.3em]
+\multicolumn{3}{c}{\textbf{Reusability}}\\
+\hspace{1em} & (+) Files will open and execute correctly for years after project is completed.
+& (-) Potentially fragile – if not maintained / not bundled with all required and correctly versioned dependencies\\
+
+\hspace{1em} &  & (+) Facilitates modular implementations that make complex model representations more tractable.\\
+
+\hspace{1em} &  & (+) Facilitates customised integration with existing data / decision systems.\\
+
+\addlinespace[0.3em]
+\multicolumn{3}{c}{\textbf{Updatability}}\\
+\hspace{1em}\multirow{-7}{7em}{\raggedright\arraybackslash \textbf{Ethical}} & (-) Selective modification with appropriate attribution can be difficult.
+& (-) Facilitates collaborative development and maintenance.\\
+\bottomrule
+\end{tabular}
+\end{table}
 
@@
 \item
-  \textbf{establish socially acceptable user requirements and design specifications} (during CHEM planning);
+  \emph{establish socially acceptable user requirements and design specifications} (during CHEM planning);
 \item
-  \textbf{ensure fitness for purpose} (of CHEM implementation); and
+  \emph{ensure fitness for purpose} (of CHEM implementation); and
 \item
-  \textbf{support socially beneficial use} (on CHEM release).
+  \emph{support socially beneficial use} (on CHEM release).
 \end{enumerate}
@@
 These value judgments influence the assumptions, selection of model features and standards for evidence that shape health economic model projects \citep{HARVARD2020112975}.
-For example, as illustrated in Table \ref{tab:proscons}, project resource constraints may require model developers to make trade-offs when agreeing CHEM \textbf{user requirements and design specifications}.
+For example, as illustrated in Table \ref{tab:proscons}, project resource constraints may require model developers to make trade-offs when agreeing CHEM \emph{user requirements and design specifications}.
 These trade-offs in turn determine how straightforward it is for a CHEM to be subsequently amended to reflect alternative value judgments relating to model conceptualisation and mathematical formalisation (Table \ref{tab:timelygls}).
 
-Modellers have duties both to ensure a computational model is \textbf{fit for purpose} and to provide potential third-party users with the means of assessing its adequacy for their proposed uses \citep{Erdemir2020, Feenstra2022, thompson2019escape, 10.3389/fpubh.2017.00068}.
+Modellers have duties both to ensure a computational model is \emph{fit for purpose} and to provide potential third-party users with the means of assessing its adequacy for their proposed uses \citep{Erdemir2020, Feenstra2022, thompson2019escape, 10.3389/fpubh.2017.00068}.
 However, it is common for health economic models to have serious methodological flaws \citep{carletto_zanuzzi_sammarco_russo_2020, WONDER2015467}; insufficient validation \citep{Ghabri2019, kolovos2017model, haji2013model}, poor reproducibility \citep{Jalali2021, McManus2019, Bermejo2017}; and undeclared errors \citep{Radeva2020}.
@@
 
-A CHEM will have limited \textbf{social benefit} if it is rarely used, if mis-used or when its acceptability and adequacy rapidly decay.
+A CHEM will have limited \emph{social benefit} if it is rarely used, if mis-used or when its acceptability and adequacy rapidly decay.
 Reuse of CHEMs as components of other models can potentially make model development more efficient \citep{Arnold2010, garcia2021cost}.
@@
 
-Taking steps to make computational models \textbf{transparent} is an important part of ethical public health modelling practice \citep{10.3389/fpubh.2017.00068}.
+\begin{table}
+
+\caption{\label{tab:timelygls}Transparent, reusable and updatable (TRU) computational health economic models (CHEMs) are suggestive of ethical modelling practice}
+\centering
+\begin{tabular}[t]{>{}l>{\raggedright\arraybackslash}p{13em}>{\raggedright\arraybackslash}p{13em}>{\raggedright\arraybackslash}p{13em}}
+\toprule
+\multicolumn{1}{c}{\em{\textbf{ }}} & \multicolumn{3}{c}{\em{\textbf{Project team responsibility}}} \\
+\cmidrule(l{3pt}r{3pt}){2-4}
+  & Social acceptability & Fitness for purpose & Beneficial use\\
+\midrule
+\textbf{Transparent} & Modeller judgments, model features and verification checks can be reviewed by third parties.
+& Modeller judgments, model features and verification checks can be reviewed by third parties.
+& Decision-makers can understand the strengths and weakness of models before applying them.\\
+
+\textbf{Reusable} &  & Third party use increases likelihood of errors being identified. & Can inform more decision problems, in more contexts with less duplicative effort.\\
+
+\textbf{Updatable} & \multirow{-2}{13em}{\raggedright\arraybackslash Models can be modified to reflect alternative value judgments.} & Models that are maintained can be validly used for longer.
+& Models can be validly used for longer.\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+Taking steps to make computational models \emph{transparent} is an important part of ethical public health modelling practice \citep{10.3389/fpubh.2017.00068}.
 Guidance on transparency in health economic modelling recommend that model code and data should be clearly documented \citep{Eddy2012}.
@@
 
-A CHEM that is \textbf{reusable} also signals ethical modelling practice.
+A CHEM that is \emph{reusable} also signals ethical modelling practice.
 Although making a CHEM's code, data and documentation publicly available is increasingly considered good practice, it is insufficient to enable model re-use.
@@
 
-Models should be \textbf{updatable} so that they remain valid for longer, evolving as new evidence emerges and the systems being modelled change \citep{Jenkins2021, garcia2021cost}.
+Models should be \emph{updatable} so that they remain valid for longer, evolving as new evidence emerges and the systems being modelled change \citep{Jenkins2021, garcia2021cost}.
 Ensuring that a model is regularly reviewed to identify and implement required improvements is a recommended defence against model validity decay \citep{calder2018computational}.
@@
 
-How \textbf{transparent} a CHEM is can be assessed against the criteria:
+How \emph{transparent} a CHEM is can be assessed against the criteria:
 
@@
 \item
-  \textbf{T1}: Software files (executable code, testing procedures and outcomes and non-confidential data) are available in open access repositories.
+  \emph{T1}: Software files (executable code, testing procedures and outcomes and non-confidential data) are available in open access repositories.
 \item
-  \textbf{T2}: It is easy to see who funded, developed and tested each part of the CHEM and to identify the modelling team's assumptions, judgments and theories about CHEM development and use.
+  \emph{T2}: It is easy to see who funded, developed and tested each part of the CHEM and to identify the modelling team's assumptions, judgments and theories about CHEM development and use.
 \end{itemize}
 
-How \textbf{reusable} a CHEM is can be assessed against the criteria:
+How \emph{reusable} a CHEM is can be assessed against the criteria:
 
@@
 \item
-  \textbf{R1}: Programming practices facilitate both generalisability and transferability.
+  \emph{R1}: Programming practices facilitate both generalisability and transferability.
 \item
-  \textbf{R2}: Licenses restrict only unethical use and allow anyone to ethically reuse model code and non-confidential data, in whole or in part, without charge, and for purposes that include the creation of derivative works.
+  \emph{R2}: Licenses restrict only unethical use and allow anyone to ethically reuse model code and non-confidential data, in whole or in part, without charge, and for purposes that include the creation of derivative works.
 \end{itemize}
 
-How \textbf{updatable} a CHEM is can be assessed against the criteria:
+How \emph{updatable} a CHEM is can be assessed against the criteria:
 
@@
 \item
-  \textbf{U1}: Maintenance infrastructure is in place to support version control and collaboration with model users.
+  \emph{U1}: Maintenance infrastructure is in place to support version control and collaboration with model users.
 \item
-  \textbf{U2}: Each new release of a CHEM is systematically retested, with changes implemented to minimise disruptions for existing model users.
+  \emph{U2}: Each new release of a CHEM is systematically retested, with changes implemented to minimise disruptions for existing model users.
 \end{itemize}
@@
 
-One framework library provides a \textbf{foundation for modular CHEM implementations}.
+One framework library provides a \emph{foundation for modular CHEM implementations}.
 In modular model implementations, modules need to be able to share inputs and outputs with each other and to be run as independent models \citep{barros2023empowering}.
@@
 
-Three framework libraries are designed to help streamline and standardise workflows for \textbf{authoring CHEM modules} from the template module.
+Three framework libraries are designed to help streamline and standardise workflows for \emph{authoring CHEM modules} from the template module.
 The R language supports functional and object-oriented programming paradigms \citep{10.1214/13-STS452}.
@@
 
-A library for \textbf{managing CHEM data} contains tools for supplying CHEM modules with input data ingested from local (i.e., a user's computer) or remote (online repositories) locations, labelling CHEM module datasets and exporting CHEM module data to online repositories.
-A library for \textbf{authoring reproducible analyses} contains tools to help write programs that apply CHEM modules to compatible datasets for the purpose of undertaking health economic analyses.
+A library for \emph{managing CHEM data} contains tools for supplying CHEM modules with input data ingested from local (i.e., a user's computer) or remote (online repositories) locations, labelling CHEM module datasets and exporting CHEM module data to online repositories.
+A library for \emph{authoring reproducible analyses} contains tools to help write programs that apply CHEM modules to compatible datasets for the purpose of undertaking health economic analyses.
 These analysis programs can be either self-documenting (code is integrated with plain English explanations of what it does) or trigger the creation of explanatory documents (e.g., a scientific manuscript).
+
+\begin{table}
+
+\caption{\label{tab:cpkgs}Software framework R libraries}
+\centering
+\begin{tabular}[t]{l>{\raggedright\arraybackslash}m{20em}>{\raggedright\arraybackslash}m{20em}}
+\toprule
+Package & Purpose & R library dependencies\\
+\midrule
+ready4 & Provide a template and novel syntax for modular CHEM implementations and tools for finding interoperable CHEM modules, datasets and reproducible analysis programs.
+& assertthat bib2df dataverse dplyr fs Hmisc kableExtra knitr lifecycle magrittr methods natmanager piggyback purrr readr readxl rlang rmarkdown rvest stats stringi stringr testit testthat tibble tidyRSS tools utils zen4R\\
+ready4fun & Streamline and standardise the authoring and documenting of functions that support transferable and generalisable model algorithms.
+& desc devtools dplyr gert Hmisc knitr lifecycle lubridate magrittr methods piggyback pkgdown purrr readxl ready4 ready4show ready4use rlang sinew stats stringi stringr testit testthat tibble tidyr tools usethis utils xfun\\
+ready4class & Streamline and standardise the authoring and documenting of new interoperable CHEM modules.
+& devtools dplyr fs gtools Hmisc knitr lifecycle magrittr methods purrr ready4 ready4fun ready4show rlang stats stringi stringr testit testthat tibble tidyr usethis utils\\
+ready4pack & Help bundle and disseminate newly created CHEM modules as R libraries that are documented, licensed and quality assured.
+& dataverse dplyr knitr lifecycle magrittr methods purrr ready4 ready4class ready4fun rlang stringr testthat tibble tidyr utils\\
+ready4use & Help manage the labelling and transfer of data between CHEM modules and local and remote data repositories.
+& data.table dataverse dplyr fs Hmisc knitr lifecycle magrittr methods piggyback purrr readxl ready4 ready4show rlang stats stringi stringr testit testthat tibble tidyr utils\\
+\addlinespace
+ready4show & Facilitate the use of CHEM modules in programs to implement integrated and reproducible data ingest, analysis and reporting pipelines.
+& dataverse DescTools dplyr flextable grDevices here Hmisc kableExtra knitr knitrBootstrap lifecycle magrittr methods officer purrr ready4 rlang rmarkdown stringi stringr testthat tibble tidyr utils xtable\\
+\bottomrule
+\end{tabular}
+\end{table}
 
@@
 Some initial outputs from this work are publicly available as development version releases.
+
+\bgroup 
+    \origfigure[H]
+
+\includegraphics[width=400px,]{Figure1} \caption{High level summary of planned implementation of youth mental health economic model}\label{fig:fig1}
+
+    \endfigure
+\egroup
 
@@
 \begin{landscape}
+
+\begin{table}
+
+\caption{\label{tab:checktb}Assessment of a CHEM implementation in youth mental health using Transparent, Reusable and Updatable (TRU) criteria}
+\centering
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{10em}l>{\raggedright\arraybackslash}p{35em}}
+\toprule
+Criterion & Met? & Detail\\
+\midrule
+\textbf{T1 Software files are open access} & Yes & All source code and testing procedures are available in public GitHub repositories, with each code release persistently available in a Zenodo repository.
+As the study dataset contains confidential patient records, it was not published.
+Instead, a synthetic representation of the study dataset is persistently available in a repository in the Harvard Dataverse.
+Data files to support out of sample application of models are published at the same location.\\
+\textbf{T2 Project team contributions and judgments are easily identified} & Yes & All module libraries, programs, and datasets are distributed with citation information.
+Public GitHub repositories detail author code contributions over project development history.
+Model catalogues persistently available on the Harvard Dataverse describe the predictive performance of models under multiple usage regimes.
+Each code library is documented with worked examples of how to apply CHEM modules.
+Analysis and reporting programs are self-documenting.
+Sub-routines for generating reports are documented with README files.\\
+\textbf{R1 Programming practices promote generalisability and transferability} & Yes & CHEMs are written using both functional and object-oriented paradigms.
+Code library documentation websites include hypothetical examples of generalisability (applying study algorithm to estimate mapping models from new data with the same predictor and outcome variables) and transferability (adapting study algorithm to develop mapping models from datasets with different predictor variables and outcomes measured with a different utility instrument).\\
+\textbf{R2 Licenses restrict only unethical reuse} & Yes & All code is distributed using GPL-3 licenses.
+Datasets use an amended version of template terms provided by Harvard Dataverse, allowing reuse of data subject to some ethical restrictions (e.g., use in efforts to reidentify study participants is prohibited).\\
+\textbf{U1 Maintenance infrastructure is in place} & Yes & All code is version controlled using git and GitHub, with semantic versioning.
+Each code library has a specified maintainer and guidance for potential code contributors is available on the project website.\\
+\addlinespace
+\textbf{U2 New releases are systematically retested and deprecated} & Partial & Continuous integration is used for all code libraries, primarily for acceptance testing.
+Only limited use is made of unit testing.
+Retired library code is deprecated using tools from the lifecycle R library.
+Library documentation articles and datasets are also deprecated.\\
+\bottomrule
+\end{tabular}
+\end{table}
 
@@
 \newpage
-
-\hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
-
-\newpage
-
-\hypertarget{tables-and-figures}{%
-\subsection*{Tables and figures}\label{tables-and-figures}}
-\addcontentsline{toc}{subsection}{Tables and figures}
-
-\begin{table}
-
-\caption{\label{tab:proscons}Implications of choosing commercial modelling software or an open-source programming language for the computational implementation of health economic models}
-\centering
-\begin{tabular}[t]{>{\raggedright\arraybackslash}p{7em}>{\raggedright\arraybackslash}p{20em}>{\raggedright\arraybackslash}p{20em}}
-\toprule
-Implications & Commercial modelling software & Open-source programming language\\
-\midrule
- & (+) Will include tools to efficienty accomplish many common modelling tasks. & (-) Initial development is likely to be time and resource intensive.\\
-
- & (+) Requires limited or no programming skills. & (+) Over medium term, efficiency savings are possible if:\\
-
- & (-) Requires model developers and users to purchase software licenses & (i)  artefacts (code and data) from pre-existing models are leveraged; and / or\\
-
-\multirow{-4}{7em}{\raggedright\arraybackslash \textbf{Resources}} &  & (ii)    maintaining and transferring (e.g. to new decision problems / contexts) model.\\
-\cmidrule{1-3}
-\addlinespace[0.3em]
-\multicolumn{3}{c}{\textbf{Transparency}}\\
-\hspace{1em} & (+) Popular tools (e.g. Excel) are readily understood by many. & (+) Easy to publicly share testable source code while selectively restricting access to confidential data.\\
-
-\hspace{1em} & (-) Non seemless integration with scientific manuscript authoring pipelines raises risk of (undetected) transcription errors when reporting results.
-& (+) Easy to make clear who has developed and tested each part.\\
-
-\hspace{1em} &  & (-) Novel code increases likelihood of (undetected) software errors.\\
-
-\addlinespace[0.3em]
-\multicolumn{3}{c}{\textbf{Reusability}}\\
-\hspace{1em} & (+) Files will open and execute correctly for years after project is completed.
-& (-) Potentially fragile – if not maintained / not bundled with all required and correctly versioned dependencies\\
-
-\hspace{1em} &  & (+) Facilitates modular implementations that make complex model representations more tractable.\\
-
-\hspace{1em} &  & (+) Facilitates customised integration with existing data / decision systems.\\
-
-\addlinespace[0.3em]
-\multicolumn{3}{c}{\textbf{Updatability}}\\
-\hspace{1em}\multirow{-7}{7em}{\raggedright\arraybackslash \textbf{Ethical}} & (-) Selective modification with appropriate attribution can be difficult.
-& (-) Facilitates collaborative development and maintenance.\\
-\bottomrule
-\end{tabular}
-\end{table}
-\newpage
-
-\begin{table}
-
-\caption{\label{tab:timelygls}Transparent, reusable and updatable (TRU) computational health economic models (CHEMs) are suggestive of ethical modelling practice}
-\centering
-\begin{tabular}[t]{>{}l>{\raggedright\arraybackslash}p{13em}>{\raggedright\arraybackslash}p{13em}>{\raggedright\arraybackslash}p{13em}}
-\toprule
-\multicolumn{1}{c}{\em{\textbf{ }}} & \multicolumn{3}{c}{\em{\textbf{Project team responsibility}}} \\
-\cmidrule(l{3pt}r{3pt}){2-4}
-  & Social acceptability & Fitness for purpose & Beneficial use\\
-\midrule
-\textbf{Transparent} & Modeller judgments, model features and verification checks can be reviewed by third parties.
-& Modeller judgments, model features and verification checks can be reviewed by third parties.
-& Decision-makers can understand the strengths and weakness of models before applying them.\\
-
-\textbf{Reusable} &  & Third party use increases likelihood of errors being identified. & Can inform more decision problems, in more contexts with less duplicative effort.\\
-
-\textbf{Updatable} & \multirow{-2}{13em}{\raggedright\arraybackslash Models can be modified to reflect alternative value judgments.} & Models that are maintained can be validly used for longer.
-& Models can be validly used for longer.\\
-\bottomrule
-\end{tabular}
-\end{table}
-\newpage
-
-\begin{table}
-
-\caption{\label{tab:cpkgs}Software framework R libraries}
-\centering
-\begin{tabular}[t]{l>{\raggedright\arraybackslash}m{20em}>{\raggedright\arraybackslash}m{20em}}
-\toprule
-Package & Purpose & R library dependencies\\
-\midrule
-ready4 & Provide a template and novel syntax for modular CHEM implementations and tools for finding interoperable CHEM modules, datasets and reproducible analysis programs.
-& assertthat bib2df dataverse dplyr fs Hmisc kableExtra knitr lifecycle magrittr methods natmanager piggyback purrr readr readxl rlang rmarkdown rvest stats stringi stringr testit testthat tibble tidyRSS tools utils zen4R\\
-ready4fun & Streamline and standardise the authoring and documenting of functions that support transferable and generalisable model algorithms.
-& desc devtools dplyr gert Hmisc knitr lifecycle lubridate magrittr methods piggyback pkgdown purrr readxl ready4 ready4show ready4use rlang sinew stats stringi stringr testit testthat tibble tidyr tools usethis utils xfun\\
-ready4class & Streamline and standardise the authoring and documenting of new interoperable CHEM modules.
-& devtools dplyr fs gtools Hmisc knitr lifecycle magrittr methods purrr ready4 ready4fun ready4show rlang stats stringi stringr testit testthat tibble tidyr usethis utils\\
-ready4pack & Help bundle and disseminate newly created CHEM modules as R libraries that are documented, licensed and quality assured.
-& dataverse dplyr knitr lifecycle magrittr methods purrr ready4 ready4class ready4fun rlang stringr testthat tibble tidyr utils\\
-ready4use & Help manage the labelling and transfer of data between CHEM modules and local and remote data repositories.
-& data.table dataverse dplyr fs Hmisc knitr lifecycle magrittr methods piggyback purrr readxl ready4 ready4show rlang stats stringi stringr testit testthat tibble tidyr utils\\
-\addlinespace
-ready4show & Facilitate the use of CHEM modules in programs to implement integrated and reproducible data ingest, analysis and reporting pipelines.
-& dataverse DescTools dplyr flextable grDevices here Hmisc kableExtra knitr knitrBootstrap lifecycle magrittr methods officer purrr ready4 rlang rmarkdown stringi stringr testthat tibble tidyr utils xtable\\
-\bottomrule
-\end{tabular}
-\end{table}
-\newpage
-
-\begin{table}
-
-\caption{\label{tab:checktb}Assessment of a CHEM implementation in youth mental health using Transparent, Reusable and Updatable (TRU) criteria}
-\centering
-\begin{tabular}[t]{>{\raggedright\arraybackslash}p{10em}l>{\raggedright\arraybackslash}p{35em}}
-\toprule
-Criterion & Met? & Detail\\
-\midrule
-\textbf{T1 Software files are open access} & Yes & All source code and testing procedures are available in public GitHub repositories, with each code release persistently available in a Zenodo repository.
-As the study dataset contains confidential patient records, it was not published.
-Instead, a synthetic representation of the study dataset is persistently available in a repository in the Harvard Dataverse.
-Data files to support out of sample application of models are published at the same location.\\
-\textbf{T2 Project team contributions and judgments are easily identified} & Yes & All module libraries, programs, and datasets are distributed with citation information.
-Public GitHub repositories detail author code contributions over project development history.
-Model catalogues persistently available on the Harvard Dataverse describe the predictive performance of models under multiple usage regimes.
-Each code library is documented with worked examples of how to apply CHEM modules.
-Analysis and reporting programs are self-documenting.
-Sub-routines for generating reports are documented with README files.\\
-\textbf{R1 Programming practices promote generalisability and transferability} & Yes & CHEMs are written using both functional and object-oriented paradigms.
-Code library documentation websites include hypothetical examples of generalisability (applying study algorithm to estimate mapping models from new data with the same predictor and outcome variables) and transferability (adapting study algorithm to develop mapping models from datasets with different predictor variables and outcomes measured with a different utility instrument).\\
-\textbf{R2 Licenses restrict only unethical reuse} & Yes & All code is distributed using GPL-3 licenses.
-Datasets use an amended version of template terms provided by Harvard Dataverse, allowing reuse of data subject to some ethical restrictions (e.g., use in efforts to reidentify study participants is prohibited).\\
-\textbf{U1 Maintenance infrastructure is in place} & Yes & All code is version controlled using git and GitHub, with semantic versioning.
-Each code library has a specified maintainer and guidance for potential code contributors is available on the project website.\\
-\addlinespace
-\textbf{U2 New releases are systematically retested and deprecated} & Partial & Continuous integration is used for all code libraries, primarily for acceptance testing.
-Only limited use is made of unit testing.
-Retired library code is deprecated using tools from the lifecycle R library.
-Library documentation articles and datasets are also deprecated.\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\newpage
-
-\bgroup 
-    \origfigure[H]
-
-\includegraphics[width=400px,]{../Data/images/Figure1} \caption{High level summary of planned implementation of youth mental health economic model}\label{fig:fig1}
-
-    \endfigure
-\egroup 
-\newpage
-
-\newpage
 \appendix

### 2023-10-23 setup.R

@@ -64,7 +64,7 @@ X@figures_in_body_lgl <- F
 # Make manual edits of Markdown files
 #authorReport(X, consent_1L_chr = "Y") # For Preprint
 params_ls <- list(X = X)
-params_ls$X@figures_in_body_lgl <- params_ls$X@tables_in_body_lgl <- F
+#params_ls$X@figures_in_body_lgl <- params_ls$X@tables_in_body_lgl <- F
 rmarkdown::render(paste0("Markdown/Manuscript/Parent_",
                          "PDF",#
                          "/",

### 2024-01-24 R/SAFETY_DEPRECATED.R
more pruning

@@ -1,70 +1,0 @@
-df <- tibble::tibble(Package = c("ready4",
-                                 "ready4fun",
-                                 "ready4class",
-                                 "ready4pack",
-                                 "ready4use",
-                                 "ready4show"),
-                     # Version = Package %>%
-                     #   purrr::map_chr(~utils::packageDescription(.x) %>%
-                     #                    purrr::pluck("Version")),
-                     Focus = c("Syntax and template",
-                               "Modules",
-                               "Functions",
-                               "Libraries",
-                               "Data",
-                               "Analysis and reporting"),
-                     `T` = c("3","2-3","2-3","1","1-2","2,4,6"), 
-                     I = c("","4","","1-3","",""),
-                     M = c("3","","2","1-2","1",""),
-                     E = c("", "1","1-2","1","3",""),
-                     L = c("","","","1,3","2-3",""),
-                     Y = c("","","","","","1-2"),
-                     `Depends on` = Package %>%
-                       purrr::map(~ {
-                         utils::packageDescription(.x) %>%
-                           `[`(c("Depends", "Imports")) %>%
-                           purrr::map(~{
-                             if(is.null(.x)){
-                               character(0)
-                             }else{
-                               .x %>%
-                                 strsplit(",\\n") %>%
-                                 purrr::flatten_chr() %>%
-                                 purrr::map(~strsplit(.x,", ") %>%
-                                              purrr::flatten_chr()) %>%
-                                 purrr::flatten_chr() %>% sort() %>%
-                                 purrr::discard(~startsWith(.x,"R "))
-                             }
-                           }) %>%
-                           purrr::flatten_chr() %>%
-                           unique() %>%
-                           sort() %>%
-                           purrr::map_chr(~{
-                             updated_1L_chr <- stringr::str_replace_all(.x,"\\n"," ")
-                             problem_idx_1L_chr <- stringr::str_locate(updated_1L_chr," ")[1,1] %>%
-                               unname()
-                             if(!is.na(problem_idx_1L_chr))
-                               updated_1L_chr <- updated_1L_chr %>%
-                               stringr::str_sub(end = problem_idx_1L_chr-1)
-                             updated_1L_chr %>% 
-                               trimws(which = "left") 
[…]

### 2024-01-24 Markdown/Manuscript/Child_RMDs/Clippings.Rmd
extracted ethics component

@@
 ---
+<!-- Functions to implement model algorithms can be associated with a module via . -->
+
+<!-- to provide tools for authoring CHEMs, supplying those CHEMs with data and using CHEMs to implement reproducible modelling analyses. -->
+
+<!-- The ready4pack library depends on two other module authoring libraries. <!-- MOVED CONTENT -->
+
+<!-- Each CHEM module authored with the ready4 framework will include both a data structure (specifying the required properties of data that can validly be supplied to a module) and a set of algorithms (specifying the operations that can be performed on data contained in a module instance).
+-->
+
+<!-- development version -->
+
+<!-- Talk about DARTH (https://doi.org/10.1007/s40273-019-00837-x )/ BCEA -->
 

### 2024-01-24 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
close to submission update - except tables
missing tables
one table to go
extracted ethics component

@@
 
-(i)	propose core ethical responsibilities for CHEM developers and criteria for assessing ethical CHEM implementations;
+(i)	describe a prototype software framework we have developed to support the ethical implementation of CHEMs; and
+<!-- propose a set of ethical responsibilities for CHEM project teams and criteria for assessing ethical CHEM implementations; -->
 
-(ii) describe a prototype software framework we have developed to support the ethical implementation of CHEMs; and
+<!-- (ii)  -->
 

### 2024-01-24 Markdown/Manuscript/Child_RMDs/MS_Cndl_Tabs_Not_In_Body.Rmd
extracted ethics component

@@
 
-```{r, child = '../Child_RMDs/MS_Tables_1.Rmd', echo=FALSE}
-```
+<!-- # ```{r, child = '../Child_RMDs/MS_Tables_1.Rmd', echo=FALSE} -->
+<!-- # ``` -->
+<!-- # \newpage -->
+<!-- # ```{r, child = '../Child_RMDs/MS_Tables_2.Rmd', echo=FALSE} -->
+<!-- ``` -->
+
 \newpage
-```{r, child = '../Child_RMDs/MS_Tables_2.Rmd', echo=FALSE}
-```
-\newpage
+
 ```{r, child = '../Child_RMDs/MS_Tables_3.Rmd', echo=FALSE}
 ```
+
 \newpage
+
 ```{r, child = '../Child_RMDs/MS_Tables_4.Rmd', echo=FALSE}

### 2024-01-24 Markdown/Manuscript/Child_RMDs/MS_Conclusion.Rmd
one table to go
extracted ethics component

@@
 `r ifelse(is.na(params$X@conclusion_1L_chr),"",params$X@conclusion_1L_chr)` 
-We have identified criteria that can be used to systematically assess the extent to which the computational implementation of health economic models adheres to transparency, reusability and updatability criteria.
-We have developed a prototype software framework that can support the implementation of CHEMs that largely meet these criteria.
+<!-- We have identified criteria that can be used to systematically assess the extent to which the computational implementation of health economic models adheres to transparency, reusability and updatability criteria.
+-->
+We have developed a prototype software framework that can support the implementation of CHEMs that largely meet explicit criteria for CHEM transparency, reusability and updataility.
 Our framework can be used as a prototype for developing future software frameworks to support ethical implementation of CHEMs.
+Barriers to ethical CHEM practice arising from resource constraints should be addressed by research funders.

### 2024-01-24 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
extracted ethics component

@@
 
-<!-- Talk about DARTH (https://doi.org/10.1007/s40273-019-00837-x )/ BCEA -->
-Ethical practice is a core expectation of health researchers and computational methods underpin most quantitative research, yet an understanding of what constitutes ethical public health modelling practice is underdeveloped [@10.3389/fpubh.2017.00068].
+<!-- Ethical practice is a core expectation of health researchers and computational methods underpin most quantitative research, yet an understanding of what constitutes ethical public health modelling practice is underdeveloped [@10.3389/fpubh.2017.00068].
 We have addressed this gap with our proposed responsibilities for model developers and funders, enabling CHEM attributes and CHEM implementation assessment criteria.
-
-<!-- The less numerous and more focused assessment criteria we propose may potentially be more tractable to implement in reviews of models authored by third parties and as the basis for designing software frameworks to support ethical computational model implementation.
 -->
 
-<!-- Two issues for funders - allow support for beneficial use, foster viable communities. -->
-
-Currently, many if not most existing CHEMs are insufficiently transparent [@Jalali2021; @McManus2019; @Bermejo2017; @Ghabri2019], not reusable [@Feenstra2022; @Emerson2019], nor updatable [@Sampson2017; @10.3389/fpubh.2022.899874].
-<!-- DELETION --> Addressing these issues will require changes to the tools, practices and funding underpinning health economic model development.
+<!-- Currently, many if not most existing CHEMs are insufficiently transparent [@Jalali2021; @McManus2019; @Bermejo2017; @Ghabri2019], not reusable [@Feenstra2022; @Emerson2019], nor updatable [@Sampson2017; @10.3389/fpubh.2022.899874].
+Addressing these issues will require changes to the tools, practices and funding underpinning health economic model development.
+-->
 
@@
 However, better tools alone are insufficient and policy and institutional changes are also required.
-Reducing waste in research is a core responsibility of research funders [@chalmers2014increase] and funding the development of CHEMs that are not adequately understood, reused or updated is wasteful.
+<!-- Reducing waste in research is a core responsibility of research funders [@chalmers2014increase] and funding the development of CHEMs that are not adequately understood, reused or updated is wasteful.
 Existing incentive structures for health economists generally do not promote facilitating peers to reuse their work and funding is rarely adequate to maintain and routinely update a model.
@@
 Development of software frameworks to support ethical CHEM implementations could enable and enhance each of these strategies.
-
-A future software framework for ethical CHEMs would ideally incorporate a base set of features useful to developers of computational models across all domains of public health and health economics, with the capability for community-led extensions that are tailored to the needs of modellers focused on specific health-conditions.
+--> A future software framework for ethical CHEMs would ideally incorporate a base set of features useful to developers of computational models across all domains of public health and health economics, with the capability for community-led extensions that are tailored to the needs of modellers focused on specific health-conditions.
 Such approaches will likely be important to ensure a sufficient potential user-base to make CHEM software frameworks sustainable.

### 2024-01-24 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
extracted ethics component

@@
 
-<!-- Add intro text -->
 We are using the ready4 software framework to implement multiple transparent, reusable and updatable CHEMs in youth mental health (see Figure \@ref(fig:fig1)).
@@
 
-We created a checklist (Table \@ref(tab:checktb)) that we used to subjectively assess these study outputs against TRU criteria.
+We created a checklist (Table \@ref(tab:checktb)) that we used to subjectively assess these study outputs against <!-- Edit_start -->explicit criteria for assessing transparent, reusable and updatable CHEMs that we have previously developed (add REF) <!-- Edit_end -->.
 For each criterion, we provided a global assessment of whether it was met using the responses “yes”, “no” or “partial”.

### 2024-01-24 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
extracted ethics component

@@
 
-To support the development of CHEMs that meet TRU assessment criteria, we have created a prototype software framework called ready4.
+To support the development of CHEMs that are Transparent, Reusable and Updatable (TRU),<!-- assessment criteria,  --> we have created a prototype software framework called ready4.
 The software framework aims to provide a toolkit for: (i) enabling modular implementation of CHEMs; (ii) authoring and documenting CHEM modules; (iii) managing the labelling and transfer of CHEM input and output data; and (iv) authoring reproducible analyses that apply CHEMs to compatible data.
@@
 To achieve these goals, we have implemented the software framework as R [@RCORE2022] code libraries that integrate with a number of online services and which are supported by a documentation website.
-<!-- We have designed this framework to enable ethical computational implementations of health economic models that are both open-source (for transparency and reusability) and modular (for reusability and updatability).
-The framework aims to support the standardization and interoperability that are core enablers of implementing a modular and open source approaches.
--->
 
@@
 
-<!-- Functions to implement model algorithms can be associated with a module via . -->
-
-<!-- to provide tools for authoring CHEMs, supplying those CHEMs with data and using CHEMs to implement reproducible modelling analyses. -->
-
-<!-- The ready4pack library depends on two other module authoring libraries. <!-- MOVED CONTENT -->
-
-<!-- Each CHEM module authored with the ready4 framework will include both a data structure (specifying the required properties of data that can validly be supplied to a module) and a set of algorithms (specifying the operations that can be performed on data contained in a module instance).
--->
-
-<!-- development version -->
-
 A library for *managing CHEM data* contains tools for supplying CHEM modules with input data ingested from local (i.e., a user's computer) or remote (online repositories) locations, labelling CHEM module datasets and exporting CHEM module data to online repositories.
@@
 Framework libraries are designed to be used in conjunction with a number of third-party online services that we established and configured accounts with.
-<!-- To facilitate its application to our youth mental health project, we established and configured accounts with these required services (see Availability of data and materials). -->
 

### 2024-01-24 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
one table to go
extracted ethics component

@@
 
-Health economics is a discipline concerned with problems that arise due to scarce resources, such as how to value health and healthcare, allocate healthcare budgets and configure health services [@wagstaff2012four].
+<!-- Health economics is a discipline concerned with problems that arise due to scarce resources, such as how to value health and healthcare, allocate healthcare budgets and configure health services [@wagstaff2012four].
 In seeking to solve these problems, health economists typically use models which are simplified and selective representations of systems that are believed to influence human health.
@@
 However, the ease of independently assessing the validity of this assumption depends in part on how a health economic model has been implemented computationally.
-<!-- through execution of a computer program that applies the computational model to selected input data). -->
-<!-- the execution of a computer program that applies a computational model to compatible data inputs (e.g., parameter values) and performs a sequence of numeric calculations. -->
-<!-- the predictions reported in health economic studies are now almost always -->
+-->
 
-The set of software files implementing a health economic model's structure, data and algorithms can be called a computational health economic model (CHEM).
+<!-- The set of software files implementing a health economic model's structure, data and algorithms can be called a computational health economic model (CHEM).
 CHEMs can be developed using commercial modelling software or open-source programming languages such as Python [@python2009] or R [@RCORE2022].
-An advantage of commercial modelling software is that users often require no or limited programming skills to develop and apply CHEMs.
+An advantage of commercial modelling software is that users often require limited or no programming skills to develop and apply CHEMs.
 However, open-source software programming languages may facilitate the development of CHEMs that are more transparent, reusable and updatable [@incerti2019r; @Pouwels2022].
 The decision about what type of software development platform to use must balance ethical considerations and resource constraints (see Table \@ref(tab:proscons)).
-
-<!-- modelling team value judgments about priority CHEM features and the skills, resource and time constraints within which a CHEM project needs to be delivered -->
+-->
 
@@
 
-Open-source CHEMs remain rare [@Feenstra2022; @Emerson2019].
+<!-- Open-source CHEMs remain rare [@Feenstra2022; @Emerson2019].
 The software used to develop CHEMs was identified as a barrier to open-source model implementations by participants in a 2020 survey of health economists [@Pouwels2022].
 Other reported barriers relate to difficulties in generalising models, updating models and transferring model data, concerns about the level of public access and lack of interest from decision-makers, and legal, confidentiality and security considerations [@Pouwels2022].
-<!-- Additional resources, skills and tools may be required to overcome a number of barriers to greater health economist adoption of open-source development. -->
-<!-- A major consideration in open-source software development, is the selection of an appropriate software framework.  -->
-<!-- on considerations such as model comprehensiveness, generalisability, reproducibility and transferability -->
-<!-- Although there appears to be in principle support from many health economists for greater use of open source health economic models (OSHEMs)  [@Pouwels2022], actual implementations are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022].
-Barriers to adoption of OSHEMs include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations [@Pouwels2022; @Wu2019].
-Adherence to good practice guidance is an essential requirement for healthcare modelling [@Erdemir2020],  -->
+-->
 
-Better software frameworks could potentially help address some of the barriers to open-source CHEM development.
+<!-- Better software frameworks could potentially help address some of the barriers to open-source CHEM development.  -->
 A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users [@myllarniemi2018development].
@@
 
-<!-- We are developing a model to explore multiple economic questions relating to the mental health of young people aged 12 to 25.   -->
-<!-- When making choices about how to implement this health economic model computationally, we wished to facilitate ethical development and use. -->
-
-A high-level software framework for implementing open-source CHEMs in R has previously been developed with the primary aim of improving model transparency [@alarid2019need].
+A high-level software framework for implementing open-source <!-- Modification_start -->Computational Health Economic Models (CHEMs)<!-- Modification_end --> in R has previously been developed with the primary aim of improving model transparency [@alarid2019need].
 However, to gain widespread adoption, a software framework for CHEMs may need to provide tools to help model developers meet a broader range of ethical practice requirements.
 There are multiple challenges to overcome.
-Firstly, the ethical responsibilities of public health computational modellers remain poorly understood <!-- and inadequately fulfilled  [@pliakos2021ethics; @thompson2022escape;]-->[@10.3389/fpubh.2017.00068] and the computational modelling landscape is changing fast [@calder2018computational].
+Firstly, <!-- the ethical responsibilities of public health computational modellers remain poorly understood [@10.3389/fpubh.2017.00068] and  -->the computational modelling landscape is changing fast [@calder2018computational].
 Secondly, software frameworks can be challenging and time consuming to create and may become excessively complex over time [@edwin2014software].
 Thirdly, software frameworks can be difficult to learn, often requiring model developers to undergo specialist training [@myllarniemi2018development].
-
-<!-- a software framework is unlikely to be widely adopted unless the benefits to developers outweigh the costs associated with using it. -->
-<!-- However, guidance on developing, selecting and using software frameworks for ethical CHEM implementations is scarce. -->
-<!--  -->
-<!-- Transparency has been proposed as one of the core ethical responsibilities of public health computational modellers [@10.3389/fpubh.2017.00068].  -->
-<!-- Although computational models are widely used to inform health policy and system design [@dakin2015influence; @Erdemir2020; @LO2022100570; @Christene006827], -->

### 2024-01-24 Markdown/Manuscript/Child_RMDs/MS_Tables.Rmd
extracted ethics component

--- 2023-01-23 Markdown/Manuscript/Child_RMDs/MS_Tables.Rmd
@@
 if(params$X@tables_in_body_lgl){
-  child_docs_ls <- list(one = "../Child_RMDs/MS_Tables_1.RMD",
-                        two = "../Child_RMDs/MS_Tables_2.RMD",
-                        three = "../Child_RMDs/MS_Tables_3.RMD")
+  child_docs_ls <- list(
+    one = NULL,
+    # "../Child_RMDs/MS_Tables_1.Rmd",
+                        two = NULL,
+    # "../Child_RMDs/MS_Tables_2.Rmd",
+                        three = "../Child_RMDs/MS_Tables_3.Rmd",
+                        four = "../Child_RMDs/MS_Tables_4.Rmd")
 }else{
     child_docs_ls <- list(one = NULL,
-                      two = NULL)
+                          two = NULL,
+                          three = NULL,
+                          four = NULL)
 }

### 2024-01-24 setup.R

@@ -10,7 +10,7 @@ X <- Ready4showSynopsis(#background_1L_chr = "Our study is entirely fictional.",
                         ethics_1L_chr = "Software framework development did not involve human subject research and was not ethically reviewed. The utility mapping worked example is a previously reported study that was reviewed and granted approval by the University of Melbourne’s Human Research Ethics Committee, and the local Human Ethics and Advisory Group (1645367.1).",
                         funding_1L_chr = "Software framework development was funded by Orygen, VicHealth, Victoria University and an Australian Government Research Training Program (RTP) Scholarship. The utility mapping study used as a worked example was funded by the National Health and Medical Research Council (NHMRC, APP1076940), Orygen and headspace.",
                         #interval_chr = "three months",
-                        keywords_chr = c("computational models", "ethics of modelling", "health economics", "mental disorders", "open-source models", "software frameworks"),
+                        keywords_chr = c("computational models", "health economics", "mental disorders", "open-source models", "software frameworks"),
                         outp_formats_chr = "PDF",
                         #sample_desc_1L_chr = "The study sample is fake data that pretends to be young people aged 12 to 25 years who attended Australian primary care services for mental health related needs between November 2019 to August 2020.",
                         title_1L_chr = "A prototype software framework for transparent, reusable and updatable computational health economic models")
@@ -37,17 +37,11 @@ X <- renewSlot(X,
                "abstract_args_ls",
                {
                  args_ls <- X@abstract_args_ls
-                 args_ls$abstract_ls <- list(Summary = "Most health economic analyses are undertaken with the aid of computers. However, the ethical dimensions of implementing health economic models as software (or computational health economic models (CHEMs)) are poorly understood. 
-                                                        We propose that developers and funders of CHEMs share ethical responsibilities to (i) establish socially acceptable user requirements and design specifications; (ii) ensure fitness for purpose; and (iii) support socially beneficial use. 
-                                                        We further propose that a transparent (T), reusable (R) and updatable (U) CHEM is suggestive of a project team that has largely fulfilled these responsibilities.
-                                                        We propose six criteria for assessing CHEMs: (T1) software files are open access; (T2) project team contributions and judgments are easily identified; 
-                                                        (R1) programming practices promote generalisability and transferability; (R2) licenses restrict only unethical reuse; (U1) maintenance infrastructure is in place; and 
-                                                        (U2) new releases are systematically retested and appropriately deprecated.
-                                                        To facilitate CHEMs that meet TRU criteria, we have developed a prototype software framework in the open-source programming language R.
[…]

### 2024-02-16 Markdown/Manuscript/Child_RMDs/Clippings.Rmd
minor edits to body

@@
 
-Computational models, particularly those addressing economic topics, have become essential tools for health policy development [@dakin2015influence; @Erdemir2020].
-Although influential and widely used, health economic models typically have a number of limitations that at best restrict their usefulness and which in some cases may facilitate harmful misuse.
-
 There is a strong case for making health economists more accountable for the appropriate use and social acceptability of their models.
@@
 
-The resource and skills intensive undertaking of modelling could be made more tractable if it was easier for health economists to re-use each other's models [@Arnold2010].
-However, as many health economic models are owned by pharmaceutical companies and consultancies, commercial considerations can limit the reuse of models and their constituent code and data [@Feenstra2022].
-Legal and ethical issues such as privacy and confidentiality requirements further limit public release of some model artefacts [@Pouwels2022].
-Transferring a health economic model developed for one jurisdiction for application in another typically involves retaining some features and updating others [@barbieri2010international].
-However, models do not always make implementation choices (for example, use of concepts with standardised meanings across jurisdictions<!-- [@garcia2021cost] -->, supplying context specific data as replaceable data-packs and distributing source code under licenses that allow derivative works) that facilitate model transferability.
+, supplying context specific data as replaceable data-packs and distributing source code under licenses that allow derivative works) that facilitate model transferability.
 
@@
 The career trajectories of health economists can also mitigate against adequate maintenance of a model, it being relatively common for model authors to have moved on from the team that owns the model and / or from working on the health condition for which the model was developed.
-
-A potential strategy for improving model accountability, reusability and updatability is to make models both modular and open-source.
-
-A modular model is constructed from multiple reusable and replaceable sub-models (modules) [@pan2021modular].
-Modules can share inputs and outputs with other modules or can be run as independent models [@barros2023empowering].
-Advantages of modular models include feasibility (large projects are broken into smaller tasks, with each component independently developed and tested) and flexibility (making it easier to selectively replace or update specific parts of a model and to scale up or down the level of granularity) [@pan2021modular].
-Modular approaches are currently being used to facilitate the development of complex computational models in disciplines such as biology [@pan2021modular], ecology [@barros2023empowering] and neuroscience [@frazier2022robust].
-In health economics the related and enabling concept of reference models has been recommended [@Afzali2013], but peer reviewed studies describing modular health economic models remain relatively rare, though examples exist in infectious disease [@Trauer2017] and cardiology [@Urach2013].
-
-Modular models provide an opportunity for multiple modelling teams to contribute to, test and reuse models.
-To enhance this capacity, modular models may be implemented as open source projects that give others liberal permissions to access and use model source code and data [@pan2021modular; @barros2023empowering; @frazier2022robust].
-Although there appears to be in principle support from many health economists for greater use of open source health economic models (OSHEMs)  [@Pouwels2022], actual implementations are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022].
-Barriers to adoption of OSHEMs include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations [@Pouwels2022; @Wu2019].
-Adherence to good practice guidance is an essential requirement for healthcare modelling [@Erdemir2020], but guidelines for implementing OSHEMs remain scarce, piecemeal and need improving [@Sampson2019].
 

### 2024-02-16 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
minor edits to body

--- 2023-10-08 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
@@
 
-(i)	proposed criteria for assessing ethical CHEM implementations;
-
-(ii) a prototype software framework for the ethical implementation of CHEMs; and
-
-(iii)	how the software framework is being used to develop an open-source CHEM in youth mental health, with an initial focus on valuing health outcomes.
+(i)	a prototype software framework we have developed to support the development of modular and open source CHEMs; and
+<!-- propose a set of ethical responsibilities for CHEM project teams and criteria for assessing ethical CHEM implementations; -->
+<!-- (ii)  -->
+(ii)	how we have applied that software framework to develop and share an initial set of modules for a economic model of youth mental health.

### 2024-02-16 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
minor edits to body

@@
 
-To support the development of CHEMs that are Transparent, Reusable and Updatable (TRU),<!-- assessment criteria,  --> we have created a prototype software framework called ready4.
+## Purpose
+The overarching goal of our software framework, which we call ready4, is to support the development of CHEMs that meet explicit criteria for transparency, reusability and updatability.
+We have describe these criteria elsewhere [@ethicsCHEMS2024], but briefly they are: software files are open access, developer contributions are easily identified, programming practices promote selective reuse, licenses restrict only unethical reuse, maintenance infrastructure is in place and systematic retesting and deprecation with each new release.
+
+## User requirements
+
+1) Provide a standardised template model module and programming syntax.
+
+2) Develop consolidated project documentation and provide tools to find model modules, datasets and study replication programs.
+
+3) Author, document and share model modules, integrating with online services for open source software development
+
+4) Ingest, label and share model data, integrating with online services for open science data archiving.
+
+5) Implement integrated and reproducible data ingest, analysis and reporting pipelines.
+
+## XXXYYY
 The software framework aims to provide a toolkit for: (i) enabling modular implementation of CHEMs; (ii) authoring and documenting CHEM modules; (iii) managing the labelling and transfer of CHEM input and output data; and (iv) authoring reproducible analyses that apply CHEMs to compatible data.

### 2024-02-16 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
minor edits to body

@@
 
+<!-- Import_start -->Computational models, particularly those addressing economic topics, have become essential tools for health policy development [@dakin2015influence; @Erdemir2020].
+Although influential and widely used, health economic models can be skills and resource intensive to undertake.<!-- Import_end --> One suggestion for making health economic modelling projects more tractable is for health economists to re-use each other's models [@Arnold2010].
+A potential strategy for achieving this goal is to make computational health economic models (CHEMs) both modular and open-source.
+A modular model is constructed from multiple reusable and replaceable sub-models (modules) [@pan2021modular].
+Modules can share inputs and outputs with other modules or can be run as independent models [@barros2023empowering].
+Advantages of modular models include feasibility (large projects are broken into smaller tasks, with each component independently developed and tested) and flexibility (making it easier to selectively replace or update specific parts of a model and to scale up or down the level of granularity) [@pan2021modular].
+Modular approaches are currently being used to facilitate the development of complex computational models in disciplines such as biology [@pan2021modular], ecology [@barros2023empowering] and neuroscience [@frazier2022robust].
+In health economics the related and enabling concept of reference models has been recommended [@Afzali2013], but peer reviewed studies describing modular health economic models remain relatively rare, though examples exist in infectious disease [@Trauer2017] and cardiology [@Urach2013].
+
+Modular CHEMs provide an opportunity for multiple modelling teams to contribute to, test and reuse models.
+To enhance this capacity, modular CHEMs may be implemented as open source projects that give others liberal permissions to access and use model source code and data [@pan2021modular; @barros2023empowering; @frazier2022robust].
+Although there appears to be in principle support from many health economists for greater use of open source CHEMs  [@Pouwels2022], actual implementations are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022].
+Barriers to adoption of open source CHEMs include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations [@Pouwels2022; @Wu2019].
+<!-- Adherence to good practice guidance is an essential requirement for healthcare modelling [@Erdemir2020], but  --><!-- Guidelines for implementing open source CHEMs remain scarce, piecemeal and need improving [@Sampson2019].
+-->As many health economic models are owned by pharmaceutical companies and consultancies, commercial considerations can limit the reuse of models and their constituent code and data [@Feenstra2022].
+Legal and ethical issues such as privacy and confidentiality requirements further limit public release of some model artefacts [@Pouwels2022].
+
+<!-- Transferring a health economic model developed for one jurisdiction for application in another typically involves retaining some features and updating others [@barbieri2010international].
+However, models do not always make implementation choices (for example, use of concepts with standardised meanings across jurisdictions)<!-- [@garcia2021cost] -->  <!-- facilitate such selective re-use.
+-->
+
 <!-- Open-source CHEMs remain rare [@Feenstra2022; @Emerson2019].
@@
 
-<!-- Better software frameworks could potentially help address some of the barriers to open-source CHEM development.  -->
-A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users [@myllarniemi2018development].
+<!-- typically have a number of limitations that at best restrict their usefulness and which in some cases may facilitate harmful misuse. -->
+
+Some of the barriers<!-- Give examples --> to the development of open-source and modular CHEMs may be amenable to technical solutions such as software frameworks.<!-- Check last sentence was not used in ethics manuscript  --> A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users [@myllarniemi2018development].
 A software framework provides a foundation for developing multiple software applications with shared resources (e.g., code and data files), that can be modified to suit specific needs.
@@
 Software frameworks have widely been developed and implemented in data science, for example, PyTorch [@PyTorch2019] for machine learning using Python.
+However, software frameworks can be challenging and time consuming to create and may become excessively complex over time [@edwin2014software].
+Software frameworks can also be difficult to learn, often requiring model developers to undergo specialist training [@myllarniemi2018development].
 
-A high-level software framework for implementing open-source <!-- Modification_start -->Computational Health Economic Models (CHEMs)<!-- Modification_end --> in R has previously been developed with the primary aim of improving model transparency [@alarid2019need].
-However, to gain widespread adoption, a software framework for CHEMs may need to provide tools to help model developers meet a broader range of ethical practice requirements.
-There are multiple challenges to overcome.
-Firstly, <!-- the ethical responsibilities of public health computational modellers remain poorly understood [@10.3389/fpubh.2017.00068] and  -->the computational modelling landscape is changing fast [@calder2018computational].
-Secondly, software frameworks can be challenging and time consuming to create and may become excessively complex over time [@edwin2014software].
-Thirdly, software frameworks can be difficult to learn, often requiring model developers to undergo specialist training [@myllarniemi2018development].
+<!-- There are multiple challenges to overcome when developing a software framework.
+Firstly, <!-- the ethical responsibilities of public health computational modellers remain poorly understood [@10.3389/fpubh.2017.00068] and  --><!-- the computational modelling landscape is changing fast [@calder2018computational].
+-->
+
+<!-- A high-level software framework for implementing open-source <!-- Modification_start --><!--  CHEMsin R has previously been developed with the primary aim of improving model transparency [@alarid2019need].
+-->
+
+<!-- However, to gain widespread adoption, a software framework for CHEMs may need to provide tools to help model developers meet a broader range of ethical practice requirements.  -->

### 2024-02-17 Markdown/Manuscript/Child_RMDs/Clippings.Rmd
added URs

@@
 We enabled GitHub Pages in each repository we used for code library development to facilitate the creation and hosting of library documentation websites.
-We also developed a consolidated and versioned project documentation website [@rfwn2022] using the Hugo framework [@hugo_2023] and Docsy theme [@docsy_2023].
+We also developed a consolidated and versioned project documentation website [@ready424] using the Hugo framework [@hugo_2023] and Docsy theme [@docsy_2023].
 To host that website we established an account with Netlify [@netlify_2023] and linked that service to our GitHub organisation so that the website would automatically update whenever the source code in its GitHub repository was edited.
@@
 The program used to implement the utility mapping analysis [@hamilton_matthew_2022_6129906] combines modules from four module libraries ([@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155]) and two framework libraries [@ready4use2022; @ready4show2022].
-Example literate programs published on the ready4 documentation website [@rfwn2022] use toy data [@DVN/HJXYKQ_2021] to illustrate the potential for ready4 modules to facilitate study replication and transferability.
+Example literate programs published on the ready4 documentation website [@ready424] use toy data [@DVN/HJXYKQ_2021] to illustrate the potential for ready4 modules to facilitate study replication and transferability.
 As demonstrated by the checklist we developed (Table \@ref(tab:checktb)), our framework's standards also provide a mechanism for to assess the extent to which the ready4 MOSHEM meets explicit objectives.
@@
 improvements to documentation, code contributions) to open source projects.
-Our project website [@rfwn2022] includes details of multiple ways to contribute to ready4.
+Our project website [@ready424] includes details of multiple ways to contribute to ready4.
 
@@
 
-<!-- (described in more detail on the project documentation website [@rfwn2022])  -->
+<!-- (described in more detail on the project documentation website [@ready424])  -->
 <!-- Sustained funding -->
@@
 Our initial work on *readyforwhatsnext* is focused on Victoria, Australia but the framework we are using to develop it is designed to facilitate extension by ourselves and others to different jurisdictional decision contexts.
-Progress is reported on a project website [@rfwn2022].
+Progress is reported on a project website [@ready424].
 -->

### 2024-02-17 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
added URs

@@
 ## User requirements
+We developed user requirements (URs) for ready4 to address challenges we faced during the initial phases of an open source modelling project we are developing in youth mental health called readyforwhatsnext [@rfwn2024].
+The requirements for ready4 were not defined at the start of the project, but evolved over six years (2018-2024) as we became aware of each new challenge.
+Currently, these requirements are:
 
-1) Provide a standardised template model module and programming syntax.
+UR 1) A *template* from which all CHEM modules can be created.
 
-2) Develop consolidated project documentation and provide tools to find model modules, datasets and study replication programs.
+UR 2) A simple *syntax* to support consistency in how CHEM modules are used in health economic analysis programs.
 
-3) Author, document and share model modules, integrating with online services for open source software development
+UR 3) Integration with online open source software development services to streamline the *authoring, testing, documenting and sharing of CHEM modules*.
 
-4) Ingest, label and share model data, integrating with online services for open science data archiving.
+UR 4) Integration with online open science data archiving services to streamline the *ingesting, labeling and sharing of CHEM data*.
 
-5) Implement integrated and reproducible data ingest, analysis and reporting pipelines.
+UR 5) Tools to help *author replicable health economic analysis programs and reporting subroutines*.
 
-## XXXYYY
-The software framework aims to provide a toolkit for: (i) enabling modular implementation of CHEMs; (ii) authoring and documenting CHEM modules; (iii) managing the labelling and transfer of CHEM input and output data; and (iv) authoring reproducible analyses that apply CHEMs to compatible data.
+UR 6) Tools to *find CHEM modules, datasets and replication programs*.
 
-To achieve these goals, we have implemented the software framework as R [@RCORE2022] code libraries that integrate with a number of online services and which are supported by a documentation website.
+UR 7) Integration with open source project documentation tools to *develop and maintain a consolidated CHEM project website*.
 
-## R libraries 
+## Implementation
+<!-- The software framework aims to provide a toolkit for: (i) enabling modular implementation of CHEMs; (ii) authoring and documenting CHEM modules; (iii) managing the labelling and transfer of CHEM input and output data; and (iv) authoring reproducible analyses that apply CHEMs to compatible data.
+-->
+We implemented the software framework as R [@RCORE2022] code libraries that integrate with a number of online services and which are supported by a documentation website.
+
+### R libraries 
 A library in the R language will typically depend on multiple other R libraries, all of which potentially have different authors.
@@
 
-One framework library provides a *foundation for modular CHEM implementations*.
+One library provides the foundation for the ready4 framework.
 In modular model implementations, modules need to be able to share inputs and outputs with each other and to be run as independent models [@barros2023empowering].
-To achieve this, the foundation framework library defines a template CHEM module (using R’s S4 class system), which can be used to create other CHEM modules with a common set of inherited properties.
-One of these inherited properties is a novel syntax of 15 core commands that enable CHEM module algorithms to be consistently named.
-The foundation library also contains tools for retrieving web-based information on CHEM modules, datasets and analysis programs authored with the framework and tools for partially automating updates to a project documentation website.
+To achieve this, the foundation framework library defines a template CHEM module (using R’s S4 class system), which can be used to create other CHEM modules with a common set of inherited properties (meeting *UR 1*).
+One of these inherited properties is a novel syntax of 15 core commands that enable CHEM module algorithms to be consistently named (meeting *UR 2*).
+The foundation library also contains tools for retrieving web-based information on CHEM modules, datasets and analysis programs authored with ready4 (meeting *UR 6*) and tools for developing and maintaining a project documentation website (*UR 7*).
 
-Three framework libraries are designed to help streamline and standardise workflows for *authoring CHEM modules* from the template module.
+Three framework libraries are designed to meet *UR 3*.
 The R language supports functional and object-oriented programming paradigms [@10.1214/13-STS452].
@@
 One module authoring library contains tools for writing functions in a consistent house style and automatically generating basic documentation for each function.
-A second module authoring library contains tools to help streamline and standardise the authoring and documenting of novel CHEM modules.
+A second module authoring library contains tools to help streamline and standardise the authoring of novel, documented CHEM modules from the template CHEM module.
 A third module authoring library provides tools for disseminating themed bundles of CHEM modules as R libraries that are:
@@
 
-A library for *managing CHEM data* contains tools for supplying CHEM modules with input data ingested from local (i.e., a user's computer) or remote (online repositories) locations, labelling CHEM module datasets and exporting CHEM module data to online repositories.
-A library for *authoring reproducible analyses* contains tools to help write programs that apply CHEM modules to compatible datasets for the purpose of undertaking health economic analyses.
-These analysis programs can be either self-documenting (code is integrated with plain English explanations of what it does) or trigger the creation of explanatory documents (e.g., a scientific manuscript).
+A library for managing CHEM data contains tools for supplying CHEM modules with input data ingested from local (i.e., a user's computer) or remote (online repositories) locations, labelling CHEM module datasets and exporting CHEM module data to online repositories (meeting *UR 4*).
+A library for authoring reproducible analysis programs and reporting subroutines (*UR5*) contains tools to help write executables that apply CHEM modules to compatible datasets for the purpose of undertaking health economic analyses.
+The library supports the creation of analysis programs that are self-documenting (code is integrated with plain English explanations of what it does) and subroutines that can be used as templates that trigger the creation of explanatory documents (e.g., a scientific manuscript).
 
@@
 
-##	Online services 
+###	Online services 
 Framework libraries are designed to be used in conjunction with a number of third-party online services that we established and configured accounts with.
@@
 
-##	Documentation website
+###	Documentation website
 We developed a framework documentation website (https://www.ready4-dev.com) that provides guidance to model developers on how to use and contribute improvements to the ready4 software framework and CHEM modules developed with it.

### 2024-02-18 Markdown/Manuscript/Child_RMDs/Clippings.Rmd
added motivation

@@
 
-The software development practice of encapsulation [@8717448] can be used to help ensure that model modules continue to work as intended when they are combined [@ready4oop2022].
+<!-- The software development practice of encapsulation [@8717448] can be used to help ensure that model modules continue to work as intended when they are combined [@ready4oop2022].
 In some cases, combining modules may mean new versions of modules have to be created to better account for interaction effects.
 The concept of inheritance [@8717448] can be used to write code that efficiently achieves this objective as well as to facilitate selective editing of modules when transferring models to different decision contexts [@ready4oop2022].
+-->
+
 Writing algorithms as collections of functions (short, self-contained and reusable software routines that each perform a discrete task) is recommended as good practice for scientific computing [@Wilson_2017].

### 2024-02-18 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
added motivation

@@
 ---
-
-We are using the ready4 software framework to implement multiple transparent, reusable and updatable CHEMs in youth mental health (see Figure \@ref(fig:fig1)).
-Some initial outputs from this work are publicly available as development version releases.
-
-```{r, child = child_figs_ls$fig1, echo=FALSE}
-```
-
-##	Economic topics
-Currently, we are using the ready4 software framework to develop, apply, and share youth mental health CHEMs in four of the twelve domains of health economics identified by Wagstaff and Culyer [@wagstaff2012four]:
-
--	health and its value (our projects: models to map psychological and functional measures to health utility);
-
--	determinants of health and ill-health (our projects: models for creating synthetic household populations with key risk and protective factors for mental disorders);
-
--	demand for health and health care (our projects: spatial epidemiology and help-seeking choice models); and
-
--	supply of health services (our projects: a model of primary mental health care services for young people).
-
-Potential future directions are to supplement this work with CHEMs in two additional Wagstaff and Culyer domains of: (i) public health (to model the impact of selected fiscal policy and regulation options on young people's mental health); and (ii) human resources (to model the supply and behaviours of the youth mental health workforce).
-Our ultimate aim is to flexibly combining all our CHEMs in analyses that help answer questions in two additional Wagstaff and Culyer domains:
-
--	efficiency and equity (our goal: assess the distributional impacts and identify the optimal targeting of youth mental health interventions); and
-
--	economic evaluation (our goal: assess the cost-utility of competing policy options for improving the mental health of young people).
 

### 2024-02-18 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
added motivation

@@
 Modular implementations enable models to be constructed from multiple independently reusable and replaceable sub-models (modules) [@pan2021modular].
-The programming concept inheritance [@8717448], deployed in object-oriented programming approaches, can facilitate the duplication and selective modification of models.
+<!-- The programming concept inheritance [@8717448], deployed in object-oriented programming approaches, can facilitate the duplication and selective modification of models.  -->
 Granting permissions to others to use, test and adapt models and their components, can be facilitated by two broad categories of open source licenses.

### 2024-02-18 Markdown/Manuscript/Child_RMDs/MS_Imp_Motivation.Rmd
added motivation

---
title: "MS_Imp_Guidelines"
output: html_document
date: '2022-07-21'
---

We became interested in modular and open-source approaches to CHEM development in 2018 when beginning to plan how to synthesise a number of current or planned economic modelling projects in youth mental health in one multi-purpose model. This overarching youth mental health model  is called readyforwhatsnext [@rfwn2024]. Initially we planned to construct readyforwhatsnext from projects in four of the twelve domains of health economics identified by Wagstaff and Culyer [@wagstaff2012four]:

-	health and its value (our projects: models to map psychological and functional measures to health utility);

-	determinants of health and ill-health (our projects: models for creating synthetic household populations with key risk and protective factors for mental disorders);

-	demand for health and health care (our projects: spatial epidemiology and help-seeking choice models); and

-	supply of health services (our projects: a model of primary mental health care services for young people).

Potential future directions are to supplement readyforwhatsnext with projects in two additional Wagstaff and Culyer domains of: (i) public health (to model the impact of selected fiscal policy and regulation options on young people's mental health); and (ii) human resources (to model the supply and behaviours of the youth mental health workforce). Our ultimate aim is for readyforwhatsnext to flexibly combine its constituent parts in analyses that help answer questions in two additional Wagstaff and Culyer domains:

-	efficiency and equity (our goal: assess the distributional impacts and identify the optimal targeting of youth mental health interventions); and

-	economic evaluation (our goal: assess the cost-utility of competing policy options for improving the mental health of young people).

Although we are principally interested in using readyforwhatsnext to answer policy questions relating to the mental health of young people in Australia, we want to facilitate transferability by other teams to different jurisdictions. A high level schematic of how we aim to implement readyforwhatsnext as a modular and open source CHEM is outlined in Figure \@ref(fig:fig1).

```{r, child = child_figs_ls$fig1, echo=FALSE}
```

### 2024-02-18 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
added motivation

@@
 ## Purpose
-The overarching goal of our software framework, which we call ready4, is to support the development of CHEMs that meet explicit criteria for transparency, reusability and updatability.
-We have describe these criteria elsewhere [@ethicsCHEMS2024], but briefly they are: software files are open access, developer contributions are easily identified, programming practices promote selective reuse, licenses restrict only unethical reuse, maintenance infrastructure is in place and systematic retesting and deprecation with each new release.
+We decided to develop a software framework to help us address challenges we encountered during the planning and early implementation of readyforwhatsnext.
+The software framework is called ready4 [@ready424].
+The purpose of ready4 is to support the development of CHEMs that meet explicit criteria for transparency, reusability and updatability.
+We have describe these criteria elsewhere [@ethicsCHEMS2024], but briefly they are: software files are open access, developer contributions are easily identified, programming practices promote selective reuse, licenses restrict only unethical reuse, maintenance infrastructure is in place and new releases are systematically retested, with and deprecation of outdated artefacts.
 
 ## User requirements
-We developed user requirements (URs) for ready4 to address challenges we faced during the initial phases of an open source modelling project we are developing in youth mental health called readyforwhatsnext [@rfwn2024].
-The requirements for ready4 were not defined at the start of the project, but evolved over six years (2018-2024) as we became aware of each new challenge.
+We created ready4 with one primary user group in mind - ourselves.
+The user requirements (URs) for ready4 evolved over six years (2018-2024) as we became aware of new challenges in implementing readyforwhatsnext that we needed to solve.
+We specified these user requirements in terms that facilitate solutions that may meet the needs of two other CHEM developers.
 Currently, these requirements are:
 
-UR 1) A *template* from which all CHEM modules can be created.
+UR 1) A *template CHEM module* which can be used to create CHEM modules that can: (i) safely share inputs and outputs with each other without impairing any module's integrity; (ii) be run as independent models; and (iii) be selectively replaced, updated or extended.
 
-UR 2) A simple *syntax* to support consistency in how CHEM modules are used in health economic analysis programs.
+UR2) *Tools* for creating new CHEM modules from the template module.
 
-UR 3) Integration with online open source software development services to streamline the *authoring, testing, documenting and sharing of CHEM modules*.
+UR 3) A simple *syntax* to support consistency in how CHEM modules are used in health economic analysis programs.
 
-UR 4) Integration with online open science data archiving services to streamline the *ingesting, labeling and sharing of CHEM data*.
+UR 4) Integration with online open source software development services to streamline the *authoring, testing, documenting and sharing of CHEM modules*.
 
-UR 5) Tools to help *author replicable health economic analysis programs and reporting subroutines*.
+UR 5) Integration with online open science data archiving services to streamline the *ingesting, labeling and sharing of CHEM data*.
 
-UR 6) Tools to *find CHEM modules, datasets and replication programs*.
+UR 6) Tools to help *author replicable health economic analysis programs and reporting subroutines*.
 
-UR 7) Integration with open source project documentation tools to *develop and maintain a consolidated CHEM project website*.
+UR 7) Tools to *find CHEM modules, datasets and replication programs*.
+
+UR 8) Integration with tools for documenting open source software to help *develop and maintain a consolidated CHEM project website*.
 
@@
 ### R libraries 
-A library in the R language will typically depend on multiple other R libraries, all of which potentially have different authors.
+A library in the R language will typically depend on multiple other R libraries, many of which are likely to have different authors.
 As the number of third-party dependencies of an R library grows so does the fragility of that library (e.g., the library may cease to work as intended due to changes in one of its dependency libraries).
@@
 One library provides the foundation for the ready4 framework.
-In modular model implementations, modules need to be able to share inputs and outputs with each other and to be run as independent models [@barros2023empowering].
-To achieve this, the foundation framework library defines a template CHEM module (using R’s S4 class system), which can be used to create other CHEM modules with a common set of inherited properties (meeting *UR 1*).
-One of these inherited properties is a novel syntax of 15 core commands that enable CHEM module algorithms to be consistently named (meeting *UR 2*).
-The foundation library also contains tools for retrieving web-based information on CHEM modules, datasets and analysis programs authored with ready4 (meeting *UR 6*) and tools for developing and maintaining a project documentation website (*UR 7*).
+<!-- In modular model implementations, modules need to be able to share inputs and outputs with each other and to be run as independent models [@barros2023empowering].
+-->The ready4 foundation library defines a template CHEM module using R’s S4 class system, that supports an object-oriented programming paradigm.
+Two notable features of object-oriented programming are encapsulation [@8717448] and inheritence [@8717448].
+Encapsulation allows a CHEM module to bundle model data and algorithms in a protected environment.
+Encapsulation can be used to help ensure that CHEM modules continue to work as intended when they are combined<!-- [@ready4oop2022] -->.
+Inheritence allows new CHEM modules to be created that inherit some or all of the properties of a parent module.
+Inheritence is useful in cases where it is necessary to update CHEM modules that are being combined to account for interaction effects.
+Inheritance also facilitates the selective editing of CHEM modules when transferring models to different decision contexts <!-- [@ready4oop2022] -->.
+The ready4 template CHEM module can therefore be used to create other CHEM modules that inherit common set of properties (meeting *UR 1*).
+One of these inherited properties is a novel syntax of 15 core commands that enable CHEM module algorithms to be consistently named (meeting *UR 3*).
+The foundation library also contains tools for retrieving web-based information on CHEM modules, datasets and analysis programs authored with ready4 (meeting *UR 7*) and tools for developing and maintaining a project documentation website (*UR 8*).
 
-Three framework libraries are designed to meet *UR 3*.
-The R language supports functional and object-oriented programming paradigms [@10.1214/13-STS452].
+Three framework libraries are designed to meet *URs 2 and 4*.
+<!-- Define functional and object-oriented approaches, acceptance and unit testing.
+-->The R language supports functional and object-oriented programming paradigms [@10.1214/13-STS452].
 Authoring with each of these paradigms is facilitated by a dedicated CHEM module authoring library.
@@
 
-A library for managing CHEM data contains tools for supplying CHEM modules with input data ingested from local (i.e., a user's computer) or remote (online repositories) locations, labelling CHEM module datasets and exporting CHEM module data to online repositories (meeting *UR 4*).
-A library for authoring reproducible analysis programs and reporting subroutines (*UR5*) contains tools to help write executables that apply CHEM modules to compatible datasets for the purpose of undertaking health economic analyses.
+A library for managing CHEM data contains tools for supplying CHEM modules with input data ingested from local (i.e., a user's computer) or remote (online repositories) locations, labelling CHEM module datasets and exporting CHEM module data to online repositories (meeting *UR 5*).
+A library for authoring reproducible analysis programs and reporting subroutines (*UR6*) contains tools to help write executables that apply CHEM modules to compatible datasets for the purpose of undertaking health economic analyses.
 The library supports the creation of analysis programs that are self-documenting (code is integrated with plain English explanations of what it does) and subroutines that can be used as templates that trigger the creation of explanatory documents (e.g., a scientific manuscript).
@@
 ###	Online services 
-Framework libraries are designed to be used in conjunction with a number of third-party online services that we established and configured accounts with.
+Framework libraries are designed to be used in conjunction with a number of third-party online services that users of the framework will need to establish and configure accounts with.
 

### 2024-02-20 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
minor

@@
 
-Although we are principally interested in using CHEMs to answer policy questions relating to the mental health of young people in Australia, we want to facilitate CHEM transferability to other jurisdictions.
+<!-- Although we are principally interested in using CHEMs to answer policy questions relating to the mental health of young people in Australia, we want to facilitate CHEM transferability to other jurisdictions.
+-->
+
 Our CHEMs are being derived from and applied to real data (which can be empirical, simulated or assumption, so long as it is appropriate for use in analysis intended to inform decision-making) from Australia.

### 2024-02-20 Markdown/Manuscript/Child_RMDs/MS_Imp_Motivation.Rmd
minor

@@
 This overarching youth mental health model  is called readyforwhatsnext [@rfwn2024].
-Initially we planned to construct readyforwhatsnext from projects in four of the twelve domains of health economics identified by Wagstaff and Culyer [@wagstaff2012four]:
+Initially, we plan to construct readyforwhatsnext from projects in four of the twelve domains of health economics identified by Wagstaff and Culyer [@wagstaff2012four]:
 

### 2024-02-20 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
minor

@@
 The purpose of ready4 is to support the development of CHEMs that meet explicit criteria for transparency, reusability and updatability.
-We have describe these criteria elsewhere [@ethicsCHEMS2024], but briefly they are: software files are open access, developer contributions are easily identified, programming practices promote selective reuse, licenses restrict only unethical reuse, maintenance infrastructure is in place and new releases are systematically retested, with and deprecation of outdated artefacts.
+We have describe these criteria elsewhere [@ethicsCHEMS2024], but briefly they are: software files are open access, developer contributions are easily identified, programming practices promote selective reuse, licenses restrict only unethical reuse, maintenance infrastructure is in place and new releases are systematically retested, with deprecation of outdated artefacts.
 
@@
 
-UR 1) A *template CHEM module* which can be used to create CHEM modules that can: (i) safely share inputs and outputs with each other without impairing any module's integrity; (ii) be run as independent models; and (iii) be selectively replaced, updated or extended.
+UR 1) A *template* for creating CHEM modules that can: (i) safely share inputs and outputs with each other without impairing any module's integrity; (ii) be run as independent models; and (iii) be selectively replaced, updated or extended.
 
-UR2) *Tools* for creating new CHEM modules from the template module.
+UR 2) *Developer tools* that integrate with online open source software development services to support streamlined workflows for authoring R libaries of CHEM modules that are: (i) created using the template module; (ii) written in a consistent house style; (iii) consistently documented; (iv) licensed for reuse; (v) bundled with citation data specifying authorship, funding source, version number and a Digital Object Identifier (DOI); and (vi) quality assured with publicly available acceptance and unit tests.
 
-UR 3) A simple *syntax* to support consistency in how CHEM modules are used in health economic analysis programs.
+UR 3) A simple *syntax* that promotes support consistency in how algorithms associated with CHEM modules are described and used in health economic analysis programs.
 
-UR 4) Integration with online open source software development services to streamline the *authoring, testing, documenting and sharing of CHEM modules*.
+<!-- UR 4) Integration with online open source software development services to streamline the *authoring, testing, documenting and sharing of CHEM modules*.  -->
 
-UR 5) Integration with online open science data archiving services to streamline the *ingesting, labeling and sharing of CHEM data*.
+UR 5) *Data management tools* that integrate with online data repository services to streamline the ingesting, labeling and sharing of publicly available and confidential data.
 
-UR 6) Tools to help *author replicable health economic analysis programs and reporting subroutines*.
+UR 6) *Reporting tools* that include: 
+<!-- help generate tables for multiple outputs, retrieve templates, modify templates with authorship and results -->
+(i) replicable health economic analysis programs; and (ii) reporting subroutines that.
 
@@
 Inheritence is useful in cases where it is necessary to update CHEM modules that are being combined to account for interaction effects.
-Inheritance also facilitates the selective editing of CHEM modules when transferring models to different decision contexts <!-- [@ready4oop2022] -->.
+Inheritance also facilitates the selective editing of CHEM modules when transferring models to different decision contexts<!-- [@ready4oop2022] -->.
 The ready4 template CHEM module can therefore be used to create other CHEM modules that inherit common set of properties (meeting *UR 1*).

### 2024-02-20 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
moved URs

@@
 
-(i)	a prototype software framework we have developed to support the development of modular and open source CHEMs; and
+(i)	our motivation for developing a transferable CHEM in youth mental health;
+
+(ii) a prototype software framework we have developed to support the development of transferable CHEMs; and
 <!-- propose a set of ethical responsibilities for CHEM project teams and criteria for assessing ethical CHEM implementations; -->
 <!-- (ii)  -->
-(ii)	how we have applied that software framework to develop and share an initial set of modules for a economic model of youth mental health.
+(ii)	how we have applied that software framework to develop and share an initial set of modules for our youth mental health CHEM.

### 2024-02-20 Markdown/Manuscript/Child_RMDs/MS_Imp_Motivation.Rmd
moved URs

@@
 This overarching youth mental health model is called readyforwhatsnext [@rfwn2024].
+
+## Economic topics
 Initially, we plan to construct readyforwhatsnext from projects in four of the twelve domains of health economics identified by Wagstaff and Culyer [@wagstaff2012four]:
@@
 
-Although we are principally interested in using readyforwhatsnext to answer policy questions relating to the mental health of young people in Australia, we want to facilitate transferability by other teams to different jurisdictions.
-A high level schematic of how we aim to implement readyforwhatsnext as a modular and open source CHEM is outlined in Figure \@ref(fig:fig1).
+A high level schematic of how we aim to implement readyforwhatsnext as a modular and open source CHEM to address these topics is outlined in Figure \@ref(fig:fig1).
 
@@
 ```
+
+## User requirements
+Although we are principally interested in using readyforwhatsnext to answer policy questions relating to the mental health of young people in Australia, we want to facilitate model transfer to other jurisdictions.
+We believe that a good starting point for facilitating model transferable is to develop a CHEM that is relatively easy to understand, use and adapt.
+For that reason, the initial user-requirements we specified for readyforwhatsnext are to meet six explicit criteria for transparency, reusability and updatability.
+We have describe these criteria elsewhere [@ethicsCHEMS2024], but briefly they are:
+
+T1) Software files are open access;
+
+T2) Developer contributions are easily identified;
+
+T3) Programming practices promote selective reuse;
+
+T4) Licenses restrict only unethical reuse; <!-- rephrase Liceses permit derivative works-->
+
+T5) Maintenance infrastructure is in place; and
+
+T6) New releases are systematically retested, with deprecation of outdated artefacts.

### 2024-02-20 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
moved URs

@@
 
-## Purpose
 We decided to develop a software framework to help us address challenges we encountered during the planning and early implementation of readyforwhatsnext.
 The software framework is called ready4 [@ready424].
-The purpose of ready4 is to support the development of CHEMs that meet explicit criteria for transparency, reusability and updatability.
-We have describe these criteria elsewhere [@ethicsCHEMS2024], but briefly they are: software files are open access, developer contributions are easily identified, programming practices promote selective reuse, licenses restrict only unethical reuse, maintenance infrastructure is in place and new releases are systematically retested, with deprecation of outdated artefacts.
 
@@
 
-UR 3) A simple *syntax* that promotes support consistency in how algorithms associated with CHEM modules are described and used in health economic analysis programs.
+UR 3) A *syntax* that promotes simplicity and consistency in how algorithms associated with CHEM modules are described and used in health economic analysis programs.
 
@@
 
-UR 6) *Reporting tools* that include: 
+UR 6) *Reporting tools* that: (i) help author programs for generating analysis reports and scientific summaries from a template that can render documents in HTML, Adobe PDF and Microsoft Word file formats; (ii) retrieve version specific reporting template programs from online code repositories and (iii) supply study specific data (e.g authorship details, input data and analysis results) to reporting template programs to render reports and scientific summaries.
 <!-- help generate tables for multiple outputs, retrieve templates, modify templates with authorship and results -->
-(i) replicable health economic analysis programs; and (ii) reporting subroutines that.
 
-UR 7) Tools to *find CHEM modules, datasets and replication programs*.
+UR 7) *Search tools* to retrieve web based information on a CHEM project's: (i) publicly available model modules, module libraries and tutorials; (ii) datasets and data collections; and (iii) replication programs and reporting templates.
 
-UR 8) Integration with tools for documenting open source software to help *develop and maintain a consolidated CHEM project website*.
+UR 8) *Documentation tools* that integrate with open source website development and hosting infrastructure to help: (i) develop a consolidated project documentation website that synthesises data from mulitple code library websites and code and data repositories; and (ii) partially automate the updating of website resources such as tutorials and code and data release information.
 

### 2024-02-20 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
moved URs

@@
 Although influential and widely used, health economic models can be skills and resource intensive to undertake.<!-- Import_end --> One suggestion for making health economic modelling projects more tractable is for health economists to re-use each other's models [@Arnold2010].
-A potential strategy for achieving this goal is to make computational health economic models (CHEMs) both modular and open-source.
+
+<!-- Imported_from_Ethics-->Key concerns for health economists when considering whether to reuse a model are generalisability (application without adaptation) and transferability (selective reuse and/or modification of model components) [@RN39].
+<!-- End_Imported_from_Ethics -->A potential strategy for achieving both these goals is to make computational health economic models (CHEMs) both modular and open-source.
 A modular model is constructed from multiple reusable and replaceable sub-models (modules) [@pan2021modular].

### 2024-02-20 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
one table to go
extracted ethics component
added motivation
moved URs

@@
 
-# Ethical responsibilities and assessment criteria
-```{r child="../Child_RMDs/MS_Imp_Guidelines.Rmd", echo=FALSE}
+# Motivation
+```{r child="../Child_RMDs/MS_Imp_Motivation.Rmd", echo=FALSE}
 ```
@@
 
-# Application in youth mental health
+# Initial application
 ```{r child="../Child_RMDs/MS_Imp_Example.Rmd", echo=FALSE}

### 2024-02-20 Markdown/Manuscript/Parent_PDF/Springer.Rmd
moved URs

@@
 
-title: A prototype software framework for transparent, reusable and updatable computational health economic models
-titlerunning: Framework for ethical computational models
+title: A prototype software framework for transferable computational health economic models
+titlerunning: Framework for transferable computational models
 

### 2024-02-20 setup.R

@@ -13,7 +13,7 @@ X <- Ready4showSynopsis(#background_1L_chr = "Our study is entirely fictional.",
                         keywords_chr = c("computational models", "health economics", "mental disorders", "open-source models", "software frameworks"),
                         outp_formats_chr = "PDF",
                         #sample_desc_1L_chr = "The study sample is fake data that pretends to be young people aged 12 to 25 years who attended Australian primary care services for mental health related needs between November 2019 to August 2020.",
-                        title_1L_chr = "A prototype software framework for transparent, reusable and updatable computational health economic models")
+                        title_1L_chr = "A prototype software framework for transferable computational health economic models")
 X <- renewSlot(X,
                "authors_r3", 
                {

### 2024-02-21 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
minor tidies

--- 2024-02-16 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
@@
 
-(i)	a prototype software framework we have developed to support the development of modular and open source CHEMs; and
+(i)	our motivation for developing a modular and open source CHEM in youth mental health;
+
+(ii) a prototype software framework we have developed to support the development of transferable CHEMs; and
 <!-- propose a set of ethical responsibilities for CHEM project teams and criteria for assessing ethical CHEM implementations; -->
 <!-- (ii)  -->
-(ii)	how we have applied that software framework to develop and share an initial set of modules for a economic model of youth mental health.
+(ii)	how we have applied the prototype software framework to develop and share an initial set of modules for our youth mental health CHEM.

### 2024-02-21 Markdown/Manuscript/Child_RMDs/MS_Imp_Motivation.Rmd
minor tidies

@@
 
-Potential future directions are to supplement readyforwhatsnext with projects in two additional Wagstaff and Culyer domains of: (i) public health (to model the impact of selected fiscal policy and regulation options on young people's mental health); and (ii) human resources (to model the supply and behaviours of the youth mental health workforce).
+Potential future directions are to incorporate projects in two additional Wagstaff and Culyer domains of: (i) public health (to model the impact of selected fiscal policy and regulation options on young people's mental health); and (ii) human resources (to model the supply and behaviours of the youth mental health workforce).
 Our ultimate aim is for readyforwhatsnext to flexibly combine its constituent parts in analyses that help answer questions in two additional Wagstaff and Culyer domains:
@@
 
-## User requirements
+## Transferability
 Although we are principally interested in using readyforwhatsnext to answer policy questions relating to the mental health of young people in Australia, we want to facilitate model transfer to other jurisdictions.
 We believe that a good starting point for facilitating model transferable is to develop a CHEM that is relatively easy to understand, use and adapt.
-For that reason, the initial user-requirements we specified for readyforwhatsnext are to meet six explicit criteria for transparency, reusability and updatability.
-We have describe these criteria elsewhere [@ethicsCHEMS2024], but briefly they are:
+For that reason, the transferability requirements we specified for readyforwhatsnext are to meet six explicit criteria for transparency, reusability and updatability.
+We have describe these criteria and theire relationship to ethical modelling practice elsewhere [@ethicsCHEMS2024], but briefly they are:
 
@@
 
-T4) Licenses restrict only unethical reuse; <!-- rephrase Liceses permit derivative works-->
+T4) Licenses restrict permit derivative works; <!-- rephrase Liceses permit derivative works-->
 
@@
 
-T6) New releases are systematically retested, with deprecation of outdated artefacts.
+T6) Systematic retesting and deprecation.

### 2024-02-21 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
minor tidies

@@
 <!-- Imported_from_Ethics-->Key concerns for health economists when considering whether to reuse a model are generalisability (application without adaptation) and transferability (selective reuse and/or modification of model components) [@RN39].
-<!-- End_Imported_from_Ethics -->A potential strategy for achieving both these goals is to make computational health economic models (CHEMs) both modular and open-source.
+Health economic models are likely to require at least some modification to be validly applied to a new jurisdiction, time period or decision problem.
+How difficult it is to undertake such a model transfer depends in part on whether the Computational Health Economic Model (CHEM) - the software files that implement the model - can be readily understood, applied and adapted.
+
+<!-- End_Imported_from_Ethics -->A potential strategy for promoting the transferability of health economic models is to develop CHEMs that are both modular and open-source.
 A modular model is constructed from multiple reusable and replaceable sub-models (modules) [@pan2021modular].

### 2024-02-21 Markdown/Manuscript/Parent_PDF/Springer.Rmd
minor tidies

@@
 
-title: A prototype software framework for transferable computational health economic models
+title: A prototype software framework for transferable computational health economic models and its early application in youth mental health
 titlerunning: Framework for transferable computational models

### 2024-02-21 setup.R

@@ -13,7 +13,7 @@ X <- Ready4showSynopsis(#background_1L_chr = "Our study is entirely fictional.",
                         keywords_chr = c("computational models", "health economics", "mental disorders", "open-source models", "software frameworks"),
                         outp_formats_chr = "PDF",
                         #sample_desc_1L_chr = "The study sample is fake data that pretends to be young people aged 12 to 25 years who attended Australian primary care services for mental health related needs between November 2019 to August 2020.",
-                        title_1L_chr = "A prototype software framework for transferable computational health economic models")
+                        title_1L_chr = "A prototype software framework for transferable computational health economic models and its early application in youth mental health")
 X <- renewSlot(X,
                "authors_r3", 
                {

### 2024-02-21 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
up to example

@@
 -->
-
-Our CHEMs are being derived from and applied to real data (which can be empirical, simulated or assumption, so long as it is appropriate for use in analysis intended to inform decision-making) from Australia.
-To help demonstrate the potential use of CHEMs in other decision contexts, we also create toy datasets.
-Data created for illustration purposes is prominently labelled as not for use in decision-analysis.
 
@@
 
+## Online services
+To track our code coverage, we linked our GitHub organisation to an account we established at codecov [@codecov_2022].
+The framework also supports integrations with the open science repositories Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] that provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each code and data collection.
+
+The third party services that our framework is designed to work with include GitHub, Zenodo, Dataverse,
+codecov [@codecov_2022]
+
+We created a GitHub organisation (a collection of code repositories) where source code that we author is stored and version controlled.
+We configured individual repositories in our GitHub organisation to implement continuous integration.
+By default, code libraries authored with our framework will use continuous integration to assess compliance with policies specified by the Comprehensive R Archive Network (CRAN) [@CRAN2022].
+To track our code coverage, we linked our GitHub organisation to an account we established at codecov [@codecov_2022].
+To facilitate the creation and hosting of documentation websites, we enabled GitHub Pages in each repository used for code library development.
+
+We also created a Zenodo community - a collection of permanent, uniquely identified repositories.
+We then linked our Zenodo community and GitHub organisation so that every time we specify a version of code in one of our GitHub repositories as a “release”, a copy of that code is automatically created on Zenodo with a DOI.
+Finally, to manage model datasets, we created a dedicated collection within the Harvard Dataverse installation.
+
+## Documentation website
+We used functions from our foundation framework library to partially automate website updates relating to available CHEM modules, datasets and analysis programs.
+
 \blandscape

### 2024-02-21 Markdown/Manuscript/Child_RMDs/MS_Imp_Motivation.Rmd
up to example

@@
 ## Economic topics
-Initially, we plan to construct readyforwhatsnext from projects in four of the twelve domains of health economics identified by Wagstaff and Culyer [@wagstaff2012four]:
+Initially, we are constructing readyforwhatsnext from projects in four of the twelve domains of health economics identified by Wagstaff and Culyer [@wagstaff2012four]:
 
@@
 
-Potential future directions are to incorporate projects in two additional Wagstaff and Culyer domains of: (i) public health (to model the impact of selected fiscal policy and regulation options on young people's mental health); and (ii) human resources (to model the supply and behaviours of the youth mental health workforce).
+Potential future directions could incorporate projects in two additional Wagstaff and Culyer domains of: (i) public health (to model the impact of selected fiscal policy and regulation options on young people's mental health); and (ii) human resources (to model the supply and behaviours of the youth mental health workforce).
 Our ultimate aim is for readyforwhatsnext to flexibly combine its constituent parts in analyses that help answer questions in two additional Wagstaff and Culyer domains:
@@
 
-A high level schematic of how we aim to implement readyforwhatsnext as a modular and open source CHEM to address these topics is outlined in Figure \@ref(fig:fig1).
-
-```{r, child = child_figs_ls$fig1, echo=FALSE}
-```
-
 ## Transferability
 Although we are principally interested in using readyforwhatsnext to answer policy questions relating to the mental health of young people in Australia, we want to facilitate model transfer to other jurisdictions.
-We believe that a good starting point for facilitating model transferable is to develop a CHEM that is relatively easy to understand, use and adapt.
-For that reason, the transferability requirements we specified for readyforwhatsnext are to meet six explicit criteria for transparency, reusability and updatability.
-We have describe these criteria and theire relationship to ethical modelling practice elsewhere [@ethicsCHEMS2024], but briefly they are:
+The transferability requirements we have specified for readyforwhatsnext are to meet six explicit criteria for transparency, reusability and updatability.
+We have describe these criteria and their relationship to ethical modelling practice elsewhere [@ethicsCHEMS2024], but briefly they are:
 
@@
 
-T4) Licenses restrict permit derivative works; <!-- rephrase Liceses permit derivative works-->
+T4) Licenses permit derivative works; <!-- rephrase Liceses permit derivative works-->
 
@@
 T6) Systematic retesting and deprecation.
+
+The readyforwhatsnext model is being derived from and applied to real Australian data (which can be empirical, simulated or assumption, so long as it is appropriate for use in analysis intended to inform decision-making).
+To help demonstrate the potential transferability of readyforwhatsnext to other decision contexts, we are also creating toy datasets.
+Toy data created for illustration purposes will be prominently labelled as not for use in decision-analysis.
+
+A high level schematic guiding our implementation of readyforwhatsnext as a modular and open source CHEM is outlined in Figure \@ref(fig:fig1).
+
+```{r, child = child_figs_ls$fig1, echo=FALSE}
+```

### 2024-02-21 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
up to example

@@
 
-We decided to develop a software framework to help us address challenges we encountered during the planning and early implementation of readyforwhatsnext.
-The software framework is called ready4 [@ready424].
+We began developing a prototype software framework in order to address a number of challenges we encountered during the planning and early implementation of readyforwhatsnext.
+The software framework is called ready4.
 
@@
 We created ready4 with one primary user group in mind - ourselves.
-The user requirements (URs) for ready4 evolved over six years (2018-2024) as we became aware of new challenges in implementing readyforwhatsnext that we needed to solve.
-We specified these user requirements in terms that facilitate solutions that may meet the needs of two other CHEM developers.
+The user requirements (URs) for ready4 evolved over six years (2018-2024) as we became aware of new issues that we needed to solve.
 Currently, these requirements are:
 
-UR 1) A *template* for creating CHEM modules that can: (i) safely share inputs and outputs with each other without impairing any module's integrity; (ii) be run as independent models; and (iii) be selectively replaced, updated or extended.
+UR 1) A *template module* for use in CHEM implementations in which modules can: (i) be run as independent models; (ii) safely combined, sharing inputs and outputs with each other without unintended interference; and (iii) be selectively replaced, updated or extended.
 
@@
 
-UR 3) A *syntax* that promotes simplicity and consistency in how algorithms associated with CHEM modules are described and used in health economic analysis programs.
+UR 3) A *programming syntax* that promotes simplicity and consistency in how algorithms associated with CHEM modules are described and used in health economic analysis programs.
 
@@
 ###	Online services 
-Framework libraries are designed to be used in conjunction with a number of third-party online services that users of the framework will need to establish and configure accounts with.
+Framework libraries are designed to be used in conjunction with a number of third-party online services that users of ready4 will need to establish and configure accounts with.
+The framework's developer tools integrate with online code development, testing and archiving services.
+The ready4 framework uses the GitHub [@github2007] service's tools for: software development, testing, version control and distribution; hosting of documentation websites; and transparent record keeping of collaborator contributions.
+A useful concept for informing software users about the extensiveness of testing procedures is code coverage [@ERICWONG2010188] - the proportion of code that has been explicitly tested.
+The ready4 framework uses the codecov [@codecov_2022] service to measure and share information about code coverage.
+The open science repository service Zenodo [@Zenodo2013] is used to provide persistent storage, uniquely identified with a a Digital Object Identifier (DOI), of each code release.
 
-We created a GitHub organisation (a collection of code repositories) where source code that we author is stored and version controlled.
-We configured individual repositories in our GitHub organisation to implement continuous integration.
-By default, code libraries authored with our framework will use continuous integration to assess compliance with policies specified by the Comprehensive R Archive Network (CRAN) [@CRAN2022].
-To track our code coverage, we linked our GitHub organisation to an account we established at codecov [@codecov_2022].
-To facilitate the creation and hosting of documentation websites, we enabled GitHub Pages in each repository used for code library development.
-
-We also created a Zenodo community - a collection of permanent, uniquely identified repositories.
-We then linked our Zenodo community and GitHub organisation so that every time we specify a version of code in one of our GitHub repositories as a “release”, a copy of that code is automatically created on Zenodo with a DOI.
-Finally, to manage model datasets, we created a dedicated collection within the Harvard Dataverse installation.
+The framework's data management tools use the Dataverse [@Dataverse2007] data repository service for persistent, uniquely identifiable and versioned storage of model input and output data.
+For the management of frequently updated datasets that do not require persistent storage, ready4 uses GitHub.
 
@@
 The documentation website is versioned, which means documentation relating to prior versions of framework software can be archived, retrieved and viewed.
-
 The documentation website was developed using the Hugo framework [@hugo_2023], Docsy theme [@docsy_2023] and Algolia DocSearch [@algoliadocsearch_2023] and is hosted using the Netlify [@netlify_2023] service.
-We used functions from our foundation framework library to partially automate website updates relating to available CHEM modules, datasets and analysis programs.
 We linked our Netlify account to our GitHub organisation so that the project website would automatically update whenever its source code (publicly available in a GitHub repository) was edited.

### 2024-02-21 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
up to example

@@
 
-Some of the barriers<!-- Give examples --> to the development of open-source and modular CHEMs may be amenable to technical solutions such as software frameworks.<!-- Check last sentence was not used in ethics manuscript  --> A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users [@myllarniemi2018development].
+Some of the technical barriers<!-- Give examples --> to the development of open-source and modular CHEMs could be addressed by appropriate software frameworks.<!-- Check last sentence was not used in ethics manuscript  --> A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users [@myllarniemi2018development].
 A software framework provides a foundation for developing multiple software applications with shared resources (e.g., code and data files), that can be modified to suit specific needs.

### 2024-02-23 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
nearly done on model

--- 2024-02-20 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
@@
 -->
+Our early use of the ready4 framework has focused on developing readyforwhatsnext modules for constructing, sharing and using utility mapping models in youth mental health.
 
-Our CHEMs are being derived from and applied to real data (which can be empirical, simulated or assumption, so long as it is appropriate for use in analysis intended to inform decision-making) from Australia.
-To help demonstrate the potential use of CHEMs in other decision contexts, we also create toy datasets.
-Data created for illustration purposes is prominently labelled as not for use in decision-analysis.
+## Model user requirements
+The initial model user requirements (MURs) that we specified for initial readyforwhatsnext modules we developed for utility mapping were:
 
-## Case study: health and its value
+MUR 1) *Variable validation tools* that: (i) define the allowable range (minimum and maximum) and numeric class (integer or double precision) associated with different psychological, functional and health utility summary measures appropriate for use in youth mental health samples; (ii) provide an informative error message that halts an analysis or reporting program's execution should impermissible values be assigned to each measure.
+
+MUR 2) *Dataset description tools* that: (i) attach metadata to a human records dataset that specifies the unique person identifier, group assignment and data collection round variables; and (ii) generate tabular and graphical summaries of dataset descriptive statistics.
+
+MUR 3) *Multi-attribute instrument tools* that: (i) attaches structured metadata about an instrument (e.g.
+name, version, country, items, domains, parameter values for scoring algorithms) to a human records dataset; (ii) applies a pre-written (for AQol-6D and EQ-5D instruments) or user-supplied instrument scoring function to a human records dataset; and (iii) generates descriptive plots of a dataset's instrument scores for individual items, domains and totals (weighted and unweighted).
+
+MUR 4) *Utility mapping model construction tools* that: (i) attach structured metadata about the target utility instrument and candidate predictor variables and covariates to a human records dataset; (ii) generate descriptive tables, a correlation matrix and plots about the variables to be assessed for inclusion in models; (iii) attach structured metadata about the candidate utility mapping models to be assessed; (iv) generate tabular and graphical summaries of the performance of each combination of model, predictors and covariates specified for evaluation by either a user or by a default algorithm; (v) strip confidential records from the constructed models so that they are able to be publicly shared.
+
+MUR 5) *Utility mapping reporting tools* that: (i) generate from a reporting template a PDF catalogue summarising the predictive performance under multiple configurations of utility mapping models selected for public dissemination; (ii) generate from a reporting template (either a pre-written default or a user-supplied customisation) a scientific summary manuscript summarising a utility mapping study; (iii) share model catalogues and (if desired) scientific summary along with metadata about utility mapping models in an open access repository; and (iv) facilitate the authoring of a single consolidated study reproducibility program that implements all steps inclusive of data ingest, instrument scoring, model construction, report authoring and dissemination of study artefacts.
+
+MUR 6) *Utility prediction tools* that: (i) search open access repositories for utility mapping models developed with readyforwhastnext; (ii) retrieve relevant metadata, including a link to the model catalogue for models specified by a user; (iii) applies selected utility mapping model to make out of sample predictions using a dataset provided by a user; and (iv) (where there is health utility data at two time points) convert predicted health utility scores to Quality Adjusted Life Years (QALYs).
+
+## Model implementation
+
+### Online service configuration
+We established and configured accounts with the online services supported by ready4.
+We created a GitHub organisation (a collection of code repositories) where source code that we author is stored and version controlled at https://github.com/ready4-dev/.
+We configured individual repositories in our GitHub organisation to implement continuous integration to assess the compliance of our module libraries with policies specified by the Comprehensive R Archive Network (CRAN) [@CRAN2022].
+<!-- To track our code coverage, we linked our GitHub organisation to an account we established at codecov [@codecov_2022].
+--> To facilitate the creation and hosting of module library websites, we enabled GitHub Pages in each code repository.
+We also created a Zenodo community, a collection of permanent, uniquely identified repositories, at https://zenodo.org/communities/ready4/.
+We then linked our Zenodo community and GitHub organisation so that every time we specify a version of code in one of our GitHub repositories as a “release”, a copy of that code is automatically archived on Zenodo with a DOI.
+Finally, to manage model datasets, we created a dedicated collection (https://dataverse.harvard.edu/dataverse/ready4) within the Harvard Dataverse installation.
+
+<!-- To track our code coverage, we linked our GitHub organisation to an account we established at codecov [@codecov_2022].  -->
+<!-- The framework also supports integrations with the open science repositories Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] that provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each code and data collection.
+-->
+<!-- The third party services that our framework is designed to work with include GitHub, Zenodo, Dataverse, -->
+<!-- codecov [@codecov_2022] -->
+
+### Outputs
 We have previously described a study [@Hamilton2021.07.07.21260129] to develop utility mapping models for use in samples of young people presenting to primary mental health services.
@@
 
+```{r, child = child_docs_ls$threeb, echo=FALSE}
+```
+
+(Table \@ref(tab:rfwnlibs)).
+
+## Documentation website
+We used functions from our foundation framework library to partially automate website updates relating to available CHEM modules, datasets and analysis programs.
+
+## Transferability assessment
 We created a checklist (Table \@ref(tab:checktb)) that we used to subjectively assess these study outputs against <!-- Edit_start -->explicit criteria for assessing transparent, reusable and updatable CHEMs that we have previously developed (add REF) <!-- Edit_end -->.

### 2024-02-23 Markdown/Manuscript/Child_RMDs/MS_Imp_Motivation.Rmd
nearly done on model

@@
 ## Transferability
-Although we are principally interested in using readyforwhatsnext to answer policy questions relating to the mental health of young people in Australia, we want to facilitate model transfer to other jurisdictions.
-The transferability requirements we have specified for readyforwhatsnext are to meet six explicit criteria for transparency, reusability and updatability.
-We have describe these criteria and their relationship to ethical modelling practice elsewhere [@ethicsCHEMS2024], but briefly they are:
+We are principally interested in using readyforwhatsnext to answer policy questions relating to the mental health of young people in Australia.
+Australian mental health services are primarily planned and commissioned by the Australian Government, the governments of Australia's state and territories and independent organisations focused on smaller regions called Primary Health Networks.
+Promoting mentally healthy local communities is also an important role for Australian local governments.
+Australia is an international leader in developing innovative youth mental health service models that are subsequently adopted in other jurisdictions [@RN27].
+For these reasons, we want readyforwhatsnext to be implemented in a manner that facilitates its transfer to multiple decision contexts.
+
+However, there are ethical risks associated with each potential transfer, in particular the need to ensure social acceptability, fitness for purpose and appropriate use of readyforwhatsnext in each new decision context.
+For that reason, we have set the goal of readyforwhatsnext meeting six explicit criteria for transparency, reusability and updatability (TRU criteria).
+We have describe these criteria and their origins in ethical modelling practice elsewhere [@ethicsCHEMS2024], but briefly they are:
+
+<!-- Model mutipurpose and complexity increasing validation [@Feenstra2022] -->
 
@@
 
-T3) Programming practices promote selective reuse;
+R1) Programming practices promote selective reuse;
 
-T4) Licenses permit derivative works; <!-- rephrase Liceses permit derivative works-->
+R2) Licenses permit derivative works; <!-- rephrase Liceses permit derivative works-->
 
-T5) Maintenance infrastructure is in place; and
+U1) Maintenance infrastructure is in place; and
 
-T6) Systematic retesting and deprecation.
+U6) Systematic retesting and deprecation.
 
-The readyforwhatsnext model is being derived from and applied to real Australian data (which can be empirical, simulated or assumption, so long as it is appropriate for use in analysis intended to inform decision-making).
+We are developing readyforwhatsnext using real Australian data (which can be empirical, simulated or assumption, so long as it is appropriate for use in analysis intended to inform decision-making).
 To help demonstrate the potential transferability of readyforwhatsnext to other decision contexts, we are also creating toy datasets.
-Toy data created for illustration purposes will be prominently labelled as not for use in decision-analysis.
-
-A high level schematic guiding our implementation of readyforwhatsnext as a modular and open source CHEM is outlined in Figure \@ref(fig:fig1).
+Toy data created for illustration purposes is prominently labelled as not for use in decision-analysis.
+<!-- PHNS -->
+A high level schematic guiding our implementation of readyforwhatsnext as a transferable CHEM is outlined in Figure \@ref(fig:fig1).
 

### 2024-02-23 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
nearly done on model

@@
 
-We began developing a prototype software framework in order to address a number of challenges we encountered during the planning and early implementation of readyforwhatsnext.
+To enable us to adopt a development approach to readyforwhatsnext that is consistent with meeting all six TRU criteria, we developed a prototype software framework.
 The software framework is called ready4.
 
-## User requirements
+## Framework user requirements
 We created ready4 with one primary user group in mind - ourselves.
-The user requirements (URs) for ready4 evolved over six years (2018-2024) as we became aware of new issues that we needed to solve.
+The framework user requirements (FURs) for ready4 evolved over six years (2018-2024) as we became aware of new issues that we needed to solve.
 Currently, these requirements are:
 
-UR 1) A *template module* for use in CHEM implementations in which modules can: (i) be run as independent models; (ii) safely combined, sharing inputs and outputs with each other without unintended interference; and (iii) be selectively replaced, updated or extended.
+FUR 1) A *template module* for use in CHEM implementations in which modules can: (i) be run as independent models; (ii) safely combined, sharing inputs and outputs with each other without unintended interference; and (iii) be selectively replaced, updated or extended.
 
-UR 2) *Developer tools* that integrate with online open source software development services to support streamlined workflows for authoring R libaries of CHEM modules that are: (i) created using the template module; (ii) written in a consistent house style; (iii) consistently documented; (iv) licensed for reuse; (v) bundled with citation data specifying authorship, funding source, version number and a Digital Object Identifier (DOI); and (vi) quality assured with publicly available acceptance and unit tests.
+FUR 2) A *programming syntax* that promotes simplicity and consistency in how algorithms associated with CHEM modules are described and used in health economic analysis programs.
 
-UR 3) A *programming syntax* that promotes simplicity and consistency in how algorithms associated with CHEM modules are described and used in health economic analysis programs.
+FUR 3) *Developer tools* that integrate with online software development services to support streamlined workflows for authoring R libaries of CHEM modules that are: (i) created using the template module; (ii) written in a consistent house style; (iii) consistently documented; (iv) licensed for reuse; (v) bundled with citation data specifying authorship, funding source, version number and a Digital Object Identifier (DOI); and (vi) quality assured with publicly available acceptance and unit tests.
 
-<!-- UR 4) Integration with online open source software development services to streamline the *authoring, testing, documenting and sharing of CHEM modules*.  -->
+<!-- FUR 4) Integration with online open source software development services to streamline the *authoring, testing, documenting and sharing of CHEM modules*.  -->
 
-UR 5) *Data management tools* that integrate with online data repository services to streamline the ingesting, labeling and sharing of publicly available and confidential data.
+FUR 4) *Data management tools* that integrate with online data repository services to streamline the ingesting, labeling and sharing of publicly available and confidential data.
 
-UR 6) *Reporting tools* that: (i) help author programs for generating analysis reports and scientific summaries from a template that can render documents in HTML, Adobe PDF and Microsoft Word file formats; (ii) retrieve version specific reporting template programs from online code repositories and (iii) supply study specific data (e.g authorship details, input data and analysis results) to reporting template programs to render reports and scientific summaries.
+FUR 5) *Reporting tools* that: (i) help author reporting template programs that render documents in HTML, Adobe PDF and Microsoft Word file formats; (ii) retrieve version specific reporting template programs from online code repositories and (iii) supply study specific data (e.g authorship details, input data and analysis results) to reporting template programs to render reports and scientific summaries.
 <!-- help generate tables for multiple outputs, retrieve templates, modify templates with authorship and results -->
 
-UR 7) *Search tools* to retrieve web based information on a CHEM project's: (i) publicly available model modules, module libraries and tutorials; (ii) datasets and data collections; and (iii) replication programs and reporting templates.
+FUR 6) *Search tools* to retrieve web based information on a CHEM project's: (i) publicly available model modules, module libraries and tutorials; (ii) datasets and data collections; and (iii) replication programs and reporting templates.
 
-UR 8) *Documentation tools* that integrate with open source website development and hosting infrastructure to help: (i) develop a consolidated project documentation website that synthesises data from mulitple code library websites and code and data repositories; and (ii) partially automate the updating of website resources such as tutorials and code and data release information.
+FUR 7) *Documentation tools* that integrate with open source website development and hosting infrastructure to help: (i) develop a consolidated project documentation website that synthesises content from the individual websites of the project's module libraries, datasets and programs; and (ii) partially automate the updating of website resources such as tutorials and itemised lists of code and data releases.
 
-## Implementation
+## Framework implementation
 <!-- The software framework aims to provide a toolkit for: (i) enabling modular implementation of CHEMs; (ii) authoring and documenting CHEM modules; (iii) managing the labelling and transfer of CHEM input and output data; and (iv) authoring reproducible analyses that apply CHEMs to compatible data.
 -->
-We implemented the software framework as R [@RCORE2022] code libraries that integrate with a number of online services and which are supported by a documentation website.
+We implemented ready4 as R [@RCORE2022] code libraries that integrate with a number of online services. The framework is documented by a project website.
 
@@
 Two notable features of object-oriented programming are encapsulation [@8717448] and inheritence [@8717448].
-Encapsulation allows a CHEM module to bundle model data and algorithms in a protected environment.
-Encapsulation can be used to help ensure that CHEM modules continue to work as intended when they are combined<!-- [@ready4oop2022] -->.
+Encapsulation allows a CHEM module to bundle model data and algorithms in a protected environment, which is useful for helping ensure that CHEM modules continue to work as intended when they are combined<!-- [@ready4oop2022] -->.
 Inheritence allows new CHEM modules to be created that inherit some or all of the properties of a parent module.
-Inheritence is useful in cases where it is necessary to update CHEM modules that are being combined to account for interaction effects.
-Inheritance also facilitates the selective editing of CHEM modules when transferring models to different decision contexts<!-- [@ready4oop2022] -->.
-The ready4 template CHEM module can therefore be used to create other CHEM modules that inherit common set of properties (meeting *UR 1*).
-One of these inherited properties is a novel syntax of 15 core commands that enable CHEM module algorithms to be consistently named (meeting *UR 3*).
-The foundation library also contains tools for retrieving web-based information on CHEM modules, datasets and analysis programs authored with ready4 (meeting *UR 7*) and tools for developing and maintaining a project documentation website (*UR 8*).
+Inheritence is useful in cases where it is necessary to update CHEM modules that are being combined to account for interaction effects or to selective edit CHEM modulesbeing transfered to different decision contexts<!-- [@ready4oop2022] -->.
+The ready4 template CHEM module can be used to create other CHEM modules that inherit a common set of properties (meeting *FUR 1*).
+One of these inherited properties is a novel syntax of 15 core commands that enable CHEM module algorithms to be consistently named (meeting *FUR 2*).
+The foundation library also contains tools for retrieving web-based information on CHEM modules, datasets and analysis programs authored with ready4 (meeting *FUR 6*) and tools for developing and maintaining a project documentation website (*FUR 7*).
 
-Three framework libraries are designed to meet *URs 2 and 4*.
+Three framework module authoring libraries are designed to meet *FUR 3*.
 <!-- Define functional and object-oriented approaches, acceptance and unit testing.
 -->The R language supports functional and object-oriented programming paradigms [@10.1214/13-STS452].
-Authoring with each of these paradigms is facilitated by a dedicated CHEM module authoring library.
+Authoring with each of these paradigms is supported by ready4.
 One module authoring library contains tools for writing functions in a consistent house style and automatically generating basic documentation for each function.
 A second module authoring library contains tools to help streamline and standardise the authoring of novel, documented CHEM modules from the template CHEM module.
-A third module authoring library provides tools for disseminating themed bundles of CHEM modules as R libraries that are:
+A third module authoring library provides tools for disseminating themed bundles of CHEM modules as R libraries that are: documented (with a website and PDF manuals); licensed (using the copyleft GNU GPL-3 [66] by default); easily citable (citation information can be retrieved within an R session or from hosting repositories); and quality assured (each update triggers continuous integration workflows, including any acceptance and unit tests created by module library authors).
 
--	documented (with a website and PDF manuals);
-
--	licensed (using the copyleft GNU GPL-3 [66] by default);
-
--	easily citable (citation information can be retrieved within an R session or from hosting repositories); and
-
--	quality assured (each update triggers continuous integration workflows, including any acceptance and unit tests created by module library authors).
-
-A library for managing CHEM data contains tools for supplying CHEM modules with input data ingested from local (i.e., a user's computer) or remote (online repositories) locations, labelling CHEM module datasets and exporting CHEM module data to online repositories (meeting *UR 5*).
-A library for authoring reproducible analysis programs and reporting subroutines (*UR6*) contains tools to help write executables that apply CHEM modules to compatible datasets for the purpose of undertaking health economic analyses.
+A library for managing CHEM data contains tools for supplying CHEM modules with input data ingested from local (i.e., a user's computer) or remote (online repositories) locations, labelling CHEM module datasets and exporting CHEM module data to online repositories (meeting *FUR 4*).
+A library for authoring reproducible analysis programs and reporting subroutines (*FUR5*) contains tools to help write executables that apply CHEM modules to compatible datasets for the purpose of undertaking health economic analyses.
 The library supports the creation of analysis programs that are self-documenting (code is integrated with plain English explanations of what it does) and subroutines that can be used as templates that trigger the creation of explanatory documents (e.g., a scientific manuscript).
@@
 The ready4 framework uses the GitHub [@github2007] service's tools for: software development, testing, version control and distribution; hosting of documentation websites; and transparent record keeping of collaborator contributions.
-A useful concept for informing software users about the extensiveness of testing procedures is code coverage [@ERICWONG2010188] - the proportion of code that has been explicitly tested.
+The continuous integration [@CI2017] tools provided by GitHub are used to trigger systematic retesting of module libraries with every edit.
+<!-- Imported -->These tests can be unit tests (to verify that small, isolated sections of code produce the correct output when run independently) and acceptance tests (to verify that the correct output is produced when multiple code components are run together to perform tasks that meet core user-requirements [@martin2003agile]).
+A useful concept for informing software users about the extensiveness of testing procedures is code coverage [@ERICWONG2010188] - reports of the proportion of code that has been explicitly tested.
 The ready4 framework uses the codecov [@codecov_2022] service to measure and share information about code coverage.
-The open science repository service Zenodo [@Zenodo2013] is used to provide persistent storage, uniquely identified with a a Digital Object Identifier (DOI), of each code release.
-
+<!-- End_Imported -->The open science repository service Zenodo [@Zenodo2013] is used to provide persistent storage, uniquely identified with a a Digital Object Identifier (DOI), of each code release.
 The framework's data management tools use the Dataverse [@Dataverse2007] data repository service for persistent, uniquely identifiable and versioned storage of model input and output data.
@@
 ###	Documentation website
-We developed a framework documentation website (https://www.ready4-dev.com) that provides guidance to model developers on how to use and contribute improvements to the ready4 software framework and CHEM modules developed with it.
+A project documentation website (https://www.ready4-dev.com) provides guidance to model developers on how to use and contribute improvements to the ready4 software framework.
 The documentation website is versioned, which means documentation relating to prior versions of framework software can be archived, retrieved and viewed.

### 2024-02-23 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
nearly done on model

--- 2024-02-20 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
@@
 <!-- Imported_from_Ethics-->Key concerns for health economists when considering whether to reuse a model are generalisability (application without adaptation) and transferability (selective reuse and/or modification of model components) [@RN39].
-<!-- End_Imported_from_Ethics -->A potential strategy for achieving both these goals is to make computational health economic models (CHEMs) both modular and open-source.
+Health economic models are likely to require at least some modification before they can be validly applied to a new jurisdiction, time period or decision problem.
+The difficulty of undertaking such a model transfer depends in part on whether the Computational Health Economic Model (CHEM) - the software files that implement the model - can be readily understood, used and edited.
+
+<!-- End_Imported_from_Ethics -->A potential strategy for implementing transferable CHEMs is to adopt a modular and open-source approach to model development.
 A modular model is constructed from multiple reusable and replaceable sub-models (modules) [@pan2021modular].
@@
 Advantages of modular models include feasibility (large projects are broken into smaller tasks, with each component independently developed and tested) and flexibility (making it easier to selectively replace or update specific parts of a model and to scale up or down the level of granularity) [@pan2021modular].
-Modular approaches are currently being used to facilitate the development of complex computational models in disciplines such as biology [@pan2021modular], ecology [@barros2023empowering] and neuroscience [@frazier2022robust].
-In health economics the related and enabling concept of reference models has been recommended [@Afzali2013], but peer reviewed studies describing modular health economic models remain relatively rare, though examples exist in infectious disease [@Trauer2017] and cardiology [@Urach2013].
+Modular approaches have been used to facilitate the development of complex computational models in disciplines such as biology [@pan2021modular], ecology [@barros2023empowering] and neuroscience [@frazier2022robust].
+In health economics the related and enabling concept of reference models has been recommended [@Afzali2013].
+Peer reviewed studies describing modular health economic models remain relatively rare, though examples exist in infectious disease [@Trauer2017] and cardiology [@Urach2013].
 
-Modular CHEMs provide an opportunity for multiple modelling teams to contribute to, test and reuse models.
-To enhance this capacity, modular CHEMs may be implemented as open source projects that give others liberal permissions to access and use model source code and data [@pan2021modular; @barros2023empowering; @frazier2022robust].
-Although there appears to be in principle support from many health economists for greater use of open source CHEMs  [@Pouwels2022], actual implementations are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022].
-Barriers to adoption of open source CHEMs include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations [@Pouwels2022; @Wu2019].
-<!-- Adherence to good practice guidance is an essential requirement for healthcare modelling [@Erdemir2020], but  --><!-- Guidelines for implementing open source CHEMs remain scarce, piecemeal and need improving [@Sampson2019].
--->As many health economic models are owned by pharmaceutical companies and consultancies, commercial considerations can limit the reuse of models and their constituent code and data [@Feenstra2022].
-Legal and ethical issues such as privacy and confidentiality requirements further limit public release of some model artefacts [@Pouwels2022].
+<!-- Modular CHEMs provide an opportunity for multiple modelling teams to contribute to, test and reuse models.  -->
+A number of modular modelling projects have been implemented as open source projects that give others liberal permissions to access and use model source code and data [@pan2021modular; @barros2023empowering; @frazier2022robust].
+Many health economists support greater use of open-source CHEMs as a means of improving model transparency, promoting model reuse, making model development more efficient and gaining the confidence of model users [@Pouwels2022].
+However, actual implementations of open-source CHEMs are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022], with barriers to adoption including concerns about intellectual property, confidentiality, model misuse and the resources required to maintain open source implementations [@Pouwels2022; @Wu2019].
+<!--Benefits --><!-- Adherence to good practice guidance is an essential requirement for healthcare modelling [@Erdemir2020], but  --><!-- Guidelines for implementing open source CHEMs remain scarce, piecemeal and need improving [@Sampson2019].
+-->Health economic models can be owned by pharmaceutical companies and consultancies, so commercial considerations can limit the reuse of models and their constituent code and data [@Feenstra2022].
+Barriers relating to model generalisability and transferability and the software platforms used to implement CHEMs are also important [@Pouwels2022].
 
@@
 
-Some of the barriers<!-- Give examples --> to the development of open-source and modular CHEMs may be amenable to technical solutions such as software frameworks.<!-- Check last sentence was not used in ethics manuscript  --> A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users [@myllarniemi2018development].
+Some of the technical barriers<!-- Give examples --> to the development of transferable CHEMs could be addressed by appropriate software frameworks.<!-- Check last sentence was not used in ethics manuscript  --> A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users [@myllarniemi2018development].
 A software framework provides a foundation for developing multiple software applications with shared resources (e.g., code and data files), that can be modified to suit specific needs.

### 2024-02-23 Markdown/Manuscript/Child_RMDs/MS_Tables.Rmd
nearly done on model

--- 2023-08-16 Markdown/Manuscript/Child_RMDs/MS_Tables.Rmd
@@
 if(params$X@tables_in_body_lgl){
-  child_docs_ls <- list(one = "../Child_RMDs/MS_Tables_1.Rmd",
-                        two = "../Child_RMDs/MS_Tables_2.Rmd",
+  child_docs_ls <- list(
+    one = NULL,
+    # "../Child_RMDs/MS_Tables_1.Rmd",
+                        two = NULL,
+    # "../Child_RMDs/MS_Tables_2.Rmd",
                         three = "../Child_RMDs/MS_Tables_3.Rmd",
+    threeb = "../Child_RMDs/MS_Tables_3b.Rmd", 
                         four = "../Child_RMDs/MS_Tables_4.Rmd")
@@
                           three = NULL,
+                          threeb = NULL,
                           four = NULL)

### 2024-02-23 Markdown/Manuscript/Child_RMDs/MS_Tables_3b.Rmd
nearly done on model

---
title: "Predr_Cors"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
```{r rfwnlibs, tab.cap='readyforwhatsnext module libraries for utility mapping', tab.id = 'cpkgs', echo = F, results = 'asis'}
library(kableExtra)  
df <- tibble::tibble(Package = c("youthvars",
                                       "scorz",
                                       "specific",
                                       "TTU",
                                       "youthu"),
                     Purpose = c("Describe and validate youth mental health human record datasets.",
                                 "Score multi-attribute instruments.",
                                 "Construct and evaluate utility mapping models.",
                                 "Implement reproducible utility mapping sudies.",
                                 "Apply utility mapping models to out of sample data."),
                           `R library dependencies` = Package %>%
                             purrr::map(~ {
                               utils::packageDescription(.x) %>%
                                 `[`(c("Depends", "Imports")) %>%
                                 purrr::map(~{
                                   if(is.null(.x)){
                                     character(0)
                                     }else{
                                       .x %>%
                                         strsplit(",\\n") %>%
                                         purrr::flatten_chr() %>%
                                         purrr::map(~strsplit(.x,", ") %>%
                                                      purrr::flatten_chr()) %>%
                                         purrr::flatten_chr() %>% sort() %>%
                                         purrr::discard(~startsWith(.x,"R "))
                                       }
                                   }) %>%
                                 purrr::flatten_chr() %>%
                                 unique() %>%
                                 sort() %>%
                                 purrr::map_chr(~{
                                   updated_1L_chr <- stringr::str_replace_all(.x,"\\n"," ")
                                   problem_idx_1L_chr <- stringr::str_locate(updated_1L_chr," ")[1,1] %>%
                                     unname()
                                   if(!is.na(problem_idx_1L_chr))
                                     updated_1L_chr <- updated_1L_chr %>%
                                     stringr::str_sub(end = problem_idx_1L_chr-1)
                                   updated_1L_chr %>% 
                                     trimws(which = "left") 
                                   })
                               }) %>% 
                             purrr::map_chr (~ .x %>% paste0(collapse = " "))) %>% 
  as.data.frame() 
df <- df %>%
  dplyr::select(Package,
                Purpose,
                `R library dependencies`)

names_chr <- names(df)
if(params$X@outp_formats_chr[1] == "Word") {
  library("flextable")
  library("ftExtra")
  df %>% 
    ready4show::print_table(output_type_1L_chr = params$X@outp_formats_chr[1],
                            caption_1L_chr = knitr::opts_current$get("tab.cap"),
                            mkdn_tbl_ref_1L_chr = paste0("tab:",knitr::opts_current$get("tab.id")),
                            use_rdocx_1L_lgl = ifelse(params$X@outp_formats_chr[1]=="Word",T,F),
                            add_to_row_ls = NULL,
                            sanitize_fn = NULL) %>%
    ftExtra::colformat_md()
  }else{
    df %>%
      kableExtra::kbl(booktabs = T, 
                      escape = F,
                      caption = knitr::opts_current$get("tab.cap")) %>%
      kableExtra::kable_paper(full_width = F) %>%
      kableExtra::column_spec(2, width = "20em", latex_valign = "m") %>%
      kableExtra::column_spec(3, width = "20em",
                              latex_valign = "m")
    }
```

### 2024-02-23 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
onto discussion

@@
 
-### Outputs
-We have previously described a study [@Hamilton2021.07.07.21260129] to develop utility mapping models for use in samples of young people presenting to primary mental health services.
-The ready4 software framework was used in that study to develop CHEM modules, supply those modules with data and implement modelling analyses, creating the following artefacts:
+### Modules
+We used all six ready4 framework libraries to author five development version readyforwhatsnext module libraries (Table \@ref(tab:rfwnlibs)).
+These libraries are youthvars [@hamilton_matthew_2022_6084467] which addresses MURs 1 and 2, scorz [@hamilton_matthew_2022_6084824] which addresses MUR 3, specific [@hamilton_matthew_2022_6116701] which addresses MUR 4, TTU [@gao_caroline_2022_6130155] which addresses MUR 5 and youthu [@matthew_p_hamilton_2021_5646669] which addresses MUR 6.
 
-- development version module libraries for describing and validating youth mental health human record datasets [@hamilton_matthew_2022_6084467], scoring health utility [@hamilton_matthew_2022_6084824], specifying utility mapping models [@hamilton_matthew_2022_6116701] and implementing reproducible utility mapping studies [@gao_caroline_2022_6130155];
+### Reporting templates
+We used the framework reporting tools library to author two reporting templates that are designed to be used in conjunction with these utility mapping models.
+The first reporting template is used to create a catalogue of utility mapping models [@hamilton_matthew_2022_6116385].
+The second reporting template can be used to generate a manuscript [@matthew_p_hamilton_2022_5976988] providing a scientific summary of each study implemented with these modules.
 
- - a development version library of functions for finding and using utility mapping models developed with these tools [@matthew_p_hamilton_2021_5646669];
-
- - collections of real data (study input and results [@DVN/DKDIB0_2021]) and toy data (synthetic populations for testing model modules [@DVN/HJXYKQ_2021]);
-
- - programs for replicating all steps from data ingest to manuscript production [@hamilton_matthew_2022_6129906], applying utility mapping models to new data [@hamilton_matthew_2022_6416330] and generating a synthetic representation of the study dataset [@hamilton_matthew_p_2022_6321821]; and
-
- - subroutines for creating a catalogue of utility mapping models [@hamilton_matthew_2022_6116385] and generating a draft scientific manuscript [@matthew_p_hamilton_2022_5976988] for studies implemented with these modules.
+### Application
+We have previously described a study [@Hamilton2021.07.07.21260129] that used applied these modules and reporting templates to develop utility mapping models in a sample of young people presenting to primary mental health services.
+We used these module libraries to write programs that reproduced that study's reporting and analysis algorithm [@hamilton_matthew_2022_6129906], to demonstratehow to applying the utility mapping models constructed in that study to new data [@hamilton_matthew_2022_6416330] and to generate a synthetic representation of the study dataset [@hamilton_matthew_p_2022_6321821].
+We also created an open access study input parameters and results dataset [@DVN/DKDIB0_2021]) and toy datasets to help demonstrate the transferability of the study algorithm [@DVN/HJXYKQ_2021]).
 
@@
 
-(Table \@ref(tab:rfwnlibs)).
-
 ## Documentation website
-We used functions from our foundation framework library to partially automate website updates relating to available CHEM modules, datasets and analysis programs.
+We created a documentation website (https://readyforwhatsnext.org/) using functions from our foundation framework library to partially automate content updates relating to available modules, datasets and analysis programs.
 
 ## Transferability assessment
-We created a checklist (Table \@ref(tab:checktb)) that we used to subjectively assess these study outputs against <!-- Edit_start -->explicit criteria for assessing transparent, reusable and updatable CHEMs that we have previously developed (add REF) <!-- Edit_end -->.
+We created a checklist (Table \@ref(tab:checktb)) that we used to subjectively assess these study outputs against <!-- Edit_start -->our TRU criteria <!-- Edit_end -->.
 For each criterion, we provided a global assessment of whether it was met using the responses “yes”, “no” or “partial”.
-We believe our utility mapping study CHEMs have satisfactorily met five of the six criteria (T1, T2, R1, R2 and U1) and have partially met one criterion (U2).
+We believe our utility mapping study modules have satisfactorily met five of the six criteria (T1, T2, R1, R2 and U1) and have partially met one criterion (U2).
 The main shortcomings that we identified when applying the assessment criteria was that we have yet to adequately implement unit testing of the R libraries authored as part of this study.

### 2024-02-25 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
on to discussion

@@
 ## Model user requirements
-The initial model user requirements (MURs) that we specified for initial readyforwhatsnext modules we developed for utility mapping were:
+The initial model user requirements (MURs) that we specified for the readyforwhatsnext modules we developed for utility mapping are:
 
@@
 
-MUR 2) *Dataset description tools* that: (i) attach metadata to a human records dataset that specifies the unique person identifier, group assignment and data collection round variables; and (ii) generate tabular and graphical summaries of dataset descriptive statistics.
+MUR 2) *Dataset description tools* that: (i) attach structured metadata to a human records dataset that specify the unique person identifier, group assignment and data collection round variables; and (ii) generate tabular and graphical summaries of dataset descriptive statistics.
 
@@
 
-MUR 4) *Utility mapping model construction tools* that: (i) attach structured metadata about the target utility instrument and candidate predictor variables and covariates to a human records dataset; (ii) generate descriptive tables, a correlation matrix and plots about the variables to be assessed for inclusion in models; (iii) attach structured metadata about the candidate utility mapping models to be assessed; (iv) generate tabular and graphical summaries of the performance of each combination of model, predictors and covariates specified for evaluation by either a user or by a default algorithm; (v) strip confidential records from the constructed models so that they are able to be publicly shared.
+MUR 4) *Utility mapping model construction tools* that: (i) attach structured metadata about the target utility instrument and candidate predictor variables and covariates to be used in constructing utility mapping models to a human records dataset; (ii) generate descriptive tables, a correlation matrix and plots about the variables to be assessed for inclusion in models; (iii) attach structured metadata about the candidate utility mapping models to be assessed; (iv) generate tabular and graphical summaries of the performance of each combination of model, predictors and covariates specified for evaluation by either a user or by a default algorithm; (v) strip confidential records from the constructed models so that they are able to be publicly shared.
 

### 2024-02-25 Markdown/Manuscript/Child_RMDs/MS_Imp_Motivation.Rmd
on to discussion

@@
 
-We became interested in modular and open-source approaches to CHEM development in 2018 when beginning to plan how to synthesise a number of current or planned economic modelling projects in youth mental health in one multi-purpose model.
+We became interested in solving some of the technical barriers to transferable CHEMs in 2018 when considering how to synthesise multiple youth mental health economic modelling projectsin one multi-purpose model.
 This overarching youth mental health model is called readyforwhatsnext [@rfwn2024].
@@
 ## Economic topics
-Initially, we are constructing readyforwhatsnext from projects in four of the twelve domains of health economics identified by Wagstaff and Culyer [@wagstaff2012four]:
+We are constructing readyforwhatsnext from projects in four of the twelve domains of health economics identified by Wagstaff and Culyer [@wagstaff2012four]. These are:
 
@@
 
-Potential future directions could incorporate projects in two additional Wagstaff and Culyer domains of: (i) public health (to model the impact of selected fiscal policy and regulation options on young people's mental health); and (ii) human resources (to model the supply and behaviours of the youth mental health workforce).
+Potential future directions for readyforwhatsnext may incorporate projects in two additional Wagstaff and Culyer domains of: (i) public health (to model the impact of selected fiscal policy and regulation options on young people's mental health); and (ii) human resources (to model the supply and behaviours of the youth mental health workforce).
 Our ultimate aim is for readyforwhatsnext to flexibly combine its constituent parts in analyses that help answer questions in two additional Wagstaff and Culyer domains:
@@
 We are principally interested in using readyforwhatsnext to answer policy questions relating to the mental health of young people in Australia.
-Australian mental health services are primarily planned and commissioned by the Australian Government, the governments of Australia's state and territories and independent organisations focused on smaller regions called Primary Health Networks.
+Australian public mental health services can be planned and commissioned by the Australian Government, the governments of Australia's state and territories and independent organisations focused on smaller regions called Primary Health Networks.
 Promoting mentally healthy local communities is also an important role for Australian local governments.
-Australia is an international leader in developing innovative youth mental health service models that are subsequently adopted in other jurisdictions [@RN27].
-For these reasons, we want readyforwhatsnext to be implemented in a manner that facilitates its transfer to multiple decision contexts.
+The mental health of young people is a global priority [@https://doi.org/10.1002/wps.20938] and Australia has initiated youth mental health service model reforms that have been adopted in other jurisdictions [@RN27].
+For these reasons, we aim to develop readyforwhatsnext in a manner that facilitates its transfer to multiple decision contexts.
 
-However, there are ethical risks associated with each potential transfer, in particular the need to ensure social acceptability, fitness for purpose and appropriate use of readyforwhatsnext in each new decision context.
+However, there are ethical risks associated with each potential transfer, in particular the need to ensure the social acceptability, fitness for purpose and appropriate use of readyforwhatsnext in each new decision context [@ethicsCHEMS2024].
 For that reason, we have set the goal of readyforwhatsnext meeting six explicit criteria for transparency, reusability and updatability (TRU criteria).
@@
 
-U6) Systematic retesting and deprecation.
+U6) Software is systematically retested and deprecated.
 

### 2024-02-25 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
on to discussion

@@
 
-To enable us to adopt a development approach to readyforwhatsnext that is consistent with meeting all six TRU criteria, we developed a prototype software framework.
-The software framework is called ready4.
+To help readyforwhatsnext meet all six TRU criteria, we developed a prototype software framework. The software framework is called ready4 [@ready424].
 
@@
 
-FUR 1) A *template module* for use in CHEM implementations in which modules can: (i) be run as independent models; (ii) safely combined, sharing inputs and outputs with each other without unintended interference; and (iii) be selectively replaced, updated or extended.
+FUR 1) A reusable *template* for CHEM modules that can: (i) be run as independent models; (ii) safely combined, sharing inputs and outputs with each other without unintended interference; and (iii) be selectively replaced, updated or extended.
 
-FUR 2) A *programming syntax* that promotes simplicity and consistency in how algorithms associated with CHEM modules are described and used in health economic analysis programs.
+FUR 2) A *programming syntax* that promotes simplicity and consistency in how algorithms associated with CHEM modules are: (i) labelled; and (ii) used in health economic analysis programs.
 
-FUR 3) *Developer tools* that integrate with online software development services to support streamlined workflows for authoring R libaries of CHEM modules that are: (i) created using the template module; (ii) written in a consistent house style; (iii) consistently documented; (iv) licensed for reuse; (v) bundled with citation data specifying authorship, funding source, version number and a Digital Object Identifier (DOI); and (vi) quality assured with publicly available acceptance and unit tests.
+FUR 3) *Module authoring tools* that integrate with online software development services to help author R libraries of CHEM modules that are: (i) created using the template module; (ii) written in a consistent house style; (iii) always at least minimally documented; (iv) licensed for reuse; (v) bundled with authorship, funding source, version number and a Digital Object Identifier (DOI) metadata; and (vi) quality assured with publicly available testing artefacts.
 
@@
 
-FUR 4) *Data management tools* that integrate with online data repository services to streamline the ingesting, labeling and sharing of publicly available and confidential data.
+FUR 4) *Data management tools* that integrate with online data repository services to streamline: (i) the ingesting and labeling of confidential and non-confidential data; and  (ii) the sharing of non-confidential data.
 
-FUR 5) *Reporting tools* that: (i) help author reporting template programs that render documents in HTML, Adobe PDF and Microsoft Word file formats; (ii) retrieve version specific reporting template programs from online code repositories and (iii) supply study specific data (e.g authorship details, input data and analysis results) to reporting template programs to render reports and scientific summaries.
+FUR 5) *Reporting tools* that: help (i) author reporting templates that render documents in HTML, Adobe PDF and Microsoft Word file formats; (ii) retrieve version specific reporting templates  from online code repositories and (iii) supply study specific data (e.g authorship details, input data and analysis results) to reporting templates to render reports and scientific summaries.
 <!-- help generate tables for multiple outputs, retrieve templates, modify templates with authorship and results -->
@@
 
-FUR 7) *Documentation tools* that integrate with open source website development and hosting infrastructure to help: (i) develop a consolidated project documentation website that synthesises content from the individual websites of the project's module libraries, datasets and programs; and (ii) partially automate the updating of website resources such as tutorials and itemised lists of code and data releases.
+FUR 7) *Documentation tools* that integrate with open source website development and hosting infrastructure to help: (i) develop a project documentation website that consolidates content from the websites of individual module libraries, datasets and programs; and (ii) partially automate the updating of website resources such as tutorials and itemised lists of code and data releases.
 
@@
 Two notable features of object-oriented programming are encapsulation [@8717448] and inheritence [@8717448].
-Encapsulation allows a CHEM module to bundle model data and algorithms in a protected environment, which is useful for helping ensure that CHEM modules continue to work as intended when they are combined<!-- [@ready4oop2022] -->.
-Inheritence allows new CHEM modules to be created that inherit some or all of the properties of a parent module.
-Inheritence is useful in cases where it is necessary to update CHEM modules that are being combined to account for interaction effects or to selective edit CHEM modulesbeing transfered to different decision contexts<!-- [@ready4oop2022] -->.
+Encapsulation allows a CHEM module to bundle model data and algorithms in a protected environment, which is useful for helping ensure that CHEM modules continue to work as intended when combined<!-- [@ready4oop2022] -->.
+Inheritence allows new CHEM modules to inherit some or all of the properties of a parent module.
+Inheritence is useful when it is necessary to selectively modify CHEM modules, for example to that to account for interaction effects when CHEMs are combined or to account for the features of a different decision contexts to which they are being transferred<!-- [@ready4oop2022] -->.
 The ready4 template CHEM module can be used to create other CHEM modules that inherit a common set of properties (meeting *FUR 1*).
@@
 ###	Online services 
-Framework libraries are designed to be used in conjunction with a number of third-party online services that users of ready4 will need to establish and configure accounts with.
-The framework's developer tools integrate with online code development, testing and archiving services.
+Framework libraries are designed to be used in conjunction with a number of third-party online services that developers using ready4 need to establish and configure accounts with.
+The framework's module authoring tools integrate with online code development, testing and archiving services.
 The ready4 framework uses the GitHub [@github2007] service's tools for: software development, testing, version control and distribution; hosting of documentation websites; and transparent record keeping of collaborator contributions.

### 2024-02-25 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
on to discussion

@@
 Health economic models are likely to require at least some modification before they can be validly applied to a new jurisdiction, time period or decision problem.
-The difficulty of undertaking such a model transfer depends in part on whether the Computational Health Economic Model (CHEM) - the software files that implement the model - can be readily understood, used and edited.
+The difficulty of undertaking such a model transfer depends in part on whether third parties can readily understand, use and edit the software files that implement the model - the Computational Health Economic Model (CHEM).
 
-<!-- End_Imported_from_Ethics -->A potential strategy for implementing transferable CHEMs is to adopt a modular and open-source approach to model development.
+<!-- End_Imported_from_Ethics -->A potential strategy for implementing transferable CHEMs is to adopt an open-source and modular approach to model development.
+Open source projects grant third parties liberal permissions to access, use and modify model source code and data.
+Many health economists support greater use of open-source CHEMs as a means of improving model transparency, promoting model reuse, making model development more efficient and gaining the confidence of model users [@Pouwels2022].
+A number of complex open source computational modelling projects in disciplines such as biology [@pan2021modular], ecology [@barros2023empowering] and neuroscience [@frazier2022robust] have been implemented as modular models.
 A modular model is constructed from multiple reusable and replaceable sub-models (modules) [@pan2021modular].
@@
 Advantages of modular models include feasibility (large projects are broken into smaller tasks, with each component independently developed and tested) and flexibility (making it easier to selectively replace or update specific parts of a model and to scale up or down the level of granularity) [@pan2021modular].
-Modular approaches have been used to facilitate the development of complex computational models in disciplines such as biology [@pan2021modular], ecology [@barros2023empowering] and neuroscience [@frazier2022robust].
-In health economics the related and enabling concept of reference models has been recommended [@Afzali2013].
-Peer reviewed studies describing modular health economic models remain relatively rare, though examples exist in infectious disease [@Trauer2017] and cardiology [@Urach2013].
 
 <!-- Modular CHEMs provide an opportunity for multiple modelling teams to contribute to, test and reuse models.  -->
-A number of modular modelling projects have been implemented as open source projects that give others liberal permissions to access and use model source code and data [@pan2021modular; @barros2023empowering; @frazier2022robust].
-Many health economists support greater use of open-source CHEMs as a means of improving model transparency, promoting model reuse, making model development more efficient and gaining the confidence of model users [@Pouwels2022].
-However, actual implementations of open-source CHEMs are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022], with barriers to adoption including concerns about intellectual property, confidentiality, model misuse and the resources required to maintain open source implementations [@Pouwels2022; @Wu2019].
+<!-- @Jansen2019 -->
+<!-- @thokala2023living LIVING HTA-->
+<!-- https://www.ispor.org/publications/journals/value-outcomes-spotlight/vos-archives/issue/view/addressing-assessment-and-access-issues-for-rare-diseases/the-role-of-education-in-shaping-an-open-source-future -->
+Actual implementations of open-source CHEMs are relatively rare [@Emerson2019; @Michalczyk2018; @Feenstra2022].
+Recent efforts to build this field including an initiative to develop a suite of open source CHEMs addressing different health conditions in the United States [@Jansen2019] and a Canadian platform facilitating access to and validation of multiple CHEMs [@harvard2022developing].
+Modular health economic models are also rare, though examples exist in infectious disease [@Trauer2017] and cardiology [@Urach2013].
+Barriers to greater use of open-source approaches include health economist concerns about intellectual property, confidentiality, model misuse and the resources required to maintain open source implementations [@Pouwels2022; @Wu2019].
 <!--Benefits --><!-- Adherence to good practice guidance is an essential requirement for healthcare modelling [@Erdemir2020], but  --><!-- Guidelines for implementing open source CHEMs remain scarce, piecemeal and need improving [@Sampson2019].
--->Health economic models can be owned by pharmaceutical companies and consultancies, so commercial considerations can limit the reuse of models and their constituent code and data [@Feenstra2022].
-Barriers relating to model generalisability and transferability and the software platforms used to implement CHEMs are also important [@Pouwels2022].
-
+-->When health economic models are owned by pharmaceutical companies and consultancies, commercial considerations may also limit the reuse of models and their constituent code and data [@Feenstra2022].
+Health econmists have also identified issues relating to model generalisability and transferability and model implementation software platforms as important barriers to open-source CHEMs [@Pouwels2022].
+We are not aware of published literature identifying barriers to modular CHEMs, but potentially these may relate to the limited benefit of undertaking modular approaches in projects that are not also open-source.
+<!-- Move to discussion--><!-- In health economics the related and enabling concept of reference models has been recommended [@Afzali2013].  -->
 <!-- Transferring a health economic model developed for one jurisdiction for application in another typically involves retaining some features and updating others [@barbieri2010international].
@@
 -->
-
 <!-- Open-source CHEMs remain rare [@Feenstra2022; @Emerson2019].
@@
 -->
-
 <!-- typically have a number of limitations that at best restrict their usefulness and which in some cases may facilitate harmful misuse. -->
 
-Some of the technical barriers<!-- Give examples --> to the development of transferable CHEMs could be addressed by appropriate software frameworks.<!-- Check last sentence was not used in ethics manuscript  --> A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users [@myllarniemi2018development].
+Some of the technical barriers<!-- Give examples --> to the development of transferable CHEMs that use open-source and modular approaches could be addressed by appropriate software frameworks.<!-- Check last sentence was not used in ethics manuscript  --> A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users [@myllarniemi2018development].
 A software framework provides a foundation for developing multiple software applications with shared resources (e.g., code and data files), that can be modified to suit specific needs.

### 2024-02-25 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
abstract updated

@@
 
-MUR 3) *Multi-attribute instrument tools* that: (i) attaches structured metadata about an instrument (e.g.
-name, version, country, items, domains, parameter values for scoring algorithms) to a human records dataset; (ii) applies a pre-written (for AQol-6D and EQ-5D instruments) or user-supplied instrument scoring function to a human records dataset; and (iii) generates descriptive plots of a dataset's instrument scores for individual items, domains and totals (weighted and unweighted).
+MUR 3) *Multi-attribute instrument scoring tools* that: (i) attach structured metadata about an instrument (e.g.
+name, version, country, items, domains, parameter values for scoring algorithms) to a human records dataset; (ii) apply pre-written (for AQol-6D and EQ-5D instruments) or user-supplied instrument scoring functions to a human records dataset; and (iii) generate descriptive plots of a dataset's instrument scores for individual items, domains and totals (weighted and unweighted).
 
@@
 
-MUR 5) *Utility mapping reporting tools* that: (i) generate from a reporting template a PDF catalogue summarising the predictive performance under multiple configurations of utility mapping models selected for public dissemination; (ii) generate from a reporting template (either a pre-written default or a user-supplied customisation) a scientific summary manuscript summarising a utility mapping study; (iii) share model catalogues and (if desired) scientific summary along with metadata about utility mapping models in an open access repository; and (iv) facilitate the authoring of a single consolidated study reproducibility program that implements all steps inclusive of data ingest, instrument scoring, model construction, report authoring and dissemination of study artefacts.
+MUR 5) *Utility mapping study reporting tools* that: (i) generate from a reporting template a PDF catalogue summarising the predictive performance under multiple configurations of utility mapping models selected for public dissemination; (ii) generate from a reporting template (either a pre-written default or a user-supplied customisation) a scientific summary manuscript summarising a utility mapping study; (iii) share model catalogues and (if desired) scientific summary along with metadata about utility mapping models in an open access repository; and (iv) facilitate the authoring of a single consolidated study reproducibility program that implements all steps inclusive of data ingest, instrument scoring, model construction, report authoring and dissemination of study artefacts.
 
@@
 We have previously described a study [@Hamilton2021.07.07.21260129] that used applied these modules and reporting templates to develop utility mapping models in a sample of young people presenting to primary mental health services.
-We used these module libraries to write programs that reproduced that study's reporting and analysis algorithm [@hamilton_matthew_2022_6129906], to demonstratehow to applying the utility mapping models constructed in that study to new data [@hamilton_matthew_2022_6416330] and to generate a synthetic representation of the study dataset [@hamilton_matthew_p_2022_6321821].
+We used these module libraries to write programs that reproduced that study's reporting and analysis algorithm [@hamilton_matthew_2022_6129906], to demonstrate how to applying the utility mapping models constructed in that study to new data [@hamilton_matthew_2022_6416330] and to generate a synthetic representation of the study dataset [@hamilton_matthew_p_2022_6321821].
 We also created an open access study input parameters and results dataset [@DVN/DKDIB0_2021]) and toy datasets to help demonstrate the transferability of the study algorithm [@DVN/HJXYKQ_2021]).
@@
 ## Documentation website
-We created a documentation website (https://readyforwhatsnext.org/) using functions from our foundation framework library to partially automate content updates relating to available modules, datasets and analysis programs.
+We used using the search and documentation tools from our foundation framework library to
+create and help maintain a documentation website (https://readyforwhatsnext.org/) that includes details on available model modules, datasets and analysis programs and tutorials on using model modules.
 
 ## Transferability assessment
-We created a checklist (Table \@ref(tab:checktb)) that we used to subjectively assess these study outputs against <!-- Edit_start -->our TRU criteria <!-- Edit_end -->.
+We subjectively assessed these utility mapping model artefacts against <!-- Edit_start -->our TRU criteria <!-- Edit_end --> (Table \@ref(tab:checktb)).
 For each criterion, we provided a global assessment of whether it was met using the responses “yes”, “no” or “partial”.
-We believe our utility mapping study modules have satisfactorily met five of the six criteria (T1, T2, R1, R2 and U1) and have partially met one criterion (U2).
-The main shortcomings that we identified when applying the assessment criteria was that we have yet to adequately implement unit testing of the R libraries authored as part of this study.
+We believe our utility mapping study modules have satisfactorily met four of the six criteria (T1, R1, R2 and U1) and have partially met two criteria (T2 and U2).
+The main shortcomings that we identified when applying the assessment criteria was that we have yet to: (i) ensure that module library documentation includes examples of how to apply all exported methods and functions; and (ii) adequately implement unit testing.
 

### 2024-02-25 Markdown/Manuscript/Child_RMDs/MS_Tables_4.Rmd
abstract updated

@@
 df <- data.frame(Criterion = c("T1 Software files are open access", 
-                               "T2 Project team contributions and judgments are easily identified", 
-                               "R1 Programming practices promote generalisability and transferability",
-                               "R2 Licenses restrict only unethical reuse",
+                               "T2 Developer contributions and judgments on appropriate use are easily identified", 
+                               "R1 Programming practices promote selective reuse",
+                               "R2 Licenses permit derivative works",
                                "U1 Maintenance infrastructure is in place",
-                               "U2 New releases are systematically retested and deprecated"),
-                 `Met?` = c(rep("Yes",5),"Partial"),
+                               "U2 Releases are systematically retested and deprecated"),
+                 `Met?` = c("Yes","Partial",rep("Yes",3),"Partial"),
                  Detail = c("All source code and testing procedures are available in public GitHub repositories, with each code release persistently available in a Zenodo repository.
@@
 Each code library is documented with worked examples of how to apply CHEM modules.
+However, documentation of individual functions and methods need more examples.
 Analysis and reporting programs are self-documenting.

### 2024-02-25 setup.R

@@ -37,16 +37,20 @@ X <- renewSlot(X,
                "abstract_args_ls",
                {
                  args_ls <- X@abstract_args_ls
-                 args_ls$abstract_ls <- list(Summary = "To facilitate Computational Health Economic Models (CHEMs) that are Transparent, Reusable and Updatable (TRU), we have developed a prototype software framework in the open-source programming language R.
-                                                        The framework comprises six code libraries for authoring CHEMs, supplying CHEMs with data and undertaking analyses with CHEMs. 
-                                                        The prototype software framework integrates with services for software development and research data archiving. 
-                                                        We used the framework to developed an initial set of utility mapping CHEMs in youth mental health that can be assessed as meeting explicit TRU criteria.
-                                                        Our software framework has potential value as a prototype for future tools to support ethical implementation of CHEMs.",
+                 args_ls$abstract_ls <- list(Summary = "We are developing an open source and modular Computational Health Economic Model (CHEM) in youth mental health.
+                                                        In order for that CHEM to be readily transferable to multiple jurisdictions, we aim for it to meet six explicit transparency, reusability and updatability (TRU) criteria.
+                                                        These criteria are: (T1) open access software files; (T2) easily identifiable developer contributions and judgments; (R1) programming practices promote selective reuse; (R2) permissions for derivative works; (U1) maintenance infrastructure; and (U2) systematic retesting and deprecation.
+                                                        To overcome technical challenges to achieving this goal, we developed a prototype software framework.
+                                                        We specified framework user requirements for a template CHEM module, a simple programming syntax and tools for authoring new CHEM modules, supplying CHEMs with data, reporting reproducible analyses, searching for CHEM modules and maintaining a project website.
+                                                        We developed the framework as six development version code libraries in the open-source programming language R that integrate with online services for software development and research data archiving. 
+                                                        We used the framework to author five development version R libraries of utility mapping CHEM modules in youth mental health that provide tools for variable validation, dataset description, multi-attribute instrument scoring, construction of mapping models, reporting of mapping studies and making out of sample predictions.
+                                                        We assessed these utility mapping modules as meeting TRU criteria T1, R1-2 and U1. The remaining two TRU criteria are partially met, but require more detailed documentation (for T2) and more unit testing (for U2).
+                                                        Our software framework has potential value as a prototype for future tools to support the development of transferable CHEMs.",
[…]

### 2024-02-27 Markdown/Manuscript/Child_RMDs/MS_Available_Data_And_Resources.Rmd
working on discussion
cull

@@
 
-Development versions of all code repositories referenced in this article are available in https://github.com/ready4-dev/ .
-Archived code releases are available in https://zenodo.org/communities/ready4  .
-
-All data repositories referenced in this article are available in https://dataverse.harvard.edu/dataverse/ready4 .
+The ready4 framework is documented at https://www.ready4-dev.com.
+Documentation on readyforwhatsnext is available at https://readyforwhatsnext.org/.
+Development versions of all code repositories referenced in this article are available in https://github.com/ready4-dev/.
+Archived code releases are available in https://zenodo.org/communities/ready4.
+All data repositories referenced in this article are available in https://dataverse.harvard.edu/dataverse/ready4.

### 2024-02-27 Markdown/Manuscript/Child_RMDs/MS_Conclusion.Rmd
cull

@@
 -->
-We have developed a prototype software framework that can support the implementation of CHEMs that largely meet explicit criteria for CHEM transparency, reusability and updataility.
-Our framework can be used as a prototype for developing future software frameworks to support ethical implementation of CHEMs.
-Barriers to ethical CHEM practice arising from resource constraints should be addressed by research funders.
+Our software framework provides the outline of a technical solution to some of the challenges of transferable CHEM development using open-source and modular approaches.
+Our framework can be used as a prototype for developing future software frameworks to support implementation of transferable CHEMs.
+<!-- Barriers to ethical CHEM practice arising from resource constraints should be addressed by research funders. -->

### 2024-02-27 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
cull

@@
 
-As illustrated by Table \@ref(tab:checktb), we have developed a prototype software framework that can be used to implement youth mental health CHEMs that largely satisfy our TRU criteria.
-However, in its current form our software framework is too fragile to be recommended as anything more than a prototype for supporting the development needs of other modelling teams and projects.
-We developed our prototype software framework primarily to address the user requirements of one group – ourselves.
-Factors such as user enjoyment, usability, active user-community and supporting resources influence adoption of software frameworks [@myllarniemi2018development].
-We currently lack the resources required to  address these issues for our software framework.
+As illustrated by Table \@ref(tab:checktb), we have developed a software framework and used it to implement CHEM modules that largely satisfy explicit criteria for transparency, reusability and updatability.
+However, in its current status as a development release, our software framework is too fragile to be recommended as anything more than a prototype for supporting the development needs of other modelling teams and projects.
+<!-- We developed our prototype software framework primarily to address the user requirements of one group – ourselves.
+-->Factors such as user enjoyment, usability, active user-community and supporting resources influence adoption of software frameworks [@myllarniemi2018development].
+We currently lack the resources required to systematically address these issues for our software framework.
 
@@
 Secondly, implementation that combines both object-oriented and functional programming paradigms can avail of the modular and syntactical simplicity benefits of the former, while limiting needless bundling of code artefacts.
-Thirdly, a sensible trade-off needs to be found between transparent code implementation (which requires clear and sufficiently detailed documentation) and Agile Software Development (for which a foundational principle is prioritising the development of working code over writing documentation [@beck2001manifesto]).
+Thirdly, a sensible trade-off needs to be found between transparent code implementation (which requires clear and sufficiently detailed documentation) and prioritising the development of working code over writing documentation  (a foundation principle of Agile Software Development [@beck2001manifesto]).
 Our software framework makes this trade off by enforcing the use of consistent code style conventions and file organisation which in turn enables automated generation of simple documentation at every CHEM module update.
@@
 
-Our software framework provides the outline of a technical solution to some of the challenges of open source CHEM development.
-However, better tools alone are insufficient and policy and institutional changes are also required.
+We have used toy data to demonstrate how our initial readyforwhatsnext CHEM module libraries, originally developed for a single utility mapping study [@Hamilton2021.07.07.21260129], can be applied to datasets with different concepts and variable names, to construct models with different utility instruments, predictors and covariates and to develop and use both cross-sectional and longitudinal mapping models.
+However, it should be noted that these CHEM module libraries are currently only available as development releases.
+When assessing libraries against TRU criteria, we identified the need to write more custom documentation and unit tests of individual modules.
+We plan to undertake these improvements as part of future quality assurance work required prior to submission of these libraries for archiving on CRAN [@CRAN2022].
+
+It is also important to highlight that our framework only addresses barriers to health economic model transferability that arise from how a model is implemented as software (ie, CHEMs).
+Health economists must also consider conceptual or theoretical validity issues.
+For example, the candidate models currently available in our scorz library [@hamilton_matthew_2022_6084824] were chosen because of their suitability for mapping to the utility instrument (AQoL-6D [@Richardson2012AQ]) used in the study [@Hamilton2021.07.07.21260129] for which scorz was originally developed.
+It is likely that other types of model would be more appropriate for mapping to utility instruments that produce less continuous total score distributions [@Hamilton2021.07.07.21260129].
+Therefore, although the utility mapping modules of readyforwhatsnext *can* be used to develop models to map to different utility instruments, further development of these tools will be required before *validly applied* to some study questions.
+Our software framework is designed to make such required extensions more straightforward to implement.
+
+Greater use of reference models [@Afzali2013], methodological innovation to improve model transferability [@craig2018taking] and the development of regularly updated CHEMs that can support "living Health Technology Assessment" [@thokala2023living] have all previously been recommended.
+Software frameworks could be enabling technologies for all of these goals.
+<!-- However, better tools alone are insufficient and policy and institutional changes are also required.
+-->
 <!-- Reducing waste in research is a core responsibility of research funders [@chalmers2014increase] and funding the development of CHEMs that are not adequately understood, reused or updated is wasteful.
@@
 Development of software frameworks to support ethical CHEM implementations could enable and enhance each of these strategies.
---> A future software framework for ethical CHEMs would ideally incorporate a base set of features useful to developers of computational models across all domains of public health and health economics, with the capability for community-led extensions that are tailored to the needs of modellers focused on specific health-conditions.
+--> A future software framework for transferable CHEMs would ideally incorporate a base set of features useful to developers of computational models across all domains of public health and health economics, with the capability for community-led extensions that are tailored to the needs of modellers focused on specific health-conditions.
 Such approaches will likely be important to ensure a sufficient potential user-base to make CHEM software frameworks sustainable.

### 2024-02-27 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
cull

@@
 ## Model user requirements
-The initial model user requirements (MURs) that we specified for the readyforwhatsnext modules we developed for utility mapping are:
+The model user requirements (MURs) that we specified for the readyforwhatsnext's initial modules are:
 
-MUR 1) *Variable validation tools* that: (i) define the allowable range (minimum and maximum) and numeric class (integer or double precision) associated with different psychological, functional and health utility summary measures appropriate for use in youth mental health samples; (ii) provide an informative error message that halts an analysis or reporting program's execution should impermissible values be assigned to each measure.
+MUR 1) *Variable validation tools* that: (i) define the allowable values and numeric class (integer or double precision) associated with different psychological, functional and health utility measures appropriate for use in youth mental health samples; (ii) provide an informative error message that halts an analysis or reporting program's execution should impermissible values be assigned to each measure.
 
-MUR 2) *Dataset description tools* that: (i) attach structured metadata to a human records dataset that specify the unique person identifier, group assignment and data collection round variables; and (ii) generate tabular and graphical summaries of dataset descriptive statistics.
+MUR 2) *Dataset description tools* that: (i) attach structured metadata to a human records dataset that specify unique person identifier, group assignment and data collection round variables; and (ii) generate tabular and graphical summaries of dataset descriptive statistics.
 
 MUR 3) *Multi-attribute instrument scoring tools* that: (i) attach structured metadata about an instrument (e.g.
-name, version, country, items, domains, parameter values for scoring algorithms) to a human records dataset; (ii) apply pre-written (for AQol-6D and EQ-5D instruments) or user-supplied instrument scoring functions to a human records dataset; and (iii) generate descriptive plots of a dataset's instrument scores for individual items, domains and totals (weighted and unweighted).
+name, version, country, items, domains, parameter values for scoring algorithms) to a human records dataset; (ii) apply pre-written (for AQol-6D [@Richardson2012AQ] and EQ-5D [@devlin2017eq] instruments) or user-supplied instrument scoring functions to a human records dataset; and (iii) generate descriptive plots of a dataset's instrument scores for individual items, domains and totals (weighted and unweighted).
 
@@
 
-MUR 5) *Utility mapping study reporting tools* that: (i) generate from a reporting template a PDF catalogue summarising the predictive performance under multiple configurations of utility mapping models selected for public dissemination; (ii) generate from a reporting template (either a pre-written default or a user-supplied customisation) a scientific summary manuscript summarising a utility mapping study; (iii) share model catalogues and (if desired) scientific summary along with metadata about utility mapping models in an open access repository; and (iv) facilitate the authoring of a single consolidated study reproducibility program that implements all steps inclusive of data ingest, instrument scoring, model construction, report authoring and dissemination of study artefacts.
+MUR 5) *Utility mapping study reporting tools* that: (i) generate from a reporting template a PDF catalogue summarising the predictive performance under multiple configurations of utility mapping models selected for public dissemination; (ii) generate from a reporting template (either a pre-written default or a user-supplied customisation) a scientific manuscript summarising a utility mapping study; (iii) share model catalogues and (if desired) scientific summary along with metadata about utility mapping models in an open access repository; and (iv) facilitate the authoring of a consolidated study replication program that implements data ingest, instrument scoring, model construction, report authoring and dissemination of study artefacts.
 
-MUR 6) *Utility prediction tools* that: (i) search open access repositories for utility mapping models developed with readyforwhastnext; (ii) retrieve relevant metadata, including a link to the model catalogue for models specified by a user; (iii) applies selected utility mapping model to make out of sample predictions using a dataset provided by a user; and (iv) (where there is health utility data at two time points) convert predicted health utility scores to Quality Adjusted Life Years (QALYs).
+MUR 6) *Utility prediction tools* that: (i) search open access repositories for utility mapping models developed with readyforwhastnext; (ii) retrieve relevant metadata, including a link to the model catalogue for models specified by a user; (iii) apply selected utility mapping models to make out of sample predictions using a dataset provided by a user; and (iv) (where there is health utility data at two time points) convert predicted health utility scores to Quality Adjusted Life Years (QALYs).
 
@@
 
-### Modules
+### Module libraries
 We used all six ready4 framework libraries to author five development version readyforwhatsnext module libraries (Table \@ref(tab:rfwnlibs)).
@@
 ### Reporting templates
-We used the framework reporting tools library to author two reporting templates that are designed to be used in conjunction with these utility mapping models.
-The first reporting template is used to create a catalogue of utility mapping models [@hamilton_matthew_2022_6116385].
-The second reporting template can be used to generate a manuscript [@matthew_p_hamilton_2022_5976988] providing a scientific summary of each study implemented with these modules.
+We used the framework reporting tools library to author two reporting templates that are designed to be used in conjunction with these utility mapping modules.
+The first reporting template [@hamilton_matthew_2022_6116385] is used to create a catalogue of utility mapping models.
+The second reporting template [@matthew_p_hamilton_2022_5976988] can be used to generate a manuscript providing a scientific summary of each study implemented with these modules.
 
 ### Application
-We have previously described a study [@Hamilton2021.07.07.21260129] that used applied these modules and reporting templates to develop utility mapping models in a sample of young people presenting to primary mental health services.
-We used these module libraries to write programs that reproduced that study's reporting and analysis algorithm [@hamilton_matthew_2022_6129906], to demonstrate how to applying the utility mapping models constructed in that study to new data [@hamilton_matthew_2022_6416330] and to generate a synthetic representation of the study dataset [@hamilton_matthew_p_2022_6321821].
-We also created an open access study input parameters and results dataset [@DVN/DKDIB0_2021]) and toy datasets to help demonstrate the transferability of the study algorithm [@DVN/HJXYKQ_2021]).
+We have previously described a study [@Hamilton2021.07.07.21260129] that used these module libraries and reporting templates to develop and document utility mapping models in a sample of young people presenting to primary mental health services.
+We used these module libraries to write programs for replicating that study's reporting and analysis algorithm [@hamilton_matthew_2022_6129906], to demonstrate how to apply the utility mapping models constructed in that study to new data [@hamilton_matthew_2022_6416330] and to generate a synthetic representation of the study dataset [@hamilton_matthew_p_2022_6321821].
+We also created an open access study input parameters and results dataset [@DVN/DKDIB0_2021] and toy datasets to help demonstrate the transferability of the study algorithm [@DVN/HJXYKQ_2021].
 
@@
 ## Documentation website
-We used using the search and documentation tools from our foundation framework library to
-create and help maintain a documentation website (https://readyforwhatsnext.org/) that includes details on available model modules, datasets and analysis programs and tutorials on using model modules.
+Using the framework website as a template, we used the search and documentation tools from our foundation framework library to create and help maintain a project documentation website (https://readyforwhatsnext.org/).
+The project website includes details on available model modules, datasets and analysis programs and tutorials on how these artefacts can be used.
 
 ## Transferability assessment
-We subjectively assessed these utility mapping model artefacts against <!-- Edit_start -->our TRU criteria <!-- Edit_end --> (Table \@ref(tab:checktb)).
+We subjectively assessed these utility mapping model artefacts against <!-- Edit_start -->TRU criteria <!-- Edit_end --> (Table \@ref(tab:checktb)).
 For each criterion, we provided a global assessment of whether it was met using the responses “yes”, “no” or “partial”.
-We believe our utility mapping study modules have satisfactorily met four of the six criteria (T1, R1, R2 and U1) and have partially met two criteria (T2 and U2).
-The main shortcomings that we identified when applying the assessment criteria was that we have yet to: (i) ensure that module library documentation includes examples of how to apply all exported methods and functions; and (ii) adequately implement unit testing.
+We believe that our utility mapping study module libraries, code and data repositories and documentation have satisfactorily met four of the six criteria (T1, R1, R2 and U1) and have partially met two criteria (T2 and U2).
+The main shortcomings that we identified when applying the assessment criteria was that individual modules and functions have yet to: (i) be supported with human authored documentation that includes examples of how they can be used; and (ii) be quality assured through unit testing.
 

### 2024-02-27 Markdown/Manuscript/Child_RMDs/MS_Imp_Motivation.Rmd
abstract updated
cull

@@
 
-We became interested in solving some of the technical barriers to transferable CHEMs in 2018 when considering how to synthesise multiple youth mental health economic modelling projectsin one multi-purpose model.
+We became interested in solving some of the technical barriers to transferable CHEMs in 2018 when considering how to synthesise multiple youth mental health economic modelling projects in one multi-purpose model.
 This overarching youth mental health model is called readyforwhatsnext [@rfwn2024].
@@
 
-Potential future directions for readyforwhatsnext may incorporate projects in two additional Wagstaff and Culyer domains of: (i) public health (to model the impact of selected fiscal policy and regulation options on young people's mental health); and (ii) human resources (to model the supply and behaviours of the youth mental health workforce).
-Our ultimate aim is for readyforwhatsnext to flexibly combine its constituent parts in analyses that help answer questions in two additional Wagstaff and Culyer domains:
+Potential future directions for readyforwhatsnext may incorporate projects in two additional domains: (i) public health (to model the impact of selected fiscal policy and regulation options on young people's mental health); and (ii) human resources (to model the supply and behaviours of the youth mental health workforce).
+Our ultimate aim is for readyforwhatsnext to flexibly combine its constituent parts in analyses that help answer questions in a further two domains:
 
@@
 
-However, there are ethical risks associated with each potential transfer, in particular the need to ensure the social acceptability, fitness for purpose and appropriate use of readyforwhatsnext in each new decision context [@ethicsCHEMS2024].
+However, there are ethical risks associated with each potential transfer, in particular the need to ensure the social acceptability, fitness for purpose and appropriate use of a CHEM in each new decision context [@ethicsCHEMS2024].
 For that reason, we have set the goal of readyforwhatsnext meeting six explicit criteria for transparency, reusability and updatability (TRU criteria).
-We have describe these criteria and their origins in ethical modelling practice elsewhere [@ethicsCHEMS2024], but briefly they are:
+We have described these criteria and their origins in ethical modelling practice elsewhere [@ethicsCHEMS2024], but briefly they are:
 
@@
 
-T2) Developer contributions are easily identified;
+T2) Developer contributions and judgments on appropriate use are easily identified;
 
@@
 
-U6) Software is systematically retested and deprecated.
+U6) Releases are systematically retested and deprecated.
 
-We are developing readyforwhatsnext using real Australian data (which can be empirical, simulated or assumption, so long as it is appropriate for use in analysis intended to inform decision-making).
+To achieve these goals we are implementing readyforwhatsnext as an open-source, modular model.
+Open source projects grant third parties liberal permissions to access, use and modify model source code and data.
+A modular model is constructed from multiple reusable and replaceable sub-models (modules) [@pan2021modular].
+<!-- Modules can share inputs and outputs with other modules or can be run as independent models [@barros2023empowering].
+-->We are developing readyforwhatsnext using real Australian data (which can be empirical, simulated or assumption, so long as it is appropriate for use in analysis intended to inform decision-making).
 To help demonstrate the potential transferability of readyforwhatsnext to other decision contexts, we are also creating toy datasets.

### 2024-02-27 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
cull

@@
 
-FUR 3) *Module authoring tools* that integrate with online software development services to help author R libraries of CHEM modules that are: (i) created using the template module; (ii) written in a consistent house style; (iii) always at least minimally documented; (iv) licensed for reuse; (v) bundled with authorship, funding source, version number and a Digital Object Identifier (DOI) metadata; and (vi) quality assured with publicly available testing artefacts.
+FUR 3) *Module authoring tools* that integrate with online software development services to help author R libraries of CHEM modules that are: (i) created using the template module; (ii) written in a consistent house style; (iii) always at least minimally documented; (iv) licensed for reuse; (v) bundled with authorship, funding source, version number and Digital Object Identifier (DOI) metadata; and (vi) quality assured with publicly available testing artefacts.
 
@@
 
-FUR 5) *Reporting tools* that: help (i) author reporting templates that render documents in HTML, Adobe PDF and Microsoft Word file formats; (ii) retrieve version specific reporting templates  from online code repositories and (iii) supply study specific data (e.g authorship details, input data and analysis results) to reporting templates to render reports and scientific summaries.
+FUR 5) *Reporting tools* that: help (i) author reporting templates for rendering documents in HTML, Adobe PDF and Microsoft Word file formats; (ii) retrieve version specific reporting templates from online code repositories and (iii) supply study specific data (e.g authorship details, input data and analysis results) to reporting templates to render custom reports and scientific summaries.
 <!-- help generate tables for multiple outputs, retrieve templates, modify templates with authorship and results -->
@@
 
-FUR 7) *Documentation tools* that integrate with open source website development and hosting infrastructure to help: (i) develop a project documentation website that consolidates content from the websites of individual module libraries, datasets and programs; and (ii) partially automate the updating of website resources such as tutorials and itemised lists of code and data releases.
+FUR 7) *Documentation tools* that integrate with open source website development and hosting infrastructure to help: (i) develop a CHEM project documentation website that consolidates content from the websites of individual CHEM module libraries, datasets and programs; and (ii) partially automate the updating of website resources such as tutorials and itemised lists of code and data releases.
 
@@
 <!-- In modular model implementations, modules need to be able to share inputs and outputs with each other and to be run as independent models [@barros2023empowering].
--->The ready4 foundation library defines a template CHEM module using R’s S4 class system, that supports an object-oriented programming paradigm.
-Two notable features of object-oriented programming are encapsulation [@8717448] and inheritence [@8717448].
+-->To meet *FUR 1*, the ready4 [@ready4lib24] foundation library defines a template CHEM module using R’s S4 class system, that supports an object-oriented programming paradigm.
+Two notable features of object-oriented programming are encapsulation [@8717448] and inheritance [@8717448].
 Encapsulation allows a CHEM module to bundle model data and algorithms in a protected environment, which is useful for helping ensure that CHEM modules continue to work as intended when combined<!-- [@ready4oop2022] -->.
-Inheritence allows new CHEM modules to inherit some or all of the properties of a parent module.
-Inheritence is useful when it is necessary to selectively modify CHEM modules, for example to that to account for interaction effects when CHEMs are combined or to account for the features of a different decision contexts to which they are being transferred<!-- [@ready4oop2022] -->.
-The ready4 template CHEM module can be used to create other CHEM modules that inherit a common set of properties (meeting *FUR 1*).
+Inheritance allows new CHEM modules to inherit some or all of the properties of a parent module.
+Inheritance is useful when it is necessary to selectively modify CHEM modules, for example to account for: (i) interaction effects when CHEMs are combined; or (ii) distinctive features of a new decision contexts to which they are being transferred<!-- [@ready4oop2022] -->.
+The ready4 template CHEM module can be used to create other CHEM modules that inherit a common set of properties.
 One of these inherited properties is a novel syntax of 15 core commands that enable CHEM module algorithms to be consistently named (meeting *FUR 2*).
-The foundation library also contains tools for retrieving web-based information on CHEM modules, datasets and analysis programs authored with ready4 (meeting *FUR 6*) and tools for developing and maintaining a project documentation website (*FUR 7*).
+The foundation library also contains tools for retrieving web-based information on CHEM modules, datasets and analysis programs authored with ready4 (meeting *FUR 6*) and tools for developing and maintaining a CHEM project's documentation website (meeting *FUR 7*).
 
@@
 Authoring with each of these paradigms is supported by ready4.
-One module authoring library contains tools for writing functions in a consistent house style and automatically generating basic documentation for each function.
-A second module authoring library contains tools to help streamline and standardise the authoring of novel, documented CHEM modules from the template CHEM module.
-A third module authoring library provides tools for disseminating themed bundles of CHEM modules as R libraries that are: documented (with a website and PDF manuals); licensed (using the copyleft GNU GPL-3 [66] by default); easily citable (citation information can be retrieved within an R session or from hosting repositories); and quality assured (each update triggers continuous integration workflows, including any acceptance and unit tests created by module library authors).
+The ready4fun [@ready4funlib24] library contains tools for writing functions in a consistent house style and automatically generating basic documentation for each function.
+The ready4class [@ready4classlib24] library contains tools to help streamline and standardise the authoring of novel, documented CHEM modules from the template CHEM module.
+The ready4pack [@ready4packlib24] library provides tools for disseminating themed bundles of CHEM modules as R libraries that are: documented (with a website and PDF manuals); licensed (using the copyleft GNU GPL-3 [66] by default); easily citable (citation information can be retrieved within an R session or from hosting repositories); and quality assured (each update triggers the running of any tests created by module library authors, with test results publicly documented).
 
-A library for managing CHEM data contains tools for supplying CHEM modules with input data ingested from local (i.e., a user's computer) or remote (online repositories) locations, labelling CHEM module datasets and exporting CHEM module data to online repositories (meeting *FUR 4*).
-A library for authoring reproducible analysis programs and reporting subroutines (*FUR5*) contains tools to help write executables that apply CHEM modules to compatible datasets for the purpose of undertaking health economic analyses.
+The ready4use [@ready4uselib24] library for managing CHEM data contains tools for supplying CHEM modules with input data ingested from local (i.e., a user's computer) or remote (online repositories) locations, labelling CHEM module datasets and exporting CHEM module data to online repositories (meeting *FUR 4*).
+The ready4show [@ready4showlib24] library for authoring reproducible analysis programs and reporting subroutines (*FUR5*) contains tools to help write executables that apply CHEM modules to compatible datasets for the purpose of undertaking reproducible health economic analyses.
 The library supports the creation of analysis programs that are self-documenting (code is integrated with plain English explanations of what it does) and subroutines that can be used as templates that trigger the creation of explanatory documents (e.g., a scientific manuscript).
@@
 ###	Online services 
-Framework libraries are designed to be used in conjunction with a number of third-party online services that developers using ready4 need to establish and configure accounts with.
-The framework's module authoring tools integrate with online code development, testing and archiving services.
-The ready4 framework uses the GitHub [@github2007] service's tools for: software development, testing, version control and distribution; hosting of documentation websites; and transparent record keeping of collaborator contributions.
+Framework libraries are designed to be used in conjunction with a number of third-party online services.
+The framework's module authoring tools use the GitHub [@github2007] service's tools for: software development, testing, version control and distribution; hosting of documentation websites; and transparent record keeping of collaborator contributions.
 The continuous integration [@CI2017] tools provided by GitHub are used to trigger systematic retesting of module libraries with every edit.
@@
 A useful concept for informing software users about the extensiveness of testing procedures is code coverage [@ERICWONG2010188] - reports of the proportion of code that has been explicitly tested.
-The ready4 framework uses the codecov [@codecov_2022] service to measure and share information about code coverage.
-<!-- End_Imported -->The open science repository service Zenodo [@Zenodo2013] is used to provide persistent storage, uniquely identified with a a Digital Object Identifier (DOI), of each code release.
+The module authoring libraries use the codecov [@codecov_2022] service to measure and share information about code coverage.
+<!-- End_Imported -->The open science repository service Zenodo [@Zenodo2013] is used by the module authoring libraries to provide persistent storage, uniquely identified with a Digital Object Identifier (DOI), of each code release.
 The framework's data management tools use the Dataverse [@Dataverse2007] data repository service for persistent, uniquely identifiable and versioned storage of model input and output data.
-For the management of frequently updated datasets that do not require persistent storage, ready4 uses GitHub.
+For the management of frequently updated datasets that do not require persistent storage, all framework libraries use GitHub.
 

### 2024-02-27 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
cull

@@
 <!-- Import_start -->Computational models, particularly those addressing economic topics, have become essential tools for health policy development [@dakin2015influence; @Erdemir2020].
-Although influential and widely used, health economic models can be skills and resource intensive to undertake.<!-- Import_end --> One suggestion for making health economic modelling projects more tractable is for health economists to re-use each other's models [@Arnold2010].
+Although influential and widely used, health economic models can be skills and resource intensive to develop.<!-- Import_end --> One suggestion for making health economic modelling projects more tractable is for health economists to re-use each other's models [@Arnold2010].
 
@@
 
-<!-- End_Imported_from_Ethics -->A potential strategy for implementing transferable CHEMs is to adopt an open-source and modular approach to model development.
+<!-- End_Imported_from_Ethics -->
+<!-- A potential strategy for implementing transferable CHEMs is to adopt an open-source and modular approach to model development.
 Open source projects grant third parties liberal permissions to access, use and modify model source code and data.
-Many health economists support greater use of open-source CHEMs as a means of improving model transparency, promoting model reuse, making model development more efficient and gaining the confidence of model users [@Pouwels2022].
-A number of complex open source computational modelling projects in disciplines such as biology [@pan2021modular], ecology [@barros2023empowering] and neuroscience [@frazier2022robust] have been implemented as modular models.
+Potential benefits of open-source CHEMs that have been identified by health economists include improving model transparency, promoting model reuse, making model development more efficient and gaining the confidence of model users [@Pouwels2022].
+A number of complex open source computational modelling projects in disciplines such as biology [@pan2021modular], ecology [@barros2023empowering] and neuroscience [@frazier2022robust] have also been implemented as modular models.
 A modular model is constructed from multiple reusable and replaceable sub-models (modules) [@pan2021modular].
@@
 Advantages of modular models include feasibility (large projects are broken into smaller tasks, with each component independently developed and tested) and flexibility (making it easier to selectively replace or update specific parts of a model and to scale up or down the level of granularity) [@pan2021modular].
+-->
 
@@
 <!-- https://www.ispor.org/publications/journals/value-outcomes-spotlight/vos-archives/issue/view/addressing-assessment-and-access-issues-for-rare-diseases/the-role-of-education-in-shaping-an-open-source-future -->
-Actual implementations of open-source CHEMs are relatively rare [@Emerson2019; @Michalczyk2018; @Feenstra2022].
+<!-- Actual implementations of open-source CHEMs are relatively rare [@Emerson2019; @Michalczyk2018; @Feenstra2022].
 Recent efforts to build this field including an initiative to develop a suite of open source CHEMs addressing different health conditions in the United States [@Jansen2019] and a Canadian platform facilitating access to and validation of multiple CHEMs [@harvard2022developing].
@@
 Barriers to greater use of open-source approaches include health economist concerns about intellectual property, confidentiality, model misuse and the resources required to maintain open source implementations [@Pouwels2022; @Wu2019].
+-->
 <!--Benefits --><!-- Adherence to good practice guidance is an essential requirement for healthcare modelling [@Erdemir2020], but  --><!-- Guidelines for implementing open source CHEMs remain scarce, piecemeal and need improving [@Sampson2019].
--->When health economic models are owned by pharmaceutical companies and consultancies, commercial considerations may also limit the reuse of models and their constituent code and data [@Feenstra2022].
-Health econmists have also identified issues relating to model generalisability and transferability and model implementation software platforms as important barriers to open-source CHEMs [@Pouwels2022].
+-->
+<!-- When health economic models are owned by pharmaceutical companies and consultancies, commercial considerations may also limit the reuse of models and their constituent code and data [@Feenstra2022].
+Health economists have also identified issues relating to model generalisability and transferability and the software platforms in which CHEMs are authored as important barriers to open-source CHEMs [@Pouwels2022].
 We are not aware of published literature identifying barriers to modular CHEMs, but potentially these may relate to the limited benefit of undertaking modular approaches in projects that are not also open-source.
+-->
 <!-- Move to discussion--><!-- In health economics the related and enabling concept of reference models has been recommended [@Afzali2013].  -->
@@
 
-Some of the technical barriers<!-- Give examples --> to the development of transferable CHEMs that use open-source and modular approaches could be addressed by appropriate software frameworks.<!-- Check last sentence was not used in ethics manuscript  --> A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users [@myllarniemi2018development].
+Some of the barriers<!-- Give examples --> to the development of transferable CHEMs <!-- that use open-source and modular approaches  -->could be addressed by appropriate software frameworks.<!-- Check last sentence was not used in ethics manuscript  --> A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users [@myllarniemi2018development].
 A software framework provides a foundation for developing multiple software applications with shared resources (e.g., code and data files), that can be modified to suit specific needs.

### 2024-02-27 Markdown/Manuscript/Child_RMDs/MS_Tables_3.Rmd
cull

--- 2023-10-21 Markdown/Manuscript/Child_RMDs/MS_Tables_3.Rmd
@@
 library(kableExtra)  
-df <- tibble::tibble(Package = c("ready4",
+df <- tibble::tibble(Library = c("ready4",
                                        "ready4fun",
@@
                            # U = c("","","","1-3","1",""),
-                           `R library dependencies` = Package %>%
+                           `R library dependencies` = Library %>%
                              purrr::map(~ {
@@
 
-  dplyr::select(Package,
+  dplyr::select(Library,
                 #Ref,
@@
 #                     ])
-# colnames(df) <- c("Package",
+# colnames(df) <- c("Library",
 #                   ifelse(params$X@outp_formats_chr[1] == "Word","XXX"," "),
@@
 #                   "R library dependencies")
-#df$Package <- "![](../Data/images/ready4.png){ width=10% }"#"\\includegraphics[valign=T,scale=2.5,raise=2mm]{../Data/images/ready4.png}"
+#df$Library <- "![](../Data/images/ready4.png){ width=10% }"#"\\includegraphics[valign=T,scale=2.5,raise=2mm]{../Data/images/ready4.png}"
 #df$`Standard     `  <- df$`Standard     ` %>% stringr::str_replace_all("&nbsp;"," ")
@@
     #df$Ref<-NULL
-    #df$Package <- ""
-    df$Package  <- df$Package %>% 
-                      purrr::map_chr(~paste0("\\includegraphics[valign=M,width=1.9cm,raise=4mm]{../Data/images/",.x,"_logo.png}"))#scale=0.4,raise=3mm]
-    # df$Package <- "\\includegraphics[valign=M,scale=0.08,raise=3mm]{../Data/images/ready4.png}"
+    #df$Library <- ""
+    # df$Library  <- df$Library %>% 
+    #                   purrr::map_chr(~paste0("\\includegraphics[valign=M,width=1.9cm,raise=4mm]{../Data/images/",.x,"_logo.png}"))#scale=0.4,raise=3mm]
+    # df$Library <- "\\includegraphics[valign=M,scale=0.08,raise=3mm]{../Data/images/ready4.png}"
     #df[,c(1,3,5:6)]   %>%

### 2024-02-27 Markdown/Manuscript/Child_RMDs/MS_Tables_3b.Rmd
cull

@@
 ---
-```{r rfwnlibs, tab.cap='readyforwhatsnext module libraries for utility mapping', tab.id = 'cpkgs', echo = F, results = 'asis'}
+```{r rfwnlibs, tab.cap='Model module libraries for utility mapping', tab.id = 'cpkgs', echo = F, results = 'asis'}
 library(kableExtra)  
-df <- tibble::tibble(Package = c("youthvars",
+df <- tibble::tibble(Library = c("youthvars",
                                        "scorz",
@@
                                  "Apply utility mapping models to out of sample data."),
-                           `R library dependencies` = Package %>%
+                           `R library dependencies` = Library %>%
                              purrr::map(~ {
@@
 df <- df %>%
-  dplyr::select(Package,
+  dplyr::select(Library,
                 Purpose,

### 2024-02-27 Markdown/Manuscript/Parent_PDF/Springer.Rmd
cull

@@
   - firstname: David  
+    particle: G
     lastname: Baker
@@
 keywords:  
+  - adolescence
   - computational models
-  - ethics of modelling
   - health economics

### 2024-02-27 Markdown/Manuscript/Parent_Word/UNUSED_Parent_Word.Rmd
cull

---
bibliography: ../Data/WordBibliography.bib
output:
  bookdown::markdown_document2:
    base_format: "officedown::rdocx_document"
    number_sections: no
    tables:
      style: Table
      layout: autofit
      width: 1.0
      caption:
        style: Table Caption
        pre: 'Table '
        sep: ': '
      conditional:
        first_row: true
        first_column: false
        last_row: false
        last_column: false
        no_hband: false
        no_vband: true
    pandoc_args: 
      - "--metadata-file=../Header/header_common.yaml"
      - '--lua-filter=../Filters/scholarly-metadata.lua'
      - '--lua-filter=../Filters/author-info-blocks.lua'
      - '--lua-filter=../Filters/pagebreaks.lua'
  bookdown::word_document2:
    tables:
      style: Table
      layout: autofit
      width: 1.0
      caption:
        style: Table Caption
        pre: 'Table '
        sep: ': '
      conditional:
        first_row: true
        first_column: false
        last_row: false
        last_column: false
        no_hband: false
        no_vband: true
    pandoc_args: 
      - "--metadata-file=../Header/header_common.yaml"
      - '--lua-filter=../Filters/scholarly-metadata.lua'
      - '--lua-filter=../Filters/author-info-blocks.lua'
      - '--lua-filter=../Filters/pagebreaks.lua'
  officedown::rdocx_document:
    base_format: "bookdown::word_document2"
    number_sections: no
    tables:
      style: Table
      layout: autofit
      width: 1.0
      caption:
        style: Table Caption
        pre: 'Table '
        sep: ': '
      conditional:
        first_row: true
        first_column: false
        last_row: false
        last_column: false
        no_hband: false
        no_vband: true
    pandoc_args: 
      - "--metadata-file=../Header/header_common.yaml"
      - '--lua-filter=../Filters/scholarly-metadata.lua'
      - '--lua-filter=../Filters/author-info-blocks.lua'
      - '--lua-filter=../Filters/pagebreaks.lua'
params:
  X: NULL
abstract: "`r paste0(stringr::str_replace_all(stringr::str_replace_all(stringr::str_replace_all(stringr::str_replace_all(readLines('../Header/abstract.txt'),'\\\\\\\\textbf',''),'\\{','**'),'\\}','**'),'\\\\\\\\newline','\\\\n'),collapse=' ')`"
graphics: yes
csl: plos.csl
---

```{r echo = F}
library(officedown)
library(ready4show)
```
```{r child="../Child_RMDs/All_Content.Rmd", echo=FALSE}
```

### 2024-02-27 setup.R

@@ -7,10 +7,10 @@ X <- Ready4showSynopsis(#background_1L_chr = "Our study is entirely fictional.",
                         coi_1L_chr = "None declared.",
                         #conclusion_1L_chr = "We have identified criteria that can be used to systematically assess extent to which the computational implementation of health economic models adheres to the ethical goals of transparency, reusability and updatability. We have developed an open-source software framework that can support the ethical computational implementation of economic models in youth mental health. Our framework can be used as a prototype for developing future software frameworks to support ethical implementation of CHEMs.",
                         digits_int = 3L,
-                        ethics_1L_chr = "Software framework development did not involve human subject research and was not ethically reviewed. The utility mapping worked example is a previously reported study that was reviewed and granted approval by the University of Melbourne’s Human Research Ethics Committee, and the local Human Ethics and Advisory Group (1645367.1).",
-                        funding_1L_chr = "Software framework development was funded by Orygen, VicHealth, Victoria University and an Australian Government Research Training Program (RTP) Scholarship. The utility mapping study used as a worked example was funded by the National Health and Medical Research Council (NHMRC, APP1076940), Orygen and headspace.",
+                        ethics_1L_chr = "Software framework development did not involve human subject research and was not ethically reviewed. The utility mapping modules were originally developed to implement a previously reported study that was reviewed and granted approval by the University of Melbourne’s Human Research Ethics Committee, and the local Human Ethics and Advisory Group (1645367.1).",
+                        funding_1L_chr = "Software framework development was funded by Orygen, VicHealth, Victoria University and an Australian Government Research Training Program (RTP) Scholarship to Matthew Hamilton. The utility mapping study to which utility mapping modules were applied was funded by the National Health and Medical Research Council (NHMRC, APP1076940), Orygen and headspace.",
                         #interval_chr = "three months",
-                        keywords_chr = c("computational models", "health economics", "mental disorders", "open-source models", "software frameworks"),
+                        keywords_chr = c("adolescence", "computational models", "health economics", "mental disorders", "open-source models", "software frameworks"),
                         outp_formats_chr = "PDF",
                         #sample_desc_1L_chr = "The study sample is fake data that pretends to be young people aged 12 to 25 years who attended Australian primary care services for mental health related needs between November 2019 to August 2020.",
                         title_1L_chr = "A prototype software framework for transferable computational health economic models and its early application in youth mental health")
@@ -37,15 +37,18 @@ X <- renewSlot(X,
                "abstract_args_ls",
                {
                  args_ls <- X@abstract_args_ls
[…]

### 2024-03-01 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
nearly done on model
ready for comparison

--- 2024-02-20 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
@@
 <!-- (ii)  -->
-(ii)	how we have applied that software framework to develop and share an initial set of modules for our youth mental health CHEM.
+
+(iii)	how we have applied the prototype software framework to undertake initial development of our youth mental health CHEM.

### 2024-03-01 Markdown/Manuscript/Child_RMDs/MS_Conclusion.Rmd
ready for comparison

@@
 -->
-Our software framework provides the outline of a technical solution to some of the challenges of transferable CHEM development using open-source and modular approaches.
-Our framework can be used as a prototype for developing future software frameworks to support implementation of transferable CHEMs.
+Our software framework provides a solution to some technical barriers we faced when seeking to implement a transferable CHEM in youth mental health.
+Our framework can be used as a prototype for developing future software frameworks that address the user-requirements of the broader health economic modelling community.
 <!-- Barriers to ethical CHEM practice arising from resource constraints should be addressed by research funders. -->

### 2024-03-01 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
ready for comparison

--- 2024-01-24 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
@@
 
-As illustrated by Table \@ref(tab:checktb), we have developed a prototype software framework that can be used to implement youth mental health CHEMs that largely satisfy our TRU criteria.
-However, in its current form our software framework is too fragile to be recommended as anything more than a prototype for supporting the development needs of other modelling teams and projects.
-We developed our prototype software framework primarily to address the user requirements of one group – ourselves.
-Factors such as user enjoyment, usability, active user-community and supporting resources influence adoption of software frameworks [@myllarniemi2018development].
-We currently lack the resources required to  address these issues for our software framework.
+As illustrated by Table \@ref(tab:checktb), we have developed a software framework and used it to author CHEM modules that largely satisfy explicit criteria for transparency, reusability and updatability.
+We have used toy data to demonstrate how these CHEM module libraries, originally developed for a single utility mapping study [@Hamilton2021.07.07.21260129], can be applied: (i) to datasets from new samples with different concepts and variable names; (ii) to construct models with different utility instruments, predictors and covariates; and (iii) to develop and use both cross-sectional and longitudinal mapping models.
 
-However, our prototype has a number of features that future work on CHEM software frameworks may find useful to incorporate.
-Firstly, developing a software framework to work within an existing and widely used open source programming language such as R, can keep framework scope relatively narrow.
-This makes it more tractable to develop, maintain and learn, and facilitates integration with other modelling tools written in that language (e.g., the dependency libraries we list in Table \@ref(tab:cpkgs)).
-Secondly, implementation that combines both object-oriented and functional programming paradigms can avail of the modular and syntactical simplicity benefits of the former, while limiting needless bundling of code artefacts.
-Thirdly, a sensible trade-off needs to be found between transparent code implementation (which requires clear and sufficiently detailed documentation) and Agile Software Development (for which a foundational principle is prioritising the development of working code over writing documentation [@beck2001manifesto]).
+<!--  it should be noted that  -->Our framework and CHEM module R libraries are currently publicly available as development releases<!-- .
+When assessing libraries against TRU criteria, we identified the need to write  -->.
+We plan to undertake a number of key improvements, such as more detailed documentation, comprehensive unit testing and streamlining dependencies,<!-- as part of future quality assurance work required--> prior to submitting these libraries for quality assurance and dissemination by CRAN [@CRAN2022].
+
+Although designed to address challenges specific to our project, ready4 can be a <!-- too fragile to be recommended as anything more than a  -->prototype for future software frameworks that meet the user requirements of other modelling teams and projects.
+<!-- We developed our prototype software framework primarily to address the user requirements of one group – ourselves.
+-->Our prototype has a number of features that such future work can build on.<!-- that future work on CHEM software frameworks may find useful to incorporate.
+--> Firstly, developing a software framework to work within an existing and widely used open source programming language such as R, can keep framework scope relatively narrow.
+This makes it more tractable to develop, maintain and learn, and facilitates integration with other modelling tools written in that language (e.g., the dependency libraries we list in Tables \@ref(tab:cpkgs) and \@ref(tab:rfwnlibs)).
+Secondly, <!-- implementation that combines both object-oriented and functional programming paradigms can avail of the modular and syntactical simplicity benefits of the former, while limiting needless bundling of code artefacts.
+Thirdly, -->a sensible trade-off needs to be found between transparent code implementation (which requires clear and sufficiently detailed documentation) and prioritising the development of working code over writing documentation  (a foundation principle of Agile Software Development [@beck2001manifesto]).
 Our software framework makes this trade off by enforcing the use of consistent code style conventions and file organisation which in turn enables automated generation of simple documentation at every CHEM module update.
-All model data-structures and algorithms are therefore always documented (at least minimally, with machine authored content), meaning model developers have a requirement to write customised documentation less frequently.
-Many of the features of our prototype software framework have the potential to be significantly enhanced through integration with evolving code and documentation authoring capabilities of large language models.
+<!-- All model data-structures and algorithms are therefore always documented (at least minimally, with machine authored content), meaning model developers have a requirement to write customised documentation less frequently.
+Many of the  -->
 
-Our software framework provides the outline of a technical solution to some of the challenges of open source CHEM development.
-However, better tools alone are insufficient and policy and institutional changes are also required.
-<!-- Reducing waste in research is a core responsibility of research funders [@chalmers2014increase] and funding the development of CHEMs that are not adequately understood, reused or updated is wasteful.
+<!-- It is also important to highlight that  -->
+Our framework addresses barriers to <!-- health economic model  -->transferability specific to how a model is implemented as software (ie, CHEMs).
+Health economists must also consider conceptual or theoretical validity<!-- issues -->.
+For example, the candidate models currently available in our scorz library [@hamilton_matthew_2022_6084824] were chosen because of their suitability for mapping to the utility instrument (AQoL-6D [@Richardson2012AQ]) used in the study [@Hamilton2021.07.07.21260129] for which scorz was originally developed.
+We have identified a need to use alternative models for mapping to utility instruments that produce less continuous total score distributions [@Hamilton2021.07.07.21260129].
+Our software framework is designed to make such extensions more straightforward to implement.
+
+Factors such as <!-- user enjoyment,  -->usability, active user-community and supporting resources influence adoption of software frameworks [@myllarniemi2018development].
+To systematically address these issues for our prototype software framework would require investments in engaging the health economic modelling community to refine framework user requirements, software re-development and testing to meet those requirements, integration with evolving code and documentation authoring capabilities of large language models, the development of improved and more comprehensive documentation and training resources and proactive user-community building and support.
+We currently lack the resources to undertake these tasks.
+
+Adequately planned, resourced and implemented software frameworks are potentially important enablers of improved health economic modelling practice.
+Reference models [@Afzali2013], methodological innovation to improve model transferability [@craig2018taking] and the development of regularly updated CHEMs that can support "living Health Technology Assessment" [@thokala2023living] would all be facilitated by a trusted software framework for implementing more transparent, reusable and updatable CHEMs.
+<!-- However, better tools alone are insufficient and policy and institutional changes are also required.
+--><!-- Reducing waste in research is a core responsibility of research funders [@chalmers2014increase] and funding the development of CHEMs that are not adequately understood, reused or updated is wasteful.
 Existing incentive structures for health economists generally do not promote facilitating peers to reuse their work and funding is rarely adequate to maintain and routinely update a model.
@@
 Development of software frameworks to support ethical CHEM implementations could enable and enhance each of these strategies.
---> A future software framework for ethical CHEMs would ideally incorporate a base set of features useful to developers of computational models across all domains of public health and health economics, with the capability for community-led extensions that are tailored to the needs of modellers focused on specific health-conditions.
+--> A future software framework for CHEMs would ideally incorporate a base set of features useful to developers of computational models across all domains of public health and health economics, with the capability for community-led extensions that are tailored to the needs of modellers focused on specific health-conditions.
 Such approaches will likely be important to ensure a sufficient potential user-base to make CHEM software frameworks sustainable.

### 2024-03-01 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
ready for comparison

@@
 
-MUR 6) *Utility prediction tools* that: (i) search open access repositories for utility mapping models developed with readyforwhastnext; (ii) retrieve relevant metadata, including a link to the model catalogue for models specified by a user; (iii) apply selected utility mapping models to make out of sample predictions using a dataset provided by a user; and (iv) (where there is health utility data at two time points) convert predicted health utility scores to Quality Adjusted Life Years (QALYs).
+MUR 6) *Utility prediction tools* that: (i) search open access repositories for utility mapping models developed with readyforwhatsnext; (ii) retrieve relevant metadata, including a link to the model catalogue for models specified by a user; (iii) apply selected utility mapping models to make out of sample predictions using a dataset provided by a user; and (iv) (where there is health utility data at two time points) convert predicted health utility scores to Quality Adjusted Life Years (QALYs).
 
@@
 ### Reporting templates
-We used the framework reporting tools library to author two reporting templates that are designed to be used in conjunction with these utility mapping modules.
+We used the ready4show library to author two reporting templates that are designed to be used in conjunction with these utility mapping modules.
 The first reporting template [@hamilton_matthew_2022_6116385] is used to create a catalogue of utility mapping models.
@@
 ## Documentation website
-Using the framework website as a template, we used the search and documentation tools from our foundation framework library to create and help maintain a project documentation website (https://readyforwhatsnext.org/).
+Using the framework website as a template, we used the search and documentation tools from the ready4 library to create and maintain a project documentation website (https://readyforwhatsnext.org/).
 The project website includes details on available model modules, datasets and analysis programs and tutorials on how these artefacts can be used.
@@
 ## Transferability assessment
-We subjectively assessed these utility mapping model artefacts against <!-- Edit_start -->TRU criteria <!-- Edit_end --> (Table \@ref(tab:checktb)).
+We subjectively assessed these utility mapping model artefacts against <!-- Edit_start -->TRU criteria<!-- Edit_end --> (Table \@ref(tab:checktb)).
 For each criterion, we provided a global assessment of whether it was met using the responses “yes”, “no” or “partial”.
 We believe that our utility mapping study module libraries, code and data repositories and documentation have satisfactorily met four of the six criteria (T1, R1, R2 and U1) and have partially met two criteria (T2 and U2).
-The main shortcomings that we identified when applying the assessment criteria was that individual modules and functions have yet to: (i) be supported with human authored documentation that includes examples of how they can be used; and (ii) be quality assured through unit testing.
+The main shortcomings we identified were that individual modules and functions have yet to: (i) be supported with human authored documentation that includes examples of how they can be used; and (ii) be quality assured through unit testing.
 

### 2024-03-01 Markdown/Manuscript/Child_RMDs/MS_Imp_Motivation.Rmd
ready for comparison

@@
 Potential future directions for readyforwhatsnext may incorporate projects in two additional domains: (i) public health (to model the impact of selected fiscal policy and regulation options on young people's mental health); and (ii) human resources (to model the supply and behaviours of the youth mental health workforce).
-Our ultimate aim is for readyforwhatsnext to flexibly combine its constituent parts in analyses that help answer questions in a further two domains:
+Our ultimate aim is to flexibly combine model components in analyses that answer questions in a further two domains:
 
@@
 Australian public mental health services can be planned and commissioned by the Australian Government, the governments of Australia's state and territories and independent organisations focused on smaller regions called Primary Health Networks.
-Promoting mentally healthy local communities is also an important role for Australian local governments.
-The mental health of young people is a global priority [@https://doi.org/10.1002/wps.20938] and Australia has initiated youth mental health service model reforms that have been adopted in other jurisdictions [@RN27].
+<!-- Promoting mentally healthy local communities is also an important role for Australian local governments.
+-->The mental health of young people is a global priority [@https://doi.org/10.1002/wps.20938] and Australia has initiated youth mental health service model reforms that have been adopted in other jurisdictions [@RN27].
 For these reasons, we aim to develop readyforwhatsnext in a manner that facilitates its transfer to multiple decision contexts.
@@
 However, there are ethical risks associated with each potential transfer, in particular the need to ensure the social acceptability, fitness for purpose and appropriate use of a CHEM in each new decision context [@ethicsCHEMS2024].
-For that reason, we have set the goal of readyforwhatsnext meeting six explicit criteria for transparency, reusability and updatability (TRU criteria).
+We therefore aim for readyforwhatsnext to meet six *transparency*, *reusability* and *updatability* (TRU) criteria.
 We have described these criteria and their origins in ethical modelling practice elsewhere  [@ethicsCHEMS2024], but briefly they are:
@@
 
-To achieve these goals we are implementing readyforwhatsnext as an open-source, modular model.
-Open source projects grant third parties liberal permissions to access, use and modify model source code and data.
+To meet these criteria we are implementing readyforwhatsnext as an open-source, modular model.
+Open source projects grant third parties permissions to access, use and modify model source code and data.
 A modular model is constructed from multiple reusable and replaceable sub-models (modules) [@pan2021modular].
 <!-- Modules can share inputs and outputs with other modules or can be run as independent models [@barros2023empowering].
--->We are developing readyforwhatsnext using real Australian data (which can be empirical, simulated or assumption, so long as it is appropriate for use in analysis intended to inform decision-making).
-To help demonstrate the potential transferability of readyforwhatsnext to other decision contexts, we are also creating toy datasets.
-Toy data created for illustration purposes is prominently labelled as not for use in decision-analysis.
-<!-- PHNS -->
-A high level schematic guiding our implementation of readyforwhatsnext as a transferable CHEM is outlined in Figure \@ref(fig:fig1).
+-->When undertaking analyses intended to inform decision-making, readyforwhatsnext uses real Australian data (which can be empirical, simulated or assumption-based).
+To help demonstrate the potential transferability of readyforwhatsnext to other decision contexts, we are creating toy datasets.
+<!-- PHNS -->A high-level schematic guiding our implementation of readyforwhatsnext is outlined in Figure \@ref(fig:fig1).
 

### 2024-03-01 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
ready for comparison

@@
 
-To help readyforwhatsnext meet all six TRU criteria, we developed a prototype software framework. The software framework is called ready4 [@ready424].
+To help readyforwhatsnext meet all six TRU criteria, we developed a prototype software framework called ready4 [@ready424].
 
 ## Framework user requirements
-We created ready4 with one primary user group in mind - ourselves.
-The framework user requirements (FURs) for ready4 evolved over six years (2018-2024) as we became aware of new issues that we needed to solve.
+<!-- We created ready4 with one primary user group in mind - ourselves.
+-->The framework user requirements (FURs) for ready4 evolved over six years (2018-2024) as we encountered new implementation issues for readyforwhatsnext that we needed to solve.
 Currently, these requirements are:
 
-FUR 1) A reusable *template* for CHEM modules that can: (i) be run as independent models; (ii) safely combined, sharing inputs and outputs with each other without unintended interference; and (iii) be selectively replaced, updated or extended.
+FUR 1) A reusable *template* for CHEM modules that can be: (i) run as independent models; (ii) safely combined, sharing inputs and outputs with each other without unintended interference; and (iii) selectively replaced, updated or extended.
 
@@
 
-FUR 3) *Module authoring tools* that integrate with online software development services to help author R libraries of CHEM modules that are: (i) created using the template module; (ii) written in a consistent house style; (iii) always at least minimally documented; (iv) licensed for reuse; (v) bundled with authorship, funding source, version number and Digital Object Identifier (DOI) metadata; and (vi) quality assured with publicly available testing artefacts.
+FUR 3) *Module authoring tools* that integrate with online software development services to help author CHEM modules that are: (i) created using the template module; (ii) written in a consistent house style; (iii) always at least minimally documented; (iv) licensed for reuse; (v) bundled as R libraries with authorship, funding source, version number and Digital Object Identifier (DOI) metadata; and (vi) quality assured with publicly available testing artefacts.
 
@@
 
-FUR 5) *Reporting tools* that: help (i) author reporting templates for rendering documents in HTML, Adobe PDF and Microsoft Word file formats; (ii) retrieve version specific reporting templates from online code repositories and (iii) supply study specific data (e.g authorship details, input data and analysis results) to reporting templates to render custom reports and scientific summaries.
+FUR 5) *Reporting tools* that: help (i) author reporting template programs for rendering HTML, Adobe PDF and Microsoft Word outputs; (ii) retrieve version specific reporting template programs from online code repositories and (iii) supply reporting template programs with study specific data (e.g., authorship details, input data and analysis results) to render custom reports.
 <!-- help generate tables for multiple outputs, retrieve templates, modify templates with authorship and results -->
 
-FUR 6) *Search tools* to retrieve web based information on a CHEM project's: (i) publicly available model modules, module libraries and tutorials; (ii) datasets and data collections; and (iii) replication programs and reporting templates.
+FUR 6) *Search tools* to retrieve web-based information on a CHEM project's: (i) model modules and tutorials; (ii) datasets and data collections; and (iii) replication and reporting template programs.
 
@@
 ### R libraries 
-A library in the R language will typically depend on multiple other R libraries, many of which are likely to have different authors.
-As the number of third-party dependencies of an R library grows so does the fragility of that library (e.g., the library may cease to work as intended due to changes in one of its dependency libraries).
+R libraries typically depend on multiple other R libraries<!-- , many likely to have different authors -->.
+As the number of dependencies of an R library grows, so does the fragility of that library (e.g., the library may cease to work as intended due to changes in one of its dependency libraries).
 To reduce the fragility of our framework we implemented it as multiple R libraries rather than one R library.
-In total we authored six novel R libraries to implement the ready4 framework, all of which have distinct purposes and dependencies (Table \@ref(tab:cpkgs)).
+We authored six novel R libraries to implement the ready4 framework, all of which have distinct purposes and dependencies (Table \@ref(tab:cpkgs)).
 
-One library provides the foundation for the ready4 framework.
 <!-- In modular model implementations, modules need to be able to share inputs and outputs with each other and to be run as independent models [@barros2023empowering].
@@
 Inheritance allows new CHEM modules to inherit some or all of the properties of a parent module.
-Inheritance is useful when it is necessary to selectively modify CHEM modules, for example to account for: (i) interaction effects when CHEMs are combined; or (ii) distinctive features of a new decision contexts to which they are being transferred<!-- [@ready4oop2022] -->.
+Inheritance is useful when modifying CHEM modules, for example to account for: (i) interaction effects when CHEMs are combined; or (ii) distinctive features of a new decision contexts to which they are being transferred<!-- [@ready4oop2022] -->.
 The ready4 template CHEM module can be used to create other CHEM modules that inherit a common set of properties.
-One of these inherited properties is a novel syntax of 15 core commands that enable CHEM module algorithms to be consistently named (meeting *FUR 2*).
-The foundation library also contains tools for retrieving web-based information on CHEM modules, datasets and analysis programs authored with ready4 (meeting *FUR 6*) and tools for developing and maintaining a CHEM project's documentation website (meeting *FUR 7*).
+One of these inherited properties is a novel syntax of 15 core commands that enable CHEM module algorithms to be consistently named and described (meeting *FUR 2*).
+The ready4 library also contains tools for retrieving web-based information on CHEM modules, datasets and analysis programs (meeting *FUR 6*) and tools for developing and maintaining a CHEM project's documentation website (meeting *FUR 7*).
 
-Three framework module authoring libraries are designed to meet *FUR 3*.
+Three module authoring libraries are designed to meet *FUR 3*.
 <!-- Define functional and object-oriented approaches, acceptance and unit testing.
--->The R language supports functional and object-oriented programming paradigms [@10.1214/13-STS452].
+The R language supports functional and object-oriented programming paradigms [@10.1214/13-STS452].
 Authoring with each of these paradigms is supported by ready4.
-The ready4fun [@ready4funlib24] library contains tools for writing functions in a consistent house style and automatically generating basic documentation for each function.
+-->The ready4fun [@ready4funlib24] library contains tools for writing functions in a consistent house style and automatically generating basic documentation for each function.
 The ready4class [@ready4classlib24] library contains tools to help streamline and standardise the authoring of novel, documented CHEM modules from the template CHEM module.
@@
 ###	Online services 
-Framework libraries are designed to be used in conjunction with a number of third-party online services.
-The framework's module authoring tools use the GitHub [@github2007] service's tools for: software development, testing, version control and distribution; hosting of documentation websites; and transparent record keeping of collaborator contributions.
-The continuous integration [@CI2017] tools provided by GitHub are used to trigger systematic retesting of module libraries with every edit.
-<!-- Imported -->These tests can be unit tests (to verify that small, isolated sections of code produce the correct output when run independently) and acceptance tests (to verify that the correct output is produced when multiple code components are run together to perform tasks that meet core user-requirements [@martin2003agile]).
-A useful concept for informing software users about the extensiveness of testing procedures is code coverage [@ERICWONG2010188] - reports of the proportion of code that has been explicitly tested.
-The module authoring libraries use the codecov [@codecov_2022] service to measure and share information about code coverage.
+Framework libraries are designed to be used in conjunction with a number of online services.
+The  module authoring libraries use the GitHub [@github2007] service's tools for: software development, testing, version control and distribution; hosting of documentation websites; and transparent record keeping of collaborator contributions.
+Continuous integration [@CI2017] tools provided by GitHub are used to trigger systematic retesting of module libraries with every edit.
+<!-- Imported -->Tests can be unit tests (verifying the correct output when small, isolated sections of code are run independently) and acceptance tests (verifying the correct output from multiple code components are run together to meet core user-requirements [@martin2003agile]).
+<!-- A useful concept for informing software users about the extensiveness of testing procedures is .
+-->The module authoring libraries use the codecov [@codecov_2022] service to measure and share information about code coverage [@ERICWONG2010188] - the proportion of code that has been explicitly tested.
 <!-- End_Imported -->The open science repository service Zenodo [@Zenodo2013] is used by the module authoring libraries to provide persistent storage, uniquely identified with a Digital Object Identifier (DOI), of each code release.
-The framework's data management tools use the Dataverse [@Dataverse2007] data repository service for persistent, uniquely identifiable and versioned storage of model input and output data.
+The ready4use library uses the Dataverse [@Dataverse2007] data repository service for persistent, uniquely identifiable and versioned storage of model input and output data.
 For the management of frequently updated datasets that do not require persistent storage, all framework libraries use GitHub.
@@
 A project documentation website (https://www.ready4-dev.com) provides guidance to model developers on how to use and contribute improvements to the ready4 software framework.
-The documentation website is versioned, which means documentation relating to prior versions of framework software can be archived, retrieved and viewed.
+Prior versions of the documentation website are archived and publicly accessible.
 The documentation website was developed using the Hugo framework [@hugo_2023], Docsy theme [@docsy_2023] and Algolia DocSearch [@algoliadocsearch_2023] and is hosted using the Netlify [@netlify_2023] service.
-We linked our Netlify account to our GitHub organisation so that the project website would automatically update whenever its source code (publicly available in a GitHub repository) was edited.
+We linked our Netlify account to our GitHub organisation so that the project website automatically updates whenever its (publicly available) source code is edited.

### 2024-03-01 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
ready for comparison

@@
 
-<!-- Imported_from_Ethics-->Key concerns for health economists when considering whether to reuse a model are generalisability (application without adaptation) and transferability (selective reuse and/or modification of model components) [@RN39].
+<!-- Imported_from_Ethics-->Key concerns for health economists when considering whether to reuse a model are generalisability (application without adaptation) and transferability (application of selected components and/or application with modification) [@RN39].
 Health economic models are likely to require at least some modification before they can be validly applied to a new jurisdiction, time period or decision problem.
-The difficulty of undertaking such a model transfer depends in part on whether third parties can readily understand, use and edit the software files that implement the model - the Computational Health Economic Model (CHEM).
+Making such modifications is harder if the software files that implement the model - the Computational Health Economic Model (CHEM) – cannot be readily understand, used and edited.
 
@@
 
-Some of the barriers<!-- Give examples --> to the development of transferable CHEMs <!-- that use open-source and modular approaches  -->could be addressed by appropriate software frameworks.<!-- Check last sentence was not used in ethics manuscript  --> A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users [@myllarniemi2018development].
+Some of the barriers<!-- Give examples --> to the development of transferable CHEMs <!-- that use open-source and modular approaches  -->could be addressed by appropriate software frameworks.<!-- Check last sentence was not used in ethics manuscript  --> A software framework is a shared common technology used by developers to collaboratively author software <!-- and which is not typically visible to software end-users  -->[@myllarniemi2018development].
 A software framework provides a foundation for developing multiple software applications with shared resources (e.g., code and data files), that can be modified to suit specific needs.
 Advantages of using software frameworks include facilitating code reuse and extension, promoting good programming practice and the capability to provide enhanced functionality and performance without additional effort by developers [@edwin2014software].
-Software frameworks have widely been developed and implemented in data science, for example, PyTorch [@PyTorch2019] for machine learning using Python.
+<!-- Software frameworks have widely been developed and implemented in data science, for example, PyTorch [@PyTorch2019] for machine learning using Python.
 However, software frameworks can be challenging and time consuming to create and may become excessively complex over time [@edwin2014software].
 Software frameworks can also be difficult to learn, often requiring model developers to undergo specialist training [@myllarniemi2018development].
+-->
 

### 2024-03-01 Markdown/Manuscript/Child_RMDs/MS_Tables_3.Rmd
ready for comparison

@@
                       escape = F,
+                      linesep = "\\addlinespace",
                       caption = knitr::opts_current$get("tab.cap")) %>%
@@
       kableExtra::column_spec(3, width = "20em",
-                              latex_valign = "m")
+                              latex_valign = "m") %>%
+      kableExtra::kable_styling(latex_options = "striped")
     }

### 2024-03-01 Markdown/Manuscript/Parent_PDF/Springer.Rmd
ready for comparison

@@
     info:
-#      orgdiv: XXXXXXXXXXX
+      orgdiv: Flinders Health and Medical Research Institute
       orgname: Flinders University   

### 2024-03-02 Markdown/Manuscript/Child_RMDs/MS_Body.Rmd
submission ready

@@
 <!-- Add child RMDs for results content -->
+
+**Key points for decision makers:**
+
+-	How health economic models are implemented as software significantly shapes how easy they are to transfer to other decision contexts.
+
+-	We have developed a software framework that can help implement a transparent, reusable and updatable economic model in youth mental health.
+
+-	Our framework can be a prototype for software tools that improve the transferability of health economic models more generally.
 
@@
 ```
+
+## Author contributions
+MPH led the conceptualisation and software implementation of ready4 and readyforwhatsnext and manuscript drafting.
+MH, CG and GW co-authored the software described in this article.
+All co-authors critically reviewed and revised manuscript drafts and approved the final manuscript text.

### 2024-03-02 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
submission ready

@@
 
-As illustrated by Table \@ref(tab:checktb), we have developed a software framework and used it to author CHEM modules that largely satisfy explicit criteria for transparency, reusability and updatability.
+We have developed a software framework and used it to author CHEM modules that largely satisfy explicit criteria for transparency, reusability and updatability.
 We have used toy data to demonstrate how these CHEM module libraries, originally developed for a single utility mapping study [@Hamilton2021.07.07.21260129], can be applied: (i) to datasets from new samples with different concepts and variable names; (ii) to construct models with different utility instruments, predictors and covariates; and (iii) to develop and use both cross-sectional and longitudinal mapping models.
@@
 Factors such as <!-- user enjoyment,  -->usability, active user-community and supporting resources influence adoption of software frameworks [@myllarniemi2018development].
-To systematically address these issues for our prototype software framework would require investments in engaging the health economic modelling community to refine framework user requirements, software re-development and testing to meet those requirements, integration with evolving code and documentation authoring capabilities of large language models, the development of improved and more comprehensive documentation and training resources and proactive user-community building and support.
+To systematically address these issues for our prototype would require investments in: (i) engaging the health economic modelling community in refining framework user requirements; (ii) undertaking software re-development and testing to meet those requirements: (iii) incoporating the evolving code and documentation authoring capabilities of large language models; (iv) the development of improved and more comprehensive documentation and training resources; and (v) proactive user-community building and support.
 We currently lack the resources to undertake these tasks.

### 2024-03-02 Markdown/Manuscript/Child_RMDs/MS_Imp_Motivation.Rmd
submission ready

@@
 We are principally interested in using readyforwhatsnext to answer policy questions relating to the mental health of young people in Australia.
-Australian public mental health services can be planned and commissioned by the Australian Government, the governments of Australia's state and territories and independent organisations focused on smaller regions called Primary Health Networks.
+Australian public mental health services can be planned and commissioned by the Australian Government, the governments of Australia's state and territories and independent, regionally focused organisations called Primary Health Networks.
 <!-- Promoting mentally healthy local communities is also an important role for Australian local governments.
@@
 -->When undertaking analyses intended to inform decision-making, readyforwhatsnext uses real Australian data (which can be empirical, simulated or assumption-based).
-To help demonstrate the potential transferability of readyforwhatsnext to other decision contexts, we are creating toy datasets.
+To help demonstrate the potential transferability of readyforwhatsnext to other decision contexts, we are creating synthetic or toy datasets ("fake" data that realistically represent the key features of observed data, but which can be shared without confidentiality concerns  [@bellovin2019privacy]).
 <!-- PHNS -->A high-level schematic guiding our implementation of readyforwhatsnext is outlined in Figure \@ref(fig:fig1).

### 2024-03-06 Markdown/Manuscript/Child_RMDs/MS_Body.Rmd
safety

@@
 
-## Author contributions
+## Author contributions{-#author-contributions}
 MPH led the conceptualisation and software implementation of ready4 and readyforwhatsnext and manuscript drafting.
-MH, CG and GW co-authored the software described in this article.
+MPH, CG and GW co-authored the software described in this article.
 All co-authors critically reviewed and revised manuscript drafts and approved the final manuscript text.

### 2024-03-06 Markdown/Manuscript/LaTeX/Resubmission_files/Submission.tex
safety

%Version 2.1 April 2023
% See section 11 of the User Manual for version history
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                 %%
%% Please do not use \input{...} to include other tex files.       %%
%% Submit your LaTeX manuscript as one .tex document.              %%
%%                                                                 %%
%% All additional figures and files should be attached             %%
%% separately and not embedded in the \TeX\ document itself.       %%
%%                                                                 %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[sn-vancouver,Numbered,pdflatex]{sn-jnl}

%%%% Standard Packages
%%<additional latex packages if required can be included here>

\usepackage{graphicx}%
\usepackage{multirow}%
\usepackage{amsmath,amssymb,amsfonts}%
\usepackage{amsthm}%
\usepackage{mathrsfs}%
\usepackage[title]{appendix}%
\usepackage{xcolor}%
\usepackage{textcomp}%
\usepackage{manyfoot}%
\usepackage{booktabs}%
\usepackage{algorithm}%
\usepackage{algorithmicx}%
\usepackage{algpseudocode}%
\usepackage{listings}%
%%%%

%%%%%=============================================================================%%%%
%%%%  Remarks: This template is provided to aid authors with the preparation
%%%%  of original research articles intended for submission to journals published
%%%%  by Springer Nature. The guidance has been prepared in partnership with
%%%%  production teams to conform to Springer Nature technical requirements.
%%%%  Editorial and presentation requirements differ among journal portfolios and
%%%%  research disciplines. You may find sections in this template are irrelevant
%%%%  to your work and are empowered to omit any such section if allowed by the
%%%%  journal you intend to submit to. The submission guidelines and policies
%%%%  of the journal take precedence. A detailed User Manual is available in the
%%%%  template package for technical guidance.
%%%%%=============================================================================%%%%

%% Per the spinger doc, new theorem styles can be included using built in style, 
%% but it seems the don't work so commented below
%\theoremstyle{thmstyleone}%
\newtheorem{theorem}{Theorem}%  meant for continuous numbers
%%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
%% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
\newtheorem{proposition}[theorem]{Proposition}%
%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.

%% \theoremstyle{thmstyletwo}%
\theoremstyle{remark}
\newtheorem{example}{Example}%
\newtheorem{remark}{Remark}%

%% \theoremstyle{thmstylethree}%
\theoremstyle{definition}
\newtheorem{definition}{Definition}%

\usepackage{float}
\let\origfigure\figure
\let\endorigfigure\endfigure
\renewenvironment{figure}[1][2] {
    \expandafter\origfigure\expandafter[H]
} {
    \endorigfigure
}
\usepackage{lscape}
\usepackage{pdflscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}
\usepackage[none]{hyphenat}
\usepackage[export]{adjustbox}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{array}
\usepackage{wrapfig}
\usepackage{colortbl}
\usepackage{booktabs} 
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage[normalem]{ulem}
\usepackage{threeparttablex}
\usepackage{makecell}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\raggedbottom

% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% From pandoc table feature
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}

\begin{document}

\title[Framework for transferable computational models]{A prototype software framework for transferable computational health economic models and its early application in youth mental health}

%%=============================================================%%
%% Prefix	-> \pfx{Dr}
%% GivenName	-> \fnm{Joergen W.}
%% Particle	-> \spfx{van der} -> surname prefix
%% FamilyName	-> \sur{Ploeg}
%% Suffix	-> \sfx{IV}
%% NatureName	-> \tanm{Poet Laureate} -> Title after name
%% Degrees	-> \dgr{MSc, PhD}
%% \author*[1,2]{\pfx{Dr} \fnm{Joergen W.} \spfx{van der} \sur{Ploeg} \sfx{IV} \tanm{Poet Laureate}
%%                 \dgr{MSc, PhD}}\email{iauthor@gmail.com}
%%=============================================================%%

\author*[1,2]{\fnm{Matthew} \spfx{P} \sur{Hamilton} }\email{\href{mailto:matthew.hamilton1@monash.edu}{\nolinkurl{matthew.hamilton1@monash.edu}}}

\author[2,3,1]{\fnm{Caroline} \sur{Gao} }

\author[4]{\fnm{Glen} \sur{Wiesner} }

\author[2,3]{\fnm{Kate} \spfx{M} \sur{Filia} }

\author[2,3]{\fnm{Jana} \spfx{M} \sur{Menssink} }

\author[5]{\fnm{Petra} \sur{Plencnerova} }

\author[2,3]{\fnm{David} \spfx{G} \sur{Baker} }

\author[2,3]{\fnm{Patrick} \spfx{D} \sur{McGorry} }

\author[6,3]{\fnm{Alexandra} \sur{Parker} }

\author[7]{\fnm{Jonathan} \sur{Karnon} }

\author[2,3]{\fnm{Sue} \spfx{M} \sur{Cotton} }

\author[1]{\fnm{Cathrine} \sur{Mihalopoulos} }

  \affil*[1]{\orgdiv{School of Public Health and Preventive Medicine}, \orgname{Monash University}, \orgaddress{\city{Melbourne}, \country{Australia}}}
  \affil[2]{\orgname{Orygen}, \orgaddress{\city{Parkville}, \country{Australia}}}
  \affil[3]{\orgdiv{Centre for Youth Mental Health}, \orgname{The University of Melbourne}, \orgaddress{\city{Parkville}, \country{Australia}}}
  \affil[4]{\orgname{Heart Foundation}, \orgaddress{\city{Docklands}, \country{Australia}}}
  \affil[5]{\orgname{headspace National Youth Mental Health Foundation}, \orgaddress{\city{Melbourne}, \country{Australia}}}
  \affil[6]{\orgdiv{Institute for Health and Sport}, \orgname{Victoria University}, \orgaddress{\city{Footscray}, \country{Australia}}}
  \affil[7]{\orgdiv{Flinders Health and Medical Research Institute}, \orgname{Flinders University}, \orgaddress{\city{Adelaide}, \country{Australia}}}

\abstract{\textbf{Summary: } We are developing an economic model to explore multiple topics in Australian youth mental health policy. We want that model to be readily transferable to other jurisdictions. We developed a software framework for authoring transparent, reusable and updatable Computational Health Economic Models (CHEMs) (the software files that implement health economic models). We specified framework user requirements of a template CHEM module that facilitates modular model implementations, a simple programming syntax and tools for authoring new CHEM modules, supplying CHEMs with data, reporting reproducible CHEM analyses, searching for CHEM modules and maintaining a CHEM project website. We implemented the framework as six development version code libraries in the programming language R that integrate with online services for software development and research data archiving. We used the framework to author five development version R libraries of CHEM modules focused on utility mapping in youth mental health. These modules provide tools for variable validation, dataset description, multi-attribute instrument scoring, construction of mapping models, reporting of mapping studies and making out of sample predictions. We assessed these CHEM module libraries as mostly meeting transparency, reusability and updatability criteria that we have previously developed, but requiring more detailed documentation and unit testing of individual modules. Our software framework has potential value as a prototype for future tools to support the development of transferable CHEMs. \newline \newline \textbf{Code: } Visit \url{https://www.ready4-dev.com} for more information about how to find, install and apply the prototype software framework. \newline \newline}

\keywords{adolescence, computational models, health economics, mental disorders, open-source models, software frameworks}

\pacs[JEL Classification]{C63, C88, I10}
\pacs[MSC Classification]{91-08}

\maketitle

\textbf{Key points for decision makers:}

\begin{itemize}
\item
  How health economic models are implemented as software significantly shapes how easy they are to transfer to other decision contexts.
\item
  We have developed a software framework that can help implement a transparent, reusable and updatable economic model in youth mental health.
\item
  Our framework can be a prototype for software tools that improve the transferability of health economic models more generally.
\end{itemize}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Computational models, particularly those addressing economic topics, have become essential tools for health policy development \citep{dakin2015influence, Erdemir2020}. Although influential and widely used, health economic models can be skills and resource intensive to develop. One suggestion for making health economic modelling projects more tractable is for health economists to re-use each other's models \citep{Arnold2010}.

Key concerns for health economists when considering whether to reuse a model are generalisability (application without adaptation) and transferability (application of selected components and/or application with modification) \citep{RN39}. Health economic models are likely to require at least some modification before they can be validly applied to a new jurisdiction, time period or decision problem. Making such modifications is harder if the software files that implement the model - the Computational Health Economic Model (CHEM) -- cannot be readily understand, used and edited.

Some of the barriers to the development of transferable CHEMs could be addressed by appropriate software frameworks. A software framework is a shared common technology used by developers to collaboratively author software \citep{myllarniemi2018development}. A software framework provides a foundation for developing multiple software applications with shared resources (e.g., code and data files), that can be modified to suit specific needs. Advantages of using software frameworks include facilitating code reuse and extension, promoting good programming practice and the capability to provide enhanced functionality and performance without additional effort by developers \citep{edwin2014software}.

In this paper, we describe:

\begin{enumerate}
\def\labelenumi{(\roman{enumi})}
\item
  our motivation for developing a transferable CHEM in youth mental health;
\item
  a prototype software framework we have developed to support the development of transferable CHEMs; and
\item
  how we have applied the prototype software framework to undertake initial development of our youth mental health CHEM.
\end{enumerate}

\hypertarget{motivation}{%
\section{Motivation}\label{motivation}}

We became interested in solving some of the technical barriers to transferable CHEMs in 2018 when considering how to synthesise multiple youth mental health economic modelling projects in one multi-purpose model. This overarching youth mental health model is called readyforwhatsnext \citep{rfwn2024}.

\hypertarget{economic-topics}{%
\subsection{Economic topics}\label{economic-topics}}

We are constructing readyforwhatsnext from projects in four of the twelve domains of health economics identified by Wagstaff and Culyer \citep{wagstaff2012four}. These are:

\begin{itemize}
\item
  health and its value (our projects: models to map psychological and functional measures to health utility);
\item
  determinants of health and ill-health (our projects: models for creating synthetic household populations with key risk and protective factors for mental disorders);
\item
  demand for health and health care (our projects: spatial epidemiology and help-seeking choice models); and
\item
  supply of health services (our projects: a model of primary mental health care services for young people).
\end{itemize}

Potential future directions for readyforwhatsnext may incorporate projects in two additional domains: (i) public health (to model the impact of selected fiscal policy and regulation options on young people's mental health); and (ii) human resources (to model the supply and behaviours of the youth mental health workforce). Our ultimate aim is to flexibly combine model components in analyses that answer questions in a further two domains:

\begin{itemize}
\item
  efficiency and equity (our goal: assess the distributional impacts and identify the optimal targeting of youth mental health interventions); and
\item
  economic evaluation (our goal: assess the cost-utility of competing policy options for improving the mental health of young people).
\end{itemize}

\hypertarget{transferability}{%
\subsection{Transferability}\label{transferability}}

We are principally interested in using readyforwhatsnext to answer policy questions relating to the mental health of young people in Australia. Australian public mental health services can be planned and commissioned by the Australian Government, the governments of Australia's state and territories and independent, regionally focused organisations called Primary Health Networks. The mental health of young people is a global priority \citep{https://doi.org/10.1002/wps.20938} and Australia has initiated youth mental health service model reforms that have been adopted in other jurisdictions \citep{RN27}. For these reasons, we aim to develop readyforwhatsnext in a manner that facilitates its transfer to multiple decision contexts.

However, there are ethical risks associated with each potential transfer, in particular the need to ensure the social acceptability, fitness for purpose and appropriate use of a CHEM in each new decision context \citep{ethicsCHEMS2024}. We therefore aim for readyforwhatsnext to meet six \emph{transparency}, \emph{reusability} and \emph{updatability} (TRU) criteria. We have described these criteria and their origins in ethical modelling practice elsewhere \citep{ethicsCHEMS2024}, but briefly they are:

T1) Software files are open access;

T2) Developer contributions and judgments on appropriate use are easily identified;

R1) Programming practices promote selective reuse;

R2) Licenses permit derivative works;

U1) Maintenance infrastructure is in place; and

U6) Releases are systematically retested and deprecated.

To meet these criteria we are implementing readyforwhatsnext as an open-source, modular model. Open source projects grant third parties permissions to access, use and modify model source code and data. A modular model is constructed from multiple reusable and replaceable sub-models (modules) \citep{pan2021modular}. When undertaking analyses intended to inform decision-making, readyforwhatsnext uses real Australian data (which can be empirical, simulated or assumption-based). To help demonstrate the potential transferability of readyforwhatsnext to other decision contexts, we are creating synthetic or toy datasets (``fake'' data that realistically represent the key features of observed data, but which can be shared without confidentiality concerns \citep{bellovin2019privacy}). A high-level schematic guiding our implementation of readyforwhatsnext is outlined in Figure \ref{fig:fig1}.

\bgroup 
    \origfigure[H]

\includegraphics[width=400px,]{Figure1} \caption{High level summary of planned implementation of youth mental health economic model}\label{fig:fig1}

    \endfigure
\egroup

\hypertarget{prototype-software-framework}{%
\section{Prototype software framework}\label{prototype-software-framework}}

To help readyforwhatsnext meet all six TRU criteria, we developed a prototype software framework called ready4 \citep{ready424}.

\hypertarget{framework-user-requirements}{%
\subsection{Framework user requirements}\label{framework-user-requirements}}

The framework user requirements (FURs) for ready4 evolved over six years (2018-2024) as we encountered new implementation issues for readyforwhatsnext that we needed to solve. Currently, these requirements are:

FUR 1) A reusable \emph{template} for CHEM modules that can be: (i) run as independent models; (ii) safely combined, sharing inputs and outputs with each other without unintended interference; and (iii) selectively replaced, updated or extended.

FUR 2) A \emph{programming syntax} that promotes simplicity and consistency in how algorithms associated with CHEM modules are: (i) labelled; and (ii) used in health economic analysis programs.

FUR 3) \emph{Module authoring tools} that integrate with online software development services to help author CHEM modules that are: (i) created using the template module; (ii) written in a consistent house style; (iii) always at least minimally documented; (iv) licensed for reuse; (v) bundled as R libraries with authorship, funding source, version number and Digital Object Identifier (DOI) metadata; and (vi) quality assured with publicly available testing artefacts.

FUR 4) \emph{Data management tools} that integrate with online data repository services to streamline: (i) the ingesting and labeling of confidential and non-confidential data; and (ii) the sharing of non-confidential data.

FUR 5) \emph{Reporting tools} that: help (i) author reporting template programs for rendering HTML, Adobe PDF and Microsoft Word outputs; (ii) retrieve version specific reporting template programs from online code repositories and (iii) supply reporting template programs with study specific data (e.g., authorship details, input data and analysis results) to render custom reports.

FUR 6) \emph{Search tools} to retrieve web-based information on a CHEM project's: (i) model modules and tutorials; (ii) datasets and data collections; and (iii) replication and reporting template programs.

FUR 7) \emph{Documentation tools} that integrate with open source website development and hosting infrastructure to help: (i) develop a CHEM project documentation website that consolidates content from the websites of individual CHEM module libraries, datasets and programs; and (ii) partially automate the updating of website resources such as tutorials and itemised lists of code and data releases.

\hypertarget{framework-implementation}{%
\subsection{Framework implementation}\label{framework-implementation}}

We implemented ready4 as R \citep{RCORE2022} code libraries that integrate with a number of online services. The framework is documented by a project website.

\hypertarget{r-libraries}{%
\subsubsection{R libraries}\label{r-libraries}}

R libraries typically depend on other R libraries. As the number of dependencies of an R library grows, so does the fragility of that library (e.g., the library may cease to work as intended due to changes in one of its dependency libraries). To reduce the fragility of our framework we implemented it as multiple R libraries rather than one R library. We authored six novel R libraries to implement the ready4 framework, all of which have distinct purposes and dependencies (Table \ref{tab:cpkgs}).

To meet \emph{FUR 1}, the ready4 \citep{ready4lib24} foundation library defines a template CHEM module using R's S4 class system, that supports an object-oriented programming paradigm. Two notable features of object-oriented programming are encapsulation \citep{8717448} and inheritance \citep{8717448}. Encapsulation allows a CHEM module to bundle model data and algorithms in a protected environment, which is useful for helping ensure that CHEM modules continue to work as intended when combined. Inheritance allows new CHEM modules to inherit some or all of the properties of a parent module. Inheritance is useful when modifying CHEM modules, for example to account for: (i) interaction effects when CHEMs are combined; or (ii) distinctive features of a new decision contexts to which they are being transferred. The ready4 template CHEM module can be used to create other CHEM modules that inherit a common set of properties. One of these inherited properties is a novel syntax of 15 core commands that enable CHEM module algorithms to be consistently named and described (meeting \emph{FUR 2}). The ready4 library also contains tools for retrieving web-based information on CHEM modules, datasets and analysis programs (meeting \emph{FUR 6}) and tools for developing and maintaining a CHEM project's documentation website (meeting \emph{FUR 7}).

Three module authoring libraries are designed to meet \emph{FUR 3}. The ready4fun \citep{ready4funlib24} library contains tools for writing functions in a consistent house style and automatically generating basic documentation for each function. The ready4class \citep{ready4classlib24} library contains tools to help streamline and standardise the authoring of novel, documented CHEM modules from the template CHEM module. The ready4pack \citep{ready4packlib24} library provides tools for disseminating themed bundles of CHEM modules as R libraries that are: documented (with a website and PDF manuals); licensed (using the copyleft GNU GPL-3 {[}66{]} by default); easily citable (citation information can be retrieved within an R session or from hosting repositories); and quality assured (each update triggers the running of any tests created by module library authors, with test results publicly documented).

The ready4use \citep{ready4uselib24} library for managing CHEM data contains tools for supplying CHEM modules with input data ingested from local (i.e., a user's computer) or remote (online repositories) locations, labelling CHEM module datasets and exporting CHEM module data to online repositories (meeting \emph{FUR 4}). The ready4show \citep{ready4showlib24} library for authoring reproducible analysis programs and reporting subroutines (\emph{FUR5}) contains tools to help write executables that apply CHEM modules to compatible datasets for the purpose of undertaking reproducible health economic analyses. The library supports the creation of analysis programs that are self-documenting (code is integrated with plain English explanations of what it does) and subroutines that can be used as templates that trigger the creation of explanatory documents (e.g., a scientific manuscript).

\begin{table}
\centering\centering
\caption{\label{tab:cpkgs}Software framework R libraries}
\centering
\begin{tabular}[t]{l>{\raggedright\arraybackslash}m{20em}>{\raggedright\arraybackslash}m{20em}}
\toprule
Library & Purpose & R library dependencies\\
\midrule
\cellcolor{gray!10}{ready4} & \cellcolor{gray!10}{Provide a template and novel syntax for modular CHEM implementations and tools for finding interoperable CHEM modules, datasets and reproducible analysis programs.} & \cellcolor{gray!10}{dataverse dplyr gh kableExtra lifecycle magrittr methods piggyback purrr rlang rvest stats stringi stringr tibble tidyRSS tidyselect tools utils}\\
\addlinespace
ready4fun & Streamline and standardise the authoring and documenting of functions that support transferable and generalisable model algorithms. & desc devtools dplyr gert Hmisc lifecycle lubridate magrittr methods piggyback pkgdown purrr readxl ready4 ready4show ready4use rlang sinew stats stringi stringr testit tibble tidyr tools usethis utils xfun\\
\addlinespace
\cellcolor{gray!10}{ready4class} & \cellcolor{gray!10}{Streamline and standardise the authoring and documenting of new interoperable CHEM modules.} & \cellcolor{gray!10}{devtools dplyr fs gtools Hmisc knitr lifecycle magrittr methods purrr ready4 ready4fun ready4show rlang stats stringi stringr testit testthat tibble tidyr usethis utils}\\
\addlinespace
ready4pack & Help bundle and disseminate newly created CHEM modules as R libraries that are documented, licensed and quality assured. & dataverse dplyr knitr lifecycle magrittr methods purrr ready4 ready4class ready4fun rlang stringr testthat tibble tidyr utils\\
\addlinespace
\cellcolor{gray!10}{ready4use} & \cellcolor{gray!10}{Help manage the labelling and transfer of data between CHEM modules and local and remote data repositories.} & \cellcolor{gray!10}{data.table dataverse dplyr fs Hmisc knitr lifecycle magrittr methods piggyback purrr readxl ready4 ready4show rlang stats stringi stringr testit testthat tibble tidyr utils}\\
\addlinespace
ready4show & Facilitate the use of CHEM modules in programs to implement integrated and reproducible data ingest, analysis and reporting pipelines. & dataverse DescTools dplyr flextable grDevices here Hmisc kableExtra knitr knitrBootstrap lifecycle magrittr methods officer purrr ready4 rlang rmarkdown stringi stringr testthat tibble tidyr utils xtable\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{online-services}{%
\subsubsection{Online services}\label{online-services}}

Framework libraries are designed to be used in conjunction with a number of online services. The module authoring libraries use the GitHub \citep{github2007} service's tools for: software development, testing, version control and distribution; hosting of documentation websites; and transparent record keeping of collaborator contributions. Continuous integration \citep{CI2017} tools provided by GitHub are used to trigger systematic retesting of module libraries with every edit. Tests can be unit tests (verifying the correct output when small, isolated sections of code are run independently) and acceptance tests (verifying the correct output from multiple code components are run together to meet core user-requirements \citep{martin2003agile}). The module authoring libraries use the codecov \citep{codecov_2022} service to measure and share information about code coverage \citep{ERICWONG2010188} - the proportion of code that has been explicitly tested. The open science repository service Zenodo \citep{Zenodo2013} is used by the module authoring libraries to provide persistent storage, uniquely identified with a Digital Object Identifier (DOI), of each code release. The ready4use library uses the Dataverse \citep{Dataverse2007} data repository service for persistent, uniquely identifiable and versioned storage of model input and output data. For the management of frequently updated datasets that do not require persistent storage, all framework libraries use GitHub.

\hypertarget{documentation-website}{%
\subsubsection{Documentation website}\label{documentation-website}}

A project documentation website (\url{https://www.ready4-dev.com}) provides guidance to model developers on how to use and contribute improvements to the ready4 software framework. Prior versions of the documentation website are archived and publicly accessible. The documentation website was developed using the Hugo framework \citep{hugo_2023}, Docsy theme \citep{docsy_2023} and Algolia DocSearch \citep{algoliadocsearch_2023} and is hosted using the Netlify \citep{netlify_2023} service. We linked our Netlify account to our GitHub organisation so that the project website automatically updates whenever its (publicly available) source code is edited.

\hypertarget{prototype-model-modules}{%
\section{Prototype model modules}\label{prototype-model-modules}}

Our early use of the ready4 framework has focused on developing readyforwhatsnext modules for constructing, sharing and using utility mapping models in youth mental health.

\hypertarget{model-user-requirements}{%
\subsection{Model user requirements}\label{model-user-requirements}}

The model user requirements (MURs) that we specified for the readyforwhatsnext's initial modules are:

MUR 1) \emph{Variable validation tools} that: (i) define the allowable values and numeric class (integer or double precision) associated with different psychological, functional and health utility measures appropriate for use in youth mental health samples; (ii) provide an informative error message that halts an analysis or reporting program's execution should impermissible values be assigned to each measure.

MUR 2) \emph{Dataset description tools} that: (i) attach structured metadata to a human records dataset that specify unique person identifier, group assignment and data collection round variables; and (ii) generate tabular and graphical summaries of dataset descriptive statistics.

MUR 3) \emph{Multi-attribute instrument scoring tools} that: (i) attach structured metadata about an instrument (e.g.~name, version, country, items, domains, parameter values for scoring algorithms) to a human records dataset; (ii) apply pre-written (for AQol-6D \citep{Richardson2012AQ} and EQ-5D \citep{devlin2017eq} instruments) or user-supplied instrument scoring functions to a human records dataset; and (iii) generate descriptive plots of a dataset's instrument scores for individual items, domains and totals (weighted and unweighted).

MUR 4) \emph{Utility mapping model construction tools} that: (i) attach structured metadata about the target utility instrument and candidate predictor variables and covariates to be used in constructing utility mapping models to a human records dataset; (ii) generate descriptive tables, a correlation matrix and plots about the variables to be assessed for inclusion in models; (iii) attach structured metadata about the candidate utility mapping models to be assessed; (iv) generate tabular and graphical summaries of the performance of each combination of model, predictors and covariates specified for evaluation by either a user or by a default algorithm; (v) strip confidential records from the constructed models so that they are able to be publicly shared.

MUR 5) \emph{Utility mapping study reporting tools} that: (i) generate from a reporting template a PDF catalogue summarising the predictive performance under multiple configurations of utility mapping models selected for public dissemination; (ii) generate from a reporting template (either a pre-written default or a user-supplied customisation) a scientific manuscript summarising a utility mapping study; (iii) share model catalogues and (if desired) scientific summary along with metadata about utility mapping models in an open access repository; and (iv) facilitate the authoring of a consolidated study replication program that implements data ingest, instrument scoring, model construction, report authoring and dissemination of study artefacts.

MUR 6) \emph{Utility prediction tools} that: (i) search open access repositories for utility mapping models developed with readyforwhatsnext; (ii) retrieve relevant metadata, including a link to the model catalogue for models specified by a user; (iii) apply selected utility mapping models to make out of sample predictions using a dataset provided by a user; and (iv) (where there is health utility data at two time points) convert predicted health utility scores to Quality Adjusted Life Years (QALYs).

\hypertarget{model-implementation}{%
\subsection{Model implementation}\label{model-implementation}}

\hypertarget{online-service-configuration}{%
\subsubsection{Online service configuration}\label{online-service-configuration}}

We established and configured accounts with the online services supported by ready4. We created a GitHub organisation (a collection of code repositories) where source code that we author is stored and version controlled at \url{https://github.com/ready4-dev/}. We configured individual repositories in our GitHub organisation to implement continuous integration to assess the compliance of our module libraries with policies specified by the Comprehensive R Archive Network (CRAN) \citep{CRAN2022}. To facilitate the creation and hosting of module library websites, we enabled GitHub Pages in each code repository. We also created a Zenodo community, a collection of permanent, uniquely identified repositories, at \url{https://zenodo.org/communities/ready4/}. We then linked our Zenodo community and GitHub organisation so that every time we specify a version of code in one of our GitHub repositories as a ``release'', a copy of that code is automatically archived on Zenodo with a DOI. Finally, to manage model datasets, we created a dedicated collection (\url{https://dataverse.harvard.edu/dataverse/ready4}) within the Harvard Dataverse installation.

\hypertarget{module-libraries}{%
\subsubsection{Module libraries}\label{module-libraries}}

We used all six ready4 framework libraries to author five development version readyforwhatsnext module libraries (Table \ref{tab:rfwnlibs}). These libraries are youthvars \citep{hamilton_matthew_2022_6084467} which addresses MURs 1 and 2, scorz \citep{hamilton_matthew_2022_6084824} which addresses MUR 3, specific \citep{hamilton_matthew_2022_6116701} which addresses MUR 4, TTU \citep{gao_caroline_2022_6130155} which addresses MUR 5 and youthu \citep{matthew_p_hamilton_2021_5646669} which addresses MUR 6.

\hypertarget{reporting-templates}{%
\subsubsection{Reporting templates}\label{reporting-templates}}

We used the ready4show library to author two reporting templates that are designed to be used in conjunction with these utility mapping modules. The first reporting template \citep{hamilton_matthew_2022_6116385} is used to create a catalogue of utility mapping models. The second reporting template \citep{matthew_p_hamilton_2022_5976988} can be used to generate a manuscript providing a scientific summary of each study implemented with these modules.

\hypertarget{application}{%
\subsubsection{Application}\label{application}}

We have previously described a study \citep{Hamilton2021.07.07.21260129} that used these module libraries and reporting templates to develop and document utility mapping models in a sample of young people presenting to primary mental health services. We used these module libraries to write programs for replicating that study's reporting and analysis algorithm \citep{hamilton_matthew_2022_6129906}, to demonstrate how to apply the utility mapping models constructed in that study to new data \citep{hamilton_matthew_2022_6416330} and to generate a synthetic representation of the study dataset \citep{hamilton_matthew_p_2022_6321821}. We also created an open access study input parameters and results dataset \citep{DVN/DKDIB0_2021} and toy datasets to help demonstrate the transferability of the study algorithm \citep{DVN/HJXYKQ_2021}.

\begin{table}
\centering\centering
\caption{\label{tab:rfwnlibs}Model module libraries for utility mapping}
\centering
\begin{tabular}[t]{l>{\raggedright\arraybackslash}m{20em}>{\raggedright\arraybackslash}m{20em}}
\toprule
Library & Purpose & R library dependencies\\
\midrule
\cellcolor{gray!10}{youthvars} & \cellcolor{gray!10}{Describe and validate youth mental health human record datasets.} & \cellcolor{gray!10}{arsenal assertthat car cowplot dplyr ggplot2 ggpubr gridExtra here Hmisc hutils kableExtra knitr knitrBootstrap lifecycle lubridate magrittr MASS Matrix matrixcalc methods mice psych purrr ready4 ready4show ready4use rlang scales simstudy stats stringi stringr testthat tibble tidyselect utils}\\
\addlinespace
scorz & Score multi-attribute instruments. & dplyr eq5d Hmisc hutils knitr knitrBootstrap lifecycle magrittr methods mice purrr ready4 ready4use rlang simstudy stats stringi stringr testthat tibble tidyselect youthvars\\
\addlinespace
\cellcolor{gray!10}{specific} & \cellcolor{gray!10}{Construct and evaluate utility mapping models.} & \cellcolor{gray!10}{assertthat boot Boruta brms caret cowplot dataverse DescTools dplyr enrichwith ggalt ggfortify ggplot2 gtools here Hmisc hutils kableExtra knitr knitrBootstrap lifecycle magrittr MASS methods parallel psych purrr randomForest ready4 ready4show ready4use rlang scorz stats stringi stringr synthpop testthat tibble tidyr tidyselect utils viridis xfun youthvars}\\
\addlinespace
TTU & Implement reproducible utility mapping sudies. & dplyr ggplot2 Hmisc knitr lifecycle magrittr methods purrr R.utils ready4 ready4show ready4use rlang scorz specific stringr testthat utils\\
\addlinespace
\cellcolor{gray!10}{youthu} & \cellcolor{gray!10}{Apply utility mapping models to out of sample data.} & \cellcolor{gray!10}{assertthat BCEA boot dataverse dplyr lifecycle lubridate magrittr MatchIt methods purrr ready4 ready4use rlang specific stats stringi stringr tibble tidyr tidyselect truncnorm utils youthvars}\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{documentation-website-1}{%
\subsection{Documentation website}\label{documentation-website-1}}

Using the framework website as a template, we used the search and documentation tools from the ready4 library to create and maintain a project documentation website (\url{https://readyforwhatsnext.org/}). The project website includes details on available model modules, datasets and analysis programs and tutorials on how these artefacts can be used.

\hypertarget{transferability-assessment}{%
\subsection{Transferability assessment}\label{transferability-assessment}}

We subjectively assessed these utility mapping model artefacts against TRU criteria (Table \ref{tab:checktb}). For each criterion, we provided a global assessment of whether it was met using the responses ``yes'', ``no'' or ``partial''. We believe that our utility mapping study module libraries, code and data repositories and documentation have satisfactorily met four of the six criteria (T1, R1, R2 and U1) and have partially met two criteria (T2 and U2). The main shortcomings we identified were that individual modules and functions have yet to: (i) be supported with human authored documentation that includes examples of how they can be used; and (ii) be quality assured through unit testing.

\begin{landscape}

\begin{table}
\centering\centering
\caption{\label{tab:checktb}Assessment of a CHEM implementation in youth mental health using Transparent, Reusable and Updatable (TRU) criteria}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{10em}l>{\raggedright\arraybackslash}p{35em}}
\toprule
Criterion & Met? & Detail\\
\midrule
\cellcolor{gray!10}{\textbf{T1 Software files are open access}} & \cellcolor{gray!10}{Yes} & \cellcolor{gray!10}{All source code and testing procedures are available in public GitHub repositories, with each code release persistently available in a Zenodo repository. As the study dataset contains confidential patient records, it was not published. Instead, a synthetic representation of the study dataset is persistently available in a repository in the Harvard Dataverse. Data files to support out of sample application of models are published at the same location.}\\
\textbf{T2 Developer contributions and judgments on appropriate use are easily identified} & Partial & All module libraries, programs, and datasets are distributed with citation information. Public GitHub repositories detail author code contributions over project development history. Model catalogues persistently available on the Harvard Dataverse describe the predictive performance of models under multiple usage regimes. Each code library is documented with worked examples of how to apply CHEM modules. However, documentation of individual functions and methods are algorithm generated and need more customisation, including more examples of use. Analysis and reporting programs are self-documenting. Sub-routines for generating reports are documented with README files.\\
\cellcolor{gray!10}{\textbf{R1 Programming practices promote selective reuse}} & \cellcolor{gray!10}{Yes} & \cellcolor{gray!10}{CHEMs are written using both functional and object-oriented paradigms. Code library documentation websites include hypothetical examples of generalisability (applying study algorithm to estimate mapping models from new data with the same predictor and outcome variables) and transferability (adapting study algorithm to develop mapping models from datasets with different predictor variables and outcomes measured with a different utility instrument).}\\
\textbf{R2 Licenses permit derivative works} & Yes & All code is distributed using GPL-3 licenses. Datasets use an amended version of template terms provided by Harvard Dataverse, allowing reuse of data subject to some ethical restrictions (e.g., use in efforts to reidentify study participants is prohibited).\\
\cellcolor{gray!10}{\textbf{U1 Maintenance infrastructure is in place}} & \cellcolor{gray!10}{Yes} & \cellcolor{gray!10}{All code is version controlled using git and GitHub, with semantic versioning. Each code library has a specified maintainer and guidance for potential code contributors is available on the project website.}\\
\addlinespace
\textbf{U2 Releases are systematically retested and deprecated} & Partial & Continuous integration is used for all code libraries, primarily for acceptance testing. Only limited use is made of unit testing. Retired library code is deprecated using tools from the lifecycle R library. Library documentation articles and datasets are also deprecated.\\
\bottomrule
\end{tabular}
\end{table}

\end{landscape}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

We have developed a software framework and used it to author CHEM modules that largely satisfy explicit criteria for transparency, reusability and updatability. We have used toy data to demonstrate how these CHEM module libraries, originally developed for a single utility mapping study \citep{Hamilton2021.07.07.21260129}, can be applied: (i) to datasets from new samples with different concepts and variable names; (ii) to construct models with different utility instruments, predictors and covariates; and (iii) to develop and use both cross-sectional and longitudinal mapping models.

Our framework and CHEM module R libraries are currently publicly available as development releases. We plan to undertake a number of key improvements, such as more detailed documentation, comprehensive unit testing and streamlining dependencies, prior to submitting these libraries for quality assurance and dissemination by CRAN \citep{CRAN2022}.

Although designed to address challenges specific to our project, ready4 can be a prototype for future software frameworks that meet the user requirements of other modelling teams and projects. Our prototype has a number of features that such future work can build on. Firstly, developing a software framework to work within an existing and widely used open source programming language such as R, can keep framework scope relatively narrow. This makes it more tractable to develop, maintain and learn, and facilitates integration with other modelling tools written in that language (e.g., the dependency libraries we list in Tables \ref{tab:cpkgs} and \ref{tab:rfwnlibs}). Secondly, a sensible trade-off needs to be found between transparent code implementation (which requires clear and sufficiently detailed documentation) and prioritising the development of working code over writing documentation (a foundation principle of Agile Software Development \citep{beck2001manifesto}). Our software framework makes this trade off by enforcing the use of consistent code style conventions and file organisation which in turn enables automated generation of simple documentation at every CHEM module update.

Our framework addresses barriers to transferability specific to how a model is implemented as software (ie, CHEMs). Health economists must also consider conceptual or theoretical validity. For example, the candidate models currently available in our scorz library \citep{hamilton_matthew_2022_6084824} were chosen because of their suitability for mapping to the utility instrument (AQoL-6D \citep{Richardson2012AQ}) used in the study \citep{Hamilton2021.07.07.21260129} for which scorz was originally developed. We have identified a need to use alternative models for mapping to utility instruments that produce less continuous total score distributions \citep{Hamilton2021.07.07.21260129}. Our software framework is designed to make such extensions more straightforward to implement.

Factors such as usability, active user-community and supporting resources influence adoption of software frameworks \citep{myllarniemi2018development}. To systematically address these issues for our prototype would require investments in: (i) engaging the health economic modelling community in refining framework user requirements; (ii) undertaking software re-development and testing to meet those requirements: (iii) incoporating the evolving code and documentation authoring capabilities of large language models; (iv) the development of improved and more comprehensive documentation and training resources; and (v) proactive user-community building and support. We currently lack the resources to undertake these tasks.

Adequately planned, resourced and implemented software frameworks are potentially important enablers of improved health economic modelling practice. Reference models \citep{Afzali2013}, methodological innovation to improve model transferability \citep{craig2018taking} and the development of regularly updated CHEMs that can support ``living Health Technology Assessment'' \citep{thokala2023living} would all be facilitated by a trusted software framework for implementing more transparent, reusable and updatable CHEMs. A future software framework for CHEMs would ideally incorporate a base set of features useful to developers of computational models across all domains of public health and health economics, with the capability for community-led extensions that are tailored to the needs of modellers focused on specific health-conditions. Such approaches will likely be important to ensure a sufficient potential user-base to make CHEM software frameworks sustainable.

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

Our software framework provides a solution to some technical barriers we faced when seeking to implement a transferable CHEM in youth mental health. Our framework can be used as a prototype for developing future software frameworks that address the user-requirements of the broader health economic modelling community.

\hypertarget{acknowledgement}{%
\subsection*{Acknowledgement}\label{acknowledgement}}
\addcontentsline{toc}{subsection}{Acknowledgement}

The authors would like to acknowledge the contribution of John Gillam who provided advisory input to this research.

\hypertarget{availability-of-data-and-materials}{%
\subsection*{Availability of data and materials}\label{availability-of-data-and-materials}}
\addcontentsline{toc}{subsection}{Availability of data and materials}

The ready4 framework is documented at \url{https://www.ready4-dev.com}. Documentation on readyforwhatsnext is available at \url{https://readyforwhatsnext.org/}. Development versions of all code repositories referenced in this article are available in \url{https://github.com/ready4-dev/}. Archived code releases are available in \url{https://zenodo.org/communities/ready4}. All data repositories referenced in this article are available in \url{https://dataverse.harvard.edu/dataverse/ready4}.

\hypertarget{ethics-approval}{%
\subsection*{Ethics approval}\label{ethics-approval}}
\addcontentsline{toc}{subsection}{Ethics approval}

Software framework development did not involve human subject research and was not ethically reviewed. The utility mapping modules were originally developed to implement a previously reported study that was reviewed and granted approval by the University of Melbourne's Human Research Ethics Committee, and the local Human Ethics and Advisory Group (1645367.1).

\hypertarget{funding}{%
\subsection*{Funding}\label{funding}}
\addcontentsline{toc}{subsection}{Funding}

Software framework development was funded by Orygen, VicHealth, Victoria University and an Australian Government Research Training Program (RTP) Scholarship to Matthew Hamilton. The utility mapping study to which utility mapping modules were applied was funded by the National Health and Medical Research Council (NHMRC, APP1076940), Orygen and headspace.

\hypertarget{conflict-of-interest}{%
\subsection*{Conflict of Interest}\label{conflict-of-interest}}
\addcontentsline{toc}{subsection}{Conflict of Interest}

None declared.

\hypertarget{author-contributions}{%
\subsection*{Author contributions}\label{author-contributions}}

MPH led the conceptualisation and software implementation of ready4 and readyforwhatsnext and manuscript drafting. MPH, CG and GW co-authored the software described in this article. All co-authors critically reviewed and revised manuscript drafts and approved the final manuscript text.

\newpage
\appendix
\counterwithin{figure}{section}
\counterwithin{table}{section}

\bibliography{bibliography.bib}

\end{document}
